### 2024-06-02 paper.tex
draft as of 060124

\documentclass[aip, jcp, reprint, onecolumn]{revtex4-2}

\bibliographystyle{apsrev4-2}

\usepackage{physics}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage[colorlinks=true, linkcolor=black, urlcolor=blue, citecolor=black, anchorcolor=black]{hyperref}

\graphicspath{{"main/"}}
\begin{document}
%Title of paper
\title{Coherent Hyper-Raman Four Wave Mixing Spectroscopies}

\author{Ryan P. McDonnell} 
\author{Daniel D. Kohler}
\author{John C. Wright} \email{wright@chem.wisc.edu}

\affiliation{Department of Chemistry, 
        University of Wisconsin - Madison, 
        Madison, Wisconsin 53706, 
        United States of America}

\date{\today}

\begin{abstract}
Nonlinear, four wave mixing vibrational spectroscopies are often used to probe intramolecular vibrational coupling and relaxation dynamics.
Three wave mixing vibrational spectroscopies are similarly often used to understand the spectroscopy and dynamics of interfacial species.
Most of these methods rely on infrared or Raman transitions to generate output. 
The implementation of a nonlinear hyper-Raman spectroscopy, which first appears at third order perturbation theory, can provide a useful analogue to these techniques.
Singly Vibrationally Enhanced (SIVE) spectroscopy, a type of nonlinear hyper-Raman spectroscopy, is an underdeveloped four wave mixing technique which shows promise to disentangle ultrafast vibrational dynamics in isotropic systems without need for anharmonicities.
We derive selection rules and coherent interference effects in singly resonant SIVE (SR-SIVE).
The theory of SR-SIVE is extended to account for vibronic coupling induced by two-photon absorption, i.e. doubly resonant SIVE (DR-SIVE), akin to a resonant hyper-Raman process. 
DR-SIVE is shown to be a type of resonance IR spectroscopy and is likely able to resolve vibronic coupling.
The linenarrowing abilities of DR-SIVE are discussed.
We showcase the difference in selection rules of SR-SIVE and DR-SIVE through a study of cyanocobalamin, highlighting the sensitivity of these measurements on non-resonant and resonant hyper-Raman hyperpolarizabilities, respectively.
\end{abstract}

\maketitle

\section{Introduction}
Coherent multidimensional spectroscopy (CMDS) is a family of three and four wave mixing methods which form the optical analogue of multidimensional nuclear magnetic resonance (NMR) spectroscopy.\cite{Cho2008, RN335}
Multiresonant, four wave mixing CMDS experiments, first proposed by Oudar and Shen in 1980,\cite{RN307} directly probe coupling between different vibrational, electronic, and vibronic states. \cite{RN307, RN281, RN342, Cho2008, RN335, Ogilvie2019, RN325} 
CMDS has resolved intramolecular vibrational, vibronic, excitonic, and electronic coupling in numerous systems. \cite{Carlson1990, RN345, RN342, RN343, RN324, Czech2015, Gaynor2017, Ogilvie2019, RN325}
A particular class of CMDS methods, coherent Raman based four wave mixing spectroscopies, can provide explicit probes of vibrational and excitonic coupling in a variety of systems.

Not all CMDS methods are used to dissect intramolecular couplings.\cite{Shen1987_CPL}
Singly vibrationally enhanced (SIVE) is a four wave mixing method which, when detuned from  electronic resonances, does not probe intramolecular couplings. 
Non-parametric, singly resonant SIVE (SR-SIVE) spectroscopy was the first infrared CMDS method to successfully discriminate against non-resonant background.\cite{RN351, RN352}
In SR-SIVE, an infrared pulse is resonant with a vibrational mode, and two other input pulses are used to induce a scattering process to provide output.
SIVE was documented long ago to have characteristics similar to spontaneous hyper-Raman scattering spectroscopy. \cite{RN352}
Hyper-Raman scattering, first theorized by Decius \textit{et al.} and experimentally observed by Terhune \textit{et al.}, is the two photon analogue to Raman scattering. \cite{Cyvin1965, Terhune1965}
Compared to Raman spectroscopy, Hyper-Raman scattering cross sections are often small, making it a difficult technique to successfully implement.\cite{RN515, Kelley2010} 
The different selection rules of hyper-Raman scattering, however, make it a unique alternative to Raman scattering to understand vibrational spectra and vibronic coupling in molecular systems.
In 1998, Cho et al. proposed a parametric six wave mixing technique which was the coherent analogue of hyper-Raman scattering. \cite{Cho1998}
However, since most six wave mixing methods cascade into four wave mixing processes,\cite{RN243, Cho2000_Cascade} it is preferable to investigate coherent four wave mixing analogues to hyper-Raman scattering.

While SIVE showed promise as an upconverted infrared spectroscopy method, it was quickly supplemented by a doubly vibrationally resonant method, doubly vibrationally enhanced (DOVE) spectroscopy, to investigate intra- and intermolecular vibrational coupling. \cite{RN345, RN101, Cho2000}
As a result, investigations of SIVE stagnated; to date, there are less than a dozen studies which report on SR-SIVE. \cite{RN350, RN416, RN351, RN352, RN353, Chen1998, RN362, RN418, McDonnell2024, Bonn2024}
Recent reports highlight non-negligible SIVE interference in DOVE experiments as well as the suitability of SIVE pathways to interpret ultrafast relaxation dynamics in isotropic systems. \cite{Bonn2024, McDonnell2024}
These reports motivate deeper analysis on the properties of SIVE spectroscopy.

Fully coherent, ultrafast probes of vibronic coupling would yield insight into processes that control ultrafast electronic relaxation in molecular and biological systems. \cite{Bredenbeck2015, Arsenault2021}
Some years ago, Cho proposed a parametric, doubly resonant infrared/visible pathway to probe vibronic coupling in isotropic systems. \cite{Cho2001}
In this method, a single infrared pulse is resonant with a vibrational mode, and a two photon absorption event from a near infrared (NIR) or visible pulse is used to generate the four wave mixing signal.
These pathways are referred to herein as DR-SIVE.
Methods analogous to DR-SIVE, where two photon absorption from the infrared pulse and single photon absorption from the visible pulse is used to generate output, i.e., stimulated Raman processes, have been reported. \cite{RN301, RN120}

An experimental complexity in executing four wave mixing experiments is the demand of three separate input pulses, often all at different frequencies.
For example, in the case of DOVE, two of the three input pulses must be scanable infrared pulses. \cite{RN345} 
Only recently have methods been developed for seamless tuning and scanning of ultrafast optical parametric amplifiers across swaths of frequency space. \cite{RN162, McDonnell2024, SkyeOPA, KyleOPA}
Since SR-SIVE demands only a single resonance to be scanned, the experiment can be performed using two input pulses: one tunable, infrared OPA to scan across vibrational resonances, and a two photon absorption from the signal process of a separate OPA, or output from the oscillator which pumps the infrared OPA.
As such, laboratories experienced in sum frequency generation (SFG) spectroscopy can perform SIVE spectroscopy to understand bulk dynamics and spectroscopy using nearly the same setup.\cite{Shen1987_CPL}

Inspired by recent work which demonstrated the presence of SIVE in ultrafast DOVE experiments,\cite{McDonnell2024} we investigate the parameters which result in both SR and DR-SIVE output. \cite{Cho2000, Bonn2024}
We develop simple expressions which relate transition dipoles and hyper-Raman polarizabilties and the overall SR-SIVE output, yielding gross selection rules. 
It is shown that a SIVE active mode must be both IR and hyper-Raman active.
Since any IR active vibration is also hyper-Raman active, \cite{Andrews1978} we demonstrate that SIVE is a coherent analogue of hyper-Raman scattering spectroscopy for IR active vibrations, i.e., SIVE is an optically upconverted infrared spectroscopy.
This is akin to sum and difference frequency generation (SFG, DFG) being coherent Raman analogues for IR active vibrations. \cite{Shen90}

We investigate properties of doubly resonant SIVE (DR-SIVE) to understand how coupling between vibrational and vibronic states can be measured through DR-SIVE.
DR-SIVE is shown to demand one and two-photon absorptions between the ground and excited state.
DR-SIVE is thus the four wave mixing analogue of doubly resonant infrared-visible sum frequency generation. \cite{Shen94}
Based upon these selection rules, we investigate SR-SIVE and DR-SIVE spectroscopy of cyanocobalamin and find good agreement between the theoretical and experimental results.

\section{Experimental Methods}
The ultrafast laser system has been described in detail elsewhere. \cite{RN278, Kaufman2024}
Briefly, an 80 MHz Ti-Sapphire ultrafast oscillator (Spectra-Physics Tsunami) created 35 fs seed pulses, amplified by a 1 kHz regnerative amplifier (Spectra-Physics Spitfire Ace) to approximately 5 W.
A mask in the regenerative amplifier stretched the input pulses to roughly 1 ps.
The resultant output was used to pump four independent OPAs, two of which are relevant for this study.
OPA1 (TOPAS-800, Light Conversion), referred to as $\omega_1$, was tuned for difference frequency generation (DFG) with an external stage (NDFG "DF2", Light Conversion).
OPA2 (OPA-800C, Spectra Physics), referred to as $\omega_2$, was tuned in its signal arrangement. 
Grating and crystal positions in OPA1 was externally controlled using \texttt{WinTOPAS} (Light Conversion).
Grating and BBO crystal positions in OPA2 were computer controlled through communication with 50 mm DC actuators (PMC). %todo: who tf makes PMC motors?
The OPAs were independently tuned through the \texttt{Attune} package, controlled by the \texttt{yaqc} and \texttt{Bluesky} packages. \cite{RN414, RN386, SkyeOPA, KyleOPA}
The power spectra and tuning results are found in Figure X.
Movable retroreflectors (Thorlabs) controlled by 50 mm DC actuators (PMC) are used to measure coherence dynamics.
The beams are focused into the sample using a BOXCARS geometry.\cite{RN308, Kaufman2024}
To enforce frequency dependent temporal pulse overlap, the maximum points of a third order cross correlation between $\omega_1$ and $\omega_3$ measured in CaF$_2$ were used to generate frequency dependent zero delay values.
The nonlinear output was isolated through chopping schemes and a set of spatial apertures, directed into a monochromator (Horiba Micro-HR) and homodyne detected through a photomultiplier tube (Hamamatsu H7422-20), recorded and converted to digital output using a data acquisition unit (National Instruments).
\textit{in-situ} power corrections are performed by dividing the recorded spectra by OPA output measured by home-built pyroelectric detectors.

The cyanocobalamin (CNCbl) [DOT Scientific inc., CAS no. 68-19-9] samples were prepared as drop casted thin films.
CNCbl was dissolved in methanol (MeOH) [Fisher Scientific, HPLC Grade, CAS no. 67-56-1] until a concentrated solution was formed (concentration $\sim$ 10 mg CNCbl/ mL MeOH). 
All chemicals were used as obtained without further purification.
The solution was deposited on a microscope coverslip and allowed to dry in a dessicator until a thin layer was formed.

\section{Properties of SIVE Spectroscopy}
Singly resonant SIVE (SR-SIVE) spectroscopy has potential to provide deeper insight into single quantum decoherence times and molecular orientation in condensed systems.
Similarities between SR-SIVE spectroscopy, infrared spectroscopy and spontaneous hyper-Raman scattering have been noted previously. \cite{RN352, Bonn2024}
In this section, we make the connections between SIVE and hyper-Raman scattering explicit and remark on the properties of SIVE that become apparent after inspecting the selection rules.

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=3.375in]{main/wmel1.png}
	\caption{Wave Mixing Energy Level (WMEL) diagrams of the relevant SR-SIVE pathways in the (a) $\vec{k}_4 = -\vec{k}_1 + \vec{k}_2 + \vec{k}_3$ and (b) $\vec{k}_4 = \vec{k}_1 + \vec{k}_2 + \vec{k}_3$ phasematching geometries. \cite{RN286, RN352}
	$\ket{g}$ is the ground state, $\ket{v}$ is an infrared active vibration and $\ket{m}, \ket{n}$ are virtual states.
	Solid and dashed horizontal lines indicate real and virtual states, whereas solid and dotted arrows indicate ket and bra side transitions, respectively. 
	These diagrams can be permuted to generate additional resonant WMEL diagrams.}
	\label{fig:sivewmel}
\end{figure}

It is useful to expose relationships between transition dipoles, Raman polarizabilities and hyper-Raman polarizabilities in the driven limit. \cite{Simpson2004, RN120}
In the driven limit, under the electric dipole approximation, the I$^{th}$ component of the third order nonlinear output polarization, ${P}^{(3)}_I$, of any four wave mixing process, induced by electric fields E, at output frequency $\omega_4$ is written as \cite{RN307}
\begin{equation} \label{polarization}
{P}^{(3)}_I (\omega_4)  = \chi^{(3)}_{IJKL} E_J E_K E_L 
\end{equation}
where $\chi^{(3)}_{IJKL}$ is the IJKL element of the third order electrical susceptibility, a rank four tensor. 
Note that we choose the convention where an arbitrary electric field, assuming a plane wave, is written in Fourier components as 
\begin{equation}
	\vec{E}(\omega) = \frac{1}{2} E_0 \exp(i(\vec{k}\cdot\vec{x} - \omega t)) + c.c.
\end{equation}
where $E_0$ is the pulse amplitude $\vec{k}$ is a wavevector.
The $IJKL$ element of $\chi^{(3)}$, $\chi^{(3)}$ is generally described as
\begin{equation}
	\chi^{(3)}_{IJKL} = NF(\omega_4) \langle \gamma_{ijkl} \rangle
\end{equation}
where N is a number density, F is the Lorentz local field factor, and $\gamma_{ijkl}$ is the third order polarizability (i.e., second hyperpolarizability). 
The brackets indicate an orientational average. 
Uppercase letters refer to laboratory frame coordinates and lower case letters refer to molecular frame coordinates.

Lineshape analysis is essential for extracting quantitative information from CMDS spectra.
Scanning across resonances create dispersive lineshapes, i.e, self-heterodyning, which inform on $\Re{\chi^{(3)}_{IJKL}}$ and $\Im{\chi^{(3)}_{IJKL}}$.\cite{Levenson1974_1, Levenson1974_2}
Resonant SIVE lineshapes are complicated by amplitude level interference between the sample and its substrate and/or sample cell windows. \cite{RN362}
These effects have been treated in excellent detail for three laser infrared-infrared-visible SIVE using the pathway in \autoref{fig:sivewmel}a, and provide methods to export quantitative information from SIVE spectra. \cite{RN418}

Expressions for $\gamma_{ijkl}$ can be found by solving Liouville-von Neumann equation for an output density matrix element $\rho_{ij}$.
Generally, under the electric dipole approximation, the density matrix, $\bar{\rho}(t)$, is propagated through the Liouville-von Neumann equation as \cite{RN455}
\begin{equation}\label{matrix}
	\dot{\bar{\rho}}(t) = \frac{1}{i \hbar}[H_0 - \vec{\mu}\cdot \sum_j E_j(\vec{x},t), \bar{\rho}(t)] + \bar{\Gamma} \bar{\rho}(t)
\end{equation} %check if bar or double bar
where $H_0$ is the system (time independent) Hamiltonian, $\vec{\mu}$ is the electric transition dipole moment, $\vec{E}(\vec{x},t)$ is a time dependent electric field, and $\bar{\Gamma}$ is the pure dephasing rate vector. 
In the rotating frame, $\tilde{\rho}_{ij} = \rho_{ij} e^{-i \omega_{ij}t}$.
By solving \autoref{matrix} under steady state ($\dot{\bar{\rho}}(t) = 0$) in the rotating frame, expressions for $\gamma_{ijkl}$ can be readily obtained by multiplying the output dipole moment, $\mu_i$ by the final density matrix element $\rho_{ij}$.

\subsection{SR-SIVE Selection Rules}
To make the connection between SR-SIVE and hyper-Raman scattering, we investigate the gross selection rules of SR-SIVE-IR.
By propagating density matrix elements in the steady state limit, the SIVE hyperpolarizability is \cite{RN119}
\begin{equation}\label{sivegamma}
		\gamma_{ijkl} =	- \sum_{m, n} \frac{1}{\varepsilon_0} \frac{1}{4D} \frac{1}{\hbar^3} \frac{\mu^{i}_{v n} \mu^{j}_{nm} \mu^{k}_{mg} \mu^{l}_{gv} }{\Delta_{nv} \Delta_{mv}\Delta_{gv}}  \rho_{gg}
\end{equation}
where: $\mu^{j}_{ab}$ is the $j^{th}$ element of $\mel{a}{\vec{\mu}}{b}$, $\Delta_{kl} = \omega_{kl} - \omega_{j} - i\Gamma_{kl}$, $\omega_j$ is the frequency of the j$^{th}$ input field, $\Gamma_{kl}$ is the dephasing of $\rho_{kl}$ and $\rho_{gg}$ is the ground state density.
For simplicity, we consider the results for the process diagrammed in \autoref{fig:sivewmel}a, but by multiplying by (-1) and taking a complex conjugate, which arise from the bra-side transition in \autoref{fig:sivewmel}a, results for the \autoref{fig:sivewmel}b  process are obtained.
Note that $\omega_j \rightarrow -\omega_j$ for a bra side transition.
D, the Maker-Terhune degeneracy factor, accounts for permutation symmetry in $\gamma_{ijkl}$ and is defined as $\frac{n!}{(n-m)!}$, where $n$ is the total number of input fields (3 for any four wave mixing experiment) and $m$ is the number of distinguishable input fields.\cite{RN134} 
For a SIVE experiment using two or three distinct input fields, as considered here, D = 6.
Note that $\ket{m}, \ket{n}$ are virtual states (\autoref{fig:sivewmel}).
By contracting over the virtual states to form the hyper-Raman hyperpolarizability $\beta$ (i.e., Placzek approximation), this expression can be simplified immensely.\cite{Long1970} 
Note, however, that if $\omega_2$, $\omega_3$, as depicted in \autoref{fig:sivewmel}, are nearly resonant with any state, the Placzek approximation fails. \cite{Placzek1937, Long1970}
Assuming the validity of the Placzek approximation, \autoref{sivegamma} is written as 
\begin{equation}\label{sivebeta}
	\gamma_{ijkl} =	-\frac{1}{\varepsilon_0} \frac{1}{24 \hbar}\frac{\beta^{(ijk)}_{gv} \mu^{(l)}_{gv}}{\Delta_{gv}} \rho_{gg}
\end{equation}
As such, any mode that is SIVE active must be both hyper-Raman and IR active.
However, since any IR active vibrational mode is hyper-Raman active,\cite{Cyvin1965, Andrews1978} any IR active mode is SIVE active.
This makes SIVE an optically upconverted infrared spectroscopy of isotropic samples, as its selection rules are identically those of IR spectroscopy, but its output is generally in the visible.
Unlike SFG spectroscopy, which is dependent upon both the infrared and Raman activity of a mode (through symmetry constraints, this demands that the microscopic SFG output from centrosymmetric species vanishes),\cite{Shen90, Cotton} SIVE is a nonlinear, optically upconverted spectroscopy for any infrared active mode.

To understand SR-SIVE selection rules more finely, the dipole and first hyperpolarizability operators are Taylor expanded in terms of an n$^{\text{th}}$ normal mode coordinate $Q_n$ about equilibrium: \cite{Long1970}
\begin{subequations}
	\begin{equation}
		\mu = \mu_0 + \frac{\partial \mu}{\partial Q_n} Q_n + \order{\sum_{m,n}{Q_m Q_n}}
	\end{equation}
	\begin{equation}
		\beta = \beta_{0} + \frac{\partial \beta}{\partial Q_n} Q_n + \order{\sum_{m,n}{Q_m Q_n}}
	\end{equation}
\end{subequations}
Substituting into \autoref{sivebeta} gives the SIVE-IR-I hyperpolarizability to $\order{Q_n}$ as \begin{equation}\label{SIVEselection}
		\gamma_{ijkl} =	-\frac{1}{\varepsilon_0} \frac{1}{24 \hbar}  \frac{1}{{\Delta_{gv}}} \ \frac{\partial \beta^{(ijk)}}{\partial Q_n} {\frac{\partial \mu^{(l)}}{\partial Q_n}}  (\mel{g}{Q_n}{v})^2\ \rho_{gg}
\end{equation}
Since this expression is non-zero in the harmonic oscillator limit, SR-SIVE output is allowed for harmonic transitions. 
Similar to SFG, SR-SIVE does not demand anharmonic ground state potential energy surfaces for spectral output. \cite{Shen94, Cho2000}
This selection rule is generally valid for any SR-SIVE process in the $-\vec{k}_1 + \vec{k}_2  + \vec{k}_3$ and $\vec{k}_1 + \vec{k}_2  + \vec{k}_3$ phasematching geometries when the Placzek approximation is valid.

A useful attribute of this selection rule is the added ability of polarization control arising from the hyperpolarizability tensor. 
Similar to polarization control in second harmonic and sum frequency generation experiments which probe different elements of the infrared transition dipole and Raman polarizability tensor,\cite{Heinz1982} probing different elements of the hyperpolarizability tensor in SR-SIVE can greatly assist in understanding ultrafast dynamics in isotropic systems. \cite{Shen90, Bonn2024}
Polarization control in IR-pump-SIVE-probe, analogous to ultrafast transient absorption spectroscopy, would be an interesting venue to assess the sensitivity of SR-SIVE to different hyper-Raman tensor elements.

To motivate the application of SIVE spectroscopy, we perform an approximate calculation to compare the output of parametric SIVE-IR (\autoref{fig:sivewmel}b) to that of vibrational SFG (vSFG) spectroscopy.
Absorption effects are neglected for simplicity.
To allow comparison between the two methods, the output polarizations of each process is written as
\begin{widetext}
	\begin{subequations}
		\begin{equation}
			\abs{P^{(2)}_{\text{SFG}}} = N_{surf} F(\omega_1+\omega_2) \abs{\langle \alpha_{ij}\mu_{k} \rangle E_J(\omega_2)E_K(\omega_1)} 
		\end{equation}
		\begin{equation}
			\abs{P^{(3)}_{\text{SIVE}}} = N_{bulk}  F(\omega_1+\omega_2 +\omega_3) \abs{\langle \beta_{ijk} \mu_{l} \rangle E_J{(\omega_3)}E_K(\omega_2)E_L(\omega_1)} \l_{eff}
		\end{equation}
	\end{subequations}
\end{widetext}
where $\alpha_{ij}$ is the Raman polarizability, N$_{bulk}$ is the bulk number density, and N$_{surf}$ is the surface number density (10$^{19}$ m$^{-2}$).\cite{RN133, RN503}
For liquids with molar masses less than $\sim$100 g mol$^{-1}$ and densities roughly equal to that of H$_2$O$_{(l)}$ at room temperature, N$_{bulk} \sim$ 10$^{28}$ m$^{-3}$.
We assume the bulk optical interaction length ($\l_{eff}$) to be roughly 10 $\mu$m.\cite{RN133} %see chapter 25 of Shen's NLO book
A normal dispersion curve is assumed so that $F(\omega_1+\omega_2) \approx F(\omega_1+\omega_2 +\omega_3)$.
To simplify analysis, orientational averaging is ignored and the input and output fields are all co-polarized (I=J=K=L=Z), so that
\begin{equation}
		P_{ratio} \equiv \frac{\abs{P^{(3)}_{\text{SIVE}}}}{\abs{P^{(2)}_{\text{SFG}}}} \approx \frac{N_{bulk}}{N_{surf}} \frac{\beta}{\alpha} E(\omega_3) \l_{eff} \sim 10^4 \frac{\beta}{\alpha} E(\omega_3)\\
\end{equation}
Ziegler has noted that for a field of intensity 10 GW/cm$^{2}$, $\frac{\beta E}{\alpha} \sim 10^{-3} $ for vibrational modes when $E(\omega_3)$ is largely detuned from electronic resonances. \cite{Ziegler87_CPL, RN515}
Such an intensity is easily obtained using modern ultrafast sources.
As such,
\begin{equation}
\begin{split}
		P_{ratio} &\sim 10^4 \frac{\beta E(\omega_3)}{\alpha} \sim 10
\end{split}
\end{equation}
Since the intensity ratio scales as $\abs{P_{ratio}}^2$, we see that the SIVE output is roughly 100 times stronger than vibrational SFG.
It is important to note that this derivation ignored absorption and orientational averaging effects, which can significantly reduce output from either process.

\subsection{Interference in SR-SIVE}
It is well known that nonlinear wave mixing processes which share the same time ordering and output frequency will interfere. \cite{RN135, Bonn2024}
Understanding interfering pathways is useful because they can, in some cases, eliminate output. \cite{RN342, RN135}
The WMEL diagrams presented in \autoref{fig:sivewmel} outline resonant SIVE processes when the infrared pulse $(\omega_1)$ is resonant with a vibrational mode. 
However, if $\omega_2$ becomes vibrationally resonant and $\omega_1$ is non-resonant, then other SIVE pathways appear.\cite{McDonnell2024} 
While the methods in \autoref{fig:sivewmel2} possess identical selection rules to \autoref{fig:sivewmel}, the WMEL diagrams presented in \autoref{fig:sivewmel2} may significantly interfere with DOVE-IR and DOVE-Raman spectra.
The time ordering in DOVE-IR and DOVE-Raman spectra is used to interpret anharmonicities, as DOVE-IR and DOVE-Raman destructively interfere when outputs are at the same frequency. \cite{RN135, RN324}
It is therefore important to understand how the corresponding SIVE pathways interfere.
To this end, we investigate how the SIVE-IR-II and SIVE-Raman pathways (\autoref{fig:sivewmel2}a, b, respectively) interfere under the rotating wave approximation.

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=3.375in]{main/wmel2.png}
	\caption{Wave Mixing Energy Level (WMEL) diagrams of interfering SR-SIVE pathways in the  $\vec{k}_4 = -\vec{k}_1 + \vec{k}_2 + \vec{k}_3$ phasematching geometry. 
	(a) is similar to the process diagrammed in \autoref{fig:sivewmel}, whereas (b) is similar to a singly resonant coherent anti-Stokes Raman-type process.}
	\label{fig:sivewmel2}
\end{figure}

We employ the response function formalism of Mukamel for this analysis. \cite{RN287}
The third order response functions, $R^{(3)}$, for SR-SIVE-IR-II ($R^{(3)}_{S_{II}}$) and SR-SIVE-Raman ($R^{(3)}_{R}$) (\autoref{fig:sivewmel2}a, b) are 
\begin{subequations}
	\begin{equation} \label{mixing:a}
		R^{(3)}_{S_{II}} (t_2) = -\frac{i}{\hbar} [\beta(t_2), \mu(0)] \exp(-i\Delta_{v''g}t_2) \theta(t_2)
	\end{equation}
	\begin{equation}\label{mixing:b}
		\begin{split}
			R^{(3)}_{R} (t_2) & = \frac{i}{\hbar} [\beta(t_2), \mu(0)] \exp(-i\Delta_{v''g}t_2) \theta(t_2) = - R^{(3)}_{S_{II}} (t_2)\\
		\end{split}
	\end{equation}
\end{subequations}
By assuming that the beams which stimulate hyper-Raman scattering, $\vec{E}_1, \vec{E}_3$, interact simultaneously at some time $\tau$ after $\vec{E}_2$ interacts with the sample, the total output polarization, $\vec{P}^{(3)}(t)$, is written as \cite{Cho2001}
\begin{widetext}
	\begin{equation}\label{polarization_SRSIVE_a}
		\begin{split}
			\vec{P}^{(3)}(t) &= \vec{P}_{S_{II}}(t) + \vec{P}_{R}(t)\\
			&= \int_0^\infty \mathrm{d}t_2 (R^{(3)}_{S_{II}} (t_2) + R^{(3)}_{R} (t_2))\vdots \vec{E}_3(t) \vec{E}_1(t) \vec{E}_2(t-t_2 + \tau)\\
			&= \int_0^\infty \mathrm{d}t_2 (R^{(3)}_{S_{II}} (t_2) - R^{(3)}_{S_{II}} (t_2))\vdots \vec{E}_3(t) \vec{E}_1(t) \vec{E}_2(t-t_2 + \tau) \\
			&= 0
		\end{split}
	\end{equation}
\end{widetext}
It is clear the total output polarization for SR-SIVE-IR-II and SR-SIVE-Raman vanishes, or, SR-SIVE-IR-II and SR-SIVE-Raman perfectly destructively interfere.
The absence of SR-SIVE-IR-II pathways in ultrafast DOVE work is rationalized by this calculation. \cite{RN367, McDonnell2024}
In the case of the time ordered SR-SIVE-IR-I pathway, there are no opportunities for interference as all other pathways are nonresonant with the first interaction. 
A possible mechanism for interfering output in the SR-SIVE-I pathway are cascaded second order processes (SFG, DFG). \cite{RN243, RN300}
In isotropic media, SFG and DFG vanish under the electric dipole approximation,\cite{RN231} so cascades are unlikely to inhibit output in centrosymmetric media.
In media where SFG and DFG are allowed, e.g. surfaces or noncentrosymmetric media, second order cascades may become important. 
Generally, for nonlinear spectroscopies which share the same phasematching conditions as SR-SIVE (e.g., DOVE), it is useful to note that SR-SIVE-IR-I is not canceled, whereas SR-SIVE-IR-II and SR-SIVE-Raman permanently cancel.

\subsection{Rovibrational SR-SIVE Selection Rules} %this can probably be deleted but wanted to add just in case...
Recent developments in nonlinear spectroscopy have demonstrated the feasibility of multidimensional infrared spectroscopy of gaseous and quasi-free species. \cite{Ziegler2018, Gronborg2022, RN325, Chen2024}
DOVE and 2D-IR have been used to isolate coupling between fundamentals, overtones and combination bands of gaseous species in several molecular systems. 
Since resonance hyper-Raman scattering spectroscopy was developed as a gas phase spectroscopy, we briefly investigate the properties of rovibrational SR-SIVE.\cite{Ziegler1987}

The rovibrational selection rules are generated through calculating \autoref{sivebeta} in a $\ket{vJM} \equiv \ket{v} \otimes {\ket{JM}}$ basis, where $\{\ket{v}\}$ is a basis of vibrational states and $\{\ket{JM}\}$ is a basis of rotational states ($J$ is the rotational quantum number and $M$ is its z projection, respectively).
By writing $\vec{\mu} = T_q^{(1)}$ and $\beta_{ijk} = T_{q_1}^{(1)} + T_{q_2}^{(2)} + T_{q_3}^{(3)}$, where $T^{(k)}_{q}$ is a rank k spherical tensor, it is simple to evaluate the integrals in \autoref{sivebeta} with the Wigner-Eckart theorem. \cite{Kowzan2022}
It is important to note that $\beta_{ijk}$ does not have complete tensor index symmetry.
Specifically, it has shown that the rank 1 spherical tensor ($q_1 = -1, 0 ,1$) fully contributes to $\beta_{ijk}$ but only select $T_{q_2}^{(2)} + T_{q_3}^{(3)}$ terms contribute. \cite{Andrews1978, Andrews1990}
%there is some fancy way to note that theres no index constraint but i dont remember it...
As such, its decomposition into irreducible tensor form is allowed only if the values of $q', q''$ are constrained.
By substituting the spherical tensor definitions of $\vec{\mu}$ and $\beta_{ijk}$ into \autoref{sivebeta}, it is clear that only $\Delta J = \pm 1$; $\Delta M = 0, \pm1$ transitions are allowed.
This is expected since $\vec{\mu}$ transitions demand $\Delta J = \pm 1$.
As a result, consistent with vibrational SR-SIVE, rovibrational SR-SIVE follows the same rules as common infrared rovibrational spectroscopy.

\subsection{DR-SIVE-IR Selection Rules}
DR-SIVE (where a vibrational and vibronic state are resonantly coupled) can provide a tool for measuring vibronic coupling.
This method is analogous to doubly resonant sum frequency generation. \cite{Shen94}
Multi-resonant nonlinear spectroscopies, such as coherent anti-Stokes Raman spectroscopy (CARS), 2D Electronic Vibrational (2D-EV) spectroscopy and triply resonant sum frequency generation (TRSF) spectroscopy, have been employed to resolve vibronic coupling in molecular samples. \cite{Carlson1990, Gaynor2017, RN276}
DR-SIVE provides methods to investigate vibronic coupling with only two laser pulses, as long as the electronic state is accessible via two photon absorption from the ground state (\textit{vide infra}).
Two beam, parametric and non-parametric DR-SIVE processes are diagrammed in \autoref{fig:doubsive}.
Here, states are written assuming the Born-Oppenheimer approximation, such that $\ket{a,b} = |a) \otimes \ket{b}$ for electronic states $\{|a)\}$ and vibrational states $\{\ket{b}\}$. \cite{BornOppenheimer, Albrecht1960}

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=3.375in]{main/wmel3.png}
	\caption{WMEL diagrams of some DR-SIVE pathways in the $-\vec{k}_1 + \vec{k}_2+ \vec{k}_3$  (I-a,I-b) and $\vec{k}_1 + \vec{k}_2+ \vec{k}_3$ (II-a,II-b) phasematching outputs. $\ket{g,0}$ denotes the ground states, $\ket{g,v}$ denotes a vibrational state on the ground electronic manifold; $\ket{m,n}$ denotes a virtual state, and $\ket{e,0}, \ket{e,v'}$ denote vibronic states.}
	\label{fig:doubsive}
\end{figure}

The goal of this section is to understand DR-SIVE-IR selection rules.
We begin by inspecting the selection rules of a non-parametric DR-SIVE pathway (\autoref{fig:doubsive}I-a) in the driven limit. 
The driven limit is useful as despite the sum over states approach, it avoids implications of ultrafast dephasing of the vibronic state.\cite{Cho2001} 
For consistency with previous reports, we use $\vec{R}$ to denote electric transition dipole moments (not to be confused with the response function; $\mu$ is used for transitions between states on the ground electronic state.). \cite{Ziegler1974}
Following the approach which gave \autoref{sivegamma}, we find
\begin{equation}\label{drgamma_notaylor}
	\gamma_{ijkl} = -\frac{1}{\varepsilon_0} \frac{1}{24 \hbar^3} \sum_{m,n,v'} \frac{
		R^{i}_{gv,ev'} 
		R^{j}_{ev',mn} 
		R^{k}_{mn,gv} 
		R^{l}_{gv,g0} 
	}{\Delta_{g0,gv}
		\Delta_{ev', mn}
		\Delta_{mn, g0}
	}
\end{equation}
where $R^{i}_{gv,ev'}$ is the i$^{th}$ element of $\mel{g,v}{\vec{R}}{e,v'}$.
For generality, we assume that the vibronic  $\ket{e,v'}$ does not share the same vibration with $\ket{g,v}$. \cite{Ziegler1988}
Using our definition of vibronic states, we write $\vec{M}_{ab} = (a|\vec{M}|b)$ so that, for example,
$R^{i}_{gv,ev'} = \mel{v}{M^i_{ge}}{v'}$.\cite{Albrecht1960}
Using these ideas allows us to rewrite \autoref{drgamma_notaylor} as
\begin{equation}\label{drgamma_notaylor_1}
	\gamma_{ijkl} = -\frac{1}{\varepsilon_0} \frac{1}{24 \hbar^3} \sum_{m,n,v'} \frac{
		\mel{v}{M^{i}_{ge}}{v'} 
		\mel{v'}{M^{j}_{em}}{n}
		\mel{n}{M^{k}_{mg} }{v}
		\mel{v}{M^{l}_{gg}}{0}
	}{\Delta_{g0,gv}
		\Delta_{ev', mn}
		\Delta_{mn, g0}	}
\end{equation}
Contracting over $m,n$ in \autoref{drgamma_notaylor_1} by invoking the two photon absorption polarizability $\Lambda$ gives \cite{McClain1977, Simpson2004, Olson2018}
\begin{equation}\label{drgamma_alpha_0}
	\gamma_{ijkl} = -\frac{1}{\varepsilon_0} \frac{1}{24 \hbar^2} \sum_{v'} \frac{
		\mel{v}{M^{i}_{ge}}{v'} 
		\mel{v'}{\Lambda^{jk}_{eg}}{v}
		\mel{v}{M^{l}_{gg}}{0}
	}{\Delta_{g0,gv}
		\Delta_{ev', g0}
	}
\end{equation}
where ${\Lambda^{jk}_{eg}} = (e|\Lambda^{jk}|g)$. 
Since $\Lambda^{jk}$ transforms like a rank two tensor, it is clear that the electronic transition must be both one and two photon allowed for non-zero output, similar to resonant second harmonic generation spectroscopy. \cite{Heinz1982, Nguyen1986, Simpson2004}
This is identical to a selection rule in resonance hyper-Raman scattering, as derived by Chung and Ziegler. \cite{Ziegler1988}
As such, the DR-SIVE methods discussed here are coherent, resonance hyper-Raman analogues. 
This makes DR-SIVE a type of resonance IR spectroscopy, as introduced by Boyle et al.\cite{RN491} 
However, in the methods described by \autoref{drgamma_alpha_0}, $|e)$ must be accessible through one and two photon transitions from $|g)$.
Conversely, the resonance-IR method demonstrated by Boyle et al. only requires one photon transitions between $|g)$ and $|e)$.
Systems which provide strict parity induced selection rules (e.g., benzene) will be useful for assessing the validity of these selection rules and comparing the method described here and that of Boyle et al. \cite{RN491}

\subsection{Line Narrowing in SIVE Spectroscopies}
An unavoidable consequence in electronic spectroscopy is broadened lineshapes due to the inhomogeneity of electronic transitions (e.g., vibronic sidebands, molecular collisions). 
Four wave mixing methods can line-narrow transitions and remove some impact of inhomogeneous broadening.\cite{Carlson1990line}
The line-narrowing properties of DR-SIVE are investigated so that the pathways which line-narrow correlated or anti-correlated modes (\textit{vide infra}) can be identified.
SR-SIVE cannot linenarrow transitions as it is singly resonant. \cite{RN352}

In the discussion that follows, we assume that a vibrational mode in the ground state, $\ket{g,v}$, is correlated to the frequency of a vibronic $\ket{e,v}$.\cite{Carlson1990}
If the frequency of $\ket{g,v}$ is written as $\omega_{gv} + \xi$, where $\xi$ is some external strain (e.g. molecular collisions), then the frequency of $\ket{e,v}$ is $\omega_{ev} + c\xi$, where c is a shift coefficient.
Similarly, we take the frequency of $\ket{e,0}$ as $\omega_{e0} \rightarrow \omega_{e0} + \xi$.
The strains shift resonance denominators, e.g., for $\omega_{ij} \rightarrow \omega_{ij} + c\xi$, as
\begin{equation}
	\Delta_{ij}(\xi) = \omega_{ij} + c\xi -\omega_k - i\Gamma_{ij} \equiv \Delta_{ij}(0) + c\xi
\end{equation}
Without loss of generality, we assume c = 1 for correlated modes and c = -1 for anti-correlated modes.
To understand the impact of inhomogeneity on spectral output, we convolute an output density matrix element $\rho_{ab}(\xi)$ with a normalized Lorentzian distribution $P(\xi)$ of half width $\sigma$ as \cite{Penner1976, Desiderio1979, Dick83_1, Carlson1990line} 
\begin{equation}\label{contour}
	\rho_{ab} = \int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \rho_{ab}(\xi)
\end{equation} 
While Gaussian distributions are commonly used to describe inhomogeneous broadening,\cite{RN307} Lorentzian distributions have successfully described inhomogeneous broadening in a variety of spectroscopies and yield easily interpreted closed-form solutions. \cite{Dick83_1, Carlson1990line}
For clarity, we evaluate the linenarrowing characteristics of pathway Ia (\autoref{fig:doubsive}) in detail in Appendix.
The results for all pathways in \autoref{fig:doubsive} are summarized in \autoref{T:correlated}.

\begin{table}[!htbp]
	\caption{\label{T:correlated} Line narrowing capabilities of pathways outlined in \autoref{fig:doubsive} for correlated and anti-correlated modes, as evaluated through \autoref{contour}, assuming no population feeding or saturation effects.}
	\begin{ruledtabular}
		\begin{tabular}{ccc}
			Pathway & Correlated & Anti-Correlated\\
			\hline  
			I-a & Yes & No \\
			I-b & No & Yes\\
			II-a & No & Yes\\
			II-a & No & Yes\\
		\end{tabular}
	\end{ruledtabular}
\end{table}

Although \autoref{T:correlated} identifies that only Pathway I-a can line-narrow correlated modes, these results are only valid in limits where the input pulses only weakly populate excited states.
When resonant pulses are significantly longer than the dephasing time of some state, then that state can become populated.
Excited state population effects are particularly important for understanding the spectroscopy of electronic states using input pulses with relatively long pulsewidths ($\gtrsim$ 1 ps). \cite{RN319}
First seen in fifth order perturbation theory ($\chi^{(5)}$ processes) in isotropic media, excited state populations can populate other modes, including the ground state and other vibrational/vibronic modes, inducing higher order processes.\cite{Carlson87, RN471}
These feeding mechanisms can induce line-narrowing properties in spectroscopies that cannot line-narrow in third order perturbation theory.\cite{RN319, Carlson87, RN471, RN410}
While not important for the discussion here, the implications of excited state populations are important when considering experiments using the methods in \autoref{fig:doubsive} with long pulsewidths.

\section{SIVE of cyanocobalamin}

\begin{figure*}[!htbp]
	\centering
	\includegraphics[width=6.66in]{main/cob.png}
	\caption{
		(a,c) Singly Resonant SIVE (SR-SIVE) and (b,d) Doubly Resonant SIVE (DR-SIVE) response of CNCbl using the $-\vec{k}_1 + 2\vec{k}_2$ and $\vec{k}_1 + 2\vec{k}_2$ phasematching geometries, respectively.
		Here, $\omega_2 = 8000$ cm$^{-1}$.
		$\omega_1$ is stepped in 10 $^{-1}$ intervals.
		The spectra are smoothed and power-normalized for frequency dependent power fluctuations during the scan.
		Gray pixels indicate spectral noise.
		The blue trace in (a), (b) corresponds to the spectrum at $\tau_{12}$ = 0 in (c,d), respectively.
		The red trace is an FT-IR spectrum of CNCbl, sourced from NIST. 
		All spectra are normalized to their most intense feature on $\omega \in [1300, 1700]$ cm$^{-1}$.}
	\label{fig:cobsive}
\end{figure*}

To demonstrate the results of Equations \eqref{SIVEselection} and \eqref{drgamma_alpha_0} on realistic, non-model systems, we compare singly and doubly resonant SIVE spectra of cyanocobalamin in the 1300 - 1700 cm$^{-1}$ region to its infrared spectrum (\autoref{fig:cobsive}).
Cyanocobalamin (CNCbl), or vitamin B$_{12}$ is an important form of cobalamin which forms functional coenzyme derivatives in humans.
In addition to its important biological properties, CNCbl possesses a complex electronic structure.\cite{Stich2003}
There has been a variety of spectroscopic studies on cyanocobalamin. 
Most CNCbl spectroscopic studies are focused on the vibronic structure of its electronic states.\cite{Stich2003, RN276, Salerno2020, Elmendorf2023} 
Here, we take advantage of the spectroscopic studies of CNCbl to interpret the SR-SIVE and DR-SIVE selection rules.
To our knowledge, there are no reported resonance or non-resonance hyper-Raman spectra of CNCbl, which inhibits our analysis of the CNCbl SIVE spectra.

The lowest energy electronic transition in cyanocobalamin, the $\alpha$ feature, is reported to be centered at roughly 18050 cm$^{-1}$ with a linewidth of approximately 1000 cm$^{-1}$. \cite{Stich2003, RN276}
For the Placzek approximation to hold for SR-SIVE, the two photon absorption and resultant SIVE output in \autoref{fig:sivewmel} must be below $\sim$17000 cm$^{-1}$.
A non-parametric pathway (\autoref{fig:sivewmel}a) is therefore used to experimentally collect singly resonant SIVE spectra.

The singly resonant SIVE spectrum (blue trace, \autoref{fig:cobsive}a) has rather limited structure relative to its FT-IR spectrum (red trace, \autoref{fig:cobsive}a).
The most intense feature is due to a vibrational mode situated at roughly 1585 cm$^{-1}$.
Based upon its relative spectral width, this feature is likely comprised of multiple vibrational modes in close vicinity, consistent with the FT-IR spectrum and a previous TSF spectrum of CNCbl. \cite{RN276}
This is confirmation that the selection rule presented in \autoref{SIVEselection} is appropriate for this method. 
The FT-IR spectrum shows the presence of several strong modes in the 1430 - 1560 cm$^{-1}$ which are only weakly resolved in the SIVE spectrum.
Since the input infrared beam is H polarized, it is possible that the IR pulses only weakly couples into those modes, resulting in limited output.

More interesting are the modes present at $\sim$ 1340 - 1400 and 1510 cm$^{-1}$, strongly observable in the FT-IR spectrum. 
At zero delay, these modes possess roughly 20\% SR-SIVE intensity as the 1585 cm$^{-1}$ mode.
Considering the relative infrared strength of these modes, it is likely that the 1585 cm$^{-1}$ mode possesses significant hyper-Raman character, i.e., the rank 2 and 3 components of the $\beta_{ijk}$ operator for the 1585 cm$^{-1}$ mode are important.
While non-resonant hyper-Raman studies on CNCbl are required to confirm these assignments, it appears that SIVE is a reasonable method for understanding higher order polarizabilities of infrared active modes without the need for complex hyper-Raman experiments.

Unlike the singly resonant SIVE spectrum, the doubly resonant SIVE spectrum shows many vibrational modes in CNCbl, more consistent with the infrared spectrum (\autoref{fig:doubsive}b,d).
Across the spectrum, the response at zero delay is significantly more intense than that of SR-SIVE,  
likely due to the resonance hyper-Raman process.
Resonance hyper-Raman scattering is known to increase spectral output by orders of magnitude relative to non-resonance hyper-Raman scattering in gaseous systems. \cite{Ziegler87_CPL, RN515}.
These spectra also indicate that the low lying electronic states of cobalamin are one and two photon allowed transitions, or, the lowest lying electronic state has mixed parity, as it accessible by operators that transform as odd (dipole) and even (two photon absorption) functions.

A recent resonance Raman study on vibronic coupling in CNCbl highlights a mode at 1510 cm$^{-1}$ (labeled as $\nu_1$) which strongly couples to the low lying ($\alpha, \beta$) electronic states.\cite{Elmendorf2023}
The same study suggests the mode at 1585 cm$^{-1}$ weakly couples to the $\alpha$ and $\beta$ states. 
Conversely, the DR-SIVE spectrum of CNCbl instead suggests the opposite: the 1585 cm$^{-1}$ mode strongly couples to the $\alpha$ and $\beta$ states, whereas $\nu_1$ only slightly couples (\autoref{fig:cobsive}).
This is identified through the relative intensity of the zero delay trace at 1510 and 1585 cm$^{-1}$ (\autoref{fig:cobsive}b).
These differences likely arise due to the relative hyper-Raman cross sections of these modes.
Since $\nu_1$ possesses a strong infrared cross section (\autoref{fig:cobsive}a), the weakness of $\nu_1$ in the SR-SIVE spectrum suggests it has a rather weak hyper-Raman cross section.
The weakness of the $\nu_1$ singly resonant hyper-Raman cross section may rationalize its weakness in the DR-SIVE spectrum.

In addition to the 1580 cm$^{-1}$ mode shown to significantly couple to electronic states, the modes at roughly 1340 - 1400 cm$^{-1}$ also show considerable intensity relative to the singly resonant spectrum.
The resonance Raman study above indeed highlights a variety of modes in the 1340 - 1400 cm$^{-1}$ region responsible for this coupling, consistent with the observed spectral signatures in the zero delay trace of the DR-SIVE spectrum.\cite{Elmendorf2023}
However, in the CNCbl resonance Raman study, these modes are only weakly coupled to the $\alpha$ and $\beta$ states.
These modes accordingly have some sort of strong connection to the $\alpha$ and $\beta$ states that can only be resolved through hyper-Raman spectroscopy. 
To understand these properties further, a resonance hyper-Raman study of CNCbl, and its comparison to a CNCbl resonance Raman study, is required.

Generally, the SR-SIVE and DR-SIVE spectra of CNCbl agree with previously reported spectra.
Apparent differences in coupling between the vibrational and electronic/vibronic states to those found in resonance Raman studies likely arise from hyper-Raman selection rules. 
A more thorough analysis of vibronic coupling involving these 1300 - 1500 cm$^{-1}$ modes in CNCbl is currently under investigation and will be published elsewhere. \cite{Kaufman2024_1}
Generally, these preliminary studies demonstrate the feasibility of SIVE as a coherent analogue of hyper-Raman spectroscopy and motivate further resonant and non-resonant hyper-Raman studies on complex structures for quantitative use of SIVE.\cite{MyersKelley2008}

\section{Conclusions}
Coherent vibrational, hyper-Raman type spectroscopies are identified and discussed.
Singly resonant SIVE (SR-SIVE) processes are shown to be the coherent hyper-Raman analogue of infrared active vibrations.
Since SR-SIVE is always non-zero for IR active vibrations, the method could be used as an analytical method to optically upconvert infrared transitions with small transition dipoles.
Doubly resonant SIVE (DR-SIVE) processes show promise as a probe of vibronic coupling in molecular samples.
Unlike SR-SIVE, DR-SIVE methods can linenarrow inhomogeneously broadened vibronic modes. 
These methods show promise as a probe of ultrafast relaxation dynamics in isotropic systems.

\section{Acknowledgments}
This work received support from the Department of Energy, Office of Basic Energy Sciences, Division of Materials Sciences and Engineering (Grant no. DE-SC0002162).
R.P.M. acknowledges support from the NSF Graduate Research Fellowship Program (Grant no. DGE-2137424).

%\section{Appendix A: Rationale for use of Lorentzian Distribution to calculate Line Narrowing Effects}
%Here we investigate the claim that one can substitute a Lorentzian in lieu of a Gaussian when performing the convolution integral
%\begin{equation}\label{inhomog}
%	\rho_{ij} = \int \mathrm{d}\xi P(\xi) \rho_{ij}(\xi)
%\end{equation}
%where $P(\xi)$ is a probability distribution and $\rho_{ij}$ is a density matrix element. 
%The reason for introducing a Lorentzian distribution in lieu of a Gaussian is that \autoref{inhomog} can be evaluated in closed-form if $P(\xi)$ is Lorentzian. \cite{Penner1976} 
%Consider a Lorentzian and Gaussian distribution:
%\begin{equation}\label{lorentzian}
%	f(\xi) = \frac{\sigma}{\pi} \frac{1}{\xi^2 + \sigma^2}
%\end{equation}
%\begin{equation}\label{gaussian}
%	g(\xi) = \sqrt{\frac{1}{2\pi\sigma^2}} \exp(-\frac{\xi^2}{2\sigma^2})
%\end{equation}
%We investigate the behavior of these distributions by Taylor expanding each function. 
%$f(\xi)$ is written such that
%\begin{equation}
%	f(\xi) = \frac{\sigma}{\pi}\frac{1}{\sigma^2} \frac{1}{1 + (\frac{\xi}{\sigma})^2} = \frac{1}{\pi \sigma}\frac{1}{1 + (\frac{\xi}{\sigma})^2}
%\end{equation}
%Introducing $x = \frac{\xi}{\sigma}$ and using the identity
%\begin{equation}
%	\frac{1}{1+x^2} = \frac{1}{1-(-x^2)} = \sum_{n=0}^\infty (-1)^{n}x^{2n}, |x| < 1
%\end{equation}
%we write \autoref{lorentzian} as
%\begin{equation}
%	f(x) = \frac{1}{\pi \sigma} \sum_{n=0}^\infty (-1)^{n}x^{2n}, |x| < 1
%\end{equation}
%Similarly, by using
%\begin{equation}\label{gaussianexp}
%	\exp(-ax^2) = \sum_{n=0}^\infty \frac{(-a)^n}{n!} x^{2n}, x \in \mathbb{C}
%\end{equation}
%we write \autoref{gaussian} as
%\begin{equation}
%	g(x) = \sqrt{\frac{1}{2\pi\sigma^2}} \sum_{n=0}^\infty \frac{(-1)^n  x^{2n}}{2^n n!}, x \in \mathbb{C}
%\end{equation}
%%The functional forms of $f(\xi), g(\xi)$ are very similar in the large $\sigma$ and small $\xi$ limits.
%By comparing the expansions of $f(x)$ and $g(x)$, it is clear that the primary difference between the Lorentzian and Gaussian distributions are the convergence rates due to a factor of $\frac{1}{2^n n!}$ in \autoref{gaussianexp}.
%As such, it is reasonable to substitute a Lorentzian distribution for a Gaussian distribution when evaluating \autoref{inhomog}.
%
%As a note, since the Lorentzian distribution's convergence radius is constrained by its singularities ($\pm i$), the two distributions are truly comparable only if the tails of the Lorentzian distribution are ignored.
%With this in mind, we note that
%\begin{subequations}
%	\begin{equation}
%		\frac{1}{\pi}\int_{-1}^1 \mathrm{d}x \frac{1}{1+x^2} = \frac{1}{2}
%	\end{equation}
%	\begin{equation}
%		\sqrt{\frac{1}{2\pi}} \int_{-1}^1 \mathrm{d}x \exp(-\frac{x^2}{2}) = \erf{\sqrt{\frac{1}{2}}} \approx 0.68
%	\end{equation}
%\end{subequations}
%or, the integrals are roughly similar when considering the radius of convergence of the Lorentzian distribution. 
%As such, we extend the bounds of integration from $(-1, 1)$ to $(-\infty, \infty)$ to facilitate simple calculation of \autoref{contour}.
%We note that Dick and Hochstrasser numerically showed some years ago that the tails of the Lorentzian distribution have little effect on the calculation of \autoref{inhomog}, in agreement with the suggested result.\cite{Dick83_1}
\section{Appendix A: Evaluation of Pathway I-a Linenarrowing Capability}
The output coherence  for this pathway is $\rho_{ev',gv}(\xi)$.
Setting $\eta$ equal to the numerator of \autoref{drgamma_alpha_0} along with any constants, we see
\begin{widetext}
\begin{equation}\label{ev'gv}
	\begin{split}
		\rho_{ev',gv}(\xi) &= \frac{\eta}{\Delta_{g0,gv}(\xi) \Delta_{ev',gv}(c\xi)}\\
		&=  \frac{\eta}{(-\omega_{g0,gv} - \xi + \omega_1 - i\Gamma_{g0,gv})(\omega_{ev',gv} + c\xi - (2\omega_3 + \omega_1) - i\Gamma_{ev',gv})}\\ 
		&= \frac{\eta}{(\Delta_{g0,gv}(0) - \xi)(\Delta_{ev',gv}(0) + c\xi)}\\ 
	\end{split}
\end{equation}
\end{widetext}
For notational convenience, we map $\ket{g,0} \rightarrow \ket{g}$, $\ket{g,v} \rightarrow \ket{a}$ and $\ket{e,v'} \rightarrow \ket{b}$.
Substituting into \autoref{contour}, we see:
\begin{equation}\label{integraly}
	\begin{split}
		\rho_{ba} &= \int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \rho_{ba}(\xi)\\
		&= \int_{-\infty}^\infty \mathrm{d}\xi \frac{\sigma}{\pi} \frac{1}{\xi^2 + \sigma^2} \eta \frac{1}{\Delta_{ga}(0) - \xi} \frac{1}{\Delta_{ba}(0) + c\xi}\\
		&= \frac{\eta \sigma}{\pi} \int_{-\infty}^\infty \mathrm{d}\xi\frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga}(0) - \xi} \frac{1}{\Delta_{ba}(0) + c\xi}\\
	\end{split}
\end{equation}

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=3.375in]{main/corr_contour.png}
	\caption{Poles (black dots) and contour (blue line) used to evaluate \autoref{integraly} for (a) anti-correlated and (b) correlated modes.} 
	\label{fig:contours}
\end{figure}

\subsubsection{Anti-correlated Modes}
For anti-correlated modes, the poles are situated in the complex plane as shown in \autoref{fig:contours}a.
Since \autoref{integraly} is evaluated along the real axis, one can choose to evaluate the contour in the upper or lower half of the complex plane.
Since evaluating the residues in the upper or lower half of the complex plane yields the same result for \autoref{integraly}, we choose the contour which wraps around the least number of poles.

It is clear for c = -1 that there are four poles: $\pm i \sigma, \Delta_{ga}(0), \Delta_{ba}(0)$. 
Following \autoref{fig:contours}, the contour that wraps the upper half of the complex plane has only one pole, $i \sigma$; as such, we choose to evaluate \autoref{integraly} in the upper half of the complex plane for the case of anti-correlated modes through the residue theorem as
\begin{widetext}
	\begin{equation}
		\begin{split}
			\rho_{ba} = \int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \rho_{ba}(\xi) &= 2\pi i \sum_k \lim_{\xi \rightarrow \xi_k} P(\xi) \rho_{ba}(\xi) (\xi - \xi_k)\\
			&= 2\pi i \frac{\eta \sigma}{\pi} \lim_{\xi \rightarrow i\sigma} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga}(0) - \xi} \frac{1}{\Delta_{ba}(0) - \xi} (\xi - i \sigma)\\
			&= 2 \eta \sigma i \lim_{\xi \rightarrow i\sigma} \frac{1}{\xi + i\sigma} \frac{1}{\Delta_{ga}(0) - \xi} \frac{1}{\Delta_{ba}(0) - \xi}\\
			&= 2\eta \sigma i \frac{1}{2i\sigma} \frac{1}{\Delta_{ga}(0) - i\sigma} \frac{1}{\Delta_{ba}(0) - i\sigma}\\
			&= \frac{\eta}{\Delta_{ga}(i\sigma)\Delta_{ba}(i \sigma)}\\
		\end{split}
	\end{equation}
\end{widetext}

In words, we see the inhomogeneous envelope width $\sigma$ is added to the linewidth of each resonance (e.g., $\Gamma_{ag} \rightarrow \Gamma_{ag} + \sigma$).
Therefore, pathway I-a cannot linenarrow anti-correlated modes. 
\subsubsection{Correlated Modes: c = 1}
For correlated modes, the poles are situated in the complex plane as shown in \autoref{fig:contours}.
It is clear that no matter which contour is chosen, there is a contribution to the final integral from either $\Delta_{ba}(0)$ or $\Delta_{ga}(0)$. 
For the below calculation, we choose to evaluate along the contour in the bottom half of the complex plane, i.e., the poles ($\xi_k$) are $-i\sigma, \Delta_{ga}$.
We stress that since the integral is evaluated over $\mathbb{R}$ and there are no degenerate poles, the results below can be obtained by evaluating the contour which wraps around the poles $i\sigma, \Delta_{ba}$. 
Since the $\xi_k$ are nondegenerate, \autoref{integraly} can be evaluated using the Residue theorem as 
\begin{widetext}
	\begin{equation}
		\begin{split}
			\int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \rho_{ba}(\xi) &= 2\pi i \sum_k \lim_{\xi \rightarrow \xi_k} P(\xi) \rho_{ba}(\xi) (\xi - \xi_k)\\
			&= 2\pi i \frac{\eta \sigma}{\pi} ( \lim_{\xi \rightarrow -i\sigma} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga}(0) - \xi} \frac{1}{\Delta_{ba}(0) - \xi} (\xi + i \sigma) \\ &+
			\lim_{\xi \rightarrow \Delta_{ga}(0)} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga}(0) - \xi} \frac{1}{\Delta_{ba}(0) - \xi} (\xi - \Delta_{ga}))\\
			&= 2 \eta i \sigma (\frac{1}{2 i \sigma} \frac{1}{-i \sigma - \Delta_{ga}(0)} \frac{1}{\Delta_{ba}(0) - i\sigma} ) - 2 \eta i \sigma (\frac{1}{\sigma^2 + (\Delta_{ga} (0))^2} \frac{1}{\Delta_{ga}(0) + \Delta_{ba}(0)} )\\
			&= -\frac{\eta}{\Delta_{ga}(0) + i \sigma} (\frac{1}{\Delta_{ba}(0) - i \sigma} + \frac{2i\sigma}{(\Delta_{ga}(0) - i \sigma)(\Delta_{ga}(0) + \Delta_{ba}(0))})\\
		\end{split}
	\end{equation}
\end{widetext}
The final line of the above equation shows the presence of a new term, $\frac{2i\sigma}{\Delta_{ga}(0) + \Delta_{ba}(0)}$. 
This term is amplified by the width of the inhomogeneous envelope ($\sigma$) and has a linewidth $\Gamma_{ba} + \Gamma_{ga}$, which linenarrows the transition. 
Results for the other pathways follow the same technique.
Generally, when starting from the ground state, non-parametric spectroscopies line-narrow correlated modes, and parametric spectroscopies line-narrow anti-correlated modes. \cite{Dick83_1, RN425}

\section{References}
% Create the reference section using BibTeX:
\bibliography{library.bib}

\end{document}
%
% ****** End of file apstemplate.tex ******

### 2024-06-02 build.py

@@ -1,0 +1,77 @@
+import pathlib
+import subprocess
+import platform
+import click
+
+osf_project = "2amkq"
+here = pathlib.Path(__file__).resolve().parent
+
+
+if platform.system() == 'Windows':
+    python = 'python'
+else:
+    python = 'python3'
+
+
+def print_with_line(s, char='#'):
+    s += ' '
+    s += char * (80 - len(s))
+    print(s)
+
+
+def print_then_call(*args, **kwargs):
+    print_with_line(' '.join(args), '-')
+    subprocess.run(args, check=True, **kwargs)
+
+
+def _fetch_data():
+    print_with_line('fetch data')
+    print_then_call("osf", "-p", osf_project, "clone", "-U", str(here / "data"))
+
+
+def _build_documents():
+    from library import build_paper
+    print_with_line("documents")
+    print_with_line("paper", "-")
+    build_paper.tex2pdf("paper", here)
+    build_paper.tex2pdf("paper", here, False)
+
+
+def _build_figures():
+    print_with_line('figures')
+    print_then_call(python, str(here / "workup.py"))
+    # print_then_call(python, str(here / "figures" / "preamp.py"))
+    # print_then_call(python, str(here / "figures" / "poweramp.py"))
+    # print_then_call(python, str(here / "figures" / "powerampslice.py"))
+    # print_then_call(python, str(here / "figures" / "tunetest.py"))
+    # print_then_call(python, str(here / "figures" / "spectral_delay_corrections.py"))
+
+
+@click.group()
+def main():
+    pass
+
+@main.command(name="fetch", help="download and extract the [raw data](https://osf.io/2nr9d)")
+def fetch_data():
+    _fetch_data() 
+
+@main.command(name="all", help="build all steps")
+def all_():
+    print_with_line('building everything!')
+    _fetch_data()
+    _build_figures()
+    _build_documents()
+    print_with_line('building done!')
+
+
+@main.command("documents")
+def build_documents():
+    _build_documents()
+
+@main.command(name="figures", help="generate manuscript figures from the data")
+def build_figures():
+    _build_figures()
+
+
+if __name__ == '__main__':
+    main()

### 2024-06-02 figures/workup.py

@@ -1,0 +1,129 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Tue Feb 20 14:40:11 2024
+
+@author: rpm
+"""
+
+import WrightTools as wt
+import pathlib
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+
+plt.rcParams.update({
+"text.usetex": True,
+"font.family": "mathptmx"
+})
+plt.rcParams['figure.dpi'] = 800
+
+here = pathlib.Path(__file__).resolve().parent
+# here = here.parent
+
+data_dir = here.parent / "data" 
+
+dir0 = data_dir / "2024-04-04 39092 grid_scan_wp cobalamin_thin_transmission_wig c38ec440"
+dir1 = data_dir / "2024-04-04 37050 grid_scan_wp cobalamin_thin_transmission_wig_TSF ef139d32"
+
+data0  = wt.open(dir0/'primary.wt5')
+data1  = wt.open(dir1/'primary.wt5')
+
+for data in [data0, data1]:
+    data.create_channel(name = 'normalized', values = data.daq_w1pr[:]/data.daq_pyro_1[:] /data.daq_pyro_3[:])
+    data.smooth(2, channel = 'normalized')
+    channel = data.normalized
+    data.transform('w1_points', 'D1_points')
+    split = True
+if split:
+        data0 = data0.split('w1_points', [1300,1700], units = 'wn')[1]
+        data1 = data1.split('w1_points', [1300,1700], units = 'wn')[1]
+        for data in [data0, data1]:
+            channel = data.normalized
+            channel.normalize()
+# else: channel.normalize()
+
+##ftir from pandas
+spectrum = pd.read_excel(data_dir / "cobir.xlsx")
+d2 = wt.Data(name = 'ftir')
+d2.create_variable(name = 'energy', units = 'wn', values = spectrum.energy.to_numpy())
+d2.create_channel(name = 'signal', values = spectrum.intensity.to_numpy())
+    
+
+
+
+#plot
+cols = [1, 1, "cbar"] 
+aspects = [[[0, 0], 0.2], [[1, 0], 0.9]] 
+
[…]

### 2024-06-02 build.py
Update build.py
oops

@@ -39,7 +39,7 @@ def _build_documents():
 
 def _build_figures():
     print_with_line('figures')
-    print_then_call(python, str(here / "workup.py"))
+    print_then_call(python, str(here / "figures" / "workup.py"))
     # print_then_call(python, str(here / "figures" / "preamp.py"))
     # print_then_call(python, str(here / "figures" / "poweramp.py"))
     # print_then_call(python, str(here / "figures" / "powerampslice.py"))

### 2024-06-02 paper.tex
Update paper.tex

@@
 The ultrafast laser system has been described in detail elsewhere. \cite{RN278, Kaufman2024}
-Briefly, an 80 MHz Ti-Sapphire ultrafast oscillator (Spectra-Physics Tsunami) created 35 fs seed pulses, amplified by a 1 kHz regnerative amplifier (Spectra-Physics Spitfire Ace) to approximately 5 W.
+Briefly, an 80 MHz Ti-Sapphire ultrafast oscillator (Spectra-Physics Tsunami) created 35 fs seed pulses, amplified by a 1 kHz regnerative amplifier (Spectra-Physics Spitfire Ace) to approximately 0.5 W.
 A mask in the regenerative amplifier stretched the input pulses to roughly 1 ps.
@@
 The OPAs were independently tuned through the \texttt{Attune} package, controlled by the \texttt{yaqc} and \texttt{Bluesky} packages. \cite{RN414, RN386, SkyeOPA, KyleOPA}
-The power spectra and tuning results are found in Figure X.
+The power spectra and tuning results are found in Figure X.%todo: actually graph these
 Movable retroreflectors (Thorlabs) controlled by 50 mm DC actuators (PMC) are used to measure coherence dynamics.

### 2024-06-02 paper.tex
add osf statement to paper
Update paper.tex

@@
 
-\graphicspath{{"main/"}}
+\graphicspath{{"figures/"}}
 \begin{document}
@@
 The rovibrational selection rules are generated through calculating \autoref{sivebeta} in a $\ket{vJM} \equiv \ket{v} \otimes {\ket{JM}}$ basis, where $\{\ket{v}\}$ is a basis of vibrational states and $\{\ket{JM}\}$ is a basis of rotational states ($J$ is the rotational quantum number and $M$ is its z projection, respectively).
-By writing $\vec{\mu} = T_q^{(1)}$ and $\beta_{ijk} = T_{q_1}^{(1)} + T_{q_2}^{(2)} + T_{q_3}^{(3)}$, where $T^{(k)}_{q}$ is a rank k spherical tensor, it is simple to evaluate the integrals in \autoref{sivebeta} with the Wigner-Eckart theorem.
+By writing $\vec{\mu} = T_{q_1}^{(1)}$ and $\beta_{ijk} = T_{q_1}^{(1)} + T_{q_2}^{(2)} + T_{q_3}^{(3)}$, where $T^{(k)}_{q}$ is a rank k spherical tensor, it is simple to evaluate the integrals in \autoref{sivebeta} with the Wigner-Eckart theorem.
 \cite{Kowzan2022}
 It is important to note that $\beta_{ijk}$ does not have complete tensor index symmetry.
-Specifically, it has shown that the rank 1 spherical tensor ($q_1 = -1, 0 ,1$) fully contributes to $\beta_{ijk}$ but only select $T_{q_2}^{(2)} + T_{q_3}^{(3)}$ terms contribute.
+Specifically, it has shown that the rank one spherical tensor ($T_{q_1}^{(1)}$, with $q_1 \in -1, 0 ,1$) fully contributes to $\beta_{ijk}$ but only select $T_{q_2}^{(2)} + T_{q_3}^{(3)}$ terms contribute.
 \cite{Andrews1978, Andrews1990}
-%there is some fancy way to note that theres no index constraint but i dont remember it...
+%there is some fancy way to note that theres no index constraint but i dont remember the language...
 As such, its decomposition into irreducible tensor form is allowed only if the values of $q', q''$ are constrained.
@@
 
+\section{Data Availability Statement}
+The data and workup scripts that support this study are permissively licensed and available for reuse at https://osf.io/2amkq/.
+
 \section{Acknowledgments}

### 2024-06-11 paper.tex
fixed placzek citation
edits
more on quantitative stuff.

@@
-\documentclass[aip, jcp, reprint, onecolumn]{revtex4-2}
+\documentclass[aip, jcp, reprint, twocolumn]{revtex4-2}
 
@@
 \end{equation}
-where $\chi^{(3)}_{IJKL}$ is the IJKL element of the third order electrical susceptibility, a rank four tensor. 
-Note that we choose the convention where an arbitrary electric field, assuming a plane wave, is written in Fourier components as 
-\begin{equation}
-	\vec{E}(\omega) = \frac{1}{2} E_0 \exp(i(\vec{k}\cdot\vec{x} - \omega t)) + c.c.
-\end{equation}
-where $E_0$ is the pulse amplitude $\vec{k}$ is a wavevector.
-The $IJKL$ element of $\chi^{(3)}$, $\chi^{(3)}$ is generally described as
+where $\chi^{(3)}_{IJKL}$ is the IJKL element of the third order electrical susceptibility, a rank four tensor, generally written as
 \begin{equation}
@@
 
-Lineshape analysis is essential for extracting quantitative information from CMDS spectra.
-Scanning across resonances create dispersive lineshapes, i.e, self-heterodyning, which inform on $\Re{\chi^{(3)}_{IJKL}}$ and $\Im{\chi^{(3)}_{IJKL}}$.\cite{Levenson1974_1, Levenson1974_2}
-Resonant SIVE lineshapes are complicated by amplitude level interference between the sample and its substrate and/or sample cell windows. \cite{RN362}
-These effects have been treated in excellent detail for three laser infrared-infrared-visible SIVE using the pathway in \autoref{fig:sivewmel}a, and provide methods to export quantitative information from SIVE spectra.
-\cite{RN418}
+Note that we choose the convention where an arbitrary electric field, assuming a plane wave, is written in Fourier components as 
+\begin{equation}
+	\vec{E}(\omega) = \frac{1}{2} \vec{E}_0 \exp(i(\vec{k}\cdot\vec{x} - \omega t)) + c.c.
+\end{equation}
+where $E_0$ is the pulse amplitude and $\vec{k}$ is a wavevector.
 
@@
 
-\subsection{SR-SIVE Selection Rules}
+\subsection{Vibrational SR-SIVE Selection Rules}
 To make the connection between SR-SIVE and hyper-Raman scattering, we investigate the gross selection rules of SR-SIVE-IR.
@@
 By contracting over the virtual states to form the hyper-Raman hyperpolarizability $\beta$ (i.e., Placzek approximation), this expression can be simplified immensely.\cite{Long1970} 
-Note, however, that if $\omega_2$, $\omega_3$, as depicted in \autoref{fig:sivewmel}, are nearly resonant with any state, the Placzek approximation fails. \cite{Placzek1937, Long1970}
+Note, however, that if $\omega_2$, $\omega_3$, as depicted in \autoref{fig:sivewmel}, are nearly resonant with any state, the Placzek approximation fails. \cite{Placzek1934, Long1970}
 Assuming the validity of the Placzek approximation, \autoref{sivegamma} is written as 
@@
 Absorption effects are neglected for simplicity.
+\begin{widetext}
 To allow comparison between the two methods, the output polarizations of each process is written as
-\begin{widetext}
 	\begin{subequations}
@@
 		\begin{equation}
-			\abs{P^{(3)}_{\text{SIVE}}} = N_{bulk}  F(\omega_1+\omega_2 +\omega_3) \abs{\langle \beta_{ijk} \mu_{l} \rangle E_J{(\omega_3)}E_K(\omega_2)E_L(\omega_1)} \l_{eff}
+			\abs{P^{(3)}_{\text{SIVE}}} = N_{bulk}  F(\omega_1+\omega_2 +\omega_3) \abs{\langle \beta_{ijk} \mu_{l} \rangle E_J{(\omega_3)}E_K(\omega_2)E_L(\omega_1)} \ell_{eff}
 		\end{equation}
 	\end{subequations}
+where $\alpha_{ij}$ is the Raman polarizability, N$_{bulk}$ is the bulk number density, and N$_{surf}$ is the surface number density (10$^{19}$ m$^{-2}$).\cite{RN133, RN503}	
 \end{widetext}
-where $\alpha_{ij}$ is the Raman polarizability, N$_{bulk}$ is the bulk number density, and N$_{surf}$ is the surface number density (10$^{19}$ m$^{-2}$).\cite{RN133, RN503}
 For liquids with molar masses less than $\sim$100 g mol$^{-1}$ and densities roughly equal to that of H$_2$O$_{(l)}$ at room temperature, N$_{bulk} \sim$ 10$^{28}$ m$^{-3}$.
-We assume the bulk optical interaction length ($\l_{eff}$) to be roughly 10 $\mu$m.\cite{RN133} %see chapter 25 of Shen's NLO book
+We take the bulk optical interaction length ($\ell_{eff}$) to be 10 $\mu$m.\cite{RN133} %see chapter 25 of Shen's NLO book... idk something here seems wrong
 A normal dispersion curve is assumed so that $F(\omega_1+\omega_2) \approx F(\omega_1+\omega_2 +\omega_3)$.
-To simplify analysis, orientational averaging is ignored and the input and output fields are all co-polarized (I=J=K=L=Z), so that
+To simplify analysis, orientational averaging is ignored (e.g., $\langle \beta_{ijk} \mu_{l} \rangle \approx \beta \mu$) and the input and output fields are taken to be co-polarized, so that
 \begin{equation}
-		P_{ratio} \equiv \frac{\abs{P^{(3)}_{\text{SIVE}}}}{\abs{P^{(2)}_{\text{SFG}}}} \approx \frac{N_{bulk}}{N_{surf}} \frac{\beta}{\alpha} E(\omega_3) \l_{eff} \sim 10^4 \frac{\beta}{\alpha} E(\omega_3)\\
+		P_{ratio} \equiv \frac{\abs{P^{(3)}_{\text{SIVE}}}}{\abs{P^{(2)}_{\text{SFG}}}} \approx \frac{N_{bulk}}{N_{surf}} \frac{\beta}{\alpha} E(\omega_3) \ell_{eff} \sim 10^4 \frac{\beta}{\alpha} E(\omega_3)\\
 \end{equation}
 Ziegler has noted that for a field of intensity 10 GW/cm$^{2}$, $\frac{\beta E}{\alpha} \sim 10^{-3} $ for vibrational modes when $E(\omega_3)$ is largely detuned from electronic resonances.
-\cite{Ziegler87_CPL, RN515}
+\cite{RN515}
 Such an intensity is easily obtained using modern ultrafast sources.
@@
 
-\subsection{Interference in SR-SIVE}
+\subsection{Rovibrational SR-SIVE Selection Rules} %this can probably be deleted but wanted to add just in case...
+Recent developments in nonlinear spectroscopy have demonstrated the feasibility of multidimensional infrared spectroscopy of gaseous and quasi-free species.
+\cite{Ziegler2018, Gronborg2022, RN325, Chen2024}
+DOVE and 2D-IR have been used to isolate coupling between fundamentals, overtones and combination bands of gaseous species in several molecular systems. 
+Since resonance hyper-Raman scattering spectroscopy was developed as a gas phase spectroscopy,\cite{RN515} we briefly investigate the properties of rovibrational SR-SIVE.
+
+The rovibrational selection rules are generated through calculating \autoref{sivebeta} in a $\ket{vJM} \equiv \ket{v} \otimes {\ket{JM}}$ basis, where $\{\ket{v}\}$ is a basis of vibrational states and $\{\ket{JM}\}$ is a basis of rotational states ($J$ is the rotational quantum number and $M$ is its z projection, respectively).
+By writing $\vec{\mu} = T_{q_1}^{(1)}$ and $\beta_{ijk} = T_{q_1}^{(1)} + T_{q_2}^{(2)} + T_{q_3}^{(3)}$, where $T^{(k)}_{q}$ is a rank $k$ spherical tensor, it is simple to evaluate the integrals in \autoref{sivebeta} through the Wigner-Eckart theorem.
+\cite{Kowzan2022}
+It is important to note that $\beta_{ijk}$ does not have complete tensor index symmetry.
+Specifically, it has shown that the rank one spherical tensor ($T_{q_1}^{(1)}$, with $q_1 \in \{-1, 0 ,1\}$) fully contributes to $\beta_{ijk}$ but only select $T_{q_2}^{(2)} + T_{q_3}^{(3)}$ terms contribute.
+\cite{Andrews1978, Andrews1990}
+%there is some fancy way to note that theres no index constraint but i dont remember the language...
+As such, its decomposition into irreducible tensor form is allowed only if the values of $q', q''$ are constrained.
+By substituting the spherical tensor definitions of $\vec{\mu}$ and $\beta_{ijk}$ into \autoref{sivebeta}, it is clear that only $\Delta J = \pm 1$ transitions are allowed, i.e., SIVE-IR features arise only from P or R branches (assuming the ground state is $\ket{g00}$).
+This is expected since $\vec{\mu}$ transitions demand $\Delta J = \pm 1$.
+As a result, consistent with vibrational SR-SIVE, rovibrational SR-SIVE follows the same rules as common infrared rovibrational spectroscopy.
+
+\subsection{Quantitative SR-SIVE}
+With the selection rules of SR-SIVE understood for vibrational and rovibrational spectroscopy, it becomes possible to extract quantitative information from SIVE spectra to compare to incoherent methods and other CMDS methods.
+
+Lineshape analysis is essential for extracting quantitative information from CMDS spectra.
+Scanning across resonances create dispersive lineshapes, i.e, self-heterodyning, which inform on $\Re{\chi^{(3)}}$ and $\Im{\chi^{(3)}}$.\cite{Levenson1974_1, Levenson1974_2}
+Resonant SIVE lineshapes are complicated by amplitude level interference between the sample and its substrate and/or sample cell windows. \cite{RN362}
+These effects have been treated in excellent detail for three laser infrared-infrared-visible SIVE using the pathway in \autoref{fig:sivewmel}a, and provide methods to export quantitative information from SIVE spectra.
+\cite{RN418}
+
+Most quantitative methods in an n$^{th}$ order CMDS experiment are used to extract $\chi^{(n)}$ values for comparing the relative strength of nonlinear processes in different media.
+\cite{Zhu87, RN351, RN345}
+The recorded $\chi^{(n)}$ values provide insight into how microscopic quantities ($\vec{\mu}, \alpha_{ij}, \beta_{ijk}$) impact nonlinear output.
+To our knowledge, only 2D-IR spectroscopy has taken advantage of orientationally averaged $\chi^{(3)}$ values to extract transition moments.\cite{Grechko2012}
+Previous treatments did not consider using quantitative analysis in SIVE to measure $\beta_{ijk}$ values from SIVE spectra.
+It is thus useful to investigate how a simple treatment of orientational averaging can extract $\beta_{ijk}$ from a $\chi^{(3)}_{IJKL}$ expression.
+
+The SIVE $\chi^{(3)}_{IJKL}$ expresson is
+\begin{equation}\label{chi3}
+\begin{split}
+		\chi^{(3)}_{IJKL} &\sim \langle \gamma_{ijkl} \rangle \sim \langle \beta_{ijk} \mu_l \rangle\\
+\end{split}
+\end{equation}
+The steps behind orientational averaging of $\gamma_{ijkl}$ are detailed elsewhere.\cite{Andrews1977, McDonnell2024}
+Orientational averaging for specific input polarizations shows that specific polarization schemes isolate linear combinations of different $\beta_{ijk}$ terms. 
+Infrared spectra can provide values for different $\vec{\mu}$ components.
+Since $\vec{\mu}$ is a rank-one tensor, its three Cartesian components share the simple relationship $\langle {\mu^2_x} \rangle = \langle {\mu^2_y} \rangle = \langle {\mu^2_z} \rangle = \frac{1}{3}\langle {\mu^2} \rangle$.
+\cite{RN459}
+Neglecting rotational dependence, $\langle {\mu^2} \rangle = \abs{\mu}^2 = \mu^2$.
+Substituting into \autoref{chi3} shows that
+\begin{subequations}
+	\begin{equation}
+		\begin{split}
+			\chi^{(3)}_{IJKL} &\sim \langle \beta_{ijk} \mu_l \rangle\\
+			&\sim \langle \beta_{ijk} \rangle \frac{\mu}{\sqrt{3}} 
+		\end{split}
+	\end{equation}
+This is done because any element of $\vec{\mu}$ is easily related to its magnitude through the directional cosine relationship shown above. 
+Continuing, we see
+	\begin{equation}
+		\langle \beta_{ijk} \rangle \sim \frac{\sqrt{3}}{\mu} \chi^{(3)}_{IJKL}
+	\end{equation}
+\end{subequations}
+Since $\mu^2$ can be extracted by fitting infrared spectra,\cite{RN412} it is clear that different polarization schemes in SIVE spectroscopy give a measurement of $\beta_{ijk}$ values.
+SIVE can therefore provide useful insight into the sensitivity of hyper-Raman spectroscopy to different infrared active vibrations.
+
+\subsection{Coherent Interference in SR-SIVE}
 It is well known that nonlinear wave mixing processes which share the same time ordering and output frequency will interfere. \cite{RN135, Bonn2024}
@@
 \end{figure}
-
+\begin{widetext}
 We employ the response function formalism of Mukamel for this analysis. \cite{RN287}
@@
 By assuming that the beams which stimulate hyper-Raman scattering, $\vec{E}_1, \vec{E}_3$, interact simultaneously at some time $\tau$ after $\vec{E}_2$ interacts with the sample, the total output polarization, $\vec{P}^{(3)}(t)$, is written as \cite{Cho2001}
-\begin{widetext}
 	\begin{equation}\label{polarization_SRSIVE_a}
@@
 	\end{equation}
+It is clear the total output polarization for SR-SIVE-IR-II and SR-SIVE-Raman vanishes, or, SR-SIVE-IR-II and SR-SIVE-Raman perfectly destructively interfere.
 \end{widetext}
-It is clear the total output polarization for SR-SIVE-IR-II and SR-SIVE-Raman vanishes, or, SR-SIVE-IR-II and SR-SIVE-Raman perfectly destructively interfere.
 The absence of SR-SIVE-IR-II pathways in ultrafast DOVE work is rationalized by this calculation. \cite{RN367, McDonnell2024}
@@
 A possible mechanism for interfering output in the SR-SIVE-I pathway are cascaded second order processes (SFG, DFG). \cite{RN243, RN300}
-In isotropic media, SFG and DFG vanish under the electric dipole approximation,\cite{RN231} so cascades are unlikely to inhibit output in centrosymmetric media.
+In isotropic media, SFG and DFG vanish under the electric dipole approximation,\cite{Zhu87} so cascades are unlikely to inhibit output in centrosymmetric media.
 In media where SFG and DFG are allowed, e.g. surfaces or noncentrosymmetric media, second order cascades may become important. 
@@
 
-\subsection{Rovibrational SR-SIVE Selection Rules} %this can probably be deleted but wanted to add just in case...
-Recent developments in nonlinear spectroscopy have demonstrated the feasibility of multidimensional infrared spectroscopy of gaseous and quasi-free species.
-\cite{Ziegler2018, Gronborg2022, RN325, Chen2024}
-DOVE and 2D-IR have been used to isolate coupling between fundamentals, overtones and combination bands of gaseous species in several molecular systems. 
-Since resonance hyper-Raman scattering spectroscopy was developed as a gas phase spectroscopy, we briefly investigate the properties of rovibrational SR-SIVE.\cite{Ziegler1987}
+\begin{figure}[!htbp]
+	\centering
+	\includegraphics[width=3.375in]{main/wmel3.png}
+	\caption{WMEL diagrams of some DR-SIVE pathways in the $-\vec{k}_1 + \vec{k}_2+ \vec{k}_3$  (I-a,I-b) and $\vec{k}_1 + \vec{k}_2+ \vec{k}_3$ (II-a,II-b) phasematching outputs.
+$\ket{g,0}$ denotes the ground states, $\ket{g,v}$ denotes a vibrational state on the ground electronic manifold; $\ket{m,n}$ denotes a virtual state, and $\ket{e,0}, \ket{e,v'}$ denote vibronic states.}
+	\label{fig:doubsive}
+\end{figure}
 
-The rovibrational selection rules are generated through calculating \autoref{sivebeta} in a $\ket{vJM} \equiv \ket{v} \otimes {\ket{JM}}$ basis, where $\{\ket{v}\}$ is a basis of vibrational states and $\{\ket{JM}\}$ is a basis of rotational states ($J$ is the rotational quantum number and $M$ is its z projection, respectively).
-By writing $\vec{\mu} = T_{q_1}^{(1)}$ and $\beta_{ijk} = T_{q_1}^{(1)} + T_{q_2}^{(2)} + T_{q_3}^{(3)}$, where $T^{(k)}_{q}$ is a rank k spherical tensor, it is simple to evaluate the integrals in \autoref{sivebeta} with the Wigner-Eckart theorem.
-\cite{Kowzan2022}
-It is important to note that $\beta_{ijk}$ does not have complete tensor index symmetry.
-Specifically, it has shown that the rank one spherical tensor ($T_{q_1}^{(1)}$, with $q_1 \in -1, 0 ,1$) fully contributes to $\beta_{ijk}$ but only select $T_{q_2}^{(2)} + T_{q_3}^{(3)}$ terms contribute.
-\cite{Andrews1978, Andrews1990}
-%there is some fancy way to note that theres no index constraint but i dont remember the language...
-As such, its decomposition into irreducible tensor form is allowed only if the values of $q', q''$ are constrained.
-By substituting the spherical tensor definitions of $\vec{\mu}$ and $\beta_{ijk}$ into \autoref{sivebeta}, it is clear that only $\Delta J = \pm 1$; $\Delta M = 0, \pm1$ transitions are allowed.
-This is expected since $\vec{\mu}$ transitions demand $\Delta J = \pm 1$.
-As a result, consistent with vibrational SR-SIVE, rovibrational SR-SIVE follows the same rules as common infrared rovibrational spectroscopy.
-
-\subsection{DR-SIVE-IR Selection Rules}
+\subsection{DR-SIVE-IR Selection Rules} %%most of this can probably be scrapped because... we don't really learn much new here.
 DR-SIVE (where a vibrational and vibronic state are resonantly coupled) can provide a tool for measuring vibronic coupling.
@@
 \cite{BornOppenheimer, Albrecht1960}
-
-\begin{figure}[!htbp]
-	\centering
-	\includegraphics[width=3.375in]{main/wmel3.png}
-	\caption{WMEL diagrams of some DR-SIVE pathways in the $-\vec{k}_1 + \vec{k}_2+ \vec{k}_3$  (I-a,I-b) and $\vec{k}_1 + \vec{k}_2+ \vec{k}_3$ (II-a,II-b) phasematching outputs.
-$\ket{g,0}$ denotes the ground states, $\ket{g,v}$ denotes a vibrational state on the ground electronic manifold; $\ket{m,n}$ denotes a virtual state, and $\ket{e,0}, \ket{e,v'}$ denote vibronic states.}
-	\label{fig:doubsive}
-\end{figure}
 
@@
 $R^{i}_{gv,ev'} = \mel{v}{M^i_{ge}}{v'}$.\cite{Albrecht1960}
-Using these ideas allows us to rewrite \autoref{drgamma_notaylor} as
+\begin{widetext}
+Using these ideas rewrites \autoref{drgamma_notaylor} as
 \begin{equation}\label{drgamma_notaylor_1}
@@
 where ${\Lambda^{jk}_{eg}} = (e|\Lambda^{jk}|g)$. 
+\end{widetext}
 Since $\Lambda^{jk}$ transforms like a rank two tensor, it is clear that the electronic transition must be both one and two photon allowed for non-zero output, similar to resonant second harmonic generation spectroscopy.
@@
 likely due to the resonance hyper-Raman process.
-Resonance hyper-Raman scattering is known to increase spectral output by orders of magnitude relative to non-resonance hyper-Raman scattering in gaseous systems. \cite{Ziegler87_CPL, RN515}.
+Resonance hyper-Raman scattering is known to increase spectral output by orders of magnitude relative to non-resonance hyper-Raman scattering in gaseous systems. \cite{RN515}.
 These spectra also indicate that the low lying electronic states of cobalamin are one and two photon allowed transitions, or, the lowest lying electronic state has mixed parity, as it accessible by operators that transform as odd (dipole) and even (two photon absorption) functions.
@@
 \section{Conclusions}
-Coherent vibrational, hyper-Raman type spectroscopies are identified and discussed.
+Coherent vibrational, hyper-Raman coherent four wave mixing spectroscopies are identified and discussed.
 Singly resonant SIVE (SR-SIVE) processes are shown to be the coherent hyper-Raman analogue of infrared active vibrations.
 Since SR-SIVE is always non-zero for IR active vibrations, the method could be used as an analytical method to optically upconvert infrared transitions with small transition dipoles.
+A method for measuring hyper-Raman polarizabilities, $\beta_{ijk}$, through SIVE spectroscopy was identified and discussed.
 Doubly resonant SIVE (DR-SIVE) processes show promise as a probe of vibronic coupling in molecular samples.
 Unlike SR-SIVE, DR-SIVE methods can linenarrow inhomogeneously broadened vibronic modes. 
-These methods show promise as a probe of ultrafast relaxation dynamics in isotropic systems.
+SR and DR-SIVE of cyanocobalamin (i.e., vitamin B-12) highlight the impact of hyper-Raman cross sections on SIVE output, and pave the way for future studies of complex phenomena in large molecular systems through two beam four wave mixing methods.
 
@@
 
-%\section{Appendix A: Rationale for use of Lorentzian Distribution to calculate Line Narrowing Effects}
-%Here we investigate the claim that one can substitute a Lorentzian in lieu of a Gaussian when performing the convolution integral
-%\begin{equation}\label{inhomog}
-%	\rho_{ij} = \int \mathrm{d}\xi P(\xi) \rho_{ij}(\xi)
-%\end{equation}
-%where $P(\xi)$ is a probability distribution and $\rho_{ij}$ is a density matrix element. 
-%The reason for introducing a Lorentzian distribution in lieu of a Gaussian is that \autoref{inhomog} can be evaluated in closed-form if $P(\xi)$ is Lorentzian. \cite{Penner1976} 
-%Consider a Lorentzian and Gaussian distribution:
-%\begin{equation}\label{lorentzian}
-%	f(\xi) = \frac{\sigma}{\pi} \frac{1}{\xi^2 + \sigma^2}
-%\end{equation}
-%\begin{equation}\label{gaussian}
-%	g(\xi) = \sqrt{\frac{1}{2\pi\sigma^2}} \exp(-\frac{\xi^2}{2\sigma^2})
-%\end{equation}
-%We investigate the behavior of these distributions by Taylor expanding each function. 
-%$f(\xi)$ is written such that
-%\begin{equation}
-%	f(\xi) = \frac{\sigma}{\pi}\frac{1}{\sigma^2} \frac{1}{1 + (\frac{\xi}{\sigma})^2} = \frac{1}{\pi \sigma}\frac{1}{1 + (\frac{\xi}{\sigma})^2}
-%\end{equation}
-%Introducing $x = \frac{\xi}{\sigma}$ and using the identity
-%\begin{equation}
-%	\frac{1}{1+x^2} = \frac{1}{1-(-x^2)} = \sum_{n=0}^\infty (-1)^{n}x^{2n}, |x| < 1
-%\end{equation}
-%we write \autoref{lorentzian} as
-%\begin{equation}
-%	f(x) = \frac{1}{\pi \sigma} \sum_{n=0}^\infty (-1)^{n}x^{2n}, |x| < 1
-%\end{equation}
-%Similarly, by using
-%\begin{equation}\label{gaussianexp}
-%	\exp(-ax^2) = \sum_{n=0}^\infty \frac{(-a)^n}{n!} x^{2n}, x \in \mathbb{C}
-%\end{equation}
-%we write \autoref{gaussian} as
-%\begin{equation}
-%	g(x) = \sqrt{\frac{1}{2\pi\sigma^2}} \sum_{n=0}^\infty \frac{(-1)^n  x^{2n}}{2^n n!}, x \in \mathbb{C}
-%\end{equation}
-%%The functional forms of $f(\xi), g(\xi)$ are very similar in the large $\sigma$ and small $\xi$ limits.
-%By comparing the expansions of $f(x)$ and $g(x)$, it is clear that the primary difference between the Lorentzian and Gaussian distributions are the convergence rates due to a factor of $\frac{1}{2^n n!}$ in \autoref{gaussianexp}.
-%As such, it is reasonable to substitute a Lorentzian distribution for a Gaussian distribution when evaluating \autoref{inhomog}.
-%
-%As a note, since the Lorentzian distribution's convergence radius is constrained by its singularities ($\pm i$), the two distributions are truly comparable only if the tails of the Lorentzian distribution are ignored.
-%With this in mind, we note that
-%\begin{subequations}
-%	\begin{equation}
-%		\frac{1}{\pi}\int_{-1}^1 \mathrm{d}x \frac{1}{1+x^2} = \frac{1}{2}
-%	\end{equation}
-%	\begin{equation}
-%		\sqrt{\frac{1}{2\pi}} \int_{-1}^1 \mathrm{d}x \exp(-\frac{x^2}{2}) = \erf{\sqrt{\frac{1}{2}}} \approx 0.68
-%	\end{equation}
-%\end{subequations}
-%or, the integrals are roughly similar when considering the radius of convergence of the Lorentzian distribution. 
-%As such, we extend the bounds of integration from $(-1, 1)$ to $(-\infty, \infty)$ to facilitate simple calculation of \autoref{contour}.
-%We note that Dick and Hochstrasser numerically showed some years ago that the tails of the Lorentzian distribution have little effect on the calculation of \autoref{inhomog}, in agreement with the suggested result.\cite{Dick83_1}
 \section{Appendix A: Evaluation of Pathway I-a Linenarrowing Capability}
+\begin{widetext}
 The output coherence  for this pathway is $\rho_{ev',gv}(\xi)$.
 Setting $\eta$ equal to the numerator of \autoref{drgamma_alpha_0} along with any constants, we see
-\begin{widetext}
 \begin{equation}\label{ev'gv}
@@
 \end{equation}
-\end{widetext}
+
 For notational convenience, we map $\ket{g,0} \rightarrow \ket{g}$, $\ket{g,v} \rightarrow \ket{a}$ and $\ket{e,v'} \rightarrow \ket{b}$.
@@
 Following \autoref{fig:contours}, the contour that wraps the upper half of the complex plane has only one pole, $i \sigma$; as such, we choose to evaluate \autoref{integraly} in the upper half of the complex plane for the case of anti-correlated modes through the residue theorem as
-\begin{widetext}
 	\begin{equation}
@@
 	\end{equation}
-\end{widetext}
 
@@
 Therefore, pathway I-a cannot linenarrow anti-correlated modes. 
-\subsubsection{Correlated Modes: c = 1}
+\subsubsection{Correlated Modes}
 For correlated modes, the poles are situated in the complex plane as shown in \autoref{fig:contours}.
@@
 For the below calculation, we choose to evaluate along the contour in the bottom half of the complex plane, i.e., the poles ($\xi_k$) are $-i\sigma, \Delta_{ga}$.
-We stress that since the integral is evaluated over $\mathbb{R}$ and there are no degenerate poles, the results below can be obtained by evaluating the contour which wraps around the poles $i\sigma, \Delta_{ba}$.
-Since the $\xi_k$ are nondegenerate, \autoref{integraly} can be evaluated using the Residue theorem as 
-\begin{widetext}
+We stress that since the integral is evaluated over $\mathbb{R}$ and there are no degenerate poles, the results below can be obtained by evaluating the contour which wraps around the poles $i\sigma, \Delta_{ba}$ using the Residue theorem as
+
 	\begin{equation}
@@
 			\lim_{\xi \rightarrow \Delta_{ga}(0)} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga}(0) - \xi} \frac{1}{\Delta_{ba}(0) - \xi} (\xi - \Delta_{ga}))\\
-			&= 2 \eta i \sigma (\frac{1}{2 i \sigma} \frac{1}{-i \sigma - \Delta_{ga}(0)} \frac{1}{\Delta_{ba}(0) - i\sigma} ) - 2 \eta i \sigma (\frac{1}{\sigma^2 + (\Delta_{ga} (0))^2} \frac{1}{\Delta_{ga}(0) + \Delta_{ba}(0)} )\\
+%			&= 2 \eta i \sigma (\frac{1}{2 i \sigma} \frac{1}{-i \sigma - \Delta_{ga}(0)} \frac{1}{\Delta_{ba}(0) - i\sigma} ) - 2 \eta i \sigma (\frac{1}{\sigma^2 + (\Delta_{ga} (0))^2} \frac{1}{\Delta_{ga}(0) + \Delta_{ba}(0)} )\\
 			&= -\frac{\eta}{\Delta_{ga}(0) + i \sigma} (\frac{1}{\Delta_{ba}(0) - i \sigma} + \frac{2i\sigma}{(\Delta_{ga}(0) - i \sigma)(\Delta_{ga}(0) + \Delta_{ba}(0))})\\
@@
 	\end{equation}
-\end{widetext}
 The final line of the above equation shows the presence of a new term, $\frac{2i\sigma}{\Delta_{ga}(0) + \Delta_{ba}(0)}$. 
@@
 Results for the other pathways follow the same technique.
-Generally, when starting from the ground state, non-parametric spectroscopies line-narrow correlated modes, and parametric spectroscopies line-narrow anti-correlated modes. \cite{Dick83_1, RN425}
+\end{widetext}
+%Generally, when starting from the ground state, non-parametric spectroscopies line-narrow correlated modes, and parametric spectroscopies line-narrow anti-correlated modes. \cite{Dick83_1, RN425}
 

### 2024-06-11 paper.tex
added fayer ref

@@
 The recorded $\chi^{(n)}$ values provide insight into how microscopic quantities ($\vec{\mu}, \alpha_{ij}, \beta_{ijk}$) impact nonlinear output.
-To our knowledge, only 2D-IR spectroscopy has taken advantage of orientationally averaged $\chi^{(3)}$ values to extract transition moments.\cite{Grechko2012}
+To our knowledge, only 2D-IR spectroscopy has taken advantage of orientationally averaged $\chi^{(3)}$ values to extract transition moments. \cite{Moilanen2009, Grechko2012}
 Previous treatments did not consider using quantitative analysis in SIVE to measure $\beta_{ijk}$ values from SIVE spectra.

### 2024-06-11 paper.tex
oops

@@
 The recorded $\chi^{(n)}$ values provide insight into how microscopic quantities ($\vec{\mu}, \alpha_{ij}, \beta_{ijk}$) impact nonlinear output.
-To our knowledge, only 2D-IR spectroscopy has taken advantage of orientationally averaged $\chi^{(3)}$ values to extract transition moments. \cite{Moilanen2009, Grechko2012}
+To our knowledge, only 2D-IR spectroscopy has taken advantage of orientationally averaged $\chi^{(3)}$ values to extract transition moments. \cite{Moilanen2009, RN245}
 Previous treatments did not consider using quantitative analysis in SIVE to measure $\beta_{ijk}$ values from SIVE spectra.
@@
 \end{equation} 
-While Gaussian distributions are commonly used to describe inhomogeneous broadening,\cite{RN307} Lorentzian distributions have successfully described inhomogeneous broadening in a variety of spectroscopies and yield easily interpreted closed-form solutions.
+While Gaussian distributions are commonly used to describe inhomogeneous broadening,\cite{druet1979line, RN307} Lorentzian distributions have successfully described inhomogeneous broadening in a variety of spectroscopies and yield easily interpreted closed-form solutions.
 \cite{Dick83_1, Carlson1990line}

### 2024-06-11 paper.tex
small edits

@@
-\documentclass[aip, jcp, reprint, twocolumn]{revtex4-2}
+\documentclass[aip, jcp, reprint, onecolumn]{revtex4-2}
 
@@
 Nonlinear, four wave mixing vibrational spectroscopies are often used to probe intramolecular vibrational coupling and relaxation dynamics.
-Three wave mixing vibrational spectroscopies are similarly often used to understand the spectroscopy and dynamics of interfacial species.
+Three wave mixing vibrational spectroscopies are similarly used to understand the spectroscopy and dynamics of interfacial species.
 Most of these methods rely on infrared or Raman transitions to generate output. 
-The implementation of a nonlinear hyper-Raman spectroscopy, which first appears at third order perturbation theory, can provide a useful analogue to these techniques.
-Singly Vibrationally Enhanced (SIVE) spectroscopy, a type of nonlinear hyper-Raman spectroscopy, is an underdeveloped four wave mixing technique which shows promise to disentangle ultrafast vibrational dynamics in isotropic systems without need for anharmonicities.
+The implementation of a nonlinear hyper-Raman spectroscopy, which first appears at third order perturbation theory, can provide a useful analogue to these techniques to understand the spectroscopy and dynamics of isotropic systems.
+Singly Vibrationally Enhanced (SIVE) spectroscopy, a type of nonlinear hyper-Raman spectroscopy, is an underdeveloped four wave mixing technique which shows promise as a method to disentangle ultrafast vibrational dynamics in isotropic systems without need for anharmonicities.
 We derive selection rules and coherent interference effects in singly resonant SIVE (SR-SIVE).
@@
 \textit{in-situ} power corrections are performed by dividing the recorded spectra by OPA output measured by home-built pyroelectric detectors.
+All spectra are reported on the intensity scale. %@dan if we should change to amp lmk
 
@@
 	\centering
-	\includegraphics[width=3.375in]{main/wmel1.png}
+	\includegraphics[width=3.375in]{wmel1.png}
 	\caption{Wave Mixing Energy Level (WMEL) diagrams of the relevant SR-SIVE pathways in the (a) $\vec{k}_4 = -\vec{k}_1 + \vec{k}_2 + \vec{k}_3$ and (b) $\vec{k}_4 = \vec{k}_1 + \vec{k}_2 + \vec{k}_3$ phasematching geometries.
@@
 Since resonance hyper-Raman scattering spectroscopy was developed as a gas phase spectroscopy,\cite{RN515} we briefly investigate the properties of rovibrational SR-SIVE.
+In the discussion that follows, to avoid integration over velocity dependent distributions, we assume the experiment is performed at 0 K.
+The velocity dependence of output density matrix elements does not manipulate quantum mechanical selection rules. \cite{Bracamonte2003}
 
-The rovibrational selection rules are generated through calculating \autoref{sivebeta} in a $\ket{vJM} \equiv \ket{v} \otimes {\ket{JM}}$ basis, where $\{\ket{v}\}$ is a basis of vibrational states and $\{\ket{JM}\}$ is a basis of rotational states ($J$ is the rotational quantum number and $M$ is its z projection, respectively).
-By writing $\vec{\mu} = T_{q_1}^{(1)}$ and $\beta_{ijk} = T_{q_1}^{(1)} + T_{q_2}^{(2)} + T_{q_3}^{(3)}$, where $T^{(k)}_{q}$ is a rank $k$ spherical tensor, it is simple to evaluate the integrals in \autoref{sivebeta} through the Wigner-Eckart theorem.
-\cite{Kowzan2022}
-It is important to note that $\beta_{ijk}$ does not have complete tensor index symmetry.
+The rovibrational selection rules are generated through calculating \autoref{sivebeta} in a $\ket{vJM} \equiv \ket{v} \otimes {\ket{JM}}$ basis, where $\{\ket{v}\}$ is a basis of vibrational states and $\{\ket{JM}\}$ is a basis of rotational states ($J$ is the total angular momentum and $M$ is its projection onto the space fixed quantization axis).
+By writing $\vec{\mu} = T_{q_1}^{(1)}$ and $\beta_{ijk} = T_{q_1}^{(1)} + T_{q_2}^{(2)} + T_{q_3}^{(3)}$, where $T^{(k)}_{q}$ is a rank $k$ spherical tensor, the matrix elements in \autoref{sivebeta} can be evaluated through the Wigner-Eckart theorem.
+It is important to note that $\beta_{ijk}$ does not have complete tensor index symmetry.\cite{Andrews1978}
 Specifically, it has shown that the rank one spherical tensor ($T_{q_1}^{(1)}$, with $q_1 \in \{-1, 0 ,1\}$) fully contributes to $\beta_{ijk}$ but only select $T_{q_2}^{(2)} + T_{q_3}^{(3)}$ terms contribute.
@@
 With the selection rules of SR-SIVE understood for vibrational and rovibrational spectroscopy, it becomes possible to extract quantitative information from SIVE spectra to compare to incoherent methods and other CMDS methods.
-
 Lineshape analysis is essential for extracting quantitative information from CMDS spectra.
 Scanning across resonances create dispersive lineshapes, i.e, self-heterodyning, which inform on $\Re{\chi^{(3)}}$ and $\Im{\chi^{(3)}}$.\cite{Levenson1974_1, Levenson1974_2}
-Resonant SIVE lineshapes are complicated by amplitude level interference between the sample and its substrate and/or sample cell windows. \cite{RN362}
+In previous studies, following the method introduced by Levenson and Bloembergen, an internal standard was added to the sample.
+The internal standard in most experiments was chosen to be C$_6$H$_6$ or C$_6$D$_6$, due to the strong Raman activity and measured $\chi^{(3)}$ of its ring breathing mode ($\nu_2$ in Herzberg notation).
+\cite{Levenson1974_2, RN351, RN345}
+Interference between the sample and internal standard resonances allowed measurment of $\chi^{(3)}$.
+Such a method does not require measurment of absolute intensities and instead relies on self-heterodyning of the internal standard signal. 
+Resonant SIVE lineshapes are also complicated by amplitude level interference between the sample and its substrate and/or sample cell windows. \cite{RN362}
 These effects have been treated in excellent detail for three laser infrared-infrared-visible SIVE using the pathway in \autoref{fig:sivewmel}a, and provide methods to export quantitative information from SIVE spectra.
@@
 \begin{split}
-		\chi^{(3)}_{IJKL} &\sim \langle \gamma_{ijkl} \rangle \sim \langle \beta_{ijk} \mu_l \rangle\\
+		\chi^{(3)}_{IJKL} &= NF(\omega_4) \langle \gamma_{ijkl} \rangle \sim \langle \beta_{ijk} \mu_l \rangle\\
 \end{split}
 \end{equation}
-The steps behind orientational averaging of $\gamma_{ijkl}$ are detailed elsewhere.\cite{Andrews1977, McDonnell2024}
-Orientational averaging for specific input polarizations shows that specific polarization schemes isolate linear combinations of different $\beta_{ijk}$ terms. 
+The steps behind orientational averaging of $\gamma_{ijkl}$, a rank four tensor in the molecular frame, are detailed elsewhere.\cite{Andrews1977, McDonnell2024}
+Orientational averaging shows specific polarization schemes isolate linear combinations of different $\beta_{ijk}$ terms. 
 Infrared spectra can provide values for different $\vec{\mu}$ components.
@@
 		\begin{split}
-			\chi^{(3)}_{IJKL} &\sim \langle \beta_{ijk} \mu_l \rangle\\
+			\langle \gamma_{ijkl} \rangle &\sim \langle \beta_{ijk} \mu_l \rangle\\
 			&\sim \langle \beta_{ijk} \rangle \frac{\mu}{\sqrt{3}} 
@@
 This is done because any element of $\vec{\mu}$ is easily related to its magnitude through the directional cosine relationship shown above. 
-Continuing, we see
+Continuing by substituting in the results found in \autoref{SIVEselection}, we see
 	\begin{equation}
-		\langle \beta_{ijk} \rangle \sim \frac{\sqrt{3}}{\mu} \chi^{(3)}_{IJKL}
+		\langle \beta_{ijk} \rangle = - 24\sqrt{3} \frac{\hbar \varepsilon_0 \Delta_{gv}}{NF(\omega_4)\rho_{gg}} \frac{\chi^{(3)}_{IJKL}}{\mu}
 	\end{equation}
@@
 	\centering
-	\includegraphics[width=3.375in]{main/wmel2.png}
+	\includegraphics[width=3.375in]{wmel2.png}
 	\caption{Wave Mixing Energy Level (WMEL) diagrams of interfering SR-SIVE pathways in the  $\vec{k}_4 = -\vec{k}_1 + \vec{k}_2 + \vec{k}_3$ phasematching geometry. 
-	(a) is similar to the process diagrammed in \autoref{fig:sivewmel}, whereas (b) is similar to a singly resonant coherent anti-Stokes Raman-type process.}
+	(a) is similar to the process diagrammed in \autoref{fig:sivewmel}, whereas (b) is similar to a coherent anti-Stokes Raman (CARS)-type process.}
 	\label{fig:sivewmel2}
@@
 We employ the response function formalism of Mukamel for this analysis. \cite{RN287}
-The third order response functions, $R^{(3)}$, for SR-SIVE-IR-II ($R^{(3)}_{S_{II}}$) and SR-SIVE-Raman ($R^{(3)}_{R}$) (\autoref{fig:sivewmel2}a, b) are 
+The third order response functions, $R^{(3)}$, for SR-SIVE-IR-II ($R^{(3)}_{S_{II}}$) and SR-SIVE-Raman ($R^{(3)}_{R}$) (\autoref{fig:sivewmel2}a, b), suppressing tensor indices, are 
 \begin{subequations}
@@
 \end{subequations}
-By assuming that the beams which stimulate hyper-Raman scattering, $\vec{E}_1, \vec{E}_3$, interact simultaneously at some time $\tau$ after $\vec{E}_2$ interacts with the sample, the total output polarization, $\vec{P}^{(3)}(t)$, is written as \cite{Cho2001}
+By assuming that the fields which stimulate hyper-Raman scattering, $\vec{E}_1, \vec{E}_3$, interact simultaneously at some time $\tau$ after $\vec{E}_2$ interacts with the sample, the total output polarization, $\vec{P}^{(3)}(t)$, is written as \cite{Cho2001}
 	\begin{equation}\label{polarization_SRSIVE_a}
@@
 	\centering
-	\includegraphics[width=3.375in]{main/wmel3.png}
+	\includegraphics[width=3.375in]{wmel3.png}
 	\caption{WMEL diagrams of some DR-SIVE pathways in the $-\vec{k}_1 + \vec{k}_2+ \vec{k}_3$  (I-a,I-b) and $\vec{k}_1 + \vec{k}_2+ \vec{k}_3$ (II-a,II-b) phasematching outputs.
@@
 	\centering
-	\includegraphics[width=6.66in]{main/cob.png}
+	\includegraphics[width=6.66in]{cob.png}
 	\caption{
@@
 	\centering
-	\includegraphics[width=3.375in]{main/corr_contour.png}
+	\includegraphics[width=3.375in]{corr_contour.png}
 	\caption{Poles (black dots) and contour (blue line) used to evaluate \autoref{integraly} for (a) anti-correlated and (b) correlated modes.} 

### 2024-06-11 paper.tex
Update paper.tex

@@
 where $\alpha_{ij}$ is the Raman polarizability, N$_{bulk}$ is the bulk number density, and N$_{surf}$ is the surface number density (10$^{19}$ m$^{-2}$).\cite{RN133, RN503}	
-\end{widetext}
 For liquids with molar masses less than $\sim$100 g mol$^{-1}$ and densities roughly equal to that of H$_2$O$_{(l)}$ at room temperature, N$_{bulk} \sim$ 10$^{28}$ m$^{-3}$.
@@
 \end{equation}
+\end{widetext}
 Ziegler has noted that for a field of intensity 10 GW/cm$^{2}$, $\frac{\beta E}{\alpha} \sim 10^{-3} $ for vibrational modes when $E(\omega_3)$ is largely detuned from electronic resonances.

### 2024-06-11 paper.tex
shen90 exists!

@@
 	\begin{equation}
-		\mu = \mu_0 + \frac{\partial \mu}{\partial Q_n} Q_n + \order{\sum_{m,n}{Q_m Q_n}}
+		\mu = \mu_0 + \frac{\partial \mu}{\partial Q_n} Q_n + \order{{Q_m Q_n}}
 	\end{equation}
 	\begin{equation}
-		\beta = \beta_{0} + \frac{\partial \beta}{\partial Q_n} Q_n + \order{\sum_{m,n}{Q_m Q_n}}
+		\beta = \beta_{0} + \frac{\partial \beta}{\partial Q_n} Q_n + \order{{Q_m Q_n}}
 	\end{equation}
@@
 The recorded $\chi^{(n)}$ values provide insight into how microscopic quantities ($\vec{\mu}, \alpha_{ij}, \beta_{ijk}$) impact nonlinear output.
-To our knowledge, only 2D-IR spectroscopy has taken advantage of orientationally averaged $\chi^{(3)}$ values to extract transition moments. \cite{Moilanen2009, RN245}
+To our knowledge, only vibraitonal SFG and 2D-IR spectroscopy has taken advantage of orientationally averaged $\chi^{(n)}$ values to extract transition moments. \cite{Shen90, Moilanen2009, RN245}
 Previous treatments did not consider using quantitative analysis in SIVE to measure $\beta_{ijk}$ values from SIVE spectra.

### 2024-06-14 paper.tex
Update paper.tex

@@
 %Title of paper
-\title{Coherent Hyper-Raman Four Wave Mixing Spectroscopies}
+\title{Coherent Hyper-Raman Four Wave Mixing Vibrational Spectroscopies}
 
@@
 
-Most quantitative methods in an n$^{th}$ order CMDS experiment are used to extract $\chi^{(n)}$ values for comparing the relative strength of nonlinear processes in different media.
+Most quantitative methods in an n$^{th}$ order CMDS experiment are used to extract $\chi^{(n)}$ values to compare the relative strength of nonlinear processes in different media.
 \cite{Zhu87, RN351, RN345}
@@
 
-The SIVE $\chi^{(3)}_{IJKL}$ expresson is
+The SIVE $\chi^{(3)}_{IJKL}$ expression is
 \begin{equation}\label{chi3}
@@
 \end{equation}
+This expression cannot be exactly used to extract $\beta_{ijk}$, as $\beta_{ijk}$ is a Hermitian operator but $\Delta_{gv} \in \mathbb{C}$. 
+However, when on resonance, $\Delta_{gv} = -i\Gamma_{gv}$.
+Thus, below we consider cases where the experiment is resonant, so that $\chi^{(3)}_{IJKL}$ is purely imaginary, or, (insert equation).
+Clearly, we can then see that $\langle \beta_{ijk} \mu_l \rangle \sim -\frac{1}{\Gamma_{gv}}\Im(\chi^{(3)}_{IJKL})$
+
 The steps behind orientational averaging of $\gamma_{ijkl}$, a rank four tensor in the molecular frame, are detailed elsewhere.\cite{Andrews1977, McDonnell2024}

### 2024-06-15 paper.tex
updates

@@
-\documentclass[aip, jcp, reprint, onecolumn]{revtex4-2}
+\documentclass[aip, jcp, draft, onecolumn]{revtex4-2}
 
@@
 The resultant output was used to pump four independent OPAs, two of which are relevant for this study.
-OPA1 (TOPAS-800, Light Conversion), referred to as $\omega_1$, was tuned for difference frequency generation (DFG) with an external stage (NDFG "DF2", Light Conversion).
+OPA1 (TOPAS-800, Light Conversion), referred to as $\omega_1$, was tuned for difference frequency generation (DFG) with an external stage (NDFG \"DF2\", Light Conversion).
 OPA2 (OPA-800C, Spectra Physics), referred to as $\omega_2$, was tuned in its signal arrangement. 
@@
 Scanning across resonances create dispersive lineshapes, i.e, self-heterodyning, which inform on $\Re{\chi^{(3)}}$ and $\Im{\chi^{(3)}}$.\cite{Levenson1974_1, Levenson1974_2}
-In previous studies, following the method introduced by Levenson and Bloembergen, an internal standard was added to the sample.
-The internal standard in most experiments was chosen to be C$_6$H$_6$ or C$_6$D$_6$, due to the strong Raman activity and measured $\chi^{(3)}$ of its ring breathing mode ($\nu_2$ in Herzberg notation).
-\cite{Levenson1974_2, RN351, RN345}
-Interference between the sample and internal standard resonances allowed measurment of $\chi^{(3)}$.
-Such a method does not require measurment of absolute intensities and instead relies on self-heterodyning of the internal standard signal. 
-Resonant SIVE lineshapes are also complicated by amplitude level interference between the sample and its substrate and/or sample cell windows. \cite{RN362}
-These effects have been treated in excellent detail for three laser infrared-infrared-visible SIVE using the pathway in \autoref{fig:sivewmel}a, and provide methods to export quantitative information from SIVE spectra.
-\cite{RN418}
+In the method introduced by Levenson and Bloembergen, an internal standard, often chosen to be  
+C$_6$H$_6$ or C$_6$D$_6$, due to the strong Raman activity and measured $\chi^{(3)}$ of its ring breathing mode ($\nu_2$ in Herzberg notation), causes interference. \cite{Levenson1974_2, RN351, RN345}
+This interference measures $\chi^{(3)}$ and does not require measurement of absolute intensities; it instead relies on self-heterodyning of the internal standard signal. 
+Resonant lineshapes are also complicated by amplitude level interference between the sample and its substrate and/or sample cell windows. \cite{RN362, RN418}
 
@@
 \begin{split}
-		\chi^{(3)}_{IJKL} &= NF(\omega_4) \langle \gamma_{ijkl} \rangle \sim \langle \beta_{ijk} \mu_l \rangle\\
+		\chi^{(3)}_{IJKL} &= NF(\omega_4) \langle \gamma_{ijkl} \rangle = -\frac{NF}{24 \hbar \varepsilon_0 \Delta_{gv}} \langle \beta_{ijk} \mu_l \rangle \rho_{gg}\\
 \end{split}
 \end{equation}
-This expression cannot be exactly used to extract $\beta_{ijk}$, as $\beta_{ijk}$ is a Hermitian operator but $\Delta_{gv} \in \mathbb{C}$. 
-However, when on resonance, $\Delta_{gv} = -i\Gamma_{gv}$.
-Thus, below we consider cases where the experiment is resonant, so that $\chi^{(3)}_{IJKL}$ is purely imaginary, or, (insert equation).
-Clearly, we can then see that $\langle \beta_{ijk} \mu_l \rangle \sim -\frac{1}{\Gamma_{gv}}\Im(\chi^{(3)}_{IJKL})$
+This expression cannot be used as written to extract $\beta_{ijk}$, as $\beta_{ijk}$ is a Hermitian operator, but $\Delta_{gv} \in \mathbb{C}$. 
+However, since the real and imaginary parts of $\chi^{(3)}$ can be extracted from the Bloembergen experiment, we can choose to focus on either its real or imaginary part.
+For simplicity, we investigate $\Im(\chi^{(3)})$, giving, assuming resonance conditions, 
+\begin{equation}
+	\langle \beta_{ijk} \mu_{l} \rangle = \frac{24 \hbar \varepsilon_0}{NF} \Gamma_{gv} \frac{1}{\rho_{gg}} \Im(\chi^{(3)}_{IJKL})
+\end{equation}
 
@@
 \cite{RN459}
-Neglecting rotational dependence, $\langle {\mu^2} \rangle = \abs{\mu}^2 = \mu^2$.
-Substituting into \autoref{chi3} shows that
-\begin{subequations}
-	\begin{equation}
-		\begin{split}
-			\langle \gamma_{ijkl} \rangle &\sim \langle \beta_{ijk} \mu_l \rangle\\
-			&\sim \langle \beta_{ijk} \rangle \frac{\mu}{\sqrt{3}} 
-		\end{split}
+Neglecting rotational dependence (i.e., assuming only vibrational transitions), $\langle {\mu^2} \rangle = \abs{\mu}^2 = \mu^2$, so that $\langle \beta_{ijk} \mu_l \rangle = \langle \beta_{ijk} \rangle \frac{\mu}{\sqrt{3}}$.
+By introducing the reduced mass coordinate $q_n = \sqrt{\frac{1}{m_n}} Q_n$ and using the expansions of $\beta_{ijk}$ and $\mu_{l}$ found earlier, knowing that $(\mel{v}{q}{g})^2 = \frac{\hbar}{2\omega_{vg}}$ under the harmonic approximation, shows
+\begin{equation}\label{betasive}
+	\langle \frac{\partial \beta_{ijk}}{\partial q_n} \rangle = \varepsilon_0 \frac{48 \sqrt{3} }{NF}  \frac{\Gamma_{gv} \omega_{vg}}{\rho_{gg}} \frac{\Im(\chi^{(3)}_{IJKL})}{\frac{\partial \mu_{l}}{\partial q_n}}
 \end{equation}
-This is done because any element of $\vec{\mu}$ is easily related to its magnitude through the directional cosine relationship shown above. 
-Continuing by substituting in the results found in \autoref{SIVEselection}, we see
-	\begin{equation}
-		\langle \beta_{ijk} \rangle = - 24\sqrt{3} \frac{\hbar \varepsilon_0 \Delta_{gv}}{NF(\omega_4)\rho_{gg}} \frac{\chi^{(3)}_{IJKL}}{\mu}
-	\end{equation}
-\end{subequations}
-Since $\mu^2$ can be extracted by fitting infrared spectra,\cite{RN412} it is clear that different polarization schemes in SIVE spectroscopy give a measurement of $\beta_{ijk}$ values.
-SIVE can therefore provide useful insight into the sensitivity of hyper-Raman spectroscopy to different infrared active vibrations.
 

### 2024-06-15 paper.tex
changes and added papers

@@
 \end{subequations}
-Substituting into \autoref{sivebeta} gives the SIVE-IR-I hyperpolarizability to $\order{Q_n}$ as \begin{equation}\label{SIVEselection}
-		\gamma_{ijkl} =	-\frac{1}{\varepsilon_0} \frac{1}{24 \hbar}  \frac{1}{{\Delta_{gv}}} \ \frac{\partial \beta^{(ijk)}}{\partial Q_n} {\frac{\partial \mu^{(l)}}{\partial Q_n}}  (\mel{g}{Q_n}{v})^2\ \rho_{gg}
+Substituting into \autoref{sivebeta}, and knowing that $\mel{v}{Q_n}{g} = \sqrt{\frac{\hbar}{2m_n\omega_{vg}}}$ under the harmonic approximation,\cite{RN230} where $m_n$ is the mass of the $Q_n$ mode, gives the SIVE-IR-I hyperpolarizability to $\order{Q_n}$ as \begin{equation}\label{SIVEselection}
+		\gamma_{ijkl} =	-\frac{1}{\varepsilon_0} \frac{1}{48 m_n \omega_{vg}}  \frac{1}{{\Delta_{gv}}} \ \frac{\partial \beta^{(ijk)}}{\partial Q_n} {\frac{\partial \mu^{(l)}}{\partial Q_n}}  \rho_{gg}
 \end{equation}
@@
 %there is some fancy way to note that theres no index constraint but i dont remember the language...
-As such, its decomposition into irreducible tensor form is allowed only if the values of $q', q''$ are constrained.
+As such, its decomposition into irreducible tensor form is allowed only if the values of $q_2, q_3$ are constrained.
 By substituting the spherical tensor definitions of $\vec{\mu}$ and $\beta_{ijk}$ into \autoref{sivebeta}, it is clear that only $\Delta J = \pm 1$ transitions are allowed, i.e., SIVE-IR features arise only from P or R branches (assuming the ground state is $\ket{g00}$).
@@
 Lineshape analysis is essential for extracting quantitative information from CMDS spectra.
-Scanning across resonances create dispersive lineshapes, i.e, self-heterodyning, which inform on $\Re{\chi^{(3)}}$ and $\Im{\chi^{(3)}}$.\cite{Levenson1974_1, Levenson1974_2}
-In the method introduced by Levenson and Bloembergen, an internal standard, often chosen to be  
-C$_6$H$_6$ or C$_6$D$_6$, due to the strong Raman activity and measured $\chi^{(3)}$ of its ring breathing mode ($\nu_2$ in Herzberg notation), causes interference. \cite{Levenson1974_2, RN351, RN345}
-This interference measures $\chi^{(3)}$ and does not require measurement of absolute intensities; it instead relies on self-heterodyning of the internal standard signal. 
+Scanning across resonances create dispersive lineshapes, i.e, self-heterodyning, which inform on $\Re(\chi^{(3)})$ and $\Im(\chi^{(3)})$.\cite{Levenson1974_1, Levenson1974_2}
+In the method introduced by Levenson and Bloembergen (Bloembergen Interferometry Experiment), an internal standard interferes with the resonant lineshape.
+The internal standard is often chosen to be C$_6$H$_6$ or C$_6$D$_6$, due to the strong Raman activity and measured $\chi^{(3)}$ of its ring breathing mode ($\nu_2$ in Herzberg notation), causes interference.
+\cite{Levenson1974_2, RN351, RN345}
+The self-heterodyning method measures $\chi^{(3)}$ and does not require measurement of absolute intensities; it instead relies on self-heterodyning of the internal standard signal. 
 Resonant lineshapes are also complicated by amplitude level interference between the sample and its substrate and/or sample cell windows. \cite{RN362, RN418}
@@
 This expression cannot be used as written to extract $\beta_{ijk}$, as $\beta_{ijk}$ is a Hermitian operator, but $\Delta_{gv} \in \mathbb{C}$. 
-However, since the real and imaginary parts of $\chi^{(3)}$ can be extracted from the Bloembergen experiment, we can choose to focus on either its real or imaginary part.
+However, since the real and imaginary parts of $\chi^{(3)}$ can be extracted from the Bloembergen interferometry experiment, we can choose to focus on either its real or imaginary part.
 For simplicity, we investigate $\Im(\chi^{(3)})$, giving, assuming resonance conditions, 
@@
 Neglecting rotational dependence (i.e., assuming only vibrational transitions), $\langle {\mu^2} \rangle = \abs{\mu}^2 = \mu^2$, so that $\langle \beta_{ijk} \mu_l \rangle = \langle \beta_{ijk} \rangle \frac{\mu}{\sqrt{3}}$.
-By introducing the reduced mass coordinate $q_n = \sqrt{\frac{1}{m_n}} Q_n$ and using the expansions of $\beta_{ijk}$ and $\mu_{l}$ found earlier, knowing that $(\mel{v}{q}{g})^2 = \frac{\hbar}{2\omega_{vg}}$ under the harmonic approximation, shows
+By introducing the reduced mass coordinate $q_n = \sqrt{\frac{1}{m_n}} Q_n$ and using the expansions of $\beta_{ijk}$ and $\mu_{l}$ to $\order{Q_n}$ found earlier, we see
 \begin{equation}\label{betasive}
@@
 \end{equation}
+Since $\mu$ values can be readily extracted from FT-IR spectra,\cite{RN412} this shows that SIVE can give quantitative information on the magnitude of $\beta_{ijk}$.
+
+A key result of \autoref{betasive} is that the sign of $\frac{\partial \beta_{ijk}}{\partial q_n}$ and $\frac{\partial \mu_{l}}{\partial q_n}$ can be extracted from SIVE spectra. 
+These ideas can prove useful when assessing the validity of computational methods which report on the sign of $\frac{\partial \beta_{ijk}}{\partial q_n}$.
+Similar ideas were first introduced by Shen to extract the sign of $\frac{\partial \mu_{l}}{\partial q_n}$ from vSFG spectra.\cite{Shen90}
+SIVE and vSFG together provide a unique picture of extracting signs for the microscopic observables that drive nonlinear output.
 
@@
 Without loss of generality, we assume c = 1 for correlated modes and c = -1 for anti-correlated modes.
-To understand the impact of inhomogeneity on spectral output, we convolute an output density matrix element $\rho_{ab}(\xi)$ with a normalized Lorentzian distribution $P(\xi)$ of half width $\sigma$ as \cite{Penner1976, Desiderio1979, Dick83_1, Carlson1990line}
+To understand the impact of inhomogeneity on spectral output, we convolute an output density matrix element $\rho_{ab}(\xi)$ with a normalized Lorentzian distribution $P(\xi)$ of half width at half maximum $\sigma$ as
 \begin{equation}\label{contour}
@@
 \end{equation} 
-While Gaussian distributions are commonly used to describe inhomogeneous broadening,\cite{druet1979line, RN307} Lorentzian distributions have successfully described inhomogeneous broadening in a variety of spectroscopies and yield easily interpreted closed-form solutions.
-\cite{Dick83_1, Carlson1990line}
+While Gaussian distributions are commonly used to describe inhomogeneous broadening,\cite{druet1979line, RN307, Ouellette1982} Lorentzian distributions have successfully described inhomogeneous broadening in a variety of spectroscopies and yield easily interpreted closed-form solutions.
+\cite{Penner1976, Desiderio1979, Dick83_1, Carlson1990line}
 For clarity, we evaluate the linenarrowing characteristics of pathway Ia (\autoref{fig:doubsive}) in detail in Appendix.
@@
 When resonant pulses are significantly longer than the dephasing time of some state, then that state can become populated.
-Excited state population effects are particularly important for understanding the spectroscopy of electronic states using input pulses with relatively long pulsewidths ($\gtrsim$ 1 ps). \cite{RN319}
-First seen in fifth order perturbation theory ($\chi^{(5)}$ processes) in isotropic media, excited state populations can populate other modes, including the ground state and other vibrational/vibronic modes, inducing higher order processes.\cite{Carlson87, RN471}
-These feeding mechanisms can induce line-narrowing properties in spectroscopies that cannot line-narrow in third order perturbation theory.\cite{RN319, Carlson87, RN471, RN410}
-While not important for the discussion here, the implications of excited state populations are important when considering experiments using the methods in \autoref{fig:doubsive} with long pulsewidths.
+A typical electronic dephasing time value is tens of femtoseconds. \cite{RN131}
+Excited state population effects become important for understanding the spectroscopy of electronic states when using input pulses with relatively long pulsewidths ($\gtrsim$ 500 fs).
+\cite{RN319, Yurs2011}
+First seen in fifth order perturbation theory in isotropic media ($\chi^{(5)}$ processes), excited state populations can populate other modes, including the ground state and other vibrational/vibronic modes, inducing higher order processes.\cite{Carlson87, RN471}
+These feeding mechanisms can induce line-narrowing properties in spectroscopies that cannot line-narrow in third order perturbation theory.\cite{Ouellette1982, RN319, Carlson87, RN471, RN410}
+Excited state populations become important when considering experiments using the methods in \autoref{fig:doubsive} with long pulsewidths or strong transition dipoles, as demonstrated on a variety of model systems using coherent Raman spectroscopies.
+\cite{Ouellette1982, RN471, RN338, Yurs2011}
 
@@
 Unlike SR-SIVE, DR-SIVE methods can linenarrow inhomogeneously broadened vibronic modes. 
-SR and DR-SIVE of cyanocobalamin (i.e., vitamin B-12) highlight the impact of hyper-Raman cross sections on SIVE output, and pave the way for future studies of complex phenomena in large molecular systems through two beam four wave mixing methods.
+SR and DR-SIVE of cyanocobalamin (vitamin B$_{12}$) highlight the impact of hyper-Raman cross sections on SIVE output, and pave the way for future studies of complex phenomena in large molecular systems through two beam four wave mixing methods.
 
@@
 
-\section{Appendix A: Evaluation of Pathway I-a Linenarrowing Capability}
+\section{Appendix A: Evaluation of DR-SIVE Pathway I-a Linenarrowing Capability}
 \begin{widetext}
@@
 For notational convenience, we map $\ket{g,0} \rightarrow \ket{g}$, $\ket{g,v} \rightarrow \ket{a}$ and $\ket{e,v'} \rightarrow \ket{b}$.
-Substituting into \autoref{contour}, we see:
+Substituting into \autoref{contour} and taking $P(\xi)$ to be a normalized Lorentzian distribution of half width at half maximum $\sigma$, we see:
 \begin{equation}\label{integraly}

### 2024-06-16 paper.tex
small things

@@
 Singly Vibrationally Enhanced (SIVE) spectroscopy, a type of nonlinear hyper-Raman spectroscopy, is an underdeveloped four wave mixing technique which shows promise as a method to disentangle ultrafast vibrational dynamics in isotropic systems without need for anharmonicities.
+%alternate name is hyper-(S/D)FG... which is more interesting and descriptive than SIVE imo. lmk your thoughts
 We derive selection rules and coherent interference effects in singly resonant SIVE (SR-SIVE).
@@
 SIVE was documented long ago to have characteristics similar to spontaneous hyper-Raman scattering spectroscopy. \cite{RN352}
-Hyper-Raman scattering, first theorized by Decius \textit{et al.} and experimentally observed by Terhune \textit{et al.}, is the two photon analogue to Raman scattering. \cite{Cyvin1965, Terhune1965}
-Compared to Raman spectroscopy, Hyper-Raman scattering cross sections are often small, making it a difficult technique to successfully implement.\cite{RN515, Kelley2010} 
+Hyper-Raman scattering is the two photon analogue to Raman scattering. \cite{Cyvin1965, Terhune1965}
+Compared to Raman spectroscopy, hyper-Raman scattering cross sections are often small, making it a difficult technique to successfully implement.\cite{RN515, Kelley2010} 
 The different selection rules of hyper-Raman scattering, however, make it a unique alternative to Raman scattering to understand vibrational spectra and vibronic coupling in molecular systems.
@@
 DR-SIVE is thus the four wave mixing analogue of doubly resonant infrared-visible sum frequency generation. \cite{Shen94}
-Based upon these selection rules, we investigate SR-SIVE and DR-SIVE spectroscopy of cyanocobalamin and find good agreement between the theoretical and experimental results.
+Based upon these selection rules, we investigate SR-SIVE and DR-SIVE spectroscopy of cyanocobalamin, highlighting the applicability of these methods to non-model systems.
 
@@
 Movable retroreflectors (Thorlabs) controlled by 50 mm DC actuators (PMC) are used to measure coherence dynamics.
-The beams are focused into the sample using a BOXCARS geometry.\cite{RN308, Kaufman2024}
+The beams are focused into the sample in a BOXCARS geometry.\cite{RN308, Kaufman2024}
 To enforce frequency dependent temporal pulse overlap, the maximum points of a third order cross correlation between $\omega_1$ and $\omega_3$ measured in CaF$_2$ were used to generate frequency dependent zero delay values.
@@
 where $E_0$ is the pulse amplitude and $\vec{k}$ is a wavevector.
-
+%maybe talk about maxwell wave eqn for e fields ?
 Expressions for $\gamma_{ijkl}$ can be found by solving Liouville-von Neumann equation for an output density matrix element $\rho_{ij}$.
@@
 \end{equation} %check if bar or double bar
-where $H_0$ is the system (time independent) Hamiltonian, $\vec{\mu}$ is the electric transition dipole moment, $\vec{E}(\vec{x},t)$ is a time dependent electric field, and $\bar{\Gamma}$ is the pure dephasing rate vector.
+where $H_0$ is the system (time independent) Hamiltonian, $\vec{\mu}$ is the electric transition dipole moment, $\vec{E}(\vec{x},t)$ is a time dependent electric field, and the elements of $\bar{\Gamma}$, $\Gamma_{ij}$, are dephasing rates.
 In the rotating frame, $\tilde{\rho}_{ij} = \rho_{ij} e^{-i \omega_{ij}t}$.
-By solving \autoref{matrix} under steady state ($\dot{\bar{\rho}}(t) = 0$) in the rotating frame, expressions for $\gamma_{ijkl}$ can be readily obtained by multiplying the output dipole moment, $\mu_i$ by the final density matrix element $\rho_{ij}$.
+By solving \autoref{matrix} under steady state ($\dot{\bar{\rho}}(t) = 0$) in the rotating frame, expressions for $\gamma_{ijkl}$ can be readily obtained by multiplying the output dipole moment, $\mu_i$ by the final density matrix element $\tilde{\rho}_{ij}$.
 
@@
 Specifically, it has shown that the rank one spherical tensor ($T_{q_1}^{(1)}$, with $q_1 \in \{-1, 0 ,1\}$) fully contributes to $\beta_{ijk}$ but only select $T_{q_2}^{(2)} + T_{q_3}^{(3)}$ terms contribute.
-\cite{Andrews1978, Andrews1990}
+\cite{Andrews1978, Altmann1982, Andrews1990}
 %there is some fancy way to note that theres no index constraint but i dont remember the language...
@@
 In the method introduced by Levenson and Bloembergen (Bloembergen Interferometry Experiment), an internal standard interferes with the resonant lineshape.
-The internal standard is often chosen to be C$_6$H$_6$ or C$_6$D$_6$, due to the strong Raman activity and measured $\chi^{(3)}$ of its ring breathing mode ($\nu_2$ in Herzberg notation), causes interference.
+The internal standard is often chosen to be C$_6$H$_6$ or C$_6$D$_6$, due to the strong Raman activity and measured $\chi^{(3)}$ of its ring breathing mode ($\nu_2$ in Herzberg notation).
 \cite{Levenson1974_2, RN351, RN345}
-The self-heterodyning method measures $\chi^{(3)}$ and does not require measurement of absolute intensities; it instead relies on self-heterodyning of the internal standard signal. 
-Resonant lineshapes are also complicated by amplitude level interference between the sample and its substrate and/or sample cell windows. \cite{RN362, RN418}
+Self-heterodyning of the internal standard signal measures $\chi^{(3)}$ and does not require measurement of absolute intensities. 
+Resonant lineshapes are also complicated by amplitude level interference between the sample and its substrate and/or sample cell windows, which must be accounted for to obtain quantitatively correct $\chi^{(3)}$ values.
+\cite{RN362, RN418}
 
@@
 Previous treatments did not consider using quantitative analysis in SIVE to measure $\beta_{ijk}$ values from SIVE spectra.
-It is thus useful to investigate how a simple treatment of orientational averaging can extract $\beta_{ijk}$ from a $\chi^{(3)}_{IJKL}$ expression.
+It is thus useful to investigate how a simple treatment of orientational averaging can extract $\beta_{ijk}$ from $\chi^{(3)}_{IJKL}$.
 
@@
 \begin{equation}\label{betasive}
-	\langle \frac{\partial \beta_{ijk}}{\partial q_n} \rangle = \varepsilon_0 \frac{48 \sqrt{3} }{NF}  \frac{\Gamma_{gv} \omega_{vg}}{\rho_{gg}} \frac{\Im(\chi^{(3)}_{IJKL})}{\frac{\partial \mu_{l}}{\partial q_n}}
+	\langle \frac{\partial \beta_{ijk}}{\partial q_n} \rangle = \varepsilon_0 \frac{48 \sqrt{3} }{NF}  \frac{\Gamma_{gv} \omega_{vg}}{\rho_{gg}} \frac{\Im(\chi^{(3)}_{IJKL})}{\frac{\partial \mu}{\partial q_n}}
 \end{equation}
-Since $\mu$ values can be readily extracted from FT-IR spectra,\cite{RN412} this shows that SIVE can give quantitative information on the magnitude of $\beta_{ijk}$.
+Since $\abs{\mu}$ values can be readily extracted from FT-IR spectra,\cite{RN412} this shows that SIVE can give quantitative information on the magnitude of $\beta_{ijk}$.
 
 A key result of \autoref{betasive} is that the sign of $\frac{\partial \beta_{ijk}}{\partial q_n}$ and $\frac{\partial \mu_{l}}{\partial q_n}$ can be extracted from SIVE spectra. 
+Since IR and spontaneous hyper-Raman spectroscopy report on $\Im(\chi^{(1)}) \sim \abs{\mu_{l}}^2$ and $\Im(\chi^{(5)}) \sim \abs{\beta_{ijk}}^2$,\cite{RN515} respectively, the absolute signs of $\frac{\partial \mu_{l}}{\partial q_n}$ and $\frac{\partial \beta_{ijk}}{\partial q_n}$ cannot be extracted from IR or hyper-Raman spectroscopy.
 These ideas can prove useful when assessing the validity of computational methods which report on the sign of $\frac{\partial \beta_{ijk}}{\partial q_n}$.
@@
 			&= 2\pi i \frac{\eta \sigma}{\pi} \lim_{\xi \rightarrow i\sigma} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga}(0) - \xi} \frac{1}{\Delta_{ba}(0) - \xi} (\xi - i \sigma)\\
-			&= 2 \eta \sigma i \lim_{\xi \rightarrow i\sigma} \frac{1}{\xi + i\sigma} \frac{1}{\Delta_{ga}(0) - \xi} \frac{1}{\Delta_{ba}(0) - \xi}\\
 			&= 2\eta \sigma i \frac{1}{2i\sigma} \frac{1}{\Delta_{ga}(0) - i\sigma} \frac{1}{\Delta_{ba}(0) - i\sigma}\\
@@
 
-In words, we see the inhomogeneous envelope width $\sigma$ is added to the linewidth of each resonance (e.g., $\Gamma_{ag} \rightarrow \Gamma_{ag} + \sigma$).
+In words, we see the inhomogeneous envelope width $\sigma$ is added to the linewidth of each resonance (e.g., $\Gamma_{ba} \rightarrow \Gamma_{ba} + \sigma$).
 Therefore, pathway I-a cannot linenarrow anti-correlated modes. 

### 2024-06-16 paper.tex

@@
-\documentclass[aip, jcp, draft, onecolumn]{revtex4-2}
+\documentclass[aip, jcp, reprint, twocolumn]{revtex4-2}
 
@@
 \cite{RN307, RN281, RN342, Cho2008, RN335, Ogilvie2019, RN325}
-CMDS has resolved intramolecular vibrational, vibronic, excitonic, and electronic coupling in numerous systems.
-\cite{Carlson1990, RN345, RN342, RN343, RN324, Czech2015, Gaynor2017, Ogilvie2019, RN325}
+CMDS has resolved anharmonicities and other intramolecular couplings in numerous systems. \cite{RN345, RN342, RN343, RN324, RN329, RN120, Czech2015, Gaynor2017, Ogilvie2019, RN325}
 A particular class of CMDS methods, coherent Raman based four wave mixing spectroscopies, can provide explicit probes of vibrational and excitonic coupling in a variety of systems.
@@
 As a result, investigations of SIVE stagnated; to date, there are less than a dozen studies which report on SR-SIVE.
-\cite{RN350, RN416, RN351, RN352, RN353, Chen1998, RN362, RN418, McDonnell2024, Bonn2024}
+\cite{RN350, RN416, RN351, RN352, RN353, Chen1998, RN362, RN418, Bonn2024, McDonnell2024}
 Recent reports highlight non-negligible SIVE interference in DOVE experiments as well as the suitability of SIVE pathways to interpret ultrafast relaxation dynamics in isotropic systems.
@@
 Some years ago, Cho proposed a parametric, doubly resonant infrared/visible pathway to probe vibronic coupling in isotropic systems. \cite{Cho2001}
-In this method, a single infrared pulse is resonant with a vibrational mode, and a two photon absorption event from a near infrared (NIR) or visible pulse is used to generate the four wave mixing signal.
+In this method, a single infrared pulse is resonant with a vibrational mode, and a two photon absorption event from a near infrared (NIR) or visible pulse resonant with an electronic or vibronic state is used to generate the four wave mixing signal.
 These pathways are referred to herein as DR-SIVE.
@@
 The resultant output was used to pump four independent OPAs, two of which are relevant for this study.
-OPA1 (TOPAS-800, Light Conversion), referred to as $\omega_1$, was tuned for difference frequency generation (DFG) with an external stage (NDFG \"DF2\", Light Conversion).
+OPA1 (TOPAS-800, Light Conversion), referred to as $\omega_1$, was tuned for difference frequency generation (DFG) with an external stage (NDFG ``DF2'', Light Conversion).
 OPA2 (OPA-800C, Spectra Physics), referred to as $\omega_2$, was tuned in its signal arrangement. 
@@
 The OPAs were independently tuned through the \texttt{Attune} package, controlled by the \texttt{yaqc} and \texttt{Bluesky} packages. \cite{RN414, RN386, SkyeOPA, KyleOPA}
-The power spectra and tuning results are found in Figure X.%todo: actually graph these
+The power spectra and tuning results are found in Figure X. %todo: actually graph these
 Movable retroreflectors (Thorlabs) controlled by 50 mm DC actuators (PMC) are used to measure coherence dynamics.
@@
 Such an intensity is easily obtained using modern ultrafast sources.
-As such,
+In this limit,
 \begin{equation}
@@
 \end{equation}
-Since the intensity ratio scales as $\abs{P_{ratio}}^2$, we see that the SIVE output is roughly 100 times stronger than vibrational SFG.
+Since the intensity ratio scales as $\abs{P_{ratio}}^2$, we see that the SIVE output is somewhat stronger than vibrational SFG, assuming only interfacial contributions in vSFG.
 It is important to note that this derivation ignored absorption and orientational averaging effects, which can significantly reduce output from either process.
@@
 By writing $\vec{\mu} = T_{q_1}^{(1)}$ and $\beta_{ijk} = T_{q_1}^{(1)} + T_{q_2}^{(2)} + T_{q_3}^{(3)}$, where $T^{(k)}_{q}$ is a rank $k$ spherical tensor, the matrix elements in \autoref{sivebeta} can be evaluated through the Wigner-Eckart theorem.
-It is important to note that $\beta_{ijk}$ does not have complete tensor index symmetry.\cite{Andrews1978}
-Specifically, it has shown that the rank one spherical tensor ($T_{q_1}^{(1)}$, with $q_1 \in \{-1, 0 ,1\}$) fully contributes to $\beta_{ijk}$ but only select $T_{q_2}^{(2)} + T_{q_3}^{(3)}$ terms contribute.
-\cite{Andrews1978, Altmann1982, Andrews1990}
-%there is some fancy way to note that theres no index constraint but i dont remember the language...
+It is important to note that $\beta_{ijk}$ does not have complete index symmetry.\cite{Andrews1978}
+Specifically, it has shown that $T_{q_1}^{(1)}$ fully contributes to $\beta_{ijk}$ but only select $T_{q_2}^{(2)}$ and  $T_{q_3}^{(3)}$ terms contribute. \cite{Andrews1978, Altmann1982, Andrews1990}
+%there is some fancy way to note that theres an index constraint but i dont remember the language... i think is fine
 As such, its decomposition into irreducible tensor form is allowed only if the values of $q_2, q_3$ are constrained.
@@
 The recorded $\chi^{(n)}$ values provide insight into how microscopic quantities ($\vec{\mu}, \alpha_{ij}, \beta_{ijk}$) impact nonlinear output.
-To our knowledge, only vibraitonal SFG and 2D-IR spectroscopy has taken advantage of orientationally averaged $\chi^{(n)}$ values to extract transition moments. \cite{Shen90, Moilanen2009, RN245}
+To our knowledge, only vibrational SFG and 2D-IR spectroscopy has taken advantage of orientationally averaged $\chi^{(n)}$ values to extract transition moments. \cite{Shen90, Moilanen2009, RN245}
 Previous treatments did not consider using quantitative analysis in SIVE to measure $\beta_{ijk}$ values from SIVE spectra.
@@
 Similar ideas were first introduced by Shen to extract the sign of $\frac{\partial \mu_{l}}{\partial q_n}$ from vSFG spectra.\cite{Shen90}
-SIVE and vSFG together provide a unique picture of extracting signs for the microscopic observables that drive nonlinear output.
+SIVE and vSFG together provide a unique picture of extracting signs for the microscopic quantities ($\mu, \alpha, \beta$) that drive nonlinear output.
 
@@
 The driven limit is useful as despite the sum over states approach, it avoids implications of ultrafast dephasing of the vibronic state.\cite{Cho2001} 
-For consistency with previous reports, we use $\vec{R}$ to denote electric transition dipole moments (not to be confused with the response function; $\mu$ is used for transitions between states on the ground electronic state.).
+For consistency with previous reports, we use $\vec{R}$ to denote electric transition dipole moments (not to be confused with the response function; $\vec{\mu}$ is used for transitions between states on the ground electronic state.).
 \cite{Ziegler1974}
@@
 An unavoidable consequence in electronic spectroscopy is broadened lineshapes due to the inhomogeneity of electronic transitions (e.g., vibronic sidebands, molecular collisions). 
-Four wave mixing methods can line-narrow transitions and remove some impact of inhomogeneous broadening.\cite{Carlson1990line}
+Four wave mixing methods can line-narrow transitions, i.e., resolve inhomogeneous broadening.\cite{Carlson1990line}
 The line-narrowing properties of DR-SIVE are investigated so that the pathways which line-narrow correlated or anti-correlated modes (\textit{vide infra}) can be identified.
@@
 \end{equation} 
-While Gaussian distributions are commonly used to describe inhomogeneous broadening,\cite{druet1979line, RN307, Ouellette1982} Lorentzian distributions have successfully described inhomogeneous broadening in a variety of spectroscopies and yield easily interpreted closed-form solutions.
+While Gaussian distributions are used to describe inhomogeneous broadening,\cite{druet1979line, RN307, Ouellette1982} Lorentzian distributions have satisfactorily described inhomogeneous broadening in a variety of nonlinear spectroscopies and yield easily interpreted closed-form solutions to \autoref{contour}.
 \cite{Penner1976, Desiderio1979, Dick83_1, Carlson1990line}
@@
 Although \autoref{T:correlated} identifies that only Pathway I-a can line-narrow correlated modes, these results are only valid in limits where the input pulses only weakly populate excited states.
-When resonant pulses are significantly longer than the dephasing time of some state, then that state can become populated.
-A typical electronic dephasing time value is tens of femtoseconds. \cite{RN131}
+When resonant pulses are significantly longer than the dephasing rate of some state, then that state can become populated.
+A typical electronic dephasing rate is tens of femtoseconds. \cite{RN131}
 Excited state population effects become important for understanding the spectroscopy of electronic states when using input pulses with relatively long pulsewidths ($\gtrsim$ 500 fs).
@@
 		Here, $\omega_2 = 8000$ cm$^{-1}$.
-		$\omega_1$ is stepped in 10 $^{-1}$ intervals.
+		$\omega_1$ is stepped in 10 cm$^{-1}$ intervals.
 		The spectra are smoothed and power-normalized for frequency dependent power fluctuations during the scan.
@@
 		The red trace is an FT-IR spectrum of CNCbl, sourced from NIST. 
-		All spectra are normalized to their most intense feature on $\omega \in [1300, 1700]$ cm$^{-1}$.}
+		The spectra are normalized to their most intense feature on $\omega \in [1300, 1700]$ cm$^{-1}$.}
 	\label{fig:cobsive}
@@
 \subsubsection{Correlated Modes}
-For correlated modes, the poles are situated in the complex plane as shown in \autoref{fig:contours}.
+For correlated modes, the poles are situated in the complex plane as shown in \autoref{fig:contours}b.
 It is clear that no matter which contour is chosen, there is a contribution to the final integral from either $\Delta_{ba}(0)$ or $\Delta_{ga}(0)$. 

### 2024-06-17 paper.tex
Update paper.tex
data is garbage so deleted
rovib and interference trivial so deleted

added more on sfg to explain why i want to compare (it is to motivate doing the spectroscopy)

@@
 %alternate name is hyper-(S/D)FG... which is more interesting and descriptive than SIVE imo. lmk your thoughts
-We derive selection rules and coherent interference effects in singly resonant SIVE (SR-SIVE).
-The theory of SR-SIVE is extended to account for vibronic coupling induced by two-photon absorption, i.e. doubly resonant SIVE (DR-SIVE), akin to a resonant hyper-Raman process. 
+We derive selection rules for singly resonant SIVE (SR-SIVE) and demonstrate that SR-SIVE response extracts hyper-Raman polarizabilities ($\beta$).
+The SIVE output is shown to be slightly stronger than vibrational sum frequency generation (vSFG), heavily driven by the number density probed by each process. 
+The theory of SIVE is extended to account for vibronic coupling induced by two-photon absorption, i.e. doubly resonant SIVE (DR-SIVE), akin to resonant hyper-Raman spectroscopy. 
 DR-SIVE is shown to be a type of resonance IR spectroscopy and is likely able to resolve vibronic coupling.
-The linenarrowing abilities of DR-SIVE are discussed.
-We showcase the difference in selection rules of SR-SIVE and DR-SIVE through a study of cyanocobalamin, highlighting the sensitivity of these measurements on non-resonant and resonant hyper-Raman hyperpolarizabilities, respectively.
 \end{abstract}
@@
 DR-SIVE is thus the four wave mixing analogue of doubly resonant infrared-visible sum frequency generation. \cite{Shen94}
-Based upon these selection rules, we investigate SR-SIVE and DR-SIVE spectroscopy of cyanocobalamin, highlighting the applicability of these methods to non-model systems.
 
-\section{Experimental Methods}
-The ultrafast laser system has been described in detail elsewhere. \cite{RN278, Kaufman2024}
-Briefly, an 80 MHz Ti-Sapphire ultrafast oscillator  (Spectra-Physics Tsunami) created 35 fs seed pulses, amplified by a 1 kHz regnerative amplifier (Spectra-Physics Spitfire Ace) to approximately 0.5 W.
-A mask in the regenerative amplifier stretched the input pulses to roughly 1 ps.
-The resultant output was used to pump four independent OPAs, two of which are relevant for this study.
-OPA1 (TOPAS-800, Light Conversion), referred to as $\omega_1$, was tuned for difference frequency generation (DFG) with an external stage (NDFG ``DF2'', Light Conversion).
-OPA2 (OPA-800C, Spectra Physics), referred to as $\omega_2$, was tuned in its signal arrangement. 
-Grating and crystal positions in OPA1 was externally controlled using \texttt{WinTOPAS} (Light Conversion).
-Grating and BBO crystal positions in OPA2 were computer controlled through communication with 50 mm DC actuators (PMC). %todo: who tf makes PMC motors?
-The OPAs were independently tuned through the \texttt{Attune} package, controlled by the \texttt{yaqc} and \texttt{Bluesky} packages. \cite{RN414, RN386, SkyeOPA, KyleOPA}
-The power spectra and tuning results are found in Figure X. %todo: actually graph these
-Movable retroreflectors (Thorlabs) controlled by 50 mm DC actuators (PMC) are used to measure coherence dynamics.
-The beams are focused into the sample in a BOXCARS geometry.\cite{RN308, Kaufman2024}
-To enforce frequency dependent temporal pulse overlap, the maximum points of a third order cross correlation between $\omega_1$ and $\omega_3$ measured in CaF$_2$ were used to generate frequency dependent zero delay values.
-The nonlinear output was isolated through chopping schemes and a set of spatial apertures, directed into a monochromator (Horiba Micro-HR) and homodyne detected through a photomultiplier tube (Hamamatsu H7422-20), recorded and converted to digital output using a data acquisition unit (National Instruments).
-\textit{in-situ} power corrections are performed by dividing the recorded spectra by OPA output measured by home-built pyroelectric detectors.
-All spectra are reported on the intensity scale. %@dan if we should change to amp lmk
-
-The cyanocobalamin (CNCbl) [DOT Scientific inc., CAS no. 68-19-9] samples were prepared as drop casted thin films.
-CNCbl was dissolved in methanol (MeOH) [Fisher Scientific, HPLC Grade, CAS no. 67-56-1] until a concentrated solution was formed (concentration $\sim$ 10 mg CNCbl/ mL MeOH). 
-All chemicals were used as obtained without further purification.
-The solution was deposited on a microscope coverslip and allowed to dry in a dessicator until a thin layer was formed.
-
-\section{Properties of SIVE Spectroscopy}
+\section{Results and Discussion}
 Singly resonant SIVE (SR-SIVE) spectroscopy has potential to provide deeper insight into single quantum decoherence times and molecular orientation in condensed systems.
@@
 
-Note that we choose the convention where an arbitrary electric field, assuming a plane wave, is written in Fourier components as 
-\begin{equation}
-	\vec{E}(\omega) = \frac{1}{2} \vec{E}_0 \exp(i(\vec{k}\cdot\vec{x} - \omega t)) + c.c.
-\end{equation}
-where $E_0$ is the pulse amplitude and $\vec{k}$ is a wavevector.
-%maybe talk about maxwell wave eqn for e fields ?
-Expressions for $\gamma_{ijkl}$ can be found by solving Liouville-von Neumann equation for an output density matrix element $\rho_{ij}$.
-Generally, under the electric dipole approximation, the density matrix, $\bar{\rho}(t)$, is propagated through the Liouville-von Neumann equation as \cite{RN455}
-\begin{equation}\label{matrix}
-	\dot{\bar{\rho}}(t) = \frac{1}{i \hbar}[H_0 - \vec{\mu}\cdot \sum_j E_j(\vec{x},t), \bar{\rho}(t)] + \bar{\Gamma} \bar{\rho}(t)
-\end{equation} %check if bar or double bar
-where $H_0$ is the system (time independent) Hamiltonian, $\vec{\mu}$ is the electric transition dipole moment, $\vec{E}(\vec{x},t)$ is a time dependent electric field, and the elements of $\bar{\Gamma}$, $\Gamma_{ij}$, are dephasing rates.
-In the rotating frame, $\tilde{\rho}_{ij} = \rho_{ij} e^{-i \omega_{ij}t}$.
-By solving \autoref{matrix} under steady state ($\dot{\bar{\rho}}(t) = 0$) in the rotating frame, expressions for $\gamma_{ijkl}$ can be readily obtained by multiplying the output dipole moment, $\mu_i$ by the final density matrix element $\tilde{\rho}_{ij}$.
-
 \subsection{Vibrational SR-SIVE Selection Rules}
@@
 \end{equation}
-where: $\mu^{j}_{ab}$ is the $j^{th}$ element of $\mel{a}{\vec{\mu}}{b}$, $\Delta_{kl} = \omega_{kl} - \omega_{j} - i\Gamma_{kl}$, $\omega_j$ is the frequency of the j$^{th}$ input field, $\Gamma_{kl}$ is the dephasing of $\rho_{kl}$ and $\rho_{gg}$ is the ground state density.
+where: $\mu^{j}_{ab}$ is the $j^{th}$ element of $\mel{a}{\vec{\mu}}{b}$, $\Delta_{kl} = \omega_{kl} - \omega_{j} - i\Gamma_{kl}$, $\omega_j$ is the frequency of the j$^{th}$ input field, $\Gamma_{kl}$ is the dephasing of $\rho_{kl}$ and $\rho_{gg}$ is the ground state population.
 For simplicity, we consider the results for the process diagrammed in \autoref{fig:sivewmel}a, but by multiplying by (-1) and taking a complex conjugate, which arise from the bra-side transition in \autoref{fig:sivewmel}a, results for the \autoref{fig:sivewmel}b  process are obtained.
@@
 
-To motivate the application of SIVE spectroscopy, we perform an approximate calculation to compare the output of parametric SIVE-IR (\autoref{fig:sivewmel}b) to that of vibrational SFG (vSFG) spectroscopy.
+\subsection{Comparison to Sum Frequency Generation}
+Since the hyper-Raman process is effectively a two-photon process, a setup using only two lasers can perform the SIVE experiment by investigating $\pm \vec{k}_1 + 2\vec{k}_2$ processes.
+The other commonly used two laser CMDS method is sum frequency generation, a $\chi^{(2)}$ technique, whose phasematching is dictated by $\vec{k}_1 + \vec{k}_2$.
+The SFG output scales as $\chi^{(2)}_{IJK} \sim \langle \alpha_{ij} \mu_k \rangle$, where $\alpha_{ij}$ is the Raman polarizability tensor.
+Since SFG is dependent upon transitions that transform like both rank-one and rank-two tensors, this enforces a microscopic constraint that SFG cannot yield output for centrosymmetric species under the electric dipole moment.
+This follows from simple parity arguments, where inversion centers demand states possess distinct parity selection rules. \cite{RN230}
+Macroscopically, inversion symmetry in the output polarization eliminates output from centrosymmetric species under the electric dipole approximation.
+As a result, the output of SFG is significantly reduced relative to most third order spectroscopies because the output only depends on surface species.
+However, since SIVE spectroscopy is dependent upon a hyper-Raman transition, it is useful to compare the relative output of the two processes to identify how SIVE output compares to SFG.
+
+To motivate the application of SIVE spectroscopy, we perform a calculation to compare the output of parametric SIVE-IR (\autoref{fig:sivewmel}b) to that of vibrational SFG (vSFG) spectroscopy.
 Absorption effects are neglected for simplicity.
@@
 	\end{subequations}
-where $\alpha_{ij}$ is the Raman polarizability, N$_{bulk}$ is the bulk number density, and N$_{surf}$ is the surface number density (10$^{19}$ m$^{-2}$).\cite{RN133, RN503}	
+where N$_{bulk}$ is the bulk number density, and N$_{surf}$ is the surface number density (10$^{19}$ m$^{-2}$).\cite{RN133, RN503}	
 For liquids with molar masses less than $\sim$100 g mol$^{-1}$ and densities roughly equal to that of H$_2$O$_{(l)}$ at room temperature, N$_{bulk} \sim$ 10$^{28}$ m$^{-3}$.
@@
 
-\subsection{Rovibrational SR-SIVE Selection Rules} %this can probably be deleted but wanted to add just in case...
-Recent developments in nonlinear spectroscopy have demonstrated the feasibility of multidimensional infrared spectroscopy of gaseous and quasi-free species.
-\cite{Ziegler2018, Gronborg2022, RN325, Chen2024}
-DOVE and 2D-IR have been used to isolate coupling between fundamentals, overtones and combination bands of gaseous species in several molecular systems. 
-Since resonance hyper-Raman scattering spectroscopy was developed as a gas phase spectroscopy,\cite{RN515} we briefly investigate the properties of rovibrational SR-SIVE.
-In the discussion that follows, to avoid integration over velocity dependent distributions, we assume the experiment is performed at 0 K.
-The velocity dependence of output density matrix elements does not manipulate quantum mechanical selection rules. \cite{Bracamonte2003}
-
-The rovibrational selection rules are generated through calculating \autoref{sivebeta} in a $\ket{vJM} \equiv \ket{v} \otimes {\ket{JM}}$ basis, where $\{\ket{v}\}$ is a basis of vibrational states and $\{\ket{JM}\}$ is a basis of rotational states ($J$ is the total angular momentum and $M$ is its projection onto the space fixed quantization axis).
-By writing $\vec{\mu} = T_{q_1}^{(1)}$ and $\beta_{ijk} = T_{q_1}^{(1)} + T_{q_2}^{(2)} + T_{q_3}^{(3)}$, where $T^{(k)}_{q}$ is a rank $k$ spherical tensor, the matrix elements in \autoref{sivebeta} can be evaluated through the Wigner-Eckart theorem.
-It is important to note that $\beta_{ijk}$ does not have complete index symmetry.\cite{Andrews1978}
-Specifically, it has shown that $T_{q_1}^{(1)}$ fully contributes to $\beta_{ijk}$ but only select $T_{q_2}^{(2)}$ and  $T_{q_3}^{(3)}$ terms contribute. \cite{Andrews1978, Altmann1982, Andrews1990}
-%there is some fancy way to note that theres an index constraint but i dont remember the language... i think is fine
-As such, its decomposition into irreducible tensor form is allowed only if the values of $q_2, q_3$ are constrained.
-By substituting the spherical tensor definitions of $\vec{\mu}$ and $\beta_{ijk}$ into \autoref{sivebeta}, it is clear that only $\Delta J = \pm 1$ transitions are allowed, i.e., SIVE-IR features arise only from P or R branches (assuming the ground state is $\ket{g00}$).
-This is expected since $\vec{\mu}$ transitions demand $\Delta J = \pm 1$.
-As a result, consistent with vibrational SR-SIVE, rovibrational SR-SIVE follows the same rules as common infrared rovibrational spectroscopy.
-
 \subsection{Quantitative SR-SIVE}
-With the selection rules of SR-SIVE understood for vibrational and rovibrational spectroscopy, it becomes possible to extract quantitative information from SIVE spectra to compare to incoherent methods and other CMDS methods.
+With the selection rules of SR-SIVE understood for vibrational spectroscopy, it becomes possible to extract quantitative information from SIVE spectra to compare to incoherent methods and other CMDS methods.
 Lineshape analysis is essential for extracting quantitative information from CMDS spectra.
@@
 SIVE and vSFG together provide a unique picture of extracting signs for the microscopic quantities ($\mu, \alpha, \beta$) that drive nonlinear output.
-
-\subsection{Coherent Interference in SR-SIVE}
-It is well known that nonlinear wave mixing processes which share the same time ordering and output frequency will interfere. \cite{RN135, Bonn2024}
-Understanding interfering pathways is useful because they can, in some cases, eliminate output. \cite{RN342, RN135}
-The WMEL diagrams presented in \autoref{fig:sivewmel} outline resonant SIVE processes when the infrared pulse $(\omega_1)$ is resonant with a vibrational mode. 
-However, if $\omega_2$ becomes vibrationally resonant and $\omega_1$ is non-resonant, then other SIVE pathways appear.\cite{McDonnell2024} 
-While the methods in \autoref{fig:sivewmel2} possess identical selection rules to \autoref{fig:sivewmel}, the WMEL diagrams presented in \autoref{fig:sivewmel2} may significantly interfere with DOVE-IR and DOVE-Raman spectra.
-The time ordering in DOVE-IR and DOVE-Raman spectra is used to interpret anharmonicities, as DOVE-IR and DOVE-Raman destructively interfere when outputs are at the same frequency. \cite{RN135, RN324}
-It is therefore important to understand how the corresponding SIVE pathways interfere.
-To this end, we investigate how the SIVE-IR-II and SIVE-Raman pathways (\autoref{fig:sivewmel2}a, b, respectively) interfere under the rotating wave approximation.
-
-\begin{figure}[!htbp]
-	\centering
-	\includegraphics[width=3.375in]{wmel2.png}
-	\caption{Wave Mixing Energy Level (WMEL) diagrams of interfering SR-SIVE pathways in the  $\vec{k}_4 = -\vec{k}_1 + \vec{k}_2 + \vec{k}_3$ phasematching geometry. 
-	(a) is similar to the process diagrammed in \autoref{fig:sivewmel}, whereas (b) is similar to a coherent anti-Stokes Raman (CARS)-type process.}
-	\label{fig:sivewmel2}
-\end{figure}
-\begin{widetext}
-We employ the response function formalism of Mukamel for this analysis. \cite{RN287}
-The third order response functions, $R^{(3)}$, for SR-SIVE-IR-II ($R^{(3)}_{S_{II}}$) and SR-SIVE-Raman ($R^{(3)}_{R}$) (\autoref{fig:sivewmel2}a, b), suppressing tensor indices, are 
-\begin{subequations}
-	\begin{equation} \label{mixing:a}
-		R^{(3)}_{S_{II}} (t_2) = -\frac{i}{\hbar} [\beta(t_2), \mu(0)] \exp(-i\Delta_{v''g}t_2) \theta(t_2)
-	\end{equation}
-	\begin{equation}\label{mixing:b}
-		\begin{split}
-			R^{(3)}_{R} (t_2) & = \frac{i}{\hbar} [\beta(t_2), \mu(0)] \exp(-i\Delta_{v''g}t_2) \theta(t_2) = - R^{(3)}_{S_{II}} (t_2)\\
-		\end{split}
-	\end{equation}
-\end{subequations}
-By assuming that the fields which stimulate hyper-Raman scattering, $\vec{E}_1, \vec{E}_3$, interact simultaneously at some time $\tau$ after $\vec{E}_2$ interacts with the sample, the total output polarization, $\vec{P}^{(3)}(t)$, is written as \cite{Cho2001}
-	\begin{equation}\label{polarization_SRSIVE_a}
-		\begin{split}
-			\vec{P}^{(3)}(t) &= \vec{P}_{S_{II}}(t) + \vec{P}_{R}(t)\\
-			&= \int_0^\infty \mathrm{d}t_2 (R^{(3)}_{S_{II}} (t_2) + R^{(3)}_{R} (t_2))\vdots \vec{E}_3(t) \vec{E}_1(t) \vec{E}_2(t-t_2 + \tau)\\
-			&= \int_0^\infty \mathrm{d}t_2 (R^{(3)}_{S_{II}} (t_2) - R^{(3)}_{S_{II}} (t_2))\vdots \vec{E}_3(t) \vec{E}_1(t) \vec{E}_2(t-t_2 + \tau) \\
-			&= 0
-		\end{split}
-	\end{equation}
-It is clear the total output polarization for SR-SIVE-IR-II and SR-SIVE-Raman vanishes, or, SR-SIVE-IR-II and SR-SIVE-Raman perfectly destructively interfere.
-\end{widetext}
-The absence of SR-SIVE-IR-II pathways in ultrafast DOVE work is rationalized by this calculation. \cite{RN367, McDonnell2024}
-In the case of the time ordered SR-SIVE-IR-I pathway, there are no opportunities for interference as all other pathways are nonresonant with the first interaction. 
-A possible mechanism for interfering output in the SR-SIVE-I pathway are cascaded second order processes (SFG, DFG). \cite{RN243, RN300}
-In isotropic media, SFG and DFG vanish under the electric dipole approximation,\cite{Zhu87} so cascades are unlikely to inhibit output in centrosymmetric media.
-In media where SFG and DFG are allowed, e.g. surfaces or noncentrosymmetric media, second order cascades may become important. 
-Generally, for nonlinear spectroscopies which share the same phasematching conditions as SR-SIVE (e.g., DOVE), it is useful to note that SR-SIVE-IR-I is not canceled, whereas SR-SIVE-IR-II and SR-SIVE-Raman permanently cancel.
 
@@
 Conversely, the resonance-IR method demonstrated by Boyle et al. only requires one photon transitions between $|g)$ and $|e)$.
-Systems which provide strict parity induced selection rules (e.g., benzene) will be useful for assessing the validity of these selection rules and comparing the method described here and that of Boyle et al.
+Systems which provide strict parity selection rules (e.g., benzene) will be useful for assessing the validity of these selection rules and comparing the method described here and that of Boyle et al.
 \cite{RN491}
@@
 
-\section{SIVE of cyanocobalamin}
-
-\begin{figure*}[!htbp]
-	\centering
-	\includegraphics[width=6.66in]{cob.png}
-	\caption{
-		(a,c) Singly Resonant SIVE (SR-SIVE) and (b,d) Doubly Resonant SIVE (DR-SIVE) response of CNCbl using the $-\vec{k}_1 + 2\vec{k}_2$ and $\vec{k}_1 + 2\vec{k}_2$ phasematching geometries, respectively.
-		Here, $\omega_2 = 8000$ cm$^{-1}$.
-		$\omega_1$ is stepped in 10 cm$^{-1}$ intervals.
-		The spectra are smoothed and power-normalized for frequency dependent power fluctuations during the scan.
-		Gray pixels indicate spectral noise.
-		The blue trace in (a), (b) corresponds to the spectrum at $\tau_{12}$ = 0 in (c,d), respectively.
-		The red trace is an FT-IR spectrum of CNCbl, sourced from NIST. 
-		The spectra are normalized to their most intense feature on $\omega \in [1300, 1700]$ cm$^{-1}$.}
-	\label{fig:cobsive}
-\end{figure*}
-
-To demonstrate the results of Equations \eqref{SIVEselection} and \eqref{drgamma_alpha_0} on realistic, non-model systems, we compare singly and doubly resonant SIVE spectra of cyanocobalamin in the 1300 - 1700 cm$^{-1}$ region to its infrared spectrum (\autoref{fig:cobsive}).
-Cyanocobalamin (CNCbl), or vitamin B$_{12}$ is an important form of cobalamin which forms functional coenzyme derivatives in humans.
-In addition to its important biological properties, CNCbl possesses a complex electronic structure.\cite{Stich2003}
-There has been a variety of spectroscopic studies on cyanocobalamin. 
-Most CNCbl spectroscopic studies are focused on the vibronic structure of its electronic states.\cite{Stich2003, RN276, Salerno2020, Elmendorf2023} 
-Here, we take advantage of the spectroscopic studies of CNCbl to interpret the SR-SIVE and DR-SIVE selection rules.
-To our knowledge, there are no reported resonance or non-resonance hyper-Raman spectra of CNCbl, which inhibits our analysis of the CNCbl SIVE spectra.
-
-The lowest energy electronic transition in cyanocobalamin, the $\alpha$ feature, is reported to be centered at roughly 18050 cm$^{-1}$ with a linewidth of approximately 1000 cm$^{-1}$.
-\cite{Stich2003, RN276}
-For the Placzek approximation to hold for SR-SIVE, the two photon absorption and resultant SIVE output in \autoref{fig:sivewmel} must be below $\sim$17000 cm$^{-1}$.
-A non-parametric pathway (\autoref{fig:sivewmel}a) is therefore used to experimentally collect singly resonant SIVE spectra.
-
-The singly resonant SIVE spectrum (blue trace, \autoref{fig:cobsive}a) has rather limited structure relative to its FT-IR spectrum (red trace, \autoref{fig:cobsive}a).
-The most intense feature is due to a vibrational mode situated at roughly 1585 cm$^{-1}$.
-Based upon its relative spectral width, this feature is likely comprised of multiple vibrational modes in close vicinity, consistent with the FT-IR spectrum and a previous TSF spectrum of CNCbl.
-\cite{RN276}
-This is confirmation that the selection rule presented in \autoref{SIVEselection} is appropriate for this method. 
-The FT-IR spectrum shows the presence of several strong modes in the 1430 - 1560 cm$^{-1}$ which are only weakly resolved in the SIVE spectrum.
-Since the input infrared beam is H polarized, it is possible that the IR pulses only weakly couples into those modes, resulting in limited output.
-
-More interesting are the modes present at $\sim$ 1340 - 1400 and 1510 cm$^{-1}$, strongly observable in the FT-IR spectrum. 
-At zero delay, these modes possess roughly 20\% SR-SIVE intensity as the 1585 cm$^{-1}$ mode.
-Considering the relative infrared strength of these modes, it is likely that the 1585 cm$^{-1}$ mode possesses significant hyper-Raman character, i.e., the rank 2 and 3 components of the $\beta_{ijk}$ operator for the 1585 cm$^{-1}$ mode are important.
-While non-resonant hyper-Raman studies on CNCbl are required to confirm these assignments, it appears that SIVE is a reasonable method for understanding higher order polarizabilities of infrared active modes without the need for complex hyper-Raman experiments.
-
-Unlike the singly resonant SIVE spectrum, the doubly resonant SIVE spectrum shows many vibrational modes in CNCbl, more consistent with the infrared spectrum (\autoref{fig:doubsive}b,d).
-Across the spectrum, the response at zero delay is significantly more intense than that of SR-SIVE,  
-likely due to the resonance hyper-Raman process.
-Resonance hyper-Raman scattering is known to increase spectral output by orders of magnitude relative to non-resonance hyper-Raman scattering in gaseous systems. \cite{RN515}.
-These spectra also indicate that the low lying electronic states of cobalamin are one and two photon allowed transitions, or, the lowest lying electronic state has mixed parity, as it accessible by operators that transform as odd (dipole) and even (two photon absorption) functions.
-
-A recent resonance Raman study on vibronic coupling in CNCbl highlights a mode at 1510 cm$^{-1}$ (labeled as $\nu_1$) which strongly couples to the low lying ($\alpha, \beta$) electronic states.\cite{Elmendorf2023}
-The same study suggests the mode at 1585 cm$^{-1}$ weakly couples to the $\alpha$ and $\beta$ states. 
-Conversely, the DR-SIVE spectrum of CNCbl instead suggests the opposite: the 1585 cm$^{-1}$ mode strongly couples to the $\alpha$ and $\beta$ states, whereas $\nu_1$ only slightly couples (\autoref{fig:cobsive}).
-This is identified through the relative intensity of the zero delay trace at 1510 and 1585 cm$^{-1}$ (\autoref{fig:cobsive}b).
-These differences likely arise due to the relative hyper-Raman cross sections of these modes.
-Since $\nu_1$ possesses a strong infrared cross section (\autoref{fig:cobsive}a), the weakness of $\nu_1$ in the SR-SIVE spectrum suggests it has a rather weak hyper-Raman cross section.
-The weakness of the $\nu_1$ singly resonant hyper-Raman cross section may rationalize its weakness in the DR-SIVE spectrum.
-
-In addition to the 1580 cm$^{-1}$ mode shown to significantly couple to electronic states, the modes at roughly 1340 - 1400 cm$^{-1}$ also show considerable intensity relative to the singly resonant spectrum.
-The resonance Raman study above indeed highlights a variety of modes in the 1340 - 1400 cm$^{-1}$ region responsible for this coupling, consistent with the observed spectral signatures in the zero delay trace of the DR-SIVE spectrum.\cite{Elmendorf2023}
-However, in the CNCbl resonance Raman study, these modes are only weakly coupled to the $\alpha$ and $\beta$ states.
-These modes accordingly have some sort of strong connection to the $\alpha$ and $\beta$ states that can only be resolved through hyper-Raman spectroscopy. 
-To understand these properties further, a resonance hyper-Raman study of CNCbl, and its comparison to a CNCbl resonance Raman study, is required.
-
-Generally, the SR-SIVE and DR-SIVE spectra of CNCbl agree with previously reported spectra.
-Apparent differences in coupling between the vibrational and electronic/vibronic states to those found in resonance Raman studies likely arise from hyper-Raman selection rules. 
-A more thorough analysis of vibronic coupling involving these 1300 - 1500 cm$^{-1}$ modes in CNCbl is currently under investigation and will be published elsewhere. \cite{Kaufman2024_1}
-Generally, these preliminary studies demonstrate the feasibility of SIVE as a coherent analogue of hyper-Raman spectroscopy and motivate further resonant and non-resonant hyper-Raman studies on complex structures for quantitative use of SIVE.\cite{MyersKelley2008}
-
 \section{Conclusions}
@@
 A method for measuring hyper-Raman polarizabilities, $\beta_{ijk}$, through SIVE spectroscopy was identified and discussed.
+Extracting the magnitude and sign of $\beta_{ijk}$ using SIVE methods can help assess the quality of theoretical methods which calculate hyper-Raman spectra. 
 Doubly resonant SIVE (DR-SIVE) processes show promise as a probe of vibronic coupling in molecular samples.
 Unlike SR-SIVE, DR-SIVE methods can linenarrow inhomogeneously broadened vibronic modes.
-SR and DR-SIVE of cyanocobalamin (vitamin B$_{12}$) highlight the impact of hyper-Raman cross sections on SIVE output, and pave the way for future studies of complex phenomena in large molecular systems through two beam four wave mixing methods.
-
-\section{Data Availability Statement}
-The data and workup scripts that support this study are permissively licensed and available for reuse at https://osf.io/2amkq/.
 

### 2024-06-24 paper.tex
many changes
introduced several sections which need to be finished. at the end, i would like this paper to be something like the Minh Cho 1998 6WM hyper Raman paper - just outlining what the spectroscopy can do but in this case, also providing some results.

@@
 The implementation of a nonlinear hyper-Raman spectroscopy, which first appears at third order perturbation theory, can provide a useful analogue to these techniques to understand the spectroscopy and dynamics of isotropic systems.
-Singly Vibrationally Enhanced (SIVE) spectroscopy, a type of nonlinear hyper-Raman spectroscopy, is an underdeveloped four wave mixing technique which shows promise as a method to disentangle ultrafast vibrational dynamics in isotropic systems without need for anharmonicities.
-%alternate name is hyper-(S/D)FG... which is more interesting and descriptive than SIVE imo. lmk your thoughts
-We derive selection rules for singly resonant SIVE (SR-SIVE) and demonstrate that SR-SIVE response extracts hyper-Raman polarizabilities ($\beta$).
-The SIVE output is shown to be slightly stronger than vibrational sum frequency generation (vSFG), heavily driven by the number density probed by each process. 
-The theory of SIVE is extended to account for vibronic coupling induced by two-photon absorption, i.e. doubly resonant SIVE (DR-SIVE), akin to resonant hyper-Raman spectroscopy. 
-DR-SIVE is shown to be a type of resonance IR spectroscopy and is likely able to resolve vibronic coupling.
+Hyper Difference Frequency Generation (hyper-DFG) spectroscopy, a type of nonlinear hyper-Raman spectroscopy also known as singly vibrationally enhanced spectroscopy (SIVE), is an underdeveloped four wave mixing technique which shows promise as a method to disentangle ultrafast vibrational dynamics in isotropic systems without need for anharmonicities.
+We derive selection rules for singly resonant hyper-DFG and demonstrate it provides a simpler method to extract hyper-Raman polarizabilities ($\beta$).
+The hyper-DFG output is shown to be slightly stronger than vibrational difference frequency generation (vSFG), heavily driven by the number density probed by each process. 
+We demonstrate the capabilities of hyper-DFG through probing the spectra and coherence dynamics of the $\nu$(CH) modes in CH$_3$CN.
+The theory of hyper-DFG is extended to account for vibronic coupling induced by two-photon absorption, i.e. doubly resonant hyper-Raman (DR-HDFG), akin to resonant hyper-Raman spectroscopy. 
+DR-HDFG is shown to be a type of resonance IR spectroscopy and is likely able to resolve vibronic coupling.
+
 \end{abstract}
@@
 Singly vibrationally enhanced (SIVE) is a four wave mixing method which, when detuned from  electronic resonances, does not probe intramolecular couplings. 
-Non-parametric, singly resonant SIVE (SR-SIVE) spectroscopy was the first infrared CMDS method to successfully discriminate against non-resonant background.\cite{RN351, RN352}
-In SR-SIVE, an infrared pulse is resonant with a vibrational mode, and two other input pulses are used to induce a scattering process to provide output.
-SIVE was documented long ago to have characteristics similar to spontaneous hyper-Raman scattering spectroscopy. \cite{RN352}
+Non-parametric, hyper difference frequency generation (hyper-DFG) spectroscopy was the first infrared CMDS method to successfully discriminate against non-resonant background.\cite{RN351, RN352}
+Hyper-DFG has also been refered to as singly vibrationally enhanced (SIVE) spectroscopy. \cite{RN351}
+In hyper-DFG, an infrared pulse is resonant with a vibrational mode, and two other input pulses are used to induce a scattering process to provide output.
+Hyper-DFG was documented long ago to have characteristics similar to spontaneous hyper-Raman scattering spectroscopy. \cite{RN352}
 Hyper-Raman scattering is the two photon analogue to Raman scattering. \cite{Cyvin1965, Terhune1965}
@@
 
-While SIVE showed promise as an upconverted infrared spectroscopy method, it was quickly supplemented by a doubly vibrationally resonant method, doubly vibrationally enhanced (DOVE) spectroscopy, to investigate intra- and intermolecular vibrational coupling.
+While hyper-DFG showed promise as an upconverted infrared spectroscopy method, it was quickly supplemented by a doubly vibrationally resonant method, doubly vibrationally enhanced (DOVE) spectroscopy, to investigate intra- and intermolecular vibrational coupling.
 \cite{RN345, RN101, Cho2000}
-As a result, investigations of SIVE stagnated; to date, there are less than a dozen studies which report on SR-SIVE.
+As a result, investigations of hyper-DFG stagnated; to date, there are less than a dozen studies which report on hyper-DFG.
 \cite{RN350, RN416, RN351, RN352, RN353, Chen1998, RN362, RN418, Bonn2024, McDonnell2024}
-Recent reports highlight non-negligible SIVE interference in DOVE experiments as well as the suitability of SIVE pathways to interpret ultrafast relaxation dynamics in isotropic systems.
+Recent reports highlight non-negligible hyper-DFG interference in DOVE experiments as well as the suitability of hyper-DFG pathways to interpret ultrafast relaxation dynamics in isotropic systems.
 \cite{Bonn2024, McDonnell2024}
-These reports motivate deeper analysis on the properties of SIVE spectroscopy.
+These reports motivate deeper analysis on the properties of hyper-DFG spectroscopy.
 
@@
 In this method, a single infrared pulse is resonant with a vibrational mode, and a two photon absorption event from a near infrared (NIR) or visible pulse resonant with an electronic or vibronic state is used to generate the four wave mixing signal.
-These pathways are referred to herein as DR-SIVE.
-Methods analogous to DR-SIVE, where two photon absorption from the infrared pulse and single photon absorption from the visible pulse is used to generate output, i.e., stimulated Raman processes, have been reported.
+These pathways are referred to herein as doubly resonant hyper-DFG (DR-HDFG).
+Methods analogous to DR-HDFG, where two photon absorption from the infrared pulse and single photon absorption from the visible pulse is used to generate output, i.e., stimulated Raman processes, have been reported.
 \cite{RN301, RN120}
@@
 Only recently have methods been developed for seamless tuning and scanning of ultrafast optical parametric amplifiers across swaths of frequency space. \cite{RN162, McDonnell2024, SkyeOPA, KyleOPA}
-Since SR-SIVE demands only a single resonance to be scanned, the experiment can be performed using two input pulses: one tunable, infrared OPA to scan across vibrational resonances, and a two photon absorption from the signal process of a separate OPA, or output from the oscillator which pumps the infrared OPA.
-As such, laboratories experienced in sum frequency generation (SFG) spectroscopy can perform SIVE spectroscopy to understand bulk dynamics and spectroscopy using nearly the same setup.\cite{Shen1987_CPL}
+Since HDFG demands only a single resonance to be scanned, the experiment can be performed using two input pulses: one tunable, infrared OPA to scan across vibrational resonances, and a two photon absorption from the signal process of a separate OPA, or output from the oscillator which pumps the infrared OPA.
+As such, laboratories experienced in sum frequency generation (SFG) spectroscopy can perform HDFG spectroscopy to understand bulk dynamics and spectroscopy using nearly the same setup.\cite{Shen1987_CPL}
 
-Inspired by recent work which demonstrated the presence of SIVE in ultrafast DOVE experiments,\cite{McDonnell2024} we investigate the parameters which result in both SR and DR-SIVE output.
+Inspired by recent work which demonstrated the presence of HDFG in ultrafast DOVE experiments,\cite{McDonnell2024} we investigate the parameters which result in both SR and DR-SIVE output.
 \cite{Cho2000, Bonn2024}
-We develop simple expressions which relate transition dipoles and hyper-Raman polarizabilties and the overall SR-SIVE output, yielding gross selection rules. 
-It is shown that a SIVE active mode must be both IR and hyper-Raman active.
-Since any IR active vibration is also hyper-Raman active, \cite{Andrews1978} we demonstrate that SIVE is a coherent analogue of hyper-Raman scattering spectroscopy for IR active vibrations, i.e., SIVE is an optically upconverted infrared spectroscopy.
+We develop simple expressions which relate transition dipoles and hyper-Raman polarizabilties and the overall HDFG output, yielding gross selection rules. 
+It is shown that a HDFG active mode must be both IR and hyper-Raman active.
+Since any IR active vibration is also hyper-Raman active, \cite{Andrews1978} we demonstrate that HDFG is a coherent analogue of hyper-Raman scattering spectroscopy for IR active vibrations, i.e., HDFG is an optically upconverted infrared spectroscopy.
 This is akin to sum and difference frequency generation (SFG, DFG) being coherent Raman analogues for IR active vibrations. \cite{Shen90}
 
-We investigate properties of doubly resonant SIVE (DR-SIVE) to understand how coupling between vibrational and vibronic states can be measured through DR-SIVE.
-DR-SIVE is shown to demand one and two-photon absorptions between the ground and excited state.
-DR-SIVE is thus the four wave mixing analogue of doubly resonant infrared-visible sum frequency generation. \cite{Shen94}
+We investigate properties of DR-HDFG to understand how coupling between vibrational and vibronic states can be measured.
+DR-HDFG is shown to demand one and two-photon absorptions between the ground and excited state.
+DR-HDFG is thus the four wave mixing analogue of doubly resonant infrared-visible sum frequency generation. \cite{Shen94}
 
-\section{Results and Discussion}
-Singly resonant SIVE (SR-SIVE) spectroscopy has potential to provide deeper insight into single quantum decoherence times and molecular orientation in condensed systems.
-Similarities between SR-SIVE spectroscopy, infrared spectroscopy and spontaneous hyper-Raman scattering have been noted previously. \cite{RN352, Bonn2024}
-In this section, we make the connections between SIVE and hyper-Raman scattering explicit and remark on the properties of SIVE that become apparent after inspecting the selection rules.
+\section{Steady State Hyper-DFG Spectroscopy}
+\subsection{Singly Resonant HDFG}
+Singly resonant hyper difference generation spectroscopy (HDFG) spectroscopy has potential to provide deeper insight into single quantum decoherence times and molecular orientation in condensed systems.
+Similarities between HDFG spectroscopy, infrared spectroscopy and spontaneous hyper-Raman scattering have been noted previously. \cite{RN352, Bonn2024}
+In this section, we make the connections between HDFG and hyper-Raman scattering explicit and its properties.
 
@@
 	\includegraphics[width=3.375in]{wmel1.png}
-	\caption{Wave Mixing Energy Level (WMEL) diagrams of the relevant SR-SIVE pathways in the (a) $\vec{k}_4 = -\vec{k}_1 + \vec{k}_2 + \vec{k}_3$ and (b) $\vec{k}_4 = \vec{k}_1 + \vec{k}_2 + \vec{k}_3$ phasematching geometries.
+	\caption{Wave Mixing Energy Level (WMEL) diagrams of the relevant HDFG pathways in the (a) $\vec{k}_4 = -\vec{k}_1 + \vec{k}_2 + \vec{k}_3$ and (b) $\vec{k}_4 = \vec{k}_1 + \vec{k}_2 + \vec{k}_3$ phasematching geometries.
 \cite{RN286, RN352}
@@
 
-\subsection{Vibrational SR-SIVE Selection Rules}
-To make the connection between SR-SIVE and hyper-Raman scattering, we investigate the gross selection rules of SR-SIVE-IR.
-By propagating density matrix elements in the steady state limit, the SIVE hyperpolarizability is \cite{RN119}
+To make the connection between HDFG and hyper-Raman scattering, we investigate its gross selection rules.
+By propagating density matrix elements in the steady state limit, the HDFG hyperpolarizability is \cite{RN119}
 \begin{equation}\label{sivegamma}
@@
 D, the Maker-Terhune degeneracy factor, accounts for permutation symmetry in $\gamma_{ijkl}$ and is defined as $\frac{n!}{(n-m)!}$, where $n$ is the total number of input fields (3 for any four wave mixing experiment) and $m$ is the number of distinguishable input fields.\cite{RN134}
-For a SIVE experiment using two or three distinct input fields, as considered here, D = 6.
+For a HDFG experiment using two or three distinct input fields, as considered here, D = 6.
 Note that $\ket{m}, \ket{n}$ are virtual states (\autoref{fig:sivewmel}).
@@
 \end{equation}
-As such, any mode that is SIVE active must be both hyper-Raman and IR active.
-However, since any IR active vibrational mode is hyper-Raman active,\cite{Cyvin1965, Andrews1978} any IR active mode is SIVE active.
-This makes SIVE an optically upconverted infrared spectroscopy of isotropic samples, as its selection rules are identically those of IR spectroscopy, but its output is generally in the visible.
-Unlike SFG spectroscopy, which is dependent upon both the infrared and Raman activity of a mode (through symmetry constraints, this demands that the microscopic SFG output from centrosymmetric species vanishes),\cite{Shen90, Cotton} SIVE is a nonlinear, optically upconverted spectroscopy for any infrared active mode.
-
-To understand SR-SIVE selection rules more finely, the dipole and first hyperpolarizability operators are Taylor expanded in terms of an n$^{\text{th}}$ normal mode coordinate $Q_n$ about equilibrium: \cite{Long1970}
+Taylor expanding the dipole and first hyperpolarizability operators in terms of an n$^{\text{th}}$ normal mode coordinate $Q_n$ about equilibrium: \cite{Long1970}
 \begin{subequations}
@@
 \end{subequations}
-Substituting into \autoref{sivebeta}, and knowing that $\mel{v}{Q_n}{g} = \sqrt{\frac{\hbar}{2m_n\omega_{vg}}}$ under the harmonic approximation,\cite{RN230} where $m_n$ is the mass of the $Q_n$ mode, gives the SIVE-IR-I hyperpolarizability to $\order{Q_n}$ as \begin{equation}\label{SIVEselection}
+Substituting into \autoref{sivebeta}, and knowing that $\mel{v}{Q_n}{g} = \sqrt{\frac{\hbar}{2m_n\omega_{vg}}}$ under the harmonic approximation,\cite{RN230} where $m_n$ is the mass of the $Q_n$ mode, gives the HDFG hyperpolarizability to $\order{Q_n}$ as \begin{equation}\label{SIVEselection}
 	\gamma_{ijkl} =	-\frac{1}{\varepsilon_0} \frac{1}{48 m_n \omega_{vg}}  \frac{1}{{\Delta_{gv}}} \ \frac{\partial \beta^{(ijk)}}{\partial Q_n} {\frac{\partial \mu^{(l)}}{\partial Q_n}}  \rho_{gg}
 \end{equation}
-Since this expression is non-zero in the harmonic oscillator limit, SR-SIVE output is allowed for harmonic transitions. 
-Similar to SFG, SR-SIVE does not demand anharmonic ground state potential energy surfaces for spectral output. \cite{Shen94, Cho2000}
-This selection rule is generally valid for any SR-SIVE process in the $-\vec{k}_1 + \vec{k}_2  + \vec{k}_3$ and $\vec{k}_1 + \vec{k}_2  + \vec{k}_3$ phasematching geometries when the Placzek approximation is valid.
+Since this expression is non-zero in the harmonic oscillator limit, HDFG output is allowed for harmonic transitions. 
+Similar to SFG, HDFG does not demand anharmonic ground state potential energy surfaces for spectral output. \cite{Shen94, Cho2000}
+This selection rule is generally valid for any HDFG or hyper sum frequency generation (HSFG) process in the $-\vec{k}_1 + \vec{k}_2  + \vec{k}_3$ and $\vec{k}_1 + \vec{k}_2  + \vec{k}_3$ phasematching geometries when the Placzek approximation is valid.
 
+\autoref{SIVEselection} shows any HDFG active mode must be both hyper-Raman and IR active.
+However, since any IR active vibrational mode is hyper-Raman active,\cite{Cyvin1965, Andrews1978} any IR active mode is HDFG active.
+This makes HDFG an optically upconverted infrared spectroscopy of isotropic samples, as its selection rules are identically those of IR spectroscopy, but its output is generally in the visible.
 A useful attribute of this selection rule is the added ability of polarization control arising from the hyperpolarizability tensor. 
-Similar to polarization control in second harmonic and sum frequency generation experiments which probe different elements of the infrared transition dipole and Raman polarizability tensor,\cite{Heinz1982} probing different elements of the hyperpolarizability tensor in SR-SIVE can greatly assist in understanding ultrafast dynamics in isotropic systems.
+Similar to polarization control in second harmonic and sum frequency generation experiments which probe different elements of the infrared transition dipole and Raman polarizability tensor,\cite{Heinz1982} probing different elements of the hyperpolarizability tensor in HDFG can greatly assist in understanding ultrafast dynamics in isotropic systems.
 \cite{Shen90, Bonn2024}
-Polarization control in IR-pump-SIVE-probe, analogous to ultrafast transient absorption spectroscopy, would be an interesting venue to assess the sensitivity of SR-SIVE to different hyper-Raman tensor elements.
+Polarization control in IR-pump-HDFG-probe, analogous to ultrafast transient absorption spectroscopy, would be an interesting venue to assess the sensitivity of HDFG to different hyper-Raman tensor elements.
 
-\subsection{Comparison to Sum Frequency Generation}
-Since the hyper-Raman process is effectively a two-photon process, a setup using only two lasers can perform the SIVE experiment by investigating $\pm \vec{k}_1 + 2\vec{k}_2$ processes.
+Since the hyper-Raman process is stimulated by a two-photon process, a setup using only two lasers can perform the HDFG experiment by investigating $\pm \vec{k}_1 + 2\vec{k}_2$ processes, assuming a two photon absorption from a single pulse stimulates the hyper-Raman process.
 The other commonly used two laser CMDS method is sum frequency generation, a $\chi^{(2)}$ technique, whose phasematching is dictated by $\vec{k}_1 + \vec{k}_2$.
@@
 As a result, the output of SFG is significantly reduced relative to most third order spectroscopies because the output only depends on surface species.
-However, since SIVE spectroscopy is dependent upon a hyper-Raman transition, it is useful to compare the relative output of the two processes to identify how SIVE output compares to SFG.
+However, since HDFG is dependent upon a hyper-Raman transition, it is useful to compare the relative output of the two processes to identify how HDFG output compares to SFG.
 
-To motivate the application of SIVE spectroscopy, we perform a calculation to compare the output of parametric SIVE-IR (\autoref{fig:sivewmel}b) to that of vibrational SFG (vSFG) spectroscopy.
+To motivate the application of HDFG spectroscopy, we perform a calculation to compare HDFG and vibrational SFG (vSFG) output.
 Absorption effects are neglected for simplicity.
@@
 		\begin{equation}
-			\abs{P^{(3)}_{\text{SIVE}}} = N_{bulk}  F(\omega_1+\omega_2 +\omega_3) \abs{\langle \beta_{ijk} \mu_{l} \rangle E_J{(\omega_3)}E_K(\omega_2)E_L(\omega_1)} \ell_{eff}
+			\abs{P^{(3)}_{\text{HDFG}}} = N_{bulk}  F(-\omega_1+\omega_2 +\omega_3) \abs{\langle \beta_{ijk} \mu_{l} \rangle E_J{(\omega_3)}E_K(\omega_2)E_L(-\omega_1)} \ell_{eff}
 		\end{equation}
@@
 We take the bulk optical interaction length ($\ell_{eff}$) to be 10 $\mu$m.\cite{RN133} %see chapter 25 of Shen's NLO book... idk something here seems wrong
-A normal dispersion curve is assumed so that $F(\omega_1+\omega_2) \approx F(\omega_1+\omega_2 +\omega_3)$.
+A normal dispersion curve is assumed so that $F(\omega_1+\omega_2) \approx F(-\omega_1+\omega_2 +\omega_3)$.
 To simplify analysis, orientational averaging is ignored (e.g., $\langle \beta_{ijk} \mu_{l} \rangle \approx \beta \mu$) and the input and output fields are taken to be co-polarized, so that
 \begin{equation}
-		P_{ratio} \equiv \frac{\abs{P^{(3)}_{\text{SIVE}}}}{\abs{P^{(2)}_{\text{SFG}}}} \approx \frac{N_{bulk}}{N_{surf}} \frac{\beta}{\alpha} E(\omega_3) \ell_{eff} \sim 10^4 \frac{\beta}{\alpha} E(\omega_3)\\
+		P_{ratio} \equiv \frac{\abs{P^{(3)}_{\text{HDFG}}}}{\abs{P^{(2)}_{\text{SFG}}}} \approx \frac{N_{bulk}}{N_{surf}} \frac{\beta}{\alpha} E(\omega_3) \ell_{eff} \sim 10^4 \frac{\beta}{\alpha} E(\omega_3)\\
 \end{equation}
@@
 Such an intensity is easily obtained using modern ultrafast sources.
-In this limit,
-\begin{equation}
-\begin{split}
-		P_{ratio} &\sim 10^4 \frac{\beta E(\omega_3)}{\alpha} \sim 10
-\end{split}
-\end{equation}
-Since the intensity ratio scales as $\abs{P_{ratio}}^2$, we see that the SIVE output is somewhat stronger than vibrational SFG, assuming only interfacial contributions in vSFG.
+In this limit, $P_\text{ratio} \sim 10$.
+Since the intensity ratio scales as $\abs{P_{ratio}}^2$, we see that the HDFG output is somewhat stronger than vibrational SFG, assuming only interfacial contributions in vSFG.
 It is important to note that this derivation ignored absorption and orientational averaging effects, which can significantly reduce output from either process.
 
-\subsection{Quantitative SR-SIVE}
-With the selection rules of SR-SIVE understood for vibrational spectroscopy, it becomes possible to extract quantitative information from SIVE spectra to compare to incoherent methods and other CMDS methods.
+With the selection rules of HDFG understood for vibrational spectroscopy, it becomes possible to extract quantitative information from its spectra.
 Lineshape analysis is essential for extracting quantitative information from CMDS spectra.
@@
 
-The SIVE $\chi^{(3)}_{IJKL}$ expression is
+The HDFG $\chi^{(3)}_{IJKL}$ expression is
 \begin{equation}\label{chi3}
@@
 Orientational averaging shows specific polarization schemes isolate linear combinations of different $\beta_{ijk}$ terms. 
-Infrared spectra can provide values for different $\vec{\mu}$ components.
+Infrared spectra can provide $\vec{\mu}$ values.
 Since $\vec{\mu}$ is a rank-one tensor, its three Cartesian components share the simple relationship $\langle {\mu^2_x} \rangle = \langle {\mu^2_y} \rangle = \langle {\mu^2_z} \rangle = \frac{1}{3}\langle {\mu^2} \rangle$.
 \cite{RN459}
-Neglecting rotational dependence (i.e., assuming only vibrational transitions), $\langle {\mu^2} \rangle = \abs{\mu}^2 = \mu^2$, so that $\langle \beta_{ijk} \mu_l \rangle = \langle \beta_{ijk} \rangle \frac{\mu}{\sqrt{3}}$.
+Neglecting rotational dependence (i.e., assuming only vibrational transitions), $\langle {\mu^2} \rangle = \mu^2$, so that $\langle \beta_{ijk} \mu_l \rangle = \langle \beta_{ijk} \rangle \frac{\abs{\mu}}{\sqrt{3}}$.
 By introducing the reduced mass coordinate $q_n = \sqrt{\frac{1}{m_n}} Q_n$ and using the expansions of $\beta_{ijk}$ and $\mu_{l}$ to $\order{Q_n}$ found earlier, we see
@@
 \end{equation}
-Since $\abs{\mu}$ values can be readily extracted from FT-IR spectra,\cite{RN412} this shows that SIVE can give quantitative information on the magnitude of $\beta_{ijk}$.
-
-A key result of \autoref{betasive} is that the sign of $\frac{\partial \beta_{ijk}}{\partial q_n}$ and $\frac{\partial \mu_{l}}{\partial q_n}$ can be extracted from SIVE spectra. 
-Since IR and spontaneous hyper-Raman spectroscopy report on $\Im(\chi^{(1)}) \sim \abs{\mu_{l}}^2$ and $\Im(\chi^{(5)}) \sim \abs{\beta_{ijk}}^2$,\cite{RN515} respectively, the absolute signs of $\frac{\partial \mu_{l}}{\partial q_n}$ and $\frac{\partial \beta_{ijk}}{\partial q_n}$ cannot be extracted from IR or hyper-Raman spectroscopy.
-These ideas can prove useful when assessing the validity of computational methods which report on the sign of $\frac{\partial \beta_{ijk}}{\partial q_n}$.
-Similar ideas were first introduced by Shen to extract the sign of $\frac{\partial \mu_{l}}{\partial q_n}$ from vSFG spectra.\cite{Shen90}
-SIVE and vSFG together provide a unique picture of extracting signs for the microscopic quantities ($\mu, \alpha, \beta$) that drive nonlinear output.
+Since $\abs{\mu}$ values can be readily extracted from FT-IR spectra,\cite{RN412} this shows that HDFG can give quantitative information on the magnitude of $\beta_{ijk}$.
+HDFG and vSFG together provide a unique picture of extracting the microscopic quantities ($\mu, \alpha, \beta$) that drive nonlinear output.
 
@@
 	\includegraphics[width=3.375in]{wmel3.png}
-	\caption{WMEL diagrams of some DR-SIVE pathways in the $-\vec{k}_1 + \vec{k}_2+ \vec{k}_3$  (I-a,I-b) and $\vec{k}_1 + \vec{k}_2+ \vec{k}_3$ (II-a,II-b) phasematching outputs.
+	\caption{WMEL diagrams of some (I-a,I-b) DR-HDFG and (II-a,II-b) DR-HSFG pathways.
 $\ket{g,0}$ denotes the ground states, $\ket{g,v}$ denotes a vibrational state on the ground electronic manifold; $\ket{m,n}$ denotes a virtual state, and $\ket{e,0}, \ket{e,v'}$ denote vibronic states.}
@@
 
-\subsection{DR-SIVE-IR Selection Rules} %%most of this can probably be scrapped because... we don't really learn much new here.
-DR-SIVE (where a vibrational and vibronic state are resonantly coupled) can provide a tool for measuring vibronic coupling.
-This method is analogous to doubly resonant sum frequency generation. \cite{Shen94}
-Multi-resonant nonlinear spectroscopies, such as coherent anti-Stokes Raman spectroscopy (CARS), 2D Electronic Vibrational (2D-EV) spectroscopy and triply resonant sum frequency generation (TRSF) spectroscopy, have been employed to resolve vibronic coupling in molecular samples.
-\cite{Carlson1990, Gaynor2017, RN276}
-DR-SIVE provides methods to investigate vibronic coupling with only two laser pulses, as long as the electronic state is accessible via two photon absorption from the ground state (\textit{vide infra}).
-Two beam, parametric and non-parametric DR-SIVE processes are diagrammed in \autoref{fig:doubsive}.
+\subsection{Doubly Resonant HDFG}
+While HDFG can provide useful information about the properties of molecular vibrations, it is immediately apparent that \autoref{fig:sivewmel} can inform on molecular electronic structure by making the hyper-Raman transition resonant with a vibronic state.
+DR-HDFG (where a vibrational and vibronic state are resonantly coupled) can provide a tool for measuring vibronic coupling.
+This method is analogous to doubly resonant sum frequency generation (DR-SFG). \cite{Shen94}
+Many multi-resonant nonlinear spectroscopies have been developed to resolve vibronic coupling in molecular samples. \cite{Carlson1990, Gaynor2017, RN276}
+DR-HDFG provides methods to investigate vibronic coupling with only two laser pulses, as long as the electronic state is accessible via two photon absorption from the ground state (\textit{vide infra}).
+Two beam, parametric and non-parametric DR-HDFG processes are diagrammed in \autoref{fig:doubsive}.
 Here, states are written assuming the Born-Oppenheimer approximation, such that $\ket{a,b} = |a) \otimes \ket{b}$ for electronic states $\{|a)\}$ and vibrational states $\{\ket{b}\}$.
@@
 The goal of this section is to understand DR-SIVE-IR selection rules.
-We begin by inspecting the selection rules of a non-parametric DR-SIVE pathway (\autoref{fig:doubsive}I-a) in the driven limit. 
+We begin by inspecting the selection rules of a non-parametric DR-HDFG pathway (\autoref{fig:doubsive}I-a) in the driven limit. 
 The driven limit is useful as despite the sum over states approach, it avoids implications of ultrafast dephasing of the vibronic state.\cite{Cho2001} 
@@
 $R^{i}_{gv,ev'} = \mel{v}{M^i_{ge}}{v'}$.\cite{Albrecht1960}
-\begin{widetext}
 Using these ideas rewrites \autoref{drgamma_notaylor} as
@@
 \end{equation}
-Contracting over $m,n$ in \autoref{drgamma_notaylor_1} by invoking the two photon absorption polarizability $\Lambda$ gives \cite{McClain1977, Simpson2004, Olson2018}
-\begin{equation}\label{drgamma_alpha_0}
-	\gamma_{ijkl} = -\frac{1}{\varepsilon_0} \frac{1}{24 \hbar^2} \sum_{v'} \frac{
-		\mel{v}{M^{i}_{ge}}{v'} 
-		\mel{v'}{\Lambda^{jk}_{eg}}{v}
-		\mel{v}{M^{l}_{gg}}{0}
-	}{\Delta_{g0,gv}
-		\Delta_{ev', g0}
-	}
-\end{equation}
-where ${\Lambda^{jk}_{eg}} = (e|\Lambda^{jk}|g)$. 
-\end{widetext}
-Since $\Lambda^{jk}$ transforms like a rank two tensor, it is clear that the electronic transition must be both one and two photon allowed for non-zero output, similar to resonant second harmonic generation spectroscopy.
-\cite{Heinz1982, Nguyen1986, Simpson2004}
-This is identical to a selection rule in resonance hyper-Raman scattering, as derived by Chung and Ziegler. \cite{Ziegler1988}
-As such, the DR-SIVE methods discussed here are coherent, resonance hyper-Raman analogues. 
-This makes DR-SIVE a type of resonance IR spectroscopy, as introduced by Boyle et al.\cite{RN491} 
-However, in the methods described by \autoref{drgamma_alpha_0}, $|e)$ must be accessible through one and two photon transitions from $|g)$.
-Conversely, the resonance-IR method demonstrated by Boyle et al. only requires one photon transitions between $|g)$ and $|e)$.
-Systems which provide strict parity selection rules (e.g., benzene) will be useful for assessing the validity of these selection rules and comparing the method described here and that of Boyle et al.
+The first three terms in the numerator coorespond to a resonance hyper-Raman scattering process, whose selection rules have been derived in detail by Chung and Ziegler. \cite{Ziegler1988}
+As such, the DR-HDFG methods discussed here are coherent, resonance hyper-Raman analogues. 
+A typical Albrecht $A,B,C$ decomposition of these vibronic operators, as shown by Chung and Ziegler, demonstrates the feasibility for one and two photon electronic transitions.
+Briefly,... %todo: discuss Ziegler ABC terms in some detail. They are what drive this paper.
+A simulated spectrum highlighting the contributions of these terms (\autoref{fig:doubres_spec}) shows...
+\begin{figure}[!htbp]
+	\centering
+	\includegraphics[width=3.375in]{drsive_spectrum.png}
+	\caption{Spectrum showing sensitivity of DR-HDFG to well displacements in vibronic coupling.
+		Model includes both Franck-Condon and Herzberg Teller effects.
+		(a) Potential energy surfaces, (b) 2D spectrum including all A,B,C components, (c,d,e) A, B, C term contributions (respectively) to (b).}
+	\label{fig:doubres_spec}
+\end{figure}
+
+%These results also make DR-HDFG a type of resonance IR spectroscopy, as introduced by Boyle et al for resonant triple sum frequency generation.\cite{RN491} 
+%However, in the methods described by \autoref{drgamma_alpha_0}, $|e)$ must be accessible through one and two photon transitions from $|g)$.
+%Conversely, the resonance-IR method demonstrated by Boyle et al. only requires one photon transitions between $|g)$ and $|e)$.
+%Systems which provide strict parity selection rules (e.g., benzene) will be useful for assessing the validity of these selection rules and comparing the method described here and that of Boyle et al.
 \cite{RN491}
 
-\subsection{Line Narrowing in SIVE Spectroscopies}
 An unavoidable consequence in electronic spectroscopy is broadened lineshapes due to the inhomogeneity of electronic transitions (e.g., vibronic sidebands, molecular collisions). 
 Four wave mixing methods can line-narrow transitions, i.e., resolve inhomogeneous broadening.\cite{Carlson1990line}
-The line-narrowing properties of DR-SIVE are investigated so that the pathways which line-narrow correlated or anti-correlated modes (\textit{vide infra}) can be identified.
-SR-SIVE cannot linenarrow transitions as it is singly resonant. \cite{RN352}
+The line-narrowing properties of DR-HDFG are investigated so that the pathways which line-narrow correlated or anti-correlated modes (\textit{vide infra}) can be identified.
+Singly resonant HDFG cannot linenarrow transitions. \cite{RN352}
 
@@
 
-\section{Conclusions}
+\section{Mixed-Domain Hyper-DFG}
+Some words about why mixed domain is great (kill NRB, isolate FID based stuff etc)
+Then introduce problems (pathway interference) which can screw things up. This then leads into the main section.
+
+It is well known that nonlinear wave mixing processes which share the same time ordering and output frequency will interfere. \cite{RN135, Bonn2024}
+Understanding interfering pathways is useful because they can, in some cases, eliminate output. \cite{RN342, RN135}
+The WMEL diagrams presented in \autoref{fig:sivewmel} outline resonant HDFG processes when the infrared pulse $(\omega_1)$ is resonant with a vibrational mode. 
+However, if $\omega_2$ becomes resonant and $\omega_1$ is non-resonant, then other HDFG pathways appear.\cite{McDonnell2024} 
+While the methods in \autoref{fig:sivewmel2} possess identical selection rules to \autoref{fig:sivewmel}, the WMEL diagrams presented in \autoref{fig:sivewmel2} may significantly interfere with DOVE-IR and DOVE-Raman spectra.
+The time ordering in DOVE-IR and DOVE-Raman spectra is used to interpret anharmonicities, as DOVE-IR and DOVE-Raman destructively interfere when outputs are at the same frequency. \cite{RN135, RN324}
+It is therefore important to understand how the corresponding HDFG pathways interfere.
+To this end, we investigate how the HDFG-IR-II and HDFG-Raman pathways (\autoref{fig:sivewmel2}a, b, respectively) interfere under the rotating wave approximation.
+
+\begin{figure}[!htbp]
+	\centering
+	\includegraphics[width=3.375in]{figures/wmel2.png}
+	\caption{Wave Mixing Energy Level (WMEL) diagrams of interfering hyper-DFG pathways in the  $\vec{k}_4 = -\vec{k}_1 + \vec{k}_2 + \vec{k}_3$ phasematching geometry. 
+		(a) is similar to the process diagrammed in \autoref{fig:sivewmel}, whereas (b) is similar to a singly resonant coherent anti-Stokes Raman-type process.}
+	\label{fig:sivewmel2}
+\end{figure}
+
+We employ the response function formalism of Mukamel for this analysis. \cite{RN287}
+The third order response functions, $R^{(3)}$, for \autoref{fig:sivewmel2}a ($R^{(3)}_{a}$) and \autoref{fig:sivewmel2}b ($R^{(3)}_{b}$) are 
+\begin{subequations}
+	\begin{equation} \label{mixing:a}
+		R^{(3)}_{a} (t_2) = -\frac{i}{\hbar} [\beta(t_2), \mu(0)] \exp(-i\Delta_{v''g}t_2) \theta(t_2)
+	\end{equation}
+	\begin{equation}\label{mixing:b}
+		\begin{split}
+			R^{(3)}_{b} (t_2) & = \frac{i}{\hbar} [\beta(t_2), \mu(0)] \exp(-i\Delta_{v''g}t_2) \theta(t_2)\\
+		\end{split}
+	\end{equation}
+\end{subequations}
+The total response function is $R^{(3)}_\text{tot} (t_2) = R^{(3)}_{a} (t_2) + R^{(3)}_{b} (t_2) = 0$. 
+Since the total output response function vanishes in this time-ordering, the pathways in \autoref{fig:sivewmel2} perfectly destructively interfere.
+Therefore, to measure coherent dynamics via hyper-DFG, the time ordering shown in \autoref{fig:sivewmel} should be used.
+These ideas have been seen experimentally in ultrafast DOVE work, as described elsewhere. \cite{RN367, McDonnell2024}
+In the case of the time ordered (\autoref{fig:sivewmel}a) pathway, there are no opportunities for interference as all other pathways are nonresonant with the first interaction. 
+A possible mechanism for interfering output in the (\autoref{fig:sivewmel}a) pathway are cascaded second order processes (SFG, DFG). \cite{RN243, RN300}
+In isotropic media, SFG and DFG vanish under the electric dipole approximation,\cite{RN231} so cascades are unlikely to inhibit output in centrosymmetric media.
+In media where SFG and DFG are allowed, e.g. surfaces or noncentrosymmetric media, second order cascades may become important.
+
+%todo: measuring Coherence and Population Lifetimes
+
+\section{Experimental Hyper-DFG Results}
+With the theoretical description of HDFG provided, we will investigate steady state and transient HDFG spectra of $\nu$(CH) modes in CH$_3$CN.
+
+\subsection{dynamics} 
+Look at coherence dynamics of v(CH), v(CN) in CH3CN. 
+THIS EXPERIMENT IS DEFINITELY EASIER THAN EXTRACTING CHI3.
+
+\subsection{Calculation of $\beta$ for v(CH) modes in CH3CN}
+do the classic C6D6 at CH3CN expt ? (or CaF2, whatever) - get interferogram, fit, get numbers.
+Dipoles of CH3CN fitted by John in the 2003 paper, so only need to get $\beta$. 
+Compare this to the theoretical CH3CN hyper Raman paper.
+We can decide if this is worth it.
+
+\section{Conclusions}%didn't change to HDFG down here because lazy
 Coherent vibrational, hyper-Raman coherent four wave mixing spectroscopies are identified and discussed.

### 2024-07-06 paper.tex
initial stuff to account for ABC
Need to clarify a lot and makes things clearer / read smoothly.

Also notational issues need to be fixed.

@@
 Most of these methods rely on infrared or Raman transitions to generate output. 
-The implementation of a nonlinear hyper-Raman spectroscopy, which first appears at third order perturbation theory, can provide a useful analogue to these techniques to understand the spectroscopy and dynamics of isotropic systems.
-Hyper Difference Frequency Generation (hyper-DFG) spectroscopy, a type of nonlinear hyper-Raman spectroscopy also known as singly vibrationally enhanced spectroscopy (SIVE), is an underdeveloped four wave mixing technique which shows promise as a method to disentangle ultrafast vibrational dynamics in isotropic systems without need for anharmonicities.
+Implementing a nonlinear spectroscopy involving hyper-Raman transitions, first appearing under third order perturbation theory, can provide a useful analogue to infrared and Raman based nonlinear spectroscopies to understand the spectroscopy and dynamics of isotropic systems.
+Hyper Difference Frequency Generation (HDFG) spectroscopy, also known as singly vibrationally enhanced spectroscopy (SIVE), is an underdeveloped, hyper-Raman based four wave mixing vibrational spectroscopy.
+However, the spectroscopic and dynamic properties of HDFG have not been fully explored.
 We derive selection rules for singly resonant hyper-DFG and demonstrate it provides a simpler method to extract hyper-Raman polarizabilities ($\beta$).
-The hyper-DFG output is shown to be slightly stronger than vibrational difference frequency generation (vSFG), heavily driven by the number density probed by each process. 
-We demonstrate the capabilities of hyper-DFG through probing the spectra and coherence dynamics of the $\nu$(CH) modes in CH$_3$CN.
-The theory of hyper-DFG is extended to account for vibronic coupling induced by two-photon absorption, i.e. doubly resonant hyper-Raman (DR-HDFG), akin to resonant hyper-Raman spectroscopy. 
-DR-HDFG is shown to be a type of resonance IR spectroscopy and is likely able to resolve vibronic coupling.
+HDFG output is shown to be similar in magnitude to vibrational sum frequency generation (vSFG). 
+We demonstrate the properties and capabilities of HDFG through measuring spectra and coherence dynamics of multiple infrared active modes in CH$_3$CN.
+HDFG shows promise as a method to disentangle ultrafast vibrational dynamics in isotropic systems without need for anharmonicities.
 
@@
 
+\begin{figure}[!htbp]
+	\centering
+	\includegraphics[width=3.375in]{dfg_hdfg_hr_wmel.png}
+	\caption{Wave Mixing Energy Level (WMEL) diagrams of difference frequency generation (DFG), hyper difference frequency generation (HDFG) and spontaneous hyper-Raman scattering. \cite{RN286, RN352}
+		$\ket{g}$ is the ground state, $\ket{v}$ is an infrared active vibration and $\ket{m}, \ket{n}$ are virtual states.
+		Solid and dashed horizontal lines indicate real and virtual states, whereas solid and dotted arrows indicate ket and bra side transitions, respectively.
+%todo: add Raman to this WMEL!
+dfg Raman hyperDFG hyperRaman
+		}
+	\label{fig:comparisonwmel}
+\end{figure}
+
 Not all CMDS methods are used to dissect intramolecular couplings.\cite{Shen1987_CPL}
-Singly vibrationally enhanced (SIVE) is a four wave mixing method which, when detuned from  electronic resonances, does not probe intramolecular couplings. 
-Non-parametric, hyper difference frequency generation (hyper-DFG) spectroscopy was the first infrared CMDS method to successfully discriminate against non-resonant background.\cite{RN351, RN352}
-Hyper-DFG has also been refered to as singly vibrationally enhanced (SIVE) spectroscopy. \cite{RN351}
+Non-parametric, hyper difference frequency generation (hyper-DFG) spectroscopy, similar to difference frequency generation (\autoref{fig:comparisonwmel}), is a four wave mixing method which, when detuned from  electronic resonances, does not probe intramolecular couplings.
+HDFG was the first infrared CMDS method to successfully discriminate against non-resonant background.\cite{RN351, RN352}
+Hyper-DFG has also been referred to as singly vibrationally enhanced (SIVE) spectroscopy. \cite{RN351}
 In hyper-DFG, an infrared pulse is resonant with a vibrational mode, and two other input pulses are used to induce a scattering process to provide output.
@@
 In this method, a single infrared pulse is resonant with a vibrational mode, and a two photon absorption event from a near infrared (NIR) or visible pulse resonant with an electronic or vibronic state is used to generate the four wave mixing signal.
-These pathways are referred to herein as doubly resonant hyper-DFG (DR-HDFG).
-Methods analogous to DR-HDFG, where two photon absorption from the infrared pulse and single photon absorption from the visible pulse is used to generate output, i.e., stimulated Raman processes, have been reported.
+The non-parametric pathways similar to this method are referred to herein as doubly resonant hyper-DFG (DR-HDFG).
+Methods analogous to DR-HDFG, where two photon absorption from the infrared pulse and one photon absorption from the visible pulse is used to generate output, i.e., stimulated Raman processes, have been reported.
 \cite{RN301, RN120}
@@
 \section{Steady State Hyper-DFG Spectroscopy}
-\subsection{Singly Resonant HDFG}
 Singly resonant hyper difference generation spectroscopy (HDFG) spectroscopy has potential to provide deeper insight into single quantum decoherence times and molecular orientation in condensed systems.
 Similarities between HDFG spectroscopy, infrared spectroscopy and spontaneous hyper-Raman scattering have been noted previously. \cite{RN352, Bonn2024}
-In this section, we make the connections between HDFG and hyper-Raman scattering explicit and its properties.
+In this section, we make the connections between HDFG and hyper-Raman scattering explicit and investigate the steady state properties of singly resonant HDFG.
 
@@
 This makes HDFG an optically upconverted infrared spectroscopy of isotropic samples, as its selection rules are identically those of IR spectroscopy, but its output is generally in the visible.
-A useful attribute of this selection rule is the added ability of polarization control arising from the hyperpolarizability tensor. 
-Similar to polarization control in second harmonic and sum frequency generation experiments which probe different elements of the infrared transition dipole and Raman polarizability tensor,\cite{Heinz1982} probing different elements of the hyperpolarizability tensor in HDFG can greatly assist in understanding ultrafast dynamics in isotropic systems.
+A useful attribute of the $\beta_{ijk}$ dependence in HDFG output is added polarization control. 
+Similar to SHG and SFG experiments that probe different elements of the infrared transition dipole and Raman polarizability tensors,\cite{Heinz1982} probing different elements of $\beta_{ijk}$ in HDFG can greatly assist in understanding ultrafast dynamics in isotropic systems, as suggested by Seliya et al.
 \cite{Shen90, Bonn2024}
-Polarization control in IR-pump-HDFG-probe, analogous to ultrafast transient absorption spectroscopy, would be an interesting venue to assess the sensitivity of HDFG to different hyper-Raman tensor elements.
+Polarization control in IR-pump-HDFG-probe, analogous to ultrafast transient absorption spectroscopy for vibrational modes, would be an interesting venue to assess the sensitivity of HDFG to different hyper-Raman tensor elements.
 
-Since the hyper-Raman process is stimulated by a two-photon process, a setup using only two lasers can perform the HDFG experiment by investigating $\pm \vec{k}_1 + 2\vec{k}_2$ processes, assuming a two photon absorption from a single pulse stimulates the hyper-Raman process.
+Previous spontaneous hyper-Raman work interpreted the origin of hyper-Raman signal in terms of Franck-Condon, Herzberg-Teller and Duschinsky type couplings.\cite{Ziegler1988} %todo: cite the other papers.
+As such, we investigate \autoref{SIVEselection} using an Albrecht ABC type formalism which naturally incorporates these types of couplings.
+To do so, we write the states in terms of a Born-Oppenheimer basis $\ket{a,b}$, where $\ket{a,b} = |a) \otimes \ket{b}$ for electronic states $\{|a)\}$ and vibrational states $\{\ket{b}\}$.
+\cite{BornOppenheimer, Albrecht1960}
+Here, $\ket{g}, \ket{v}$ are vibrational states on the ground electronic state $|g)$ and $\ket{m} \rightarrow \ket{m,j}$, $\ket{n} \rightarrow \ket{n,k}$ are virtual states.
+For consistency with previous reports, we use $\vec{R}$ to denote electric transition dipole moments ($\vec{\mu}$ is used for transitions between states on the ground electronic state.).
+\cite{Ziegler1974}
+Following the approach which gave \autoref{sivegamma}, we find
+\begin{equation}\label{drgamma_notaylor}
+	\gamma_{ijkl} = -\frac{1}{\varepsilon_0} \frac{1}{24 \hbar^3} \sum_{m,n,j,k} \frac{
+		R^{i}_{gv, nk} 
+		R^{j}_{nk,mj} 
+		R^{k}_{mj,gg} 
+		R^{l}_{gv,gg} 
+	}{\Delta_{g0,gg}
+		\Delta_{nk, mj}
+		\Delta_{mj, gg}
+	}
+\end{equation}
+where $R^{i}_{ab,cd}$ is the i$^{th}$ element of $\mel{a,b}{\vec{R}}{c,d}$.\cite{Ziegler1988}
+Using our definition of vibronic states, we write $\vec{M}_{ab} = (a|\vec{M}|b)$ so that, for example,
+$R^{i}_{gv,ev'} = \mel{v}{M^i_{ge}}{v'}$.\cite{Albrecht1960}
+Using these ideas rewrites \autoref{drgamma_notaylor} as
+\begin{equation}\label{drgamma_notaylor_1}
+	\begin{split}
+		\gamma_{ijkl} &= -\frac{1}{\varepsilon_0} \frac{1}{24 \hbar^3} \sum_{m,n,v'} \frac{
+			\mel{v}{M^{i}_{ge}}{v'} 
+			\mel{v'}{M^{j}_{em}}{n}
+			\mel{n}{M^{k}_{mg} }{v}
+			\mel{v}{M^{l}_{gg}}{0}
+		}{\Delta_{g0,gv}
+			\Delta_{ev', mn}
+			\Delta_{mn, g0}	} \\
+	\end{split}
+\end{equation}
+Chung and Ziegler showed some years ago that expanding ${\vec{M}_{ij}}$ to $\order{Q}$ yields $A, B, C$ coefficients similar to the Albrecht formalism of Raman scattering.
+\cite{Albrecht1961, Ziegler1988}
+The $A$ term depends upon Franck-Condon $\order{Q^0}$ transitions, the $B$ term depends upon Herzberg-Teller ($\order{Q}$) transitions, and the $C$ term depends on Duschinsky ($\order{Q^2}$) transitions.
+Here, we ignore the C term as it depends on one and two photon forbidden transitions which have yet to be observed in spontaneous hyper-Raman scattering. \cite{Ziegler1988}
+The full derivation of $A,B$ have been given elsewhere, so only their final forms will be given.
+
+By compiling all the terms that scale with $\order{Q^0}$, i.e. $\vec{M}_{ij_0}$, $A$ is written as
+\begin{equation}
+	\begin{split}
+		A_{ijk} &= \text{crap times Franck Condon}\\
+	\end{split}
+\end{equation}
+where terms such as $\langle v | v' \rangle$ are Franck-Condon factors.
+
+something about the A term. SHOW THAT IT VANISHES FOR SINGLY RES TERMS
+
+It is important to note that in the case of singly resonant HDFG, $A_{ijk}$ vanishes, or only Herzberg-Teller contributions are present in SR-HDFG. \cite{Neddersen1989}
+
+Similarly, the $B$ terms scale with $\order{Q}$, such that
+\begin{equation}
+	\begin{split}
+		B_{ijk} &= \text{crap}\\
+	\end{split}
+\end{equation}
+Then B term. 
+B term has new sum over another normal mode Ql that must be included because when I expand in terms of Q there are 3N-6-1 normal modes I can talk to (3N-6-1, assuming nonlinear and that the -1 comes from assuming we end in v)
+Blah Blah Blah
+%todo: So clearly HDFG has heavy dependence on HT type couplings! 
+%This likely explains the relative weakness of HDFG in solvents such as hexane. \cite{RN351}
+%fix the equation so that the dipole is clearly isolated from the hyper Raman part. Write beta as A+B+C?
+%todo: segue into vibronic coupling
+
+While HDFG can provide useful information about the properties of molecular vibrations, it is immediately apparent that \autoref{fig:sivewmel} can inform on molecular electronic structure by making the hyper-Raman transition resonant with a vibronic state.
+DR-HDFG (where a vibrational and vibronic state are resonantly coupled) can provide a tool for measuring vibronic coupling.
+This method is analogous to doubly resonant sum frequency generation (DR-SFG). \cite{Shen94}
+Many multi-resonant nonlinear spectroscopies have been developed to resolve vibronic coupling in molecular samples. \cite{Carlson1990, Gaynor2017, RN276}
+DR-HDFG provides methods to investigate vibronic coupling with only two laser pulses, as long as the electronic state is accessible via two photon absorption from the ground state (\textit{vide infra}).
+Two beam, parametric and non-parametric DR-HDFG processes are diagrammed in \autoref{fig:doubsive}.
+%todo: insert discussion on ABC terms
+%todo: write hamiltonian like Gaynor to make clear what we are doing (and put in a picture in Figure doubbleresspec)
+
+To interpret HDFG selection rules, we use a slightly modified version of equation xyz to account for the added vibronic resonance. 
+This change immediately makes the A term nonzero in the case of noncentrosymmetric systems.
+
+A simulated spectrum highlighting the contributions of these terms (\autoref{fig:doubres_spec}) on potential wells with displacements $\Delta$ shows... 
+\begin{figure}[!htbp]
+	\centering
+	\includegraphics[width=3.375in]{drsive_spectrum.png}
+	\caption{Spectrum showing sensitivity of DR-HDFG to well displacements in vibronic coupling.
+		Model includes both Franck-Condon and Herzberg Teller effects.
+		(a) Potential energy surfaces, 2D spectrum where (b) $\Delta = 0$, (c) $\Delta = 0.5$, (d) $\Delta = 1$}
+	\label{fig:doubres_spec}
+\end{figure}
+
+%These results also make DR-HDFG a type of resonance IR spectroscopy, as introduced by Boyle et al for resonant triple sum frequency generation.\cite{RN491} 
+%However, in the methods described by \autoref{drgamma_alpha_0}, $|e)$ must be accessible through one and two photon transitions from $|g)$.
+%Conversely, the resonance-IR method demonstrated by Boyle et al. only requires one photon transitions between $|g)$ and $|e)$.
+%Systems which provide strict parity selection rules (e.g., benzene) will be useful for assessing the validity of these selection rules and comparing the method described here and that of Boyle et al.
+\cite{RN491}
+
+\subsection{Quantification}
+Since the hyper-Raman process is stimulated by a two-photon process, a setup using only two lasers can perform a coherent four wave mixing hyper-Raman experiment by investigating $\pm \vec{k}_1 + 2\vec{k}_2$ processes, assuming a two photon absorption from a single pulse stimulates the hyper-Raman process.
 The other commonly used two laser CMDS method is sum frequency generation, a $\chi^{(2)}$ technique, whose phasematching is dictated by $\vec{k}_1 + \vec{k}_2$.
 The SFG output scales as $\chi^{(2)}_{IJK} \sim \langle \alpha_{ij} \mu_k \rangle$, where $\alpha_{ij}$ is the Raman polarizability tensor.
-Since SFG is dependent upon transitions that transform like both rank-one and rank-two tensors, this enforces a microscopic constraint that SFG cannot yield output for centrosymmetric species under the electric dipole moment.
-This follows from simple parity arguments, where inversion centers demand states possess distinct parity selection rules. \cite{RN230}
-Macroscopically, inversion symmetry in the output polarization eliminates output from centrosymmetric species under the electric dipole approximation.
+Since SFG is dependent upon transitions that transform like both rank-one and rank-two tensors, this enforces a microscopic constraint that SFG cannot yield output for centrosymmetric species under the electric dipole approximation.
+This follows from the presence of an inversion center in centrosymmetric systems, which demands strict parity selection rules. \cite{RN230}
+Macroscopically, inversion symmetry in the output polarization eliminates output from centrosymmetric species under the electric dipole approximation.\cite{RN227, RN132}
 As a result, the output of SFG is significantly reduced relative to most third order spectroscopies because the output only depends on surface species.
@@
 \cite{Levenson1974_2, RN351, RN345}
+%okay clearly this wont work lol we need something that is IR active... CaF2?%
 Self-heterodyning of the internal standard signal measures $\chi^{(3)}$ and does not require measurement of absolute intensities. 
@@
 To our knowledge, only vibrational SFG and 2D-IR spectroscopy has taken advantage of orientationally averaged $\chi^{(n)}$ values to extract transition moments. \cite{Shen90, Moilanen2009, RN245}
-Previous treatments did not consider using quantitative analysis in SIVE to measure $\beta_{ijk}$ values from SIVE spectra.
 It is thus useful to investigate how a simple treatment of orientational averaging can extract $\beta_{ijk}$ from $\chi^{(3)}_{IJKL}$.
@@
 This expression cannot be used as written to extract $\beta_{ijk}$, as $\beta_{ijk}$ is a Hermitian operator, but $\Delta_{gv} \in \mathbb{C}$. 
-However, since the real and imaginary parts of $\chi^{(3)}$ can be extracted from the Bloembergen interferometry experiment, we can choose to focus on either its real or imaginary part.
+However, since the real and imaginary parts of $\chi^{(3)}$ can be extracted from the Bloembergen interferometry experiment, and $\beta_{ijk}$ is present in either term, we can choose to focus on the real or imaginary part of $\chi^{(3)}$.
 For simplicity, we investigate $\Im(\chi^{(3)})$, giving, assuming resonance conditions, 
@@
 Since $\abs{\mu}$ values can be readily extracted from FT-IR spectra,\cite{RN412} this shows that HDFG can give quantitative information on the magnitude of $\beta_{ijk}$.
-HDFG and vSFG together provide a unique picture of extracting the microscopic quantities ($\mu, \alpha, \beta$) that drive nonlinear output.
+HDFG and vSFG together provide unique methods to extract the microscopic quantities ($\mu, \alpha, \beta$) that drive nonlinear output.
 
@@
 
-\subsection{Doubly Resonant HDFG}
-While HDFG can provide useful information about the properties of molecular vibrations, it is immediately apparent that \autoref{fig:sivewmel} can inform on molecular electronic structure by making the hyper-Raman transition resonant with a vibronic state.
-DR-HDFG (where a vibrational and vibronic state are resonantly coupled) can provide a tool for measuring vibronic coupling.
-This method is analogous to doubly resonant sum frequency generation (DR-SFG). \cite{Shen94}
-Many multi-resonant nonlinear spectroscopies have been developed to resolve vibronic coupling in molecular samples. \cite{Carlson1990, Gaynor2017, RN276}
-DR-HDFG provides methods to investigate vibronic coupling with only two laser pulses, as long as the electronic state is accessible via two photon absorption from the ground state (\textit{vide infra}).
-Two beam, parametric and non-parametric DR-HDFG processes are diagrammed in \autoref{fig:doubsive}.
-Here, states are written assuming the Born-Oppenheimer approximation, such that $\ket{a,b} = |a) \otimes \ket{b}$ for electronic states $\{|a)\}$ and vibrational states $\{\ket{b}\}$.
-\cite{BornOppenheimer, Albrecht1960}
-
-The goal of this section is to understand DR-SIVE-IR selection rules.
-We begin by inspecting the selection rules of a non-parametric DR-HDFG pathway (\autoref{fig:doubsive}I-a) in the driven limit. 
-The driven limit is useful as despite the sum over states approach, it avoids implications of ultrafast dephasing of the vibronic state.\cite{Cho2001} 
-For consistency with previous reports, we use $\vec{R}$ to denote electric transition dipole moments (not to be confused with the response function; $\vec{\mu}$ is used for transitions between states on the ground electronic state.).
-\cite{Ziegler1974}
-Following the approach which gave \autoref{sivegamma}, we find
-\begin{equation}\label{drgamma_notaylor}
-	\gamma_{ijkl} = -\frac{1}{\varepsilon_0} \frac{1}{24 \hbar^3} \sum_{m,n,v'} \frac{
-		R^{i}_{gv,ev'} 
-		R^{j}_{ev',mn} 
-		R^{k}_{mn,gv} 
-		R^{l}_{gv,g0} 
-	}{\Delta_{g0,gv}
-		\Delta_{ev', mn}
-		\Delta_{mn, g0}
-	}
-\end{equation}
-where $R^{i}_{gv,ev'}$ is the i$^{th}$ element of $\mel{g,v}{\vec{R}}{e,v'}$.
-For generality, we assume that the vibronic  $\ket{e,v'}$ does not share the same vibration with $\ket{g,v}$. \cite{Ziegler1988}
-Using our definition of vibronic states, we write $\vec{M}_{ab} = (a|\vec{M}|b)$ so that, for example,
-$R^{i}_{gv,ev'} = \mel{v}{M^i_{ge}}{v'}$.\cite{Albrecht1960}
-Using these ideas rewrites \autoref{drgamma_notaylor} as
-\begin{equation}\label{drgamma_notaylor_1}
-	\gamma_{ijkl} = -\frac{1}{\varepsilon_0} \frac{1}{24 \hbar^3} \sum_{m,n,v'} \frac{
-		\mel{v}{M^{i}_{ge}}{v'} 
-		\mel{v'}{M^{j}_{em}}{n}
-		\mel{n}{M^{k}_{mg} }{v}
-		\mel{v}{M^{l}_{gg}}{0}
-	}{\Delta_{g0,gv}
-		\Delta_{ev', mn}
-		\Delta_{mn, g0}	}
-\end{equation}
-The first three terms in the numerator coorespond to a resonance hyper-Raman scattering process, whose selection rules have been derived in detail by Chung and Ziegler. \cite{Ziegler1988}
-As such, the DR-HDFG methods discussed here are coherent, resonance hyper-Raman analogues. 
-A typical Albrecht $A,B,C$ decomposition of these vibronic operators, as shown by Chung and Ziegler, demonstrates the feasibility for one and two photon electronic transitions.
-Briefly,... %todo: discuss Ziegler ABC terms in some detail. They are what drive this paper.
-A simulated spectrum highlighting the contributions of these terms (\autoref{fig:doubres_spec}) shows...
-\begin{figure}[!htbp]
-	\centering
-	\includegraphics[width=3.375in]{drsive_spectrum.png}
-	\caption{Spectrum showing sensitivity of DR-HDFG to well displacements in vibronic coupling.
-		Model includes both Franck-Condon and Herzberg Teller effects.
-		(a) Potential energy surfaces, (b) 2D spectrum including all A,B,C components, (c,d,e) A, B, C term contributions (respectively) to (b).}
-	\label{fig:doubres_spec}
-\end{figure}
-
-%These results also make DR-HDFG a type of resonance IR spectroscopy, as introduced by Boyle et al for resonant triple sum frequency generation.\cite{RN491} 
-%However, in the methods described by \autoref{drgamma_alpha_0}, $|e)$ must be accessible through one and two photon transitions from $|g)$.
-%Conversely, the resonance-IR method demonstrated by Boyle et al. only requires one photon transitions between $|g)$ and $|e)$.
-%Systems which provide strict parity selection rules (e.g., benzene) will be useful for assessing the validity of these selection rules and comparing the method described here and that of Boyle et al.
-\cite{RN491}
-
-An unavoidable consequence in electronic spectroscopy is broadened lineshapes due to the inhomogeneity of electronic transitions (e.g., vibronic sidebands, molecular collisions). 
-Four wave mixing methods can line-narrow transitions, i.e., resolve inhomogeneous broadening.\cite{Carlson1990line}
-The line-narrowing properties of DR-HDFG are investigated so that the pathways which line-narrow correlated or anti-correlated modes (\textit{vide infra}) can be identified.
-Singly resonant HDFG cannot linenarrow transitions. \cite{RN352}
-
-In the discussion that follows, we assume that a vibrational mode in the ground state, $\ket{g,v}$, is correlated to the frequency of a vibronic $\ket{e,v}$.\cite{Carlson1990}
-If the frequency of $\ket{g,v}$ is written as $\omega_{gv} + \xi$, where $\xi$ is some external strain (e.g.
-molecular collisions), then the frequency of $\ket{e,v}$ is $\omega_{ev} + c\xi$, where c is a shift coefficient.
-Similarly, we take the frequency of $\ket{e,0}$ as $\omega_{e0} \rightarrow \omega_{e0} + \xi$.
-The strains shift resonance denominators, e.g., for $\omega_{ij} \rightarrow \omega_{ij} + c\xi$, as
-\begin{equation}
-	\Delta_{ij}(\xi) = \omega_{ij} + c\xi -\omega_k - i\Gamma_{ij} \equiv \Delta_{ij}(0) + c\xi
-\end{equation}
-Without loss of generality, we assume c = 1 for correlated modes and c = -1 for anti-correlated modes.
-To understand the impact of inhomogeneity on spectral output, we convolute an output density matrix element $\rho_{ab}(\xi)$ with a normalized Lorentzian distribution $P(\xi)$ of half width at half maximum $\sigma$ as
-\begin{equation}\label{contour}
-	\rho_{ab} = \int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \rho_{ab}(\xi)
-\end{equation} 
-While Gaussian distributions are used to describe inhomogeneous broadening,\cite{druet1979line, RN307, Ouellette1982} Lorentzian distributions have satisfactorily described inhomogeneous broadening in a variety of nonlinear spectroscopies and yield easily interpreted closed-form solutions to \autoref{contour}.
-\cite{Penner1976, Desiderio1979, Dick83_1, Carlson1990line}
-For clarity, we evaluate the linenarrowing characteristics of pathway Ia (\autoref{fig:doubsive}) in detail in Appendix.
-The results for all pathways in \autoref{fig:doubsive} are summarized in \autoref{T:correlated}.
-
-\begin{table}[!htbp]
-	\caption{\label{T:correlated} Line narrowing capabilities of pathways outlined in \autoref{fig:doubsive} for correlated and anti-correlated modes, as evaluated through \autoref{contour}, assuming no population feeding or saturation effects.}
-	\begin{ruledtabular}
-		\begin{tabular}{ccc}
-			Pathway & Correlated & Anti-Correlated\\
-			\hline  
-			I-a & Yes & No \\
-			I-b & No & Yes\\
-			II-a & No & Yes\\
-			II-a & No & Yes\\
-		\end{tabular}
-	\end{ruledtabular}
-\end{table}
-
-Although \autoref{T:correlated} identifies that only Pathway I-a can line-narrow correlated modes, these results are only valid in limits where the input pulses only weakly populate excited states.
-When resonant pulses are significantly longer than the dephasing rate of some state, then that state can become populated.
-A typical electronic dephasing rate is tens of femtoseconds. \cite{RN131}
-Excited state population effects become important for understanding the spectroscopy of electronic states when using input pulses with relatively long pulsewidths ($\gtrsim$ 500 fs).
-\cite{RN319, Yurs2011}
-First seen in fifth order perturbation theory in isotropic media ($\chi^{(5)}$ processes), excited state populations can populate other modes, including the ground state and other vibrational/vibronic modes, inducing higher order processes.\cite{Carlson87, RN471}
-These feeding mechanisms can induce line-narrowing properties in spectroscopies that cannot line-narrow in third order perturbation theory.\cite{Ouellette1982, RN319, Carlson87, RN471, RN410}
-Excited state populations become important when considering experiments using the methods in \autoref{fig:doubsive} with long pulsewidths or strong transition dipoles, as demonstrated on a variety of model systems using coherent Raman spectroscopies.
-\cite{Ouellette1982, RN471, RN338, Yurs2011}
+\subsection{Comparison to 2DEV and 2DVE spectroscopy}
+Compare James' stuff and make connections.
 
@@
 The WMEL diagrams presented in \autoref{fig:sivewmel} outline resonant HDFG processes when the infrared pulse $(\omega_1)$ is resonant with a vibrational mode. 
-However, if $\omega_2$ becomes resonant and $\omega_1$ is non-resonant, then other HDFG pathways appear.\cite{McDonnell2024} 
+However, if $\omega_2$ ($\omega_1$) becomes resonant (non-resonant), then other HDFG pathways appear.\cite{McDonnell2024} 
 While the methods in \autoref{fig:sivewmel2} possess identical selection rules to \autoref{fig:sivewmel}, the WMEL diagrams presented in \autoref{fig:sivewmel2} may significantly interfere with DOVE-IR and DOVE-Raman spectra.
@@
 	\caption{Wave Mixing Energy Level (WMEL) diagrams of interfering hyper-DFG pathways in the  $\vec{k}_4 = -\vec{k}_1 + \vec{k}_2 + \vec{k}_3$ phasematching geometry. 
-		(a) is similar to the process diagrammed in \autoref{fig:sivewmel}, whereas (b) is similar to a singly resonant coherent anti-Stokes Raman-type process.}
+		(a) is similar to the process diagrammed in \autoref{fig:sivewmel}, whereas (b) is similar to a singly resonant coherent anti-Stokes Raman-type process.
+		%todo: add pump-SIVE-probe to this set of WMELs
+		}
 	\label{fig:sivewmel2}
@@
 
-\section{Appendix A: Evaluation of DR-SIVE Pathway I-a Linenarrowing Capability}
-\begin{widetext}
-The output coherence  for this pathway is $\rho_{ev',gv}(\xi)$.
-Setting $\eta$ equal to the numerator of \autoref{drgamma_alpha_0} along with any constants, we see
-\begin{equation}\label{ev'gv}
-	\begin{split}
-		\rho_{ev',gv}(\xi) &= \frac{\eta}{\Delta_{g0,gv}(\xi) \Delta_{ev',gv}(c\xi)}\\
-		&=  \frac{\eta}{(-\omega_{g0,gv} - \xi + \omega_1 - i\Gamma_{g0,gv})(\omega_{ev',gv} + c\xi - (2\omega_3 + \omega_1) - i\Gamma_{ev',gv})}\\ 
-		&= \frac{\eta}{(\Delta_{g0,gv}(0) - \xi)(\Delta_{ev',gv}(0) + c\xi)}\\ 
-	\end{split}
-\end{equation}
-
-For notational convenience, we map $\ket{g,0} \rightarrow \ket{g}$, $\ket{g,v} \rightarrow \ket{a}$ and $\ket{e,v'} \rightarrow \ket{b}$.
-Substituting into \autoref{contour} and taking $P(\xi)$ to be a normalized Lorentzian distribution of half width at half maximum $\sigma$, we see:
-\begin{equation}\label{integraly}
-	\begin{split}
-		\rho_{ba} &= \int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \rho_{ba}(\xi)\\
-		&= \int_{-\infty}^\infty \mathrm{d}\xi \frac{\sigma}{\pi} \frac{1}{\xi^2 + \sigma^2} \eta \frac{1}{\Delta_{ga}(0) - \xi} \frac{1}{\Delta_{ba}(0) + c\xi}\\
-		&= \frac{\eta \sigma}{\pi} \int_{-\infty}^\infty \mathrm{d}\xi\frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga}(0) - \xi} \frac{1}{\Delta_{ba}(0) + c\xi}\\
-	\end{split}
-\end{equation}
-
-\begin{figure}[!htbp]
-	\centering
-	\includegraphics[width=3.375in]{corr_contour.png}
-	\caption{Poles (black dots) and contour (blue line) used to evaluate \autoref{integraly} for (a) anti-correlated and (b) correlated modes.} 
-	\label{fig:contours}
-\end{figure}
-
-\subsubsection{Anti-correlated Modes}
-For anti-correlated modes, the poles are situated in the complex plane as shown in \autoref{fig:contours}a.
-Since \autoref{integraly} is evaluated along the real axis, one can choose to evaluate the contour in the upper or lower half of the complex plane.
-Since evaluating the residues in the upper or lower half of the complex plane yields the same result for \autoref{integraly}, we choose the contour which wraps around the least number of poles.
-
-It is clear for c = -1 that there are four poles: $\pm i \sigma, \Delta_{ga}(0), \Delta_{ba}(0)$. 
-Following \autoref{fig:contours}, the contour that wraps the upper half of the complex plane has only one pole, $i \sigma$; as such, we choose to evaluate \autoref{integraly} in the upper half of the complex plane for the case of anti-correlated modes through the residue theorem as
-	\begin{equation}
-		\begin{split}
-			\rho_{ba} = \int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \rho_{ba}(\xi) &= 2\pi i \sum_k \lim_{\xi \rightarrow \xi_k} P(\xi) \rho_{ba}(\xi) (\xi - \xi_k)\\
-			&= 2\pi i \frac{\eta \sigma}{\pi} \lim_{\xi \rightarrow i\sigma} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga}(0) - \xi} \frac{1}{\Delta_{ba}(0) - \xi} (\xi - i \sigma)\\
-			&= 2\eta \sigma i \frac{1}{2i\sigma} \frac{1}{\Delta_{ga}(0) - i\sigma} \frac{1}{\Delta_{ba}(0) - i\sigma}\\
-			&= \frac{\eta}{\Delta_{ga}(i\sigma)\Delta_{ba}(i \sigma)}\\
-		\end{split}
-	\end{equation}
-
-In words, we see the inhomogeneous envelope width $\sigma$ is added to the linewidth of each resonance (e.g., $\Gamma_{ba} \rightarrow \Gamma_{ba} + \sigma$).
-Therefore, pathway I-a cannot linenarrow anti-correlated modes. 
-\subsubsection{Correlated Modes}
-For correlated modes, the poles are situated in the complex plane as shown in \autoref{fig:contours}b.
-It is clear that no matter which contour is chosen, there is a contribution to the final integral from either $\Delta_{ba}(0)$ or $\Delta_{ga}(0)$. 
-For the below calculation, we choose to evaluate along the contour in the bottom half of the complex plane, i.e., the poles ($\xi_k$) are $-i\sigma, \Delta_{ga}$.
-We stress that since the integral is evaluated over $\mathbb{R}$ and there are no degenerate poles, the results below can be obtained by evaluating the contour which wraps around the poles $i\sigma, \Delta_{ba}$ using the Residue theorem as
-
-	\begin{equation}
-		\begin{split}
-			\int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \rho_{ba}(\xi) &= 2\pi i \sum_k \lim_{\xi \rightarrow \xi_k} P(\xi) \rho_{ba}(\xi) (\xi - \xi_k)\\
-			&= 2\pi i \frac{\eta \sigma}{\pi} ( \lim_{\xi \rightarrow -i\sigma} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga}(0) - \xi} \frac{1}{\Delta_{ba}(0) - \xi} (\xi + i \sigma) \\ &+
-			\lim_{\xi \rightarrow \Delta_{ga}(0)} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga}(0) - \xi} \frac{1}{\Delta_{ba}(0) - \xi} (\xi - \Delta_{ga}))\\
-%			&= 2 \eta i \sigma (\frac{1}{2 i \sigma} \frac{1}{-i \sigma - \Delta_{ga}(0)} \frac{1}{\Delta_{ba}(0) - i\sigma} ) - 2 \eta i \sigma (\frac{1}{\sigma^2 + (\Delta_{ga} (0))^2} \frac{1}{\Delta_{ga}(0) + \Delta_{ba}(0)} )\\
-			&= -\frac{\eta}{\Delta_{ga}(0) + i \sigma} (\frac{1}{\Delta_{ba}(0) - i \sigma} + \frac{2i\sigma}{(\Delta_{ga}(0) - i \sigma)(\Delta_{ga}(0) + \Delta_{ba}(0))})\\
-		\end{split}
-	\end{equation}
-The final line of the above equation shows the presence of a new term, $\frac{2i\sigma}{\Delta_{ga}(0) + \Delta_{ba}(0)}$. 
-This term is amplified by the width of the inhomogeneous envelope ($\sigma$) and has a linewidth $\Gamma_{ba} + \Gamma_{ga}$, which linenarrows the transition. 
-Results for the other pathways follow the same technique.
-\end{widetext}
-%Generally, when starting from the ground state, non-parametric spectroscopies line-narrow correlated modes, and parametric spectroscopies line-narrow anti-correlated modes. \cite{Dick83_1, RN425}
-
 \section{References}
@@
 %
-% ****** End of file apstemplate.tex ******

### 2024-07-08 paper.tex
wip
added more on abcs but need to do vibronic coupling still

@@
 	\centering
-	\includegraphics[width=3.375in]{dfg_hdfg_hr_wmel.png}
-	\caption{Wave Mixing Energy Level (WMEL) diagrams of difference frequency generation (DFG), hyper difference frequency generation (HDFG) and spontaneous hyper-Raman scattering. \cite{RN286, RN352}
+	\includegraphics[width=3.375in]{f1.png}
+	\caption{Wave Mixing Energy Level (WMEL) diagrams of difference frequency generation (DFG), spontaneous Raman scattering, hyper difference frequency generation (HDFG) and spontaneous hyper-Raman scattering.
+\cite{RN286, RN352}
 		$\ket{g}$ is the ground state, $\ket{v}$ is an infrared active vibration and $\ket{m}, \ket{n}$ are virtual states.
@@
 The different selection rules of hyper-Raman scattering, however, make it a unique alternative to Raman scattering to understand vibrational spectra and vibronic coupling in molecular systems.
-In 1998, Cho et al. proposed a parametric six wave mixing technique which was the coherent analogue of hyper-Raman scattering. \cite{Cho1998}
-However, since most six wave mixing methods cascade into four wave mixing processes,\cite{RN243, Cho2000_Cascade} it is preferable to investigate coherent four wave mixing analogues to hyper-Raman scattering.
+Some years ago, Cho et al. proposed parametric six wave mixing techniques as the coherent analogue of hyper-Raman scattering. \cite{Cho1997, Cho1998}
+However, since most six wave mixing methods cascade into four wave mixing processes,\cite{RN243, Cho2000_Cascade}, and their output would be dependent upon the square magnitude of the hyper-Raman scattering cross section, a small number,\cite{RN515} it is preferable to investigate coherent four wave mixing analogues to hyper-Raman scattering.
 
@@
 \cite{RN345, RN101, Cho2000}
-As a result, investigations of hyper-DFG stagnated; to date, there are less than a dozen studies which report on hyper-DFG.
+As a result, investigations of hyper-DFG stagnated; to date`Z, there are less than a dozen studies which report on hyper-DFG.
 \cite{RN350, RN416, RN351, RN352, RN353, Chen1998, RN362, RN418, Bonn2024, McDonnell2024}
@@
 
-\begin{figure}[!htbp]
-	\centering
-	\includegraphics[width=3.375in]{wmel1.png}
-	\caption{Wave Mixing Energy Level (WMEL) diagrams of the relevant HDFG pathways in the (a) $\vec{k}_4 = -\vec{k}_1 + \vec{k}_2 + \vec{k}_3$ and (b) $\vec{k}_4 = \vec{k}_1 + \vec{k}_2 + \vec{k}_3$ phasematching geometries.
-\cite{RN286, RN352}
-	$\ket{g}$ is the ground state, $\ket{v}$ is an infrared active vibration and $\ket{m}, \ket{n}$ are virtual states.
-	Solid and dashed horizontal lines indicate real and virtual states, whereas solid and dotted arrows indicate ket and bra side transitions, respectively. 
-	These diagrams can be permuted to generate additional resonant WMEL diagrams.}
-	\label{fig:sivewmel}
-\end{figure}
-
 It is useful to expose relationships between transition dipoles, Raman polarizabilities and hyper-Raman polarizabilities in the driven limit. \cite{Simpson2004, RN120}
@@
 \begin{equation}\label{sivegamma}
-		\gamma_{ijkl} =	- \sum_{m, n} \frac{1}{\varepsilon_0} \frac{1}{4D} \frac{1}{\hbar^3} \frac{\mu^{i}_{v n} \mu^{j}_{nm} \mu^{k}_{mg} \mu^{l}_{gv} }{\Delta_{nv} \Delta_{mv}\Delta_{gv}}  \rho_{gg}
+		\gamma_{ijkl} =	- \sum_{m, n} \frac{1}{\varepsilon_0} \frac{1}{4D} \frac{1}{\hbar^3} \frac{\mu^{vn}_{i} \mu^{nm}_{j} \mu^{mg}_{k} \mu^{gv}_{l} }{\Delta_{nv} \Delta_{mv}\Delta_{gv}}  \rho_{gg}
 \end{equation}
-where: $\mu^{j}_{ab}$ is the $j^{th}$ element of $\mel{a}{\vec{\mu}}{b}$, $\Delta_{kl} = \omega_{kl} - \omega_{j} - i\Gamma_{kl}$, $\omega_j$ is the frequency of the j$^{th}$ input field, $\Gamma_{kl}$ is the dephasing of $\rho_{kl}$ and $\rho_{gg}$ is the ground state population.
-For simplicity, we consider the results for the process diagrammed in \autoref{fig:sivewmel}a, but by multiplying by (-1) and taking a complex conjugate, which arise from the bra-side transition in \autoref{fig:sivewmel}a, results for the \autoref{fig:sivewmel}b  process are obtained.
-Note that $\omega_j \rightarrow -\omega_j$ for a bra side transition.
-D, the Maker-Terhune degeneracy factor, accounts for permutation symmetry in $\gamma_{ijkl}$ and is defined as $\frac{n!}{(n-m)!}$, where $n$ is the total number of input fields (3 for any four wave mixing experiment) and $m$ is the number of distinguishable input fields.\cite{RN134}
+where: $\mu^{ab}_{j}$ is the $j^{th}$ element of $\mel{a}{\vec{\mu}}{b}$, $\Delta_{kl} = \omega_{kl} - \omega_{j} - i\Gamma_{kl}$, $\omega_j$ is the frequency of the j$^{th}$ input field, $\Gamma_{kl}$ is the dephasing of $\rho_{kl}$ and $\rho_{gg}$ is the ground state population.
+D, the Maker-Terhune degeneracy factor, accounts for permutation symmetry in $\gamma_{ijkl}$.\cite{RN134} 
 For a HDFG experiment using two or three distinct input fields, as considered here, D = 6.
 Note that $\ket{m}, \ket{n}$ are virtual states (\autoref{fig:sivewmel}).
-By contracting over the virtual states to form the hyper-Raman hyperpolarizability $\beta$ (i.e., Placzek approximation), this expression can be simplified immensely.\cite{Long1970} 
-Note, however, that if $\omega_2$, $\omega_3$, as depicted in \autoref{fig:sivewmel}, are nearly resonant with any state, the Placzek approximation fails. \cite{Placzek1934, Long1970}
-Assuming the validity of the Placzek approximation, \autoref{sivegamma} is written as 
+By contracting over the virtual states to form the hyper-Raman hyperpolarizability $\beta$, this expression can be simplified immensely.\cite{Long1970} 
+Note, however, that if $\omega_2$, $\omega_3$, as depicted in \autoref{fig:comparisonwmel}, are nearly resonant with any state, the contraction is not allowed. \cite{Placzek1934, Long1970}
+Assuming $\omega_2$, $\omega_3$ are significantly detuned from any local resonance, \autoref{sivegamma} is written as 
 \begin{equation}\label{sivebeta}
-	\gamma_{ijkl} =	-\frac{1}{\varepsilon_0} \frac{1}{24 \hbar}\frac{\beta^{(ijk)}_{gv} \mu^{(l)}_{gv}}{\Delta_{gv}} \rho_{gg}
+	\gamma_{ijkl} =	-\frac{1}{\varepsilon_0} \frac{1}{24 \hbar}\frac{\beta^{gv}_{ijk} \mu^{gv}_{l}}{\Delta_{gv}} \rho_{gg}
 \end{equation}
@@
 \end{subequations}
-Substituting into \autoref{sivebeta}, and knowing that $\mel{v}{Q_n}{g} = \sqrt{\frac{\hbar}{2m_n\omega_{vg}}}$ under the harmonic approximation,\cite{RN230} where $m_n$ is the mass of the $Q_n$ mode, gives the HDFG hyperpolarizability to $\order{Q_n}$ as \begin{equation}\label{SIVEselection}
-	\gamma_{ijkl} =	-\frac{1}{\varepsilon_0} \frac{1}{48 m_n \omega_{vg}}  \frac{1}{{\Delta_{gv}}} \ \frac{\partial \beta^{(ijk)}}{\partial Q_n} {\frac{\partial \mu^{(l)}}{\partial Q_n}}  \rho_{gg}
+Substituting into \autoref{sivebeta} gives the HDFG hyperpolarizability to $\order{Q_n}$ as \begin{equation}\label{SIVEselection}
+	\gamma_{ijkl} =	-\frac{1}{\varepsilon_0} \frac{1}{48 m_n \omega_{vg}}  \frac{1}{{\Delta_{gv}}} \ \frac{\partial \beta^{gv}_{ijk}}{\partial Q_n} {\frac{\partial \mu^{gv}_{l}}{\partial Q_n}}  \rho_{gg}
 \end{equation}
+where $\mel{v}{Q_n}{g} = \sqrt{\frac{\hbar}{2m_n\omega_{vg}}}$ under the harmonic approximation,\cite{RN230} and $m_n$ is the ``mass'' of the $Q_n$ mode. 
 Since this expression is non-zero in the harmonic oscillator limit, HDFG output is allowed for harmonic transitions. 
 Similar to SFG, HDFG does not demand anharmonic ground state potential energy surfaces for spectral output. \cite{Shen94, Cho2000}
-This selection rule is generally valid for any HDFG or hyper sum frequency generation (HSFG) process in the $-\vec{k}_1 + \vec{k}_2  + \vec{k}_3$ and $\vec{k}_1 + \vec{k}_2  + \vec{k}_3$ phasematching geometries when the Placzek approximation is valid.
+This selection rule is generally valid for any HDFG or hyper sum frequency generation (HSFG) process in the $-\vec{k}_1 + \vec{k}_2  + \vec{k}_3$ and $\vec{k}_1 + \vec{k}_2  + \vec{k}_3$ phasematching geometries when $\omega_2$ and $\omega_3$ are sufficiently detuned from any resonance.
 
-\autoref{SIVEselection} shows any HDFG active mode must be both hyper-Raman and IR active.
-However, since any IR active vibrational mode is hyper-Raman active,\cite{Cyvin1965, Andrews1978} any IR active mode is HDFG active.
-This makes HDFG an optically upconverted infrared spectroscopy of isotropic samples, as its selection rules are identically those of IR spectroscopy, but its output is generally in the visible.
-A useful attribute of the $\beta_{ijk}$ dependence in HDFG output is added polarization control. 
-Similar to SHG and SFG experiments that probe different elements of the infrared transition dipole and Raman polarizability tensors,\cite{Heinz1982} probing different elements of $\beta_{ijk}$ in HDFG can greatly assist in understanding ultrafast dynamics in isotropic systems, as suggested by Seliya et al.
-\cite{Shen90, Bonn2024}
-Polarization control in IR-pump-HDFG-probe, analogous to ultrafast transient absorption spectroscopy for vibrational modes, would be an interesting venue to assess the sensitivity of HDFG to different hyper-Raman tensor elements.
+So far, only Placzek approximation type arguments have been used to interpret HDFG output.
+Previous spontaneous hyper-Raman work interpreted the origin of hyper-Raman signal in terms of Franck-Condon, Herzberg-Teller and Duschinsky type couplings.\cite{Ziegler1988} 
+As such, we extend \autoref{SIVEselection} using an Albrecht ABC type formalism to account for these couplings.
+The formalism will first be developed for singly resonant HDFG, but extension to doubly resonant HDFG is straightforward and will be discussed later.
 
-Previous spontaneous hyper-Raman work interpreted the origin of hyper-Raman signal in terms of Franck-Condon, Herzberg-Teller and Duschinsky type couplings.\cite{Ziegler1988} %todo: cite the other papers.
-As such, we investigate \autoref{SIVEselection} using an Albrecht ABC type formalism which naturally incorporates these types of couplings.
-To do so, we write the states in terms of a Born-Oppenheimer basis $\ket{a,b}$, where $\ket{a,b} = |a) \otimes \ket{b}$ for electronic states $\{|a)\}$ and vibrational states $\{\ket{b}\}$.
+To employ the Albrecht formalism, we write the states in terms of a Born-Oppenheimer basis $\ket{a,b}$, where $\ket{a,b} = |a) \otimes \ket{b}$ for electronic states $\{|a)\}$ and vibrational states $\{\ket{b}\}$.
 \cite{BornOppenheimer, Albrecht1960}
-Here, $\ket{g}, \ket{v}$ are vibrational states on the ground electronic state $|g)$ and $\ket{m} \rightarrow \ket{m,j}$, $\ket{n} \rightarrow \ket{n,k}$ are virtual states.
-For consistency with previous reports, we use $\vec{R}$ to denote electric transition dipole moments ($\vec{\mu}$ is used for transitions between states on the ground electronic state.).
+For simplicity, we choose $\ket{g}, \ket{v}$ to be vibrational states on the ground electronic state $|g)$ and $\ket{m} \rightarrow \ket{m,j}$, $\ket{n} \rightarrow \ket{n,k}$ are virtual states.
+For consistency with previous reports, we use $\vec{R}$ to denote electric transition dipole moments ($\vec{\mu}$ is reserved for transitions between states on the ground electronic state).
 \cite{Ziegler1974}
@@
 	\gamma_{ijkl} = -\frac{1}{\varepsilon_0} \frac{1}{24 \hbar^3} \sum_{m,n,j,k} \frac{
-		R^{i}_{gv, nk} 
-		R^{j}_{nk,mj} 
-		R^{k}_{mj,gg} 
-		R^{l}_{gv,gg} 
+		R_{i}^{gv, nk} 
+		R_{j}^{nk,mj} 
+		R_{k}^{mj,gg} 
+		R_{l}^{gv,gg} 
 	}{\Delta_{g0,gg}
@@
 \end{equation}
-where $R^{i}_{ab,cd}$ is the i$^{th}$ element of $\mel{a,b}{\vec{R}}{c,d}$.\cite{Ziegler1988}
-Using our definition of vibronic states, we write $\vec{M}_{ab} = (a|\vec{M}|b)$ so that, for example,
-$R^{i}_{gv,ev'} = \mel{v}{M^i_{ge}}{v'}$.\cite{Albrecht1960}
+where $R_{i}^{ab,cd}$ is the i$^{th}$ element of $\mel{a,b}{\vec{R}}{c,d}$.\cite{Ziegler1988}
+Using our definition of vibronic states, we write $\vec{M}^{ab} = (a|\vec{M}|b)$ so that, for example,
+$R_{i}^{gv,ev'} = \mel{v}{M_i^{ge}}{v'}$.\cite{Albrecht1960}
 Using these ideas rewrites \autoref{drgamma_notaylor} as
@@
 		\gamma_{ijkl} &= -\frac{1}{\varepsilon_0} \frac{1}{24 \hbar^3} \sum_{m,n,v'} \frac{
-			\mel{v}{M^{i}_{ge}}{v'} 
-			\mel{v'}{M^{j}_{em}}{n}
-			\mel{n}{M^{k}_{mg} }{v}
-			\mel{v}{M^{l}_{gg}}{0}
+			\mel{v}{M_{i}^{ge}}{v'} 
+			\mel{v'}{M_{j}^{em}}{n}
+			\mel{n}{M_{k}^{mg} }{v}
+			\mel{v}{M_{l}^{gg}}{0}
 		}{\Delta_{g0,gv}
@@
 			\Delta_{mn, g0}	} \\
+%	&= 	-\frac{1}{\varepsilon_0} \frac{1}{24 \hbar^3} \sum_{m,n,v'} \frac{
+%		\mel{v}{M_{i}^{ge}}{v'} 
+%		\mel{v'}{M_{j}^{em}}{n}
+%		\mel{n}{M_{k}^{mg} }{v}
+%		\mel{v}{\mu_{l}}{0}
+%	}{\Delta_{g0,gv}
+%		\Delta_{ev', mn}
+%		\Delta_{mn, g0}	} \\
 	\end{split}
 \end{equation}
-Chung and Ziegler showed some years ago that expanding ${\vec{M}_{ij}}$ to $\order{Q}$ yields $A, B, C$ coefficients similar to the Albrecht formalism of Raman scattering.
-\cite{Albrecht1961, Ziegler1988}
-The $A$ term depends upon Franck-Condon $\order{Q^0}$ transitions, the $B$ term depends upon Herzberg-Teller ($\order{Q}$) transitions, and the $C$ term depends on Duschinsky ($\order{Q^2}$) transitions.
+Chung and Ziegler showed some years ago that expanding $\vec{M}^{ij}$ to $\order{Q}$ as
+\begin{equation}
+\vec{M}^{ij} = \vec{M}^{ij}_0 + \sum_z \frac{\partial\vec{M}^{ij}}{\partial Q_z}
+\end{equation} yields $A, B, C$ coefficients similar to those in the Albrecht formalism of Raman scattering. \cite{Albrecht1961, Ziegler1988}
+The $A$ term depends upon Franck-Condon ($\order{Q^0}$) transitions, the $B$ term depends upon Herzberg-Teller ($\order{Q}$) transitions, and the $C$ term depends on Duschinsky ($\order{Q^2}$) transitions.
 Here, we ignore the C term as it depends on one and two photon forbidden transitions which have yet to be observed in spontaneous hyper-Raman scattering. \cite{Ziegler1988}
 The full derivation of $A,B$ have been given elsewhere, so only their final forms will be given.
+In the discussion that follows, we take $\hbar = e = 1$ for simplicity.
 
-By compiling all the terms that scale with $\order{Q^0}$, i.e. $\vec{M}_{ij_0}$, $A$ is written as
+By compiling all the terms that scale with $\order{Q^0}$, i.e. $\vec{M}^{ij}_0$, $A$ is written as
 \begin{equation}
 	\begin{split}
-		A_{ijk} &= \text{crap times Franck Condon}\\
+		A_{ijk} = \sum_{m,n,j,k} M^{gn}_{0,i} 
+		M^{nm}_{0,j} 
+		M^{mg}_{0,k}
+		 \langle v | k \rangle
+		 \langle k | j \rangle
+		 \langle j | g \rangle \\
 	\end{split}
 \end{equation}
-where terms such as $\langle v | v' \rangle$ are Franck-Condon factors.
-
-something about the A term. SHOW THAT IT VANISHES FOR SINGLY RES TERMS
-
-It is important to note that in the case of singly resonant HDFG, $A_{ijk}$ vanishes, or only Herzberg-Teller contributions are present in SR-HDFG. \cite{Neddersen1989}
-
-Similarly, the $B$ terms scale with $\order{Q}$, such that
+and $B$ is written as a sum of two terms, $B_1, B_2$, as
+\begin{subequations}
 	\begin{equation}
 		\begin{split}
-		B_{ijk} &= \text{crap}\\
+			B_{1_{ijk}} &= \sum_{m,n,j,k,z} M^{gn}_{0,i} \langle v | k \rangle \lbrack
+			 \frac{\partial M^{nm}_{j}}{\partial Q_z} \mel{k}{Q_z}{j} M^{mg}_{0,k} \langle j | g \rangle
+			+M^{nm}_{0,j} \langle k | j \rangle \frac{\partial M^{mg}_{k}}{\partial Q_z} \mel{j}{Q_z}{g} \rbrack \\
 		\end{split}
 	\end{equation}
-Then B term. 
-B term has new sum over another normal mode Ql that must be included because when I expand in terms of Q there are 3N-6-1 normal modes I can talk to (3N-6-1, assuming nonlinear and that the -1 comes from assuming we end in v)
-Blah Blah Blah
-%todo: So clearly HDFG has heavy dependence on HT type couplings! 
-%This likely explains the relative weakness of HDFG in solvents such as hexane. \cite{RN351}
-%fix the equation so that the dipole is clearly isolated from the hyper Raman part. Write beta as A+B+C?
-%todo: segue into vibronic coupling
-
-While HDFG can provide useful information about the properties of molecular vibrations, it is immediately apparent that \autoref{fig:sivewmel} can inform on molecular electronic structure by making the hyper-Raman transition resonant with a vibronic state.
+	\begin{equation}
+	\begin{split}
+			B_{2_{ijk}} = \sum_{m,n,j,k,z} \frac{\partial M^{gn}_{i}}{\partial Q_z} \mel{v}{Q_z}{k} M^{nm}_{0,j} 
+			M^{mg}_{0,k}
+			\langle k | j \rangle
+			\langle j | g \rangle
+	\end{split}
+	\end{equation}
+\end{subequations}
+where terms such as $\langle a | b \rangle$ are Franck-Condon factors and $\mel{a}{Q_z}{b}$ are Herzberg-Teller coupling factors. %include parameterization of the states?
+When $\omega_2$ and $\omega_3$ are nonresonant, the resonance denominators lose their dependence on the vibrational quantum number and the sum can be contracted over ${j, k}$. 
+Assuming a normal mode basis, this takes $\sum_{j,k}\langle v | k \rangle \langle k | j \rangle \langle j | g \rangle = \delta_{vg} = 0$, or, A$_{ijk}$ vanishes for singly resonant HDFG.
+\cite{Neddersen1989}
+The B terms do not suffer from this problem.
+The Herzberg-Teller matrix elements, where $Q_z$ is a normal mode of the system which is not $\ket{g}$ or $\ket{v}$, allows for coupling between different terms that result in non-zero B terms.
+As a result, singly resonant HDFG has significant dependence upon those modes which participate in Herzberg-Teller coupling. 
+This likely explains the relative weakness of HDFG in solvents such as hexane. \cite{RN351}
+The singly resonant HDFG response can then be approximated as
+\begin{equation}
+	\gamma_{ijkl} \sim B_{ijk} \mu_l
+\end{equation}
+or, while a vibrational mode must be infrared active for HDFG output, it must also significantly participate in vibronic coupling, i.e., large B values are a necessity for singly resonant HDFG response.
+\subsection{Doubly Resonant}
+While HDFG can provide useful information about the properties of molecular vibrations, it is apparent that HDFG can inform on molecular electronic structure by making the hyper-Raman transition resonant with a vibronic state.
 DR-HDFG (where a vibrational and vibronic state are resonantly coupled) can provide a tool for measuring vibronic coupling.
@@
 Many multi-resonant nonlinear spectroscopies have been developed to resolve vibronic coupling in molecular samples. \cite{Carlson1990, Gaynor2017, RN276}
-DR-HDFG provides methods to investigate vibronic coupling with only two laser pulses, as long as the electronic state is accessible via two photon absorption from the ground state (\textit{vide infra}).
+DR-HDFG provides methods to investigate vibronic coupling with only two laser pulses.
 Two beam, parametric and non-parametric DR-HDFG processes are diagrammed in \autoref{fig:doubsive}.
-%todo: insert discussion on ABC terms
+
+\begin{figure}[!htbp]
+	\centering
+	\includegraphics[width=3.375in]{wmel3.png}
+	\caption{WMEL diagrams of some (I-a,I-b) DR-HDFG and (II-a,II-b) DR-HSFG pathways.
+$\ket{g,0}$ denotes the ground states, $\ket{g,v}$ denotes a vibrational state on the ground electronic manifold; $\ket{m,n}$ denotes a virtual state, and $\ket{e,0}, \ket{e,v'}$ denote vibronic states.}
+	\label{fig:doubsive}
+\end{figure}
+
+To explicitly incorporate vibronic coupling into the selection reules for DR-HDFG, we consider
+
 %todo: write hamiltonian like Gaynor to make clear what we are doing (and put in a picture in Figure doubbleresspec)
-
 To interpret HDFG selection rules, we use a slightly modified version of equation xyz to account for the added vibronic resonance. 
@@
 \subsection{Quantification}
+
 Since the hyper-Raman process is stimulated by a two-photon process, a setup using only two lasers can perform a coherent four wave mixing hyper-Raman experiment by investigating $\pm \vec{k}_1 + 2\vec{k}_2$ processes, assuming a two photon absorption from a single pulse stimulates the hyper-Raman process.
@@
 With the selection rules of HDFG understood for vibrational spectroscopy, it becomes possible to extract quantitative information from its spectra.
+A useful attribute of the $\beta_{ijk}$ dependence in HDFG output is added polarization control. 
+Similar to SFG experiments that probe different elements of the infrared transition dipole and Raman polarizability tensors, probing different elements of $\beta_{ijk}$ in HDFG can greatly assist in understanding ultrafast dynamics in isotropic systems, as suggested by Seliya et al.
+\cite{Shen90, RN224, Bonn2024}
+Polarization control in IR-pump-HDFG-probe, analogous to ultrafast transient absorption spectroscopy for vibrational modes, would be an interesting venue to assess the sensitivity of HDFG to different hyper-Raman tensor elements.
+
 Lineshape analysis is essential for extracting quantitative information from CMDS spectra.
@@
 This expression cannot be used as written to extract $\beta_{ijk}$, as $\beta_{ijk}$ is a Hermitian operator, but $\Delta_{gv} \in \mathbb{C}$. 
-However, since the real and imaginary parts of $\chi^{(3)}$ can be extracted from the Bloembergen interferometry experiment, and $\beta_{ijk}$ is present in either term, we can choose to focus on the real or imaginary part of $\chi^{(3)}$.
+However, since the real and imaginary components of $\chi^{(3)}$ can be extracted from the Bloembergen interferometry experiment, and $\beta_{ijk}$ is present in either term, we can choose to focus on the real or imaginary part of $\chi^{(3)}$.
 For simplicity, we investigate $\Im(\chi^{(3)})$, giving, assuming resonance conditions, 
@@
 HDFG and vSFG together provide unique methods to extract the microscopic quantities ($\mu, \alpha, \beta$) that drive nonlinear output.
-
-\begin{figure}[!htbp]
-	\centering
-	\includegraphics[width=3.375in]{wmel3.png}
-	\caption{WMEL diagrams of some (I-a,I-b) DR-HDFG and (II-a,II-b) DR-HSFG pathways.
-$\ket{g,0}$ denotes the ground states, $\ket{g,v}$ denotes a vibrational state on the ground electronic manifold; $\ket{m,n}$ denotes a virtual state, and $\ket{e,0}, \ket{e,v'}$ denote vibronic states.}
-	\label{fig:doubsive}
-\end{figure}
 
@@
 
-\section{Experimental Hyper-DFG Results}
+\section{Experimental Hyper-DFG of CH$_3$CN}
 With the theoretical description of HDFG provided, we will investigate steady state and transient HDFG spectra of $\nu$(CH) modes in CH$_3$CN.
+%@dan I choose these modes because easily accessible with df1, but since you have moved to df2 since we can also choose the v(CN) mode$
 
-\subsection{dynamics} 
-Look at coherence dynamics of v(CH), v(CN) in CH3CN. 
-THIS EXPERIMENT IS DEFINITELY EASIER THAN EXTRACTING CHI3.
-
-\subsection{Calculation of $\beta$ for v(CH) modes in CH3CN}
-do the classic C6D6 at CH3CN expt ? (or CaF2, whatever) - get interferogram, fit, get numbers.
-Dipoles of CH3CN fitted by John in the 2003 paper, so only need to get $\beta$. 
-Compare this to the theoretical CH3CN hyper Raman paper.
-We can decide if this is worth it.
+todo: collect Wigner of ch3cn @ caf2.
 

### 2024-07-08 figures/wmels.py

@@ -1,0 +1,118 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Jul  8 10:53:49 2024
+
+@author: rpm
+"""
+
+import matplotlib.pyplot as plt 
+from WrightTools.diagrams import WMEL
+plt.rcParams['figure.dpi'] = 1600
+
+compar = True
+f1 = True
+f2 = True
+f3 = True
+f4 = True
+
+if compar:
+    fig = WMEL.Artist([4,1], [0, 0.2, 0.6, 1], state_names=("$\mathsf{| g\\rangle}$",
+                                                                   "$\mathsf{|v\\rangle}$", 
+                                                                   "$\mathsf{|m\\rangle}$",
+                                                                   "$\mathsf{|n\\rangle}$"), number_of_interactions=5, state_font_size=9, state_text_buffer = 0.6, virtual = [2,3])
+
+
+    fig.add_arrow([0,0], 0, [0,1], kind='bra', color="k", label = "$\mathsf{1}$", head_length = 0.075)
+    fig.add_arrow([0,0], 1, [0,3], kind='ket', color="k", label = "$\mathsf{2}$", head_length = 0.075)
+    fig.add_arrow([0,0], 2, [3,1], kind='out', color="blue", label = "$\mathsf{3}$", head_length = 0.075)
+    
+    fig.add_arrow([1,0], 0, [0,3], kind='bra', color="k", label = "$\mathsf{1}$", head_length = 0.075)
+    fig.add_arrow([1,0], 1, [3,1], kind='bra', color="k", label = "$\mathsf{2}$", head_length = 0.075)
+    fig.add_arrow([1,0], 2, [0,3], kind='ket', color="k", label = "$\mathsf{3}$", head_length = 0.075)    
+    fig.add_arrow([1,0], 3, [3,1], kind='out', color="blue", label = "$\mathsf{4}$", head_length = 0.075)
+
+    fig.add_arrow([2,0], 0, [0,1], kind='bra', color="k", label = "$\mathsf{1}$", head_length = 0.075)
+    fig.add_arrow([2,0], 1, [0,2], kind='ket', color="k", label = "$\mathsf{2}$", head_length = 0.075)
+    fig.add_arrow([2,0], 2, [2,3], kind='ket', color="k", label = "$\mathsf{3}$", head_length = 0.075)
[…]

### 2024-07-09 paper.tex
fixed more in the singly resonant section
need to focus on the doubly res section now (make figures particuarly..)

@@
 Hyper Difference Frequency Generation (HDFG) spectroscopy, also known as singly vibrationally enhanced spectroscopy (SIVE), is an underdeveloped, hyper-Raman based four wave mixing vibrational spectroscopy.
-However, the spectroscopic and dynamic properties of HDFG have not been fully explored.
+The spectroscopic and dynamic properties of HDFG have not been fully explored.
 We derive selection rules for singly resonant hyper-DFG and demonstrate it provides a simpler method to extract hyper-Raman polarizabilities ($\beta$).
@@
 
-\begin{figure}[!htbp]
+\begin{figure*}[!htbp]
 	\centering
-	\includegraphics[width=3.375in]{f1.png}
+	\includegraphics[width=6.66in]{f1.png}
 	\caption{Wave Mixing Energy Level (WMEL) diagrams of difference frequency generation (DFG), spontaneous Raman scattering, hyper difference frequency generation (HDFG) and spontaneous hyper-Raman scattering.
@@
 	\label{fig:comparisonwmel}
-\end{figure}
+\end{figure*}
 
@@
 \vec{M}^{ij} = \vec{M}^{ij}_0 + \sum_z \frac{\partial\vec{M}^{ij}}{\partial Q_z}
-\end{equation} yields $A, B, C$ coefficients similar to those in the Albrecht formalism of Raman scattering. \cite{Albrecht1961, Ziegler1988}
-The $A$ term depends upon Franck-Condon ($\order{Q^0}$) transitions, the $B$ term depends upon Herzberg-Teller ($\order{Q}$) transitions, and the $C$ term depends on Duschinsky ($\order{Q^2}$) transitions.
-Here, we ignore the C term as it depends on one and two photon forbidden transitions which have yet to be observed in spontaneous hyper-Raman scattering. \cite{Ziegler1988}
-The full derivation of $A,B$ have been given elsewhere, so only their final forms will be given.
-In the discussion that follows, we take $\hbar = e = 1$ for simplicity.
+\end{equation} yields $A, B, C$ coefficients similar to those in the Albrecht formalism of Raman scattering, \cite{Albrecht1961, Ziegler1988} so that
+\begin{equation}
+		\gamma_{ijkl} \sim \frac{(A_{ijk} + B_{ijk} + C_{ijk})\mel{v}{\mu_{l}}{0}} {\Delta_{g0,gv}}
+\end{equation}
+The $A$ term depends upon Franck-Condon ($\order{Q^0}$) transitions, the $B$ term depends upon Herzberg-Teller ($\order{Q}$) transitions, and the $C$ term depends on $\order{Q^2}$ transitions. 
+The C term is suppressed in the following discussion as it depends on one and two photon forbidden transitions which have yet to be observed in spontaneous hyper-Raman scattering. \cite{Ziegler1988}
+In the discussion that follows, we take $\hbar = e = 1$.
 
-By compiling all the terms that scale with $\order{Q^0}$, i.e. $\vec{M}^{ij}_0$, $A$ is written as
+By compiling all the terms that scale with $\order{Q^0}$, $A$ is written as
 \begin{equation}
 	\begin{split}
-		A_{ijk} = \sum_{m,n,j,k} M^{gn}_{0,i} 
-		M^{nm}_{0,j} 
-		M^{mg}_{0,k}
+		A_{qrs} = \sum_{m,n,j,k} M^{gn}_{0,q} 
+		M^{nm}_{0,r} 
+		M^{mg}_{0,s}
 		 \langle v | k \rangle
 		 \langle k | j \rangle
-		 \langle j | g \rangle \\
+		 \langle j | g \rangle 
+		 \frac{1}{\Delta_{nk,mj} \Delta_{mj, gg}}
+		 \\
 	\end{split}
 \end{equation}
-and $B$ is written as a sum of two terms, $B_1, B_2$, as
+and by compiling all terms that scale with $\order{Q}$, $B$ is written as $B = B_1 + B_2$,\cite{Bonang1992} where
 \begin{subequations}
@@
 		\begin{split}
-			B_{1_{ijk}} &= \sum_{m,n,j,k,z} M^{gn}_{0,i} \langle v | k \rangle \lbrack
-			 \frac{\partial M^{nm}_{j}}{\partial Q_z} \mel{k}{Q_z}{j} M^{mg}_{0,k} \langle j | g \rangle
-			+M^{nm}_{0,j} \langle k | j \rangle \frac{\partial M^{mg}_{k}}{\partial Q_z} \mel{j}{Q_z}{g} \rbrack \\
+			B_{1_{qrs}} &= \sum_{m,n,j,k,z} M^{gn}_{0,q} \langle v | k \rangle \lbrack
+			 \frac{\partial M^{nm}_{r}}{\partial Q_z} \mel{k}{Q_z}{j} M^{mg}_{0,s} \langle j | g \rangle
+			+M^{nm}_{0,r} \langle k | j \rangle \frac{\partial M^{mg}_{s}}{\partial Q_z} \mel{j}{Q_z}{g} \rbrack \frac{1}{\Delta_{nk,mj} \Delta_{mj, gg}}\\
 		\end{split}
@@
 	\begin{split}
-			B_{2_{ijk}} = \sum_{m,n,j,k,z} \frac{\partial M^{gn}_{i}}{\partial Q_z} \mel{v}{Q_z}{k} M^{nm}_{0,j} 
-			M^{mg}_{0,k}
+			B_{2_{qrs}} = \sum_{m,n,j,k,z} \frac{\partial M^{gn}_{q}}{\partial Q_z} \mel{v}{Q_z}{k} M^{nm}_{0,r} 
+			M^{mg}_{0,s}
 			\langle k | j \rangle
 			\langle j | g \rangle 
+			\frac{1}{\Delta_{nk,mj} \Delta_{mj, gg}}
 	\end{split}
@@
 where terms such as $\langle a | b \rangle$ are Franck-Condon factors and $\mel{a}{Q_z}{b}$ are Herzberg-Teller coupling factors. %include parameterization of the states?
-When $\omega_2$ and $\omega_3$ are nonresonant, the resonance denominators lose their dependence on the vibrational quantum number and the sum can be contracted over ${j, k}$. 
-Assuming a normal mode basis, this takes $\sum_{j,k}\langle v | k \rangle \langle k | j \rangle \langle j | g \rangle = \delta_{vg} = 0$, or, A$_{ijk}$ vanishes for singly resonant HDFG.
+
+When $\omega_2$ and $\omega_3$ are largely detuned from a local resonance, the resonance denominators lose their dependence on vibrational quantum number.
+In the case of the $A$ term, the sum can now be contracted over ${j, k}$. 
+Assuming a normal mode basis, $A_{ijk} \sim \sum_{j,k}\langle v | k \rangle \langle k | j \rangle \langle j | g \rangle = \delta_{vg} = 0$, or, A$_{ijk}$ vanishes for singly resonant HDFG.
 \cite{Neddersen1989}
 The B terms do not suffer from this problem.
-The Herzberg-Teller matrix elements, where $Q_z$ is a normal mode of the system which is not $\ket{g}$ or $\ket{v}$, allows for coupling between different terms that result in non-zero B terms.
+The Herzberg-Teller matrix elements, where $\ket{z} \neq \{\ket{g}, \ket{v}\}$ is a normal mode, allows for non-zero B terms.
 As a result, singly resonant HDFG has significant dependence upon those modes which participate in Herzberg-Teller coupling. 
-This likely explains the relative weakness of HDFG in solvents such as hexane. \cite{RN351}
-The singly resonant HDFG response can then be approximated as
+This likely explains the relative weakness of HDFG response from hexane $\nu$(CH) modes. \cite{RN351}
+The singly resonant HDFG susceptibility can then be approximated as
 \begin{equation}
-	\gamma_{ijkl} \sim B_{ijk} \mu_l
+	\chi^{(3)}_{IJKL} \sim \langle B_{ijk} \mu_l \rangle
 \end{equation}
-or, while a vibrational mode must be infrared active for HDFG output, it must also significantly participate in vibronic coupling, i.e., large B values are a necessity for singly resonant HDFG response.
+or, while a vibrational mode must be infrared active for HDFG output, large $B$ values are a necessity for singly resonant HDFG response.
 \subsection{Doubly Resonant}
-While HDFG can provide useful information about the properties of molecular vibrations, it is apparent that HDFG can inform on molecular electronic structure by making the hyper-Raman transition resonant with a vibronic state.
-DR-HDFG (where a vibrational and vibronic state are resonantly coupled) can provide a tool for measuring vibronic coupling.
-This method is analogous to doubly resonant sum frequency generation (DR-SFG). \cite{Shen94}
+While HDFG can provide useful information about the properties of molecular vibrations, it is apparent that HDFG can inform on molecular electronic structure by making the hyper-Raman transition resonant with a vibronic state, i.e.
+doubly resonant HDFG (DR-HDFG).
+DR-HDFG (where a vibrational and vibronic state are resonantly coupled) can provide a tool for measuring vibronic coupling, analogous to fully resonant DFG. \cite{Dick83_1, Shen94}
 Many multi-resonant nonlinear spectroscopies have been developed to resolve vibronic coupling in molecular samples. \cite{Carlson1990, Gaynor2017, RN276}
@@
 
-Since the hyper-Raman process is stimulated by a two-photon process, a setup using only two lasers can perform a coherent four wave mixing hyper-Raman experiment by investigating $\pm \vec{k}_1 + 2\vec{k}_2$ processes, assuming a two photon absorption from a single pulse stimulates the hyper-Raman process.
+Since the hyper-Raman process is stimulated by a two-photon process, a setup using only one optical parametric amplifier can perform a coherent four wave mixing hyper-Raman experiment by investigating $\pm \vec{k}_1 + 2\vec{k}_2$ processes, assuming a two photon absorption from a single pulse stimulates the hyper-Raman process.
 The other commonly used two laser CMDS method is sum frequency generation, a $\chi^{(2)}$ technique, whose phasematching is dictated by $\vec{k}_1 + \vec{k}_2$.
@@
 Absorption effects are neglected for simplicity.
-\begin{widetext}
-To allow comparison between the two methods, the output polarizations of each process is written as
+The output polarizations of each process is written as
 	\begin{subequations}
@@
 \end{equation}
-\end{widetext}
 Ziegler has noted that for a field of intensity 10 GW/cm$^{2}$, $\frac{\beta E}{\alpha} \sim 10^{-3} $ for vibrational modes when $E(\omega_3)$ is largely detuned from electronic resonances.
@@
 Orientational averaging shows specific polarization schemes isolate linear combinations of different $\beta_{ijk}$ terms. 
-Infrared spectra can provide $\vec{\mu}$ values.
+Infrared spectra can provide $\abs{\vec{\mu}}$ values.
 Since $\vec{\mu}$ is a rank-one tensor, its three Cartesian components share the simple relationship $\langle {\mu^2_x} \rangle = \langle {\mu^2_y} \rangle = \langle {\mu^2_z} \rangle = \frac{1}{3}\langle {\mu^2} \rangle$.

### 2024-07-09 paper.tex
oops

@@
 %Title of paper
-\title{Coherent Hyper-Raman Four Wave Mixing Vibrational Spectroscopies}
+\title{Coherent Hyper-Raman Four Wave Mixing Vibrational Spectroscopy}
 
@@
 \begin{equation}
-\vec{M}^{ij} = \vec{M}^{ij}_0 + \sum_z \frac{\partial\vec{M}^{ij}}{\partial Q_z}
-\end{equation} yields $A, B, C$ coefficients similar to those in the Albrecht formalism of Raman scattering, \cite{Albrecht1961, Ziegler1988} so that
+\vec{M}^{ij} = \vec{M}^{ij}_0 + \sum_z \frac{\partial\vec{M}^{ij}}{\partial Q_z} Q_z
+\end{equation} 
+yields $A, B, C$ coefficients similar to those in the Albrecht formalism of Raman scattering, \cite{Albrecht1961, Ziegler1988} so that
 \begin{equation}
@@
 In the case of the $A$ term, the sum can now be contracted over ${j, k}$. 
-Assuming a normal mode basis, $A_{ijk} \sim \sum_{j,k}\langle v | k \rangle \langle k | j \rangle \langle j | g \rangle = \delta_{vg} = 0$, or, A$_{ijk}$ vanishes for singly resonant HDFG.
+Assuming a normal mode basis, $A_{qrs} \sim \sum_{j,k}\langle v | k \rangle \langle k | j \rangle \langle j | g \rangle = \delta_{vg} = 0$, i.e., A$_{qrs}$ vanishes for singly resonant HDFG.
 \cite{Neddersen1989}
-The B terms do not suffer from this problem.
-The Herzberg-Teller matrix elements, where $\ket{z} \neq \{\ket{g}, \ket{v}\}$ is a normal mode, allows for non-zero B terms.
-As a result, singly resonant HDFG has significant dependence upon those modes which participate in Herzberg-Teller coupling. 
-This likely explains the relative weakness of HDFG response from hexane $\nu$(CH) modes. \cite{RN351}
-The singly resonant HDFG susceptibility can then be approximated as
+The Herzberg-Teller matrix elements, where $\ket{z} \neq \{\ket{g}, \ket{v}\}$ is a normal mode, do not vanish under these conditions.
+As a result, the singly resonant HDFG susceptibility can be approximated as
 \begin{equation}
@@
 \end{equation}
-or, while a vibrational mode must be infrared active for HDFG output, large $B$ values are a necessity for singly resonant HDFG response.
+or, while a vibrational mode must be infrared active for HDFG output, vibronic activity is a necessity for singly resonant HDFG response.
 \subsection{Doubly Resonant}

### 2024-07-09 paper.tex
edits

@@
 	\centering
-	\includegraphics[width=6.66in]{f1.png}
+	\includegraphics[width=6.66in]{comparisonwmel.png}
 	\caption{Wave Mixing Energy Level (WMEL) diagrams of difference frequency generation (DFG), spontaneous Raman scattering, hyper difference frequency generation (HDFG) and spontaneous hyper-Raman scattering.
@@
 		Solid and dashed horizontal lines indicate real and virtual states, whereas solid and dotted arrows indicate ket and bra side transitions, respectively. 
-%todo: add Raman to this WMEL!
-dfg Raman hyperDFG hyperRaman
 		}
@@
 For a HDFG experiment using two or three distinct input fields, as considered here, D = 6.
-Note that $\ket{m}, \ket{n}$ are virtual states (\autoref{fig:sivewmel}).
 By contracting over the virtual states to form the hyper-Raman hyperpolarizability $\beta$, this expression can be simplified immensely.\cite{Long1970} 
@@
 	\centering
-	\includegraphics[width=3.375in]{wmel3.png}
+	\includegraphics[width=3.375in]{drwmel.png}
 	\caption{WMEL diagrams of some (I-a,I-b) DR-HDFG and (II-a,II-b) DR-HSFG pathways.
@@
 Understanding interfering pathways is useful because they can, in some cases, eliminate output. \cite{RN342, RN135}
-The WMEL diagrams presented in \autoref{fig:sivewmel} outline resonant HDFG processes when the infrared pulse $(\omega_1)$ is resonant with a vibrational mode. 
+The WMEL diagram presented in \autoref{fig:comparisonwmel} outlines a resonant HDFG process where the infrared pulse $(\omega_1)$ is resonant with a vibrational mode. 
 However, if $\omega_2$ ($\omega_1$) becomes resonant (non-resonant), then other HDFG pathways appear.\cite{McDonnell2024} 
-While the methods in \autoref{fig:sivewmel2} possess identical selection rules to \autoref{fig:sivewmel}, the WMEL diagrams presented in \autoref{fig:sivewmel2} may significantly interfere with DOVE-IR and DOVE-Raman spectra.
-The time ordering in DOVE-IR and DOVE-Raman spectra is used to interpret anharmonicities, as DOVE-IR and DOVE-Raman destructively interfere when outputs are at the same frequency. \cite{RN135, RN324}
-It is therefore important to understand how the corresponding HDFG pathways interfere.
-To this end, we investigate how the HDFG-IR-II and HDFG-Raman pathways (\autoref{fig:sivewmel2}a, b, respectively) interfere under the rotating wave approximation.
-
+While the methods in \autoref{fig:sivewmel2} possess identical selection rules to \autoref{fig:sivewmel}, the WMEL diagrams presented in \autoref{fig:sivewmel2} will interfere.
 \begin{figure}[!htbp]
 	\centering
-	\includegraphics[width=3.375in]{figures/wmel2.png}
+	\includegraphics[width=3.375in]{figures/timeorderedwmel.png}
 	\caption{Wave Mixing Energy Level (WMEL) diagrams of interfering hyper-DFG pathways in the  $\vec{k}_4 = -\vec{k}_1 + \vec{k}_2 + \vec{k}_3$ phasematching geometry. 
@@
 
-We employ the response function formalism of Mukamel for this analysis. \cite{RN287}
-The third order response functions, $R^{(3)}$, for \autoref{fig:sivewmel2}a ($R^{(3)}_{a}$) and \autoref{fig:sivewmel2}b ($R^{(3)}_{b}$) are 
+To investigate interfering pathways, we employ the response function formalism of Mukamel. \cite{RN287}
+The third order response functions for \autoref{fig:sivewmel2}a ($R^{(3)}_{a}$) and \autoref{fig:sivewmel2}b ($R^{(3)}_{b}$) are 
 \begin{subequations}
@@
 \end{subequations}
-The total response function is $R^{(3)}_\text{tot} (t_2) = R^{(3)}_{a} (t_2) + R^{(3)}_{b} (t_2) = 0$. 
+The total response function is therefore $R^{(3)}_\text{tot} (t_2) = R^{(3)}_{a} (t_2) + R^{(3)}_{b} (t_2) = 0$. 
 Since the total output response function vanishes in this time-ordering, the pathways in \autoref{fig:sivewmel2} perfectly destructively interfere.
-Therefore, to measure coherent dynamics via hyper-DFG, the time ordering shown in \autoref{fig:sivewmel} should be used.
+Therefore, to measure coherent dynamics via hyper-DFG, the time ordering shown in \autoref{fig:comparisonwmel} should be used.
 These ideas have been seen experimentally in ultrafast DOVE work, as described elsewhere. \cite{RN367, McDonnell2024}
-In the case of the time ordered (\autoref{fig:sivewmel}a) pathway, there are no opportunities for interference as all other pathways are nonresonant with the first interaction. 
-A possible mechanism for interfering output in the (\autoref{fig:sivewmel}a) pathway are cascaded second order processes (SFG, DFG). \cite{RN243, RN300}
+In the case of the \autoref{fig:comparisonwmel} pathway, there are no opportunities for interference, as all other pathways are nonresonant with the first interaction. 
+A possible mechanism for interfering output in the \autoref{fig:comparisonwmel} pathway are cascaded second order processes (SFG, DFG). \cite{RN243, RN300}
 In isotropic media, SFG and DFG vanish under the electric dipole approximation,\cite{RN231} so cascades are unlikely to inhibit output in centrosymmetric media.

### 2024-07-09 figures/wmels.py

@@ -7,15 +7,12 @@ Created on Mon Jul  8 10:53:49 2024
 
 import matplotlib.pyplot as plt 
 from WrightTools.diagrams import WMEL
-plt.rcParams['figure.dpi'] = 1600
 
-compar = True
-f1 = True
-f2 = True
-f3 = True
-f4 = True
+comparisonwmel = True
+timeorderedwmel = True
+drwmel = True
 
-if compar:
+if comparisonwmel:
     fig = WMEL.Artist([4,1], [0, 0.2, 0.6, 1], state_names=("$\mathsf{| g\\rangle}$",
                                                                    "$\mathsf{|v\\rangle}$", 
                                                                    "$\mathsf{|m\\rangle}$",
@@ -37,36 +34,17 @@ if compar:
     fig.add_arrow([2,0], 3, [3,1], kind='out', color="blue", label = "$\mathsf{4}$", head_length = 0.075)
     
     fig.add_arrow([3,0], 0, [0,2], kind='bra', color="k", label = "$\mathsf{1}$", head_length = 0.075)
-    fig.add_arrow([3,0], 0, [2,3], kind='bra', color="k", label = "$\mathsf{2}$", head_length = 0.075)
-    fig.add_arrow([3,0], 1, [3,1], kind='bra', color="k", label = "$\mathsf{3}$", head_length = 0.075)
-    fig.add_arrow([3,0], 2, [0,2], kind='ket', color="k", label = "$\mathsf{4}$", head_length = 0.075)    
+    fig.add_arrow([3,0], 0, [2,3], kind='bra', color="k", label = "$\mathsf{1}$", head_length = 0.075)
+    fig.add_arrow([3,0], 1, [3,1], kind='bra', color="k", label = "$\mathsf{2}$", head_length = 0.075)
+    fig.add_arrow([3,0], 2, [0,2], kind='ket', color="k", label = "$\mathsf{3}$", head_length = 0.075)    
     fig.add_arrow([3,0], 2, [2,3], kind='ket', color="k", label = "$\mathsf{3}$", head_length = 0.075)
     fig.add_arrow([3,0], 3, [3,1], kind='out', color="blue", label = "$\mathsf{4}$", head_length = 0.075)     
 
     fig.label_columns(['$\mathsf{DFG}$','$\mathsf{Raman}$', '$\mathsf{HDFG}$', '$\mathsf{Hyper-Raman}$'], font_size = 10)
     
[…]

### 2024-07-10 paper.tex
small things

@@
 Implementing a nonlinear spectroscopy involving hyper-Raman transitions, first appearing under third order perturbation theory, can provide a useful analogue to infrared and Raman based nonlinear spectroscopies to understand the spectroscopy and dynamics of isotropic systems.
-Hyper Difference Frequency Generation (HDFG) spectroscopy, also known as singly vibrationally enhanced spectroscopy (SIVE), is an underdeveloped, hyper-Raman based four wave mixing vibrational spectroscopy.
+Hyper Difference Frequency Generation (hyper-DFG, or HDFG) spectroscopy, also known as singly vibrationally enhanced spectroscopy (SIVE), is an underdeveloped, hyper-Raman based four wave mixing vibrational spectroscopy.
 The spectroscopic and dynamic properties of HDFG have not been fully explored.
@@
 \section{Introduction}
-Coherent multidimensional spectroscopy (CMDS) is a family of three and four wave mixing methods which form the optical analogue of multidimensional nuclear magnetic resonance (NMR) spectroscopy.\cite{Cho2008, RN335}
+Coherent multidimensional spectroscopy (CMDS) is a family of three and four wave mixing methods which form the optical analogue of multidimensional nuclear magnetic resonance (NMR) spectroscopy.\cite{RN103, Cho2008, RN335}
 Multiresonant, four wave mixing CMDS experiments, first proposed by Oudar and Shen in 1980,\cite{RN307} directly probe coupling between different vibrational, electronic, and vibronic states.
-\cite{RN307, RN281, RN342, Cho2008, RN335, Ogilvie2019, RN325}
+\cite{RN307, RN281, RN103, RN342, Cho2008, RN335, Ogilvie2019, RN325}
 CMDS has resolved anharmonicities and other intramolecular couplings in numerous systems. \cite{RN345, RN342, RN343, RN324, RN329, RN120, Czech2015, Gaynor2017, Ogilvie2019, RN325}
-A particular class of CMDS methods, coherent Raman based four wave mixing spectroscopies, can provide explicit probes of vibrational and excitonic coupling in a variety of systems.
+A particular class of CMDS methods, coherent Raman based four wave mixing spectroscopies, can provide explicit probes of these couplings in a variety of systems. \cite{RN103, RN335}
 
@@
 Not all CMDS methods are used to dissect intramolecular couplings.\cite{Shen1987_CPL}
-Non-parametric, hyper difference frequency generation (hyper-DFG) spectroscopy, similar to difference frequency generation (\autoref{fig:comparisonwmel}), is a four wave mixing method which, when detuned from  electronic resonances, does not probe intramolecular couplings.
+The most well known example is sum frequency generation (SFG), a three wave mixing technique used to interpret vibrational structure and dynamics at interfaces. \cite{RN394, Piontek2023}
+Non-parametric, hyper difference frequency generation (hyper-DFG, or HDFG) spectroscopy, similar to difference frequency generation (\autoref{fig:comparisonwmel}), is a four wave mixing method which, when detuned from  electronic resonances, does not probe intramolecular couplings.
 HDFG was the first infrared CMDS method to successfully discriminate against non-resonant background.\cite{RN351, RN352}
-Hyper-DFG has also been referred to as singly vibrationally enhanced (SIVE) spectroscopy. \cite{RN351}
-In hyper-DFG, an infrared pulse is resonant with a vibrational mode, and two other input pulses are used to induce a scattering process to provide output.
-Hyper-DFG was documented long ago to have characteristics similar to spontaneous hyper-Raman scattering spectroscopy. \cite{RN352}
+HDFG has also been referred to as singly vibrationally enhanced (SIVE) spectroscopy. \cite{RN351}
+In HDFG, an infrared pulse is resonant with a vibrational mode, and two other input pulses are used to induce a scattering process to provide output.
+HDFG was documented long ago to have characteristics similar to spontaneous hyper-Raman scattering spectroscopy. \cite{RN352}
 Hyper-Raman scattering is the two photon analogue to Raman scattering. \cite{Cyvin1965, Terhune1965}
@@
 
-While hyper-DFG showed promise as an upconverted infrared spectroscopy method, it was quickly supplemented by a doubly vibrationally resonant method, doubly vibrationally enhanced (DOVE) spectroscopy, to investigate intra- and intermolecular vibrational coupling.
+While HDFG showed promise as an upconverted infrared spectroscopy method, it was quickly supplemented by a doubly vibrationally resonant method, doubly vibrationally enhanced (DOVE) spectroscopy, to investigate intra- and intermolecular vibrational coupling.
 \cite{RN345, RN101, Cho2000}
-As a result, investigations of hyper-DFG stagnated; to date`Z, there are less than a dozen studies which report on hyper-DFG.
+As a result, investigations of HDFG stagnated; to date, there are less than a dozen studies which report on HDFG.
 \cite{RN350, RN416, RN351, RN352, RN353, Chen1998, RN362, RN418, Bonn2024, McDonnell2024}
-Recent reports highlight non-negligible hyper-DFG interference in DOVE experiments as well as the suitability of hyper-DFG pathways to interpret ultrafast relaxation dynamics in isotropic systems.
+Recent reports highlight non-negligible HDFG interference in DOVE experiments as well as the suitability of HDFG pathways to interpret ultrafast relaxation dynamics in isotropic systems.
 \cite{Bonn2024, McDonnell2024}
-These reports motivate deeper analysis on the properties of hyper-DFG spectroscopy.
+These reports motivate deeper analysis on the properties of HDFG spectroscopy.
 
@@
 In this method, a single infrared pulse is resonant with a vibrational mode, and a two photon absorption event from a near infrared (NIR) or visible pulse resonant with an electronic or vibronic state is used to generate the four wave mixing signal.
-The non-parametric pathways similar to this method are referred to herein as doubly resonant hyper-DFG (DR-HDFG).
+The non-parametric pathways similar to this method are referred to herein as doubly resonant HDFG (DR-HDFG).
 Methods analogous to DR-HDFG, where two photon absorption from the infrared pulse and one photon absorption from the visible pulse is used to generate output, i.e., stimulated Raman processes, have been reported.
@@
 
+%todo: discussion on ABC terms and what they mean.
+
 We investigate properties of DR-HDFG to understand how coupling between vibrational and vibronic states can be measured.
@@
 
-It is useful to expose relationships between transition dipoles, Raman polarizabilities and hyper-Raman polarizabilities in the driven limit. \cite{Simpson2004, RN120}
-In the driven limit, under the electric dipole approximation, the I$^{th}$ component of the third order nonlinear output polarization, ${P}^{(3)}_I$, of any four wave mixing process, induced by electric fields E, at output frequency $\omega_4$ is written as \cite{RN307}
+It is useful to expose relationships between transition dipoles, Raman polarizabilities and hyper-Raman polarizabilities in the driven limit. \cite{Druet1978, Simpson2004}
+In the driven limit, under the electric dipole approximation, the I$^{th}$ component of the third order nonlinear output polarization, ${P}^{(3)}_I$, of any four wave mixing process, induced by electric fields E, at output frequency $\omega_4$ is written as (using Einstein summation) \cite{RN307}
 \begin{equation} \label{polarization}
@@
 This follows from the presence of an inversion center in centrosymmetric systems, which demands strict parity selection rules. \cite{RN230}
-Macroscopically, inversion symmetry in the output polarization eliminates output from centrosymmetric species under the electric dipole approximation.\cite{RN227, RN132}
-As a result, the output of SFG is significantly reduced relative to most third order spectroscopies because the output only depends on surface species.
+Macroscopically, oddness in spatial inversion of the output polarization eliminates output from centrosymmetric species under the electric dipole approximation.\cite{RN227, RN132}
+As a result, the output of SFG is significantly reduced relative to most third order spectroscopies because the output depends on surface species.
 However, since HDFG is dependent upon a hyper-Raman transition, it is useful to compare the relative output of the two processes to identify how HDFG output compares to SFG.
@@
 	\includegraphics[width=3.375in]{figures/timeorderedwmel.png}
-	\caption{Wave Mixing Energy Level (WMEL) diagrams of interfering hyper-DFG pathways in the  $\vec{k}_4 = -\vec{k}_1 + \vec{k}_2 + \vec{k}_3$ phasematching geometry. 
+	\caption{Wave Mixing Energy Level (WMEL) diagrams of interfering HDFG pathways in the  $\vec{k}_4 = -\vec{k}_1 + \vec{k}_2 + \vec{k}_3$ phasematching geometry. 
 		(a) is similar to the process diagrammed in \autoref{fig:sivewmel}, whereas (b) is similar to a singly resonant coherent anti-Stokes Raman-type process.
@@
 Since the total output response function vanishes in this time-ordering, the pathways in \autoref{fig:sivewmel2} perfectly destructively interfere.
-Therefore, to measure coherent dynamics via hyper-DFG, the time ordering shown in \autoref{fig:comparisonwmel} should be used.
+Therefore, to measure coherent dynamics via HDFG, the time ordering shown in \autoref{fig:comparisonwmel} should be used.
 These ideas have been seen experimentally in ultrafast DOVE work, as described elsewhere. \cite{RN367, McDonnell2024}

### 2024-07-12 paper.tex
more edits

@@
 Not all CMDS methods are used to dissect intramolecular couplings.\cite{Shen1987_CPL}
-The most well known example is sum frequency generation (SFG), a three wave mixing technique used to interpret vibrational structure and dynamics at interfaces. \cite{RN394, Piontek2023}
+The most well known example is sum frequency generation (SFG), a three wave mixing technique used to interpret vibrational structure and dynamics at interfaces. \cite{RN431, Piontek2023}
 Non-parametric, hyper difference frequency generation (hyper-DFG, or HDFG) spectroscopy, similar to difference frequency generation (\autoref{fig:comparisonwmel}), is a four wave mixing method which, when detuned from  electronic resonances, does not probe intramolecular couplings.
@@
 HDFG was documented long ago to have characteristics similar to spontaneous hyper-Raman scattering spectroscopy. \cite{RN352}
-Hyper-Raman scattering is the two photon analogue to Raman scattering. \cite{Cyvin1965, Terhune1965}
+Hyper-Raman scattering is the two photon analogue to Raman scattering. \cite{Cyvin1965, Terhune1965, Kozich2007}
 Compared to Raman spectroscopy, hyper-Raman scattering cross sections are often small, making it a difficult technique to successfully implement.\cite{RN515, Kelley2010} 
@@
 Some years ago, Cho et al. proposed parametric six wave mixing techniques as the coherent analogue of hyper-Raman scattering. \cite{Cho1997, Cho1998}
-However, since most six wave mixing methods cascade into four wave mixing processes,\cite{RN243, Cho2000_Cascade}, and their output would be dependent upon the square magnitude of the hyper-Raman scattering cross section, a small number,\cite{RN515} it is preferable to investigate coherent four wave mixing analogues to hyper-Raman scattering.
+However, since most six wave mixing methods cascade into four wave mixing processes,\cite{RN243, RN302, Cho2000_Cascade}, and their output would be dependent upon the square magnitude of the hyper-Raman scattering cross section, a small number,\cite{RN515} it is preferable to investigate coherent four wave mixing analogues to hyper-Raman scattering.
 
@@
 
-An experimental complexity in executing four wave mixing experiments is the demand of three separate input pulses, often all at different frequencies.
-For example, in the case of DOVE, two of the three input pulses must be scanable infrared pulses. \cite{RN345} 
+An experimental complexity in executing Raman based four wave mixing experiments is the demand of three separate input pulses, often at different frequencies.
+For example, in the case of DOVE, two of the three inputs must be scanable infrared pulses. \cite{RN345} 
 Only recently have methods been developed for seamless tuning and scanning of ultrafast optical parametric amplifiers across swaths of frequency space. \cite{RN162, McDonnell2024, SkyeOPA, KyleOPA}
 Since HDFG demands only a single resonance to be scanned, the experiment can be performed using two input pulses: one tunable, infrared OPA to scan across vibrational resonances, and a two photon absorption from the signal process of a separate OPA, or output from the oscillator which pumps the infrared OPA.
+\cite{Wang2021}
 As such, laboratories experienced in sum frequency generation (SFG) spectroscopy can perform HDFG spectroscopy to understand bulk dynamics and spectroscopy using nearly the same setup.\cite{Shen1987_CPL}
@@
 For a HDFG experiment using two or three distinct input fields, as considered here, D = 6.
-By contracting over the virtual states to form the hyper-Raman hyperpolarizability $\beta$, this expression can be simplified immensely.\cite{Long1970} 
-Note, however, that if $\omega_2$, $\omega_3$, as depicted in \autoref{fig:comparisonwmel}, are nearly resonant with any state, the contraction is not allowed. \cite{Placzek1934, Long1970}
-Assuming $\omega_2$, $\omega_3$ are significantly detuned from any local resonance, \autoref{sivegamma} is written as 
+We first investigate the selection rules through a Placzek type formalism.
+Contracting over the virtual states forms the hyper-Raman hyperpolarizability $\beta$.\cite{Long1970, Willetts1992} 
+Assuming $\omega_2$, $\omega_3$ are significantly detuned from any local resonance (\autoref{fig:comparisonwmel}),\cite{Placzek1934, Long1970} \autoref{sivegamma} is written as 
 \begin{equation}\label{sivebeta}
@@
 \end{equation}
-where $\mel{v}{Q_n}{g} = \sqrt{\frac{\hbar}{2m_n\omega_{vg}}}$ under the harmonic approximation,\cite{RN230} and $m_n$ is the ``mass'' of the $Q_n$ mode. 
+where $\mel{v}{Q_n}{g} = \sqrt{\frac{\hbar}{2m_n\omega_{vg}}}$ and $m_n$ is the ``mass'' of the $Q_n$ mode.  \cite{RN230}
 Since this expression is non-zero in the harmonic oscillator limit, HDFG output is allowed for harmonic transitions. 
@@
 
-So far, only Placzek approximation type arguments have been used to interpret HDFG output.
-Previous spontaneous hyper-Raman work interpreted the origin of hyper-Raman signal in terms of Franck-Condon, Herzberg-Teller and Duschinsky type couplings.\cite{Ziegler1988} 
-As such, we extend \autoref{SIVEselection} using an Albrecht ABC type formalism to account for these couplings.
-The formalism will first be developed for singly resonant HDFG, but extension to doubly resonant HDFG is straightforward and will be discussed later.
+While Placzek approximation type arguments are useful to understand the general source of HDFG output, it is insightful to interpret the origin of signal in terms of Albrecht ABC type terms.\cite{Ziegler1988}
+As such, we extend $\beta_{ijk}$ in \autoref{SIVEselection} using the hyper-Raman ABC formalism to understand how vibronic coupling manipulates selection rules for singly and doubly resonant HDFG \autoref{fig:hdfg}.
+\cite{Ziegler1988, Baranov1990}
 
-To employ the Albrecht formalism, we write the states in terms of a Born-Oppenheimer basis $\ket{a,b}$, where $\ket{a,b} = |a) \otimes \ket{b}$ for electronic states $\{|a)\}$ and vibrational states $\{\ket{b}\}$.
-\cite{BornOppenheimer, Albrecht1960}
-For simplicity, we choose $\ket{g}, \ket{v}$ to be vibrational states on the ground electronic state $|g)$ and $\ket{m} \rightarrow \ket{m,j}$, $\ket{n} \rightarrow \ket{n,k}$ are virtual states.
+\begin{figure}[!htbp]
+	\centering
+	\includegraphics[width=3.375in]{hdfg.png}
+	\caption{WMEL diagrams of (a) singly resonant and (b) doubly resonant HDFG. 
+	}
+	\label{fig:hdfg}
+\end{figure}
+
+To employ the Albrecht formalism, we write the states in terms of a Born-Oppenheimer basis $\ket{a,b}$, where $\ket{a,b} = |a(Q)) \otimes \ket{b}$ for electronic states $\{|a(Q))\}$ and vibrational states $\{\ket{b}\}$ (i.e., adiabatic approximation).
+\cite{BornOppenheimer, Tang1970}
+The dependence of the electronic states on the adiabatic parameter $Q$ is suppressed for simplicity.
+The states are labeled as shown in \autoref{fig:hdfg}.
 For consistency with previous reports, we use $\vec{R}$ to denote electric transition dipole moments ($\vec{\mu}$ is reserved for transitions between states on the ground electronic state).
@@
 \begin{equation}\label{drgamma_notaylor}
-	\gamma_{ijkl} = -\frac{1}{\varepsilon_0} \frac{1}{24 \hbar^3} \sum_{m,n,j,k} \frac{
-		R_{i}^{gv, nk} 
-		R_{j}^{nk,mj} 
-		R_{k}^{mj,gg} 
-		R_{l}^{gv,gg} 
-	}{\Delta_{g0,gg}
-		\Delta_{nk, mj}
-		\Delta_{mj, gg}
+	\gamma_{ijkl} = -\frac{1}{\varepsilon_0} \frac{1}{24 \hbar^3} \sum_{m,n,e,v'} \frac{
+		R_{i}^{gv, ev'} 
+		R_{j}^{ev',mn} 
+		R_{k}^{mn,g0} 
+		R_{l}^{g0,gv} 
+	}{\Delta_{g0,gv}
+		\Delta_{ev', mn}
+		\Delta_{mn, g0}
 	}
@@
 Using our definition of vibronic states, we write $\vec{M}^{ab} = (a|\vec{M}|b)$ so that, for example,
-$R_{i}^{gv,ev'} = \mel{v}{M_i^{ge}}{v'}$.\cite{Albrecht1960}
+$R_{i}^{gv,ev'} = \mel{v}{M_i^{ge}}{v'}$.
 Using these ideas rewrites \autoref{drgamma_notaylor} as
@@
 	\begin{split}
-		\gamma_{ijkl} &= -\frac{1}{\varepsilon_0} \frac{1}{24 \hbar^3} \sum_{m,n,v'} \frac{
+		\gamma_{ijkl} &= -\frac{1}{\varepsilon_0} \frac{1}{24 \hbar^3} \sum_{m,n,e,v'} \frac{
 			\mel{v}{M_{i}^{ge}}{v'} 
@@
 \end{equation}
-The $A$ term depends upon Franck-Condon ($\order{Q^0}$) transitions, the $B$ term depends upon Herzberg-Teller ($\order{Q}$) transitions, and the $C$ term depends on $\order{Q^2}$ transitions. 
-The C term is suppressed in the following discussion as it depends on one and two photon forbidden transitions which have yet to be observed in spontaneous hyper-Raman scattering. \cite{Ziegler1988}
-In the discussion that follows, we take $\hbar = e = 1$.
+The $A$ term depends upon $\order{Q^0}$ transitions (i.e., Condon approximation), the $B$ term depends upon $\order{Q}$ transitions, and the $C$ term depends on $\order{Q^2}$ transitions. 
+The C term is suppressed in the following discussion as it depends on one and two photon forbidden transitions. \cite{Ziegler1988}
+Note that other reports obtain $A, B, C$ coefficents through a Herzberg-Teller expansion of the electronic states, where $|a) = |a)_0 + \sum_{a \neq b} \frac{(\partial H / \partial Q )_0  Q}{E_a - E_b} |a)_0$.\cite{HerzbergTeller1933, Neddersen1989, Baranov1990}
+This approach is not used here as the expansion of the vibronic dipole moment in terms of normal mode coordinates provides similar insight.
 
-By compiling all the terms that scale with $\order{Q^0}$, $A$ is written as
+By compiling all the terms that scale with $\order{Q^0}$, $A$ is written, assuming contraction over the nonresonant vibrational states $\ket{n}$ as
 \begin{equation}
 	\begin{split}
-		A_{qrs} = \sum_{m,n,j,k} M^{gn}_{0,q} 
-		M^{nm}_{0,r} 
-		M^{mg}_{0,s}
-		 \langle v | k \rangle
-		 \langle k | j \rangle
-		 \langle j | g \rangle 
-		 \frac{1}{\Delta_{nk,mj} \Delta_{mj, gg}}
+		A_{ijk} = \frac{1}{\hbar^2}\sum_{m,e,v'} M^{ge}_{0,i} 
+		M^{em}_{0,j} 
+		M^{mg}_{0,k}
+		 \langle v | v' \rangle
+		 \langle v' | 0 \rangle 
+		 \frac{1}{\Delta_{ev',m} \Delta_{m, g0}}
 		 \\
@@
 		\begin{split}
-			B_{1_{qrs}} &= \sum_{m,n,j,k,z} M^{gn}_{0,q} \langle v | k \rangle \lbrack
-			 \frac{\partial M^{nm}_{r}}{\partial Q_z} \mel{k}{Q_z}{j} M^{mg}_{0,s} \langle j | g \rangle
-			+M^{nm}_{0,r} \langle k | j \rangle \frac{\partial M^{mg}_{s}}{\partial Q_z} \mel{j}{Q_z}{g} \rbrack \frac{1}{\Delta_{nk,mj} \Delta_{mj, gg}}\\
+			B_{1_{ijk}} &= \frac{1}{\hbar^2} \sum_{m,e,v',z} M^{ge}_{0,i} \langle v | v' \rangle \lbrack
+			 \frac{\partial M^{em}_{j}}{\partial Q_z} M^{mg}_{0,k} \mel{v'}{Q_z}{0} 
+			+M^{em}_{0,j} \frac{\partial M^{mg}_{k}}{\partial Q_z} \mel{v'}{Q_z}{0} \rbrack \frac{1}{\Delta_{ev',m} \Delta_{m, g0}}\\
 		\end{split}
@@
 	\begin{split}
-			B_{2_{qrs}} = \sum_{m,n,j,k,z} \frac{\partial M^{gn}_{q}}{\partial Q_z} \mel{v}{Q_z}{k} M^{nm}_{0,r} 
-			M^{mg}_{0,s}
-			\langle k | j \rangle
-			\langle j | g \rangle 
-			\frac{1}{\Delta_{nk,mj} \Delta_{mj, gg}}
+			B_{2_{ijk}} = \frac{1}{\hbar^2} \sum_{m,e,v',z} \frac{\partial M^{ge}_{i}}{\partial Q_z} M^{em}_{0,j} 
+			M^{mg}_{0,k} \mel{v}{Q_z}{v'} 
+			\langle v' | 0 \rangle 
+			\frac{1}{\Delta_{ev',m} \Delta_{m, g0}}
 	\end{split}
@@
 \end{subequations}
-where terms such as $\langle a | b \rangle$ are Franck-Condon factors and $\mel{a}{Q_z}{b}$ are Herzberg-Teller coupling factors. %include parameterization of the states?
+where terms such as $\langle a | b \rangle$ are Franck-Condon factors.
 
-When $\omega_2$ and $\omega_3$ are largely detuned from a local resonance, the resonance denominators lose their dependence on vibrational quantum number.
-In the case of the $A$ term, the sum can now be contracted over ${j, k}$. 
-Assuming a normal mode basis, $A_{qrs} \sim \sum_{j,k}\langle v | k \rangle \langle k | j \rangle \langle j | g \rangle = \delta_{vg} = 0$, i.e., A$_{qrs}$ vanishes for singly resonant HDFG.
-\cite{Neddersen1989}
-The Herzberg-Teller matrix elements, where $\ket{z} \neq \{\ket{g}, \ket{v}\}$ is a normal mode, do not vanish under these conditions.
-As a result, the singly resonant HDFG susceptibility can be approximated as
+In the case of singly resonant HDFG, $\omega_3$ is also detuned which further contracts the sum over ${v'}$. 
+Assuming a normal mode basis, we see for singly resonant HDFG that
+\begin{subequations}
+\begin{equation}
+	A_{ijk} \sim \sum_{v'}\langle v | v' \rangle \langle v' | 0 \rangle = \delta_{v0} = 0
+\end{equation}
+\begin{equation}
+	B_{1_{ijk}} = \frac{1}{\hbar^2} \sum_{m,e,z} M^{ge}_{0,i} \lbrack
+	\frac{\partial M^{em}_{j}}{\partial Q_z} M^{mg}_{0,k}
+	+M^{em}_{0,j} \frac{\partial M^{mg}_{k}}{\partial Q_z} \rbrack \frac{\mel{v}{Q_z}{0}}{\Delta_{e,m} \Delta_{m, g0}}
+\end{equation}
+\begin{equation}
+	B_{2_{ijk}} = \frac{1}{\hbar^2} \sum_{m,e,z} \frac{\partial M^{ge}_{i}}{\partial Q_z} M^{em}_{0,j} 
+	M^{mg}_{0,k}  
+	\frac{\mel{v}{Q_z}{0}}{\Delta_{e,m} \Delta_{m, g0}}
+\end{equation}
+\end{subequations}
+i.e., A$_{ijk}$ vanishes, but B$_{ijk}$ is non-zero, for singly resonant HDFG. 
+The singly resonant HDFG susceptibility can be approximated as
 \begin{equation}
@@
 or, while a vibrational mode must be infrared active for HDFG output, vibronic activity is a necessity for singly resonant HDFG response.
-\subsection{Doubly Resonant}
-While HDFG can provide useful information about the properties of molecular vibrations, it is apparent that HDFG can inform on molecular electronic structure by making the hyper-Raman transition resonant with a vibronic state, i.e.
-doubly resonant HDFG (DR-HDFG).
+Breakdown of the Condon approximation in singly resonant HDFG supports the relative small intensities of HDFG, reported to be roughly an order of magnitude larger than nonresonant background, in hexane and other organic solvents.
+\cite{RN351, RN353}
+
+The selection rules for DR-HDFG are different. 
+DR-HDFG output is dependent upon the $A,B$ terms prior to contraction over $\ket{v'}$. 
+Based upon the presence of the $A$ term in DR-HDFG, it is apparent that DR-HDFG can inform on molecular electronic structure.
 DR-HDFG (where a vibrational and vibronic state are resonantly coupled) can provide a tool for measuring vibronic coupling, analogous to fully resonant DFG. \cite{Dick83_1, Shen94}
@@
 DR-HDFG provides methods to investigate vibronic coupling with only two laser pulses.
-Two beam, parametric and non-parametric DR-HDFG processes are diagrammed in \autoref{fig:doubsive}.
-
-\begin{figure}[!htbp]
-	\centering
-	\includegraphics[width=3.375in]{drwmel.png}
-	\caption{WMEL diagrams of some (I-a,I-b) DR-HDFG and (II-a,II-b) DR-HSFG pathways.
-$\ket{g,0}$ denotes the ground states, $\ket{g,v}$ denotes a vibrational state on the ground electronic manifold; $\ket{m,n}$ denotes a virtual state, and $\ket{e,0}, \ket{e,v'}$ denote vibronic states.}
-	\label{fig:doubsive}
-\end{figure}
 
@@
 
-\subsection{Quantification}
-
-Since the hyper-Raman process is stimulated by a two-photon process, a setup using only one optical parametric amplifier can perform a coherent four wave mixing hyper-Raman experiment by investigating $\pm \vec{k}_1 + 2\vec{k}_2$ processes, assuming a two photon absorption from a single pulse stimulates the hyper-Raman process.
-The other commonly used two laser CMDS method is sum frequency generation, a $\chi^{(2)}$ technique, whose phasematching is dictated by $\vec{k}_1 + \vec{k}_2$.
-The SFG output scales as $\chi^{(2)}_{IJK} \sim \langle \alpha_{ij} \mu_k \rangle$, where $\alpha_{ij}$ is the Raman polarizability tensor.
-Since SFG is dependent upon transitions that transform like both rank-one and rank-two tensors, this enforces a microscopic constraint that SFG cannot yield output for centrosymmetric species under the electric dipole approximation.
-This follows from the presence of an inversion center in centrosymmetric systems, which demands strict parity selection rules. \cite{RN230}
+Since the hyper-Raman process is stimulated by a two-photon process, a setup using only one optical parametric amplifier can perform a coherent four wave mixing hyper-Raman experiment by investigating $\pm \vec{k}_1 + 2\vec{k}_2$ processes (i.e.
+two laser CMDS), assuming a two photon absorption from a single pulse stimulates the hyper-Raman process.
+The most commonly used two laser CMDS method is sum frequency generation, a $\chi^{(2)}$ technique whose phasematching is dictated by $\vec{k}_1 + \vec{k}_2$.
+SFG output scales as $\chi^{(2)}_{IJK} \sim \langle \alpha_{ij} \mu_k \rangle$, where $\alpha_{ij}$ is the Raman polarizability tensor.
+Since SFG is dependent upon transitions that transform like both rank-one and rank-two tensors, parity enforces a microscopic constraint that SFG cannot yield output for centrosymmetric species under the electric dipole approximation due to the presence of an inversion center.
+\cite{RN230}
 Macroscopically, oddness in spatial inversion of the output polarization eliminates output from centrosymmetric species under the electric dipole approximation.\cite{RN227, RN132}
@@
 \cite{Levenson1974_2, RN351, RN345}
-%okay clearly this wont work lol we need something that is IR active... CaF2?%
+Other standards include CaF$_2$, a commmonly used optical window used in four wave mixing experiments. \cite{RN362}
 Self-heterodyning of the internal standard signal measures $\chi^{(3)}$ and does not require measurement of absolute intensities. 
@@
 The recorded $\chi^{(n)}$ values provide insight into how microscopic quantities ($\vec{\mu}, \alpha_{ij}, \beta_{ijk}$) impact nonlinear output.
-To our knowledge, only vibrational SFG and 2D-IR spectroscopy has taken advantage of orientationally averaged $\chi^{(n)}$ values to extract transition moments. \cite{Shen90, Moilanen2009, RN245}
-It is thus useful to investigate how a simple treatment of orientational averaging can extract $\beta_{ijk}$ from $\chi^{(3)}_{IJKL}$.
+Calculating $\beta_{ijk}$ values from hyper-Raman experiments is difficult and has only been performed for a selection of molecular vibrations. \cite{Xu1997, Shoute2005, Kelley2010}
+Methods reported in the literature to measure absolute hyper-Raman polarizabilities depend upon external standards such as hyperpolarizabilities of dissolved samples or two-photon absorption cross sections (also difficult to measure).
+Since the Bloembergen interferometry experiment only relies on the third order susceptibility for measured species (such as benzene or CaF$_2$), it is possible to use quantitative four wave mixing spectroscopy to calculcate $\beta_{ijk}$ values.
+It is thus useful to investigate how a treatment of orientational averaging can extract $\beta_{ijk}$ from $\chi^{(3)}_{IJKL}$.
 
@@
 \end{equation}
-This expression cannot be used as written to extract $\beta_{ijk}$, as $\beta_{ijk}$ is a Hermitian operator, but $\Delta_{gv} \in \mathbb{C}$. 
+\autoref{chi3} cannot be used as written to extract $\beta_{ijk}$, as $\beta_{ijk}$ is a Hermitian operator, but $\Delta_{gv} \in \mathbb{C}$. 
 However, since the real and imaginary components of $\chi^{(3)}$ can be extracted from the Bloembergen interferometry experiment, and $\beta_{ijk}$ is present in either term, we can choose to focus on the real or imaginary part of $\chi^{(3)}$.
@@
 The steps behind orientational averaging of $\gamma_{ijkl}$, a rank four tensor in the molecular frame, are detailed elsewhere.\cite{Andrews1977, McDonnell2024}
-Orientational averaging shows specific polarization schemes isolate linear combinations of different $\beta_{ijk}$ terms. 
-Infrared spectra can provide $\abs{\vec{\mu}}$ values.
-Since $\vec{\mu}$ is a rank-one tensor, its three Cartesian components share the simple relationship $\langle {\mu^2_x} \rangle = \langle {\mu^2_y} \rangle = \langle {\mu^2_z} \rangle = \frac{1}{3}\langle {\mu^2} \rangle$.
-\cite{RN459}
-Neglecting rotational dependence (i.e., assuming only vibrational transitions), $\langle {\mu^2} \rangle = \mu^2$, so that $\langle \beta_{ijk} \mu_l \rangle = \langle \beta_{ijk} \rangle \frac{\abs{\mu}}{\sqrt{3}}$.
+Orientational averaging shows specific polarization schemes isolate linear combinations of different $\beta_{ijk}$ terms. \cite{Kauranen1996}
 By introducing the reduced mass coordinate $q_n = \sqrt{\frac{1}{m_n}} Q_n$ and using the expansions of $\beta_{ijk}$ and $\mu_{l}$ to $\order{Q_n}$ found earlier, we see
 \begin{equation}\label{betasive}
-	\langle \frac{\partial \beta_{ijk}}{\partial q_n} \rangle = \varepsilon_0 \frac{48 \sqrt{3} }{NF}  \frac{\Gamma_{gv} \omega_{vg}}{\rho_{gg}} \frac{\Im(\chi^{(3)}_{IJKL})}{\frac{\partial \mu}{\partial q_n}}
+	\langle \frac{\partial \beta_{ijk}}{\partial q_n} {\frac{\partial \mu_l}{\partial q_n}} \rangle = \frac{48 \varepsilon_0}{NF}  \frac{\Gamma_{gv} \omega_{vg}}{\rho_{gg}} {\Im(\chi^{(3)}_{IJKL})}
 \end{equation}
-Since $\abs{\mu}$ values can be readily extracted from FT-IR spectra,\cite{RN412} this shows that HDFG can give quantitative information on the magnitude of $\beta_{ijk}$.
-HDFG and vSFG together provide unique methods to extract the microscopic quantities ($\mu, \alpha, \beta$) that drive nonlinear output.
-
-\subsection{Comparison to 2DEV and 2DVE spectroscopy}
-Compare James' stuff and make connections.
+Since $\abs{\mu}$ values can be readily extracted from FT-IR spectra,\cite{RN412} HDFG can give quantitative information on the magnitude of $\beta_{ijk}$.
 
@@
 Extracting the magnitude and sign of $\beta_{ijk}$ using SIVE methods can help assess the quality of theoretical methods which calculate hyper-Raman spectra.
-Doubly resonant SIVE (DR-SIVE) processes show promise as a probe of vibronic coupling in molecular samples.
-Unlike SR-SIVE, DR-SIVE methods can linenarrow inhomogeneously broadened vibronic modes.
 

### 2024-07-12 figures/wmels.py

@@ -7,10 +7,12 @@ Created on Mon Jul  8 10:53:49 2024
 
 import matplotlib.pyplot as plt 
 from WrightTools.diagrams import WMEL
+import WrightTools as wt
 
-comparisonwmel = True
-timeorderedwmel = True
-drwmel = True
+comparisonwmel = False
+hdfg = True
+timeorderedwmel = False
+drwmel = False
 
 if comparisonwmel:
     fig = WMEL.Artist([4,1], [0, 0.2, 0.6, 1], state_names=("$\mathsf{| g\\rangle}$",
@@ -43,6 +45,19 @@ if comparisonwmel:
     fig.label_columns(['$\mathsf{DFG}$','$\mathsf{Raman}$', '$\mathsf{HDFG}$', '$\mathsf{Hyper-Raman}$'], font_size = 10)
     
     plt.savefig("comparisonwmel.png", bbox_inches='tight')
+
+if hdfg:
+    fig = WMEL.Artist([1,1], [0, 0.2, 0.6, 1], state_names=("$\mathsf{| g, 0\\rangle}$",
+                                                                   "$\mathsf{|g, v\\rangle}$", 
+                                                                   "$\mathsf{|m, n\\rangle}$",
+                                                                   "$\mathsf{|e, v'\\rangle}$"), number_of_interactions=5, state_font_size=9, state_text_buffer = 0.6, virtual = [2])
+
+    fig.add_arrow([0,0], 0, [0,1], kind='bra', color="k", label = "$\mathsf{1}$", head_length = 0.075)
+    fig.add_arrow([0,0], 1, [0,2], kind='ket', color="k", label = "$\mathsf{2}$", head_length = 0.075)
+    fig.add_arrow([0,0], 2, [2,3], kind='ket', color="k", label = "$\mathsf{3}$", head_length = 0.075)
+    fig.add_arrow([0,0], 3, [3,1], kind='out', color="blue", label = "$\mathsf{4}$", head_length = 0.075)
+    
+    fig.label_columns(['$(\mathsf{b})$'], font_size = 10)
 
 if timeorderedwmel:
     fig = WMEL.Artist([2,1], [0, 0.2, 0.6, 1], state_names=("$\mathsf{| g\\rangle}$",

### 2024-07-12 paper.tex
edits

@@
 \autoref{chi3} cannot be used as written to extract $\beta_{ijk}$, as $\beta_{ijk}$ is a Hermitian operator, but $\Delta_{gv} \in \mathbb{C}$. 
-However, since the real and imaginary components of $\chi^{(3)}$ can be extracted from the Bloembergen interferometry experiment, and $\beta_{ijk}$ is present in either term, we can choose to focus on the real or imaginary part of $\chi^{(3)}$.
+However, since the real and imaginary components of $\chi^{(3)}$ can be measured through the Bloembergen interferometry experiment, and $\beta_{ijk}$ is present in either term, we can choose to focus on the real or imaginary part of $\chi^{(3)}$.
 For simplicity, we investigate $\Im(\chi^{(3)})$, giving, assuming resonance conditions, 
@@
 \end{equation}
-Since $\abs{\mu}$ values can be readily extracted from FT-IR spectra,\cite{RN412} HDFG can give quantitative information on the magnitude of $\beta_{ijk}$.
+Since $\abs{\mu}$ values can be readily extracted from FT-IR spectra,\cite{RN119, RN412} HDFG can give quantitative information on the magnitude of $\beta_{ijk}$.
 

### 2024-07-15 paper.tex
edits

@@
 \cite{Cho2000, Bonn2024}
-We develop simple expressions which relate transition dipoles and hyper-Raman polarizabilties and the overall HDFG output, yielding gross selection rules. 
-It is shown that a HDFG active mode must be both IR and hyper-Raman active.
-Since any IR active vibration is also hyper-Raman active, \cite{Andrews1978} we demonstrate that HDFG is a coherent analogue of hyper-Raman scattering spectroscopy for IR active vibrations, i.e., HDFG is an optically upconverted infrared spectroscopy.
-This is akin to sum and difference frequency generation (SFG, DFG) being coherent Raman analogues for IR active vibrations. \cite{Shen90}
+This paper is outlined as follows.
+In section \ref{steadystate}, we discuss the selection rules behind singly and doubly resonant HDFG in terms of hyper-Raman A,B,C coefficients.
+In section \ref{quant}, the quantitative aspects of HDFG is discussed.
+In section \ref{mixeddomain}, mixed time-frequency domain HDFG is discussed, and is applied to the simple case of CH$_3$CN in section \ref{Expt}. 
+\section{Experimental}\label{experimental}
 
-%todo: discussion on ABC terms and what they mean.
+The ultrafast laser system has been described in detail elsewhere. \cite{RN278}
+Briefly, an 80 MHz Ti-Sapphire ultrafast oscillator  (Spectra-Physics Tsunami) created 35 fs seed pulses, amplified by a 1 kHz regnerative amplifier (Spectra-Physics Spitfire Ace) to approximately 0.5 W.
+A mask in the regenerative amplifier stretched the input pulses to roughly 1 ps.
+The resultant output was used to pump four independent OPAs, two of which are relevant for this study.
+OPA1 (TOPAS-800, Light Conversion), referred to as $\omega_1$, was tuned for difference frequency generation (DFG) with an external stage (NDFG ``DF2'', Light Conversion).
+OPA2 (OPA-800C, Spectra Physics), referred to as $\omega_2$, was tuned in its signal arrangement. 
+OPA3, a homebuilt OPA, is tuned in its signal arrangement and referred to as $\omega_3$.
+Grating and crystal positions in OPA1 was externally controlled using \texttt{WinTOPAS} (Light Conversion).
+Grating and BBO crystal positions in OPA2 and OPA3 were computer controlled through communication with DC actuators.
+The OPAs were independently tuned through the \texttt{Attune} package, controlled by the \texttt{yaqc} and \texttt{Bluesky} packages. \cite{RN414, RN386, SkyeOPA, KyleOPA}
+The power spectra and tuning results are found in Figure X. %todo: actually graph these
+Movable retroreflectors (Thorlabs) controlled by 50 mm DC actuators (PMC) are used to measure coherence dynamics.
+The beams are focused using a BOXCARS geometry.\cite{RN308, Kaufman2024}
+To enforce frequency dependent temporal pulse overlap, the maximum points of a third order cross correlation between $\omega_1$ and $\omega_3$ measured in CaF$_2$ were used to generate frequency dependent zero delay values.
+The nonlinear output was isolated through chopping schemes and a set of spatial apertures, directed into a monochromator (Horiba Micro-HR) and homodyne detected through a photomultiplier tube (Hamamatsu H7422-20), recorded and converted to digital output using a data acquisition unit (National Instruments).
+\textit{in-situ} power corrections are performed by dividing the recorded spectra by OPA output measured by home-built pyroelectric detectors.
+All spectra are reported on the intensity scale.
 
-We investigate properties of DR-HDFG to understand how coupling between vibrational and vibronic states can be measured.
-DR-HDFG is shown to demand one and two-photon absorptions between the ground and excited state.
-DR-HDFG is thus the four wave mixing analogue of doubly resonant infrared-visible sum frequency generation. \cite{Shen94}
+The cyanocobalamin (CNCbl) [DOT Scientific inc., CAS no. 68-19-9] samples were prepared as drop casted thin films.
+CNCbl was dissolved in methanol (MeOH) [Fisher Scientific, HPLC Grade, CAS no. 67-56-1] until a concentrated solution was formed (concentration $\sim$ 10 mg CNCbl/ mL MeOH). 
+All chemicals were used as obtained without further purification.
+The solution was deposited on a microscope coverslip and allowed to dry in a dessicator until a thin layer was formed.
 
-\section{Steady State Hyper-DFG Spectroscopy}
+\section{Steady State HDFG Spectroscopy}\label{steadystate}
 Singly resonant hyper difference generation spectroscopy (HDFG) spectroscopy has potential to provide deeper insight into single quantum decoherence times and molecular orientation in condensed systems.
 Similarities between HDFG spectroscopy, infrared spectroscopy and spontaneous hyper-Raman scattering have been noted previously. \cite{RN352, Bonn2024}
-In this section, we make the connections between HDFG and hyper-Raman scattering explicit and investigate the steady state properties of singly resonant HDFG.
+In this section, we investigate the steady state properties of HDFG and make the connections between HDFG and hyper-Raman scattering explicit.
 
@@
 \end{equation}
-Taylor expanding the dipole and first hyperpolarizability operators in terms of an n$^{\text{th}}$ normal mode coordinate $Q_n$ about equilibrium: \cite{Long1970}
+It is important to note that the properties of $\beta_{ijk}$ change dependent upon whether $\omega_2$ and $\omega_3$ are degenerate. \cite{Andrews1978, Altmann1982}
+Taylor expanding the dipole and first hyperpolarizability operators in terms of an n$^{\text{th}}$ normal mode coordinate $Q_n$ about equilibrium as\cite{Long1970}
 \begin{subequations}
@@
 \end{subequations}
-Substituting into \autoref{sivebeta} gives the HDFG hyperpolarizability to $\order{Q_n}$ as \begin{equation}\label{SIVEselection}
+and substituting into \autoref{sivebeta} gives the HDFG hyperpolarizability to $\order{Q_n}$ as \begin{equation}\label{SIVEselection}
 	\gamma_{ijkl} =	-\frac{1}{\varepsilon_0} \frac{1}{48 m_n \omega_{vg}}  \frac{1}{{\Delta_{gv}}} \ \frac{\partial \beta^{gv}_{ijk}}{\partial Q_n} {\frac{\partial \mu^{gv}_{l}}{\partial Q_n}}  \rho_{gg}
@@
 This selection rule is generally valid for any HDFG or hyper sum frequency generation (HSFG) process in the $-\vec{k}_1 + \vec{k}_2  + \vec{k}_3$ and $\vec{k}_1 + \vec{k}_2  + \vec{k}_3$ phasematching geometries when $\omega_2$ and $\omega_3$ are sufficiently detuned from any resonance.
-
-While Placzek approximation type arguments are useful to understand the general source of HDFG output, it is insightful to interpret the origin of signal in terms of Albrecht ABC type terms.\cite{Ziegler1988}
-As such, we extend $\beta_{ijk}$ in \autoref{SIVEselection} using the hyper-Raman ABC formalism to understand how vibronic coupling manipulates selection rules for singly and doubly resonant HDFG \autoref{fig:hdfg}.
-\cite{Ziegler1988, Baranov1990}
 
@@
 
-To employ the Albrecht formalism, we write the states in terms of a Born-Oppenheimer basis $\ket{a,b}$, where $\ket{a,b} = |a(Q)) \otimes \ket{b}$ for electronic states $\{|a(Q))\}$ and vibrational states $\{\ket{b}\}$ (i.e., adiabatic approximation).
+While Placzek type arguments provide general source of HDFG output, it is insightful to interpret the origin of signal in terms of Albrecht ABC type terms.\cite{Ziegler1988} 
+We write $\beta_{ijk}$ in \autoref{SIVEselection} using the hyper-Raman ABC formalism to understand how vibronic coupling manipulates selection rules for singly and doubly resonant HDFG (\autoref{fig:hdfg}).
+\cite{Ziegler1988, Baranov1990}
+To employ this formalism, we write the states in terms of a Born-Oppenheimer basis $\ket{a,b}$, where $\ket{a,b} = |a(Q)) \otimes \ket{b}$ for electronic states $\{|a(Q))\}$ and vibrational states $\{\ket{b}\}$ (i.e., adiabatic approximation).
 \cite{BornOppenheimer, Tang1970}
@@
 For consistency with previous reports, we use $\vec{R}$ to denote electric transition dipole moments ($\vec{\mu}$ is reserved for transitions between states on the ground electronic state).
-\cite{Ziegler1974}
+\cite{Tang1970}
 Following the approach which gave \autoref{sivegamma}, we find
@@
 \end{equation}
-where $R_{i}^{ab,cd}$ is the i$^{th}$ element of $\mel{a,b}{\vec{R}}{c,d}$.\cite{Ziegler1988}
+where $R_{i}^{ab,cd}$ is the i$^{th}$ element of $\mel{a,b}{\vec{R}}{c,d}$.
 Using our definition of vibronic states, we write $\vec{M}^{ab} = (a|\vec{M}|b)$ so that, for example,
@@
 			\mel{n}{M_{k}^{mg} }{v}
-			\mel{v}{M_{l}^{gg}}{0}
+			\mel{v}{\mu_{l}}{0}
 		}{\Delta_{g0,gv}
@@
 The $A$ term depends upon $\order{Q^0}$ transitions (i.e., Condon approximation), the $B$ term depends upon $\order{Q}$ transitions, and the $C$ term depends on $\order{Q^2}$ transitions. 
-The C term is suppressed in the following discussion as it depends on one and two photon forbidden transitions. \cite{Ziegler1988}
-Note that other reports obtain $A, B, C$ coefficents through a Herzberg-Teller expansion of the electronic states, where $|a) = |a)_0 + \sum_{a \neq b} \frac{(\partial H / \partial Q )_0  Q}{E_a - E_b} |a)_0$.\cite{HerzbergTeller1933, Neddersen1989, Baranov1990}
-This approach is not used here as the expansion of the vibronic dipole moment in terms of normal mode coordinates provides similar insight.
+The C term is suppressed in the following discussion as it depends on one and two photon forbidden transitions. \cite{Ziegler1988, Neddersen1989, Bonang1992}
+Note that some reports obtain $A, B, C$ coefficients through a Herzberg-Teller expansion of the electronic states, $|a) = |a)_0 + \sum_{a \neq b} \frac{(\partial H / \partial Q )_0  Q}{E_a - E_b} |a)_0$, to explicitly expose vibronic couplings in terms of $\partial H / \partial Q $, where H is the electronic Hamiltonian.\cite{HerzbergTeller1933, Petrov1985, Neddersen1989, Baranov1990}
+This approach is not used here as the expansion of $\vec{M}^{ij}$ in normal mode coordinates provides sufficient physical insight into hyper-Raman selection rules.
 
-By compiling all the terms that scale with $\order{Q^0}$, $A$ is written, assuming contraction over the nonresonant vibrational states $\ket{n}$ as
+By contracting over the virtual vibrational states $\ket{n}$, the $A$ and $B$ coefficients, where $B = B_1 + B_2$, are written as
+\begin{widetext}
+\begin{subequations}
 \begin{equation}
@@
 \end{equation}
-and by compiling all terms that scale with $\order{Q}$, $B$ is written as $B = B_1 + B_2$,\cite{Bonang1992} where
-\begin{subequations}
 	\begin{equation}
@@
 \end{subequations}
+\end{widetext}
 where terms such as $\langle a | b \rangle$ are Franck-Condon factors. 
+These expressions are valid for both singly and doubly resonant HDFG, but based upon the resonance schemes, further simplifications can be made (\textit{vide infra}).
 
-In the case of singly resonant HDFG, $\omega_3$ is also detuned which further contracts the sum over ${v'}$. 
+In the case of singly resonant HDFG, $\omega_3$ is also detuned from any resonance, which permits contraction over ${v'}$ as the dependence on $\ket{v'}$ in the resonance denominator can be neglected.
 Assuming a normal mode basis, we see for singly resonant HDFG that
@@
 \end{equation}
-or, while a vibrational mode must be infrared active for HDFG output, vibronic activity is a necessity for singly resonant HDFG response.
-Breakdown of the Condon approximation in singly resonant HDFG supports the relative small intensities of HDFG, reported to be roughly an order of magnitude larger than nonresonant background, in hexane and other organic solvents.
-\cite{RN351, RN353}
+or, while a vibrational mode must be infrared active for HDFG output, vibronic activity is necessary for singly resonant HDFG response.
+The breakdown of the Condon approximation in singly resonant HDFG supports the relative small HDFG $\chi^{(3)}$ values ($\sim$ order of magnitude larger than nonresonant background) in hexane and similar organic solvents.
+\cite{RN350, RN351, RN353}
 
 The selection rules for DR-HDFG are different. 
-DR-HDFG output is dependent upon the $A,B$ terms prior to contraction over $\ket{v'}$. 
-Based upon the presence of the $A$ term in DR-HDFG, it is apparent that DR-HDFG can inform on molecular electronic structure.
 DR-HDFG (where a vibrational and vibronic state are resonantly coupled) can provide a tool for measuring vibronic coupling, analogous to fully resonant DFG. \cite{Dick83_1, Shen94}
@@
 DR-HDFG provides methods to investigate vibronic coupling with only two laser pulses.
+DR-HDFG output is dependent upon the $A,B$ terms prior to contraction over $\ket{v'}$. 
+Based upon the presence of the $A$ term in DR-HDFG, it is apparent that DR-HDFG can inform on molecular electronic structure.
 
@@
 
+\section{Quantitative Aspects of HDFG}\label{quant}
+
 Since the hyper-Raman process is stimulated by a two-photon process, a setup using only one optical parametric amplifier can perform a coherent four wave mixing hyper-Raman experiment by investigating $\pm \vec{k}_1 + 2\vec{k}_2$ processes (i.e.
@@
 		\begin{equation}
-			\abs{P^{(2)}_{\text{SFG}}} = N_{surf} F(\omega_1+\omega_2) \abs{\langle \alpha_{ij}\mu_{k} \rangle E_J(\omega_2)E_K(\omega_1)} 
+			\abs{P^{(2)}_{\text{SFG}}} = N_{surf} F(\omega_1+\omega_2) \abs{\langle \alpha_{ij}\mu_{k} \rangle E(\omega_2)E(\omega_1)} 
 		\end{equation}
 		\begin{equation}
-			\abs{P^{(3)}_{\text{HDFG}}} = N_{bulk}  F(-\omega_1+\omega_2 +\omega_3) \abs{\langle \beta_{ijk} \mu_{l} \rangle E_J{(\omega_3)}E_K(\omega_2)E_L(-\omega_1)} \ell_{eff}
+			\abs{P^{(3)}_{\text{HDFG}}} = N_{bulk}  F(2\omega_2-\omega_1) \abs{\langle \beta_{ijk} \mu_{l} \rangle E{(\omega_2)}E(\omega_2)E(-\omega_1)} \ell_{eff}
 		\end{equation}
@@
 We take the bulk optical interaction length ($\ell_{eff}$) to be 10 $\mu$m.\cite{RN133} %see chapter 25 of Shen's NLO book... idk something here seems wrong
-A normal dispersion curve is assumed so that $F(\omega_1+\omega_2) \approx F(-\omega_1+\omega_2 +\omega_3)$.
+A normal dispersion curve is assumed so that $F(\omega_1+\omega_2) \approx F(2\omega_2-\omega_1)$.
 To simplify analysis, orientational averaging is ignored (e.g., $\langle \beta_{ijk} \mu_{l} \rangle \approx \beta \mu$) and the input and output fields are taken to be co-polarized, so that
 \begin{equation}
-		P_{ratio} \equiv \frac{\abs{P^{(3)}_{\text{HDFG}}}}{\abs{P^{(2)}_{\text{SFG}}}} \approx \frac{N_{bulk}}{N_{surf}} \frac{\beta}{\alpha} E(\omega_3) \ell_{eff} \sim 10^4 \frac{\beta}{\alpha} E(\omega_3)\\
+		P_{ratio} \equiv \frac{\abs{P^{(3)}_{\text{HDFG}}}}{\abs{P^{(2)}_{\text{SFG}}}} \approx \frac{N_{bulk}}{N_{surf}} \frac{\beta}{\alpha} E(\omega_2) \ell_{eff} \sim 10^4 \frac{\beta}{\alpha} E(\omega_2)\\
 \end{equation}
-Ziegler has noted that for a field of intensity 10 GW/cm$^{2}$, $\frac{\beta E}{\alpha} \sim 10^{-3} $ for vibrational modes when $E(\omega_3)$ is largely detuned from electronic resonances.
+Ziegler has noted that for a field of intensity 10 GW/cm$^{2}$, $\frac{\beta E}{\alpha} \sim 10^{-3} $ for vibrational modes when $E(\omega_2)$ is largely detuned from electronic resonances.
 \cite{RN515}
@@
 With the selection rules of HDFG understood for vibrational spectroscopy, it becomes possible to extract quantitative information from its spectra.
-A useful attribute of the $\beta_{ijk}$ dependence in HDFG output is added polarization control. 
-Similar to SFG experiments that probe different elements of the infrared transition dipole and Raman polarizability tensors, probing different elements of $\beta_{ijk}$ in HDFG can greatly assist in understanding ultrafast dynamics in isotropic systems, as suggested by Seliya et al.
-\cite{Shen90, RN224, Bonn2024}
-Polarization control in IR-pump-HDFG-probe, analogous to ultrafast transient absorption spectroscopy for vibrational modes, would be an interesting venue to assess the sensitivity of HDFG to different hyper-Raman tensor elements.
-
 Lineshape analysis is essential for extracting quantitative information from CMDS spectra.
@@
 In the method introduced by Levenson and Bloembergen (Bloembergen Interferometry Experiment), an internal standard interferes with the resonant lineshape.
-The internal standard is often chosen to be C$_6$H$_6$ or C$_6$D$_6$, due to the strong Raman activity and measured $\chi^{(3)}$ of its ring breathing mode ($\nu_2$ in Herzberg notation).
-\cite{Levenson1974_2, RN351, RN345}
-Other standards include CaF$_2$, a commmonly used optical window used in four wave mixing experiments. \cite{RN362}
 Self-heterodyning of the internal standard signal measures $\chi^{(3)}$ and does not require measurement of absolute intensities. 
@@
 \end{equation}
-
 The steps behind orientational averaging of $\gamma_{ijkl}$, a rank four tensor in the molecular frame, are detailed elsewhere.\cite{Andrews1977, McDonnell2024}
-Orientational averaging shows specific polarization schemes isolate linear combinations of different $\beta_{ijk}$ terms. \cite{Kauranen1996}
+Briefly, a tensor in the molecular frame, A$_{ijkl}$ is transformed into an element of the same tensor in the laboratory frame, A$_{IJKL}$ through A$_{IJKL}$ = $\theta^{ijkl}_{IJKL} A_{ijkl} = \langle A_{ijkl} \rangle$, where summation over repeated indices is implied, and $\theta$ is the transformation operator.
+\cite{McDonnell2024}
+Orientational averaging shows specific polarization schemes isolate linear combinations of different $\beta_{ijk}$ terms. \cite{Cyvin1965, Bersohn1966, Kauranen1996}
 By introducing the reduced mass coordinate $q_n = \sqrt{\frac{1}{m_n}} Q_n$ and using the expansions of $\beta_{ijk}$ and $\mu_{l}$ to $\order{Q_n}$ found earlier, we see
@@
 
-\section{Mixed-Domain Hyper-DFG}
-Some words about why mixed domain is great (kill NRB, isolate FID based stuff etc)
-Then introduce problems (pathway interference) which can screw things up. This then leads into the main section.
+\section{Mixed-Domain HDFG}\label{mixeddomain}
+The properties of steady state HDFG (complete pulse overlap) are useful for understanding the selection rules that drive output.
+Time domain HDFG could be a useful alternative technique for measuring single quantum coherence dephasing times (T$_2$).
+The response function for the HDFG pathway illustrated in \autoref{fig:hdfg}a, assuming $\omega_2$ and $\omega_3$ are temporally overlapped, is \cite{RN287, Cho2001}
+\begin{equation}
+	R^{(3)}(t) = \frac{i}{\hbar} [\beta(t), \mu(0)] \exp(-i\Delta_{gv}t) \theta(t) 
+\end{equation}  
+The pure time-domain HDFG output reports on the dephasing characteristics of the $\ket{g}\bra{v}$ coherence. 
+This method provides practitioners of sum frequency generation the ability to probe isotropic dephasing dynamics without many meaningful changes in their optical setup, and thus compare $\ket{g}\bra{v}$ dephasing in the bulk and at the interface.\cite{RN224}
+
+Transient HDFG spectroscopy, or pump-HDFG-probe, similar to transient vSFG spectroscopy, can be implemented to learn about relaxation dynamics in isotropic systems. \cite{RN224, Bonn2024}
+A useful attribute of the $\beta_{ijk}$ dependence in HDFG output is added polarization control. 
+Similar to SFG experiments that probe different elements of the infrared transition dipole and Raman polarizability tensors, probing different elements of $\beta_{ijk}$ in HDFG can greatly assist in understanding ultrafast dynamics in isotropic systems, as suggested by Seliya et al.
+\cite{Shen90, RN224, Bonn2024}
+Polarization control in IR-pump-HDFG-probe, analogous to ultrafast transient absorption spectroscopy for vibrational modes, would be an interesting venue to assess the sensitivity of HDFG to different hyper-Raman tensor elements.
+
+Combinations of time and frequency domain spectroscopy, also called mixed domain spectroscopy, are useful ways to understand frequency-dependent dynamics. \cite{RN135, RN171, RN131}
+Mixed domain spectroscopy is a useful alternative to steady state spectroscopy as pulse separation can eliminate nonresonant background and isolate specific pulse ordering sequences.
+\cite{RN372, RN324, McDonnell2024}
+Isolating different pulse orderings can isolate pathway specific signal and minimize interference from unwanted pathways which share the same phasematching constraints. 
+Mixed domain HDFG can resolve frequency dependent free induction decay, which could prove useful for understanding isotropic dynamics of single quantum coherences. 
+Mixed domain resonant HDFG, using pathways similar to those in \autoref{fig:hdfg}b, could also measure electronic-vibrational correlation functions, as discussed by Cho. \cite{Cho2001}
 
@@
 Understanding interfering pathways is useful because they can, in some cases, eliminate output. \cite{RN342, RN135}
-The WMEL diagram presented in \autoref{fig:comparisonwmel} outlines a resonant HDFG process where the infrared pulse $(\omega_1)$ is resonant with a vibrational mode. 
-However, if $\omega_2$ ($\omega_1$) becomes resonant (non-resonant), then other HDFG pathways appear.\cite{McDonnell2024} 
-While the methods in \autoref{fig:sivewmel2} possess identical selection rules to \autoref{fig:sivewmel}, the WMEL diagrams presented in \autoref{fig:sivewmel2} will interfere.
+While we have only isolated one specific HDFG process so far, there are at least fourteen different WMELs which can provide HDFG output. \cite{RN352}
+If $\omega_2$ ($\omega_1$) becomes resonant (non-resonant), then other HDFG pathways appear (\autoref{fig:sivewmel2}).\cite{McDonnell2024} 
+While the methods in \autoref{fig:sivewmel2} possess identical selection rules to \autoref{fig:hdfg}, the WMEL diagrams presented in \autoref{fig:sivewmel2} will interfere, as they share the same phasematching condition but have oppositely signed amplitudes.
 \begin{figure}[!htbp]
@@
 	\includegraphics[width=3.375in]{figures/timeorderedwmel.png}
-	\caption{Wave Mixing Energy Level (WMEL) diagrams of interfering HDFG pathways in the  $\vec{k}_4 = -\vec{k}_1 + \vec{k}_2 + \vec{k}_3$ phasematching geometry. 
-		(a) is similar to the process diagrammed in \autoref{fig:sivewmel}, whereas (b) is similar to a singly resonant coherent anti-Stokes Raman-type process.
-		%todo: add pump-SIVE-probe to this set of WMELs
+	\caption{WMEL diagrams of interfering HDFG pathways in the  $\vec{k}_4 = -\vec{k}_1 + \vec{k}_2 + \vec{k}_3$ phasematching geometry. 
 		}
@@
 
-To investigate interfering pathways, we employ the response function formalism of Mukamel. \cite{RN287}
 The third order response functions for \autoref{fig:sivewmel2}a ($R^{(3)}_{a}$) and \autoref{fig:sivewmel2}b ($R^{(3)}_{b}$) are 
@@
 \end{subequations}
-The total response function is therefore $R^{(3)}_\text{tot} (t_2) = R^{(3)}_{a} (t_2) + R^{(3)}_{b} (t_2) = 0$. 
+The total response function in this time ordering is therefore $R^{(3)}_\text{tot} (t_2) = R^{(3)}_{a} (t_2) + R^{(3)}_{b} (t_2) = 0$. 
 Since the total output response function vanishes in this time-ordering, the pathways in \autoref{fig:sivewmel2} perfectly destructively interfere.
-Therefore, to measure coherent dynamics via HDFG, the time ordering shown in \autoref{fig:comparisonwmel} should be used.
-These ideas have been seen experimentally in ultrafast DOVE work, as described elsewhere. \cite{RN367, McDonnell2024}
-In the case of the \autoref{fig:comparisonwmel} pathway, there are no opportunities for interference, as all other pathways are nonresonant with the first interaction. 
-A possible mechanism for interfering output in the \autoref{fig:comparisonwmel} pathway are cascaded second order processes (SFG, DFG). \cite{RN243, RN300}
-In isotropic media, SFG and DFG vanish under the electric dipole approximation,\cite{RN231} so cascades are unlikely to inhibit output in centrosymmetric media.
-In media where SFG and DFG are allowed, e.g. surfaces or noncentrosymmetric media, second order cascades may become important.
+Therefore, to measure dynamics via HDFG, the time ordering shown in \autoref{fig:hdfg} should be used.
+These ideas have been seen experimentally in ultrafast DOVE work. \cite{RN367, McDonnell2024}
+In the case of the \autoref{fig:hdfg}a time ordering, there are no opportunities for interference from other third order processes. 
+However, a possible mechanism for interfering output in the \autoref{fig:hdfg}a pathway is a cascaded second order process (SFG, DFG). \cite{RN243, RN300}
+While unimportant in isotropic systems, second order cascades may become important in media where SFG and DFG are allowed, e.g. surfaces or noncentrosymmetric media.
 
-%todo: measuring Coherence and Population Lifetimes
-
-\section{Experimental Hyper-DFG of CH$_3$CN}
+\section{Experimental HDFG of CH$_3$CN}\label{Expt}
 With the theoretical description of HDFG provided, we will investigate steady state and transient HDFG spectra of $\nu$(CH) modes in CH$_3$CN.
-%@dan I choose these modes because easily accessible with df1, but since you have moved to df2 since we can also choose the v(CN) mode$
 
@@
 
-\section{Conclusions}%didn't change to HDFG down here because lazy
+\section{Conclusions}%todo:fix!
 Coherent vibrational, hyper-Raman coherent four wave mixing spectroscopies are identified and discussed.

### 2024-07-15 figures/wmels.py

@@ -7,12 +7,12 @@ Created on Mon Jul  8 10:53:49 2024
 
 import matplotlib.pyplot as plt 
 from WrightTools.diagrams import WMEL
-import WrightTools as wt
+# import WrightTools as wt
 
-comparisonwmel = False
+comparisonwmel = True
 hdfg = True
-timeorderedwmel = False
-drwmel = False
+timeorderedwmel = True
+drwmel = True
 
 if comparisonwmel:
     fig = WMEL.Artist([4,1], [0, 0.2, 0.6, 1], state_names=("$\mathsf{| g\\rangle}$",
@@ -112,3 +112,4 @@ if drwmel:
     fig.label_columns(['$(\mathsf{a})$','$(\mathsf{b})$'], font_size = 10)
     fig.label_rows(['$\mathsf{I}$','$\mathsf{II}$'], font_size=15, text_buffer=1.5)
     plt.savefig("drwmel.png", bbox_inches='tight')
+    

### 2024-07-15 paper.tex
Update paper.tex

@@
 Not all CMDS methods are used to dissect intramolecular couplings.\cite{Shen1987_CPL}
-The most well known example is sum frequency generation (SFG), a three wave mixing technique used to interpret vibrational structure and dynamics at interfaces. \cite{RN431, Piontek2023}
+The most well known example is sum frequency generation (SFG), a three wave mixing technique used to interpret vibrational structure and dynamics at interfaces. \cite{RN224, Piontek2023}
 Non-parametric, hyper difference frequency generation (hyper-DFG, or HDFG) spectroscopy, similar to difference frequency generation (\autoref{fig:comparisonwmel}), is a four wave mixing method which, when detuned from  electronic resonances, does not probe intramolecular couplings.
@@
 Some years ago, Cho et al. proposed parametric six wave mixing techniques as the coherent analogue of hyper-Raman scattering. \cite{Cho1997, Cho1998}
-However, since most six wave mixing methods cascade into four wave mixing processes,\cite{RN243, RN302, Cho2000_Cascade}, and their output would be dependent upon the square magnitude of the hyper-Raman scattering cross section, a small number,\cite{RN515} it is preferable to investigate coherent four wave mixing analogues to hyper-Raman scattering.
+However, since most six wave mixing methods cascade into four wave mixing processes,\cite{RN243, Cho2000_Cascade}, and their output would be dependent upon the square magnitude of the hyper-Raman scattering cross section, a small number,\cite{RN515} it is preferable to investigate coherent four wave mixing analogues to hyper-Raman scattering.
 
@@
 
-Inspired by recent work which demonstrated the presence of HDFG in ultrafast DOVE experiments,\cite{McDonnell2024} we investigate the parameters which result in both SR and DR-SIVE output.
-\cite{Cho2000, Bonn2024}
+Inspired by recent work which demonstrated the presence of HDFG in ultrafast DOVE experiments, we investigate the parameters which result in both SR and DR-SIVE output.
+\cite{Cho2000, Bonn2024, McDonnell2024}
 This paper is outlined as follows.
-In section \ref{steadystate}, we discuss the selection rules behind singly and doubly resonant HDFG in terms of hyper-Raman A,B,C coefficients.
-In section \ref{quant}, the quantitative aspects of HDFG is discussed.
+In section \ref{steadystate}, we discuss the selection rules behind singly and doubly resonant HDFG first through the Placzek approximation, and then through hyper-Raman A,B,C coefficients.
+In section \ref{quant}, the quantitative aspects of HDFG are discussed, and a method to extract hyper-Raman hyperpolarizabilities ($\beta_{ijk}$) from HDFG spectra is identified.
 In section \ref{mixeddomain}, mixed time-frequency domain HDFG is discussed, and is applied to the simple case of CH$_3$CN in section \ref{Expt}.
+
 \section{Experimental}\label{experimental}
-
 The ultrafast laser system has been described in detail elsewhere. \cite{RN278}
-Briefly, an 80 MHz Ti-Sapphire ultrafast oscillator  (Spectra-Physics Tsunami) created 35 fs seed pulses, amplified by a 1 kHz regnerative amplifier (Spectra-Physics Spitfire Ace) to approximately 0.5 W.
+Briefly, an 80 MHz Ti-Sapphire ultrafast oscillator  (Spectra-Physics Tsunami) created 35 fs seed pulses, amplified by a 1 kHz regenerative amplifier (Spectra-Physics Spitfire Ace) to approximately 0.5 W.
 A mask in the regenerative amplifier stretched the input pulses to roughly 1 ps.
@@
 \section{Steady State HDFG Spectroscopy}\label{steadystate}
+\subsection{Placzek Method}
 Singly resonant hyper difference generation spectroscopy (HDFG) spectroscopy has potential to provide deeper insight into single quantum decoherence times and molecular orientation in condensed systems.
-Similarities between HDFG spectroscopy, infrared spectroscopy and spontaneous hyper-Raman scattering have been noted previously. \cite{RN352, Bonn2024}
+Similarities between HDFG spectroscopy, infrared spectroscopy and spontaneous hyper-Raman scattering have been noted previously. \cite{RN352, Bonn2024, McDonnell2024}
 In this section, we investigate the steady state properties of HDFG and make the connections between HDFG and hyper-Raman scattering explicit.
 
-It is useful to expose relationships between transition dipoles, Raman polarizabilities and hyper-Raman polarizabilities in the driven limit. \cite{Druet1978, Simpson2004}
+It is useful to expose relationships between transition dipoles, Raman polarizabilities and hyper-Raman hyperpolarizabilities in the driven limit. \cite{Druet1978, Simpson2004}
 In the driven limit, under the electric dipole approximation, the I$^{th}$ component of the third order nonlinear output polarization, ${P}^{(3)}_I$, of any four wave mixing process, induced by electric fields E, at output frequency $\omega_4$ is written as (using Einstein summation) \cite{RN307}
@@
 We first investigate the selection rules through a Placzek type formalism.
-Contracting over the virtual states forms the hyper-Raman hyperpolarizability $\beta$.\cite{Long1970, Willetts1992} 
+Contracting over the virtual states forms the hyper-Raman hyperpolarizability $\beta$.\cite{Long1970} 
 Assuming $\omega_2$, $\omega_3$ are significantly detuned from any local resonance (\autoref{fig:comparisonwmel}),\cite{Placzek1934, Long1970} \autoref{sivegamma} is written as 
@@
 \end{figure}
-
-While Placzek type arguments provide general source of HDFG output, it is insightful to interpret the origin of signal in terms of Albrecht ABC type terms.\cite{Ziegler1988} 
+\subsection{Albrecht Type Expansion}
+While Placzek type arguments provide the general source of HDFG output, it is insightful to interpret the origin of signal in terms of Albrecht ABC type terms.\cite{Ziegler1988} 
 We write $\beta_{ijk}$ in \autoref{SIVEselection} using the hyper-Raman ABC formalism to understand how vibronic coupling manipulates selection rules for singly and doubly resonant HDFG (\autoref{fig:hdfg}).
@@
 			\Delta_{mn, g0}	} \\
-%	&= 	-\frac{1}{\varepsilon_0} \frac{1}{24 \hbar^3} \sum_{m,n,v'} \frac{
-%		\mel{v}{M_{i}^{ge}}{v'} 
-%		\mel{v'}{M_{j}^{em}}{n}
-%		\mel{n}{M_{k}^{mg} }{v}
-%		\mel{v}{\mu_{l}}{0}
-%	}{\Delta_{g0,gv}
-%		\Delta_{ev', mn}
-%		\Delta_{mn, g0}	} \\
 	\end{split}
@@
 The C term is suppressed in the following discussion as it depends on one and two photon forbidden transitions. \cite{Ziegler1988, Neddersen1989, Bonang1992}
-Note that some reports obtain $A, B, C$ coefficients through a Herzberg-Teller expansion of the electronic states, $|a) = |a)_0 + \sum_{a \neq b} \frac{(\partial H / \partial Q )_0  Q}{E_a - E_b} |a)_0$, to explicitly expose vibronic couplings in terms of $\partial H / \partial Q $, where H is the electronic Hamiltonian.\cite{HerzbergTeller1933, Petrov1985, Neddersen1989, Baranov1990}
+Note that some reports obtain $A, B, C$ coefficients through a Herzberg-Teller expansion of the electronic states, $|a) = |a)_0 + \sum_z \sum_{a \neq b} \frac{(\partial H / \partial Q_z )_0  Q_z}{E_a - E_b} |a)_0$, to explicitly expose vibronic couplings in terms of $\partial H / \partial Q_z $, where H is the electronic Hamiltonian.\cite{HerzbergTeller1933, Petrov1985, Neddersen1989, Baranov1990}
 This approach is not used here as the expansion of $\vec{M}^{ij}$ in normal mode coordinates provides sufficient physical insight into hyper-Raman selection rules.
@@
 These expressions are valid for both singly and doubly resonant HDFG, but based upon the resonance schemes, further simplifications can be made (\textit{vide infra}).
-
+\subsubsection{Singly Resonant HDFG}
 In the case of singly resonant HDFG, $\omega_3$ is also detuned from any resonance, which permits contraction over ${v'}$ as the dependence on $\ket{v'}$ in the resonance denominator can be neglected.
@@
 \cite{RN350, RN351, RN353}
-
+\subsubsection{Doubly Resonant HDFG}
 The selection rules for DR-HDFG are different. 
@@
 \cite{RN230}
-Macroscopically, oddness in spatial inversion of the output polarization eliminates output from centrosymmetric species under the electric dipole approximation.\cite{RN227, RN132}
+Macroscopically, oddness in spatial inversion of the output polarization eliminates output from centrosymmetric species under the electric dipole approximation.\cite{RN133, RN132}
 As a result, the output of SFG is significantly reduced relative to most third order spectroscopies because the output depends on surface species.
@@
 The output polarizations of each process is written as
+\begin{widetext}
 	\begin{subequations}
@@
 \end{subequations}
+\end{widetext}
 where N$_{bulk}$ is the bulk number density, and N$_{surf}$ is the surface number density (10$^{19}$ m$^{-2}$).\cite{RN133, RN503}	
@@
 
-It is well known that nonlinear wave mixing processes which share the same time ordering and output frequency will interfere. \cite{RN135, Bonn2024}
-Understanding interfering pathways is useful because they can, in some cases, eliminate output. \cite{RN342, RN135}
+It is well known that nonlinear wave mixing processes which share the same time ordering and output frequency will interfere. \cite{RN342, RN135}
+Understanding interfering pathways is useful because they can, in some cases, eliminate output. 
 While we have only isolated one specific HDFG process so far, there are at least fourteen different WMELs which can provide HDFG output. \cite{RN352}

### 2024-07-15 paper.tex
started2dplot

@@
 
-To explicitly incorporate vibronic coupling into the selection reules for DR-HDFG, we consider
+The impact of vibronic coupling in the 2D spectrum is made clear by using a simple model.
+Using a two-well system described by $H_g = p^2/2m + 1/2 \hbar \omega q^2$ and $H_e = p^2/2m + 1/2 \hbar \omega (q-\Delta)^2$, the A and B contributions can be easily evaluated using Franck-Condon type integrals tabulated elsewhere.
+\cite{Carlson1988thesis}
 

### 2024-07-15 figures/2D_spec.py

@@ -1,0 +1,87 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Tue Jan 17 09:28:39 2023
+
+@author: rpm
+"""
+
+import math
+from sympy import *
+import numpy as np
+import WrightTools as wt
+import matplotlib.pyplot as plt 
+import matplotlib
+
+
+#define harmonic wells
+def gs(k):
+    return 0.1*k**2
+
+def es(k):
+    return 0.1*(k-0.5)**2 + 0.65
+
+
+#coordinate#
+kg = np.linspace(-2.5, 2.5, 500) #ground state coordinates
+ke = np.linspace(-2, 3, 500) #excited state coordinates
+
+#plots#
+
+#make plot
+
+fig, ax = plt.subplots(figsize=(3.5, 3.5), layout='constrained')
+plt.rcParams['figure.dpi'] = 1000
+
+plt.plot(kg,gs(kg), linewidth = '4',label = '$C_{\chi = + 1}$', color = 'cyan')
+plt.plot(ke,es(ke), linewidth = '4',label = '$C_{\chi = - 1}$', color = 'orange')
+# delta
+plt.axvline(x=0.5, color = 'purple', linestyle='--', label = '$\Delta$')
+
+#beautificiation#
+
+matplotlib.rcParams.update({'font.size': 10})
+
+plt.xlabel(r'q (arb.)')
+plt.xticks(ticks = [])
+plt.yticks(ticks = [])
+plt.ylabel(r'Energy')
+plt.xlim(-3.5,3.5)
+plt.ylim(-0.1, 1.4)
+
+matplotlib.rcParams.update({'font.size': 10})
+
+# plt.legend(loc = 'upper center')   
+
+
+plt.show()
+
+##make the 2d plot
+
+#define Franck-Condon factors following page 164 of Roger Carlson's thesis in terms of Delta
+def f00(q): #<0|0>
+    return np.e**(-q**2/4)
+
+def f01(q): #<0|1>
+    return -q/(np.sqrt(2)) * f00(q)
+
+def f10(q): #<1|0>
+    return -1*f01(q)
+
+def f02(q): #<2|0> = <0|2>
+    return q**2/(2*np.sqrt(2)) * f00(q)
+
+
+#define Herzberg Teller overlap integrals following page 165 of Roger Carlson's thesis in terms of Delta
[…]

### 2024-07-16 paper.tex
edits

--- 2024-07-15 paper.tex
@@
 \begin{widetext}
-\begin{subequations}
+\begin{subequations}\label{ABterms}
 \begin{equation}
@@
 or, while a vibrational mode must be infrared active for HDFG output, vibronic activity is necessary for singly resonant HDFG response.
-The breakdown of the Condon approximation in singly resonant HDFG supports the relative small HDFG $\chi^{(3)}$ values ($\sim$ order of magnitude larger than nonresonant background) in hexane and similar organic solvents.
+The breakdown of the Condon approximation in singly resonant HDFG supports the relatively small HDFG $\chi^{(3)}$ values ($\sim$ order of magnitude larger than nonresonant background) in hexane and similar organic solvents.
 \cite{RN350, RN351, RN353}
@@
 
-To explicitly incorporate vibronic coupling into the selection reules for DR-HDFG, we consider
-
-%todo: write hamiltonian like Gaynor to make clear what we are doing (and put in a picture in Figure doubbleresspec)
-To interpret HDFG selection rules, we use a slightly modified version of equation xyz to account for the added vibronic resonance. 
-This change immediately makes the A term nonzero in the case of noncentrosymmetric systems.
-
-A simulated spectrum highlighting the contributions of these terms (\autoref{fig:doubres_spec}) on potential wells with displacements $\Delta$ shows... 
+The impact of vibronic coupling in the 2D spectrum is made clear by using a simple model.
+Using a two-well system described by $H_g = p^2/2m + 1/2 \hbar \omega q^2$ and $H_e = p^2/2m + 1/2 \hbar \omega (q-\Delta)^2 +\hbar \omega_{eg}$, the A and B contributions can be easily evaluated using Franck-Condon and Herzberg-Teller integrals tabulated elsewhere.
+\cite{Carlson1988thesis}
+By working only in terms of a single normal mode (i.e.
+removing the sum over $z$) and assuming electronic transitions occur only between $|g), |e)$ and that $v' = \{0,1,2\}$, the A and B terms are rewritten as
+\begin{widetext}
+	\begin{subequations}\label{ABterms_DR}
+		\begin{equation}
+			\begin{split}
+				A_{ijk} = \frac{1}{\hbar}\sum_{v'} M^{ge}_{0,i} 
+				\Lambda^{eg}_{0,jk}
+				\langle v | v' \rangle
+				\langle v' | 0 \rangle 
+				\frac{1}{\Delta_{ev',g0}}
+				\\
+			\end{split}
+		\end{equation}
+		\begin{equation}
+			\begin{split}
+				B_{1_{ijk}} &= \frac{1}{\hbar^2} \sum_{v',m} M^{ge}_{0,i} \langle v | v' \rangle \lbrack
+				\frac{\partial M^{em}_{j}}{\partial Q} M^{mg}_{0,k} \mel{v'}{Q}{0} 
+				+M^{em}_{0,j} \frac{\partial M^{mg}_{k}}{\partial Q} \mel{v'}{Q}{0} \rbrack \frac{1}{\Delta_{ev',m} \Delta_{m, g0}}\\
+			\end{split}
+		\end{equation}
+		\begin{equation}
+			\begin{split}
+				B_{2_{ijk}} = \frac{1}{\hbar} \sum_{v'} \frac{\partial M^{ge}_{i}}{\partial Q} 
+				\Lambda^{eg}_{0,jk} 
+				\mel{v}{Q}{v'} 
+				\langle v' | 0 \rangle 
+				\frac{1}{\Delta_{ev',g0}}
+			\end{split}
+		\end{equation}
+	\end{subequations}
+\end{widetext}
+where the electronic two photon absorption operator, $\Lambda$ was invoked to simplify summation over virtual states. \cite{McClain1977}
+It is clear from \autoref{ABterms_DR} that the Condon approximation breaks down for centrosymmetric molecules, as centrosymmetry invokes strict parity constraints that make states not accessible via both one and two photon transitions.
+This makes DR-HDFG a unique tool for studying the electronic structure of centrosymmetric species in isotropic media, as it is sensitive to non-Condon effects.
+A simulated spectrum highlighting the contributions of these terms (\autoref{fig:doubres_spec}) on potential wells with displacements $\Delta$ using arbitrary values listed in \autoref{T:hdfgvalues} show...
 \begin{figure}[!htbp]
@@
 	\includegraphics[width=3.375in]{drsive_spectrum.png}
-	\caption{Spectrum showing sensitivity of DR-HDFG to well displacements in vibronic coupling.
-		Model includes both Franck-Condon and Herzberg Teller effects.
-		(a) Potential energy surfaces, 2D spectrum where (b) $\Delta = 0$, (c) $\Delta = 0.5$, (d) $\Delta = 1$}
+	\caption{DR-HDFG $\gamma_{ijkl}$ spectrum for a simple two harmonic well system.
+		(a) Potential energy surface, (b) 2D DR-HDFG spectrum for $\Delta = 0.5$.}
 	\label{fig:doubres_spec}
@@
 
-%These results also make DR-HDFG a type of resonance IR spectroscopy, as introduced by Boyle et al for resonant triple sum frequency generation.\cite{RN491} 
-%However, in the methods described by \autoref{drgamma_alpha_0}, $|e)$ must be accessible through one and two photon transitions from $|g)$.
-%Conversely, the resonance-IR method demonstrated by Boyle et al. only requires one photon transitions between $|g)$ and $|e)$.
-%Systems which provide strict parity selection rules (e.g., benzene) will be useful for assessing the validity of these selection rules and comparing the method described here and that of Boyle et al.
-\cite{RN491}
+\begin{table}[!htbp]
+	\caption{\label{T:hdfgvalues} Values used to generate the 2D DR-HDFG plot. 
+	All Franck-Condon and Herzberg-Teller integrals are evaluated as tabulated by Carlson \cite{Carlson1988thesis}}
+	\begin{ruledtabular}
+		\begin{tabular}{cc}
+			Quantity & Value\\
+			\hline  
+			$\mel{g}{\mu}{v}$ & 0.1 D\\
+			I-b & No\\
+			II-a & No\\
+			II-a & No\\
+		\end{tabular}
+	\end{ruledtabular}
+\end{table}
 
@@
 The recorded $\chi^{(n)}$ values provide insight into how microscopic quantities ($\vec{\mu}, \alpha_{ij}, \beta_{ijk}$) impact nonlinear output.
-Calculating $\beta_{ijk}$ values from hyper-Raman experiments is difficult and has only been performed for a selection of molecular vibrations. \cite{Xu1997, Shoute2005, Kelley2010}
-Methods reported in the literature to measure absolute hyper-Raman polarizabilities depend upon external standards such as hyperpolarizabilities of dissolved samples or two-photon absorption cross sections (also difficult to measure).
+Calculating $\beta_{ijk}$ values from hyper-Raman experiments is difficult and has only been performed for a few molecular vibrations. \cite{Xu1997, Shoute2005, Kelley2010}
+Methods reported in the literature to measure absolute hyper-Raman polarizabilities depend upon external standards such as hyperpolarizabilities of dissolved samples or two-photon absorption cross sections, also difficult to measure.
 Since the Bloembergen interferometry experiment only relies on the third order susceptibility for measured species (such as benzene or CaF$_2$), it is possible to use quantitative four wave mixing spectroscopy to calculcate $\beta_{ijk}$ values.
@@
 \end{equation}
-Since $\abs{\mu}$ values can be readily extracted from FT-IR spectra,\cite{RN119, RN412} HDFG can give quantitative information on the magnitude of $\beta_{ijk}$.
+Since $\abs{\mu}$ values can be readily extracted from FT-IR spectra,\cite{RN109, RN412} HDFG can give quantitative information on the magnitude of $\beta_{ijk}$.
 
@@
 
-The third order response functions for \autoref{fig:sivewmel2}a ($R^{(3)}_{a}$) and \autoref{fig:sivewmel2}b ($R^{(3)}_{b}$) are 
+The third order response functions for the pathways detailed in \autoref{fig:sivewmel2} when $\omega_1$ and $\omega_3$ are temporally overlapped are 
 \begin{subequations}
 	\begin{equation} \label{mixing:a}
-		R^{(3)}_{a} (t_2) = -\frac{i}{\hbar} [\beta(t_2), \mu(0)] \exp(-i\Delta_{v''g}t_2) \theta(t_2)
+		R^{(3)}_{a} (t_2) = R^{(3)}_{c} (t_2) = -\frac{i}{\hbar} [\beta(t_2), \mu(0)] \exp(-i\Delta_{vg}t_2) \theta(t_2)
 	\end{equation}
@@
 		\begin{split}
-			R^{(3)}_{b} (t_2) & = \frac{i}{\hbar} [\beta(t_2), \mu(0)] \exp(-i\Delta_{v''g}t_2) \theta(t_2)\\
+			R^{(3)}_{b} (t_2) = R^{(3)}_{d} (t_2) & = \frac{i}{\hbar} [\beta(t_2), \mu(0)] \exp(-i\Delta_{vg}t_2) \theta(t_2)\\
 		\end{split}
@@
 \end{subequations}
-The total response function in this time ordering is therefore $R^{(3)}_\text{tot} (t_2) = R^{(3)}_{a} (t_2) + R^{(3)}_{b} (t_2) = 0$. 
+The total response function in this time ordering is therefore $R^{(3)}_\text{tot} (t_2) = R^{(3)}_{a} (t_2) + R^{(3)}_{b} (t_2) + R^{(3)}_{c} (t_2) + R^{(3)}_{d} (t_2) = 0$. 
 Since the total output response function vanishes in this time-ordering, the pathways in \autoref{fig:sivewmel2} perfectly destructively interfere.

### 2024-07-16 figures/wmels.py

@@ -60,23 +60,35 @@ if hdfg:
     fig.label_columns(['$(\mathsf{b})$'], font_size = 10)
 
 if timeorderedwmel:
-    fig = WMEL.Artist([2,1], [0, 0.2, 0.6, 1], state_names=("$\mathsf{| g\\rangle}$",
+    fig = WMEL.Artist([4,1], [0, 0.2, 0.4, 0.8, 1], state_names=("$\mathsf{| g\\rangle}$",
                                                                    "$\mathsf{|m\\rangle}$", 
-                                                                   "$\mathsf{|v''\\rangle}$",
-                                                                   "$\mathsf{|n\\rangle}$"), number_of_interactions=5, state_font_size=9, state_text_buffer = 0.6, virtual = [1,3])
+                                                                   "$\mathsf{|v\\rangle}$",
+                                                                   "$\mathsf{|n\\rangle}$",
+                                                                   "$\mathsf{|p\\rangle}$"), number_of_interactions=5, state_font_size=9, state_text_buffer = 0.6, virtual = [1,3,4])
 
     fig.add_arrow([0,0], 0, [0,2], kind='ket', color="k", label = "$\mathsf{2}$", head_length = 0.075)
     fig.add_arrow([0,0], 1, [0,1], kind='bra', color="k", label = "$\mathsf{1}$", head_length = 0.075)
-    fig.add_arrow([0,0], 2, [2,3], kind='ket', color="k", label = "$\mathsf{3}$", head_length = 0.075)
-    fig.add_arrow([0,0], 3, [3,1], kind='out', color="blue", label = "$\mathsf{4}$", head_length = 0.075)
+    fig.add_arrow([0,0], 2, [2,4], kind='ket', color="k", label = "$\mathsf{3}$", head_length = 0.075)
+    fig.add_arrow([0,0], 3, [4,1], kind='out', color="blue", label = "$\mathsf{4}$", head_length = 0.075)
     
     
     fig.add_arrow([1,0], 0, [0,2], kind='ket', color="k", label = "$\mathsf{2}$", head_length = 0.075)
     fig.add_arrow([1,0], 1, [2,1], kind='ket', color="k", label = "$\mathsf{1}$", head_length = 0.075)
[…]

### 2024-07-17 paper.tex
eds

@@
 \begin{abstract}
-Nonlinear, four wave mixing vibrational spectroscopies are often used to probe intramolecular vibrational coupling and relaxation dynamics.
+Nonlinear, four wave mixing vibrational spectroscopies are often used to probe intramolecular vibrational coupling and relaxation dynamics in isotropic media.
 Three wave mixing vibrational spectroscopies are similarly used to understand the spectroscopy and dynamics of interfacial species.
@@
 Hyper Difference Frequency Generation (hyper-DFG, or HDFG) spectroscopy, also known as singly vibrationally enhanced spectroscopy (SIVE), is an underdeveloped, hyper-Raman based four wave mixing vibrational spectroscopy.
-The spectroscopic and dynamic properties of HDFG have not been fully explored.
-We derive selection rules for singly resonant hyper-DFG and demonstrate it provides a simpler method to extract hyper-Raman polarizabilities ($\beta$).
-HDFG output is shown to be similar in magnitude to vibrational sum frequency generation (vSFG). 
-We demonstrate the properties and capabilities of HDFG through measuring spectra and coherence dynamics of multiple infrared active modes in CH$_3$CN.
-HDFG shows promise as a method to disentangle ultrafast vibrational dynamics in isotropic systems without need for anharmonicities.
+Despite several experimental reports on HDFG, its spectroscopic properties have not been fully explored.
+To this end, we explore the selection rules and response functions of HDFG spectroscopy.
+Through the hyper-Raman $A,B,C$ terms, we explore the selection rules of singly and doubly resonant HDFG spectroscopy, and show HDFG is a hybrid IR-hyper-Raman technique.
+HDFG is uniquely sensitive to non-Condon effects in molecular spectra.
+Through a simple comparison test, HDFG output is shown to be similar in magnitude to vibrational sum frequency generation (vSFG).
+Since HDFG can also be implemented as a two beam experiment, similar to vSFG, this makes HDFG a spectroscopy feasible for practitioners of vSFG.
+Through a simple treatment of orientational averaging, HDFG provides a simple method to extract hyper-Raman hyperpolarizabilities ($\beta$).
+HDFG shows promise as a method to disentangle vibrational spectra and dynamics in isotropic systems without need for anharmonicities.
 
@@
 \section{Introduction}
-Coherent multidimensional spectroscopy (CMDS) is a family of three and four wave mixing methods which form the optical analogue of multidimensional nuclear magnetic resonance (NMR) spectroscopy.\cite{RN103, Cho2008, RN335}
+Coherent multidimensional spectroscopy (CMDS) is a family of three and four wave mixing methods which form the optical analogue of multidimensional nuclear magnetic resonance (NMR) spectroscopy.\cite{RN103, Cho2008}
 Multiresonant, four wave mixing CMDS experiments, first proposed by Oudar and Shen in 1980,\cite{RN307} directly probe coupling between different vibrational, electronic, and vibronic states.
-\cite{RN307, RN281, RN103, RN342, Cho2008, RN335, Ogilvie2019, RN325}
-CMDS has resolved anharmonicities and other intramolecular couplings in numerous systems. \cite{RN345, RN342, RN343, RN324, RN329, RN120, Czech2015, Gaynor2017, Ogilvie2019, RN325}
-A particular class of CMDS methods, coherent Raman based four wave mixing spectroscopies, can provide explicit probes of these couplings in a variety of systems. \cite{RN103, RN335}
+\cite{RN307, RN281, RN103, RN342, Cho2008, Ogilvie2019, RN325}
+CMDS has resolved anharmonicities, ultrafast dynamics, and other intramolecular couplings in numerous systems. \cite{RN342, RN343, RN324, Czech2015, Gaynor2017, Ogilvie2019, RN325}
+
+Not all CMDS methods are used to dissect intramolecular couplings.\cite{Shen1987_CPL}
+The most well known example of such a spectroscopy is vibrational sum frequency generation (vSFG), a three wave mixing technique used to probe vibrational structure and dynamics at interfaces.
+\cite{Shen1987_CPL, RN224}
+Non-parametric, hyper difference frequency generation (hyper-DFG, or HDFG) spectroscopy, similar to difference frequency generation (\autoref{fig:comparisonwmel}), is a four wave mixing method which, when detuned from  electronic resonances, does not probe intramolecular couplings.
+HDFG was the first infrared CMDS method to successfully discriminate against non-resonant background.\cite{RN351, RN352}
+HDFG has also been referred to as singly vibrationally enhanced (SIVE) spectroscopy. \cite{RN351}
+In HDFG, an infrared pulse is resonant with a vibrational mode, and two other input pulses are used to stimulate a scattering process.
+HDFG was documented long ago to have characteristics similar to both infrared spectroscopy and spontaneous hyper-Raman scattering. \cite{RN352}
+Hyper-Raman scattering is the two photon analogue to Raman scattering. \cite{Cyvin1965, Terhune1965, Kozich2007}
+Hyper-Raman scattering cross sections are several orders of magnitude smaller than Raman scattering cross sections, making it a difficult process to detect.\cite{RN515, Kelley2010} 
+The different selection rules of hyper-Raman scattering, however, make it a unique alternative to Raman scattering to understand vibrational spectra and vibronic coupling in molecular systems.
+Some years ago, Cho et al. proposed parametric six wave mixing techniques as the coherent analogue of hyper-Raman scattering. \cite{Cho1997, Cho1998}
+However, since most six wave mixing methods cascade into four wave mixing processes and their homodyned output would be dependent upon the square magnitude of the hyper-Raman scattering cross section, \cite{RN243, RN515, Cho1997, Cho2000_Cascade} it is preferable to investigate coherent four wave mixing analogues to hyper-Raman scattering.
 
@@
 	\includegraphics[width=6.66in]{comparisonwmel.png}
-	\caption{Wave Mixing Energy Level (WMEL) diagrams of difference frequency generation (DFG), spontaneous Raman scattering, hyper difference frequency generation (HDFG) and spontaneous hyper-Raman scattering.
-\cite{RN286, RN352}
-		$\ket{g}$ is the ground state, $\ket{v}$ is an infrared active vibration and $\ket{m}, \ket{n}$ are virtual states.
+	\caption{Wave Mixing Energy Level (WMEL) diagrams of difference frequency generation (DFG), spontaneous Raman scattering, hyper difference frequency generation (HDFG) and spontaneous hyper-Raman scattering relevant to this discussion.
+\cite{RN286}
 	Solid and dashed horizontal lines indicate real and virtual states, whereas solid and dotted arrows indicate ket and bra side transitions, respectively. 
@@
 
-Not all CMDS methods are used to dissect intramolecular couplings.\cite{Shen1987_CPL}
-The most well known example is sum frequency generation (SFG), a three wave mixing technique used to interpret vibrational structure and dynamics at interfaces. \cite{RN224, Piontek2023}
-Non-parametric, hyper difference frequency generation (hyper-DFG, or HDFG) spectroscopy, similar to difference frequency generation (\autoref{fig:comparisonwmel}), is a four wave mixing method which, when detuned from  electronic resonances, does not probe intramolecular couplings.
-HDFG was the first infrared CMDS method to successfully discriminate against non-resonant background.\cite{RN351, RN352}
-HDFG has also been referred to as singly vibrationally enhanced (SIVE) spectroscopy. \cite{RN351}
-In HDFG, an infrared pulse is resonant with a vibrational mode, and two other input pulses are used to induce a scattering process to provide output.
-HDFG was documented long ago to have characteristics similar to spontaneous hyper-Raman scattering spectroscopy. \cite{RN352}
-Hyper-Raman scattering is the two photon analogue to Raman scattering. \cite{Cyvin1965, Terhune1965, Kozich2007}
-Compared to Raman spectroscopy, hyper-Raman scattering cross sections are often small, making it a difficult technique to successfully implement.\cite{RN515, Kelley2010} 
-The different selection rules of hyper-Raman scattering, however, make it a unique alternative to Raman scattering to understand vibrational spectra and vibronic coupling in molecular systems.
-Some years ago, Cho et al. proposed parametric six wave mixing techniques as the coherent analogue of hyper-Raman scattering. \cite{Cho1997, Cho1998}
-However, since most six wave mixing methods cascade into four wave mixing processes,\cite{RN243, Cho2000_Cascade}, and their output would be dependent upon the square magnitude of the hyper-Raman scattering cross section, a small number,\cite{RN515} it is preferable to investigate coherent four wave mixing analogues to hyper-Raman scattering.
-
 While HDFG showed promise as an upconverted infrared spectroscopy method, it was quickly supplemented by a doubly vibrationally resonant method, doubly vibrationally enhanced (DOVE) spectroscopy, to investigate intra- and intermolecular vibrational coupling.
 \cite{RN345, RN101, Cho2000}
-As a result, investigations of HDFG stagnated; to date, there are less than a dozen studies which report on HDFG.
-\cite{RN350, RN416, RN351, RN352, RN353, Chen1998, RN362, RN418, Bonn2024, McDonnell2024}
+As a result, investigations of HDFG stagnated; to date, there are roughly a dozen studies which report on HDFG.
+\cite{Zilian1994, RN350, RN416, RN351, RN352, RN353, Chen1998, RN362, RN418, Bonn2024, McDonnell2024}
 Recent reports highlight non-negligible HDFG interference in DOVE experiments as well as the suitability of HDFG pathways to interpret ultrafast relaxation dynamics in isotropic systems.
@@
 
-Inspired by recent work which demonstrated the presence of HDFG in ultrafast DOVE experiments, we investigate the parameters which result in both SR and DR-SIVE output.
+Inspired by recent work which demonstrated the presence of HDFG in ultrafast DOVE and terahertz-IR-visible (TIRV) experiments, we investigate the parameters which result in both SR and DR-SIVE output.
 \cite{Cho2000, Bonn2024, McDonnell2024}
-This paper is outlined as follows.
-In section \ref{steadystate}, we discuss the selection rules behind singly and doubly resonant HDFG first through the Placzek approximation, and then through hyper-Raman A,B,C coefficients.
-In section \ref{quant}, the quantitative aspects of HDFG are discussed, and a method to extract hyper-Raman hyperpolarizabilities ($\beta_{ijk}$) from HDFG spectra is identified.
-In section \ref{mixeddomain}, mixed time-frequency domain HDFG is discussed, and is applied to the simple case of CH$_3$CN in section \ref{Expt}.
-
-\section{Experimental}\label{experimental}
-The ultrafast laser system has been described in detail elsewhere. \cite{RN278}
-Briefly, an 80 MHz Ti-Sapphire ultrafast oscillator  (Spectra-Physics Tsunami) created 35 fs seed pulses, amplified by a 1 kHz regenerative amplifier (Spectra-Physics Spitfire Ace) to approximately 0.5 W.
-A mask in the regenerative amplifier stretched the input pulses to roughly 1 ps.
-The resultant output was used to pump four independent OPAs, two of which are relevant for this study.
-OPA1 (TOPAS-800, Light Conversion), referred to as $\omega_1$, was tuned for difference frequency generation (DFG) with an external stage (NDFG ``DF2'', Light Conversion).
-OPA2 (OPA-800C, Spectra Physics), referred to as $\omega_2$, was tuned in its signal arrangement. 
-OPA3, a homebuilt OPA, is tuned in its signal arrangement and referred to as $\omega_3$.
-Grating and crystal positions in OPA1 was externally controlled using \texttt{WinTOPAS} (Light Conversion).
-Grating and BBO crystal positions in OPA2 and OPA3 were computer controlled through communication with DC actuators.
-The OPAs were independently tuned through the \texttt{Attune} package, controlled by the \texttt{yaqc} and \texttt{Bluesky} packages. \cite{RN414, RN386, SkyeOPA, KyleOPA}
-The power spectra and tuning results are found in Figure X. %todo: actually graph these
-Movable retroreflectors (Thorlabs) controlled by 50 mm DC actuators (PMC) are used to measure coherence dynamics.
-The beams are focused using a BOXCARS geometry.\cite{RN308, Kaufman2024}
-To enforce frequency dependent temporal pulse overlap, the maximum points of a third order cross correlation between $\omega_1$ and $\omega_3$ measured in CaF$_2$ were used to generate frequency dependent zero delay values.
-The nonlinear output was isolated through chopping schemes and a set of spatial apertures, directed into a monochromator (Horiba Micro-HR) and homodyne detected through a photomultiplier tube (Hamamatsu H7422-20), recorded and converted to digital output using a data acquisition unit (National Instruments).
-\textit{in-situ} power corrections are performed by dividing the recorded spectra by OPA output measured by home-built pyroelectric detectors.
-All spectra are reported on the intensity scale.
-
-The cyanocobalamin (CNCbl) [DOT Scientific inc., CAS no. 68-19-9] samples were prepared as drop casted thin films.
-CNCbl was dissolved in methanol (MeOH) [Fisher Scientific, HPLC Grade, CAS no. 67-56-1] until a concentrated solution was formed (concentration $\sim$ 10 mg CNCbl/ mL MeOH). 
-All chemicals were used as obtained without further purification.
-The solution was deposited on a microscope coverslip and allowed to dry in a dessicator until a thin layer was formed.
+This paper is organized as follows.
+In \autoref{steadystate}, we identify the selection rules that drive singly and doubly resonant HDFG, first through the Placzek approximation, and then through hyper-Raman $A,B,C$ coefficients.
+Quantitative aspects of HDFG: a comparison of vSFG and HDFG output, a method to extract hyper-Raman hyperpolarizabilities ($\beta_{ijk}$) from HDFG spectra, are discussed in \autoref{quant}.
+Mixed time-frequency domain HDFG is discussed in \autoref{mixeddomain}.
 
 \section{Steady State HDFG Spectroscopy}\label{steadystate}
-\subsection{Placzek Method}
+
 Singly resonant hyper difference generation spectroscopy (HDFG) spectroscopy has potential to provide deeper insight into single quantum decoherence times and molecular orientation in condensed systems.
@@
 To make the connection between HDFG and hyper-Raman scattering, we investigate its gross selection rules.
-By propagating density matrix elements in the steady state limit, the HDFG hyperpolarizability is \cite{RN119}
+By propagating density matrix elements in the steady state limit, the HDFG hyperpolarizability is \cite{RN133}
 \begin{equation}\label{sivegamma}
-		\gamma_{ijkl} =	- \sum_{m, n} \frac{1}{\varepsilon_0} \frac{1}{4D} \frac{1}{\hbar^3} \frac{\mu^{vn}_{i} \mu^{nm}_{j} \mu^{mg}_{k} \mu^{gv}_{l} }{\Delta_{nv} \Delta_{mv}\Delta_{gv}}  \rho_{gg}
+		\gamma_{ijkl}^{gv} =	- \sum_{m, n} \frac{1}{\varepsilon_0} \frac{1}{4D} \frac{1}{\hbar^3} \frac{\mu^{vn}_{i} \mu^{nm}_{j} \mu^{mg}_{k} \mu^{gv}_{l} }{\Delta_{nv} \Delta_{mv}\Delta_{gv}}  \rho_{gg}
 \end{equation}
-where: $\mu^{ab}_{j}$ is the $j^{th}$ element of $\mel{a}{\vec{\mu}}{b}$, $\Delta_{kl} = \omega_{kl} - \omega_{j} - i\Gamma_{kl}$, $\omega_j$ is the frequency of the j$^{th}$ input field, $\Gamma_{kl}$ is the dephasing of $\rho_{kl}$ and $\rho_{gg}$ is the ground state population.
+where: $\mu^{ab}_{j}$ is the $j^{th}$ element of $\mel{a}{\vec{\mu}}{b}$, $\Delta_{kl} = \omega_{kl} - \omega_{j} - i\Gamma_{kl}$ (also known as a resonance denominator), $\omega_j$ is the frequency of the j$^{th}$ input field, $\Gamma_{kl}$ is the dephasing of $\rho_{kl}$ and $\rho_{gg}$ is the ground state population.
 D, the Maker-Terhune degeneracy factor, accounts for permutation symmetry in $\gamma_{ijkl}$.\cite{RN134} 
-For a HDFG experiment using two or three distinct input fields, as considered here, D = 6.
+For a HDFG experiment using two (three) distinct input fields, D = 3 (6).
+
+\subsection{Placzek Method}
 We first investigate the selection rules through a Placzek type formalism.
 Contracting over the virtual states forms the hyper-Raman hyperpolarizability $\beta$.\cite{Long1970} 
-Assuming $\omega_2$, $\omega_3$ are significantly detuned from any local resonance (\autoref{fig:comparisonwmel}),\cite{Placzek1934, Long1970} \autoref{sivegamma} is written as 
+Assuming $\omega_2$, $\omega_3$ are significantly detuned from any resonance (\autoref{fig:comparisonwmel}),\cite{Placzek1934, Long1970} \autoref{sivegamma} is written as 
 \begin{equation}\label{sivebeta}
-	\gamma_{ijkl} =	-\frac{1}{\varepsilon_0} \frac{1}{24 \hbar}\frac{\beta^{gv}_{ijk} \mu^{gv}_{l}}{\Delta_{gv}} \rho_{gg}
+	\gamma_{ijkl}^{gv} =	-\frac{1}{\varepsilon_0} \frac{1}{4D \hbar}\frac{\beta^{gv}_{ijk} \mu^{gv}_{l}}{\Delta_{gv}} \rho_{gg}
 \end{equation}
-It is important to note that the properties of $\beta_{ijk}$ change dependent upon whether $\omega_2$ and $\omega_3$ are degenerate. \cite{Andrews1978, Altmann1982}
-Taylor expanding the dipole and first hyperpolarizability operators in terms of an n$^{\text{th}}$ normal mode coordinate $Q_n$ about equilibrium as\cite{Long1970}
+It is important to note that the symmetry properties of $\beta_{ijk}$ change dependent upon whether $\omega_2$ and $\omega_3$ are degenerate. \cite{Andrews1978, Altmann1982}
+Taylor expanding the dipole and first hyperpolarizability operators in terms of an n$^{\text{th}}$ reduced normal mode coordinate $Q_n$ about equilibrium as\cite{Long1970, Shen90}
 \begin{subequations}
 	\begin{equation}
-		\mu = \mu_0 + \frac{\partial \mu}{\partial Q_n} Q_n + \order{{Q_m Q_n}}
+		\mu_l = \mu_{l,0} + \left(\frac{\partial \mu_l}{\partial Q_n}\right)_0 Q_n + \order{{Q_m Q_n}}
 	\end{equation}
 	\begin{equation}
-		\beta = \beta_{0} + \frac{\partial \beta}{\partial Q_n} Q_n + \order{{Q_m Q_n}}
+		\beta_{ijk} = \beta_{ijk,0} + \left(\frac{\partial \beta_{ijk}}{\partial Q_n}\right)_0 Q_n + \order{{Q_m Q_n}}
 	\end{equation}
@@
 and substituting into \autoref{sivebeta} gives the HDFG hyperpolarizability to $\order{Q_n}$ as \begin{equation}\label{SIVEselection}
-	\gamma_{ijkl} =	-\frac{1}{\varepsilon_0} \frac{1}{48 m_n \omega_{vg}}  \frac{1}{{\Delta_{gv}}} \ \frac{\partial \beta^{gv}_{ijk}}{\partial Q_n} {\frac{\partial \mu^{gv}_{l}}{\partial Q_n}}  \rho_{gg}
+	\gamma_{ijkl}^{gv} =	-\frac{1}{\varepsilon_0} \frac{1}{8D m_n \omega_{vg}}  \frac{1}{{\Delta_{gv}}} \ \left(\frac{\partial \beta^{gv}_{ijk}}{\partial Q_n}\right)_0 \left({\frac{\partial \mu^{gv}_{l}}{\partial Q_n}}\right)_0  \rho_{gg}
 \end{equation}
-where $\mel{v}{Q_n}{g} = \sqrt{\frac{\hbar}{2m_n\omega_{vg}}}$ and $m_n$ is the ``mass'' of the $Q_n$ mode.  \cite{RN230}
+where $\mel{v}{Q_n}{g} = \sqrt{\frac{\hbar}{2\omega_{vg}}}$.  \cite{RN230}
 Since this expression is non-zero in the harmonic oscillator limit, HDFG output is allowed for harmonic transitions. 
@@
 \subsection{Albrecht Type Expansion}
-While Placzek type arguments provide the general source of HDFG output, it is insightful to interpret the origin of signal in terms of Albrecht ABC type terms.\cite{Ziegler1988} 
-We write $\beta_{ijk}$ in \autoref{SIVEselection} using the hyper-Raman ABC formalism to understand how vibronic coupling manipulates selection rules for singly and doubly resonant HDFG (\autoref{fig:hdfg}).
+While Placzek type arguments provide the general source of HDFG output, it is insightful to interpret the origin of signal in terms of $A,B,C$ terms, analogous to those found in Albrecht's treatment of Raman spectroscopy.\cite{Albrecht1961, Ziegler1988}
+We write $\beta_{ijk}$ in \autoref{SIVEselection} using the hyper-Raman ABC formalism introduced by Chung and Ziegler to understand how vibronic coupling manipulates selection rules for singly and doubly resonant HDFG (\autoref{fig:hdfg}).
 \cite{Ziegler1988, Baranov1990}
@@
 The states are labeled as shown in \autoref{fig:hdfg}.
-For consistency with previous reports, we use $\vec{R}$ to denote electric transition dipole moments ($\vec{\mu}$ is reserved for transitions between states on the ground electronic state).
-\cite{Tang1970}
+For consistency with previous reports, we use $\vec{R}$ to denote electric transition dipole moments ($\vec{\mu}$ is reserved for transitions on the ground electronic state). \cite{Tang1970}
 Following the approach which gave \autoref{sivegamma}, we find
 \begin{equation}\label{drgamma_notaylor}
-	\gamma_{ijkl} = -\frac{1}{\varepsilon_0} \frac{1}{24 \hbar^3} \sum_{m,n,e,v'} \frac{
+	\gamma_{ijkl} = -\frac{1}{\varepsilon_0} \frac{1}{4D \hbar^3} \sum_{m,n,e,v'} \frac{
 		R_{i}^{gv, ev'} 
@@
 where $R_{i}^{ab,cd}$ is the i$^{th}$ element of $\mel{a,b}{\vec{R}}{c,d}$.
+It is common in the hyper-Raman community to write $\Delta_{ev', mn} \Delta_{mn, g0} = \Delta_{ev', g0}$.
 Using our definition of vibronic states, we write $\vec{M}^{ab} = (a|\vec{M}|b)$ so that, for example,
@@
 	\begin{split}
-		\gamma_{ijkl} &= -\frac{1}{\varepsilon_0} \frac{1}{24 \hbar^3} \sum_{m,n,e,v'} \frac{
+		\gamma_{ijkl} &= -\frac{1}{\varepsilon_0} \frac{1}{4D \hbar^3} \sum_{m,n,e,v'} \frac{
 			\mel{v}{M_{i}^{ge}}{v'} 
@@
 		}{\Delta_{g0,gv}
-			\Delta_{ev', mn}
-			\Delta_{mn, g0}	} \\
+			\Delta_{ev',g0}	} \\
 	\end{split}
@@
 Chung and Ziegler showed some years ago that expanding $\vec{M}^{ij}$ to $\order{Q}$ as
-\begin{equation}
-\vec{M}^{ij} = \vec{M}^{ij}_0 + \sum_z \frac{\partial\vec{M}^{ij}}{\partial Q_z} Q_z
-\end{equation} 
+$\vec{M}^{ij} = \vec{M}^{ij}_0 + \sum_z \frac{\partial\vec{M}^{ij}}{\partial Q_z} Q_z$
 yields $A, B, C$ coefficients similar to those in the Albrecht formalism of Raman scattering, \cite{Albrecht1961, Ziegler1988} so that
@@
 		 \langle v' | 0 \rangle 
-		 \frac{1}{\Delta_{ev',m} \Delta_{m, g0}}
+		 \frac{1}{\Delta_{ev', g0}}
 		 \\
@@
 		\begin{split}
-			B_{1_{ijk}} &= \frac{1}{\hbar^2} \sum_{m,e,v',z} M^{ge}_{0,i} \langle v | v' \rangle \lbrack
+			B_{1_{ijk}} &= \frac{1}{\hbar^2} \sum_{m,e,v',z} M^{ge}_{0,i} \langle v | v' \rangle \left(
 			 \frac{\partial M^{em}_{j}}{\partial Q_z} M^{mg}_{0,k} \mel{v'}{Q_z}{0} 
-			+M^{em}_{0,j} \frac{\partial M^{mg}_{k}}{\partial Q_z} \mel{v'}{Q_z}{0} \rbrack \frac{1}{\Delta_{ev',m} \Delta_{m, g0}}\\
+			+M^{em}_{0,j} \frac{\partial M^{mg}_{k}}{\partial Q_z} \mel{v'}{Q_z}{0} \right) \frac{1}{\Delta_{ev', g0}}\\
 		\end{split}
@@
 			\langle v' | 0 \rangle 
-			\frac{1}{\Delta_{ev',m} \Delta_{m, g0}}
+			\frac{1}{\Delta_{ev', g0}}
 	\end{split}
@@
 \end{widetext}
-where terms such as $\langle a | b \rangle$ are Franck-Condon factors. 
+where terms such as $\langle a | b \rangle$ and $\mel{a}{Q}{b}$ are Franck-Condon factors and Herzberg-Teller-type integrals, respectively. 
 These expressions are valid for both singly and doubly resonant HDFG, but based upon the resonance schemes, further simplifications can be made (\textit{vide infra}).
@@
 In the case of singly resonant HDFG, $\omega_3$ is also detuned from any resonance, which permits contraction over ${v'}$ as the dependence on $\ket{v'}$ in the resonance denominator can be neglected.
-Assuming a normal mode basis, we see for singly resonant HDFG that 
+This limit is usually reached when $\abs{\omega_{ev',g0} - (\omega_2 + \omega_3)} \gg 2\Gamma_{ev',g0}$.
+In such a limit, assuming a normal mode basis, we see for singly resonant HDFG that 
 \begin{subequations}
@@
 \begin{equation}
-	B_{1_{ijk}} = \frac{1}{\hbar^2} \sum_{m,e,z} M^{ge}_{0,i} \lbrack
+	B_{1_{ijk}} = \frac{1}{\hbar^2} \sum_{m,e,z} M^{ge}_{0,i} \left( 
 	\frac{\partial M^{em}_{j}}{\partial Q_z} M^{mg}_{0,k}
-	+M^{em}_{0,j} \frac{\partial M^{mg}_{k}}{\partial Q_z} \rbrack \frac{\mel{v}{Q_z}{0}}{\Delta_{e,m} \Delta_{m, g0}}
+	+M^{em}_{0,j} \frac{\partial M^{mg}_{k}}{\partial Q_z} \right) \frac{\mel{v}{Q_z}{0}}{\Delta_{e, g0}}
 \end{equation}
@@
 	M^{mg}_{0,k}  
-	\frac{\mel{v}{Q_z}{0}}{\Delta_{e,m} \Delta_{m, g0}}
+	\frac{\mel{v}{Q_z}{0}}{\Delta_{e, g0}}
 \end{equation}
@@
 i.e., A$_{ijk}$ vanishes, but B$_{ijk}$ is non-zero, for singly resonant HDFG. 
-The singly resonant HDFG susceptibility can be approximated as 
-\begin{equation}
-	\chi^{(3)}_{IJKL} \sim \langle B_{ijk} \mu_l \rangle
-\end{equation}
-or, while a vibrational mode must be infrared active for HDFG output, vibronic activity is necessary for singly resonant HDFG response.
+When $\abs{\omega_{ev',g0} - (\omega_2 + \omega_3)} \gtrsim \Gamma_{ev',g0}$, $\Re(\frac{1}{\Delta_{ev', g0}})$ can allow for small $A$ term contributions.
+As such, $A$ usually only vanishes for highly detuned electronic states. 
+In the limit where $A$ vanishes, the singly resonant HDFG susceptibility can be approximated as $\chi^{(3)}_{IJKL} \sim \langle B_{ijk} \mu_l \rangle$, or, while a vibrational mode must be infrared active for HDFG output, vibronic activity is necessary for singly resonant HDFG response.
 The breakdown of the Condon approximation in singly resonant HDFG supports the relatively small HDFG $\chi^{(3)}$ values ($\sim$ order of magnitude larger than nonresonant background) in hexane and similar organic solvents.
 \cite{RN350, RN351, RN353}
+
+%todo: more on B term
 \subsubsection{Doubly Resonant HDFG}
@@
 The impact of vibronic coupling in the 2D spectrum is made clear by using a simple model.
-Using a two-well system described by $H_g = p^2/2m + 1/2 \hbar \omega q^2$ and $H_e = p^2/2m + 1/2 \hbar \omega (q-\Delta)^2 +\hbar \omega_{eg}$, the A and B contributions can be easily evaluated using Franck-Condon and Herzberg-Teller integrals tabulated elsewhere.
+Using a two-well system described by $H_g = p^2/2m + 1/2 \hbar \omega Q^2$ and $H_e = p^2/2m + 1/2 \hbar \omega (Q-\Delta)^2 +\hbar \omega_{eg}$, the A and B contributions can be easily evaluated using Franck-Condon and Herzberg-Teller integrals tabulated elsewhere.
 \cite{Carlson1988thesis}
 By working only in terms of a single normal mode (i.e.
-removing the sum over $z$) and assuming electronic transitions occur only between $|g), |e)$ and that $v' = \{0,1,2\}$, the A and B terms are rewritten as
+removing the sum over $z$) and assuming electronic transitions occur only between $|g), |e)$ and that $v =1$, $v' = \{0,1,2\}$, the A and B terms are rewritten as
 \begin{widetext}
@@
 				\Lambda^{eg}_{0,jk}
-				\langle v | v' \rangle
+				\langle 1 | v' \rangle
 				\langle v' | 0 \rangle 
@@
 			\begin{split}
-				B_{1_{ijk}} &= \frac{1}{\hbar^2} \sum_{v',m} M^{ge}_{0,i} \langle v | v' \rangle \lbrack
+				B_{1_{ijk}} &= \frac{1}{\hbar^2} \sum_{v',m} M^{ge}_{0,i} \langle 1 | v' \rangle \left(
 				\frac{\partial M^{em}_{j}}{\partial Q} M^{mg}_{0,k} \mel{v'}{Q}{0} 
-				+M^{em}_{0,j} \frac{\partial M^{mg}_{k}}{\partial Q} \mel{v'}{Q}{0} \rbrack \frac{1}{\Delta_{ev',m} \Delta_{m, g0}}\\
+				+M^{em}_{0,j} \frac{\partial M^{mg}_{k}}{\partial Q} \mel{v'}{Q}{0} \right) \frac{1}{\Delta_{ev', g0}}\\
 			\end{split}
@@
 				\Lambda^{eg}_{0,jk} 
-				\mel{v}{Q}{v'} 
+				\mel{1}{Q}{v'} 
 				\langle v' | 0 \rangle 
@@
 It is clear from \autoref{ABterms_DR} that the Condon approximation breaks down for centrosymmetric molecules, as centrosymmetry invokes strict parity constraints that make states not accessible via both one and two photon transitions.
-This makes DR-HDFG a unique tool for studying the electronic structure of centrosymmetric species in isotropic media, as it is sensitive to non-Condon effects.
+This makes DR-HDFG a unique tool for studying the electronic structure of centrosymmetric species in isotropic media, as it is sensitive to non-Condon effects. \cite{Olson2018}
 A simulated spectrum highlighting the contributions of these terms (\autoref{fig:doubres_spec}) on potential wells with displacements $\Delta$ using arbitrary values listed in \autoref{T:hdfgvalues} show...
@@
 \begin{split}
-		\chi^{(3)}_{IJKL} &= NF(\omega_4) \langle \gamma_{ijkl} \rangle = -\frac{NF}{24 \hbar \varepsilon_0 \Delta_{gv}} \langle \beta_{ijk} \mu_l \rangle \rho_{gg}\\
+		\chi^{(3)}_{IJKL} &= NF(\omega_4) \langle \gamma_{ijkl} \rangle = -\frac{NF}{4D \hbar \varepsilon_0 \Delta_{gv}} \langle \beta_{ijk} \mu_l \rangle \rho_{gg}\\
 \end{split}
@@
 \begin{equation}
-	\langle \beta_{ijk} \mu_{l} \rangle = \frac{24 \hbar \varepsilon_0}{NF} \Gamma_{gv} \frac{1}{\rho_{gg}} \Im(\chi^{(3)}_{IJKL})
+	\langle \beta_{ijk} \mu_{l} \rangle = \frac{4D \hbar \varepsilon_0}{NF} \Gamma_{gv} \frac{1}{\rho_{gg}} \Im(\chi^{(3)}_{IJKL})
 \end{equation}
@@
 \begin{equation}\label{betasive}
-	\langle \frac{\partial \beta_{ijk}}{\partial q_n} {\frac{\partial \mu_l}{\partial q_n}} \rangle = \frac{48 \varepsilon_0}{NF}  \frac{\Gamma_{gv} \omega_{vg}}{\rho_{gg}} {\Im(\chi^{(3)}_{IJKL})}
+	\langle \frac{\partial \beta_{ijk}}{\partial q_n} {\frac{\partial \mu_l}{\partial q_n}} \rangle = \frac{8D \varepsilon_0}{NF}  \frac{\Gamma_{gv} \omega_{vg}}{\rho_{gg}} {\Im(\chi^{(3)}_{IJKL})}
 \end{equation}

### 2024-07-17 figures/2D_spec.py

@@ -67,9 +67,11 @@ def f01(q): #<0|1>
 def f10(q): #<1|0>
     return -1*f01(q)
 
-def f02(q): #<2|0> = <0|2>
+def f02(q): #<0|2>
     return q**2/(2*np.sqrt(2)) * f00(q)
 
+def f20(q): #<2|0>
+    return f02(q)
 
 #define Herzberg Teller overlap integrals following page 165 of Roger Carlson's thesis in terms of Delta
 def h00(q): #<0|Q|0>
@@ -81,7 +83,7 @@ def h01(q): #<0|Q|1>
 def h10(q): #<1|Q|0>
     return 1/np.sqrt(2) * (1 - q**2 /2) * f00(q)
 
-def h11(q):
+def h11(q): #<1|Q|1>
     return -q/2 * (1 - q**2 / 2) * f00(q)
 
 

### 2024-07-17 paper.tex
ed

@@
 Through the hyper-Raman $A,B,C$ terms, we explore the selection rules of singly and doubly resonant HDFG spectroscopy, and show HDFG is a hybrid IR-hyper-Raman technique.
-HDFG is uniquely sensitive to non-Condon effects in molecular spectra.
+Since all infrared active modes have non-zero hyper-Raman activity, this makes HDFG a type of upconverted infrared spectroscopy.
+HDFG is found to be uniquely sensitive to non-Condon effects in molecular spectra.
 Through a simple comparison test, HDFG output is shown to be similar in magnitude to vibrational sum frequency generation (vSFG).
 Since HDFG can also be implemented as a two beam experiment, similar to vSFG, this makes HDFG a spectroscopy feasible for practitioners of vSFG.
-Through a simple treatment of orientational averaging, HDFG provides a simple method to extract hyper-Raman hyperpolarizabilities ($\beta$).
+Through a simple treatment of orientational averaging, HDFG provides a simple method to extract hyper-Raman hyperpolarizabilities ($\beta$) of infrared active vibrations.
 HDFG shows promise as a method to disentangle vibrational spectra and dynamics in isotropic systems without need for anharmonicities.
@@
 Coherent multidimensional spectroscopy (CMDS) is a family of three and four wave mixing methods which form the optical analogue of multidimensional nuclear magnetic resonance (NMR) spectroscopy.\cite{RN103, Cho2008}
-Multiresonant, four wave mixing CMDS experiments, first proposed by Oudar and Shen in 1980,\cite{RN307} directly probe coupling between different vibrational, electronic, and vibronic states.
-\cite{RN307, RN281, RN103, RN342, Cho2008, Ogilvie2019, RN325}
+Multiresonant, four wave mixing CMDS experiments, first proposed by Oudar and Shen in 1980,\cite{RN307} directly probe coupling and correlations between different vibrational, electronic, and vibronic states.
+\cite{RN307, RN281, RN103, RN342, Cho2008, Dong2015, Ogilvie2019, RN325}
 CMDS has resolved anharmonicities, ultrafast dynamics, and other intramolecular couplings in numerous systems. \cite{RN342, RN343, RN324, Czech2015, Gaynor2017, Ogilvie2019, RN325}
@@
 Hyper-Raman scattering is the two photon analogue to Raman scattering. \cite{Cyvin1965, Terhune1965, Kozich2007}
-Hyper-Raman scattering cross sections are several orders of magnitude smaller than Raman scattering cross sections, making it a difficult process to detect.\cite{RN515, Kelley2010} 
-The different selection rules of hyper-Raman scattering, however, make it a unique alternative to Raman scattering to understand vibrational spectra and vibronic coupling in molecular systems.
+Hyper-Raman scattering cross sections are commonly several orders of magnitude smaller than Raman scattering cross sections, making hyper-Raman a difficult process to detect.\cite{RN515, Kelley2010} 
+The different selection rules of hyper-Raman scattering make it a unique alternative to Raman scattering to understand vibrational spectra and vibronic coupling in molecular systems. \cite{Olson2018}
 Some years ago, Cho et al. proposed parametric six wave mixing techniques as the coherent analogue of hyper-Raman scattering. \cite{Cho1997, Cho1998}
-However, since most six wave mixing methods cascade into four wave mixing processes and their homodyned output would be dependent upon the square magnitude of the hyper-Raman scattering cross section, \cite{RN243, RN515, Cho1997, Cho2000_Cascade} it is preferable to investigate coherent four wave mixing analogues to hyper-Raman scattering.
+However, since most six wave mixing methods cascade into four wave mixing processes and their homodyned output would be dependent upon the square magnitude of the hyper-Raman scattering cross section, \cite{RN243, RN515, Cho1997, Cho2000_Cascade} it is preferable to investigate four wave mixing analogues to hyper-Raman scattering.
 
@@
 \cite{Bonn2024, McDonnell2024}
-These reports motivate deeper analysis on the properties of HDFG spectroscopy.
+These reports motivate deeper analysis of HDFG spectroscopy.
 
@@
 \end{equation}
-It is important to note that the symmetry properties of $\beta_{ijk}$ change dependent upon whether $\omega_2$ and $\omega_3$ are degenerate. \cite{Andrews1978, Altmann1982}
+It is important to note that the symmetry properties of $\beta_{ijk}$ change dependent upon whether $\omega_2$ and $\omega_3$ are degenerate. \cite{Denisov1986}
 Taylor expanding the dipole and first hyperpolarizability operators in terms of an n$^{\text{th}}$ reduced normal mode coordinate $Q_n$ about equilibrium as\cite{Long1970, Shen90}
@@
 In the limit where $A$ vanishes, the singly resonant HDFG susceptibility can be approximated as $\chi^{(3)}_{IJKL} \sim \langle B_{ijk} \mu_l \rangle$, or, while a vibrational mode must be infrared active for HDFG output, vibronic activity is necessary for singly resonant HDFG response.
-The breakdown of the Condon approximation in singly resonant HDFG supports the relatively small HDFG $\chi^{(3)}$ values ($\sim$ order of magnitude larger than nonresonant background) in hexane and similar organic solvents.
+The breakdown of the Condon approximation in singly resonant HDFG supports the relatively small HDFG $\chi^{(3)}$ values ($\sim$ order of magnitude larger than nonresonant background) for hexane and similar organic solvents.
 \cite{RN350, RN351, RN353}
@@
 
-The impact of vibronic coupling in the 2D spectrum is made clear by using a simple model.
-Using a two-well system described by $H_g = p^2/2m + 1/2 \hbar \omega Q^2$ and $H_e = p^2/2m + 1/2 \hbar \omega (Q-\Delta)^2 +\hbar \omega_{eg}$, the A and B contributions can be easily evaluated using Franck-Condon and Herzberg-Teller integrals tabulated elsewhere.
-\cite{Carlson1988thesis}
 By working only in terms of a single normal mode (i.e.
@@
 This makes DR-HDFG a unique tool for studying the electronic structure of centrosymmetric species in isotropic media, as it is sensitive to non-Condon effects. \cite{Olson2018}
-A simulated spectrum highlighting the contributions of these terms (\autoref{fig:doubres_spec}) on potential wells with displacements $\Delta$ using arbitrary values listed in \autoref{T:hdfgvalues} show...
+The lineshapes of electronic-vibrational coupling probed by DR-HDFG can inform on electronic-vibrational correlations. \cite{Carlson1990line,Dong2015}
+These effects are under investigation and will the subject of a future publication.
+
+The impact of vibronic coupling in the 2D spectrum is made clear by using a simple model.
+Using a two-well system described by $H_g = p^2/2m + 1/2 \hbar \omega Q^2$ and $H_e = p^2/2m + 1/2 \hbar \omega (Q-\Delta)^2 +\hbar \omega_{eg}$, the A and B contributions can be easily evaluated using Franck-Condon and Herzberg-Teller integrals tabulated elsewhere.
+\cite{Carlson1988thesis}
+A simulated spectrum highlighting the contributions of these terms (\autoref{fig:doubres_spec}) on potential wells with $\Delta = 0.5$ using values listed in \autoref{T:hdfgvalues} dissects the $A$ and $B$ contributions to the DR-SIVE spectrum.
+
 \begin{figure}[!htbp]
@@
 
-Since the hyper-Raman process is stimulated by a two-photon process, a setup using only one optical parametric amplifier can perform a coherent four wave mixing hyper-Raman experiment by investigating $\pm \vec{k}_1 + 2\vec{k}_2$ processes (i.e.
+Since the hyper-Raman process is stimulated by a two-photon process, a setup using only one optical parametric amplifier can perform a coherent four wave mixing hyper-Raman experiment by investigating $-\vec{k}_1 + 2\vec{k}_2$ processes (i.e.
 two laser CMDS), assuming a two photon absorption from a single pulse stimulates the hyper-Raman process.
-The most commonly used two laser CMDS method is sum frequency generation, a $\chi^{(2)}$ technique whose phasematching is dictated by $\vec{k}_1 + \vec{k}_2$.
+The most commonly used two laser CMDS method is vibrational sum frequency generation (vSFG), a $\chi^{(2)}$ technique whose phasematching is dictated by $\vec{k}_1 + \vec{k}_2$.
 SFG output scales as $\chi^{(2)}_{IJK} \sim \langle \alpha_{ij} \mu_k \rangle$, where $\alpha_{ij}$ is the Raman polarizability tensor.
-Since SFG is dependent upon transitions that transform like both rank-one and rank-two tensors, parity enforces a microscopic constraint that SFG cannot yield output for centrosymmetric species under the electric dipole approximation due to the presence of an inversion center.
-\cite{RN230}
-Macroscopically, oddness in spatial inversion of the output polarization eliminates output from centrosymmetric species under the electric dipole approximation.\cite{RN133, RN132}
-As a result, the output of SFG is significantly reduced relative to most third order spectroscopies because the output depends on surface species.
-However, since HDFG is dependent upon a hyper-Raman transition, it is useful to compare the relative output of the two processes to identify how HDFG output compares to SFG.
+Both processes can be phasematched in media with normal indicies of refraction, unlike the $\vec{k}_1 + 2\vec{k}_2$ process.\cite{RN120}
+Macroscopically, oddness in spatial inversion of the vSFG polarization eliminates output from centrosymmetric species under the electric dipole approximation.\cite{RN132, RN133}
+As a result, the output of vSFG is significantly reduced relative to most third order spectroscopies because the output depends on surface number density, many orders of magnitude smaller than the bulk surface density.
+However, since HDFG is dependent upon a hyper-Raman transition, which is several orders of magnitude weaker than Raman transitions,\cite{RN515} it is useful to identify how HDFG output compares to vSFG.
 
-To motivate the application of HDFG spectroscopy, we perform a calculation to compare HDFG and vibrational SFG (vSFG) output.
+To motivate the application of HDFG spectroscopy, we perform a calculation to compare HDFG and vSFG output.
 Absorption effects are neglected for simplicity.
@@
 	\begin{equation}
-		\abs{P^{(2)}_{\text{SFG}}} = N_{surf} F(\omega_1+\omega_2) \abs{\langle \alpha_{ij}\mu_{k} \rangle E(\omega_2)E(\omega_1)} 
+		\abs{P^{(2)}_{\text{vSFG}}} = N_{surf} F(\omega_1+\omega_2) \abs{\langle \alpha_{ij}\mu_{k} \rangle E(\omega_2)E(\omega_1)} 
 	\end{equation}
@@
 \begin{equation}
-		P_{ratio} \equiv \frac{\abs{P^{(3)}_{\text{HDFG}}}}{\abs{P^{(2)}_{\text{SFG}}}} \approx \frac{N_{bulk}}{N_{surf}} \frac{\beta}{\alpha} E(\omega_2) \ell_{eff} \sim 10^4 \frac{\beta}{\alpha} E(\omega_2)\\
+		P_{ratio} \equiv \frac{\abs{P^{(3)}_{\text{HDFG}}}}{\abs{P^{(2)}_{\text{vSFG}}}} \approx \frac{N_{bulk}}{N_{surf}} \frac{\beta}{\alpha} E(\omega_2) \ell_{eff} \sim 10^4 \frac{\beta}{\alpha} E(\omega_2)\\
 \end{equation}
-Ziegler has noted that for a field of intensity 10 GW/cm$^{2}$, $\frac{\beta E}{\alpha} \sim 10^{-3} $ for vibrational modes when $E(\omega_2)$ is largely detuned from electronic resonances.
+Ziegler has noted that for a field with intensity 10 GW/cm$^{2}$, $\frac{\beta E}{\alpha} \sim 10^{-3} $ for vibrational modes when $E(\omega_2)$ is largely detuned from electronic resonances.
 \cite{RN515}
@@
 
-With the selection rules of HDFG understood for vibrational spectroscopy, it becomes possible to extract quantitative information from its spectra.
+With the selection rules of HDFG understood for vibrational spectroscopy, and with HDFG generating a large enough output polarization, it becomes possible to extract quantitative information from its spectra.
 Lineshape analysis is essential for extracting quantitative information from CMDS spectra.
@@
 Self-heterodyning of the internal standard signal measures $\chi^{(3)}$ and does not require measurement of absolute intensities. 
-Resonant lineshapes are also complicated by amplitude level interference between the sample and its substrate and/or sample cell windows, which must be accounted for to obtain quantitatively correct $\chi^{(3)}$ values.
+Resonant lineshapes are also complicated by amplitude level interference between the sample,  substrate and/or sample cell windows, which must be accounted for to obtain quantitatively correct $\chi^{(3)}$ values.
 \cite{RN362, RN418}
@@
 The recorded $\chi^{(n)}$ values provide insight into how microscopic quantities ($\vec{\mu}, \alpha_{ij}, \beta_{ijk}$) impact nonlinear output.
+These quantities are usually extracted from their incoherent analogues (IR spectroscopy, spontaneous Raman spectroscopy, spontaneous hyper-Raman spectroscopy). \cite{Levenson1974_2, RN412, Shoute2005}
 Calculating $\beta_{ijk}$ values from hyper-Raman experiments is difficult and has only been performed for a few molecular vibrations. \cite{Xu1997, Shoute2005, Kelley2010}
 Methods reported in the literature to measure absolute hyper-Raman polarizabilities depend upon external standards such as hyperpolarizabilities of dissolved samples or two-photon absorption cross sections, also difficult to measure.
-Since the Bloembergen interferometry experiment only relies on the third order susceptibility for measured species (such as benzene or CaF$_2$), it is possible to use quantitative four wave mixing spectroscopy to calculcate $\beta_{ijk}$ values.
-It is thus useful to investigate how a treatment of orientational averaging can extract $\beta_{ijk}$ from $\chi^{(3)}_{IJKL}$.
+Since the Bloembergen interferometry experiment only relies on the third order susceptibility for measured species (such as benzene or CaF$_2$), it is possible to use quantitative four wave mixing spectroscopy to calculate $\beta_{ijk}$ values.
+It is thus useful to investigate how a treatment of orientational averaging can extract $\beta_{ijk}$ from the HDFG $\chi^{(3)}_{IJKL}$ expression.
 
-The HDFG $\chi^{(3)}_{IJKL}$ expression is
+In HDFG, 
 \begin{equation}\label{chi3}
@@
 The steps behind orientational averaging of $\gamma_{ijkl}$, a rank four tensor in the molecular frame, are detailed elsewhere.\cite{Andrews1977, McDonnell2024}
-Briefly, a tensor in the molecular frame, A$_{ijkl}$ is transformed into an element of the same tensor in the laboratory frame, A$_{IJKL}$ through A$_{IJKL}$ = $\theta^{ijkl}_{IJKL} A_{ijkl} = \langle A_{ijkl} \rangle$, where summation over repeated indices is implied, and $\theta$ is the transformation operator.
+Briefly, a tensor in the molecular frame, A$_{ijkl}$ is transformed into an element of the same tensor in the laboratory frame, A$_{IJKL}$ through A$_{IJKL}$ = $\theta^{ijkl}_{IJKL} A_{ijkl} = \langle A_{ijkl} \rangle$, where summation over repeated indices is implied and $\theta$ is the transformation operator.
 \cite{McDonnell2024}
-Orientational averaging shows specific polarization schemes isolate linear combinations of different $\beta_{ijk}$ terms. \cite{Cyvin1965, Bersohn1966, Kauranen1996}
-By introducing the reduced mass coordinate $q_n = \sqrt{\frac{1}{m_n}} Q_n$ and using the expansions of $\beta_{ijk}$ and $\mu_{l}$ to $\order{Q_n}$ found earlier, we see
+Orientational averaging shows specific polarization schemes isolate linear combinations of different $\beta_{ijk}$ terms. \cite{Cyvin1965, Bersohn1966}
+By using the expansions of $\beta_{ijk}$ and $\mu_{l}$ to $\order{Q_n}$ found earlier, we see
 \begin{equation}\label{betasive}
-	\langle \frac{\partial \beta_{ijk}}{\partial q_n} {\frac{\partial \mu_l}{\partial q_n}} \rangle = \frac{8D \varepsilon_0}{NF}  \frac{\Gamma_{gv} \omega_{vg}}{\rho_{gg}} {\Im(\chi^{(3)}_{IJKL})}
+	\langle \frac{\partial \beta_{ijk}}{\partial Q_n} {\frac{\partial \mu_l}{\partial Q_n}} \rangle = \frac{8D \varepsilon_0}{NF}  \frac{\Gamma_{gv} \omega_{vg}}{\rho_{gg}} {\Im(\chi^{(3)}_{IJKL})}
 \end{equation}
-Since $\abs{\mu}$ values can be readily extracted from FT-IR spectra,\cite{RN109, RN412} HDFG can give quantitative information on the magnitude of $\beta_{ijk}$.
+Since $\abs{\mu}$ values can be extracted from FT-IR spectra,\cite{McDonnell2024} HDFG can give quantitative information on the magnitude of $\beta_{ijk}$ for infrared active vibrations.
 
@@
 The properties of steady state HDFG (complete pulse overlap) are useful for understanding the selection rules that drive output.
-Time domain HDFG could be a useful alternative technique for measuring single quantum coherence dephasing times (T$_2$).
+Time domain HDFG could be a useful alternative technique for measuring single quantum coherence dephasing times.
 The response function for the HDFG pathway illustrated in \autoref{fig:hdfg}a, assuming $\omega_2$ and $\omega_3$ are temporally overlapped, is \cite{RN287, Cho2001}
@@
 Mixed domain HDFG can resolve frequency dependent free induction decay, which could prove useful for understanding isotropic dynamics of single quantum coherences. 
-Mixed domain resonant HDFG, using pathways similar to those in \autoref{fig:hdfg}b, could also measure electronic-vibrational correlation functions, as discussed by Cho. \cite{Cho2001}
+Mixed domain resonant HDFG, using pathways similar to those in \autoref{fig:hdfg}b, could also measure electronic-vibrational fluctuations, as discussed by Cho. \cite{Cho2001}
+These methods should be able to provide complimentary information to that found in 2D Electronic-Vibrational (2D-EV) spectroscopy. \cite{Dong2015, Lewis2015, Gaynor2017}
 
@@
 
-\section{Experimental HDFG of CH$_3$CN}\label{Expt}
-With the theoretical description of HDFG provided, we will investigate steady state and transient HDFG spectra of $\nu$(CH) modes in CH$_3$CN.
-
-todo: collect Wigner of ch3cn @ caf2.
-
 \section{Conclusions}%todo:fix!

### 2024-07-17 figures/2D_spec.py

@@ -67,11 +67,18 @@ def f01(q): #<0|1>
 def f10(q): #<1|0>
     return -1*f01(q)
 
+def f11(q):
+    return (1 - q**2/2) *f00(q)
+
 def f02(q): #<0|2>
     return q**2/(2*np.sqrt(2)) * f00(q)
 
 def f20(q): #<2|0>
     return f02(q)
+
+def f12(q): #<1|2>
+    return -q * (1 - q**2/4) *f00(q)
+    
 
 #define Herzberg Teller overlap integrals following page 165 of Roger Carlson's thesis in terms of Delta
 def h00(q): #<0|Q|0>
@@ -85,5 +92,26 @@ def h10(q): #<1|Q|0>
 
 def h11(q): #<1|Q|1>
     return -q/2 * (1 - q**2 / 2) * f00(q)
+
+#define resonance denominator
+def Deltaevgo(v,x,j):
+    Gammaev =[500, 500, 500]
+    weg = 30000
+    return 1/(weg + 1500*v - x - 1j*Gammaev[j])
+
+
+#define numbers for AB terms
+Mge = 0.1
+alphage = 0.01
+dMegedQ = 0.05
+dMem = 0.025
+dMmg = 0.025
+
+#define terms
+x = np.linspace(29000, 35000, 6000)
+
+A = Mge * alphage * (f10(0.5)*f00(0.5)*Deltaevgo(0,x,0) + f11(0.5)*f10(0.5)*Deltaevgo(1,x,1) + f12(0.5)*f20(0.5)*Deltaevgo(2,x,2))
+
+B1 = 
 
 

### 2024-07-18 paper.tex
edits

@@
 Implementing a nonlinear spectroscopy involving hyper-Raman transitions, first appearing under third order perturbation theory, can provide a useful analogue to infrared and Raman based nonlinear spectroscopies to understand the spectroscopy and dynamics of isotropic systems.
-Hyper Difference Frequency Generation (hyper-DFG, or HDFG) spectroscopy, also known as singly vibrationally enhanced spectroscopy (SIVE), is an underdeveloped, hyper-Raman based four wave mixing vibrational spectroscopy.
+Hyper Difference Frequency Generation (Hyper-DFG, or HDFG) spectroscopy, also known as singly vibrationally enhanced spectroscopy (SIVE), is an underdeveloped, hyper-Raman based four wave mixing vibrational spectroscopy.
 Despite several experimental reports on HDFG, its spectroscopic properties have not been fully explored.
@@
 Since all infrared active modes have non-zero hyper-Raman activity, this makes HDFG a type of upconverted infrared spectroscopy.
-HDFG is found to be uniquely sensitive to non-Condon effects in molecular spectra.
+HDFG is found to be uniquely sensitive to non-Condon effects in centrosymmetric species.
 Through a simple comparison test, HDFG output is shown to be similar in magnitude to vibrational sum frequency generation (vSFG).
@@
 \begin{equation}\label{sivegamma}
-		\gamma_{ijkl}^{gv} =	- \sum_{m, n} \frac{1}{\varepsilon_0} \frac{1}{4D} \frac{1}{\hbar^3} \frac{\mu^{vn}_{i} \mu^{nm}_{j} \mu^{mg}_{k} \mu^{gv}_{l} }{\Delta_{nv} \Delta_{mv}\Delta_{gv}}  \rho_{gg}
+		\gamma_{ijkl}^{vg} =	- \sum_{m, n} \frac{1}{\varepsilon_0} \frac{1}{4D} \frac{1}{\hbar^3} \frac{\mu^{vn}_{i} \mu^{nm}_{j} \mu^{mg}_{k} \mu^{gv}_{l} }{\Delta_{nv} \Delta_{mv}\Delta_{gv}}  \rho_{gg}
 \end{equation}
@@
 \begin{equation}\label{sivebeta}
-	\gamma_{ijkl}^{gv} =	-\frac{1}{\varepsilon_0} \frac{1}{4D \hbar}\frac{\beta^{gv}_{ijk} \mu^{gv}_{l}}{\Delta_{gv}} \rho_{gg}
+	\gamma_{ijkl}^{vg} =	-\frac{1}{\varepsilon_0} \frac{1}{4D \hbar}\frac{\beta^{vg}_{ijk} \mu^{gv}_{l}}{\Delta_{gv}} \rho_{gg}
 \end{equation}
@@
 and substituting into \autoref{sivebeta} gives the HDFG hyperpolarizability to $\order{Q_n}$ as \begin{equation}\label{SIVEselection}
-	\gamma_{ijkl}^{gv} =	-\frac{1}{\varepsilon_0} \frac{1}{8D m_n \omega_{vg}}  \frac{1}{{\Delta_{gv}}} \ \left(\frac{\partial \beta^{gv}_{ijk}}{\partial Q_n}\right)_0 \left({\frac{\partial \mu^{gv}_{l}}{\partial Q_n}}\right)_0  \rho_{gg}
+	\gamma_{ijkl}^{vg} =	-\frac{1}{\varepsilon_0} \frac{1}{8D m_n \omega_{vg}}  \frac{1}{{\Delta_{gv}}} \ \left(\frac{\partial \beta^{vg}_{ijk}}{\partial Q_n}\right)_0 \left({\frac{\partial \mu^{gv}_{l}}{\partial Q_n}}\right)_0  \rho_{gg}
 \end{equation}
@@
 The C term is suppressed in the following discussion as it depends on one and two photon forbidden transitions. \cite{Ziegler1988, Neddersen1989, Bonang1992}
-Note that some reports obtain $A, B, C$ coefficients through a Herzberg-Teller expansion of the electronic states, $|a) = |a)_0 + \sum_z \sum_{a \neq b} \frac{(\partial H / \partial Q_z )_0  Q_z}{E_a - E_b} |a)_0$, to explicitly expose vibronic couplings in terms of $\partial H / \partial Q_z $, where H is the electronic Hamiltonian.\cite{HerzbergTeller1933, Petrov1985, Neddersen1989, Baranov1990}
+Note that some reports obtain $A, B, C$ coefficients through a Herzberg-Teller expansion of the electronic states to explicitly expose vibronic couplings in terms of $\partial H / \partial Q $, where H is the electronic Hamiltonian.\cite{HerzbergTeller1933, Petrov1985, Neddersen1989, Baranov1990}
 This approach is not used here as the expansion of $\vec{M}^{ij}$ in normal mode coordinates provides sufficient physical insight into hyper-Raman selection rules.
@@
 When $\abs{\omega_{ev',g0} - (\omega_2 + \omega_3)} \gtrsim \Gamma_{ev',g0}$, $\Re(\frac{1}{\Delta_{ev', g0}})$ can allow for small $A$ term contributions.
-As such, $A$ usually only vanishes for highly detuned electronic states. 
+As such, $A$ usually only vanishes when $\omega_2, \omega_3$ are highly detuned from electronic states. 
 In the limit where $A$ vanishes, the singly resonant HDFG susceptibility can be approximated as $\chi^{(3)}_{IJKL} \sim \langle B_{ijk} \mu_l \rangle$, or, while a vibrational mode must be infrared active for HDFG output, vibronic activity is necessary for singly resonant HDFG response.
@@
 	\caption{DR-HDFG $\gamma_{ijkl}$ spectrum for a simple two harmonic well system.
-		(a) Potential energy surface, (b) 2D DR-HDFG spectrum for $\Delta = 0.5$.}
+		(a) Potential energy surface, (b) HDFG spectrum for $\Delta = 0.5$.}
 	\label{fig:doubres_spec}
@@
 \section{Mixed-Domain HDFG}\label{mixeddomain}
-The properties of steady state HDFG (complete pulse overlap) are useful for understanding the selection rules that drive output.
+The properties of steady state HDFG (complete pulse overlap) are useful for understanding the selection rules that drive HDFG output, motivating time domain experiments.
 Time domain HDFG could be a useful alternative technique for measuring single quantum coherence dephasing times.
@@
 Mixed domain HDFG can resolve frequency dependent free induction decay, which could prove useful for understanding isotropic dynamics of single quantum coherences. 
-Mixed domain resonant HDFG, using pathways similar to those in \autoref{fig:hdfg}b, could also measure electronic-vibrational fluctuations, as discussed by Cho. \cite{Cho2001}
+Mixed domain resonant HDFG, using pathways similar to those in \autoref{fig:hdfg}b, could also measure time-dependent electronic-vibrational fluctuations, as discussed by Cho. \cite{Cho2001}
 These methods should be able to provide complimentary information to that found in 2D Electronic-Vibrational (2D-EV) spectroscopy. \cite{Dong2015, Lewis2015, Gaynor2017}
@@
 Understanding interfering pathways is useful because they can, in some cases, eliminate output. 
-While we have only isolated one specific HDFG process so far, there are at least fourteen different WMELs which can provide HDFG output. \cite{RN352}
+While we have only isolated one specific HDFG process so far, there are at least fourteen different WMELs which can provide HDFG output in the driven limit. \cite{RN352}
 If $\omega_2$ ($\omega_1$) becomes resonant (non-resonant), then other HDFG pathways appear (\autoref{fig:sivewmel2}).\cite{McDonnell2024} 

### 2024-07-18 figures/2D_spec.py

@@ -10,52 +10,20 @@ from sympy import *
 import numpy as np
 import WrightTools as wt
 import matplotlib.pyplot as plt 
-import matplotlib
+
+save = True
 
 
-#define harmonic wells
-def gs(k):
+#define harmonic wells and coordinates
+def grs(k):
     return 0.1*k**2
 
 def es(k):
     return 0.1*(k-0.5)**2 + 0.65
 
-
-#coordinate#
 kg = np.linspace(-2.5, 2.5, 500) #ground state coordinates
 ke = np.linspace(-2, 3, 500) #excited state coordinates
 
-#plots#
-
-#make plot
-
-fig, ax = plt.subplots(figsize=(3.5, 3.5), layout='constrained')
-plt.rcParams['figure.dpi'] = 1000
-
-plt.plot(kg,gs(kg), linewidth = '4',label = '$C_{\chi = + 1}$', color = 'cyan')
-plt.plot(ke,es(ke), linewidth = '4',label = '$C_{\chi = - 1}$', color = 'orange')
-# delta
-plt.axvline(x=0.5, color = 'purple', linestyle='--', label = '$\Delta$')
-
-#beautificiation#
-
-matplotlib.rcParams.update({'font.size': 10})
-
-plt.xlabel(r'q (arb.)')
-plt.xticks(ticks = [])
-plt.yticks(ticks = [])
-plt.ylabel(r'Energy')
-plt.xlim(-3.5,3.5)
-plt.ylim(-0.1, 1.4)
-
-matplotlib.rcParams.update({'font.size': 10})
-
-# plt.legend(loc = 'upper center')   
-
-
-plt.show()
-
-##make the 2d plot
 
 #define Franck-Condon factors following page 164 of Roger Carlson's thesis in terms of Delta
 def f00(q): #<0|0>
@@ -93,25 +61,76 @@ def h10(q): #<1|Q|0>
 def h11(q): #<1|Q|1>
     return -q/2 * (1 - q**2 / 2) * f00(q)
 
+def h12(q):
+    return (1 + q**2/4 - q**4/8) * f00(q)
+
+def h20(q): #<2|Q|0>
+    return -q/np.sqrt(2) * (1 - q**2 /4) * f00(q)
+
+
[…]

### 2024-07-18 figures/2D_spec.py
start

@@ -11,7 +11,7 @@ import numpy as np
 import WrightTools as wt
 import matplotlib.pyplot as plt 
 
-save = True
+save = False
 
 
 #define harmonic wells and coordinates
@@ -24,6 +24,8 @@ def es(k):
 kg = np.linspace(-2.5, 2.5, 500) #ground state coordinates
 ke = np.linspace(-2, 3, 500) #excited state coordinates
 
+#todo: make an array so I can just call specific matrix element of the fc and ht factors, then do a for loop over that array, should work out well.
+
 
 #define Franck-Condon factors following page 164 of Roger Carlson's thesis in terms of Delta
 def f00(q): #<0|0>
@@ -35,7 +37,7 @@ def f01(q): #<0|1>
 def f10(q): #<1|0>
     return -1*f01(q)
 
-def f11(q):
+def f11(q): #<1|1>
     return (1 - q**2/2) *f00(q)
 
 def f02(q): #<0|2>
@@ -61,7 +63,7 @@ def h10(q): #<1|Q|0>
 def h11(q): #<1|Q|1>
     return -q/2 * (1 - q**2 / 2) * f00(q)
 
-def h12(q):
+def h12(q): #<1|Q|2>
     return (1 + q**2/4 - q**4/8) * f00(q)
 
 def h20(q): #<2|Q|0>
@@ -78,9 +80,9 @@ def Deltaevgo(v,x,l):
 #define numbers for AB terms
 Mge = 0.1
 alphage = 0.01
-dMem = 0.0025
-dMmg = 0.0025
-dMgedQ = 0.05
+dMem = 0.00005
+dMmg = 0.00005
+dMgedQ = 0.0005
 
 
 #define terms

### 2024-07-19 paper.tex
start
more

@@
 Multiresonant, four wave mixing CMDS experiments, first proposed by Oudar and Shen in 1980,\cite{RN307} directly probe coupling and correlations between different vibrational, electronic, and vibronic states.
-\cite{RN307, RN281, RN103, RN342, Cho2008, Dong2015, Ogilvie2019, RN325}
+\cite{RN307, RN281, RN103, RN342, Cho2008, Dong2015, Ogilvie2019, Bonn2021, RN325}
 CMDS has resolved anharmonicities, ultrafast dynamics, and other intramolecular couplings in numerous systems. \cite{RN342, RN343, RN324, Czech2015, Gaynor2017, Ogilvie2019, RN325}
@@
 A simulated spectrum highlighting the contributions of these terms (\autoref{fig:doubres_spec}) on potential wells with $\Delta = 0.5$ using values listed in \autoref{T:hdfgvalues} dissects the $A$ and $B$ contributions to the DR-SIVE spectrum.
-
+%stimulated hyper Raman spectrum -- relationship
 \begin{figure}[!htbp]

### 2024-07-19 figures/2D_spec.py
added conjugate and sqrts to plot
todo: still need to put on a log scale and make A : B ~ 100 : 1

@@ -27,7 +27,7 @@ ke = np.linspace(-2, 3, 500) #excited state coordinates
 #todo: make an array so I can just call specific matrix element of the fc and ht factors, then do a for loop over that array, should work out well.
 
 
-#define Franck-Condon factors following page 164 of Roger Carlson's thesis in terms of Delta
+#define Franck-Condon factors following page 164 of Roger Carlson's thesis in terms of 'q', the offset
 def f00(q): #<0|0>
     return np.e**(-q**2/4)
 
@@ -73,20 +73,20 @@ def h20(q): #<2|Q|0>
 #define resonance denominator
 def Deltaevgo(v,x,l):
     weg = 30000
-    G = [1000, 1000, 1000] #linewidths
+    G = [1000, 1000,1000] #linewidths
     return 1/(weg + 1500*v - x - 1j*G[l]) #assuming the |0> -> |n> transiton is 1500*n 
 
 
 #define numbers for AB terms
 Mge = 0.1
 alphage = 0.01
-dMem = 0.00005
-dMmg = 0.00005
-dMgedQ = 0.0005
+dMem = 0.0025
+dMmg = 0.0025
+dMgedQ = 0.05
 
 
 #define terms
-y = np.linspace(25000, 35000, 10000)
+y = np.linspace(20000, 40000, 20000)
 d = 0.5 #offset
 
 A = Mge * alphage * (f10(d)*f00(d)*Deltaevgo(0,y,0) + f11(d)*f10(d)*Deltaevgo(1,y,1) + f12(d)*f20(d)*Deltaevgo(2,y,2)) #there must be a simpler way to do this but idk
@@ -105,18 +105,25 @@ B22 = dMgedQ * alphage *(h12(d) * f20(d)) * Deltaevgo(2, y, 2) #the v' = 2 term
 
 B2 = B20 + B21 + B22
 
+#conjugate - This is because these quantities are imaginary. We need to plot sqrt(Re(A)^2 + Im(A)^2) to get the actual lineshape. Re(A) is just the dispersive lineshape (index of refraction)
+A = (A * A.conjugate()) 
+B1 = B1 * B1.conjugate()
+B2 = B2 * B2.conjugate()
+
+#plot 
 cols = [1, 1] 
[…]

### 2024-07-20 figures/2D_spec.py
slight ed

@@ -11,7 +11,7 @@ import numpy as np
 import WrightTools as wt
 import matplotlib.pyplot as plt 
 
-save = False
+save = True
 
 
 #define harmonic wells and coordinates
@@ -86,7 +86,7 @@ dMgedQ = 0.05
 
 
 #define terms
-y = np.linspace(20000, 40000, 20000)
+y = np.linspace(20000, 40000, 40000)
 d = 0.5 #offset
 
 A = Mge * alphage * (f10(d)*f00(d)*Deltaevgo(0,y,0) + f11(d)*f10(d)*Deltaevgo(1,y,1) + f12(d)*f20(d)*Deltaevgo(2,y,2)) #there must be a simpler way to do this but idk

### 2024-07-20 paper.tex
2d figure fixed

@@
 HDFG was documented long ago to have characteristics similar to both infrared spectroscopy and spontaneous hyper-Raman scattering. \cite{RN352}
-Hyper-Raman scattering is the two photon analogue to Raman scattering. \cite{Cyvin1965, Terhune1965, Kozich2007}
+Hyper-Raman scattering is the two photon analogue to Raman scattering. \cite{Cyvin1965, Terhune1965, Andrews1978}
 Hyper-Raman scattering cross sections are commonly several orders of magnitude smaller than Raman scattering cross sections, making hyper-Raman a difficult process to detect.\cite{RN515, Kelley2010} 
+However, unlike Raman spectroscopy, all infrared active modes are hyper-Raman active, which allows infrared active modes to be probed through an inelastic scattering event. \cite{Andrews1978}
 The different selection rules of hyper-Raman scattering make it a unique alternative to Raman scattering to understand vibrational spectra and vibronic coupling in molecular systems. \cite{Olson2018}
 Some years ago, Cho et al. proposed parametric six wave mixing techniques as the coherent analogue of hyper-Raman scattering. \cite{Cho1997, Cho1998}
-However, since most six wave mixing methods cascade into four wave mixing processes and their homodyned output would be dependent upon the square magnitude of the hyper-Raman scattering cross section, \cite{RN243, RN515, Cho1997, Cho2000_Cascade} it is preferable to investigate four wave mixing analogues to hyper-Raman scattering.
+However, since most six wave mixing methods cascade into four wave mixing processes and their homodyned output would be dependent upon the hyper-Raman scattering cross section, \cite{RN243, RN515, Cho1997, Cho2000_Cascade} it is preferable to investigate four wave mixing analogues to hyper-Raman scattering.
 
@@
 Contracting over the virtual states forms the hyper-Raman hyperpolarizability $\beta$.\cite{Long1970} 
-Assuming $\omega_2$, $\omega_3$ are significantly detuned from any resonance (\autoref{fig:comparisonwmel}),\cite{Placzek1934, Long1970} \autoref{sivegamma} is written as 
+Assuming $\omega_2$, $\omega_3$ are significantly detuned from any resonance (\autoref{fig:comparisonwmel}),\cite{Placzek1934, Long1970, Altmann1982} \autoref{sivegamma} is written as 
 \begin{equation}\label{sivebeta}
@@
 \end{equation}
-It is important to note that the symmetry properties of $\beta_{ijk}$ change dependent upon whether $\omega_2$ and $\omega_3$ are degenerate. \cite{Denisov1986}
+All infrared active transitions are hyper-Raman active, making HDFG allowed for any infrared active transition. \cite{Andrews1978}
+It is important to note that the symmetry properties of $\beta_{ijk}$ change dependent upon whether $\omega_2$ and $\omega_3$ are degenerate. \cite{Denisov1986, Kozich2007}
 Taylor expanding the dipole and first hyperpolarizability operators in terms of an n$^{\text{th}}$ reduced normal mode coordinate $Q_n$ about equilibrium as\cite{Long1970, Shen90}
@@
 A simulated spectrum highlighting the contributions of these terms (\autoref{fig:doubres_spec}) on potential wells with $\Delta = 0.5$ using values listed in \autoref{T:hdfgvalues} dissects the $A$ and $B$ contributions to the DR-SIVE spectrum.
-%stimulated hyper Raman spectrum -- relationship
-\begin{figure}[!htbp]
+%stimulated hyper Raman spectrum -- relationship; make clear that this spectrum highlights anything that ends in |gv> from the IR transition!
+\begin{figure*}[!htbp]
 	\centering
-	\includegraphics[width=3.375in]{drsive_spectrum.png}
+	\includegraphics[width=6.66in]{drsive_spectrum.png}
 	\caption{DR-HDFG $\gamma_{ijkl}$ spectrum for a simple two harmonic well system.
@@
 	\label{fig:doubres_spec}
-\end{figure}
+\end{figure*}
 

### 2024-07-20 figures/2D_spec.py

@@ -4,25 +4,29 @@ Created on Tue Jan 17 09:28:39 2023
 
 @author: rpm
 """
-
-import math
-from sympy import *
 import numpy as np
 import WrightTools as wt
 import matplotlib.pyplot as plt 
+from matplotlib.patches import FancyArrowPatch
+
+wt.artists.apply_rcparams(kind="publication")
 
 save = True
 
+fontsize = 18
 
 #define harmonic wells and coordinates
+d = 0.5 #offset for es
+do = 0 #gs placement
+
 def grs(k):
-    return 0.1*k**2
+    return 0.125*(k-do)**2
 
 def es(k):
-    return 0.1*(k-0.5)**2 + 0.65
+    return 0.125*(k-d-do)**2 + 0.7
 
-kg = np.linspace(-2.5, 2.5, 500) #ground state coordinates
-ke = np.linspace(-2, 3, 500) #excited state coordinates
+kg = np.linspace(-2, 2, 500) #ground state coordinates
+ke = np.linspace(-1.75, 2.75, 500) #excited state coordinates
 
 #todo: make an array so I can just call specific matrix element of the fc and ht factors, then do a for loop over that array, should work out well.
 
@@ -50,7 +54,7 @@ def f12(q): #<1|2>
     return -q * (1 - q**2/4) *f00(q)
     
 
-#define Herzberg Teller overlap integrals following page 165 of Roger Carlson's thesis in terms of Delta
+#define Herzberg Teller overlap integrals following page 165 of Roger Carlson's thesis in terms of q
 def h00(q): #<0|Q|0>
     return -q/2 * f00(q)
 
@@ -73,21 +77,21 @@ def h20(q): #<2|Q|0>
 #define resonance denominator
 def Deltaevgo(v,x,l):
     weg = 30000
-    G = [1000, 1000,1000] #linewidths
-    return 1/(weg + 1500*v - x - 1j*G[l]) #assuming the |0> -> |n> transiton is 1500*n 
+    G = [1000, 1000, 1000] #linewidths
[…]

### 2024-07-22 figures/2D_spec.py
many fixes

@@ -11,7 +11,7 @@ from matplotlib.patches import FancyArrowPatch
 
 wt.artists.apply_rcparams(kind="publication")
 
-save = True
+save = False
 
 fontsize = 18
 
@@ -27,6 +27,65 @@ def es(k):
 
 kg = np.linspace(-2, 2, 500) #ground state coordinates
 ke = np.linspace(-1.75, 2.75, 500) #excited state coordinates
+
+#make figure
+cols = [1, 1] 
+aspects = [[[0, 0], 1], [[1, 0], 1]] 
+
+fig, gs = wt.artists.create_figure(width="dissertation", nrows=2, cols=cols, aspects=aspects, wspace=1) 
+
+ax0 = plt.subplot(gs[0,0])
+
+#hbar omega_eg arrow insert
+yarrow = [grs(0.6), es(1.3)] #where the arrows start and end
+yarrowstop = [(grs(0.6) + es(1.3))/2 - 0.06, (grs(0.6) + es(1.3))/2 + 0.06] #to put in the hbaromegaeg
+myArrow0 = FancyArrowPatch(posA=(-0.35, yarrow[0]), posB=(-0.35, yarrowstop[0]), arrowstyle='<|-', color='blue',
+                           mutation_scale=25, shrinkA=0, shrinkB=0, linewidth = 4)
+myArrow1 = FancyArrowPatch(posA=(-0.35, yarrowstop[1]), posB=(-0.35, yarrow[1]), arrowstyle='-|>', color='blue', 
+                           mutation_scale=25, shrinkA=0, shrinkB=0, linewidth = 4)
+ax0.add_artist(myArrow0)
+ax0.add_artist(myArrow1)
+
+ax0.text(-0.65, (grs(0.6) + es(1.3))/2 - 0.023, '$\mathsf{\hbar \omega_{eg}}$', fontsize = 24)
+
+#xi line 
+ax0.vlines(x = do, ymin = -0.0257, ymax = grs(do), color = 'gray', linestyle = '--', linewidth = 1)
+ax0.vlines(x = d, ymin = -0.0257, ymax = es(d), color = 'gray', linestyle = '--', linewidth = 1)
+
+#xi arrow insert
+xarrow = [do, d] #where the arrows start and end
[…]

### 2024-07-22 paper.tex

@@
 To this end, we explore the selection rules and response functions of HDFG spectroscopy.
-Through the hyper-Raman $A,B,C$ terms, we explore the selection rules of singly and doubly resonant HDFG spectroscopy, and show HDFG is a hybrid IR-hyper-Raman technique.
+Through the hyper-Raman $A,B$ terms, we explore the selection rules of singly and doubly resonant HDFG spectroscopy, and show HDFG is a hybrid IR-hyper-Raman technique.
 Since all infrared active modes have non-zero hyper-Raman activity, this makes HDFG a type of upconverted infrared spectroscopy.
@@
 Multiresonant, four wave mixing CMDS experiments, first proposed by Oudar and Shen in 1980,\cite{RN307} directly probe coupling and correlations between different vibrational, electronic, and vibronic states.
-\cite{RN307, RN281, RN103, RN342, Cho2008, Dong2015, Ogilvie2019, Bonn2021, RN325}
-CMDS has resolved anharmonicities, ultrafast dynamics, and other intramolecular couplings in numerous systems. \cite{RN342, RN343, RN324, Czech2015, Gaynor2017, Ogilvie2019, RN325}
+\cite{RN307, RN281, RN103, Cho2008}
+Four wave mixing CMDS has resolved anharmonicities, ultrafast dynamics, and other intramolecular couplings in numerous systems. \cite{Cho2008, Gaynor2017, Ziegler2018, Ogilvie2019, Bonn2021, RN325}
 
@@
 Non-parametric, hyper difference frequency generation (hyper-DFG, or HDFG) spectroscopy, similar to difference frequency generation (\autoref{fig:comparisonwmel}), is a four wave mixing method which, when detuned from  electronic resonances, does not probe intramolecular couplings.
-HDFG was the first infrared CMDS method to successfully discriminate against non-resonant background.\cite{RN351, RN352}
+HDFG was one of the first infrared CMDS methods to successfully discriminate against non-resonant background.\cite{RN351, RN352}
 HDFG has also been referred to as singly vibrationally enhanced (SIVE) spectroscopy. \cite{RN351}
@@
 HDFG was documented long ago to have characteristics similar to both infrared spectroscopy and spontaneous hyper-Raman scattering. \cite{RN352}
-Hyper-Raman scattering is the two photon analogue to Raman scattering. \cite{Cyvin1965, Terhune1965, Andrews1978}
+Hyper-Raman scattering is the two photon analogue to Raman scattering. \cite{Terhune1965, Cyvin1965, Andrews1978}
 Hyper-Raman scattering cross sections are commonly several orders of magnitude smaller than Raman scattering cross sections, making hyper-Raman a difficult process to detect.\cite{RN515, Kelley2010} 
 However, unlike Raman spectroscopy, all infrared active modes are hyper-Raman active, which allows infrared active modes to be probed through an inelastic scattering event. \cite{Andrews1978}
-The different selection rules of hyper-Raman scattering make it a unique alternative to Raman scattering to understand vibrational spectra and vibronic coupling in molecular systems. \cite{Olson2018}
-Some years ago, Cho et al. proposed parametric six wave mixing techniques as the coherent analogue of hyper-Raman scattering. \cite{Cho1997, Cho1998}
-However, since most six wave mixing methods cascade into four wave mixing processes and their homodyned output would be dependent upon the hyper-Raman scattering cross section, \cite{RN243, RN515, Cho1997, Cho2000_Cascade} it is preferable to investigate four wave mixing analogues to hyper-Raman scattering.
+The different selection rules of hyper-Raman scattering make it a unique alternative to Raman scattering to understand vibrational spectra, electronic structure and vibronic coupling in molecular systems.
+\cite{Olson2018}
+Cho et al. have proposed parametric six wave mixing techniques as the coherent analogue of hyper-Raman scattering. \cite{Cho1997, Cho1998}
+However, since most six wave mixing methods cascade into four wave mixing processes and their homodyned output would be dependent upon the hyper-Raman scattering cross section, \cite{RN243,Cho1997, Cho1998, Cho2000_Cascade} it is preferable to investigate four wave mixing analogues to hyper-Raman scattering.
 
@@
 	\includegraphics[width=6.66in]{comparisonwmel.png}
-	\caption{Wave Mixing Energy Level (WMEL) diagrams of difference frequency generation (DFG), spontaneous Raman scattering, hyper difference frequency generation (HDFG) and spontaneous hyper-Raman scattering relevant to this discussion.
+	\caption{Wave Mixing Energy Level (WMEL) diagrams of difference frequency generation (DFG), sum frequency generation (SFG), spontaneous Raman scattering, hyper difference frequency generation (HDFG), hyper sum frequency generation (HSFG) and spontaneous hyper-Raman scattering relevant to this discussion.
 \cite{RN286}
@@
 An experimental complexity in executing Raman based four wave mixing experiments is the demand of three separate input pulses, often at different frequencies.
-For example, in the case of DOVE, two of the three inputs must be scanable infrared pulses. \cite{RN345} 
-Only recently have methods been developed for seamless tuning and scanning of ultrafast optical parametric amplifiers across swaths of frequency space. \cite{RN162, McDonnell2024, SkyeOPA, KyleOPA}
+For example, in the case of DOVE, two of the three inputs must be tunable infrared pulses. \cite{RN345} 
+Only recently have methods been developed for seamless tuning and scanning of ultrafast optical parametric amplifiers across swaths of frequency space. \cite{RN162, McDonnell2024}
 Since HDFG demands only a single resonance to be scanned, the experiment can be performed using two input pulses: one tunable, infrared OPA to scan across vibrational resonances, and a two photon absorption from the signal process of a separate OPA, or output from the oscillator which pumps the infrared OPA.
 \cite{Wang2021}
-As such, laboratories experienced in sum frequency generation (SFG) spectroscopy can perform HDFG spectroscopy to understand bulk dynamics and spectroscopy using nearly the same setup.\cite{Shen1987_CPL}
+As such, laboratories experienced in sum frequency generation (SFG) spectroscopy can perform HDFG spectroscopy to understand bulk dynamics and spectroscopy using nearly the same setup.
 
@@
 In \autoref{steadystate}, we identify the selection rules that drive singly and doubly resonant HDFG, first through the Placzek approximation, and then through hyper-Raman $A,B,C$ coefficients.
-Quantitative aspects of HDFG: a comparison of vSFG and HDFG output, a method to extract hyper-Raman hyperpolarizabilities ($\beta_{ijk}$) from HDFG spectra, are discussed in \autoref{quant}.
-Mixed time-frequency domain HDFG is discussed in \autoref{mixeddomain}.
+After developing selection rules, some quantitative aspects of HDFG, particularly a comparison of vSFG and HDFG output and a method to extract hyper-Raman hyperpolarizabilities ($\beta_{ijk}$) from HDFG spectra, are discussed in \autoref{quant}.
+Finally, mixed time-frequency domain HDFG is discussed in \autoref{mixeddomain}.
 
@@
 
-It is useful to expose relationships between transition dipoles, Raman polarizabilities and hyper-Raman hyperpolarizabilities in the driven limit. \cite{Druet1978, Simpson2004}
+It is useful to expose relationships between transition dipoles, Raman polarizabilities and hyper-Raman hyperpolarizabilities in the driven limit. \cite{Simpson2004}
 In the driven limit, under the electric dipole approximation, the I$^{th}$ component of the third order nonlinear output polarization, ${P}^{(3)}_I$, of any four wave mixing process, induced by electric fields E, at output frequency $\omega_4$ is written as (using Einstein summation) \cite{RN307}
@@
 It is important to note that the symmetry properties of $\beta_{ijk}$ change dependent upon whether $\omega_2$ and $\omega_3$ are degenerate. \cite{Denisov1986, Kozich2007}
-Taylor expanding the dipole and first hyperpolarizability operators in terms of an n$^{\text{th}}$ reduced normal mode coordinate $Q_n$ about equilibrium as\cite{Long1970, Shen90}
+Taylor expanding the dipole and first hyperpolarizability operators in terms of an n$^{\text{th}}$ reduced normal mode coordinate $Q_n$ to $\order{Q_n}$ about equilibrium as\cite{Long1970, Shen90}
 \begin{subequations}
 	\begin{equation}
-		\mu_l = \mu_{l,0} + \left(\frac{\partial \mu_l}{\partial Q_n}\right)_0 Q_n + \order{{Q_m Q_n}}
+		\mu_l = \mu_{l,0} + \left(\frac{\partial \mu_l}{\partial Q_n}\right)_0 Q_n 
 	\end{equation}
 	\begin{equation}
-		\beta_{ijk} = \beta_{ijk,0} + \left(\frac{\partial \beta_{ijk}}{\partial Q_n}\right)_0 Q_n + \order{{Q_m Q_n}}
+		\beta_{ijk} = \beta_{ijk,0} + \left(\frac{\partial \beta_{ijk}}{\partial Q_n}\right)_0 Q_n
 	\end{equation}
@@
 \end{equation}
-where $\mel{v}{Q_n}{g} = \sqrt{\frac{\hbar}{2\omega_{vg}}}$.  \cite{RN230}
+where $\mel{v}{Q_n}{g} = \sqrt{\frac{\hbar}{2\omega_{vg}}}$ if $v-g = \pm 1$.  \cite{RN230}
 Since this expression is non-zero in the harmonic oscillator limit, HDFG output is allowed for harmonic transitions. 
@@
 We write $\beta_{ijk}$ in \autoref{SIVEselection} using the hyper-Raman ABC formalism introduced by Chung and Ziegler to understand how vibronic coupling manipulates selection rules for singly and doubly resonant HDFG (\autoref{fig:hdfg}).
-\cite{Ziegler1988, Baranov1990}
+\cite{Ziegler1988}
 To employ this formalism, we write the states in terms of a Born-Oppenheimer basis $\ket{a,b}$, where $\ket{a,b} = |a(Q)) \otimes \ket{b}$ for electronic states $\{|a(Q))\}$ and vibrational states $\{\ket{b}\}$ (i.e., adiabatic approximation).
@@
 The states are labeled as shown in \autoref{fig:hdfg}.
-For consistency with previous reports, we use $\vec{R}$ to denote electric transition dipole moments ($\vec{\mu}$ is reserved for transitions on the ground electronic state). \cite{Tang1970}
+For consistency with previous reports, we use $\vec{R}$ to denote electric transition dipole moments; $\vec{\mu}$ is reserved for transitions on the ground electronic state. \cite{Tang1970}
 Following the approach which gave \autoref{sivegamma}, we find
@@
 $R_{i}^{gv,ev'} = \mel{v}{M_i^{ge}}{v'}$.
-Using these ideas rewrites \autoref{drgamma_notaylor} as
-\begin{equation}\label{drgamma_notaylor_1}
-	\begin{split}
-		\gamma_{ijkl} &= -\frac{1}{\varepsilon_0} \frac{1}{4D \hbar^3} \sum_{m,n,e,v'} \frac{
-			\mel{v}{M_{i}^{ge}}{v'} 
-			\mel{v'}{M_{j}^{em}}{n}
-			\mel{n}{M_{k}^{mg} }{v}
-			\mel{v}{\mu_{l}}{0}
-		}{\Delta_{g0,gv}
-			\Delta_{ev',g0}	} \\
-	\end{split}
-\end{equation}
-Chung and Ziegler showed some years ago that expanding $\vec{M}^{ij}$ to $\order{Q}$ as
+Chung and Ziegler showed some years ago that expanding $\vec{M}^{ij}$ to $\order{Q}$ \textit{about the equilibrium point of the ground state potential surface} as
 $\vec{M}^{ij} = \vec{M}^{ij}_0 + \sum_z \frac{\partial\vec{M}^{ij}}{\partial Q_z} Q_z$
@@
 i.e., A$_{ijk}$ vanishes, but B$_{ijk}$ is non-zero, for singly resonant HDFG. 
-When $\abs{\omega_{ev',g0} - (\omega_2 + \omega_3)} \gtrsim \Gamma_{ev',g0}$, $\Re(\frac{1}{\Delta_{ev', g0}})$ can allow for small $A$ term contributions.
+When $\abs{\omega_{ev',g0} - (\omega_2 + \omega_3)} \gtrsim \Gamma_{ev',g0}$, $\Re(\frac{1}{\Delta_{ev', g0}})$ can allow for small $A$ term contributions (cf.
+the long tail associated with the $A$ term of DR-HDFG as presented in \autoref{fig:doubres_spec}b).
 As such, $A$ usually only vanishes when $\omega_2, \omega_3$ are highly detuned from electronic states. 
@@
 
-%todo: more on B term
 \subsubsection{Doubly Resonant HDFG}
@@
 DR-HDFG provides methods to investigate vibronic coupling with only two laser pulses.
-DR-HDFG output is dependent upon the $A,B$ terms prior to contraction over $\ket{v'}$. 
-Based upon the presence of the $A$ term in DR-HDFG, it is apparent that DR-HDFG can inform on molecular electronic structure.
+Experimentally, DR-HDFG would provide identical information to DR-HSFG, but only DR-HDFG is phasematchable in media with normal indices of refraction, so we focus our attention on DR-HDFG.
+\cite{RN278}
+DR-HDFG output is dependent upon the $A,B$ terms prior to contraction over $\ket{v'}$ as written in \autoref{ABterms}.
 
+Unlike a spontaneous hyper-Raman experiment, a DR-HDFG experiment selectively excites quanta in ground state vibrational modes (\autoref{fig:hdfg}), making it similar to a stimulated hyper-Raman experiment.
+As a result, the spectrum along the electronic scanning axis ($\omega_2 + \omega_3$) is significantly simplified as the coupling between the vibronic states are isolated to only $\ket{g,0}$ and $\ket{g,1}$, assuming the infrared pulse puts a single quantum in the normal mode of interest ($\ket{g,1}$).
 By working only in terms of a single normal mode (i.e.
 removing the sum over $z$) and assuming electronic transitions occur only between $|g), |e)$ and that $v =1$, $v' = \{0,1,2\}$, the A and B terms are rewritten as
-\begin{widetext}
 	\begin{subequations}\label{ABterms_DR}
@@
 			\begin{split}
-				B_{1_{ijk}} &= \frac{1}{\hbar^2} \sum_{v',m} M^{ge}_{0,i} \langle 1 | v' \rangle \left(
-				\frac{\partial M^{em}_{j}}{\partial Q} M^{mg}_{0,k} \mel{v'}{Q}{0} 
-				+M^{em}_{0,j} \frac{\partial M^{mg}_{k}}{\partial Q} \mel{v'}{Q}{0} \right) \frac{1}{\Delta_{ev', g0}}\\
+				B_{1_{ijk}} &= \frac{1}{\hbar} \sum_{v'} M^{ge}_{0,i} \langle 1 | v' \rangle 
+				\frac{\partial \Lambda^{eg}_{jk}}{\partial Q} \mel{v'}{Q}{0} 
+				\frac{1}{\Delta_{ev', g0}}\\
 			\end{split}
@@
 	\end{subequations}
-\end{widetext}
 where the electronic two photon absorption operator, $\Lambda$ was invoked to simplify summation over virtual states. \cite{McClain1977}
-It is clear from \autoref{ABterms_DR} that the Condon approximation breaks down for centrosymmetric molecules, as centrosymmetry invokes strict parity constraints that make states not accessible via both one and two photon transitions.
+The constraint of $v' = \{0,1,2\}$ is done for simplicity.
+
+The selection rules for DR-HDFG follow more clearly from \autoref{ABterms_DR}.
+It is clear from \autoref{ABterms_DR} that the Condon approximation breaks down for centrosymmetric molecules, as inversion centers invoke strict parity constraints that make states not accessible via both one and two photon transitions.
+\cite{Milojevich2013, RN230}
 This makes DR-HDFG a unique tool for studying the electronic structure of centrosymmetric species in isotropic media, as it is sensitive to non-Condon effects. \cite{Olson2018}
-The lineshapes of electronic-vibrational coupling probed by DR-HDFG can inform on electronic-vibrational correlations. \cite{Carlson1990line,Dong2015}
-These effects are under investigation and will the subject of a future publication.
+The $B_1$ and $B_2$ terms involve different types of vibronic coupling pathways.
+In $B_1$, the Herzberg-Teller coupling is associated with the two-photon absorption process, whereas in $B_2$, the Herzberg-Teller coupling is associated with one-photon emission.
+As such, $B_1$ contributions to a DR-HDFG spectrum will be sensitive to vibronic coupling between the ground state of a mode and vibrational states on the $|e)$ surface. 
+$B_2$ contributions are sensitive to vibronic coupling between the first excited state of a mode $\ket{g,1}$ and vibrational states on $|e)$.
 
-The impact of vibronic coupling in the 2D spectrum is made clear by using a simple model.
-Using a two-well system described by $H_g = p^2/2m + 1/2 \hbar \omega Q^2$ and $H_e = p^2/2m + 1/2 \hbar \omega (Q-\Delta)^2 +\hbar \omega_{eg}$, the A and B contributions can be easily evaluated using Franck-Condon and Herzberg-Teller integrals tabulated elsewhere.
-\cite{Carlson1988thesis}
-A simulated spectrum highlighting the contributions of these terms (\autoref{fig:doubres_spec}) on potential wells with $\Delta = 0.5$ using values listed in \autoref{T:hdfgvalues} dissects the $A$ and $B$ contributions to the DR-SIVE spectrum.
-%stimulated hyper Raman spectrum -- relationship; make clear that this spectrum highlights anything that ends in |gv> from the IR transition!
 \begin{figure*}[!htbp]
@@
 	\includegraphics[width=6.66in]{drsive_spectrum.png}
-	\caption{DR-HDFG $\gamma_{ijkl}$ spectrum for a simple two harmonic well system.
-		(a) Potential energy surface, (b) HDFG spectrum for $\Delta = 0.5$.}
+	\caption{Contributions of $A, B$ (\autoref{ABterms_DR}) to DR-HDFG spectrum for a simple two harmonic well system.
+		(a) Potential energy surfaces for a two-well system, (b) 1D HDFG spectrum for $\xi = 0.5$, $\omega_1 = \omega_{g1, g0}$. 
+		It is assumed that $\omega_2 = \omega_3$.
+		Note that (b) shows magnitudes of the labeled quantities.
+		The vibrational states on the $|g)$ and $|e)$ manifolds are spaced 2200 cm$^{-1}$ apart, with the vibronic states $\ket{e,v}$ given linewidths of 700 cm$^{-1}$ and $\hbar \omega_{eg}$ = 30000 cm$^{-1}$.
+		Dotted lines in (b) denote placement of vibronic resonances for $v'$ = 0, 1, 2. }
 	\label{fig:doubres_spec}
@@
 
-\begin{table}[!htbp]
-	\caption{\label{T:hdfgvalues} Values used to generate the 2D DR-HDFG plot. 
-	All Franck-Condon and Herzberg-Teller integrals are evaluated as tabulated by Carlson \cite{Carlson1988thesis}}
-	\begin{ruledtabular}
-		\begin{tabular}{cc}
-			Quantity & Value\\
-			\hline  
-			$\mel{g}{\mu}{v}$ & 0.1 D\\
-			I-b & No\\
-			II-a & No\\
-			II-a & No\\
-		\end{tabular}
-	\end{ruledtabular}
-\end{table}
+The impact of vibronic coupling in the 2D spectrum is made clear by using a simple model. \cite{Kundu2022}
+Using a two-well system described by 
+\begin{subequations}
+	\begin{equation}
+		H_g = \frac{p^2}{2m} + \frac{1}{2} m^2 \omega^2 Q^2
+	\end{equation}
+and
+	\begin{equation}
+		H_e = \frac{p^2}{2m} + \frac{1}{2} m^2 \omega^2 (Q-\xi)^2 +\hbar \omega_{eg}
+	\end{equation}
+\end{subequations}
+for the ground ($H_g$) and first excited ($H_e$) states, where $p$ is the momentum of the normal mode, the A and B contributions can be evaluated using Franck-Condon and Herzberg-Teller integrals tabulated in terms of the dimensionless offset parameter, $\xi$ (\autoref{fig:doubres_spec}a).
+\cite{Carlson1988thesis}
+The spectrum is simulated for an electronic state which is both one and two photon allowed.
+A simulated spectrum   (\autoref{fig:doubres_spec}b) highlighting the contributions of these terms on potential wells with $\xi = 0.5$ dissects the $A$ and $B$ contributions to the DR-SIVE spectrum.
+Note that unlike resonant hyper-Raman spectra, which allow transitions between different normal modes, the use of the infrared pulse provides a type of site selectivity,\cite{RN103} so that only the normal mode which $\omega_1$ pumps can be involved in the vibronic coupling analysis.
+This stimulated hyper-Raman type spectrum would be the expected result in a DR-HDFG experiment when investigating the vibronic structure of the electronic state coupled to $\ket{g,v}$.
+
+Simulating the DR-HDFG spectrum for the simple two-well system allows dissection of selection rules and spectral signatures without the need for complex couplings.
+There are two relevant regions of interest: the resonant region (2$\omega_2$ $\in$ [29000, 35000] cm$^{-1}$) and the non-resonant region.
+Focusing far away from the resonant region ($2\omega_2 \sim$ 20000 cm$^{-1}$), it is clear that $A$ term response is non-negligible. 
+As discussed above, the $A$ term in singly resonant HDFG vanishes when truly non-resonant.
+However, the simulated spectrum shows a non-negligible $A$ term contribution to DR-HDFG output well beyond $\sim$ 20000 cm$^{-1}$, the limit for this model system where $\abs{\omega_{ev',g0} - 2\omega_2} \gg 2\Gamma_{ev',g0}$.
+As such, it may be difficult to truly eliminate $A$ term resonances in HDFG spectra, even when largely detuned ($>$ 10000 cm$^{-1}$) from the electronic state.
+
+In the resonant region, the $A$ term contains character from all three possible transitions between $\ket{g,0}$, $\ket{e,v'}$ and $\ket{g,1}$. 
+Significant contributions from $\ket{e,0}$ and $\ket{e,1}$ in the spectrum correspond well with expectations given the relative wavefunction overlap in \autoref{fig:doubres_spec}a. 
+The small contribution to $A$ involving transitions with $\ket{e,2}$ is consistent with the large change in quantum number from $\ket{g,0}$ and its considerable displacement from the equilibrium point of $|g)$.
+The dependence of $A$ on these Franck-Condon factors is in agreement with expectations following \autoref{ABterms_DR}.
+
+Unlike $A$ term contributions, the $B_1$ and $B_2$ terms are dependent upon both Franck-Condon and Herzberg-Teller contributions.
+Based upon the disparity in transition amplitudes in the $B_1$ and $B_2$ terms for each vibronic transition, it is clear that the $B$ terms are sensitive to the Herzberg-Teller coupling integrals.
+The $B_1$ term, whose vibronic coupling term is involved in the two-photon absorption event from $|g)$ to $|e)$, seemingly has minimal $0-0$ contributions. 
+This is expected, as the Herzberg-Teller integral $\mel{0}{Q}{0}$ is smaller than $\mel{1}{Q}{0}$ and $\mel{2}{Q}{0}$. 
+An explanation for the contribution from the $0-1$ transition in $B_2$ is similar.
+Vibronic contributions to $B_2$ arise from the one photon emission transition; $\mel{1}{Q}{1}$ is smaller than the $\mel{1}{Q}{0}$ and $\mel{1}{Q}{2}$ contributions to the $B_2$ term.
+However, the $0-2$ transition is smaller in amplitude than the $0-1$ transition because it is also dependent upon a $\langle 2 | 0 \rangle$ Franck-Condon factor.
+In a realistic molecular system, where higher order contributions (e.g.
+Duschinsky coupling) effect vibronic coupling signatures, the spectral signatures will change to incorporate anharmonicites.
+\cite{Duschinsky1937, Carlson1990, Kundu2022}
+However, investigating coupling between $\ket{g,2v}$ and the same $\ket{e,v'}$ vibronic states will likely assist in dissecting the site-selective electronic spectra.
 
 \section{Quantitative Aspects of HDFG}\label{quant}
-
+HDFG is dependent upon a hyper-Raman transition, which is several orders of magnitude weaker than Raman transitions.\cite{RN515}
+As a result, it is useful to identify how HDFG output compares to a corresponding Raman based nonlinear spectroscopy.
 Since the hyper-Raman process is stimulated by a two-photon process, a setup using only one optical parametric amplifier can perform a coherent four wave mixing hyper-Raman experiment by investigating $-\vec{k}_1 + 2\vec{k}_2$ processes (i.e.
 two laser CMDS), assuming a two photon absorption from a single pulse stimulates the hyper-Raman process.
-The most commonly used two laser CMDS method is vibrational sum frequency generation (vSFG), a $\chi^{(2)}$ technique whose phasematching is dictated by $\vec{k}_1 + \vec{k}_2$.
+A commonly used two laser CMDS method is vibrational sum frequency generation (vSFG), a $\chi^{(2)}$ technique whose phasematching is dictated by $\vec{k}_1 + \vec{k}_2$.
 SFG output scales as $\chi^{(2)}_{IJK} \sim \langle \alpha_{ij} \mu_k \rangle$, where $\alpha_{ij}$ is the Raman polarizability tensor.
-Both processes can be phasematched in media with normal indicies of refraction, unlike the $\vec{k}_1 + 2\vec{k}_2$ process.\cite{RN120}
+Both processes can be phasematched in media with normal indices of refraction, unlike the $\vec{k}_1 + 2\vec{k}_2$ HSFG process (\autoref{fig:comparisonwmel}).\cite{RN120}
 Macroscopically, oddness in spatial inversion of the vSFG polarization eliminates output from centrosymmetric species under the electric dipole approximation.\cite{RN132, RN133}
 As a result, the output of vSFG is significantly reduced relative to most third order spectroscopies because the output depends on surface number density, many orders of magnitude smaller than the bulk surface density.
-However, since HDFG is dependent upon a hyper-Raman transition, which is several orders of magnitude weaker than Raman transitions,\cite{RN515} it is useful to identify how HDFG output compares to vSFG.
+To motivate the application of HDFG spectroscopy, we perform a calculation to compare HDFG and vSFG output, where absorption effects are neglected for simplicity.
 
-To motivate the application of HDFG spectroscopy, we perform a calculation to compare HDFG and vSFG output.
-Absorption effects are neglected for simplicity.
-The output polarizations of each process is written as
+The output polarizations under the electric dipole approximation are written as
 \begin{widetext}
@@
 	\begin{equation}
-		\abs{P^{(2)}_{\text{vSFG}}} = N_{surf} F(\omega_1+\omega_2) \abs{\langle \alpha_{ij}\mu_{k} \rangle E(\omega_2)E(\omega_1)} 
+		\abs{P^{(2)}_{\text{vSFG}}} = \frac{N_{surf}}{\ell} F(\omega_1+\omega_2) \abs{\langle \alpha_{ij}\mu_{k} \rangle E(\omega_2)E(\omega_1)} 
 	\end{equation}
 	\begin{equation}
-		\abs{P^{(3)}_{\text{HDFG}}} = N_{bulk}  F(2\omega_2-\omega_1) \abs{\langle \beta_{ijk} \mu_{l} \rangle E{(\omega_2)}E(\omega_2)E(-\omega_1)} \ell_{eff}
+		\abs{P^{(3)}_{\text{HDFG}}} = N_{bulk}  F(2\omega_2-\omega_1) \abs{\langle \beta_{ijk} \mu_{l} \rangle E{(\omega_2)}E(\omega_2)E(-\omega_1)}
 	\end{equation}
@@
 \end{widetext}
-where N$_{bulk}$ is the bulk number density, and N$_{surf}$ is the surface number density (10$^{19}$ m$^{-2}$).\cite{RN133, RN503}	
+where N$_{bulk}$ is the bulk number density, and N$_{surf}$ is the surface number density ($\sim$ 10$^{17}$ m$^{-2}$).\cite{RN133, Du1994}	
 For liquids with molar masses less than $\sim$100 g mol$^{-1}$ and densities roughly equal to that of H$_2$O$_{(l)}$ at room temperature, N$_{bulk} \sim$ 10$^{28}$ m$^{-3}$.
-We take the bulk optical interaction length ($\ell_{eff}$) to be 10 $\mu$m.\cite{RN133} %see chapter 25 of Shen's NLO book... idk something here seems wrong
+We take the length of layers along the surface normal ($\ell$) to be 10 nm.\cite{RN133}
 A normal dispersion curve is assumed so that $F(\omega_1+\omega_2) \approx F(2\omega_2-\omega_1)$.
@@
 \begin{equation}
-		P_{ratio} \equiv \frac{\abs{P^{(3)}_{\text{HDFG}}}}{\abs{P^{(2)}_{\text{vSFG}}}} \approx \frac{N_{bulk}}{N_{surf}} \frac{\beta}{\alpha} E(\omega_2) \ell_{eff} \sim 10^4 \frac{\beta}{\alpha} E(\omega_2)\\
+		P_{ratio} \equiv \frac{\abs{P^{(3)}_{\text{HDFG}}}}{\abs{P^{(2)}_{\text{vSFG}}}} \approx \frac{N_{bulk}}{N_{surf}} \frac{\beta}{\alpha} E(\omega_2) \ell \sim 10^3 \frac{\beta}{\alpha} E(\omega_2)\\
 \end{equation}
@@
 Such an intensity is easily obtained using modern ultrafast sources.
-In this limit, $P_\text{ratio} \sim 10$.
-Since the intensity ratio scales as $\abs{P_{ratio}}^2$, we see that the HDFG output is somewhat stronger than vibrational SFG, assuming only interfacial contributions in vSFG.
+In this limit, $P_\text{ratio} \sim 1$.
+Since the intensity ratio scales as $\abs{P_{ratio}}^2$, we see that the HDFG output is roughly as strong as vSFG, assuming only interfacial contributions in vSFG.
 It is important to note that this derivation ignored absorption and orientational averaging effects, which can significantly reduce output from either process. 
+Nevertheless, since HDFG produces a number of photons similar to that of vSFG, HDFG is a viable technique for investigating bulk systems.
 
@@
 \cite{RN362, RN418}
-
 Most quantitative methods in an n$^{th}$ order CMDS experiment are used to extract $\chi^{(n)}$ values to compare the relative strength of nonlinear processes in different media.
@@
 These quantities are usually extracted from their incoherent analogues (IR spectroscopy, spontaneous Raman spectroscopy, spontaneous hyper-Raman spectroscopy). \cite{Levenson1974_2, RN412, Shoute2005}
+
 Calculating $\beta_{ijk}$ values from hyper-Raman experiments is difficult and has only been performed for a few molecular vibrations. \cite{Xu1997, Shoute2005, Kelley2010}
 Methods reported in the literature to measure absolute hyper-Raman polarizabilities depend upon external standards such as hyperpolarizabilities of dissolved samples or two-photon absorption cross sections, also difficult to measure.
-Since the Bloembergen interferometry experiment only relies on the third order susceptibility for measured species (such as benzene or CaF$_2$), it is possible to use quantitative four wave mixing spectroscopy to calculate $\beta_{ijk}$ values.
+Since the Bloembergen interferometry experiment only relies on the third order susceptibility for measured species (e.g., benzene or CaF$_2$),\cite{Levenson1974_2} it is possible to use quantitative four wave mixing spectroscopy to calculate $\beta_{ijk}$ values.
 It is thus useful to investigate how a treatment of orientational averaging can extract $\beta_{ijk}$ from the HDFG $\chi^{(3)}_{IJKL}$ expression.
@@
 However, since the real and imaginary components of $\chi^{(3)}$ can be measured through the Bloembergen interferometry experiment, and $\beta_{ijk}$ is present in either term, we can choose to focus on the real or imaginary part of $\chi^{(3)}$.
-For simplicity, we investigate $\Im(\chi^{(3)})$, giving, assuming resonance conditions, 
+When resonant, $\Re(\chi^{(3)})$ vanishes.
+As such, assuming resonance conditions, we investigate $\Im(\chi^{(3)})$, giving, 
 \begin{equation}
-	\langle \beta_{ijk} \mu_{l} \rangle = \frac{4D \hbar \varepsilon_0}{NF} \Gamma_{gv} \frac{1}{\rho_{gg}} \Im(\chi^{(3)}_{IJKL})
+	\langle \beta_{ijk} \mu_{l} \rangle = -\frac{4D \hbar \varepsilon_0}{NF} \Gamma_{gv} \frac{1}{\rho_{gg}} \Im(\chi^{(3)}_{IJKL})
 \end{equation}
 The steps behind orientational averaging of $\gamma_{ijkl}$, a rank four tensor in the molecular frame, are detailed elsewhere.\cite{Andrews1977, McDonnell2024}
-Briefly, a tensor in the molecular frame, A$_{ijkl}$ is transformed into an element of the same tensor in the laboratory frame, A$_{IJKL}$ through A$_{IJKL}$ = $\theta^{ijkl}_{IJKL} A_{ijkl} = \langle A_{ijkl} \rangle$, where summation over repeated indices is implied and $\theta$ is the transformation operator.
+Briefly, a tensor in the molecular frame, A$_{ijkl}$, is transformed into an element of the same tensor in the laboratory frame, A$_{IJKL}$, through A$_{IJKL}$ = $\theta^{ijkl}_{IJKL} A_{ijkl} = \langle A_{ijkl} \rangle$, where summation over repeated indices is implied and $\theta$ is the transformation operator.
 \cite{McDonnell2024}
-Orientational averaging shows specific polarization schemes isolate linear combinations of different $\beta_{ijk}$ terms. \cite{Cyvin1965, Bersohn1966}
+Orientational averaging shows specific polarization schemes isolate linear combinations of different $\beta_{ijk}$ terms. \cite{Bersohn1966, Willetts1992, Kauranen1996}
 By using the expansions of $\beta_{ijk}$ and $\mu_{l}$ to $\order{Q_n}$ found earlier, we see
 \begin{equation}\label{betasive}
-	\langle \frac{\partial \beta_{ijk}}{\partial Q_n} {\frac{\partial \mu_l}{\partial Q_n}} \rangle = \frac{8D \varepsilon_0}{NF}  \frac{\Gamma_{gv} \omega_{vg}}{\rho_{gg}} {\Im(\chi^{(3)}_{IJKL})}
+	\langle \frac{\partial \beta_{ijk}}{\partial Q_n} {\frac{\partial \mu_l}{\partial Q_n}} \rangle = -\frac{8D \varepsilon_0}{NF}  \frac{\Gamma_{gv} \omega_{vg}}{\rho_{gg}} {\Im(\chi^{(3)}_{IJKL})}
 \end{equation}
-Since $\abs{\mu}$ values can be extracted from FT-IR spectra,\cite{McDonnell2024} HDFG can give quantitative information on the magnitude of $\beta_{ijk}$ for infrared active vibrations.
+Since $\abs{\mu}$, and by extension $\abs{\partial \mu / \partial Q}$, values can be extracted from FT-IR spectra, HDFG can give quantitative information on the magnitude of $\beta_{ijk}$ for infrared active vibrations.
+Additionally, by using two different input frequencies to stimulate the hyper-Raman transition, the asymmetric properties of $\beta_{ijk}$ can be examined and quantified.
+\cite{Christie1971, Denisov1986, Kozich2007}
+To our knowledge, no experiment has been performed which quantifies deviations of the asymmetric and symmetric components of $\beta_{ijk}$. 
+These quantitative aspects of HDFG could prove useful to examine how well computational methods calculate $\beta_{ijk}$ values and the strength of spontaneous hyper-Raman scattering with non-degenerate pulses.
 
@@
 \begin{equation}
-	R^{(3)}(t) = \frac{i}{\hbar} [\beta(t), \mu(0)] \exp(-i\Delta_{gv}t) \theta(t) 
+	R^{(3)}(t) = \frac{i}{\hbar} \beta_{ijk} \mu_l \exp(-i\Delta_{gv}t) \theta(t) 
 \end{equation}  
@@
 It is well known that nonlinear wave mixing processes which share the same time ordering and output frequency will interfere. \cite{RN342, RN135}
-Understanding interfering pathways is useful because they can, in some cases, eliminate output. 
+Understanding interfering pathways is useful because they can eliminate nonlinear output. 
 While we have only isolated one specific HDFG process so far, there are at least fourteen different WMELs which can provide HDFG output in the driven limit. \cite{RN352}
@@
 	\includegraphics[width=3.375in]{figures/timeorderedwmel.png}
-	\caption{WMEL diagrams of interfering HDFG pathways in the  $\vec{k}_4 = -\vec{k}_1 + \vec{k}_2 + \vec{k}_3$ phasematching geometry. 
+	\caption{WMEL diagrams of HDFG pathways in the  $\vec{k}_4 = -\vec{k}_1 + \vec{k}_2 + \vec{k}_3$ phasematching geometry when $\omega_2$ interacts with the system first. 
 		}
@@
 
-The third order response functions for the pathways detailed in \autoref{fig:sivewmel2} when $\omega_1$ and $\omega_3$ are temporally overlapped are 
+The third order response functions for the pathways detailed in \autoref{fig:sivewmel2} when $\omega_1$ and $\omega_3$ are temporally overlapped, assuming $\rho(-\infty) = 1$, in the limit of homogeneous broadening are
 \begin{subequations}
 	\begin{equation} \label{mixing:a}
-		R^{(3)}_{a} (t_2) = R^{(3)}_{c} (t_2) = -\frac{i}{\hbar} [\beta(t_2), \mu(0)] \exp(-i\Delta_{vg}t_2) \theta(t_2)
+		R^{(3)}_{a} (t_2) = R^{(3)}_{c} (t_2) = -\frac{i}{\hbar} \beta_{ijk}(t_2) \mu_l(0)  \exp(-i\Delta_{vg}t_2) \theta(t_2)
 	\end{equation}
 	\begin{equation}\label{mixing:b}
-		\begin{split}
-			R^{(3)}_{b} (t_2) = R^{(3)}_{d} (t_2) & = \frac{i}{\hbar} [\beta(t_2), \mu(0)] \exp(-i\Delta_{vg}t_2) \theta(t_2)\\
-		\end{split}
+			R^{(3)}_{b} (t_2) = R^{(3)}_{d} (t_2) = \frac{i}{\hbar} \beta_{ijk}(t_2) \mu_l(0)  \exp(-i\Delta_{vg}t_2) \theta(t_2)
 	\end{equation}
@@
 In the case of the \autoref{fig:hdfg}a time ordering, there are no opportunities for interference from other third order processes. 
-However, a possible mechanism for interfering output in the \autoref{fig:hdfg}a pathway is a cascaded second order process (SFG, DFG). \cite{RN243, RN300}
-While unimportant in isotropic systems, second order cascades may become important in media where SFG and DFG are allowed, e.g. surfaces or noncentrosymmetric media.
+However, a possible mechanism for interfering output in the \autoref{fig:hdfg}a pathway is a cascaded second order process (SFG, DFG). \cite{RN300}
+While unimportant in achiral isotropic systems,\cite{Belkin2000} second order cascades may become important in media where SFG and DFG are allowed, e.g.
+chiral media, interfaces or noncentrosymmetric media.
 
-\section{Conclusions}%todo:fix!
+\section{Conclusions}
 Coherent vibrational, hyper-Raman coherent four wave mixing spectroscopies are identified and discussed.
-Singly resonant SIVE (SR-SIVE) processes are shown to be the coherent hyper-Raman analogue of infrared active vibrations.
-Since SR-SIVE is always non-zero for IR active vibrations, the method could be used as an analytical method to optically upconvert infrared transitions with small transition dipoles.
-A method for measuring hyper-Raman polarizabilities, $\beta_{ijk}$, through SIVE spectroscopy was identified and discussed.
-Extracting the magnitude and sign of $\beta_{ijk}$ using SIVE methods can help assess the quality of theoretical methods which calculate hyper-Raman spectra.
+Singly resonant hyper difference frequency generation (SR-HDFG) processes are shown to be the coherent hyper-Raman analogue of infrared active vibrations.
+We find that HDFG is always allowed for harmonic transitions, making it a potential tool for measuring single quantum coherence lifetimes. 
+Through an examination of the hyper-Raman $A,B,C$ terms as they appear in the doubly resonant HDFG (DR-HDFG) output, the impact of vibronic coupling in DR-HDFG spectrum was examined.
+It is found that the $A$ term dominates in DR-HDFG, but vanishes in SR-HDFG and select cases (e.g. centrosymmetry) in DR-HDFG. 
+The non-Condon effects that are present in the absence of $A$ might prove useful for dissecting the structure of modes which involve particular IR active vibrations in vibronic coupling.
+Through a simple treatment, it is seen that HDFG and vibrational sum frequency generation (vSFG) have roughly the same output intensities. 
+This makes HDFG a reasonable spectroscopy for systems outside of the ideal solvents tested in the literature, and should be readily extended to a variety of non-ideal molecular and materials systems. 
+Based upon a simple treatment of orientational averaging, we show that HDFG can provide a probe of the hyper-Raman hyperpolarizability without a need for technically difficult, analytically rigorous hyper-Raman scattering experiments.
+The HDFG method shows promise as a spectroscopic probe of unique electronic structure effects in a variety of molecular systems, but also for understanding the dynamics of single vibrational modes. 
+\section{Data Availability}
+The workup scripts which support this work can be found at [insert github link here].
 
@@
 R.P.M. acknowledges support from the NSF Graduate Research Fellowship Program (Grant no. DGE-2137424).
+
+%todo: figure out how footnotes work...
+
+%{By defining $\Lambda^{mn}_{ij} = \sum_k (m|M_i|k) (k|M_j|n)$, expanding $\Lambda^{mn}_{ij}$ to $\order{Q}$ gives $\Lambda^{mn}_{0,ij} + \partial/ \partial Q \sum_k (m|M_i|k) (k|M_j|n) Q$ = $\Lambda^{mn}_{0,ij} + \sum_k (m|\partial M_i / \partial Q|k) (k|M_j|n) Q + (m|M_i|k) (k|\partial M_j / \partial Q|n) Q$, in agreement with the substitution made above.}
 

### 2024-07-22 paper.tex
as sent to the group on 07/22/2024

@@
 Nonlinear, four wave mixing vibrational spectroscopies are often used to probe intramolecular vibrational coupling and relaxation dynamics in isotropic media.
-Three wave mixing vibrational spectroscopies are similarly used to understand the spectroscopy and dynamics of interfacial species.
-Most of these methods rely on infrared or Raman transitions to generate output. 
-Implementing a nonlinear spectroscopy involving hyper-Raman transitions, first appearing under third order perturbation theory, can provide a useful analogue to infrared and Raman based nonlinear spectroscopies to understand the spectroscopy and dynamics of isotropic systems.
+Three wave mixing vibrational spectroscopies, such as vibrational sum frequency generation (vSFG) are similarly used to probe the spectroscopy and dynamics of interfacial species.
+Most of these methods rely on infrared and/or Raman transitions to generate output. 
+Implementing a nonlinear spectroscopy involving hyper-Raman transitions, first appearing at third order perturbation theory, can provide a useful analogue to infrared and Raman based nonlinear spectroscopies to understand the spectroscopy and dynamics of isotropic systems.
 Hyper Difference Frequency Generation (Hyper-DFG, or HDFG) spectroscopy, also known as singly vibrationally enhanced spectroscopy (SIVE), is an underdeveloped, hyper-Raman based four wave mixing vibrational spectroscopy.
@@
 \section{Introduction}
-Coherent multidimensional spectroscopy (CMDS) is a family of three and four wave mixing methods which form the optical analogue of multidimensional nuclear magnetic resonance (NMR) spectroscopy.\cite{RN103, Cho2008}
+Coherent multidimensional spectroscopy (CMDS) is a family of three and four wave mixing methods which form the optical analogue of multidimensional nuclear magnetic resonance (NMR) spectroscopy.\cite{Cho2008}
 Multiresonant, four wave mixing CMDS experiments, first proposed by Oudar and Shen in 1980,\cite{RN307} directly probe coupling and correlations between different vibrational, electronic, and vibronic states.
-\cite{RN307, RN281, RN103, Cho2008}
+\cite{RN281, RN103, Cho2008}
 Four wave mixing CMDS has resolved anharmonicities, ultrafast dynamics, and other intramolecular couplings in numerous systems. \cite{Cho2008, Gaynor2017, Ziegler2018, Ogilvie2019, Bonn2021, RN325}
@@
 HDFG was one of the first infrared CMDS methods to successfully discriminate against non-resonant background.\cite{RN351, RN352}
-HDFG has also been referred to as singly vibrationally enhanced (SIVE) spectroscopy. \cite{RN351}
+HDFG has also been referred to as singly vibrationally enhanced (SIVE) spectroscopy. \cite{RN352}
 In HDFG, an infrared pulse is resonant with a vibrational mode, and two other input pulses are used to stimulate a scattering process.
@@
 To make the connection between HDFG and hyper-Raman scattering, we investigate its gross selection rules.
-By propagating density matrix elements in the steady state limit, the HDFG hyperpolarizability is \cite{RN133}
+By propagating density matrix elements in the steady state limit under the rotating wave approximation, the HDFG hyperpolarizability is \cite{RN133}
 \begin{equation}\label{sivegamma}
@@
 \subsection{Placzek Method}
-We first investigate the selection rules through a Placzek type formalism.
+We first investigate the HDFG selection rules through a Placzek type formalism.
 Contracting over the virtual states forms the hyper-Raman hyperpolarizability $\beta$.\cite{Long1970} 
@@
 		Note that (b) shows magnitudes of the labeled quantities.
-		The vibrational states on the $|g)$ and $|e)$ manifolds are spaced 2200 cm$^{-1}$ apart, with the vibronic states $\ket{e,v}$ given linewidths of 700 cm$^{-1}$ and $\hbar \omega_{eg}$ = 30000 cm$^{-1}$.
-		Dotted lines in (b) denote placement of vibronic resonances for $v'$ = 0, 1, 2. }
+		The vibrational states on the $|g)$ and $|e)$ manifolds are spaced 2200 cm$^{-1}$ apart, with the vibronic states $\ket{e,v'}$ given linewidths of 700 cm$^{-1}$ and $\hbar \omega_{eg}$ = 30000 cm$^{-1}$.
+		Dotted lines in (b) denote the $v'$ = 0, 1, 2 vibronic resonances. 
+		The vibronic one and two photon absorption operators are scaled such that $\abs{B_j}/\abs{A} \sim$ 0.01}
 	\label{fig:doubres_spec}
@@
 \end{widetext}
-where N$_{bulk}$ is the bulk number density, and N$_{surf}$ is the surface number density ($\sim$ 10$^{17}$ m$^{-2}$).\cite{RN133, Du1994}	
+where N$_{bulk}$ is the bulk number density, and N$_{surf}$ is the surface number density ($\sim$ 10$^{16}$ m$^{-2}$ for H$_2$O adsorbed at quartz).\cite{RN133, Du1994}	
+We assumed here that $\int_{0^-}^\ell \mathrm{d}z \langle \alpha_{ij}\mu_{k} \rangle \approx \ell \langle \alpha_{ij}\mu_{k} \rangle$, where $z$ is oriented along the surface normal and $0^{-}$ is the edge of the interface where substrate begins.
+\cite{RN133}
+We take the film thickness ($\ell$) that can be probed by vSFG to be 1 nm, much less than the vSFG coherence length.\cite{RN133, Su1998}
 For liquids with molar masses less than $\sim$100 g mol$^{-1}$ and densities roughly equal to that of H$_2$O$_{(l)}$ at room temperature, N$_{bulk} \sim$ 10$^{28}$ m$^{-3}$.
-We take the length of layers along the surface normal ($\ell$) to be 10 nm.\cite{RN133}
 A normal dispersion curve is assumed so that $F(\omega_1+\omega_2) \approx F(2\omega_2-\omega_1)$.
@@
 Since the intensity ratio scales as $\abs{P_{ratio}}^2$, we see that the HDFG output is roughly as strong as vSFG, assuming only interfacial contributions in vSFG.
-It is important to note that this derivation ignored absorption and orientational averaging effects, which can significantly reduce output from either process. 
+It is important to note that this calculation assumed negligible dipole and Raman polarizability dependence upon the distance from surface normal, ignored orientational averaging effects, and presumed equivalence of local field factors, all of which can significantly reduce output from either process.
 Nevertheless, since HDFG produces a number of photons similar to that of vSFG, HDFG is a viable technique for investigating bulk systems.
@@
 Time domain HDFG could be a useful alternative technique for measuring single quantum coherence dephasing times.
-The response function for the HDFG pathway illustrated in \autoref{fig:hdfg}a, assuming $\omega_2$ and $\omega_3$ are temporally overlapped, is \cite{RN287, Cho2001}
+Working under the rotating wave approximation and neglecting spatial components, the output polarization is written in the time domain as 
 \begin{equation}
-	R^{(3)}(t) = \frac{i}{\hbar} \beta_{ijk} \mu_l \exp(-i\Delta_{gv}t) \theta(t) 
+	\begin{split}
+			\vec{P}(t) &= \int_0^\infty \mathrm{d}t_3 \int_0^\infty \mathrm{d}t_2 \int_0^\infty \mathrm{d}t_1 R^{(3)}(t_1, t_2, t_3)  \vdots \vec{E}_3(t-t_3) \\
+			&\vec{E}_2(t-t_3-t_2 - \tau_{23}) \vec{E}_1(t-t_3-t_2-t_1 - \tau_{13}) 
+	\end{split}
 \end{equation}
+where the electric fields are labeled according to their placement in the WMEL diagrams, $\tau_{ij} = \tau_i - \tau_j$ is the time delay between pulses $i$ and $j$, and R is the response function.
+\cite{RN287}
+Here, we will focus on the response function formalism for singly resonant HDFG, as the extension to doubly resonant HDFG has been treated by Cho. \cite{Cho2001}
+The response function for the HDFG pathway illustrated in \autoref{fig:hdfg}a, assuming $\omega_2$ and $\omega_3$ are temporally overlapped, not electronically resonant, and $\rho(-\infty) = 1$, in the limit of homogeneous broadening is \cite{Cho2001, Meyer2004, RN367}
+\begin{equation}
+	R^{(3)}(t_1) = \frac{i}{\hbar} \beta_{ijk}(t_1) \mu_l(0) \exp(-i\Delta_{gv}t_1) \theta(t_1) 
+\end{equation}  
+where $\theta$ is the Heaviside function.
 The pure time-domain HDFG output reports on the dephasing characteristics of the $\ket{g}\bra{v}$ coherence. 
@@
 Polarization control in IR-pump-HDFG-probe, analogous to ultrafast transient absorption spectroscopy for vibrational modes, would be an interesting venue to assess the sensitivity of HDFG to different hyper-Raman tensor elements.
-
-Combinations of time and frequency domain spectroscopy, also called mixed domain spectroscopy, are useful ways to understand frequency-dependent dynamics. \cite{RN135, RN171, RN131}
-Mixed domain spectroscopy is a useful alternative to steady state spectroscopy as pulse separation can eliminate nonresonant background and isolate specific pulse ordering sequences.
-\cite{RN372, RN324, McDonnell2024}
-Isolating different pulse orderings can isolate pathway specific signal and minimize interference from unwanted pathways which share the same phasematching constraints. 
-Mixed domain HDFG can resolve frequency dependent free induction decay, which could prove useful for understanding isotropic dynamics of single quantum coherences. 
-Mixed domain resonant HDFG, using pathways similar to those in \autoref{fig:hdfg}b, could also measure time-dependent electronic-vibrational fluctuations, as discussed by Cho. \cite{Cho2001}
-These methods should be able to provide complimentary information to that found in 2D Electronic-Vibrational (2D-EV) spectroscopy. \cite{Dong2015, Lewis2015, Gaynor2017}
 
@@
 
+Combinations of time and frequency domain spectroscopy, also called mixed domain spectroscopy, are useful ways to understand frequency-dependent dynamics. \cite{RN135, RN367, RN171, RN131}
+Mixed domain spectroscopy is a useful alternative to steady state spectroscopy as pulse separation can eliminate nonresonant background and isolate specific pulse ordering sequences.
+\cite{RN372, RN324, McDonnell2024}
+Isolating different pulse orderings can isolate pathway specific signal and minimize interference from unwanted pathways which share the same phasematching constraints. 
+Mixed domain HDFG can resolve frequency dependent free induction decay, which could prove useful for understanding isotropic dynamics of single quantum coherences. 
+Mixed domain resonant HDFG, using pathways similar to those in \autoref{fig:hdfg}b, could also measure time-dependent electronic-vibrational fluctuations, as discussed by Cho. \cite{Cho2001}
+These methods should be able to provide complimentary information to that found in 2D Electronic-Vibrational (2D-EV) spectroscopy. \cite{Dong2015, Lewis2015, Gaynor2017}
+
 \section{Conclusions}
@@
 This makes HDFG a reasonable spectroscopy for systems outside of the ideal solvents tested in the literature, and should be readily extended to a variety of non-ideal molecular and materials systems. 
-Based upon a simple treatment of orientational averaging, we show that HDFG can provide a probe of the hyper-Raman hyperpolarizability without a need for technically difficult, analytically rigorous hyper-Raman scattering experiments.
-The HDFG method shows promise as a spectroscopic probe of unique electronic structure effects in a variety of molecular systems, but also for understanding the dynamics of single vibrational modes. 
+Based upon a simple treatment of orientational averaging, we show that HDFG can extract the hyper-Raman hyperpolarizability without a need for technically difficult, analytically rigorous hyper-Raman scattering experiments.
+The HDFG method shows promise as a spectroscopic probe of unique electronic structure effects in a variety of molecular systems, but also for understanding the dynamics of single quantum coherences. 
 \section{Data Availability}

### 2024-07-22 figures/2D_spec.py

@@ -11,7 +11,7 @@ from matplotlib.patches import FancyArrowPatch
 
 wt.artists.apply_rcparams(kind="publication")
 
-save = False
+save = True
 
 fontsize = 18
 
@@ -20,10 +20,10 @@ d = 0.5 #offset for es
 do = 0 #gs placement
 
 def grs(k):
-    return 0.125*(k-do)**2
+    return 0.125*(k-do)**2 #arbitrary curvature
 
 def es(k):
-    return 0.125*(k-d-do)**2 + 0.7
+    return 0.125*(k-d-do)**2 + 0.7 #arbitrary curvature and vertical offset
 
 kg = np.linspace(-2, 2, 500) #ground state coordinates
 ke = np.linspace(-1.75, 2.75, 500) #excited state coordinates

### 2024-07-22 paper.tex
whoops

@@
 \cite{RN287}
-Here, we will focus on the response function formalism for singly resonant HDFG, as the extension to doubly resonant HDFG has been treated by Cho. \cite{Cho2001}
+Here, we will focus on the response function formalism for singly resonant HDFG, as the extension to doubly resonant HSFG, easily transferable to DR-HDFG, has been treated by Cho. \cite{Cho2001}
 The response function for the HDFG pathway illustrated in \autoref{fig:hdfg}a, assuming $\omega_2$ and $\omega_3$ are temporally overlapped, not electronically resonant, and $\rho(-\infty) = 1$, in the limit of homogeneous broadening is \cite{Cho2001, Meyer2004, RN367}

### 2024-07-22 build.py

@@ -3,7 +3,7 @@ import subprocess
 import platform
 import click
 
-osf_project = "2amkq"
+#osf_project = "2amkq"
 here = pathlib.Path(__file__).resolve().parent
 
 
@@ -39,26 +39,16 @@ def _build_documents():
 
 def _build_figures():
     print_with_line('figures')
-    print_then_call(python, str(here / "figures" / "workup.py"))
-    # print_then_call(python, str(here / "figures" / "preamp.py"))
-    # print_then_call(python, str(here / "figures" / "poweramp.py"))
-    # print_then_call(python, str(here / "figures" / "powerampslice.py"))
-    # print_then_call(python, str(here / "figures" / "tunetest.py"))
-    # print_then_call(python, str(here / "figures" / "spectral_delay_corrections.py"))
-
+    print_then_call(python, str(here / "figures" / "wmels.py"))
+    print_then_call(python, str(here / "figures" / "2D_spec.py"))
 
 @click.group()
 def main():
     pass
 
-@main.command(name="fetch", help="download and extract the [raw data](https://osf.io/2nr9d)")
-def fetch_data():
-    _fetch_data() 
-
 @main.command(name="all", help="build all steps")
 def all_():
     print_with_line('building everything!')
-    _fetch_data()
     _build_figures()
     _build_documents()
     print_with_line('building done!')

### 2024-07-22 figures/wmels.py

@@ -10,9 +10,9 @@ from WrightTools.diagrams import WMEL
 # import WrightTools as wt
 
 comparisonwmel = True
-hdfg = True
+hdfg = False
 timeorderedwmel = True
-drwmel = True
+drwmel = False
 
 if comparisonwmel:
     fig = WMEL.Artist([6,1], [0, 0.2, 0.6, 1], state_names=("$\mathsf{| g\\rangle}$",

### 2024-07-23 paper.tex
Units adjusted
This resolves issue #14.
Coverletter still in prep
Added what appears to be first journal article on coherent anti-Stokes hyper-Raman spectroscopy

@@
 \cite{Olson2018}
-Cho et al. have proposed parametric six wave mixing techniques as the coherent analogue of hyper-Raman scattering. \cite{Cho1997, Cho1998}
+Several authors have proposed parametric six wave mixing techniques as the coherent analogue of hyper-Raman scattering. \cite{Berger1978, Cho1997, Cho1998}
 However, since most six wave mixing methods cascade into four wave mixing processes and their homodyned output would be dependent upon the hyper-Raman scattering cross section, \cite{RN243,Cho1997, Cho1998, Cho2000_Cascade} it is preferable to investigate four wave mixing analogues to hyper-Raman scattering.
@@
 The C term is suppressed in the following discussion as it depends on one and two photon forbidden transitions. \cite{Ziegler1988, Neddersen1989, Bonang1992}
-Note that some reports obtain $A, B, C$ coefficients through a Herzberg-Teller expansion of the electronic states to explicitly expose vibronic couplings in terms of $\partial H / \partial Q $, where H is the electronic Hamiltonian.\cite{HerzbergTeller1933, Petrov1985, Neddersen1989, Baranov1990}
+Note that some reports obtain $A, B$ coefficients through a Herzberg-Teller expansion of the electronic states to expose vibronic couplings in terms of $\partial H / \partial Q$, where H is the electronic Hamiltonian.\cite{HerzbergTeller1933, Petrov1985, Neddersen1989, Baranov1990}
 This approach is not used here as the expansion of $\vec{M}^{ij}$ in normal mode coordinates provides sufficient physical insight into hyper-Raman selection rules.
@@
 	\begin{equation}
-		H_g = \frac{p^2}{2m} + \frac{1}{2} m^2 \omega^2 Q^2
+		H_g = \frac{p^2}{2m} + \frac{1}{2} \hbar \omega q^2
 	\end{equation}
@@
 	\begin{equation}
-		H_e = \frac{p^2}{2m} + \frac{1}{2} m^2 \omega^2 (Q-\xi)^2 +\hbar \omega_{eg}
+		H_e = \frac{p^2}{2m} + \frac{1}{2} \hbar \omega (q-\xi)^2 +\hbar \omega_{eg}
 	\end{equation}
 \end{subequations}
-for the ground ($H_g$) and first excited ($H_e$) states, where $p$ is the momentum of the normal mode, the A and B contributions can be evaluated using Franck-Condon and Herzberg-Teller integrals tabulated in terms of the dimensionless offset parameter, $\xi$ (\autoref{fig:doubres_spec}a).
+for the ground ($H_g$) and first excited ($H_e$) states, where $p$ is the momentum of the normal mode, the A and B contributions can be evaluated using Franck-Condon and Herzberg-Teller integrals tabulated in terms of the dimensionless normal mode $q$ and offset parameter $\xi$ (\autoref{fig:doubres_spec}a).
 \cite{Carlson1988thesis}
+Note that $q = m \sqrt{\omega/\hbar} Q$.
 The spectrum is simulated for an electronic state which is both one and two photon allowed.

### 2024-07-23 figures/2D_spec.py

@@ -80,7 +80,7 @@ ax0.text(ke.max()+0.12, es(ke.max())-0.05, '$\mathsf{|e)}$', fontsize = 24)
 ax0.plot(kg,grs(kg), linewidth = '4', color = 'cornflowerblue')
 ax0.plot(ke,es(ke), linewidth = '4', color = 'cornflowerblue')
 ax0.set_ylabel('$\mathsf{Energy \ (cm^{-1})}$', fontsize = fontsize)
-ax0.set_xlabel('$\mathsf{Q \ (\\frac{m}{\sqrt{kg}})}$', fontsize = fontsize)
+ax0.set_xlabel('$\mathsf{q}$', fontsize = fontsize)
 plt.ylim(-0.13, 1.4)
 plt.xlim(-2.2,3.25)
 plt.yticks(ticks = [])

### 2024-07-23 figures/2D_spec.py
fix tot scaling

@@ -9,7 +9,7 @@ import WrightTools as wt
 import matplotlib.pyplot as plt 
 from matplotlib.patches import FancyArrowPatch
 
-wt.artists.apply_rcparams(kind="publication")
+# wt.artists.apply_rcparams(kind="publication")
 
 save = True
 
@@ -46,7 +46,7 @@ myArrow1 = FancyArrowPatch(posA=(-0.35, yarrowstop[1]), posB=(-0.35, yarrow[1]),
 ax0.add_artist(myArrow0)
 ax0.add_artist(myArrow1)
 
-ax0.text(-0.65, (grs(0.6) + es(1.3))/2 - 0.023, '$\mathsf{\hbar \omega_{eg}}$', fontsize = 24)
+ax0.text(-0.65, (grs(0.6) + es(1.3))/2 - 0.023, r'$\mathsf{\hbar \omega_{eg}}$', fontsize = 24)
 
 #xi line 
 ax0.vlines(x = do, ymin = -0.0257, ymax = grs(do), color = 'gray', linestyle = '--', linewidth = 1)
@@ -58,7 +58,7 @@ xiarrow = FancyArrowPatch(posA=(xarrow[0], -0.0257), posB=(xarrow[1], -0.0257), 
 ax0.add_artist(xiarrow)
 
 
-ax0.text((do+d)/2-0.08, -0.101, '$\mathsf{\\xi}$', fontsize = 24)
+ax0.text((do+d)/2-0.08, -0.101, r'$\mathsf{\xi}$', fontsize = 24)
 
 #labeling vibrational states
 jgs = [0.6, 1.0, 1.29965]
@@ -73,14 +73,14 @@ for i in [0,1,2]:
 
     
 #harmonic surface labels
-ax0.text(kg.max()+0.12, grs(kg.max())-0.05, '$\mathsf{|g)}$', fontsize = 24)
-ax0.text(ke.max()+0.12, es(ke.max())-0.05, '$\mathsf{|e)}$', fontsize = 24)
+ax0.text(kg.max()+0.12, grs(kg.max())-0.05, r'$\mathsf{|g)}$', fontsize = 24)
+ax0.text(ke.max()+0.12, es(ke.max())-0.05, r'$\mathsf{|e)}$', fontsize = 24)
 
 #plot it
 ax0.plot(kg,grs(kg), linewidth = '4', color = 'cornflowerblue')
 ax0.plot(ke,es(ke), linewidth = '4', color = 'cornflowerblue')
[…]

### 2024-07-23 figures/wmels.py
small adjustments

@@ -18,7 +18,7 @@ if comparisonwmel:
     fig = WMEL.Artist([6,1], [0, 0.2, 0.6, 1], state_names=("$\mathsf{| g\\rangle}$",
                                                                    "$\mathsf{|v\\rangle}$", 
                                                                    "$\mathsf{|m\\rangle}$",
-                                                                   "$\mathsf{|n\\rangle}$"), number_of_interactions=5, state_font_size=9, state_text_buffer = 0.6, virtual = [2,3])
+                                                                   "$\mathsf{|n\\rangle}$"), number_of_interactions=4, state_font_size=9, state_text_buffer = 0.6, virtual = [2,3])
 
 
     fig.add_arrow([0,0], 0, [0,1], kind='bra', color="k", label = "$\mathsf{1}$", head_length = 0.075)
@@ -51,7 +51,7 @@ if comparisonwmel:
     fig.add_arrow([5,0], 2, [2,3], kind='ket', color="k", label = "$\mathsf{3}$", head_length = 0.075)
     fig.add_arrow([5,0], 3, [3,1], kind='out', color="blue", label = "$\mathsf{4}$", head_length = 0.075)     
 
-    fig.label_columns(['$\mathsf{DFG}$','$\mathsf{SFG}$','$\mathsf{Raman}$', '$\mathsf{HDFG}$', '$\mathsf{HSFG}$','$\mathsf{Hyper-Raman}$'], font_size = 10)
+    fig.label_columns(['$\mathsf{DFG}$','$\mathsf{SFG}$','$\mathsf{Raman}$', '$\mathsf{HDFG}$', '$\mathsf{HSFG}$','$\mathsf{Hyper-Raman}$'], font_size = 9)
     
     plt.savefig("comparisonwmel.png", bbox_inches='tight')
 
@@ -73,7 +73,7 @@ if timeorderedwmel:
                                                                    "$\mathsf{|m\\rangle}$", 
                                                                    "$\mathsf{|v\\rangle}$",
                                                                    "$\mathsf{|n\\rangle}$",
-                                                                   "$\mathsf{|p\\rangle}$"), number_of_interactions=5, state_font_size=9, state_text_buffer = 0.6, virtual = [1,3,4])
[…]

### 2024-07-25 paper.tex
Adjustments following group meeting discussion
This should address #16.

Many simplifications were made.
singly resonant part wiped
A discussion improved
SFG and beta terms motivated more
Added site selective discussion
Fixed WMELs (or tried to...)
Adjusted "many years ago"
Moved time domain to middle of selection rules section to motivate specific pathway.

@@
 %Title of paper
-\title{Coherent Hyper-Raman Four Wave Mixing Vibrational Spectroscopy}
+\title{Coherent IR-Hyper-Raman Four Wave Mixing Vibrational Spectroscopy}
 
@@
 Despite several experimental reports on HDFG, its spectroscopic properties have not been fully explored.
-To this end, we explore the selection rules and response functions of HDFG spectroscopy.
-Through the hyper-Raman $A,B$ terms, we explore the selection rules of singly and doubly resonant HDFG spectroscopy, and show HDFG is a hybrid IR-hyper-Raman technique.
+To this end, we investigate the selection rules and behavior of HDFG spectroscopy.
+We explore the selection rules of singly and doubly resonant HDFG spectroscopy through a Placzek and vibronic picture and show HDFG is a hybrid IR-hyper-Raman technique.
 Since all infrared active modes have non-zero hyper-Raman activity, this makes HDFG a type of upconverted infrared spectroscopy.
-HDFG is found to be uniquely sensitive to non-Condon effects in centrosymmetric species.
-Through a simple comparison test, HDFG output is shown to be similar in magnitude to vibrational sum frequency generation (vSFG).
-Since HDFG can also be implemented as a two beam experiment, similar to vSFG, this makes HDFG a spectroscopy feasible for practitioners of vSFG.
+Through a simple comparison test, we demonstrate that HDFG output is shown to be similar in magnitude to vibrational sum frequency generation (vSFG) in a transmission geometry.
+Since HDFG can also be implemented as a two beam experiment in a geometry similar to vSFG, HDFG is a feasible third order spectroscopy for vSFG practitioners.
 Through a simple treatment of orientational averaging, HDFG provides a simple method to extract hyper-Raman hyperpolarizabilities ($\beta$) of infrared active vibrations.
@@
 \cite{Bredenbeck2015, Arsenault2021}
-Some years ago, Cho proposed a parametric, doubly resonant infrared/visible pathway to probe vibronic coupling in isotropic systems. \cite{Cho2001}
+Cho has proposed a parametric, doubly resonant infrared/visible pathway to probe vibronic coupling in isotropic systems. \cite{Cho2001}
 In this method, a single infrared pulse is resonant with a vibrational mode, and a two photon absorption event from a near infrared (NIR) or visible pulse resonant with an electronic or vibronic state is used to generate the four wave mixing signal.
@@
 
-Inspired by recent work which demonstrated the presence of HDFG in ultrafast DOVE and terahertz-IR-visible (TIRV) experiments, we investigate the parameters which result in both SR and DR-SIVE output.
+Inspired by recent work which demonstrated the presence of HDFG in ultrafast DOVE and terahertz-IR-visible (TIRV) experiments, we investigate the parameters which result in HDFG output.
 \cite{Cho2000, Bonn2024, McDonnell2024}
 This paper is organized as follows.
-In \autoref{steadystate}, we identify the selection rules that drive singly and doubly resonant HDFG, first through the Placzek approximation, and then through hyper-Raman $A,B,C$ coefficients.
-After developing selection rules, some quantitative aspects of HDFG, particularly a comparison of vSFG and HDFG output and a method to extract hyper-Raman hyperpolarizabilities ($\beta_{ijk}$) from HDFG spectra, are discussed in \autoref{quant}.
-Finally, mixed time-frequency domain HDFG is discussed in \autoref{mixeddomain}.
+In \autoref{steadystate}, we first identify the selection rules that drives singly HDFG through the Placzek approximation.
+Specific, non-zero time-orderings of singly resonant HDFG are identified through a simple analysis of the relevant response functions.
+The selection rules of doubly resonant HDFG (DR-HDFG) are identified through the hyper-Raman $A,B,C$ coefficients.
+After developing selection rules, the site selective properties and useful experimental aspects of HDFG are discussed in \autoref{quant}.
+In particular, a comparison of vSFG and HDFG output is given, showing that HDFG and vSFG are roughly equally intense.
+A method to extract hyper-Raman hyperpolarizabilities ($\beta_{ijk}$) from HDFG spectra is identified and discussed.
 
-\section{Steady State HDFG Spectroscopy}\label{steadystate}
+\section{Selection Rules for HDFG Spectroscopy}\label{steadystate}
 
@@
 It is useful to expose relationships between transition dipoles, Raman polarizabilities and hyper-Raman hyperpolarizabilities in the driven limit. \cite{Simpson2004}
-In the driven limit, under the electric dipole approximation, the I$^{th}$ component of the third order nonlinear output polarization, ${P}^{(3)}_I$, of any four wave mixing process, induced by electric fields E, at output frequency $\omega_4$ is written as (using Einstein summation) \cite{RN307}
+In the driven limit, under the electric dipole approximation, the I$^{th}$ component of the third order nonlinear output polarization, ${P}^{(3)}_I$, of a four wave mixing process, induced by electric fields E, at output frequency $\omega_4$ is written as (using Einstein summation) \cite{RN307}
 \begin{equation} \label{polarization}
-{P}^{(3)}_I (\omega_4)  = \chi^{(3)}_{IJKL} E_J E_K E_L 
+{P}^{(3)}_I (\omega_4)  = \chi^{(3)}_{IJKL} E_J(\omega_3) E_K(\omega_2) E_L(\omega_1) 
 \end{equation}
@@
 where N is a number density, F is the Lorentz local field factor, and $\gamma_{ijkl}$ is the third order polarizability (i.e., second hyperpolarizability). 
-The brackets indicate an orientational average. 
+The brackets indicate an orientational (or rotational) average.\cite{Andrews1977}
 Uppercase letters refer to laboratory frame coordinates and lower case letters refer to molecular frame coordinates.
@@
 
+\subsection{Importance of Time Ordering}
+With the general selection rule of HDFG identified through the Placzek approximation, it is useful to briefly discuss time-dependent HDFG before considering the properties of $\beta_{ijk}$ in more detail.
+In time-domain spectroscopy, the output is dependent upon the third order response function, $R^{(3)}$, a rank-four tensor (indices are suppressed for simplicity).
+Neglecting spatial components, the third order nonlinear output polarization is written in the time domain as \cite{RN287}
+\begin{equation}
+	\begin{split}
+		\vec{P}^{(3)}(t) &= \int_0^\infty \mathrm{d}t_3 \int_0^\infty \mathrm{d}t_2 \int_0^\infty \mathrm{d}t_1 \langle R^{(3)}(t_1, t_2, t_3) \rangle  \vdots \vec{E}_3(t-t_3) \\
+		&\vec{E}_2(t-t_3-t_2 - \tau_{23}) \vec{E}_1(t-t_3-t_2-t_1 - \tau_{13}) 
+	\end{split}
+\end{equation}
+where the electric fields are labeled according to their placement in the WMEL diagrams and $\tau_{ij} = \tau_i - \tau_j$ is the time delay between pulses $i$ and $j$.
+Here, we will focus on the response function formalism for singly resonant HDFG, as the extension to doubly resonant HSFG, easily transferable to DR-HDFG, has been treated by Cho. \cite{Cho2001}
+The response function for the HDFG pathway illustrated in \autoref{fig:comparisonwmel}, assuming $\omega_2$ and $\omega_3$ are temporally overlapped and $\rho(-\infty) = 1$, in the limit of homogeneous broadening is
+\begin{equation}
+	R^{(3)}(t_1) = -\frac{i}{\hbar} \beta_{ijk} \mu_l \exp(-i\Delta_{gv}t_1) \theta(t_1) 
+\end{equation}  
+where $\theta$ is the Heaviside function. \cite{Cho2001, RN135, Meyer2004, RN367}
+The pure time-domain HDFG output of the \autoref{fig:comparisonwmel} pathway reports on the dephasing characteristics of the $\ket{g}\bra{v}$ coherence. 
+Since HDFG is non-zero for any harmonically allowed infrared vibration, HDFG provides a method for measuring the free induction decay of vibrational modes without the need for anharmonicities.
+
+It is well known that nonlinear wave mixing processes which share the same time ordering and output frequency will interfere. \cite{RN342, RN135}
+Understanding interfering pathways is useful because they can eliminate nonlinear output. 
+While we have only isolated one specific HDFG process so far, there are at least fourteen different WMELs which can provide HDFG output in the driven limit. \cite{RN352}
+If $\omega_2$ ($\omega_1$) becomes resonant (non-resonant), where $\omega_2 > \omega_1$, then other HDFG pathways appear (\autoref{fig:sivewmel2}).\cite{McDonnell2024} 
+While the methods in \autoref{fig:sivewmel2} possess identical selection rules to \autoref{fig:comparisonwmel}, the WMEL diagrams presented in \autoref{fig:sivewmel2} will interfere, as they share the same phasematching condition but have oppositely signed amplitudes.
+\begin{figure}[!htbp]
+	\centering
+	\includegraphics[width=3.375in]{figures/timeorderedwmel.png}
+	\caption{WMEL diagrams of HDFG pathways in the  $\vec{k}_4 = -\vec{k}_1 + \vec{k}_2 + \vec{k}_3$ phasematching geometry when $\omega_2$ interacts with the system first. 
+	}
+	\label{fig:sivewmel2}
+\end{figure}
+
+The third order response functions for the pathways detailed in \autoref{fig:sivewmel2} when $\omega_1$ and $\omega_3$ are temporally overlapped, assuming $\rho(-\infty) = 1$, in the limit of homogeneous broadening are
+\begin{subequations}
+	\begin{equation} \label{mixing:a}
+		R^{(3)}_{a} (t_2) = R^{(3)}_{c} (t_2) = -\frac{i}{\hbar} \beta_{ijk} \mu_l \exp(-i\Delta_{vg}t_2) \theta(t_2)
+	\end{equation}
+	\begin{equation}\label{mixing:b}
+		R^{(3)}_{b} (t_2) = R^{(3)}_{d} (t_2) = \frac{i}{\hbar} \beta_{ijk} \mu_l  \exp(-i\Delta_{vg}t_2) \theta(t_2)
+	\end{equation}
+\end{subequations}
+The total response function for \autoref{fig:sivewmel2} is therefore $R^{(3)}_\text{tot} (t_2) = R^{(3)}_{a} (t_2) + R^{(3)}_{b} (t_2) + R^{(3)}_{c} (t_2) + R^{(3)}_{d} (t_2) = 0$. 
+Since the total output response function vanishes in this time-ordering, the \autoref{fig:sivewmel2} pathways perfectly destructively interfere.
+Therefore, to measure dynamics via HDFG, the time ordering shown in \autoref{fig:hdfg} should be used.
+These ideas have been seen experimentally in ultrafast DOVE work. \cite{RN367, McDonnell2024}
+In the case of the \autoref{fig:hdfg}a time ordering, assuming $\omega_2 > \omega_1$, there are no other resonant WMELs that can allow for interference from other third order processes. 
+However, a possible mechanism for interfering output in the \autoref{fig:hdfg}a pathway is a cascaded second order process (SFG, DFG). \cite{RN301}
+While unimportant in achiral isotropic systems,\cite{Belkin2000} second order cascades may become important in media where SFG and DFG are allowed, e.g.
+chiral media, interfaces or noncentrosymmetric media.
+Nevertheless, in the discussion that follows for the rest of this manuscript, we will assume negligible second order cascades, and use the pathways drawn in \autoref{fig:hdfg} to examine HDFG  response.
 \begin{figure}[!htbp]
@@
 \end{figure}
-\subsection{Albrecht Type Expansion}
-While Placzek type arguments provide the general source of HDFG output, it is insightful to interpret the origin of signal in terms of $A,B,C$ terms, analogous to those found in Albrecht's treatment of Raman spectroscopy.\cite{Albrecht1961, Ziegler1988}
+
+\subsection{Expansion in terms of Hyper-Raman $A,B$ Parameters}
+While Placzek type arguments provide the general source of HDFG output in the driven limit, it is insightful to interpret the origin of signal through the $A,B,C$ terms introduced by Chung and Ziegler, analogous to those found in Albrecht's treatment of Raman spectroscopy.\cite{Albrecht1961, Ziegler1988}
 We write $\beta_{ijk}$ in \autoref{SIVEselection} using the hyper-Raman ABC formalism introduced by Chung and Ziegler to understand how vibronic coupling manipulates selection rules for singly and doubly resonant HDFG (\autoref{fig:hdfg}).
 \cite{Ziegler1988}
-To employ this formalism, we write the states in terms of a Born-Oppenheimer basis $\ket{a,b}$, where $\ket{a,b} = |a(Q)) \otimes \ket{b}$ for electronic states $\{|a(Q))\}$ and vibrational states $\{\ket{b}\}$ (i.e., adiabatic approximation).
+To employ this formalism, we write the states in a Born-Oppenheimer basis $\ket{a,b}$, where $\ket{a,b} = |a(Q)) \otimes \ket{b}$ for electronic states $\{|a(Q))\}$ and vibrational states $\{\ket{b}\}$ (i.e., adiabatic approximation).
 \cite{BornOppenheimer, Tang1970}
@@
 $R_{i}^{gv,ev'} = \mel{v}{M_i^{ge}}{v'}$.
-Chung and Ziegler showed some years ago that expanding $\vec{M}^{ij}$ to $\order{Q}$ \textit{about the equilibrium point of the ground state potential surface} as
+Chung and Ziegler showed that expanding $\vec{M}^{ij}$ to $\order{Q}$ \textit{about the equilibrium point of the ground state potential surface} as
 $\vec{M}^{ij} = \vec{M}^{ij}_0 + \sum_z \frac{\partial\vec{M}^{ij}}{\partial Q_z} Q_z$
@@
 \begin{equation}
-		\gamma_{ijkl} \sim \frac{(A_{ijk} + B_{ijk} + C_{ijk})\mel{v}{\mu_{l}}{0}} {\Delta_{g0,gv}}
+		\gamma_{ijkl} \sim \left(A_{ijk} + B_{ijk} + C_{ijk}\right) \frac{\mel{v}{\mu_{l}}{0}} {\Delta_{g0,gv}}
 \end{equation}
-The $A$ term depends upon $\order{Q^0}$ transitions (i.e., Condon approximation), the $B$ term depends upon $\order{Q}$ transitions, and the $C$ term depends on $\order{Q^2}$ transitions. 
-The C term is suppressed in the following discussion as it depends on one and two photon forbidden transitions. \cite{Ziegler1988, Neddersen1989, Bonang1992}
-Note that some reports obtain $A, B$ coefficients through a Herzberg-Teller expansion of the electronic states to expose vibronic couplings in terms of $\partial H / \partial Q$, where H is the electronic Hamiltonian.\cite{HerzbergTeller1933, Petrov1985, Neddersen1989, Baranov1990}
+The $A$ term depends upon $\order{Q^0}$ transitions (i.e., Condon approximation), the $B$ term depends upon $\order{Q}$ transitions (Herzberg-Teller contributions), and the $C$ term depends on $\order{Q^2}$ transitions.
+The C term is suppressed in the following discussion as it depends on one and two photon forbidden transitions, making its contribution to $\gamma_{ijkl}$ two orders of magnitude lesser than $A_{ijk}$.
+\cite{Ziegler1988, Neddersen1989, Bonang1992}
+Note that some reports obtain $A, B$ coefficients through a Herzberg-Teller expansion of the electronic states to expose vibronic couplings via $\partial H / \partial Q$, where H is the electronic Hamiltonian.\cite{HerzbergTeller1933, Petrov1985, Neddersen1989, Baranov1990}
 This approach is not used here as the expansion of $\vec{M}^{ij}$ in normal mode coordinates provides sufficient physical insight into hyper-Raman selection rules.
@@
 These expressions are valid for both singly and doubly resonant HDFG, but based upon the resonance schemes, further simplifications can be made (\textit{vide infra}).
-\subsubsection{Singly Resonant HDFG}
-In the case of singly resonant HDFG, $\omega_3$ is also detuned from any resonance, which permits contraction over ${v'}$ as the dependence on $\ket{v'}$ in the resonance denominator can be neglected.
-This limit is usually reached when $\abs{\omega_{ev',g0} - (\omega_2 + \omega_3)} \gg 2\Gamma_{ev',g0}$.
-In such a limit, assuming a normal mode basis, we see for singly resonant HDFG that 
-\begin{subequations}
-\begin{equation}
-	A_{ijk} \sim \sum_{v'}\langle v | v' \rangle \langle v' | 0 \rangle = \delta_{v0} = 0
-\end{equation}
-\begin{equation}
-	B_{1_{ijk}} = \frac{1}{\hbar^2} \sum_{m,e,z} M^{ge}_{0,i} \left( 
-	\frac{\partial M^{em}_{j}}{\partial Q_z} M^{mg}_{0,k}
-	+M^{em}_{0,j} \frac{\partial M^{mg}_{k}}{\partial Q_z} \right) \frac{\mel{v}{Q_z}{0}}{\Delta_{e, g0}}
-\end{equation}
-\begin{equation}
-	B_{2_{ijk}} = \frac{1}{\hbar^2} \sum_{m,e,z} \frac{\partial M^{ge}_{i}}{\partial Q_z} M^{em}_{0,j} 
-	M^{mg}_{0,k}  
-	\frac{\mel{v}{Q_z}{0}}{\Delta_{e, g0}}
-\end{equation}
-\end{subequations}
-i.e., A$_{ijk}$ vanishes, but B$_{ijk}$ is non-zero, for singly resonant HDFG. 
-When $\abs{\omega_{ev',g0} - (\omega_2 + \omega_3)} \gtrsim \Gamma_{ev',g0}$, $\Re(\frac{1}{\Delta_{ev', g0}})$ can allow for small $A$ term contributions (cf.
-the long tail associated with the $A$ term of DR-HDFG as presented in \autoref{fig:doubres_spec}b).
-As such, $A$ usually only vanishes when $\omega_2, \omega_3$ are highly detuned from electronic states. 
-In the limit where $A$ vanishes, the singly resonant HDFG susceptibility can be approximated as $\chi^{(3)}_{IJKL} \sim \langle B_{ijk} \mu_l \rangle$, or, while a vibrational mode must be infrared active for HDFG output, vibronic activity is necessary for singly resonant HDFG response.
-The breakdown of the Condon approximation in singly resonant HDFG supports the relatively small HDFG $\chi^{(3)}$ values ($\sim$ order of magnitude larger than nonresonant background) for hexane and similar organic solvents.
-\cite{RN350, RN351, RN353}
 
-\subsubsection{Doubly Resonant HDFG}
-The selection rules for DR-HDFG are different. 
+The selection rules for DR-HDFG can be made clearer by small manipulations of \autoref{ABterms}. 
 DR-HDFG (where a vibrational and vibronic state are resonantly coupled) can provide a tool for measuring vibronic coupling, analogous to fully resonant DFG. \cite{Dick83_1, Shen94}
@@
 DR-HDFG provides methods to investigate vibronic coupling with only two laser pulses.
-Experimentally, DR-HDFG would provide identical information to DR-HSFG, but only DR-HDFG is phasematchable in media with normal indices of refraction, so we focus our attention on DR-HDFG.
-\cite{RN278}
-DR-HDFG output is dependent upon the $A,B$ terms prior to contraction over $\ket{v'}$ as written in \autoref{ABterms}.
+Experimentally, DR-HDFG would provide identical information to DR-HSFG, but only DR-HDFG is phasematchable in media with normal indices of refraction,\cite{RN278} so we focus our attention on DR-HDFG.
 
@@
 		It is assumed that $\omega_2 = \omega_3$.
-		Note that (b) shows magnitudes of the labeled quantities.
+		Note that (b) plots magnitudes of the labeled quantities.
 		The vibrational states on the $|g)$ and $|e)$ manifolds are spaced 2200 cm$^{-1}$ apart, with the vibronic states $\ket{e,v'}$ given linewidths of 700 cm$^{-1}$ and $\hbar \omega_{eg}$ = 30000 cm$^{-1}$.
 		Dotted lines in (b) denote the $v'$ = 0, 1, 2 vibronic resonances. 
-		The vibronic one and two photon absorption operators are scaled such that $\abs{B_j}/\abs{A} \sim$ 0.01}
+		The vibronic one and two photon absorption operators are scaled such that $\abs{B}/\abs{A} \sim$ 0.1, following Chung and Ziegler. \cite{Ziegler1988}}
 	\label{fig:doubres_spec}
@@
 \cite{Carlson1988thesis}
-Note that $q = m \sqrt{\omega/\hbar} Q$.
+Note that $q = \sqrt{\frac{m^2\omega}{\hbar}} Q$.
 The spectrum is simulated for an electronic state which is both one and two photon allowed.
-A simulated spectrum   (\autoref{fig:doubres_spec}b) highlighting the contributions of these terms on potential wells with $\xi = 0.5$ dissects the $A$ and $B$ contributions to the DR-SIVE spectrum.
-Note that unlike resonant hyper-Raman spectra, which allow transitions between different normal modes, the use of the infrared pulse provides a type of site selectivity,\cite{RN103} so that only the normal mode which $\omega_1$ pumps can be involved in the vibronic coupling analysis.
+A simulated spectrum   (\autoref{fig:doubres_spec}b) highlighting the contributions of these terms on potential wells with $\xi = 0.5$ dissects the $A$ and $B$ contributions to the DR-HDFG spectrum.
 This stimulated hyper-Raman type spectrum would be the expected result in a DR-HDFG experiment when investigating the vibronic structure of the electronic state coupled to $\ket{g,v}$.
@@
 There are two relevant regions of interest: the resonant region (2$\omega_2$ $\in$ [29000, 35000] cm$^{-1}$) and the non-resonant region.
-Focusing far away from the resonant region ($2\omega_2 \sim$ 20000 cm$^{-1}$), it is clear that $A$ term response is non-negligible. 
-As discussed above, the $A$ term in singly resonant HDFG vanishes when truly non-resonant.
-However, the simulated spectrum shows a non-negligible $A$ term contribution to DR-HDFG output well beyond $\sim$ 20000 cm$^{-1}$, the limit for this model system where $\abs{\omega_{ev',g0} - 2\omega_2} \gg 2\Gamma_{ev',g0}$.
-As such, it may be difficult to truly eliminate $A$ term resonances in HDFG spectra, even when largely detuned ($>$ 10000 cm$^{-1}$) from the electronic state.
+Focusing far away from the resonant region ($2\omega_2 \sim$ 20000 cm$^{-1}$), the nonresonant $A$ term response is roughly equivalent to that of the resonant $B$ term response. 
+Previous reports suggest that $A$ term contributions may become negligible when significantly detuned from a resonance such that $\Delta_{ev', g0} \approx \Delta_{eg}$, i.e., the resonance denominator loses $\ket{v'}$ dependence.
+\cite{Neddersen1989}
+The lack of $\ket{v'}$ dependence in the resonance denominator causes $A$ to vanish through closure ($A_{ijk} \sim \sum_{v'} \langle 1|v' \rangle \langle v'|0\rangle$ = $\delta_{10} = 0$).
+However, the simulated spectrum (\autoref{fig:doubres_spec}b) shows a non-negligible $A$ contribution to DR-HDFG output well beyond $\sim$ 20000 cm$^{-1}$, the limit for this model system where $\abs{\omega_{ev',g0} - 2\omega_2} \gg 2\Gamma_{ev',g0}$.
+As such, it is difficult to eliminate $A$ term resonances in HDFG spectra, even when largely detuned ($\gg 2\Gamma_{ev',g0}$) from the electronic state. 
+Similar ideas have been seen in spontaneous Raman scattering. \cite{Li1990, Gong2015}
+As such, it may prove difficult to examine non-Condon effects in DR-HDFG spectra of noncentrosymmetric systems.
 
@@
 In a realistic molecular system, where higher order contributions (e.g.
-Duschinsky coupling) effect vibronic coupling signatures, the spectral signatures will change to incorporate anharmonicites.
+Duschinsky coupling) affect vibronic coupling signatures, the spectral signatures will change to incorporate anharmonicites.
 \cite{Duschinsky1937, Carlson1990, Kundu2022}
-However, investigating coupling between $\ket{g,2v}$ and the same $\ket{e,v'}$ vibronic states will likely assist in dissecting the site-selective electronic spectra.
+Investigating coupling between $\ket{g,2v}$ and the same $\ket{e,v'}$ vibronic states will likely assist in dissecting the site-selective electronic spectra.
 
-\section{Quantitative Aspects of HDFG}\label{quant}
-HDFG is dependent upon a hyper-Raman transition, which is several orders of magnitude weaker than Raman transitions.\cite{RN515}
-As a result, it is useful to identify how HDFG output compares to a corresponding Raman based nonlinear spectroscopy.
-Since the hyper-Raman process is stimulated by a two-photon process, a setup using only one optical parametric amplifier can perform a coherent four wave mixing hyper-Raman experiment by investigating $-\vec{k}_1 + 2\vec{k}_2$ processes (i.e.
-two laser CMDS), assuming a two photon absorption from a single pulse stimulates the hyper-Raman process.
+\section{Applications of HDFG}\label{quant}
+\subsection{Site Selectivity}
+Unlike resonant hyper-Raman spectroscopy, which allows transitions between different normal modes of varying quanta, the infrared pulse in the HDFG provides a type of site selectivity,\cite{RN103, Carlson1991} so that only the mode pumped by $\omega_1$ can be involved in vibronic coupling.
+HDFG methods should be able to supplement older coherent Raman based methods as a method to investigate vibronic coupling mechanisms between a specific vibration on the ground state and vibrational states on an arbitrary excited state.\cite{RN103}
+The combined infrared and hyper-Raman properties of HDFG make it highly sensitive to molecular electronic structure.
+Particularly in the case of a centrosymmetric species, non-Condon effects dominate in the spectrum as the $A$ term vanishes from the presence of an inversion center.
+The site selective properties of HDFG can allow for parsing of non-Condon effects in different vibrational modes, and extend the use of CMDS to understand the electronic and vibronic structure of simple and complex species.
+
+The hybrid infrared / hyper-Raman properties of HDFG make it an intriguing analogue of resonance IR spectroscopy.
+First demonstrated by Boyle et al., resonance IR uses a $2\vec{k}_1 + \vec{k}_3$ pathway to amplify weak infrared modes through vibronic coupling, dependent upon the Raman $A,B$ coefficients.
+\cite{RN491}
+However, the $2\vec{k}_1 + \vec{k}_3$ resonance IR method implicitly depends upon the coupling of an overtone $\ket{g,2v}$ to vibronics $\ket{e,v'}$.
+Alternatively, DR-HDFG could provide similar enhancement as a form of resonance IR spectroscopy, but only requires coupling between $\ket{g,v}$ and $\ket{e,v'}$. 
+This form of resonance IR spectroscopy would also uniquely depend upon one and two-photon absorption components, as discussed in terms of the hyper-Raman $A,B$ coefficients.
+By combining resonance IR in the HDFG and $2\vec{k}_1 + \vec{k}_3$ geometries, the sensitivity of the Raman and hyper-Raman $A,B$ coefficients to ground state vibrations and electronic structure can be assessed.
+Such experiments can help assess the quality of computationally calculated ground and excited state potential energy surfaces.
+
+\subsection{Comparison to Sum Frequency Generation}
+Despite these attributes of HDFG, four wave mixing techniques are usually unfeasible for most laboratories, as they usually demand the use of multiple optical parametric amplifiers and/or complex acousto-optic modulators.
+\cite{RN245}
+Unlike most four wave mixing techniques, HDFG can be performed using only two input beams (i.e., two color HDFG).
+In the case of two color HDFG, only one tunable infrared optical parametric amplifier is needed, as the oscillator which pumps the infrared OPA can be used to perform the two-photon upconversion needed to generate HDFG output, i.e., $-\vec{k}_1 + 2\vec{k}_2$.
 A commonly used two laser CMDS method is vibrational sum frequency generation (vSFG), a $\chi^{(2)}$ technique whose phasematching is dictated by $\vec{k}_1 + \vec{k}_2$.
-SFG output scales as $\chi^{(2)}_{IJK} \sim \langle \alpha_{ij} \mu_k \rangle$, where $\alpha_{ij}$ is the Raman polarizability tensor.
-Both processes can be phasematched in media with normal indices of refraction, unlike the $\vec{k}_1 + 2\vec{k}_2$ HSFG process (\autoref{fig:comparisonwmel}).\cite{RN120}
+vSFG output scales as $\chi^{(2)}_{IJK} \sim \langle \alpha_{ij} \mu_k \rangle$, where $\alpha_{ij}$ is the Raman polarizability tensor.
+Laboratories which use vSFG to investigate interfacial species at buried interfaces thus have the ingredients necessary to perform a HDFG experiment in a transmission geometry. \cite{Piontek2023_1}
+This would allow vSFG practitioners to perform measurements in the bulk, such as measuring free induction decay, vibrational population lifetimes, and steady-state vibrational spectra through HDFG.
+
+Assessing the relative amplitudes of vSFG and HDFG is useful for demonstrating its feasibility as a nonlinear infrared spectroscopy. 
+Note that both vSFG and HDFG can be phasematched in media with normal indices of refraction, unlike the $\vec{k}_1 + 2\vec{k}_2$ HSFG process (\autoref{fig:comparisonwmel}).\cite{RN120}
 Macroscopically, oddness in spatial inversion of the vSFG polarization eliminates output from centrosymmetric species under the electric dipole approximation.\cite{RN132, RN133}
-As a result, the output of vSFG is significantly reduced relative to most third order spectroscopies because the output depends on surface number density, many orders of magnitude smaller than the bulk surface density.
-To motivate the application of HDFG spectroscopy, we perform a calculation to compare HDFG and vSFG output, where absorption effects are neglected for simplicity.
+As a result, vSFG output is significantly reduced relative to most third order spectroscopies because it depends on surface number density, many orders of magnitude smaller than the bulk surface density.
+However, hyper-Raman transitions are commonly several orders of magnitude weaker than corresponding Raman transitions.\cite{RN515}
+As a result, it is important to compare the relative output polarizations for both vSFG and HDFG taking into account the significant disparities in number densities and oscillator strengths.
 
+To motivate the application of HDFG spectroscopy in a vSFG type geometry, we perform a calculation to compare two-color HDFG and vSFG output, where absorption effects are neglected for simplicity.
 The output polarizations under the electric dipole approximation are written as
@@
 	\begin{subequations}
-	\begin{equation}
+	\begin{equation}\label{PSFG}
 		\abs{P^{(2)}_{\text{vSFG}}} = \frac{N_{surf}}{\ell} F(\omega_1+\omega_2) \abs{\langle \alpha_{ij}\mu_{k} \rangle E(\omega_2)E(\omega_1)} 
@@
 \end{widetext}
-where N$_{bulk}$ is the bulk number density, and N$_{surf}$ is the surface number density ($\sim$ 10$^{16}$ m$^{-2}$ for H$_2$O adsorbed at quartz).\cite{RN133, Du1994}	
-We assumed here that $\int_{0^-}^\ell \mathrm{d}z \langle \alpha_{ij}\mu_{k} \rangle \approx \ell \langle \alpha_{ij}\mu_{k} \rangle$, where $z$ is oriented along the surface normal and $0^{-}$ is the edge of the interface where substrate begins.
-\cite{RN133}
-We take the film thickness ($\ell$) that can be probed by vSFG to be 1 nm, much less than the vSFG coherence length.\cite{RN133, Su1998}
-For liquids with molar masses less than $\sim$100 g mol$^{-1}$ and densities roughly equal to that of H$_2$O$_{(l)}$ at room temperature, N$_{bulk} \sim$ 10$^{28}$ m$^{-3}$.
+where N$_{bulk}$ is the bulk number density ($\sim$ 10$^{28}$ m$^{-3}$ for H$_2$O$_{(l)}$ at room temperature), and N$_{surf}$ is the surface number density ($\sim$ 10$^{16}$ m$^{-2}$ for H$_2$O adsorbed at quartz).\cite{Du1994}
+For simplicity, we assume that $\chi^{(2)}$ is a spatial constant so that $\int_{0^-}^\ell \mathrm{d}z \langle \alpha_{ij}\mu_{k} \rangle \approx \ell \langle \alpha_{ij}\mu_{k} \rangle$, where $z$ is oriented along the surface normal and $0^{-}$ is the edge of the interface where substrate begins.
+\cite{Su1998}
+We take the film thickness ($\ell$) probed by vSFG to be 1 nm, much less than the vSFG coherence length.\cite{RN133}
 A normal dispersion curve is assumed so that $F(\omega_1+\omega_2) \approx F(2\omega_2-\omega_1)$.
@@
 Nevertheless, since HDFG produces a number of photons similar to that of vSFG, HDFG is a viable technique for investigating bulk systems.
+This method provides practitioners of sum frequency generation the ability to probe isotropic dephasing dynamics without many meaningful changes in their optical setup, and thus compare  dephasing in the bulk and at the interface.\cite{RN224}
 
-With the selection rules of HDFG understood for vibrational spectroscopy, and with HDFG generating a large enough output polarization, it becomes possible to extract quantitative information from its spectra.
+Transient HDFG spectroscopy, or pump-HDFG-probe, similar to transient vSFG spectroscopy (pump-vSFG-probe), can be implemented to learn about relaxation dynamics in isotropic systems.
+\cite{RN224, Bonn2024}
+A useful attribute of the $\beta_{ijk}$ dependence in HDFG output is added polarization control. 
+Similar to SFG experiments that probe different elements of the infrared transition dipole and Raman polarizability tensors, probing different elements of $\beta_{ijk}$ in HDFG can greatly assist in understanding ultrafast dynamics in isotropic systems, as suggested by Seliya et al.
+\cite{Shen90, RN224, Bonn2024}
+Polarization control in IR-pump-HDFG-probe, analogous to polarization control in pump-vSFG-probe, would be an interesting venue to assess the sensitivity of HDFG to different hyper-Raman tensor elements, and for practioners of transient vSFG to compare polarization specific dynamics at the interface and in the bulk.
+
+\subsection{Quantitative HDFG: Measuring the Hyper-Raman Hyperpolarizability}
+With the selection rules of HDFG understood for vibrational spectroscopy, and with HDFG generating a large enough output polarization, it becomes possible to obtain quantitative information from its spectra.
 Lineshape analysis is essential for extracting quantitative information from CMDS spectra.
@@
 \cite{RN362, RN418}
-Most quantitative methods in an n$^{th}$ order CMDS experiment are used to extract $\chi^{(n)}$ values to compare the relative strength of nonlinear processes in different media.
+Most quantitative methods in an n$^{th}$ order CMDS experiment are used to measure $\chi^{(n)}$ values to compare the relative strength of nonlinear processes in different media.
 \cite{Zhu87, RN351, RN345}
 The recorded $\chi^{(n)}$ values provide insight into how microscopic quantities ($\vec{\mu}, \alpha_{ij}, \beta_{ijk}$) impact nonlinear output.
-These quantities are usually extracted from their incoherent analogues (IR spectroscopy, spontaneous Raman spectroscopy, spontaneous hyper-Raman spectroscopy). \cite{Levenson1974_2, RN412, Shoute2005}
+These quantities are usually measured using their incoherent analogues (IR spectroscopy, spontaneous Raman spectroscopy, spontaneous hyper-Raman spectroscopy). \cite{Levenson1974_2, RN412, Shoute2005}
 
-Calculating $\beta_{ijk}$ values from hyper-Raman experiments is difficult and has only been performed for a few molecular vibrations. \cite{Xu1997, Shoute2005, Kelley2010}
+Compared to $\vec{\mu}$ and $\alpha_{ij}$, it is difficult to calculate $\beta_{ijk}$ values from spontaneous hyper-Raman experiments. \cite{Kelley2010}
+Only a few experimental determinations of $\beta_{ijk}$ for vibrational modes have been performed. \cite{Xu1997, Shoute2005, Kelley2010}
 Methods reported in the literature to measure absolute hyper-Raman polarizabilities depend upon external standards such as hyperpolarizabilities of dissolved samples or two-photon absorption cross sections, also difficult to measure.
@@
 \end{equation}
-\autoref{chi3} cannot be used as written to extract $\beta_{ijk}$, as $\beta_{ijk}$ is a Hermitian operator, but $\Delta_{gv} \in \mathbb{C}$. 
-However, since the real and imaginary components of $\chi^{(3)}$ can be measured through the Bloembergen interferometry experiment, and $\beta_{ijk}$ is present in either term, we can choose to focus on the real or imaginary part of $\chi^{(3)}$.
-When resonant, $\Re(\chi^{(3)})$ vanishes.
-As such, assuming resonance conditions, we investigate $\Im(\chi^{(3)})$, giving, 
-\begin{equation}
-	\langle \beta_{ijk} \mu_{l} \rangle = -\frac{4D \hbar \varepsilon_0}{NF} \Gamma_{gv} \frac{1}{\rho_{gg}} \Im(\chi^{(3)}_{IJKL})
-\end{equation}
+For simplicity, we take $\rho_{gg} = 1$.
 The steps behind orientational averaging of $\gamma_{ijkl}$, a rank four tensor in the molecular frame, are detailed elsewhere.\cite{Andrews1977, McDonnell2024}
@@
 Orientational averaging shows specific polarization schemes isolate linear combinations of different $\beta_{ijk}$ terms. \cite{Bersohn1966, Willetts1992, Kauranen1996}
-By using the expansions of $\beta_{ijk}$ and $\mu_{l}$ to $\order{Q_n}$ found earlier, we see
+By using the expansions of $\beta_{ijk}$ and $\mu_{l}$ to $\order{Q_n}$ found earlier, and knowing that $\Re(\chi^{(3)})$ vanishes when resonant, we see
 \begin{equation}\label{betasive}
-	\langle \frac{\partial \beta_{ijk}}{\partial Q_n} {\frac{\partial \mu_l}{\partial Q_n}} \rangle = -\frac{8D \varepsilon_0}{NF}  \frac{\Gamma_{gv} \omega_{vg}}{\rho_{gg}} {\Im(\chi^{(3)}_{IJKL})}
+	\langle \frac{\partial \beta_{ijk}}{\partial Q_n} {\frac{\partial \mu_l}{\partial Q_n}} \rangle = -\frac{8D \varepsilon_0}{NF}  {\Gamma_{gv} \omega_{vg}} {\Im(\chi^{(3)}_{IJKL})}
 \end{equation}
-Since $\abs{\mu}$, and by extension $\abs{\partial \mu / \partial Q}$, values can be extracted from FT-IR spectra, HDFG can give quantitative information on the magnitude of $\beta_{ijk}$ for infrared active vibrations.
-Additionally, by using two different input frequencies to stimulate the hyper-Raman transition, the asymmetric properties of $\beta_{ijk}$ can be examined and quantified.
+Since $\abs{\partial \mu / \partial Q}$ values can be extracted from FT-IR spectra, HDFG can give quantitative information on the magnitude of $\beta_{ijk}$ for infrared active vibrations.
+Additionally, by using non-degenerate input frequencies to stimulate the hyper-Raman transition, the asymmetric properties of $\beta_{ijk}$ can be examined and quantified.
 \cite{Christie1971, Denisov1986, Kozich2007}
@@
 These quantitative aspects of HDFG could prove useful to examine how well computational methods calculate $\beta_{ijk}$ values and the strength of spontaneous hyper-Raman scattering with non-degenerate pulses.
-
-\section{Mixed-Domain HDFG}\label{mixeddomain}
-The properties of steady state HDFG (complete pulse overlap) are useful for understanding the selection rules that drive HDFG output, motivating time domain experiments.
-Time domain HDFG could be a useful alternative technique for measuring single quantum coherence dephasing times.
-Working under the rotating wave approximation and neglecting spatial components, the output polarization is written in the time domain as 
-\begin{equation}
-	\begin{split}
-			\vec{P}(t) &= \int_0^\infty \mathrm{d}t_3 \int_0^\infty \mathrm{d}t_2 \int_0^\infty \mathrm{d}t_1 R^{(3)}(t_1, t_2, t_3)  \vdots \vec{E}_3(t-t_3) \\
-			&\vec{E}_2(t-t_3-t_2 - \tau_{23}) \vec{E}_1(t-t_3-t_2-t_1 - \tau_{13}) 
-	\end{split}
-\end{equation}
-where the electric fields are labeled according to their placement in the WMEL diagrams, $\tau_{ij} = \tau_i - \tau_j$ is the time delay between pulses $i$ and $j$, and R is the response function.
-\cite{RN287}
-Here, we will focus on the response function formalism for singly resonant HDFG, as the extension to doubly resonant HSFG, easily transferable to DR-HDFG, has been treated by Cho. \cite{Cho2001}
-The response function for the HDFG pathway illustrated in \autoref{fig:hdfg}a, assuming $\omega_2$ and $\omega_3$ are temporally overlapped, not electronically resonant, and $\rho(-\infty) = 1$, in the limit of homogeneous broadening is \cite{Cho2001, Meyer2004, RN367}
-\begin{equation}
-	R^{(3)}(t_1) = \frac{i}{\hbar} \beta_{ijk}(t_1) \mu_l(0) \exp(-i\Delta_{gv}t_1) \theta(t_1) 
-\end{equation}  
-where $\theta$ is the Heaviside function.
-The pure time-domain HDFG output reports on the dephasing characteristics of the $\ket{g}\bra{v}$ coherence. 
-This method provides practitioners of sum frequency generation the ability to probe isotropic dephasing dynamics without many meaningful changes in their optical setup, and thus compare $\ket{g}\bra{v}$ dephasing in the bulk and at the interface.\cite{RN224}
-
-Transient HDFG spectroscopy, or pump-HDFG-probe, similar to transient vSFG spectroscopy, can be implemented to learn about relaxation dynamics in isotropic systems. \cite{RN224, Bonn2024}
-A useful attribute of the $\beta_{ijk}$ dependence in HDFG output is added polarization control. 
-Similar to SFG experiments that probe different elements of the infrared transition dipole and Raman polarizability tensors, probing different elements of $\beta_{ijk}$ in HDFG can greatly assist in understanding ultrafast dynamics in isotropic systems, as suggested by Seliya et al.
-\cite{Shen90, RN224, Bonn2024}
-Polarization control in IR-pump-HDFG-probe, analogous to ultrafast transient absorption spectroscopy for vibrational modes, would be an interesting venue to assess the sensitivity of HDFG to different hyper-Raman tensor elements.
-
-It is well known that nonlinear wave mixing processes which share the same time ordering and output frequency will interfere. \cite{RN342, RN135}
-Understanding interfering pathways is useful because they can eliminate nonlinear output. 
-While we have only isolated one specific HDFG process so far, there are at least fourteen different WMELs which can provide HDFG output in the driven limit. \cite{RN352}
-If $\omega_2$ ($\omega_1$) becomes resonant (non-resonant), then other HDFG pathways appear (\autoref{fig:sivewmel2}).\cite{McDonnell2024} 
-While the methods in \autoref{fig:sivewmel2} possess identical selection rules to \autoref{fig:hdfg}, the WMEL diagrams presented in \autoref{fig:sivewmel2} will interfere, as they share the same phasematching condition but have oppositely signed amplitudes.
-\begin{figure}[!htbp]
-	\centering
-	\includegraphics[width=3.375in]{figures/timeorderedwmel.png}
-	\caption{WMEL diagrams of HDFG pathways in the  $\vec{k}_4 = -\vec{k}_1 + \vec{k}_2 + \vec{k}_3$ phasematching geometry when $\omega_2$ interacts with the system first. 
-		}
-	\label{fig:sivewmel2}
-\end{figure}
-
-The third order response functions for the pathways detailed in \autoref{fig:sivewmel2} when $\omega_1$ and $\omega_3$ are temporally overlapped, assuming $\rho(-\infty) = 1$, in the limit of homogeneous broadening are
-\begin{subequations}
-	\begin{equation} \label{mixing:a}
-		R^{(3)}_{a} (t_2) = R^{(3)}_{c} (t_2) = -\frac{i}{\hbar} \beta_{ijk}(t_2) \mu_l(0)  \exp(-i\Delta_{vg}t_2) \theta(t_2)
-	\end{equation}
-	\begin{equation}\label{mixing:b}
-			R^{(3)}_{b} (t_2) = R^{(3)}_{d} (t_2) = \frac{i}{\hbar} \beta_{ijk}(t_2) \mu_l(0)  \exp(-i\Delta_{vg}t_2) \theta(t_2)
-	\end{equation}
-\end{subequations}
-The total response function in this time ordering is therefore $R^{(3)}_\text{tot} (t_2) = R^{(3)}_{a} (t_2) + R^{(3)}_{b} (t_2) + R^{(3)}_{c} (t_2) + R^{(3)}_{d} (t_2) = 0$. 
-Since the total output response function vanishes in this time-ordering, the pathways in \autoref{fig:sivewmel2} perfectly destructively interfere.
-Therefore, to measure dynamics via HDFG, the time ordering shown in \autoref{fig:hdfg} should be used.
-These ideas have been seen experimentally in ultrafast DOVE work. \cite{RN367, McDonnell2024}
-In the case of the \autoref{fig:hdfg}a time ordering, there are no opportunities for interference from other third order processes. 
-However, a possible mechanism for interfering output in the \autoref{fig:hdfg}a pathway is a cascaded second order process (SFG, DFG). \cite{RN300}
-While unimportant in achiral isotropic systems,\cite{Belkin2000} second order cascades may become important in media where SFG and DFG are allowed, e.g.
-chiral media, interfaces or noncentrosymmetric media.
-
-Combinations of time and frequency domain spectroscopy, also called mixed domain spectroscopy, are useful ways to understand frequency-dependent dynamics. \cite{RN135, RN367, RN171, RN131}
-Mixed domain spectroscopy is a useful alternative to steady state spectroscopy as pulse separation can eliminate nonresonant background and isolate specific pulse ordering sequences.
-\cite{RN372, RN324, McDonnell2024}
-Isolating different pulse orderings can isolate pathway specific signal and minimize interference from unwanted pathways which share the same phasematching constraints. 
-Mixed domain HDFG can resolve frequency dependent free induction decay, which could prove useful for understanding isotropic dynamics of single quantum coherences. 
-Mixed domain resonant HDFG, using pathways similar to those in \autoref{fig:hdfg}b, could also measure time-dependent electronic-vibrational fluctuations, as discussed by Cho. \cite{Cho2001}
-These methods should be able to provide complimentary information to that found in 2D Electronic-Vibrational (2D-EV) spectroscopy. \cite{Dong2015, Lewis2015, Gaynor2017}
 
@@
 Through an examination of the hyper-Raman $A,B,C$ terms as they appear in the doubly resonant HDFG (DR-HDFG) output, the impact of vibronic coupling in DR-HDFG spectrum was examined.
-It is found that the $A$ term dominates in DR-HDFG, but vanishes in SR-HDFG and select cases (e.g. centrosymmetry) in DR-HDFG. 
-The non-Condon effects that are present in the absence of $A$ might prove useful for dissecting the structure of modes which involve particular IR active vibrations in vibronic coupling.
+The non-Condon effects that are present in the absence of $A$ might prove useful for resolving the electronic structure of centrosymmetric species.
+DR-HDFG possesses types of site-selective properties analogous to those of nanosecond coherent Raman experiments. 
+Site-selective properties should allow for a thorough analysis of vibronic coupling schemes in isotropic systems.
 Through a simple treatment, it is seen that HDFG and vibrational sum frequency generation (vSFG) have roughly the same output intensities. 

### 2024-07-25 figures/2D_spec.py

@@ -9,7 +9,7 @@ import WrightTools as wt
 import matplotlib.pyplot as plt 
 from matplotlib.patches import FancyArrowPatch
 
-# wt.artists.apply_rcparams(kind="publication")
+wt.artists.apply_rcparams(kind="publication")
 
 save = True
 
@@ -143,12 +143,12 @@ def Deltaevgo(v,x,l):
 #define numbers for AB terms
 Mge = 0.1 #M^eg_0
 Lge = 0.01 #Lambda^eg_0
-dLeg = 0.0008 #dLambda^eg / dQ
-dMgedQ = 0.008 #dM^eg / dQ
+dLeg = 0.0007 #dLambda^eg / dQ
+dMgedQ = 0.007 #dM^eg / dQ
 
 
 #define terms
-y = np.linspace(12500, 47500, 500000)
+y = np.linspace(10000, 50000, 1000000)
 
 
 A = Mge * Lge * (f10(d)*f00(d)*Deltaevgo(0,y,0) + f11(d)*f10(d)*Deltaevgo(1,y,1) + f12(d)*f20(d)*Deltaevgo(2,y,2)) #there must be a simpler way to do this but idk
@@ -187,14 +187,15 @@ abs_max = tot.max()
 ax1 = plt.subplot(gs[0,1])
 ax1.plot(y, tot / tot.max(), linewidth = '2', label = r'$\mathsf{|A + B|}$', color = 'black', zorder = 4)
 ax1.plot(y, np.abs(A) / abs_max, linewidth = '2', label = r'$\mathsf{|A|}$', color = 'cyan', zorder = 3)
+ax1.plot(y, np.abs(B1+B2) / abs_max, linewidth = '2', label = r'$\mathsf{|B|}$', color = 'red', zorder = 3)
 ax1.plot(y, np.abs(B1) / abs_max, linewidth = '2', label = r'$\mathsf{|B_1|}$', color = 'orange', zorder = 2)
 ax1.plot(y, np.abs(B2) / abs_max, linewidth = '2', label = r'$\mathsf{|B_2|}$', color = 'green', zorder = 1)
 ax1.set_ylabel(r'$\mathsf{Amplitude \ (norm.)}$', fontsize = fontsize)
 ax1.set_xlabel(r'$\mathsf{2\omega_2} \ (\mathsf{cm}^{-1})$', fontsize = fontsize)
 
 ax1.set_yscale('log')
[…]

### 2024-07-25 paper.tex
crude refactor
move some scattered statements to the intro

@@
 
+However, a possible mechanism for interfering output in the \autoref{fig:hdfg}a pathway is a cascaded second order process (SFG, DFG). \cite{RN301}
+While unimportant in achiral isotropic systems,\cite{Belkin2000} second order cascades may become important in media where SFG and DFG are allowed, e.g.
+chiral media, interfaces or noncentrosymmetric media.
+Nevertheless, in the discussion that follows for the rest of this manuscript, we will assume negligible second order cascades, and use the pathways drawn in \autoref{fig:hdfg} to examine HDFG  response.
+
 Inspired by recent work which demonstrated the presence of HDFG in ultrafast DOVE and terahertz-IR-visible (TIRV) experiments, we investigate the parameters which result in HDFG output.
@@
 This paper is organized as follows.
-In \autoref{steadystate}, we first identify the selection rules that drives singly HDFG through the Placzek approximation.
-Specific, non-zero time-orderings of singly resonant HDFG are identified through a simple analysis of the relevant response functions.
-The selection rules of doubly resonant HDFG (DR-HDFG) are identified through the hyper-Raman $A,B,C$ coefficients.
+In \autoref{steadystate}, we first identify the selection rules that drives HDFG through the Placzek approximation. 
+% Specific, non-zero time-orderings of singly resonant HDFG are identified through a simple analysis of the relevant response functions.
+The selection rules of doubly resonant HDFG (DR-HDFG) are identified through the Herzberg-Teller dipole expansion.
 After developing selection rules, the site selective properties and useful experimental aspects of HDFG are discussed in \autoref{quant}.
@@
 
+% DDK: compiling caveats/scope narrowing statements throughout the paper; to be refined
 Singly resonant hyper difference generation spectroscopy (HDFG) spectroscopy has potential to provide deeper insight into single quantum decoherence times and molecular orientation in condensed systems.
@@
 In this section, we investigate the steady state properties of HDFG and make the connections between HDFG and hyper-Raman scattering explicit.
+
+Experimentally, DR-HDFG would provide identical information to DR-HSFG, but only DR-HDFG is phasematchable in media with normal indices of refraction,\cite{RN278} so we focus our attention on DR-HDFG.
 
@@
 For a HDFG experiment using two (three) distinct input fields, D = 3 (6).
-
-\subsection{Placzek Method}
-We first investigate the HDFG selection rules through a Placzek type formalism.
-Contracting over the virtual states forms the hyper-Raman hyperpolarizability $\beta$.\cite{Long1970} 
-Assuming $\omega_2$, $\omega_3$ are significantly detuned from any resonance (\autoref{fig:comparisonwmel}),\cite{Placzek1934, Long1970, Altmann1982} \autoref{sivegamma} is written as 
-\begin{equation}\label{sivebeta}
-	\gamma_{ijkl}^{vg} =	-\frac{1}{\varepsilon_0} \frac{1}{4D \hbar}\frac{\beta^{vg}_{ijk} \mu^{gv}_{l}}{\Delta_{gv}} \rho_{gg}
-\end{equation}
-All infrared active transitions are hyper-Raman active, making HDFG allowed for any infrared active transition. \cite{Andrews1978}
-It is important to note that the symmetry properties of $\beta_{ijk}$ change dependent upon whether $\omega_2$ and $\omega_3$ are degenerate. \cite{Denisov1986, Kozich2007}
-Taylor expanding the dipole and first hyperpolarizability operators in terms of an n$^{\text{th}}$ reduced normal mode coordinate $Q_n$ to $\order{Q_n}$ about equilibrium as\cite{Long1970, Shen90}
-\begin{subequations}
-	\begin{equation}
-		\mu_l = \mu_{l,0} + \left(\frac{\partial \mu_l}{\partial Q_n}\right)_0 Q_n 
-	\end{equation}
-	\begin{equation}
-		\beta_{ijk} = \beta_{ijk,0} + \left(\frac{\partial \beta_{ijk}}{\partial Q_n}\right)_0 Q_n
-	\end{equation}
-\end{subequations}
-and substituting into \autoref{sivebeta} gives the HDFG hyperpolarizability to $\order{Q_n}$ as \begin{equation}\label{SIVEselection}
-	\gamma_{ijkl}^{vg} =	-\frac{1}{\varepsilon_0} \frac{1}{8D m_n \omega_{vg}}  \frac{1}{{\Delta_{gv}}} \ \left(\frac{\partial \beta^{vg}_{ijk}}{\partial Q_n}\right)_0 \left({\frac{\partial \mu^{gv}_{l}}{\partial Q_n}}\right)_0  \rho_{gg}
-\end{equation}
-where $\mel{v}{Q_n}{g} = \sqrt{\frac{\hbar}{2\omega_{vg}}}$ if $v-g = \pm 1$.  \cite{RN230}
-Since this expression is non-zero in the harmonic oscillator limit, HDFG output is allowed for harmonic transitions. 
-Similar to SFG, HDFG does not demand anharmonic ground state potential energy surfaces for spectral output. \cite{Shen94, Cho2000}
-This selection rule is generally valid for any HDFG or hyper sum frequency generation (HSFG) process in the $-\vec{k}_1 + \vec{k}_2  + \vec{k}_3$ and $\vec{k}_1 + \vec{k}_2  + \vec{k}_3$ phasematching geometries when $\omega_2$ and $\omega_3$ are sufficiently detuned from any resonance.
-
-\subsection{Importance of Time Ordering}
-With the general selection rule of HDFG identified through the Placzek approximation, it is useful to briefly discuss time-dependent HDFG before considering the properties of $\beta_{ijk}$ in more detail.
-In time-domain spectroscopy, the output is dependent upon the third order response function, $R^{(3)}$, a rank-four tensor (indices are suppressed for simplicity).
-Neglecting spatial components, the third order nonlinear output polarization is written in the time domain as \cite{RN287}
-\begin{equation}
-	\begin{split}
-		\vec{P}^{(3)}(t) &= \int_0^\infty \mathrm{d}t_3 \int_0^\infty \mathrm{d}t_2 \int_0^\infty \mathrm{d}t_1 \langle R^{(3)}(t_1, t_2, t_3) \rangle  \vdots \vec{E}_3(t-t_3) \\
-		&\vec{E}_2(t-t_3-t_2 - \tau_{23}) \vec{E}_1(t-t_3-t_2-t_1 - \tau_{13}) 
-	\end{split}
-\end{equation}
-where the electric fields are labeled according to their placement in the WMEL diagrams and $\tau_{ij} = \tau_i - \tau_j$ is the time delay between pulses $i$ and $j$.
-Here, we will focus on the response function formalism for singly resonant HDFG, as the extension to doubly resonant HSFG, easily transferable to DR-HDFG, has been treated by Cho. \cite{Cho2001}
-The response function for the HDFG pathway illustrated in \autoref{fig:comparisonwmel}, assuming $\omega_2$ and $\omega_3$ are temporally overlapped and $\rho(-\infty) = 1$, in the limit of homogeneous broadening is
-\begin{equation}
-	R^{(3)}(t_1) = -\frac{i}{\hbar} \beta_{ijk} \mu_l \exp(-i\Delta_{gv}t_1) \theta(t_1) 
-\end{equation}  
-where $\theta$ is the Heaviside function. \cite{Cho2001, RN135, Meyer2004, RN367}
-The pure time-domain HDFG output of the \autoref{fig:comparisonwmel} pathway reports on the dephasing characteristics of the $\ket{g}\bra{v}$ coherence. 
-Since HDFG is non-zero for any harmonically allowed infrared vibration, HDFG provides a method for measuring the free induction decay of vibrational modes without the need for anharmonicities.
 
@@
 In the case of the \autoref{fig:hdfg}a time ordering, assuming $\omega_2 > \omega_1$, there are no other resonant WMELs that can allow for interference from other third order processes. 
-However, a possible mechanism for interfering output in the \autoref{fig:hdfg}a pathway is a cascaded second order process (SFG, DFG). \cite{RN301}
-While unimportant in achiral isotropic systems,\cite{Belkin2000} second order cascades may become important in media where SFG and DFG are allowed, e.g.
-chiral media, interfaces or noncentrosymmetric media.
-Nevertheless, in the discussion that follows for the rest of this manuscript, we will assume negligible second order cascades, and use the pathways drawn in \autoref{fig:hdfg} to examine HDFG  response.
 \begin{figure}[!htbp]
@@
 
-\subsection{Expansion in terms of Hyper-Raman $A,B$ Parameters}
+\subsection{No Electronic Resonance}
+We first investigate the HDFG selection rules through a Placzek type formalism.
+Contracting over the virtual states forms the hyper-Raman hyperpolarizability $\beta$.\cite{Long1970} 
+Assuming $\omega_2$, $\omega_3$ are significantly detuned from any resonance (\autoref{fig:comparisonwmel}),\cite{Placzek1934, Long1970, Altmann1982} \autoref{sivegamma} is written as 
+\begin{equation}\label{sivebeta}
+	\gamma_{ijkl}^{vg} =	-\frac{1}{\varepsilon_0} \frac{1}{4D \hbar}\frac{\beta^{vg}_{ijk} \mu^{gv}_{l}}{\Delta_{gv}} \rho_{gg}
+\end{equation}
+All infrared active transitions are hyper-Raman active, making HDFG allowed for any infrared active transition. \cite{Andrews1978}
+It is important to note that the symmetry properties of $\beta_{ijk}$ change dependent upon whether $\omega_2$ and $\omega_3$ are degenerate. \cite{Denisov1986, Kozich2007}
+Taylor expanding the dipole and first hyperpolarizability operators in terms of an n$^{\text{th}}$ reduced normal mode coordinate $Q_n$ to $\order{Q_n}$ about equilibrium as\cite{Long1970, Shen90}
+\begin{subequations}
+	\begin{equation}
+		\mu_l = \mu_{l,0} + \left(\frac{\partial \mu_l}{\partial Q_n}\right)_0 Q_n 
+	\end{equation}
+	\begin{equation}
+		\beta_{ijk} = \beta_{ijk,0} + \left(\frac{\partial \beta_{ijk}}{\partial Q_n}\right)_0 Q_n
+	\end{equation}
+\end{subequations}
+and substituting into \autoref{sivebeta} gives the HDFG hyperpolarizability to $\order{Q_n}$ as \begin{equation}\label{SIVEselection}
+	\gamma_{ijkl}^{vg} =	-\frac{1}{\varepsilon_0} \frac{1}{8D m_n \omega_{vg}}  \frac{1}{{\Delta_{gv}}} \ \left(\frac{\partial \beta^{vg}_{ijk}}{\partial Q_n}\right)_0 \left({\frac{\partial \mu^{gv}_{l}}{\partial Q_n}}\right)_0  \rho_{gg}
+\end{equation}
+where $\mel{v}{Q_n}{g} = \sqrt{\frac{\hbar}{2\omega_{vg}}}$ if $v-g = \pm 1$.  \cite{RN230}
+Since this expression is non-zero in the harmonic oscillator limit, HDFG output is allowed for harmonic transitions. 
+Similar to SFG, HDFG does not demand anharmonic ground state potential energy surfaces for spectral output. \cite{Shen94, Cho2000}
+This selection rule is generally valid for any HDFG or hyper sum frequency generation (HSFG) process in the $-\vec{k}_1 + \vec{k}_2  + \vec{k}_3$ and $\vec{k}_1 + \vec{k}_2  + \vec{k}_3$ phasematching geometries when $\omega_2$ and $\omega_3$ are sufficiently detuned from any resonance.
+
+\subsection{Electronic resonance and pre-resonance}
 While Placzek type arguments provide the general source of HDFG output in the driven limit, it is insightful to interpret the origin of signal through the $A,B,C$ terms introduced by Chung and Ziegler, analogous to those found in Albrecht's treatment of Raman spectroscopy.\cite{Albrecht1961, Ziegler1988}
@@
 DR-HDFG provides methods to investigate vibronic coupling with only two laser pulses.
-Experimentally, DR-HDFG would provide identical information to DR-HSFG, but only DR-HDFG is phasematchable in media with normal indices of refraction,\cite{RN278} so we focus our attention on DR-HDFG.
 
@@
 \section{Applications of HDFG}\label{quant}
+% DDK: the problem is "applications" does not fit well into the story we have framed in the intro.  
+% DDK: what about "comparisons of HDFG with other spectroscopies"?
+% also, can some of these things really be called applications?  is site-selectivity an application?  is turning a v-SFG measurement into a HDFG measurement an application?
 \subsection{Site Selectivity}
 Unlike resonant hyper-Raman spectroscopy, which allows transitions between different normal modes of varying quanta, the infrared pulse in the HDFG provides a type of site selectivity,\cite{RN103, Carlson1991} so that only the mode pumped by $\omega_1$ can be involved in vibronic coupling.
+% DDK: I kind of understand this point...but a hyper-Raman spectrum would clearly select the vibrational mode based on the Raman shift, correct?
+%  good to note the benefits of this technique compared to hyper-Raman:
+% - a form of stimulated hyper-Raman (=stronger, directional signals)
+% - experiment takes place over a short time window, so pump-probe experiments are easily implemented
+% - laser scatter is easily avoided
+% - IR active, not 
 HDFG methods should be able to supplement older coherent Raman based methods as a method to investigate vibronic coupling mechanisms between a specific vibration on the ground state and vibrational states on an arbitrary excited state.\cite{RN103}
@@
 However, the $2\vec{k}_1 + \vec{k}_3$ resonance IR method implicitly depends upon the coupling of an overtone $\ket{g,2v}$ to vibronics $\ket{e,v'}$.
-Alternatively, DR-HDFG could provide similar enhancement as a form of resonance IR spectroscopy, but only requires coupling between $\ket{g,v}$ and $\ket{e,v'}$. 
+% DDK: did we not already discuss this?  Why is this not the introduction?
+Alternatively, DR-HDFG provides another form of resonance IR spectroscopy, but only requires coupling between $\ket{g,v}$ and $\ket{e,v'}$.
 This form of resonance IR spectroscopy would also uniquely depend upon one and two-photon absorption components, as discussed in terms of the hyper-Raman $A,B$ coefficients.
@@
 \subsection{Comparison to Sum Frequency Generation}
+% this whole argument is we only need two colors...why is there a whole section on this?
 Despite these attributes of HDFG, four wave mixing techniques are usually unfeasible for most laboratories, as they usually demand the use of multiple optical parametric amplifiers and/or complex acousto-optic modulators.
-\cite{RN245}
+\cite{RN245}  % I don't understand the citation, but also a citation is not necessary...
 Unlike most four wave mixing techniques, HDFG can be performed using only two input beams (i.e., two color HDFG).
@@
 As a result, vSFG output is significantly reduced relative to most third order spectroscopies because it depends on surface number density, many orders of magnitude smaller than the bulk surface density.
+% DDK: "weaker"?
 However, hyper-Raman transitions are commonly several orders of magnitude weaker than corresponding Raman transitions.\cite{RN515}
-As a result, it is important to compare the relative output polarizations for both vSFG and HDFG taking into account the significant disparities in number densities and oscillator strengths.
 
-To motivate the application of HDFG spectroscopy in a vSFG type geometry, we perform a calculation to compare two-color HDFG and vSFG output, where absorption effects are neglected for simplicity.
-The output polarizations under the electric dipole approximation are written as
-\begin{widetext}
-	\begin{subequations}
-	\begin{equation}\label{PSFG}
-		\abs{P^{(2)}_{\text{vSFG}}} = \frac{N_{surf}}{\ell} F(\omega_1+\omega_2) \abs{\langle \alpha_{ij}\mu_{k} \rangle E(\omega_2)E(\omega_1)} 
-	\end{equation}
-	\begin{equation}
-		\abs{P^{(3)}_{\text{HDFG}}} = N_{bulk}  F(2\omega_2-\omega_1) \abs{\langle \beta_{ijk} \mu_{l} \rangle E{(\omega_2)}E(\omega_2)E(-\omega_1)}
-	\end{equation}
-\end{subequations}
-\end{widetext}
-where N$_{bulk}$ is the bulk number density ($\sim$ 10$^{28}$ m$^{-3}$ for H$_2$O$_{(l)}$ at room temperature), and N$_{surf}$ is the surface number density ($\sim$ 10$^{16}$ m$^{-2}$ for H$_2$O adsorbed at quartz).\cite{Du1994}
-For simplicity, we assume that $\chi^{(2)}$ is a spatial constant so that $\int_{0^-}^\ell \mathrm{d}z \langle \alpha_{ij}\mu_{k} \rangle \approx \ell \langle \alpha_{ij}\mu_{k} \rangle$, where $z$ is oriented along the surface normal and $0^{-}$ is the edge of the interface where substrate begins.
+% As a result, it is important to compare the relative output polarizations for both vSFG and HDFG taking into account the significant disparities in number densities and oscillator strengths.
+
+% DDK: put this calculation in the SI; it's not really important.
+% To motivate the application of HDFG spectroscopy in a vSFG type geometry, we perform a calculation to compare two-color HDFG and vSFG output, where absorption effects are neglected for simplicity.
+% The output polarizations under the electric dipole approximation are written as
+% \begin{widetext}
+% 	\begin{subequations}
+% 	\begin{equation}\label{PSFG}
+% 		\abs{P^{(2)}_{\text{vSFG}}} = \frac{N_{surf}}{\ell} F(\omega_1+\omega_2) \abs{\langle \alpha_{ij}\mu_{k} \rangle E(\omega_2)E(\omega_1)} 
+% 	\end{equation}
+% 	\begin{equation}
+% 		\abs{P^{(3)}_{\text{HDFG}}} = N_{bulk}  F(2\omega_2-\omega_1) \abs{\langle \beta_{ijk} \mu_{l} \rangle E{(\omega_2)}E(\omega_2)E(-\omega_1)}
+% 	\end{equation}
+% \end{subequations}
+% \end{widetext}
+% where N$_{bulk}$ is the bulk number density ($\sim$ 10$^{28}$ m$^{-3}$ for H$_2$O$_{(l)}$ at room temperature), and N$_{surf}$ is the surface number density ($\sim$ 10$^{16}$ m$^{-2}$ for H$_2$O adsorbed at quartz).\cite{Du1994}
+% For simplicity, we assume that $\chi^{(2)}$ is a spatial constant so that $\int_{0^-}^\ell \mathrm{d}z \langle \alpha_{ij}\mu_{k} \rangle \approx \ell \langle \alpha_{ij}\mu_{k} \rangle$, where $z$ is oriented along the surface normal and $0^{-}$ is the edge of the interface where substrate begins.
 \cite{Su1998}
-We take the film thickness ($\ell$) probed by vSFG to be 1 nm, much less than the vSFG coherence length.\cite{RN133}
-A normal dispersion curve is assumed so that $F(\omega_1+\omega_2) \approx F(2\omega_2-\omega_1)$.
-To simplify analysis, orientational averaging is ignored (e.g., $\langle \beta_{ijk} \mu_{l} \rangle \approx \beta \mu$) and the input and output fields are taken to be co-polarized, so that
-\begin{equation}
-		P_{ratio} \equiv \frac{\abs{P^{(3)}_{\text{HDFG}}}}{\abs{P^{(2)}_{\text{vSFG}}}} \approx \frac{N_{bulk}}{N_{surf}} \frac{\beta}{\alpha} E(\omega_2) \ell \sim 10^3 \frac{\beta}{\alpha} E(\omega_2)\\
-\end{equation}
-Ziegler has noted that for a field with intensity 10 GW/cm$^{2}$, $\frac{\beta E}{\alpha} \sim 10^{-3} $ for vibrational modes when $E(\omega_2)$ is largely detuned from electronic resonances.
+% We take the film thickness ($\ell$) probed by vSFG to be 1 nm, much less than the vSFG coherence length.\cite{RN133}
+% A normal dispersion curve is assumed so that $F(\omega_1+\omega_2) \approx F(2\omega_2-\omega_1)$.
+% To simplify analysis, orientational averaging is ignored (e.g., $\langle \beta_{ijk} \mu_{l} \rangle \approx \beta \mu$) and the input and output fields are taken to be co-polarized, so that
+% \begin{equation}
+% 		P_{ratio} \equiv \frac{\abs{P^{(3)}_{\text{HDFG}}}}{\abs{P^{(2)}_{\text{vSFG}}}} \approx \frac{N_{bulk}}{N_{surf}} \frac{\beta}{\alpha} E(\omega_2) \ell \sim 10^3 \frac{\beta}{\alpha} E(\omega_2)\\
+% \end{equation}
+% Ziegler has noted that for a field with intensity 10 GW/cm$^{2}$, $\frac{\beta E}{\alpha} \sim 10^{-3} $ for vibrational modes when $E(\omega_2)$ is largely detuned from electronic resonances.
 \cite{RN515}
-Such an intensity is easily obtained using modern ultrafast sources.
-In this limit, $P_\text{ratio} \sim 1$.
-Since the intensity ratio scales as $\abs{P_{ratio}}^2$, we see that the HDFG output is roughly as strong as vSFG, assuming only interfacial contributions in vSFG.
-It is important to note that this calculation assumed negligible dipole and Raman polarizability dependence upon the distance from surface normal, ignored orientational averaging effects, and presumed equivalence of local field factors, all of which can significantly reduce output from either process.
-Nevertheless, since HDFG produces a number of photons similar to that of vSFG, HDFG is a viable technique for investigating bulk systems.
-This method provides practitioners of sum frequency generation the ability to probe isotropic dephasing dynamics without many meaningful changes in their optical setup, and thus compare  dephasing in the bulk and at the interface.\cite{RN224}
+% Such an intensity is easily obtained using modern ultrafast sources.
+% In this limit, $P_\text{ratio} \sim 1$.
+% Since the intensity ratio scales as $\abs{P_{ratio}}^2$, we see that the HDFG output is roughly as strong as vSFG, assuming only interfacial contributions in vSFG.
+% It is important to note that this calculation assumed negligible dipole and Raman polarizability dependence upon the distance from surface normal, ignored orientational averaging effects, and presumed equivalence of local field factors, all of which can significantly reduce output from either process.
+% Nevertheless, since HDFG produces a number of photons similar to that of vSFG, HDFG is a viable technique for investigating bulk systems.
+% This method provides practitioners of sum frequency generation the ability to probe isotropic dephasing dynamics without many meaningful changes in their optical setup, and thus compare  dephasing in the bulk and at the interface.\cite{RN224}
 

### 2024-07-26 paper.tex
reorganize abstract/intro
new wmel figure

@@
 Nonlinear, four wave mixing vibrational spectroscopies are often used to probe intramolecular vibrational coupling and relaxation dynamics in isotropic media.
-Three wave mixing vibrational spectroscopies, such as vibrational sum frequency generation (vSFG) are similarly used to probe the spectroscopy and dynamics of interfacial species.
-Most of these methods rely on infrared and/or Raman transitions to generate output. 
-Implementing a nonlinear spectroscopy involving hyper-Raman transitions, first appearing at third order perturbation theory, can provide a useful analogue to infrared and Raman based nonlinear spectroscopies to understand the spectroscopy and dynamics of isotropic systems.
-Hyper Difference Frequency Generation (Hyper-DFG, or HDFG) spectroscopy, also known as singly vibrationally enhanced spectroscopy (SIVE), is an underdeveloped, hyper-Raman based four wave mixing vibrational spectroscopy.
-Despite several experimental reports on HDFG, its spectroscopic properties have not been fully explored.
+% Three wave mixing vibrational spectroscopies, such as vibrational sum frequency generation (vSFG) are similarly used to probe the spectroscopy and dynamics of interfacial species.
+Most of these methods rely on infrared and/or Raman transitions, but methods involving hyper-Raman transitions are also possible. 
+% Implementing a nonlinear spectroscopy involving hyper-Raman transitions can provide a useful analogue to infrared and Raman based nonlinear spectroscopies to understand the spectroscopy and dynamics of isotropic systems.
+Hyper Difference Frequency Generation (Hyper-DFG, or HDFG) spectroscopy is an underdeveloped four wave mixing vibrational spectroscopy based on the hyper-Raman transition. 
+Despite several experimental reports on HDFG, its spectroscopic properties have not been fully explored.  % DDK: what aspects do we explore?
 To this end, we investigate the selection rules and behavior of HDFG spectroscopy.
-We explore the selection rules of singly and doubly resonant HDFG spectroscopy through a Placzek and vibronic picture and show HDFG is a hybrid IR-hyper-Raman technique.
-Since all infrared active modes have non-zero hyper-Raman activity, this makes HDFG a type of upconverted infrared spectroscopy.
-Through a simple comparison test, we demonstrate that HDFG output is shown to be similar in magnitude to vibrational sum frequency generation (vSFG) in a transmission geometry.
-Since HDFG can also be implemented as a two beam experiment in a geometry similar to vSFG, HDFG is a feasible third order spectroscopy for vSFG practitioners.
-Through a simple treatment of orientational averaging, HDFG provides a simple method to extract hyper-Raman hyperpolarizabilities ($\beta$) of infrared active vibrations.
-HDFG shows promise as a method to disentangle vibrational spectra and dynamics in isotropic systems without need for anharmonicities.
+% We explore the selection rules of singly and doubly resonant HDFG spectroscopy through a Placzek and vibronic picture and show HDFG is a hybrid IR-hyper-Raman technique.
+% Since all infrared active modes have non-zero hyper-Raman activity, this makes HDFG a type of upconverted infrared spectroscopy.
+% Through a simple comparison test, we demonstrate that HDFG output is shown to be similar in magnitude to vibrational sum frequency generation (vSFG) in a transmission geometry.
+% Since HDFG can also be implemented as a two beam experiment in a geometry similar to vSFG, HDFG is a feasible third order spectroscopy for vSFG practitioners.
+% Through a simple treatment of orientational averaging, HDFG provides a simple method to extract hyper-Raman hyperpolarizabilities ($\beta$) of infrared active vibrations.
+HDFG shows promise as a method to disentangle vibrational spectra and dynamics in isotropic systems.
 
@@
 \section{Introduction}
-Coherent multidimensional spectroscopy (CMDS) is a family of three and four wave mixing methods which form the optical analogue of multidimensional nuclear magnetic resonance (NMR) spectroscopy.\cite{Cho2008}
+Coherent multidimensional spectroscopy (CMDS) is a family of nonlinear spectroscopy methods that form the optical analogue of multidimensional nuclear magnetic resonance (NMR) spectroscopy.\cite{Cho2008}
 Multiresonant, four wave mixing CMDS experiments, first proposed by Oudar and Shen in 1980,\cite{RN307} directly probe coupling and correlations between different vibrational, electronic, and vibronic states.
 \cite{RN281, RN103, Cho2008}
-Four wave mixing CMDS has resolved anharmonicities, ultrafast dynamics, and other intramolecular couplings in numerous systems. \cite{Cho2008, Gaynor2017, Ziegler2018, Ogilvie2019, Bonn2021, RN325}
+Four wave mixing CMDS has resolved anharmonicities, ultrafast dynamics, and other inter- and intra-molecular couplings in numerous systems.
+\cite{Cho2008, Gaynor2017, Ziegler2018, Ogilvie2019, Bonn2021, RN325}
+% DDK: quickly get to vibrational spectroscopy and vibrational-electronic coupling
+To target vibrational and electronic coupling, common experiments make use of Raman transitions (DOVE, TSF, CARS, SRS, RISRS, and citations).
+Here we explore the less-utilized hyper-Raman transitions in CMDS four wave mixing spectroscopy.
 
-Not all CMDS methods are used to dissect intramolecular couplings.\cite{Shen1987_CPL}
-The most well known example of such a spectroscopy is vibrational sum frequency generation (vSFG), a three wave mixing technique used to probe vibrational structure and dynamics at interfaces.
+The hyper-Raman transition is the nonlinear, two photon analogue to the Raman transition.\cite{Terhune1965, Cyvin1965, Andrews1978}
+Two photons of frequency $\omega_a+\omega_b$ inelastically scatter with matter, promoting or demoting a vibrational mode of frequency $\omega_v$ and emitting a single photon of frequency $\omega_a + \omega_b \mp \omega_v$.
+The single photon emission is a significantly different frequency from the excitation frequencies, making rejection of excitation scatter much easier.
+Unlike Raman, all infrared active modes are hyper-Raman active, which allows infrared active modes to be probed through an inelastic scattering event. \cite{Andrews1978}
+One drawback is that hyper-Raman transitions are typically weak compared to their Raman counterparts, even when accounting for the high intensities available to ultrafast pulsed lasers.\cite{RN515, Kelley2010}
+CMDS methods partially mitigate this issue because emission is spatially coherent so that all emission is directional and easily collected.
+In fact, hyper-Raman transitions have been utilized in several CMDS studies.\cite{Zilian1994, RN350, RN416, RN351, RN352, RN353, Chen1998, RN362, RN418, Bonn2024, McDonnell2024,Wang2021}
+% Fully coherent, ultrafast probes of vibronic coupling would yield insight into processes that control ultrafast electronic relaxation in molecular and biological systems.
+\cite{Bredenbeck2015, Arsenault2021}
+% Cho has proposed a parametric, doubly resonant infrared/visible pathway to probe vibronic coupling in isotropic systems. \cite{Cho2001}
+% In this method, a single infrared pulse is resonant with a vibrational mode, and a two photon absorption event from a near infrared (NIR) or visible pulse resonant with an electronic or vibronic state is used to generate the four wave mixing signal.
+% The non-parametric pathways similar to this method are referred to herein as doubly resonant HDFG (DR-HDFG).
+% Methods analogous to DR-HDFG, where two photon absorption from the infrared pulse and one photon absorption from the visible pulse is used to generate output, i.e., stimulated Raman processes, have been reported.
+\cite{RN301, RN120}
+
+% Not all CMDS methods are used to dissect intramolecular couplings.\cite{Shen1987_CPL}
+% The most well known example of such a spectroscopy is vibrational sum frequency generation (vSFG), a three wave mixing technique used to probe vibrational structure and dynamics at interfaces.
 \cite{Shen1987_CPL, RN224}
-Non-parametric, hyper difference frequency generation (hyper-DFG, or HDFG) spectroscopy, similar to difference frequency generation (\autoref{fig:comparisonwmel}), is a four wave mixing method which, when detuned from  electronic resonances, does not probe intramolecular couplings.
-HDFG was one of the first infrared CMDS methods to successfully discriminate against non-resonant background.\cite{RN351, RN352}
-HDFG has also been referred to as singly vibrationally enhanced (SIVE) spectroscopy. \cite{RN352}
-In HDFG, an infrared pulse is resonant with a vibrational mode, and two other input pulses are used to stimulate a scattering process.
-HDFG was documented long ago to have characteristics similar to both infrared spectroscopy and spontaneous hyper-Raman scattering. \cite{RN352}
-Hyper-Raman scattering is the two photon analogue to Raman scattering. \cite{Terhune1965, Cyvin1965, Andrews1978}
-Hyper-Raman scattering cross sections are commonly several orders of magnitude smaller than Raman scattering cross sections, making hyper-Raman a difficult process to detect.\cite{RN515, Kelley2010} 
-However, unlike Raman spectroscopy, all infrared active modes are hyper-Raman active, which allows infrared active modes to be probed through an inelastic scattering event. \cite{Andrews1978}
-The different selection rules of hyper-Raman scattering make it a unique alternative to Raman scattering to understand vibrational spectra, electronic structure and vibronic coupling in molecular systems.
+Hyper-Raman difference frequency generation (HDFG) spectroscopy and hyper-Raman sum frequency generation (HSFG) spectroscopy are four wave mixing CMDS methods based on direct excitation of a vibrational mode through IR absorption and subsequent scattering to or from the vibrational mode through a hyper-Raman transition.
+In HDFG/HSFG, an infrared pulse is resonant with a vibrational mode, while two other excitations stimulate the hyper-Raman scattering process.
+The infrared excitation frequency selects the vibrational modes to be stimulated through the hyper-Raman transition.  
+The other two excitation frequencies control electronic enhancement for the scattering event.
+
+\autoref{fig:comparisonwmel} shows both HDFG and HSFG processes and compares it with related spectroscopies that investigate vibrational-electronic coupling.
+The three-wave mixing ($\chi^{(2)}$) techniques are often less applicable as they require non-centrosymmetry.
+Hyper-Raman scattering itself is a six-wave mixing ($\chi^{(5)}$) technique; stimulated hyper-Raman will be weak and susceptible to FWM cascades (CITE).
+Of the many four-wave mixing techniques, HDFG and HSFG have strong similarity to Raman, stimulated Raman, and RISRS in that the electronic state must remove or add a $v$ quantum to the ground state (``ev'' coupling).
+With the other four-wave mixing techniques (\autoref{fig:comparisonwmel}, second row), the output signal depends on more states than just the vibrational mode and the electronic state (``evx'' coupling).
+As a result, the relationship between the output and vibrational-electronic coupling is more detailed, but also more complicated.
+HDFG, HSFG and Raman are more direct probes of electronic-vibrational coupling.
+Notably, HDFG and HSFG can be implemented as 2-color experiments (with $\omega_2=\omega_3$); vSFG or vDFG setups can be trivially reconfigured to perform HSFG or HDFG measurements, respectively, to investigate bulk dynamics and spectroscopy.
+
+When the hyper-Raman excitation is resonant or near-resonant with electronic states, the brightness of the vibrational feature depends on the nature of the electronic state.
+The electronic spectrum can inform on processes that control ultrafast electronic relaxation in molecular and biological systems in similar ways to resonance Raman.\cite{Bredenbeck2015, Arsenault2021}
+Since the selection rules of hyper-Raman scattering differ from Raman scattering, the hyper-Raman excitation spectra give a unique alternative to Raman scattering to understand vibrational spectra, electronic structure and vibronic coupling in molecular systems.
 \cite{Olson2018}
-Several authors have proposed parametric six wave mixing techniques as the coherent analogue of hyper-Raman scattering. \cite{Berger1978, Cho1997, Cho1998}
-However, since most six wave mixing methods cascade into four wave mixing processes and their homodyned output would be dependent upon the hyper-Raman scattering cross section, \cite{RN243,Cho1997, Cho1998, Cho2000_Cascade} it is preferable to investigate four wave mixing analogues to hyper-Raman scattering.
 
+% An experimental complexity in executing Raman based four wave mixing experiments is the demand of three separate input pulses, often at different frequencies.
+% For example, in the case of DOVE, two of the three inputs must be tunable infrared pulses. \cite{RN345} 
+% Only recently have methods been developed for seamless tuning and scanning of ultrafast optical parametric amplifiers across swaths of frequency space. \cite{RN162, McDonnell2024}
+% Since HDFG demands only a single resonance to be scanned, the experiment can be performed using two input pulses: one tunable, infrared OPA to scan across vibrational resonances, and a two photon absorption from the signal process of a separate OPA, or output from the oscillator which pumps the infrared OPA.
+\cite{Wang2021}
+% As such, laboratories experienced in sum frequency generation (SFG) spectroscopy can perform HDFG spectroscopy to understand bulk dynamics and spectroscopy using nearly the same setup.
+
+% Cho has proposed a parametric, doubly resonant infrared/visible pathway to probe vibronic coupling in isotropic systems. \cite{Cho2001}
+% In this method, a single infrared pulse is resonant with a vibrational mode, and a two photon absorption event from a near infrared (NIR) or visible pulse resonant with an electronic or vibronic state is used to generate the four wave mixing signal.
+% The non-parametric pathways similar to this method are referred to herein as doubly resonant HDFG (DR-HDFG).
+% Methods analogous to DR-HDFG, where two photon absorption from the infrared pulse and one photon absorption from the visible pulse is used to generate output, i.e., stimulated Raman processes, have been reported.
+\cite{RN301, RN120}
+
+%  which, when detuned from  electronic resonances, does not probe intramolecular couplings. 
+% HDFG was one of the first infrared CMDS methods to successfully discriminate against non-resonant background.\cite{RN351, RN352}
+
+% Hyper-Raman scattering cross sections are commonly several orders of magnitude smaller than Raman scattering cross sections, making hyper-Raman a difficult process to detect.\cite{RN515, Kelley2010}
+% Several authors have proposed parametric six wave mixing techniques as the coherent analogue of hyper-Raman scattering. \cite{Berger1978, Cho1997, Cho1998}
+% However, since most six wave mixing methods cascade into four wave mixing processes and their homodyned output would be dependent upon the hyper-Raman scattering cross section, \cite{RN243,Cho1997, Cho1998, Cho2000_Cascade} it is preferable to investigate four wave mixing analogues to hyper-Raman scattering.
+
+% DDK: Quick placeholder caption.  Needs to be refined.
 \begin{figure*}[!htbp]
 	\centering
-	\includegraphics[width=6.66in]{comparisonwmel.png}
-	\caption{Wave Mixing Energy Level (WMEL) diagrams of difference frequency generation (DFG), sum frequency generation (SFG), spontaneous Raman scattering, hyper difference frequency generation (HDFG), hyper sum frequency generation (HSFG) and spontaneous hyper-Raman scattering relevant to this discussion.
-\cite{RN286}
+	\includegraphics[width=6.66in]{taxonomy.png}
+	\caption{
+		Spectroscopic methods for investigating vibrational-electronic coupling.
+		The interactions of light with matter are shown with Wave Mixing Energy Level (WMEL) diagrams.\cite{RN286}
 		Solid and dashed horizontal lines indicate real and virtual states, whereas solid and dotted arrows indicate ket and bra side transitions, respectively. 
@@
 
-While HDFG showed promise as an upconverted infrared spectroscopy method, it was quickly supplemented by a doubly vibrationally resonant method, doubly vibrationally enhanced (DOVE) spectroscopy, to investigate intra- and intermolecular vibrational coupling.
+% While HDFG showed promise as an upconverted infrared spectroscopy method, it was quickly supplemented by a doubly vibrationally resonant method, doubly vibrationally enhanced (DOVE) spectroscopy, to investigate intra- and intermolecular vibrational coupling.
 \cite{RN345, RN101, Cho2000}
-As a result, investigations of HDFG stagnated; to date, there are roughly a dozen studies which report on HDFG.
+% As a result, investigations of HDFG stagnated; to date, there are roughly a dozen studies which report on HDFG.
 \cite{Zilian1994, RN350, RN416, RN351, RN352, RN353, Chen1998, RN362, RN418, Bonn2024, McDonnell2024}
-Recent reports highlight non-negligible HDFG interference in DOVE experiments as well as the suitability of HDFG pathways to interpret ultrafast relaxation dynamics in isotropic systems.
+% Recent reports highlight non-negligible HDFG interference in DOVE experiments as well as the suitability of HDFG pathways to interpret ultrafast relaxation dynamics in isotropic systems.
 \cite{Bonn2024, McDonnell2024}
-These reports motivate deeper analysis of HDFG spectroscopy.
+% These reports motivate deeper analysis of HDFG spectroscopy.
 
-Fully coherent, ultrafast probes of vibronic coupling would yield insight into processes that control ultrafast electronic relaxation in molecular and biological systems.
-\cite{Bredenbeck2015, Arsenault2021}
-Cho has proposed a parametric, doubly resonant infrared/visible pathway to probe vibronic coupling in isotropic systems. \cite{Cho2001}
-In this method, a single infrared pulse is resonant with a vibrational mode, and a two photon absorption event from a near infrared (NIR) or visible pulse resonant with an electronic or vibronic state is used to generate the four wave mixing signal.
-The non-parametric pathways similar to this method are referred to herein as doubly resonant HDFG (DR-HDFG).
-Methods analogous to DR-HDFG, where two photon absorption from the infrared pulse and one photon absorption from the visible pulse is used to generate output, i.e., stimulated Raman processes, have been reported.
-\cite{RN301, RN120}
-
-An experimental complexity in executing Raman based four wave mixing experiments is the demand of three separate input pulses, often at different frequencies.
-For example, in the case of DOVE, two of the three inputs must be tunable infrared pulses. \cite{RN345} 
-Only recently have methods been developed for seamless tuning and scanning of ultrafast optical parametric amplifiers across swaths of frequency space. \cite{RN162, McDonnell2024}
-Since HDFG demands only a single resonance to be scanned, the experiment can be performed using two input pulses: one tunable, infrared OPA to scan across vibrational resonances, and a two photon absorption from the signal process of a separate OPA, or output from the oscillator which pumps the infrared OPA.
-\cite{Wang2021}
-As such, laboratories experienced in sum frequency generation (SFG) spectroscopy can perform HDFG spectroscopy to understand bulk dynamics and spectroscopy using nearly the same setup.
-
-However, a possible mechanism for interfering output in the \autoref{fig:hdfg}a pathway is a cascaded second order process (SFG, DFG). \cite{RN301}
-While unimportant in achiral isotropic systems,\cite{Belkin2000} second order cascades may become important in media where SFG and DFG are allowed, e.g.
-chiral media, interfaces or noncentrosymmetric media.
-Nevertheless, in the discussion that follows for the rest of this manuscript, we will assume negligible second order cascades, and use the pathways drawn in \autoref{fig:hdfg} to examine HDFG  response.
-
-Inspired by recent work which demonstrated the presence of HDFG in ultrafast DOVE and terahertz-IR-visible (TIRV) experiments, we investigate the parameters which result in HDFG output.
+Inspired by recent work that demonstrated the presence of HDFG in ultrafast DOVE and terahertz-IR-visible (TIRV) experiments, we investigate the parameters which result in HDFG output.
 \cite{Cho2000, Bonn2024, McDonnell2024}
 This paper is organized as follows.
-In \autoref{steadystate}, we first identify the selection rules that drives HDFG through the Placzek approximation. 
+In \autoref{steadystate}, we first identify the selection rules that drives HDFG in the absence of electronic resonance. 
 % Specific, non-zero time-orderings of singly resonant HDFG are identified through a simple analysis of the relevant response functions.
-The selection rules of doubly resonant HDFG (DR-HDFG) are identified through the Herzberg-Teller dipole expansion.
+The selection rules of electronically-resonant HDFG are then identified through the Herzberg-Teller dipole expansion.
+A simple harmonic oscillator model system is used to simulate HDFG spectra and illustrate how the excited state potential energy surface affects the hyper-Raman excitation spectrum.
 After developing selection rules, the site selective properties and useful experimental aspects of HDFG are discussed in \autoref{quant}.
-In particular, a comparison of vSFG and HDFG output is given, showing that HDFG and vSFG are roughly equally intense.
+% In particular, a comparison of vSFG and HDFG output is given, showing that HDFG and vSFG are roughly equally intense.
 A method to extract hyper-Raman hyperpolarizabilities ($\beta_{ijk}$) from HDFG spectra is identified and discussed.
@@
 
+Before presenting selection rules, we note that a possible mechanism for interfering output in the \autoref{fig:hdfg}a pathway is a cascaded second order process (SFG, DFG). \cite{RN301}
+While unimportant in achiral isotropic systems,\cite{Belkin2000} second order cascades may become important in media where SFG and DFG are allowed, e.g.
+chiral media, interfaces or noncentrosymmetric media.
+Nevertheless, in the discussion that follows for the rest of this manuscript, we will assume negligible second order cascades, and use the pathways drawn in \autoref{fig:hdfg} to examine HDFG response.
+
 \subsection{No Electronic Resonance}
+Assuming $\omega_2$, $\omega_3$ are significantly detuned from any resonance (\autoref{fig:comparisonwmel}),\cite{Placzek1934, Long1970, Altmann1982} \autoref{sivegamma} is written as 
+When there is no electronic resonance, HDFG has also been referred to as singly vibrationally enhanced (SIVE) spectroscopy. \cite{RN352}
 We first investigate the HDFG selection rules through a Placzek type formalism.
 Contracting over the virtual states forms the hyper-Raman hyperpolarizability $\beta$.\cite{Long1970} 
-Assuming $\omega_2$, $\omega_3$ are significantly detuned from any resonance (\autoref{fig:comparisonwmel}),\cite{Placzek1934, Long1970, Altmann1982} \autoref{sivegamma} is written as 
 \begin{equation}\label{sivebeta}
@@
 As a result, vSFG output is significantly reduced relative to most third order spectroscopies because it depends on surface number density, many orders of magnitude smaller than the bulk surface density.
-% DDK: "weaker"?
-However, hyper-Raman transitions are commonly several orders of magnitude weaker than corresponding Raman transitions.\cite{RN515}
+% DDK: we should clarify that these cross sections are weak even for non-linear cross-sections
+Hyper-Raman cross-sections are commonly several orders of magnitude weaker than corresponding Raman transitions.\cite{RN515}
 

### 2024-07-26 paper.tex
cleanup intro

@@
 % DDK: quickly get to vibrational spectroscopy and vibrational-electronic coupling
-To target vibrational and electronic coupling, common experiments make use of Raman transitions (DOVE, TSF, CARS, SRS, RISRS, and citations).
+To target vibrational and electronic coupling, methods commonly make use of Raman transitions (DOVE, TSF, CARS, SRS, RISRS, and citations).
 Here we explore the less-utilized hyper-Raman transitions in CMDS four wave mixing spectroscopy.
@@
 In fact, hyper-Raman transitions have been utilized in several CMDS studies.\cite{Zilian1994, RN350, RN416, RN351, RN352, RN353, Chen1998, RN362, RN418, Bonn2024, McDonnell2024,Wang2021}
-% Fully coherent, ultrafast probes of vibronic coupling would yield insight into processes that control ultrafast electronic relaxation in molecular and biological systems.
-\cite{Bredenbeck2015, Arsenault2021}
-% Cho has proposed a parametric, doubly resonant infrared/visible pathway to probe vibronic coupling in isotropic systems. \cite{Cho2001}
-% In this method, a single infrared pulse is resonant with a vibrational mode, and a two photon absorption event from a near infrared (NIR) or visible pulse resonant with an electronic or vibronic state is used to generate the four wave mixing signal.
-% The non-parametric pathways similar to this method are referred to herein as doubly resonant HDFG (DR-HDFG).
-% Methods analogous to DR-HDFG, where two photon absorption from the infrared pulse and one photon absorption from the visible pulse is used to generate output, i.e., stimulated Raman processes, have been reported.
-\cite{RN301, RN120}
 
-% Not all CMDS methods are used to dissect intramolecular couplings.\cite{Shen1987_CPL}
-% The most well known example of such a spectroscopy is vibrational sum frequency generation (vSFG), a three wave mixing technique used to probe vibrational structure and dynamics at interfaces.
-\cite{Shen1987_CPL, RN224}
 Hyper-Raman difference frequency generation (HDFG) spectroscopy and hyper-Raman sum frequency generation (HSFG) spectroscopy are four wave mixing CMDS methods based on direct excitation of a vibrational mode through IR absorption and subsequent scattering to or from the vibrational mode through a hyper-Raman transition.
@@
 HDFG, HSFG and Raman are more direct probes of electronic-vibrational coupling.
-Notably, HDFG and HSFG can be implemented as 2-color experiments (with $\omega_2=\omega_3$); vSFG or vDFG setups can be trivially reconfigured to perform HSFG or HDFG measurements, respectively, to investigate bulk dynamics and spectroscopy.
+Notably, HDFG and HSFG can be implemented as 2-color experiments (with $\omega_2=\omega_3$); vSFG or vDFG setups can be trivially reconfigured to perform HSFG or HDFG measurements, respectively, to investigate ev coupling in bulk systems.
 
@@
 \cite{Olson2018}
-
-% An experimental complexity in executing Raman based four wave mixing experiments is the demand of three separate input pulses, often at different frequencies.
-% For example, in the case of DOVE, two of the three inputs must be tunable infrared pulses. \cite{RN345} 
-% Only recently have methods been developed for seamless tuning and scanning of ultrafast optical parametric amplifiers across swaths of frequency space. \cite{RN162, McDonnell2024}
-% Since HDFG demands only a single resonance to be scanned, the experiment can be performed using two input pulses: one tunable, infrared OPA to scan across vibrational resonances, and a two photon absorption from the signal process of a separate OPA, or output from the oscillator which pumps the infrared OPA.
-\cite{Wang2021}
-% As such, laboratories experienced in sum frequency generation (SFG) spectroscopy can perform HDFG spectroscopy to understand bulk dynamics and spectroscopy using nearly the same setup.
-
-% Cho has proposed a parametric, doubly resonant infrared/visible pathway to probe vibronic coupling in isotropic systems. \cite{Cho2001}
-% In this method, a single infrared pulse is resonant with a vibrational mode, and a two photon absorption event from a near infrared (NIR) or visible pulse resonant with an electronic or vibronic state is used to generate the four wave mixing signal.
-% The non-parametric pathways similar to this method are referred to herein as doubly resonant HDFG (DR-HDFG).
-% Methods analogous to DR-HDFG, where two photon absorption from the infrared pulse and one photon absorption from the visible pulse is used to generate output, i.e., stimulated Raman processes, have been reported.
-\cite{RN301, RN120}
-
-%  which, when detuned from  electronic resonances, does not probe intramolecular couplings. 
-% HDFG was one of the first infrared CMDS methods to successfully discriminate against non-resonant background.\cite{RN351, RN352}
-
-% Hyper-Raman scattering cross sections are commonly several orders of magnitude smaller than Raman scattering cross sections, making hyper-Raman a difficult process to detect.\cite{RN515, Kelley2010}
-% Several authors have proposed parametric six wave mixing techniques as the coherent analogue of hyper-Raman scattering. \cite{Berger1978, Cho1997, Cho1998}
-% However, since most six wave mixing methods cascade into four wave mixing processes and their homodyned output would be dependent upon the hyper-Raman scattering cross section, \cite{RN243,Cho1997, Cho1998, Cho2000_Cascade} it is preferable to investigate four wave mixing analogues to hyper-Raman scattering.
 
@@
 
-% While HDFG showed promise as an upconverted infrared spectroscopy method, it was quickly supplemented by a doubly vibrationally resonant method, doubly vibrationally enhanced (DOVE) spectroscopy, to investigate intra- and intermolecular vibrational coupling.
-\cite{RN345, RN101, Cho2000}
-% As a result, investigations of HDFG stagnated; to date, there are roughly a dozen studies which report on HDFG.
-\cite{Zilian1994, RN350, RN416, RN351, RN352, RN353, Chen1998, RN362, RN418, Bonn2024, McDonnell2024}
-% Recent reports highlight non-negligible HDFG interference in DOVE experiments as well as the suitability of HDFG pathways to interpret ultrafast relaxation dynamics in isotropic systems.
-\cite{Bonn2024, McDonnell2024}
-% These reports motivate deeper analysis of HDFG spectroscopy.
-
 Inspired by recent work that demonstrated the presence of HDFG in ultrafast DOVE and terahertz-IR-visible (TIRV) experiments, we investigate the parameters which result in HDFG output.
@@
 In \autoref{steadystate}, we first identify the selection rules that drives HDFG in the absence of electronic resonance. 
-% Specific, non-zero time-orderings of singly resonant HDFG are identified through a simple analysis of the relevant response functions.
 The selection rules of electronically-resonant HDFG are then identified through the Herzberg-Teller dipole expansion.
+Not surprisingly, we find the selection rules are nearly identical to those of hyper-Raman scattering.
 A simple harmonic oscillator model system is used to simulate HDFG spectra and illustrate how the excited state potential energy surface affects the hyper-Raman excitation spectrum.
 After developing selection rules, the site selective properties and useful experimental aspects of HDFG are discussed in \autoref{quant}.
-% In particular, a comparison of vSFG and HDFG output is given, showing that HDFG and vSFG are roughly equally intense.
-A method to extract hyper-Raman hyperpolarizabilities ($\beta_{ijk}$) from HDFG spectra is identified and discussed.
+A new method for extracting hyper-Raman hyperpolarizabilities ($\beta_{ijk}$) from HDFG spectra is identified and discussed.
 

### 2024-07-27 paper.tex
partway through selection rules

@@
 % DDK: compiling caveats/scope narrowing statements throughout the paper; to be refined
-Singly resonant hyper difference generation spectroscopy (HDFG) spectroscopy has potential to provide deeper insight into single quantum decoherence times and molecular orientation in condensed systems.
-Similarities between HDFG spectroscopy, infrared spectroscopy and spontaneous hyper-Raman scattering have been noted previously. \cite{RN352, Bonn2024, McDonnell2024}
-In this section, we investigate the steady state properties of HDFG and make the connections between HDFG and hyper-Raman scattering explicit.
+% Singly resonant hyper difference generation spectroscopy (HDFG) spectroscopy has potential to provide deeper insight into single quantum decoherence times and molecular orientation in condensed systems.
+% Similarities between HDFG spectroscopy, infrared spectroscopy and spontaneous hyper-Raman scattering have been noted previously. \cite{RN352, Bonn2024, McDonnell2024}
+In this section, we investigate the properties of HDFG and make the connections between HDFG and hyper-Raman scattering explicit.
+HSFG will not be discussed, but the application of our treatment to HSFG is straightforward and the information content is similar.
+We note that HDFG emission can be phase-matched in media with normal dispersion,\cite{RN278} while HSFG cannot.
 
-Experimentally, DR-HDFG would provide identical information to DR-HSFG, but only DR-HDFG is phasematchable in media with normal indices of refraction,\cite{RN278} so we focus our attention on DR-HDFG.
+Before presenting selection rules, we note that a potential interferant in HDFG spectroscopy is a sequential cascade of second order DFG and SFG processes.\cite{RN301}
+While unimportant in achiral isotropic systems,\cite{Belkin2000} second order cascades may become important in media where SFG and DFG are allowed, e.g.
+chiral media, interfaces or noncentrosymmetric media.
+Nevertheless, in the discussion that follows for the rest of this manuscript, we will assume negligible second order cascades.
+% , and use the pathways drawn in \autoref{fig:hdfg} to examine HDFG response.
 
-It is useful to expose relationships between transition dipoles, Raman polarizabilities and hyper-Raman hyperpolarizabilities in the driven limit. \cite{Simpson2004}
-In the driven limit, under the electric dipole approximation, the I$^{th}$ component of the third order nonlinear output polarization, ${P}^{(3)}_I$, of a four wave mixing process, induced by electric fields E, at output frequency $\omega_4$ is written as (using Einstein summation) \cite{RN307}
+It is useful to expose relationships between transition dipoles and hyper-Raman hyperpolarizabilities in the driven limit. \cite{Simpson2004}
+Under the electric dipole approximation, the I$^{th}$ component of the third order nonlinear output polarization, ${P}^{(3)}_I$, of a four wave mixing process, induced by electric fields $E_J$, $E_K$, and $E_L$ at output frequency $\omega_4=-\omega_1 + \omega_2 + \omega_3$ is written as (using Einstein summation): \cite{RN307}
 \begin{equation} \label{polarization}
@@
 \end{equation}
-where N is a number density, F is the Lorentz local field factor, and $\gamma_{ijkl}$ is the third order polarizability (i.e., second hyperpolarizability). 
+where $N$ is a number density, $F$ is the Lorentz local field factor, and $\gamma_{ijkl}$ is the third order polarizability (i.e., second hyperpolarizability). 
 The brackets indicate an orientational (or rotational) average.\cite{Andrews1977}
-Uppercase letters refer to laboratory frame coordinates and lower case letters refer to molecular frame coordinates.
+Uppercase letters refer to laboratory frame coordinates and lower case letters refer to corresponding molecular frame coordinates.
 
-To make the connection between HDFG and hyper-Raman scattering, we investigate its gross selection rules.
+% To make the connection between HDFG and hyper-Raman scattering, we investigate its gross selection rules.
+% DDK: note that with the current placeholder figure, the state indices will have to be changed in our expressions for e.g. mu, Delta
 By propagating density matrix elements in the steady state limit under the rotating wave approximation, the HDFG hyperpolarizability is \cite{RN133}
@@
 \end{equation}
-where: $\mu^{ab}_{j}$ is the $j^{th}$ element of $\mel{a}{\vec{\mu}}{b}$, $\Delta_{kl} = \omega_{kl} - \omega_{j} - i\Gamma_{kl}$ (also known as a resonance denominator), $\omega_j$ is the frequency of the j$^{th}$ input field, $\Gamma_{kl}$ is the dephasing of $\rho_{kl}$ and $\rho_{gg}$ is the ground state population.
-D, the Maker-Terhune degeneracy factor, accounts for permutation symmetry in $\gamma_{ijkl}$.\cite{RN134} 
-For a HDFG experiment using two (three) distinct input fields, D = 3 (6).
+where: $\mu^{ab}_{j}$ is the $j^{th}$ element of $\mel{a}{\vec{\mu}}{b}$, $\Delta_{kl} = \omega_{kl} - \omega_{j} - i\Gamma_{kl}$, $\omega_j$ is the frequency of the j$^{th}$ input field, $\Gamma_{kl}$ is the dephasing of $\rho_{kl}$ and $\rho_{gg}$ is the ground state population.
+$D$, the Maker-Terhune degeneracy factor, accounts for permutation symmetry of the excitation fields.\cite{RN134} 
+For a HDFG experiment using two (three) distinct input fields, $D = 3 (6)$.
 
-It is well known that nonlinear wave mixing processes which share the same time ordering and output frequency will interfere. \cite{RN342, RN135}
-Understanding interfering pathways is useful because they can eliminate nonlinear output. 
-While we have only isolated one specific HDFG process so far, there are at least fourteen different WMELs which can provide HDFG output in the driven limit. \cite{RN352}
-If $\omega_2$ ($\omega_1$) becomes resonant (non-resonant), where $\omega_2 > \omega_1$, then other HDFG pathways appear (\autoref{fig:sivewmel2}).\cite{McDonnell2024} 
-While the methods in \autoref{fig:sivewmel2} possess identical selection rules to \autoref{fig:comparisonwmel}, the WMEL diagrams presented in \autoref{fig:sivewmel2} will interfere, as they share the same phasematching condition but have oppositely signed amplitudes.
-\begin{figure}[!htbp]
-	\centering
-	\includegraphics[width=3.375in]{figures/timeorderedwmel.png}
-	\caption{WMEL diagrams of HDFG pathways in the  $\vec{k}_4 = -\vec{k}_1 + \vec{k}_2 + \vec{k}_3$ phasematching geometry when $\omega_2$ interacts with the system first. 
-	}
-	\label{fig:sivewmel2}
-\end{figure}
-
-The third order response functions for the pathways detailed in \autoref{fig:sivewmel2} when $\omega_1$ and $\omega_3$ are temporally overlapped, assuming $\rho(-\infty) = 1$, in the limit of homogeneous broadening are
-\begin{subequations}
-	\begin{equation} \label{mixing:a}
-		R^{(3)}_{a} (t_2) = R^{(3)}_{c} (t_2) = -\frac{i}{\hbar} \beta_{ijk} \mu_l \exp(-i\Delta_{vg}t_2) \theta(t_2)
-	\end{equation}
-	\begin{equation}\label{mixing:b}
-		R^{(3)}_{b} (t_2) = R^{(3)}_{d} (t_2) = \frac{i}{\hbar} \beta_{ijk} \mu_l  \exp(-i\Delta_{vg}t_2) \theta(t_2)
-	\end{equation}
-\end{subequations}
-The total response function for \autoref{fig:sivewmel2} is therefore $R^{(3)}_\text{tot} (t_2) = R^{(3)}_{a} (t_2) + R^{(3)}_{b} (t_2) + R^{(3)}_{c} (t_2) + R^{(3)}_{d} (t_2) = 0$. 
-Since the total output response function vanishes in this time-ordering, the \autoref{fig:sivewmel2} pathways perfectly destructively interfere.
-Therefore, to measure dynamics via HDFG, the time ordering shown in \autoref{fig:hdfg} should be used.
-These ideas have been seen experimentally in ultrafast DOVE work. \cite{RN367, McDonnell2024}
-In the case of the \autoref{fig:hdfg}a time ordering, assuming $\omega_2 > \omega_1$, there are no other resonant WMELs that can allow for interference from other third order processes. 
-\begin{figure}[!htbp]
-	\centering
-	\includegraphics[width=3.375in]{hdfg.png}
-	\caption{WMEL diagrams of (a) singly resonant and (b) doubly resonant HDFG. 
-	}
-	\label{fig:hdfg}
-\end{figure}
-
-Before presenting selection rules, we note that a possible mechanism for interfering output in the \autoref{fig:hdfg}a pathway is a cascaded second order process (SFG, DFG). \cite{RN301}
-While unimportant in achiral isotropic systems,\cite{Belkin2000} second order cascades may become important in media where SFG and DFG are allowed, e.g.
-chiral media, interfaces or noncentrosymmetric media.
-Nevertheless, in the discussion that follows for the rest of this manuscript, we will assume negligible second order cascades, and use the pathways drawn in \autoref{fig:hdfg} to examine HDFG response.
-
-\subsection{No Electronic Resonance}
+\subsection{Electronically Non-resonant}
 Assuming $\omega_2$, $\omega_3$ are significantly detuned from any resonance (\autoref{fig:comparisonwmel}),\cite{Placzek1934, Long1970, Altmann1982} \autoref{sivegamma} is written as 
@@
 All infrared active transitions are hyper-Raman active, making HDFG allowed for any infrared active transition. \cite{Andrews1978}
-It is important to note that the symmetry properties of $\beta_{ijk}$ change dependent upon whether $\omega_2$ and $\omega_3$ are degenerate. \cite{Denisov1986, Kozich2007}
-Taylor expanding the dipole and first hyperpolarizability operators in terms of an n$^{\text{th}}$ reduced normal mode coordinate $Q_n$ to $\order{Q_n}$ about equilibrium as\cite{Long1970, Shen90}
+This selection rule is generally valid for any HDFG when $\omega_2$ and $\omega_3$ are sufficiently detuned from any resonance.
+% It is important to note that the symmetry properties of $\beta_{ijk}$ change dependent upon whether $\omega_2$ and $\omega_3$ are degenerate. \cite{Denisov1986, Kozich2007}  
+% DDK: not important, I think?  does this have any bearing on our analysis?
+
+The formula gets simpler when we consider IR excitation of a normal mode.  
+Assume $\omega_1$ is tune to the $n^{\text{th}}$ reduced normal mode.
+Taylor expanding the dipole and first hyperpolarizability operators in terms of an $n^{\text{th}}$ reduced normal mode coordinate $Q_n$ to $\order{Q_n}$ about equilibrium as\cite{Long1970, Shen90}
 \begin{subequations}
@@
 \end{equation}
-where $\mel{v}{Q_n}{g} = \sqrt{\frac{\hbar}{2\omega_{vg}}}$ if $v-g = \pm 1$.  \cite{RN230}
-Since this expression is non-zero in the harmonic oscillator limit, HDFG output is allowed for harmonic transitions. 
-Similar to SFG, HDFG does not demand anharmonic ground state potential energy surfaces for spectral output. \cite{Shen94, Cho2000}
-This selection rule is generally valid for any HDFG or hyper sum frequency generation (HSFG) process in the $-\vec{k}_1 + \vec{k}_2  + \vec{k}_3$ and $\vec{k}_1 + \vec{k}_2  + \vec{k}_3$ phasematching geometries when $\omega_2$ and $\omega_3$ are sufficiently detuned from any resonance.
+% DDK: do we call m_n the reduced mass, or the effective mass?
+where we have used $\mel{n}{Q_n}{g} = \sqrt{\frac{\hbar}{2m_n\omega_{ng}}}$, $m_n$ is the reduced mass of the normal mode and $\omega_{ng}$ is the characteristic frequency.\cite{RN230}
+Since this expression is non-zero in the harmonic oscillator limit, HDFG output is allowed for normal modes in the harmonic limit.
 
-\subsection{Electronic resonance and pre-resonance}
-While Placzek type arguments provide the general source of HDFG output in the driven limit, it is insightful to interpret the origin of signal through the $A,B,C$ terms introduced by Chung and Ziegler, analogous to those found in Albrecht's treatment of Raman spectroscopy.\cite{Albrecht1961, Ziegler1988}
-We write $\beta_{ijk}$ in \autoref{SIVEselection} using the hyper-Raman ABC formalism introduced by Chung and Ziegler to understand how vibronic coupling manipulates selection rules for singly and doubly resonant HDFG (\autoref{fig:hdfg}).
-\cite{Ziegler1988}
+% DDK: wait, this is a little different; we are considering w2 as resonant with a vibrational state; we have not considered that yet...
+% leaving this out for now
+% When electronically non-resonant, there are additional restrictions on the order of the excitation pulses.
+% Specifically, when pulse 2 or 3 interacts before pulse 1, and pulse 2 is resonant with a vibrational state, there is interference between competing pathways that is highly destructive.  
+% \autoref{fig:hdfg} illustrates the competing pathways; (a) and (b) ((c) and (d)) have the same pulse ordering, but in one pathway pulse 1 stimulates a ket-side transition and in the other a bra-side transition, which imparts a $\pi$ phase shift difference.(CITE)
+
+\subsection{Electronically resonant and pre-resonant}
+
+While Placzek treatment provides the general source of HDFG output, it does not predict the behavior of $\beta_{ijk}$ as $\omega_2 + \omega_3$ is changed.
+We now explicitly consider electronic resonances through the $A,B,C$ decomposition of $\beta$ introduced by Chung and Ziegler, analogous to those found in Albrecht's treatment of Raman spectroscopy.\cite{Albrecht1961, Ziegler1988}
 To employ this formalism, we write the states in a Born-Oppenheimer basis $\ket{a,b}$, where $\ket{a,b} = |a(Q)) \otimes \ket{b}$ for electronic states $\{|a(Q))\}$ and vibrational states $\{\ket{b}\}$ (i.e., adiabatic approximation).
@@
 The dependence of the electronic states on the adiabatic parameter $Q$ is suppressed for simplicity.
-The states are labeled as shown in \autoref{fig:hdfg}.
+% DDK: can label with fig:comparisonwmel if desired
+% The states are labeled as shown in \autoref{fig:hdfg}.
 For consistency with previous reports, we use $\vec{R}$ to denote electric transition dipole moments; $\vec{\mu}$ is reserved for transitions on the ground electronic state. \cite{Tang1970}
@@
 It is common in the hyper-Raman community to write $\Delta_{ev', mn} \Delta_{mn, g0} = \Delta_{ev', g0}$.
-Using our definition of vibronic states, we write $\vec{M}^{ab} = (a|\vec{M}|b)$ so that, for example,
+Using our definition of vibronic states, we can write, for example,
 $R_{i}^{gv,ev'} = \mel{v}{M_i^{ge}}{v'}$.
-Chung and Ziegler showed that expanding $\vec{M}^{ij}$ to $\order{Q}$ \textit{about the equilibrium point of the ground state potential surface} as
+Expanding $\vec{M}^{ij}$ to $\order{Q}$ about the equilibrium point of the ground state potential surface as
 $\vec{M}^{ij} = \vec{M}^{ij}_0 + \sum_z \frac{\partial\vec{M}^{ij}}{\partial Q_z} Q_z$
@@
 \end{equation}
-The $A$ term depends upon $\order{Q^0}$ transitions (i.e., Condon approximation), the $B$ term depends upon $\order{Q}$ transitions (Herzberg-Teller contributions), and the $C$ term depends on $\order{Q^2}$ transitions.
+The $A$ term contains the static transitions (i.e., Condon approximation), the $B$ term depends upon $\order{Q}$ transitions (Herzberg-Teller contributions), and the $C$ term depends on $\order{Q^2}$ transitions.
 The C term is suppressed in the following discussion as it depends on one and two photon forbidden transitions, making its contribution to $\gamma_{ijkl}$ two orders of magnitude lesser than $A_{ijk}$.
@@
 
-The selection rules for DR-HDFG can be made clearer by small manipulations of \autoref{ABterms}. 
-DR-HDFG (where a vibrational and vibronic state are resonantly coupled) can provide a tool for measuring vibronic coupling, analogous to fully resonant DFG. \cite{Dick83_1, Shen94}
-Many multi-resonant nonlinear spectroscopies have been developed to resolve vibronic coupling in molecular samples. \cite{Carlson1990, Gaynor2017, RN276}
-DR-HDFG provides methods to investigate vibronic coupling with only two laser pulses.
-
-Unlike a spontaneous hyper-Raman experiment, a DR-HDFG experiment selectively excites quanta in ground state vibrational modes (\autoref{fig:hdfg}), making it similar to a stimulated hyper-Raman experiment.
-As a result, the spectrum along the electronic scanning axis ($\omega_2 + \omega_3$) is significantly simplified as the coupling between the vibronic states are isolated to only $\ket{g,0}$ and $\ket{g,1}$, assuming the infrared pulse puts a single quantum in the normal mode of interest ($\ket{g,1}$).
-By working only in terms of a single normal mode (i.e.
-removing the sum over $z$) and assuming electronic transitions occur only between $|g), |e)$ and that $v =1$, $v' = \{0,1,2\}$, the A and B terms are rewritten as
+The selection rules for HDFG can be made clearer by small manipulations of \autoref{ABterms}. 
+%HDFG (where a vibrational and vibronic state are resonantly coupled) can provide a tool for measuring vibronic coupling, analogous to fully resonant DFG. \cite{Dick83_1, Shen94}
+% Many multi-resonant nonlinear spectroscopies have been developed to resolve vibronic coupling in molecular samples. \cite{Carlson1990, Gaynor2017, RN276}
+% HDFG provides methods to investigate vibronic coupling with only two laser pulses.
+% HDFG experiment selectively excites quanta in ground state vibrational modes, making it similar to a stimulated hyper-Raman experiment. 
+% As a result, the spectrum along the electronic scanning axis ($\omega_2 + \omega_3$) is significantly simplified as the coupling between the vibronic states are isolated to only $\ket{g,0}$ and $\ket{g,1}$, assuming the infrared pulse puts a single quantum in the normal mode of interest ($\ket{g,1}$).
+By working only in terms of a single normal mode (i.e. removing the sum over $z$ and $v=1$) and assuming electronic transitions occur only between $|g), |e)$, 
+% $v' = \{0,1,2\}$, 
+the A and B terms are rewritten as 
 	\begin{subequations}\label{ABterms_DR}

### 2024-07-27 paper.tex
Update paper.tex

@@
 
-\subsection{Electronically Non-resonant}
-Assuming $\omega_2$, $\omega_3$ are significantly detuned from any resonance (\autoref{fig:comparisonwmel}),\cite{Placzek1934, Long1970, Altmann1982} \autoref{sivegamma} is written as 
+% DDK: or should this be "Vibrational Selection Rules"?  Does Placzek == nonresonant?
+\subsection{Electronically Non-resonant: Vibrational Selection Rules}
+When $\omega_2+\omega_3$ is significantly detuned from resonance,\cite{Placzek1934, Long1970, Altmann1982} \autoref{sivegamma} 
+% DDK: broken thought here
 When there is no electronic resonance, HDFG has also been referred to as singly vibrationally enhanced (SIVE) spectroscopy. \cite{RN352}
 We first investigate the HDFG selection rules through a Placzek type formalism.
-Contracting over the virtual states forms the hyper-Raman hyperpolarizability $\beta$.\cite{Long1970} 
+Contracting over the virtual states forms the hyper-Raman hyperpolarizability $\beta$:\cite{Long1970} 
 \begin{equation}\label{sivebeta}
-	\gamma_{ijkl}^{vg} =	-\frac{1}{\varepsilon_0} \frac{1}{4D \hbar}\frac{\beta^{vg}_{ijk} \mu^{gv}_{l}}{\Delta_{gv}} \rho_{gg}
+	\gamma_{ijkl}^{vg} =	-\frac{1}{\varepsilon_0} \frac{1}{4D \hbar}\frac{\beta^{vg}_{ijk} \mu^{gv}_{l}}{\Delta_{gv}} \rho_{gg}.
 \end{equation}
@@
 The formula gets simpler when we consider IR excitation of a normal mode.  
-Assume $\omega_1$ is tune to the $n^{\text{th}}$ reduced normal mode.
-Taylor expanding the dipole and first hyperpolarizability operators in terms of an $n^{\text{th}}$ reduced normal mode coordinate $Q_n$ to $\order{Q_n}$ about equilibrium as\cite{Long1970, Shen90}
+Assume state $v$ is the $n^{\text{th}}$ reduced normal mode.
+We Taylor expand the dipole and first hyperpolarizability operators to first order in the reduced normal mode coordinate $Q_n$ about equilibrium:\cite{Long1970, Shen90}
 \begin{subequations}
@@
 \end{subequations}
-and substituting into \autoref{sivebeta} gives the HDFG hyperpolarizability to $\order{Q_n}$ as \begin{equation}\label{SIVEselection}
+Substituting into \autoref{sivebeta} gives the HDFG hyperpolarizability to $\order{Q_n}$ as \begin{equation}\label{SIVEselection}
 	\gamma_{ijkl}^{vg} =	-\frac{1}{\varepsilon_0} \frac{1}{8D m_n \omega_{vg}}  \frac{1}{{\Delta_{gv}}} \ \left(\frac{\partial \beta^{vg}_{ijk}}{\partial Q_n}\right)_0 \left({\frac{\partial \mu^{gv}_{l}}{\partial Q_n}}\right)_0  \rho_{gg}
@@
 % DDK: do we call m_n the reduced mass, or the effective mass?
-where we have used $\mel{n}{Q_n}{g} = \sqrt{\frac{\hbar}{2m_n\omega_{ng}}}$, $m_n$ is the reduced mass of the normal mode and $\omega_{ng}$ is the characteristic frequency.\cite{RN230}
+where we have used $\mel{v}{Q_n}{g} = \sqrt{\frac{\hbar}{2m_n\omega_{ng}}}$, $m_n$ is the reduced mass of the normal mode, and $\omega_{ng}$ is the characteristic frequency.\cite{RN230}
 Since this expression is non-zero in the harmonic oscillator limit, HDFG output is allowed for normal modes in the harmonic limit.
@@
 
-\subsection{Electronically resonant and pre-resonant}
+\subsection{Electronically resonant and pre-resonant: Vibronic Selection Rules}
+% TODO: note that the IR dipole selection rule persists here--this is all about w2+w3 resonance
 
-While Placzek treatment provides the general source of HDFG output, it does not predict the behavior of $\beta_{ijk}$ as $\omega_2 + \omega_3$ is changed.
+While the Placzek treatment provides the general source of HDFG output, it does not predict the behavior of $\beta_{ijk}$ as $\omega_2 + \omega_3$ is changed.
 We now explicitly consider electronic resonances through the $A,B,C$ decomposition of $\beta$ introduced by Chung and Ziegler, analogous to those found in Albrecht's treatment of Raman spectroscopy.\cite{Albrecht1961, Ziegler1988}
@@
 \cite{BornOppenheimer, Tang1970}
-The dependence of the electronic states on the adiabatic parameter $Q$ is suppressed for simplicity.
+We will henceforth suppress the dependence of the electronic states on $Q$ for simplicity.
 % DDK: can label with fig:comparisonwmel if desired
@@
 
-By contracting over the virtual vibrational states $\ket{n}$, the $A$ and $B$ coefficients, where $B = B_1 + B_2$, are written as
+% By contracting over the virtual vibrational states $\ket{n}$, 
+The $A$ and $B$ coefficients, where $B = B_1 + B_2$, are written as:
 \begin{widetext}
@@
 where terms such as $\langle a | b \rangle$ and $\mel{a}{Q}{b}$ are Franck-Condon factors and Herzberg-Teller-type integrals, respectively. 
-These expressions are valid for both singly and doubly resonant HDFG, but based upon the resonance schemes, further simplifications can be made (\textit{vide infra}).
+At this point, the expressions are valid for both electronically resonant and non-resonant cases.
 
-The selection rules for HDFG can be made clearer by small manipulations of \autoref{ABterms}. 
+For the case of electronic resonance, further simplifications can be made.
+We restrict consideration to electronic transitions between $|g)$ and $|e)$.  
+% The selection rules for HDFG can be made clearer by small manipulations of \autoref{ABterms}. 
 %HDFG (where a vibrational and vibronic state are resonantly coupled) can provide a tool for measuring vibronic coupling, analogous to fully resonant DFG. \cite{Dick83_1, Shen94}
@@
 % As a result, the spectrum along the electronic scanning axis ($\omega_2 + \omega_3$) is significantly simplified as the coupling between the vibronic states are isolated to only $\ket{g,0}$ and $\ket{g,1}$, assuming the infrared pulse puts a single quantum in the normal mode of interest ($\ket{g,1}$).
-By working only in terms of a single normal mode (i.e. removing the sum over $z$ and $v=1$) and assuming electronic transitions occur only between $|g), |e)$, 
+By working only in terms of a single normal mode (i.e. removing the sum over $z$ and $v=1$), 
 % $v' = \{0,1,2\}$, 
@@
 	\end{subequations}
-where the electronic two photon absorption operator, $\Lambda$ was invoked to simplify summation over virtual states. \cite{McClain1977}
-The constraint of $v' = \{0,1,2\}$ is done for simplicity.
+% DDK: give Lambda an explicit definition, rather than describing it?
+where $\Lambda^{eg}_{0,jk}$ is the electronic two photon transition moment between $g$ and $e$.\cite{McClain1977}
+$\Lambda$ contains the summation over $m$ in \autoref{ABterms}.
 
-The selection rules for DR-HDFG follow more clearly from \autoref{ABterms_DR}.
-It is clear from \autoref{ABterms_DR} that the Condon approximation breaks down for centrosymmetric molecules, as inversion centers invoke strict parity constraints that make states not accessible via both one and two photon transitions.
-\cite{Milojevich2013, RN230}
-This makes DR-HDFG a unique tool for studying the electronic structure of centrosymmetric species in isotropic media, as it is sensitive to non-Condon effects. \cite{Olson2018}
+\autoref{ABterms} shows the selection rules for the vibronic transitions.
+The $A$ term is allowed whenever an electronic transition has a one- and two- photon transition moment.
+The brightness is controlled by vibrational overlap (Franck-Condon factors).
+For centrosymmetric molecules, however, an electronic transition cannot be both one- and two- photon allowed, so the $A$ term will vanish.\cite{Milojevich2013, RN230}
+This makes HDFG a unique tool for studying the electronic structure of centrosymmetric species in isotropic media, as it is sensitive to non-Condon effects.\cite{Olson2018}
+In the absence of an $A$ term, the $B$ terms will dominate.
 The $B_1$ and $B_2$ terms involve different types of vibronic coupling pathways.
 In $B_1$, the Herzberg-Teller coupling is associated with the two-photon absorption process, whereas in $B_2$, the Herzberg-Teller coupling is associated with one-photon emission.
-As such, $B_1$ contributions to a DR-HDFG spectrum will be sensitive to vibronic coupling between the ground state of a mode and vibrational states on the $|e)$ surface. 
+As such, $B_1$ contributions to a HDFG spectrum will be sensitive to vibronic coupling between the ground state of a mode and vibrational states on the $|e)$ surface. 
 $B_2$ contributions are sensitive to vibronic coupling between the first excited state of a mode $\ket{g,1}$ and vibrational states on $|e)$.
@@
 	\includegraphics[width=6.66in]{drsive_spectrum.png}
-	\caption{Contributions of $A, B$ (\autoref{ABterms_DR}) to DR-HDFG spectrum for a simple two harmonic well system.
+	\caption{Contributions of $A, B$ (\autoref{ABterms_DR}) to HDFG spectrum for a simple two harmonic well system.
 		(a) Potential energy surfaces for a two-well system, (b) 1D HDFG spectrum for $\xi = 0.5$, $\omega_1 = \omega_{g1, g0}$. 
@@
 The spectrum is simulated for an electronic state which is both one and two photon allowed.
-A simulated spectrum   (\autoref{fig:doubres_spec}b) highlighting the contributions of these terms on potential wells with $\xi = 0.5$ dissects the $A$ and $B$ contributions to the DR-HDFG spectrum.
-This stimulated hyper-Raman type spectrum would be the expected result in a DR-HDFG experiment when investigating the vibronic structure of the electronic state coupled to $\ket{g,v}$.
+A simulated spectrum (\autoref{fig:doubres_spec}b) highlighting the contributions of these terms on potential wells with $\xi = 0.5$ dissects the $A$ and $B$ contributions to the HDFG spectrum.
+This stimulated hyper-Raman type spectrum would be the expected result in a HDFG experiment when investigating the vibronic structure of the electronic state coupled to $\ket{g,v}$.
 
-Simulating the DR-HDFG spectrum for the simple two-well system allows dissection of selection rules and spectral signatures without the need for complex couplings.
+Simulating the HDFG spectrum for the simple two-well system allows dissection of selection rules and spectral signatures without the need for complex couplings.
 There are two relevant regions of interest: the resonant region (2$\omega_2$ $\in$ [29000, 35000] cm$^{-1}$) and the non-resonant region.
@@
 The lack of $\ket{v'}$ dependence in the resonance denominator causes $A$ to vanish through closure ($A_{ijk} \sim \sum_{v'} \langle 1|v' \rangle \langle v'|0\rangle$ = $\delta_{10} = 0$).
-However, the simulated spectrum (\autoref{fig:doubres_spec}b) shows a non-negligible $A$ contribution to DR-HDFG output well beyond $\sim$ 20000 cm$^{-1}$, the limit for this model system where $\abs{\omega_{ev',g0} - 2\omega_2} \gg 2\Gamma_{ev',g0}$.
+However, the simulated spectrum (\autoref{fig:doubres_spec}b) shows a non-negligible $A$ contribution to HDFG output well beyond $\sim$ 20000 cm$^{-1}$, the limit for this model system where $\abs{\omega_{ev',g0} - 2\omega_2} \gg 2\Gamma_{ev',g0}$.
 As such, it is difficult to eliminate $A$ term resonances in HDFG spectra, even when largely detuned ($\gg 2\Gamma_{ev',g0}$) from the electronic state. 
 Similar ideas have been seen in spontaneous Raman scattering. \cite{Li1990, Gong2015}
-As such, it may prove difficult to examine non-Condon effects in DR-HDFG spectra of noncentrosymmetric systems.
+As such, it may prove difficult to examine non-Condon effects in HDFG spectra of noncentrosymmetric systems.
 
@@
 
-\section{Applications of HDFG}\label{quant}
-% DDK: the problem is "applications" does not fit well into the story we have framed in the intro.  
-% DDK: what about "comparisons of HDFG with other spectroscopies"?
-% also, can some of these things really be called applications?  is site-selectivity an application?  is turning a v-SFG measurement into a HDFG measurement an application?
+\section{Comparisons with other spectroscopies}\label{quant}
 \subsection{Site Selectivity}
@@
 % - IR active, not 
-HDFG methods should be able to supplement older coherent Raman based methods as a method to investigate vibronic coupling mechanisms between a specific vibration on the ground state and vibrational states on an arbitrary excited state.\cite{RN103}
+HDFG methods can supplement other coherent Raman based methods as a method to investigate vibronic coupling mechanisms between a specific vibration on the ground state and vibrational states on an arbitrary excited state.\cite{RN103}
 The combined infrared and hyper-Raman properties of HDFG make it highly sensitive to molecular electronic structure.
@@
 % DDK: did we not already discuss this?  Why is this not the introduction?
-Alternatively, DR-HDFG provides another form of resonance IR spectroscopy, but only requires coupling between $\ket{g,v}$ and $\ket{e,v'}$.
+Alternatively, HDFG provides another form of resonance IR spectroscopy, but only requires coupling between $\ket{g,v}$ and $\ket{e,v'}$.
 This form of resonance IR spectroscopy would also uniquely depend upon one and two-photon absorption components, as discussed in terms of the hyper-Raman $A,B$ coefficients.
@@
 \subsection{Comparison to Sum Frequency Generation}
-% this whole argument is we only need two colors...why is there a whole section on this?
+% this whole argument is we only need two colors...condense this
+% also note the intro covers this now
 Despite these attributes of HDFG, four wave mixing techniques are usually unfeasible for most laboratories, as they usually demand the use of multiple optical parametric amplifiers and/or complex acousto-optic modulators.
@@
 \begin{equation}\label{betasive}
-	\langle \frac{\partial \beta_{ijk}}{\partial Q_n} {\frac{\partial \mu_l}{\partial Q_n}} \rangle = -\frac{8D \varepsilon_0}{NF}  {\Gamma_{gv} \omega_{vg}} {\Im(\chi^{(3)}_{IJKL})}
+	\left\langle \frac{\partial \beta_{ijk}}{\partial Q_n} {\frac{\partial \mu_l}{\partial Q_n}} \right\rangle = -\frac{8D \varepsilon_0}{NF}  {\Gamma_{gv} \omega_{vg}} {\Im(\chi^{(3)}_{IJKL})}
 \end{equation}
@@
 We find that HDFG is always allowed for harmonic transitions, making it a potential tool for measuring single quantum coherence lifetimes. 
-Through an examination of the hyper-Raman $A,B,C$ terms as they appear in the doubly resonant HDFG (DR-HDFG) output, the impact of vibronic coupling in DR-HDFG spectrum was examined.
+Through an examination of the hyper-Raman $A,B,C$ terms, the impact of electronic resonance and vibronic coupling in HDFG spectrum was examined.
 The non-Condon effects that are present in the absence of $A$ might prove useful for resolving the electronic structure of centrosymmetric species.
-DR-HDFG possesses types of site-selective properties analogous to those of nanosecond coherent Raman experiments. 
+HDFG possesses types of site-selective properties analogous to those of nanosecond coherent Raman experiments. 
 Site-selective properties should allow for a thorough analysis of vibronic coupling schemes in isotropic systems.

### 2024-07-28 paper.tex
following up to ddk edits
Added new time ordering section w better figure (I hope)
Adjusted text based upon JCW and DDK edits
More on slow convergence of 1/w-w' as w->0
Attempted to clean other things up

@@
 Nonlinear, four wave mixing vibrational spectroscopies are often used to probe intramolecular vibrational coupling and relaxation dynamics in isotropic media.
-% Three wave mixing vibrational spectroscopies, such as vibrational sum frequency generation (vSFG) are similarly used to probe the spectroscopy and dynamics of interfacial species.
-Most of these methods rely on infrared and/or Raman transitions, but methods involving hyper-Raman transitions are also possible. 
-% Implementing a nonlinear spectroscopy involving hyper-Raman transitions can provide a useful analogue to infrared and Raman based nonlinear spectroscopies to understand the spectroscopy and dynamics of isotropic systems.
+Most of these methods rely on infrared and/or Raman transitions, such as sum-frequency generation (SFG) spectroscopy, but methods involving hyper-Raman transitions are also possible. 
+The additional number of tensor elements in the hyper-Raman hyperpolarizability have been useful for probing condensed phase media. 
+Implementing a nonlinear spectroscopy involving hyper-Raman transitions can provide a useful analogue to infrared and Raman based nonlinear spectroscopies to understand the spectroscopy and dynamics of isotropic systems.
 Hyper Difference Frequency Generation (Hyper-DFG, or HDFG) spectroscopy is an underdeveloped four wave mixing vibrational spectroscopy based on the hyper-Raman transition. 
-Despite several experimental reports on HDFG, its spectroscopic properties have not been fully explored.  % DDK: what aspects do we explore?
-To this end, we investigate the selection rules and behavior of HDFG spectroscopy.
-% We explore the selection rules of singly and doubly resonant HDFG spectroscopy through a Placzek and vibronic picture and show HDFG is a hybrid IR-hyper-Raman technique.
-% Since all infrared active modes have non-zero hyper-Raman activity, this makes HDFG a type of upconverted infrared spectroscopy.
-% Through a simple comparison test, we demonstrate that HDFG output is shown to be similar in magnitude to vibrational sum frequency generation (vSFG) in a transmission geometry.
-% Since HDFG can also be implemented as a two beam experiment in a geometry similar to vSFG, HDFG is a feasible third order spectroscopy for vSFG practitioners.
-% Through a simple treatment of orientational averaging, HDFG provides a simple method to extract hyper-Raman hyperpolarizabilities ($\beta$) of infrared active vibrations.
+Despite several experimental reports on HDFG, its spectroscopic properties have not been fully explored.  
+To this end, we investigate the selection rules and behavior of HDFG spectroscopy as an upconverted infrared spectroscopy and as a probe of vibronic coupling in molecular systems.
 HDFG shows promise as a method to disentangle vibrational spectra and dynamics in isotropic systems.
@@
 \cite{Cho2008, Gaynor2017, Ziegler2018, Ogilvie2019, Bonn2021, RN325}
-% DDK: quickly get to vibrational spectroscopy and vibrational-electronic coupling
-To target vibrational and electronic coupling, methods commonly make use of Raman transitions (DOVE, TSF, CARS, SRS, RISRS, and citations).
-Here we explore the less-utilized hyper-Raman transitions in CMDS four wave mixing spectroscopy.
+To target vibrational and electronic coupling, methods commonly make use of Raman transitions, e.g., doubly vibrationally enhanced spectroscopy (DOVE), triple sum frequency (TSF), coherent anti-Stokes Raman spectroscopy (CARS), resonant impulse stimulated Raman spectroscopy (RISRS).\cite{RN103, Dhar1994, RN345, Cho2000, RN491}
+Here we explore the less-utilized hyper-Raman transitions in four wave mixing CMDS.
+
+\begin{figure*}[!htbp]
+	\centering
+	\includegraphics[width=6.66in]{taxonomy.png}
+	\caption{
+		Some spectroscopic methods for investigating (top) electronic-vibrational coupling and (bottom) e-v-x (x: e, v, e-v, e-v-e) coupling through different order nonlinear processes.
+		Note that the coherent $\chi^{(5)}$ e-v-x processes are difficult to isolate due to $\chi^{(3)}$ cascades. 
+		The light-matter interacitons are depicted using Wave Mixing Energy Level (WMEL) diagrams.\cite{RN286}
+		Solid and dashed horizontal lines indicate real and virtual states, whereas solid and dotted arrows indicate ket and bra side transitions, respectively. 
+	}
+	\label{fig:comparisonwmel}
+\end{figure*}
 
@@
 CMDS methods partially mitigate this issue because emission is spatially coherent so that all emission is directional and easily collected.
-In fact, hyper-Raman transitions have been utilized in several CMDS studies.\cite{Zilian1994, RN350, RN416, RN351, RN352, RN353, Chen1998, RN362, RN418, Bonn2024, McDonnell2024,Wang2021}
+In fact, hyper-Raman transitions have been observed in several CMDS studies.\cite{Zilian1994, RN350, RN416, RN351, RN352, RN353, Chen1998, RN362, RN418, Wang2021, Bonn2024, McDonnell2024}
 
@@
 The infrared excitation frequency selects the vibrational modes to be stimulated through the hyper-Raman transition.
-The other two excitation frequencies control electronic enhancement for the scattering event.
+The other two excitation frequencies control electronic enhancement for the hyper-Raman scattering event.
 
-\autoref{fig:comparisonwmel} shows both HDFG and HSFG processes and compares it with related spectroscopies that investigate vibrational-electronic coupling.
-The three-wave mixing ($\chi^{(2)}$) techniques are often less applicable as they require non-centrosymmetry.
-Hyper-Raman scattering itself is a six-wave mixing ($\chi^{(5)}$) technique; stimulated hyper-Raman will be weak and susceptible to FWM cascades (CITE).
+\autoref{fig:comparisonwmel} shows both HDFG and HSFG processes and compares them with related spectroscopies that investigate vibrational-electronic coupling.
+The three-wave mixing ($\chi^{(2)}$) techniques are often less applicable as they require non-centrosymmetry.\cite{RN227}
+Hyper-Raman scattering itself is a six-wave mixing ($\chi^{(5)}$) technique; stimulated hyper-Raman will be weak and susceptible to FWM cascades.\cite{RN515, RN243, Cho2000_Cascade}
+A coherent six-wave mixing analogue of hyper-Raman scattering, coherent anti-Stokes hyper-Raman spectroscopy (CAHRS), has been proposed and explored theoretically by several authors; however, it is also highly susceptible to FWM cascades.\cite{Berger1978, Bjarnason1980, RN243, Cho1997, Cho1998, Cho2000_Cascade}
 Of the many four-wave mixing techniques, HDFG and HSFG have strong similarity to Raman, stimulated Raman, and RISRS in that the electronic state must remove or add a $v$ quantum to the ground state (``ev'' coupling).
-With the other four-wave mixing techniques (\autoref{fig:comparisonwmel}, second row), the output signal depends on more states than just the vibrational mode and the electronic state (``evx'' coupling).
+With the other four-wave mixing techniques (\autoref{fig:comparisonwmel}, second row), the output signal depends on more states than just a single vibrational mode and electronic state (``evx'' coupling).
 As a result, the relationship between the output and vibrational-electronic coupling is more detailed, but also more complicated.
 HDFG, HSFG and Raman are more direct probes of electronic-vibrational coupling.
-Notably, HDFG and HSFG can be implemented as 2-color experiments (with $\omega_2=\omega_3$); vSFG or vDFG setups can be trivially reconfigured to perform HSFG or HDFG measurements, respectively, to investigate ev coupling in bulk systems.
+Notably, HDFG and HSFG can be implemented as 2-color experiments (with $\omega_2=\omega_3$); vibrational sum frequency generation (vSFG) or difference frequency generation (vDFG) setups can be trivially reconfigured to perform HSFG or HDFG measurements, respectively, to investigate ev coupling in bulk systems.
 
@@
 
-% DDK: Quick placeholder caption.  Needs to be refined.
-\begin{figure*}[!htbp]
-	\centering
-	\includegraphics[width=6.66in]{taxonomy.png}
-	\caption{
-		Spectroscopic methods for investigating vibrational-electronic coupling.
-		The interactions of light with matter are shown with Wave Mixing Energy Level (WMEL) diagrams.\cite{RN286}
-		Solid and dashed horizontal lines indicate real and virtual states, whereas solid and dotted arrows indicate ket and bra side transitions, respectively. 
-	}
-	\label{fig:comparisonwmel}
-\end{figure*}
-
 Inspired by recent work that demonstrated the presence of HDFG in ultrafast DOVE and terahertz-IR-visible (TIRV) experiments, we investigate the parameters which result in HDFG output.
@@
 In \autoref{steadystate}, we first identify the selection rules that drives HDFG in the absence of electronic resonance. 
-The selection rules of electronically-resonant HDFG are then identified through the Herzberg-Teller dipole expansion.
-Not surprisingly, we find the selection rules are nearly identical to those of hyper-Raman scattering.
+The selection rules of electronically-resonant HDFG are then identified through a Herzberg-Teller dipole expansion.
+HDFG is found to be allowed in any harmonic system that has infrared active vibrations.
 A simple harmonic oscillator model system is used to simulate HDFG spectra and illustrate how the excited state potential energy surface affects the hyper-Raman excitation spectrum.
-After developing selection rules, the site selective properties and useful experimental aspects of HDFG are discussed in \autoref{quant}.
-A new method for extracting hyper-Raman hyperpolarizabilities ($\beta_{ijk}$) from HDFG spectra is identified and discussed.
+After developing selection rules, the site selective properties, useful experimental aspects of HDFG, and a new scheme to extract the hyper-Raman hyperpolarizability ($\beta_{ijk}$) from HDFG spectra are discussed in \autoref{quant}.
+The main findings are summarized in \autoref{conclusion}.
 
@@
 
-% DDK: compiling caveats/scope narrowing statements throughout the paper; to be refined
-% Singly resonant hyper difference generation spectroscopy (HDFG) spectroscopy has potential to provide deeper insight into single quantum decoherence times and molecular orientation in condensed systems.
-% Similarities between HDFG spectroscopy, infrared spectroscopy and spontaneous hyper-Raman scattering have been noted previously. \cite{RN352, Bonn2024, McDonnell2024}
 In this section, we investigate the properties of HDFG and make the connections between HDFG and hyper-Raman scattering explicit.
-HSFG will not be discussed, but the application of our treatment to HSFG is straightforward and the information content is similar.
-We note that HDFG emission can be phase-matched in media with normal dispersion,\cite{RN278} while HSFG cannot.
+HSFG will not be discussed, but the application of our treatment to HSFG is straightforward and the informational content is similar.
+We note that HDFG emission can be phase-matched in media with normal dispersion, while HSFG cannot.\cite{RN278}
 
-Before presenting selection rules, we note that a potential interferant in HDFG spectroscopy is a sequential cascade of second order DFG and SFG processes.\cite{RN301}
+Before presenting selection rules, we note that a potential interferant in HDFG spectroscopy are direct and sequential cascades of second order vDFG and vSFG processes.\cite{RN297, RN302, RN301}
 While unimportant in achiral isotropic systems,\cite{Belkin2000} second order cascades may become important in media where SFG and DFG are allowed, e.g.
@@
 Nevertheless, in the discussion that follows for the rest of this manuscript, we will assume negligible second order cascades.
-% , and use the pathways drawn in \autoref{fig:hdfg} to examine HDFG response.
 
 It is useful to expose relationships between transition dipoles and hyper-Raman hyperpolarizabilities in the driven limit. \cite{Simpson2004}
-Under the electric dipole approximation, the I$^{th}$ component of the third order nonlinear output polarization, ${P}^{(3)}_I$, of a four wave mixing process, induced by electric fields $E_J$, $E_K$, and $E_L$ at output frequency $\omega_4=-\omega_1 + \omega_2 + \omega_3$ is written as (using Einstein summation): \cite{RN307}
+Under the electric dipole approximation, the I$^{th}$ component of the third order nonlinear output polarization, ${P}^{(3)}_I$, of a four wave mixing process, induced by electric fields $E_J$, $E_K$, and $E_L$ at output frequency $\omega_4=-\omega_1 + \omega_2 + \omega_3$ is written as (using Einstein summation) \cite{RN307}
 \begin{equation} \label{polarization}
@@
 
-% To make the connection between HDFG and hyper-Raman scattering, we investigate its gross selection rules.
-% DDK: note that with the current placeholder figure, the state indices will have to be changed in our expressions for e.g. mu, Delta
 By propagating density matrix elements in the steady state limit under the rotating wave approximation, the HDFG hyperpolarizability is \cite{RN133}
 \begin{equation}\label{sivegamma}
-		\gamma_{ijkl}^{vg} =	- \sum_{m, n} \frac{1}{\varepsilon_0} \frac{1}{4D} \frac{1}{\hbar^3} \frac{\mu^{vn}_{i} \mu^{nm}_{j} \mu^{mg}_{k} \mu^{gv}_{l} }{\Delta_{nv} \Delta_{mv}\Delta_{gv}}  \rho_{gg}
+		\gamma_{ijkl}^{vg} =	- \sum_{e,m} \frac{1}{\varepsilon_0} \frac{1}{4D} \frac{1}{\hbar^3} \frac{\mu^{ve}_{i} \mu^{em}_{j} \mu^{mg}_{k} \mu^{gv}_{l} }{\Delta_{ev} \Delta_{mv}\Delta_{gv}}  \rho_{gg}
 \end{equation}
@@
 $D$, the Maker-Terhune degeneracy factor, accounts for permutation symmetry of the excitation fields.\cite{RN134} 
-For a HDFG experiment using two (three) distinct input fields, $D = 3 (6)$.
+For a HDFG experiment using two (three) distinct, non-degenerate input fields, $D = 3 (6)$.
 
 % DDK: or should this be "Vibrational Selection Rules"?  Does Placzek == nonresonant?
-\subsection{Electronically Non-resonant: Vibrational Selection Rules}
-When $\omega_2+\omega_3$ is significantly detuned from resonance,\cite{Placzek1934, Long1970, Altmann1982} \autoref{sivegamma} 
-% DDK: broken thought here
+\subsection{Vibrational Selection Rules}
+
 When there is no electronic resonance, HDFG has also been referred to as singly vibrationally enhanced (SIVE) spectroscopy. \cite{RN352}
+It is useful to investigate the selection rules without vibronic resonance to understand how HDFG can be used as an upconverted infrared spectroscopy.
 We first investigate the HDFG selection rules through a Placzek type formalism.
-Contracting over the virtual states forms the hyper-Raman hyperpolarizability $\beta$:\cite{Long1970} 
+When $\omega_2+\omega_3$ is significantly detuned from resonance and the vibronic nature of the virtual states is ignored, the Placzek approximation can be used to study selection rules in terms of the hyper-Raman hyperpolarizability, $\beta$.
+\cite{Placzek1934, Long1970, Altmann1982}
+Summing over the virtual states $\ket{e}$ and $\ket{m}$ forms the hyper-Raman hyperpolarizability so that\cite{Long1970} 
 \begin{equation}\label{sivebeta}
-	\gamma_{ijkl}^{vg} =	-\frac{1}{\varepsilon_0} \frac{1}{4D \hbar}\frac{\beta^{vg}_{ijk} \mu^{gv}_{l}}{\Delta_{gv}} \rho_{gg}.
+	\gamma_{ijkl} =	-\frac{1}{\varepsilon_0} \frac{1}{4D \hbar}\frac{\beta^{vg}_{ijk} \mu^{gv}_{l}}{\Delta_{gv}} \rho_{gg}.
 \end{equation}
-All infrared active transitions are hyper-Raman active, making HDFG allowed for any infrared active transition. \cite{Andrews1978}
-This selection rule is generally valid for any HDFG when $\omega_2$ and $\omega_3$ are sufficiently detuned from any resonance.
-% It is important to note that the symmetry properties of $\beta_{ijk}$ change dependent upon whether $\omega_2$ and $\omega_3$ are degenerate. \cite{Denisov1986, Kozich2007}  
-% DDK: not important, I think?  does this have any bearing on our analysis?
+Since all infrared active transitions are hyper-Raman active, HDFG is allowed for any infrared active transition. \cite{Andrews1978}
+This selection rule is generally valid for any HDFG or HSFG process when $\omega_2$ and $\omega_3$ are sufficiently detuned from any resonance.
 
-The formula gets simpler when we consider IR excitation of a normal mode.  
-Assume state $v$ is the $n^{\text{th}}$ reduced normal mode.
-We Taylor expand the dipole and first hyperpolarizability operators to first order in the reduced normal mode coordinate $Q_n$ about equilibrium:\cite{Long1970, Shen90}
+The general selection rule can be simplified by considering excitation of an infrared active normal mode.  
+Assume state $v$ is the $v^{\text{th}}$ normal mode.
+We Taylor expand the dipole and first hyperpolarizability operators to first order in the normal mode coordinate $Q_v$ about equilibrium:\cite{Long1970, Shen90}
 \begin{subequations}
 	\begin{equation}
-		\mu_l = \mu_{l,0} + \left(\frac{\partial \mu_l}{\partial Q_n}\right)_0 Q_n 
+		\mu_l = \mu_{l,0} + \left(\frac{\partial \mu_l}{\partial Q_v}\right)_0 Q_v 
 	\end{equation}
 	\begin{equation}
-		\beta_{ijk} = \beta_{ijk,0} + \left(\frac{\partial \beta_{ijk}}{\partial Q_n}\right)_0 Q_n
+		\beta_{ijk} = \beta_{ijk,0} + \left(\frac{\partial \beta_{ijk}}{\partial Q_v}\right)_0 Q_v
 	\end{equation}
@@
 Substituting into \autoref{sivebeta} gives the HDFG hyperpolarizability to $\order{Q_n}$ as \begin{equation}\label{SIVEselection}
-	\gamma_{ijkl}^{vg} =	-\frac{1}{\varepsilon_0} \frac{1}{8D m_n \omega_{vg}}  \frac{1}{{\Delta_{gv}}} \ \left(\frac{\partial \beta^{vg}_{ijk}}{\partial Q_n}\right)_0 \left({\frac{\partial \mu^{gv}_{l}}{\partial Q_n}}\right)_0  \rho_{gg}
+	\gamma_{ijkl} =	-\frac{1}{\varepsilon_0} \frac{1}{8D \omega_{vg}}  \frac{1}{{\Delta_{gv}}} \ \left(\frac{\partial \beta^{vg}_{ijk}}{\partial Q_v}\right)_0 \left({\frac{\partial \mu^{gv}_{l}}{\partial Q_v}}\right)_0  \rho_{gg}
 \end{equation}
-% DDK: do we call m_n the reduced mass, or the effective mass?
-where we have used $\mel{v}{Q_n}{g} = \sqrt{\frac{\hbar}{2m_n\omega_{ng}}}$, $m_n$ is the reduced mass of the normal mode, and $\omega_{ng}$ is the characteristic frequency.\cite{RN230}
+where we have used $\mel{v}{Q_v}{g} = \sqrt{\frac{\hbar}{2\omega_{vg}}}$ (in the limit $v-g = 1$) and $\omega_{vg}$ is the characteristic frequency.\cite{RN459}
 Since this expression is non-zero in the harmonic oscillator limit, HDFG output is allowed for normal modes in the harmonic limit.
 
-% DDK: wait, this is a little different; we are considering w2 as resonant with a vibrational state; we have not considered that yet...
-% leaving this out for now
-% When electronically non-resonant, there are additional restrictions on the order of the excitation pulses.
-% Specifically, when pulse 2 or 3 interacts before pulse 1, and pulse 2 is resonant with a vibrational state, there is interference between competing pathways that is highly destructive.  
-% \autoref{fig:hdfg} illustrates the competing pathways; (a) and (b) ((c) and (d)) have the same pulse ordering, but in one pathway pulse 1 stimulates a ket-side transition and in the other a bra-side transition, which imparts a $\pi$ phase shift difference.(CITE)
+\subsection{Time Ordering}
+It is useful to briefly discuss the impact of time ordering on HDFG output.
+Dependent upon the time-ordering schemes, it is possible to eliminate output through destructive interference.
+While we have only isolated one specific HDFG process (\autoref{fig:comparisonwmel}), there are at least fourteen different WMELs which can provide HDFG output in the driven limit. \cite{RN352}
+If $\omega_2$ ($\omega_1$) becomes resonant (non-resonant), where $\omega_2 > \omega_1$, then other HDFG pathways appear (\autoref{fig:sivewmel2}).\cite{McDonnell2024} 
+While the methods in \autoref{fig:sivewmel2} possess identical selection rules to \autoref{fig:comparisonwmel}, the WMEL diagrams presented in \autoref{fig:sivewmel2} will interfere, as they share the same phasematching condition but have oppositely signed amplitudes.
+\begin{figure*}[!htbp]
+	\centering
+	\includegraphics[width=6.66 in]{figures/timeorderedwmel.png}
+	\caption{WMEL diagrams of HDFG pathways for when (a,b) $\omega_1$ (black arrow) interacts first and (c-f) $\omega_2$ (orange arrow) interacts first. 
+		The states are labeled as $\ket{a,b}$, where $a$ refers to an electronic state and $b$ refers to quanta in a vibration on $a$.
+		In all cases, $\omega_2 > \omega_1$.
+	}
+	\label{fig:sivewmel2}
+\end{figure*}
+
+In the limit where $\omega_2+\omega_3$ are detuned from an electronic resonance, it becomes simple to interpret the interference schemes. 
+The case where $\omega_1$ is resonant and $\omega_2 + \omega_3$ are nonresonant yields two contributed diagrams, assuming $\omega_1$ interacts with the system first.
+These WMEL diagrams possess identical phase and transition moments, which yields total constructive interference.
+Conversely, diagrams (c,d) and (e,f), when detuned from an electronic resonance, have identical transition moments but opposite phase. 
+As a result, the output from (c,d) and (e,f) completely destructively interfere; no signal can be obtained from these pathways when significantly detuned. \cite{RN287, McDonnell2024}
+
+When $\omega_2 + \omega_3$ become electronically resonant, the interference changes for the \autoref{fig:sivewmel2}c-f pathways.
+Note that only pathways (c,e,f) possess identical transition moments.
+As a result, pathways (c,d) survive and can provide output when $\omega_2+\omega_3$ is resonant with an electronic state. 
+These results provide a simple rule of thumb for collecting HDFG spectra: use \autoref{fig:sivewmel2}a,b pathways to measure spectra when significantly detuned from an electronic resonance, and any pathway can measure spectra when electronically resonant.
+However, since electronic states commonly have short dephasing times and have significantly inhomogeneous broadening,\cite{Dong2015, Lewis2015} it is likely the \autoref{fig:sivewmel2}f pathway will become triply resonant and possibly contribute greater than the other pathways.
+Such instances are system dependent. 
+For consistency, discussion will be isolated to the \autoref{fig:sivewmel2}a pathway in the sections that follow.
 
@@
 We will henceforth suppress the dependence of the electronic states on $Q$ for simplicity.
-% DDK: can label with fig:comparisonwmel if desired
-% The states are labeled as shown in \autoref{fig:hdfg}.
+
 For consistency with previous reports, we use $\vec{R}$ to denote electric transition dipole moments; $\vec{\mu}$ is reserved for transitions on the ground electronic state. \cite{Tang1970}
-Following the approach which gave \autoref{sivegamma}, we find
+Following the approach which gave \autoref{sivegamma} and using the time ordering and state labeling of \autoref{fig:sivewmel2}a, we find
 \begin{equation}\label{drgamma_notaylor}
@@
 Using our definition of vibronic states, we can write, for example,
-$R_{i}^{gv,ev'} = \mel{v}{M_i^{ge}}{v'}$.
+$R_{i}^{gv,ev'} = \mel{v}{M_i^{ge}}{v'}$, where $\vec{M}_{ab} = (a|\vec{R}|b)$.\cite{Ziegler1974}
 Expanding $\vec{M}^{ij}$ to $\order{Q}$ about the equilibrium point of the ground state potential surface as
 $\vec{M}^{ij} = \vec{M}^{ij}_0 + \sum_z \frac{\partial\vec{M}^{ij}}{\partial Q_z} Q_z$
-yields $A, B, C$ coefficients similar to those in the Albrecht formalism of Raman scattering, \cite{Albrecht1961, Ziegler1988} so that
+yields $A, B, C$ coefficients similar to those in the Albrecht formalism of Raman scattering, \cite{Albrecht1961, Warshel1977, Ziegler1988} so that
 \begin{equation}
@@
 \end{equation}
-The $A$ term contains the static transitions (i.e., Condon approximation), the $B$ term depends upon $\order{Q}$ transitions (Herzberg-Teller contributions), and the $C$ term depends on $\order{Q^2}$ transitions.
+The $A$ term contains the static ($\order{Q^0}$) transitions (i.e., Condon approximation), the $B$ term depends upon $\order{Q}$ transitions (Herzberg-Teller contributions), and the $C$ term depends on $\order{Q^2}$ transitions.
 The C term is suppressed in the following discussion as it depends on one and two photon forbidden transitions, making its contribution to $\gamma_{ijkl}$ two orders of magnitude lesser than $A_{ijk}$.
@@
 We restrict consideration to electronic transitions between $|g)$ and $|e)$.  
-% The selection rules for HDFG can be made clearer by small manipulations of \autoref{ABterms}. 
-%HDFG (where a vibrational and vibronic state are resonantly coupled) can provide a tool for measuring vibronic coupling, analogous to fully resonant DFG. \cite{Dick83_1, Shen94}
-% Many multi-resonant nonlinear spectroscopies have been developed to resolve vibronic coupling in molecular samples. \cite{Carlson1990, Gaynor2017, RN276}
-% HDFG provides methods to investigate vibronic coupling with only two laser pulses.
-% HDFG experiment selectively excites quanta in ground state vibrational modes, making it similar to a stimulated hyper-Raman experiment. 
-% As a result, the spectrum along the electronic scanning axis ($\omega_2 + \omega_3$) is significantly simplified as the coupling between the vibronic states are isolated to only $\ket{g,0}$ and $\ket{g,1}$, assuming the infrared pulse puts a single quantum in the normal mode of interest ($\ket{g,1}$).
-By working only in terms of a single normal mode (i.e. removing the sum over $z$ and $v=1$), 
+Note that HDFG experiments selectively excite quanta in ground state vibrational modes. 
+By working only in terms of a single normal mode and assuming the infrared pulse selectively excites $\ket{g,0} \rightarrow \ket{g,1}$ (i.e., removing the sum over $z$ and taking $v=1$), 
 % $v' = \{0,1,2\}$, 
@@
 	\end{subequations}
-% DDK: give Lambda an explicit definition, rather than describing it?
 where $\Lambda^{eg}_{0,jk}$ is the electronic two photon transition moment between $g$ and $e$.\cite{McClain1977}
-$\Lambda$ contains the summation over $m$ in \autoref{ABterms}.
+$\Lambda$ contains the summation over $m$ in \autoref{ABterms} (N.B., here we use $\Lambda^{ab}_{ij} = 1/\hbar \sum_m M_i^{am}M_j^{mb} $).
 
-\autoref{ABterms} shows the selection rules for the vibronic transitions.
+\autoref{ABterms_DR} shows important selection rules for the vibronic transitions.
 The $A$ term is allowed whenever an electronic transition has a one- and two- photon transition moment.
@@
 A simulated spectrum (\autoref{fig:doubres_spec}b) highlighting the contributions of these terms on potential wells with $\xi = 0.5$ dissects the $A$ and $B$ contributions to the HDFG spectrum.
-This stimulated hyper-Raman type spectrum would be the expected result in a HDFG experiment when investigating the vibronic structure of the electronic state coupled to $\ket{g,v}$.
+This stimulated hyper-Raman type spectrum would be the expected result in a HDFG experiment when investigating the vibronic structure of the electronic state coupled to $\ket{g,1}$.
 
 Simulating the HDFG spectrum for the simple two-well system allows dissection of selection rules and spectral signatures without the need for complex couplings.
+The spectrum selectively probes coupling between the vibronic states and $\ket{g,0}$, $\ket{g,1}$.
 There are two relevant regions of interest: the resonant region (2$\omega_2$ $\in$ [29000, 35000] cm$^{-1}$) and the non-resonant region.
@@
 \cite{Neddersen1989}
-The lack of $\ket{v'}$ dependence in the resonance denominator causes $A$ to vanish through closure ($A_{ijk} \sim \sum_{v'} \langle 1|v' \rangle \langle v'|0\rangle$ = $\delta_{10} = 0$).
+The lack of $\ket{v'}$ dependence in the resonance denominator would cause $A$ to vanish through closure ($A_{ijk} \sim \sum_{v'} \langle 1|v' \rangle \langle v'|0\rangle$ = $\delta_{10} = 0$).
 However, the simulated spectrum (\autoref{fig:doubres_spec}b) shows a non-negligible $A$ contribution to HDFG output well beyond $\sim$ 20000 cm$^{-1}$, the limit for this model system where $\abs{\omega_{ev',g0} - 2\omega_2} \gg 2\Gamma_{ev',g0}$.
+In other words, it appears difficult to escape the pre-resonance regime of hyper-Raman scattering.
 As such, it is difficult to eliminate $A$ term resonances in HDFG spectra, even when largely detuned ($\gg 2\Gamma_{ev',g0}$) from the electronic state. 
-Similar ideas have been seen in spontaneous Raman scattering. \cite{Li1990, Gong2015}
-As such, it may prove difficult to examine non-Condon effects in HDFG spectra of noncentrosymmetric systems.
+This is not unexpected, as when $\abs{\omega_{ev',g0} - 2\omega_2} \gg 2\Gamma_{ev',g0}$, $A_{ijk} \sim \left(2\omega_2 - \omega_{ev',g0}\right)^{-1}$, which slowly converges as $\omega_2 \rightarrow 0$.
+Similar ideas have been seen in spontaneous Raman scattering. \cite{Warshel1977, Li1990, Gong2015}
+As such, it may prove difficult to examine non-Condon effects ($B$ term contributions) in HDFG spectra of noncentrosymmetric systems.
 
@@
 Unlike $A$ term contributions, the $B_1$ and $B_2$ terms are dependent upon both Franck-Condon and Herzberg-Teller contributions.
-Based upon the disparity in transition amplitudes in the $B_1$ and $B_2$ terms for each vibronic transition, it is clear that the $B$ terms are sensitive to the Herzberg-Teller coupling integrals.
 The $B_1$ term, whose vibronic coupling term is involved in the two-photon absorption event from $|g)$ to $|e)$, seemingly has minimal $0-0$ contributions. 
@@
 In a realistic molecular system, where higher order contributions (e.g.
-Duschinsky coupling) affect vibronic coupling signatures, the spectral signatures will change to incorporate anharmonicites.
+Duschinsky rotation) affect vibronic coupling signatures, the spectral signatures will change to incorporate anharmonicites.
 \cite{Duschinsky1937, Carlson1990, Kundu2022}
-Investigating coupling between $\ket{g,2v}$ and the same $\ket{e,v'}$ vibronic states will likely assist in dissecting the site-selective electronic spectra.
+Investigating coupling between $\ket{g,2}$ and the same $\ket{e,v'}$ vibronic states will likely assist in dissecting the site-selective electronic spectra.
 
-\section{Comparisons with other spectroscopies}\label{quant}
-\subsection{Site Selectivity}
+\section{Comparisons with Other Spectroscopies}\label{quant}
 Unlike resonant hyper-Raman spectroscopy, which allows transitions between different normal modes of varying quanta, the infrared pulse in the HDFG provides a type of site selectivity,\cite{RN103, Carlson1991} so that only the mode pumped by $\omega_1$ can be involved in vibronic coupling.
-% DDK: I kind of understand this point...but a hyper-Raman spectrum would clearly select the vibrational mode based on the Raman shift, correct?
-%  good to note the benefits of this technique compared to hyper-Raman:
-% - a form of stimulated hyper-Raman (=stronger, directional signals)
-% - experiment takes place over a short time window, so pump-probe experiments are easily implemented
-% - laser scatter is easily avoided
-% - IR active, not 
+While a typical hyper-Raman experiment can probe similar information by tracking the relative intensity of a mode with different excitation color, hyper-Raman output is incoherent and difficult to detect.
+\cite{Kelley2010}
+Since HDFG output depends upon stimulated hyper-Raman scattering, the output is highly directional, increasing the efficency of detecting hyper-Raman based output. 
+As a result, it is easier to assess changes in intensities and quantify coupling strengths in terms of $\chi^{(3)}$ (\textit{vide infra}).
+
 HDFG methods can supplement other coherent Raman based methods as a method to investigate vibronic coupling mechanisms between a specific vibration on the ground state and vibrational states on an arbitrary excited state.\cite{RN103}
@@
 The hybrid infrared / hyper-Raman properties of HDFG make it an intriguing analogue of resonance IR spectroscopy.
-First demonstrated by Boyle et al., resonance IR uses a $2\vec{k}_1 + \vec{k}_3$ pathway to amplify weak infrared modes through vibronic coupling, dependent upon the Raman $A,B$ coefficients.
+First demonstrated by Boyle et al., resonance IR uses a $2\vec{k}_1 + \vec{k}_3$ pathway, identical to the TSF pathway in \autoref{fig:comparisonwmel}, to amplify weak infrared modes through vibronic coupling, dependent upon the Raman $A,B,C$ coefficients.
 \cite{RN491}
 However, the $2\vec{k}_1 + \vec{k}_3$ resonance IR method implicitly depends upon the coupling of an overtone $\ket{g,2v}$ to vibronics $\ket{e,v'}$.
-% DDK: did we not already discuss this?  Why is this not the introduction?
+% DDK: did we not already discuss this?  Why is this not the introduction? %rpm: I see this as a place to expand on it since discussion in intro is succinct
 Alternatively, HDFG provides another form of resonance IR spectroscopy, but only requires coupling between $\ket{g,v}$ and $\ket{e,v'}$.
@@
 
-\subsection{Comparison to Sum Frequency Generation}
-% this whole argument is we only need two colors...condense this
-% also note the intro covers this now
-Despite these attributes of HDFG, four wave mixing techniques are usually unfeasible for most laboratories, as they usually demand the use of multiple optical parametric amplifiers and/or complex acousto-optic modulators.
-\cite{RN245}  % I don't understand the citation, but also a citation is not necessary...
+Despite their increasing use for dissecting intra and intermolecular interactions, four wave mixing techniques are usually not feasible for most laboratories, as they usually demand the use of multiple optical parametric amplifiers and/or complex acousto-optic modulators.
 Unlike most four wave mixing techniques, HDFG can be performed using only two input beams (i.e., two color HDFG).
 In the case of two color HDFG, only one tunable infrared optical parametric amplifier is needed, as the oscillator which pumps the infrared OPA can be used to perform the two-photon upconversion needed to generate HDFG output, i.e., $-\vec{k}_1 + 2\vec{k}_2$.
-A commonly used two laser CMDS method is vibrational sum frequency generation (vSFG), a $\chi^{(2)}$ technique whose phasematching is dictated by $\vec{k}_1 + \vec{k}_2$.
-vSFG output scales as $\chi^{(2)}_{IJK} \sim \langle \alpha_{ij} \mu_k \rangle$, where $\alpha_{ij}$ is the Raman polarizability tensor.
+Vibrational sum frequency generation (vSFG) is a $\chi^{(2)}$ technique whose output, when only vibrationally resonant, scales as $\chi^{(2)}_{IJK} \sim \langle \alpha_{ij} \mu_k \rangle$, where $\alpha_{ij}$ is the Raman polarizability tensor, whose phasematching constraint is  $\vec{k}_1 + \vec{k}_2$.
 Laboratories which use vSFG to investigate interfacial species at buried interfaces thus have the ingredients necessary to perform a HDFG experiment in a transmission geometry. \cite{Piontek2023_1}
@@
 
-Assessing the relative amplitudes of vSFG and HDFG is useful for demonstrating its feasibility as a nonlinear infrared spectroscopy. 
-Note that both vSFG and HDFG can be phasematched in media with normal indices of refraction, unlike the $\vec{k}_1 + 2\vec{k}_2$ HSFG process (\autoref{fig:comparisonwmel}).\cite{RN120}
+To demonstrate the feasibility of HDFG for vSFG practitioners, we compare the relative output of each process. 
 Macroscopically, oddness in spatial inversion of the vSFG polarization eliminates output from centrosymmetric species under the electric dipole approximation.\cite{RN132, RN133}
-As a result, vSFG output is significantly reduced relative to most third order spectroscopies because it depends on surface number density, many orders of magnitude smaller than the bulk surface density.
-% DDK: we should clarify that these cross sections are weak even for non-linear cross-sections
-Hyper-Raman cross-sections are commonly several orders of magnitude weaker than corresponding Raman transitions.\cite{RN515}
+As a result, vSFG output is significantly reduced relative to most third order spectroscopies because it depends on surface number density, many orders of magnitude smaller than the bulk surface density, which is weak even for even for non-linear cross-sections.
+However, HDFG depends upon hyper-Raman cross-sections, which are commonly several orders of magnitude weaker than corresponding Raman transitions.\cite{RN515}
+As discussed in \autoref{appendixA}, these effects cancel, and the output polarization of HDFG and vSFG are roughly identical ($\abs{P_\text{vSFG} / P_\text{HDFG}} \sim 1$).
+Transient HDFG, or IR-pump-HDFG-probe, analogous to IR-pump-vSFG-probe, is therefore also feasible under similar experimental conditions, and provides vSFG practitioners a simple method to measure bulk dynamics without significant changes in an experimental setup.
+Therefore, HDFG is a feasible spectroscopy for practitioners of vSFG both in terms of experimental setup and detection feasibility.
 
-% As a result, it is important to compare the relative output polarizations for both vSFG and HDFG taking into account the significant disparities in number densities and oscillator strengths.
-
-% DDK: put this calculation in the SI; it's not really important.
-% To motivate the application of HDFG spectroscopy in a vSFG type geometry, we perform a calculation to compare two-color HDFG and vSFG output, where absorption effects are neglected for simplicity.
-% The output polarizations under the electric dipole approximation are written as
-% \begin{widetext}
-% 	\begin{subequations}
-% 	\begin{equation}\label{PSFG}
-% 		\abs{P^{(2)}_{\text{vSFG}}} = \frac{N_{surf}}{\ell} F(\omega_1+\omega_2) \abs{\langle \alpha_{ij}\mu_{k} \rangle E(\omega_2)E(\omega_1)} 
-% 	\end{equation}
-% 	\begin{equation}
-% 		\abs{P^{(3)}_{\text{HDFG}}} = N_{bulk}  F(2\omega_2-\omega_1) \abs{\langle \beta_{ijk} \mu_{l} \rangle E{(\omega_2)}E(\omega_2)E(-\omega_1)}
-% 	\end{equation}
-% \end{subequations}
-% \end{widetext}
-% where N$_{bulk}$ is the bulk number density ($\sim$ 10$^{28}$ m$^{-3}$ for H$_2$O$_{(l)}$ at room temperature), and N$_{surf}$ is the surface number density ($\sim$ 10$^{16}$ m$^{-2}$ for H$_2$O adsorbed at quartz).\cite{Du1994}
-% For simplicity, we assume that $\chi^{(2)}$ is a spatial constant so that $\int_{0^-}^\ell \mathrm{d}z \langle \alpha_{ij}\mu_{k} \rangle \approx \ell \langle \alpha_{ij}\mu_{k} \rangle$, where $z$ is oriented along the surface normal and $0^{-}$ is the edge of the interface where substrate begins.
-\cite{Su1998}
-% We take the film thickness ($\ell$) probed by vSFG to be 1 nm, much less than the vSFG coherence length.\cite{RN133}
-% A normal dispersion curve is assumed so that $F(\omega_1+\omega_2) \approx F(2\omega_2-\omega_1)$.
-% To simplify analysis, orientational averaging is ignored (e.g., $\langle \beta_{ijk} \mu_{l} \rangle \approx \beta \mu$) and the input and output fields are taken to be co-polarized, so that
-% \begin{equation}
-% 		P_{ratio} \equiv \frac{\abs{P^{(3)}_{\text{HDFG}}}}{\abs{P^{(2)}_{\text{vSFG}}}} \approx \frac{N_{bulk}}{N_{surf}} \frac{\beta}{\alpha} E(\omega_2) \ell \sim 10^3 \frac{\beta}{\alpha} E(\omega_2)\\
-% \end{equation}
-% Ziegler has noted that for a field with intensity 10 GW/cm$^{2}$, $\frac{\beta E}{\alpha} \sim 10^{-3} $ for vibrational modes when $E(\omega_2)$ is largely detuned from electronic resonances.
-\cite{RN515}
-% Such an intensity is easily obtained using modern ultrafast sources.
-% In this limit, $P_\text{ratio} \sim 1$.
-% Since the intensity ratio scales as $\abs{P_{ratio}}^2$, we see that the HDFG output is roughly as strong as vSFG, assuming only interfacial contributions in vSFG.
-% It is important to note that this calculation assumed negligible dipole and Raman polarizability dependence upon the distance from surface normal, ignored orientational averaging effects, and presumed equivalence of local field factors, all of which can significantly reduce output from either process.
-% Nevertheless, since HDFG produces a number of photons similar to that of vSFG, HDFG is a viable technique for investigating bulk systems.
-% This method provides practitioners of sum frequency generation the ability to probe isotropic dephasing dynamics without many meaningful changes in their optical setup, and thus compare  dephasing in the bulk and at the interface.\cite{RN224}
-
-Transient HDFG spectroscopy, or pump-HDFG-probe, similar to transient vSFG spectroscopy (pump-vSFG-probe), can be implemented to learn about relaxation dynamics in isotropic systems.
-\cite{RN224, Bonn2024}
-A useful attribute of the $\beta_{ijk}$ dependence in HDFG output is added polarization control. 
-Similar to SFG experiments that probe different elements of the infrared transition dipole and Raman polarizability tensors, probing different elements of $\beta_{ijk}$ in HDFG can greatly assist in understanding ultrafast dynamics in isotropic systems, as suggested by Seliya et al.
-\cite{Shen90, RN224, Bonn2024}
-Polarization control in IR-pump-HDFG-probe, analogous to polarization control in pump-vSFG-probe, would be an interesting venue to assess the sensitivity of HDFG to different hyper-Raman tensor elements, and for practioners of transient vSFG to compare polarization specific dynamics at the interface and in the bulk.
-
-\subsection{Quantitative HDFG: Measuring the Hyper-Raman Hyperpolarizability}
 With the selection rules of HDFG understood for vibrational spectroscopy, and with HDFG generating a large enough output polarization, it becomes possible to obtain quantitative information from its spectra.
@@
 Scanning across resonances create dispersive lineshapes, i.e, self-heterodyning, which inform on $\Re(\chi^{(3)})$ and $\Im(\chi^{(3)})$.\cite{Levenson1974_1, Levenson1974_2}
-In the method introduced by Levenson and Bloembergen (Bloembergen Interferometry Experiment), an internal standard interferes with the resonant lineshape.
+In the method introduced by Levenson and Bloembergen (Bloembergen interferometry experiment), an internal standard interferes with the resonant lineshape.
 Self-heterodyning of the internal standard signal measures $\chi^{(3)}$ and does not require measurement of absolute intensities. 
@@
 Methods reported in the literature to measure absolute hyper-Raman polarizabilities depend upon external standards such as hyperpolarizabilities of dissolved samples or two-photon absorption cross sections, also difficult to measure.
+\cite{Okuno2020}
 Since the Bloembergen interferometry experiment only relies on the third order susceptibility for measured species (e.g., benzene or CaF$_2$),\cite{Levenson1974_2} it is possible to use quantitative four wave mixing spectroscopy to calculate $\beta_{ijk}$ values.
@@
 Orientational averaging shows specific polarization schemes isolate linear combinations of different $\beta_{ijk}$ terms. \cite{Bersohn1966, Willetts1992, Kauranen1996}
-By using the expansions of $\beta_{ijk}$ and $\mu_{l}$ to $\order{Q_n}$ found earlier, and knowing that $\Re(\chi^{(3)})$ vanishes when resonant, we see
+By using the expansions of $\beta_{ijk}$ and $\mu_{l}$ to $\order{Q_v}$ found earlier, and knowing that $\Re(\chi^{(3)})$ vanishes when resonant, we see
 \begin{equation}\label{betasive}
-	\left\langle \frac{\partial \beta_{ijk}}{\partial Q_n} {\frac{\partial \mu_l}{\partial Q_n}} \right\rangle = -\frac{8D \varepsilon_0}{NF}  {\Gamma_{gv} \omega_{vg}} {\Im(\chi^{(3)}_{IJKL})}
+	\left\langle \frac{\partial \beta_{ijk}}{\partial Q_v} {\frac{\partial \mu_l}{\partial Q_v}} \right\rangle = -\frac{8D \varepsilon_0}{NF}  {\Gamma_{gv} \omega_{vg}} {\Im(\chi^{(3)}_{IJKL})}
 \end{equation}
-Since $\abs{\partial \mu / \partial Q}$ values can be extracted from FT-IR spectra, HDFG can give quantitative information on the magnitude of $\beta_{ijk}$ for infrared active vibrations.
+Since $\abs{\partial \mu / \partial Q}$ values can be extracted from FT-IR spectra,\cite{RN459} HDFG can give quantitative information on the magnitude of $\beta_{ijk}$ for infrared active vibrations.
 Additionally, by using non-degenerate input frequencies to stimulate the hyper-Raman transition, the asymmetric properties of $\beta_{ijk}$ can be examined and quantified.
 \cite{Christie1971, Denisov1986, Kozich2007}
-To our knowledge, no experiment has been performed which quantifies deviations of the asymmetric and symmetric components of $\beta_{ijk}$. 
-These quantitative aspects of HDFG could prove useful to examine how well computational methods calculate $\beta_{ijk}$ values and the strength of spontaneous hyper-Raman scattering with non-degenerate pulses.
+These quantitative aspects of HDFG could prove useful for examining how well computational methods calculate $\beta_{ijk}$ values and the strength of spontaneous hyper-Raman scattering with non-degenerate pulses.
 
-\section{Conclusions}
+\section{Conclusions}\label{conclusion}
 Coherent vibrational, hyper-Raman coherent four wave mixing spectroscopies are identified and discussed.
-Singly resonant hyper difference frequency generation (SR-HDFG) processes are shown to be the coherent hyper-Raman analogue of infrared active vibrations.
+Hyper-Raman difference frequency generation (HDFG) processes, a coherent analogue of infrared spectroscopy, are shown to be non-zero for all harmonically allowed infrared transitions.
 We find that HDFG is always allowed for harmonic transitions, making it a potential tool for measuring single quantum coherence lifetimes. 
 Through an examination of the hyper-Raman $A,B,C$ terms, the impact of electronic resonance and vibronic coupling in HDFG spectrum was examined.
-The non-Condon effects that are present in the absence of $A$ might prove useful for resolving the electronic structure of centrosymmetric species.
 HDFG possesses types of site-selective properties analogous to those of nanosecond coherent Raman experiments. 
 Site-selective properties should allow for a thorough analysis of vibronic coupling schemes in isotropic systems.
-Through a simple treatment, it is seen that HDFG and vibrational sum frequency generation (vSFG) have roughly the same output intensities. 
-This makes HDFG a reasonable spectroscopy for systems outside of the ideal solvents tested in the literature, and should be readily extended to a variety of non-ideal molecular and materials systems. 
-Based upon a simple treatment of orientational averaging, we show that HDFG can extract the hyper-Raman hyperpolarizability without a need for technically difficult, analytically rigorous hyper-Raman scattering experiments.
+Due to the triviality of performing HDFG as a two-beam experiment, HDFG is shown to be feasible for practioners of vibrational sum-frequency generation (vSFG) spectroscopy. 
+We show that HDFG can extract the hyper-Raman hyperpolarizability without a need for technically difficult, analytically rigorous hyper-Raman scattering experiments. 
 The HDFG method shows promise as a spectroscopic probe of unique electronic structure effects in a variety of molecular systems, but also for understanding the dynamics of single quantum coherences.
-\section{Data Availability}
-The workup scripts which support this work can be found at [insert github link here].
 
 \section{Acknowledgments}
-This work received support from the Department of Energy, Office of Basic Energy Sciences, Division of Materials Sciences and Engineering (Grant no. DE-SC0002162).
+This work received support from the National Science Foundation (Grant no. CHE-2203290).
 R.P.M. acknowledges support from the NSF Graduate Research Fellowship Program (Grant no. DGE-2137424).
 
-%todo: figure out how footnotes work...
+\section{Appendix: Comparison of vSFG and two-beam HDFG output}\label{appendixA}
+ To motivate the application of HDFG spectroscopy in a vSFG type geometry, we perform a calculation to compare two-color HDFG and vSFG output, where absorption effects are neglected for simplicity.
+ The output polarizations under the electric dipole approximation are written as
 
-%{By defining $\Lambda^{mn}_{ij} = \sum_k (m|M_i|k) (k|M_j|n)$, expanding $\Lambda^{mn}_{ij}$ to $\order{Q}$ gives $\Lambda^{mn}_{0,ij} + \partial/ \partial Q \sum_k (m|M_i|k) (k|M_j|n) Q$ = $\Lambda^{mn}_{0,ij} + \sum_k (m|\partial M_i / \partial Q|k) (k|M_j|n) Q + (m|M_i|k) (k|\partial M_j / \partial Q|n) Q$, in agreement with the substitution made above.}
+	 	\begin{subequations}
+		 	\begin{equation}\label{PSFG}
+		 		\begin{split}
+		 		\abs{P^{(2)}_{\text{vSFG}}} &= \frac{N_\text{surf}}{\ell} F(\omega_1+\omega_2) \abs{\langle \alpha_{ij}\mu_{k} \rangle E(\omega_2)E(\omega_1)} 
+		 		\end{split}
+			 \end{equation}
+		 	\begin{equation}
+		 		\begin{split}
+			 		\abs{P^{(3)}_{\text{HDFG}}} &= N_\text{bulk}  F(2\omega_2-\omega_1)  \abs{\langle \beta_{ijk} \mu_{l} \rangle E{(\omega_2)}E(\omega_2)E(-\omega_1)}
+		 		\end{split}
+			 \end{equation}
+		 \end{subequations}
+
+ where N$_\text{bulk}$ is the bulk number density ($\sim$ 10$^{28}$ m$^{-3}$ for H$_2$O$_{(l)}$ at room temperature), and N$_\text{surf}$ is the surface number density ($\sim$ 10$^{16}$ m$^{-2}$ for H$_2$O adsorbed at quartz).\cite{Du1994}
+ For simplicity, we assume that $\chi^{(2)}$ is a spatial constant so that $\int_{0^-}^\ell \mathrm{d}z \langle \alpha_{ij}\mu_{k} \rangle \approx \ell \langle \alpha_{ij}\mu_{k} \rangle$, where $z$ is oriented along the surface normal and $0^{-}$ is the edge of the interface where substrate begins.
+\cite{Su1998}
+ We take the film thickness ($\ell$) probed by vSFG to be 1 nm, much less than the vSFG coherence length.\cite{RN133}
+ A normal dispersion curve is assumed so that $F(\omega_1+\omega_2) \approx F(2\omega_2-\omega_1)$.
+ To simplify analysis, orientational averaging is ignored (e.g., $\langle \beta_{ijk} \mu_{l} \rangle \approx \beta \mu$) and the input and output fields are taken to be co-polarized, so that
+ \begin{equation}
+	 		P_\text{ratio} \equiv \frac{\abs{P^{(3)}_{\text{HDFG}}}}{\abs{P^{(2)}_{\text{vSFG}}}} \approx \frac{N_\text{bulk}}{N_\text{surf}} \frac{\beta}{\alpha} E(\omega_2) \ell \sim 10^3 \frac{\beta}{\alpha} E(\omega_2)\\
+	 \end{equation}
+ Ziegler has noted that for a field with intensity 10 GW/cm$^{2}$, $\frac{\beta E}{\alpha} \sim 10^{-3} $ for vibrational modes when $E(\omega_2)$ is largely detuned from electronic resonances.
+\cite{RN515}
+ Such an intensity is easily obtained using modern ultrafast sources.
+ In this limit, $P_\text{ratio} \sim 1$.
+ Since the intensity ratio scales as $\abs{P_\text{ratio}}^2$, we see that the HDFG output is roughly as strong as vSFG, assuming only interfacial contributions in vSFG.
+ It is important to note that this calculation assumed negligible dipole and Raman polarizability dependence upon the distance from surface normal, ignored orientational averaging effects, and presumed equivalence of local field factors, all of which can significantly reduce output from either process.
+ Nevertheless, since HDFG produces a number of photons similar to that of vSFG, HDFG is a viable technique for investigating bulk systems.
+ This method provides practitioners of sum frequency generation the ability to probe isotropic dephasing dynamics without many meaningful changes in their optical setup, and thus compare  dephasing in the bulk and at the interface.\cite{RN224}
 

### 2024-07-29 paper.tex
small issue in abstract

@@
 Nonlinear, four wave mixing vibrational spectroscopies are often used to probe intramolecular vibrational coupling and relaxation dynamics in isotropic media.
-Most of these methods rely on infrared and/or Raman transitions, such as sum-frequency generation (SFG) spectroscopy, but methods involving hyper-Raman transitions are also possible. 
-The additional number of tensor elements in the hyper-Raman hyperpolarizability have been useful for probing condensed phase media. 
+Most of these methods rely on infrared and/or Raman transitions but methods involving hyper-Raman transitions are also possible. 
 Implementing a nonlinear spectroscopy involving hyper-Raman transitions can provide a useful analogue to infrared and Raman based nonlinear spectroscopies to understand the spectroscopy and dynamics of isotropic systems.
 Hyper Difference Frequency Generation (Hyper-DFG, or HDFG) spectroscopy is an underdeveloped four wave mixing vibrational spectroscopy based on the hyper-Raman transition. 
+The method is similar in implementation to that of vibrational sum frequency generation (vSFG) and difference frequency generation (vDFG) spectroscopy.
 Despite several experimental reports on HDFG, its spectroscopic properties have not been fully explored.  

### 2024-07-29 figures/2D_spec.py

@@ -12,7 +12,6 @@ from matplotlib.patches import FancyArrowPatch
 wt.artists.apply_rcparams(kind="publication")
 
 save = True
-
 fontsize = 18
 
 #define harmonic wells and coordinates

### 2024-07-29 paper.tex
data availability statement
deleted useless words

@@
 
+\section{Data Availability Statement}
+The workup scripts that support this study are permissively licensed and available for reuse at \href{https://osf.io/2amkq/}{https://osf.io/2amkq/}.
+
 \section{Acknowledgments}
@@
 \section{Appendix: Comparison of vSFG and two-beam HDFG output}\label{appendixA}
- To motivate the application of HDFG spectroscopy in a vSFG type geometry, we perform a calculation to compare two-color HDFG and vSFG output, where absorption effects are neglected for simplicity.
+ To motivate the application of HDFG spectroscopy, we perform a calculation to compare two-color HDFG and vSFG output, where absorption effects are neglected for simplicity.
  The output polarizations under the electric dipole approximation are written as

### 2024-07-29 paper.tex
added peter chen review citation

@@
 Four wave mixing CMDS has resolved anharmonicities, ultrafast dynamics, and other inter- and intra-molecular couplings in numerous systems.
-\cite{Cho2008, Gaynor2017, Ziegler2018, Ogilvie2019, Bonn2021, RN325}
-To target vibrational and electronic coupling, methods commonly make use of Raman transitions, e.g., doubly vibrationally enhanced spectroscopy (DOVE), triple sum frequency (TSF), coherent anti-Stokes Raman spectroscopy (CARS), resonant impulse stimulated Raman spectroscopy (RISRS).\cite{RN103, Dhar1994, RN345, Cho2000, RN491}
+\cite{Cho2008, Gaynor2017, Ziegler2018, Ogilvie2019, Bonn2021, RN325, Chen2024}
+To target vibrational and electronic coupling, methods commonly make use of Raman transitions, e.g., doubly vibrationally enhanced spectroscopy (DOVE), triple sum frequency (TSF), coherent anti-Stokes Raman spectroscopy (CARS), resonant impulse stimulated Raman spectroscopy (RISRS).\cite{RN425, Dhar1994, RN345, Cho2000, RN491}
 Here we explore the less-utilized hyper-Raman transitions in four wave mixing CMDS.
@@
 Despite their increasing use for dissecting intra and intermolecular interactions, four wave mixing techniques are usually not feasible for most laboratories, as they usually demand the use of multiple optical parametric amplifiers and/or complex acousto-optic modulators.
+\cite{Chen2016}
 Unlike most four wave mixing techniques, HDFG can be performed using only two input beams (i.e., two color HDFG).
@@
 However, HDFG depends upon hyper-Raman cross-sections, which are commonly several orders of magnitude weaker than corresponding Raman transitions.\cite{RN515}
-As discussed in \autoref{appendixA}, these effects cancel, and the output polarization of HDFG and vSFG are roughly identical ($\abs{P_\text{vSFG} / P_\text{HDFG}} \sim 1$).
+As calculated in \autoref{appendixA}, these effects cancel, and the output polarization of HDFG and vSFG are roughly identical ($\abs{P_\text{vSFG} / P_\text{HDFG}} \sim 1$).
 Transient HDFG, or IR-pump-HDFG-probe, analogous to IR-pump-vSFG-probe, is therefore also feasible under similar experimental conditions, and provides vSFG practitioners a simple method to measure bulk dynamics without significant changes in an experimental setup.

### 2024-07-29 paper.tex
last few things

@@
 \cite{Cho2008, Gaynor2017, Ziegler2018, Ogilvie2019, Bonn2021, RN325, Chen2024}
-To target vibrational and electronic coupling, methods commonly make use of Raman transitions, e.g., doubly vibrationally enhanced spectroscopy (DOVE), triple sum frequency (TSF), coherent anti-Stokes Raman spectroscopy (CARS), resonant impulse stimulated Raman spectroscopy (RISRS).\cite{RN425, Dhar1994, RN345, Cho2000, RN491}
+To target vibrational and electronic coupling, methods commonly make use of Raman transitions, e.g., doubly vibrationally enhanced spectroscopy (DOVE), triple sum frequency (TSF), coherent anti-Stokes Raman spectroscopy (CARS), resonant impulse stimulated Raman spectroscopy (RISRS).\cite{RN103, Dhar1994, RN345, Cho2000, RN491}
 Here we explore the less-utilized hyper-Raman transitions in four wave mixing CMDS.
@@
 Hyper-Raman scattering itself is a six-wave mixing ($\chi^{(5)}$) technique; stimulated hyper-Raman will be weak and susceptible to FWM cascades.\cite{RN515, RN243, Cho2000_Cascade}
-A coherent six-wave mixing analogue of hyper-Raman scattering, coherent anti-Stokes hyper-Raman spectroscopy (CAHRS), has been proposed and explored theoretically by several authors; however, it is also highly susceptible to FWM cascades.\cite{Berger1978, Bjarnason1980, RN243, Cho1997, Cho1998, Cho2000_Cascade}
+A coherent six-wave mixing analogue of hyper-Raman scattering, coherent anti-Stokes hyper-Raman spectroscopy (CAHRS), has been proposed and explored theoretically by several authors; however, it is also highly susceptible to FWM cascades.\cite{Berger1978, Bjarnason1980, Cho1997, Cho1998}
 Of the many four-wave mixing techniques, HDFG and HSFG have strong similarity to Raman, stimulated Raman, and RISRS in that the electronic state must remove or add a $v$ quantum to the ground state (``ev'' coupling).
+%rpm: not sure what you're trying to say by this
 With the other four-wave mixing techniques (\autoref{fig:comparisonwmel}, second row), the output signal depends on more states than just a single vibrational mode and electronic state (``evx'' coupling).
@@
 HDFG, HSFG and Raman are more direct probes of electronic-vibrational coupling.
-Notably, HDFG and HSFG can be implemented as 2-color experiments (with $\omega_2=\omega_3$); vibrational sum frequency generation (vSFG) or difference frequency generation (vDFG) setups can be trivially reconfigured to perform HSFG or HDFG measurements, respectively, to investigate ev coupling in bulk systems.
+Notably, HDFG and HSFG can be implemented as 2-color experiments (with $\omega_2=\omega_3$);\cite{Cho2001} vibrational sum frequency generation (vSFG) or difference frequency generation (vDFG) setups can be trivially reconfigured to perform HSFG or HDFG measurements, respectively, to investigate ev coupling in bulk systems.
 
@@
 Inspired by recent work that demonstrated the presence of HDFG in ultrafast DOVE and terahertz-IR-visible (TIRV) experiments, we investigate the parameters which result in HDFG output.
-\cite{Cho2000, Bonn2024, McDonnell2024}
+\cite{Bonn2024, McDonnell2024}
 This paper is organized as follows.
@@
 
-It is useful to expose relationships between transition dipoles and hyper-Raman hyperpolarizabilities in the driven limit. \cite{Simpson2004}
+It is useful to expose relationships between nonlinear output, transition dipoles and hyper-Raman hyperpolarizabilities in the driven limit. \cite{Simpson2004}
 Under the electric dipole approximation, the I$^{th}$ component of the third order nonlinear output polarization, ${P}^{(3)}_I$, of a four wave mixing process, induced by electric fields $E_J$, $E_K$, and $E_L$ at output frequency $\omega_4=-\omega_1 + \omega_2 + \omega_3$ is written as (using Einstein summation) \cite{RN307}
@@
 These results provide a simple rule of thumb for collecting HDFG spectra: use \autoref{fig:sivewmel2}a,b pathways to measure spectra when significantly detuned from an electronic resonance, and any pathway can measure spectra when electronically resonant.
-However, since electronic states commonly have short dephasing times and have significantly inhomogeneous broadening,\cite{Dong2015, Lewis2015} it is likely the \autoref{fig:sivewmel2}f pathway will become triply resonant and possibly contribute greater than the other pathways.
+However, since electronic states commonly have short dephasing times and have significant inhomogeneous broadening,\cite{Dong2015, Lewis2015} it is likely the \autoref{fig:sivewmel2}f pathway will become triply resonant and possibly contribute greater than the other pathways.
 Such instances are system dependent. 
@@
 The brightness is controlled by vibrational overlap (Franck-Condon factors).
-For centrosymmetric molecules, however, an electronic transition cannot be both one- and two- photon allowed, so the $A$ term will vanish.\cite{Milojevich2013, RN230}
+For centrosymmetric molecules, however, an electronic transition cannot be both one- and two- photon allowed, so the $A$ term will vanish.\cite{Milojevich2013}
 This makes HDFG a unique tool for studying the electronic structure of centrosymmetric species in isotropic media, as it is sensitive to non-Condon effects.\cite{Olson2018}
@@
  For simplicity, we assume that $\chi^{(2)}$ is a spatial constant so that $\int_{0^-}^\ell \mathrm{d}z \langle \alpha_{ij}\mu_{k} \rangle \approx \ell \langle \alpha_{ij}\mu_{k} \rangle$, where $z$ is oriented along the surface normal and $0^{-}$ is the edge of the interface where substrate begins.
-\cite{Su1998}
  We take the film thickness ($\ell$) probed by vSFG to be 1 nm, much less than the vSFG coherence length.\cite{RN133}

### 2024-07-29 paper.tex
Added F factor reference and definition in paper

@@
 \begin{equation}
-	\chi^{(3)}_{IJKL} = NF(\omega_4) \langle \gamma_{ijkl} \rangle
+	\chi^{(3)}_{IJKL} = NF \langle \gamma_{ijkl} \rangle
 \end{equation}
 where $N$ is a number density, $F$ is the Lorentz local field factor, and $\gamma_{ijkl}$ is the third order polarizability (i.e., second hyperpolarizability). 
+For $j$ input and output fields with frequency $\omega_j$, 
+\begin{equation}
+	F = \prod_j \frac{\left(n(\omega_j)\right)^2 + 1}{3}
+\end{equation}
+where $n(\omega_j)$ is the refractive index at frequency $\omega_j$.\cite{Bedeaux1973}
 The brackets indicate an orientational (or rotational) average.\cite{Andrews1977}
@@
 If $\omega_2$ ($\omega_1$) becomes resonant (non-resonant), where $\omega_2 > \omega_1$, then other HDFG pathways appear (\autoref{fig:sivewmel2}).\cite{McDonnell2024} 
-While the methods in \autoref{fig:sivewmel2} possess identical selection rules to \autoref{fig:comparisonwmel}, the WMEL diagrams presented in \autoref{fig:sivewmel2} will interfere, as they share the same phasematching condition but have oppositely signed amplitudes.
+While the methods in \autoref{fig:sivewmel2} possess identical selection rules to \autoref{fig:comparisonwmel}, the WMEL diagrams presented in \autoref{fig:sivewmel2} will interfere, as they share the same phase-matching condition but have oppositely signed amplitudes.
 \begin{figure*}[!htbp]
@@
 Unlike most four wave mixing techniques, HDFG can be performed using only two input beams (i.e., two color HDFG).
-In the case of two color HDFG, only one tunable infrared optical parametric amplifier is needed, as the oscillator which pumps the infrared OPA can be used to perform the two-photon upconversion needed to generate HDFG output, i.e., $-\vec{k}_1 + 2\vec{k}_2$.
-Vibrational sum frequency generation (vSFG) is a $\chi^{(2)}$ technique whose output, when only vibrationally resonant, scales as $\chi^{(2)}_{IJK} \sim \langle \alpha_{ij} \mu_k \rangle$, where $\alpha_{ij}$ is the Raman polarizability tensor, whose phasematching constraint is  $\vec{k}_1 + \vec{k}_2$.
+In the case of two color HDFG, only one tunable infrared optical parametric amplifier is needed, as the oscillator which pumps the infrared OPA can be used to perform the two-photon upconversion needed to generate HDFG output.
+Vibrational sum frequency generation (vSFG) is a $\chi^{(2)}$ technique whose output, when only vibrationally resonant, scales as $\chi^{(2)}_{IJK} \sim \langle \alpha_{ij} \mu_k \rangle$, where $\alpha_{ij}$ is the Raman polarizability tensor, whose phase-matching constraint is  $\vec{k}_3 = \vec{k}_1 + \vec{k}_2$.
+HDFG is phase-matchable under $\vec{k}_4 = -\vec{k}_1 + 2\vec{k}_2$ conditions for most, if not all, vibrational resonances.
 Laboratories which use vSFG to investigate interfacial species at buried interfaces thus have the ingredients necessary to perform a HDFG experiment in a transmission geometry. \cite{Piontek2023_1}
-This would allow vSFG practitioners to perform measurements in the bulk, such as measuring free induction decay, vibrational population lifetimes, and steady-state vibrational spectra through HDFG.
+This would allow vSFG practitioners to perform measurements in the bulk, such as measuring steady-state vibrational spectra, free induction decay and vibrational population lifetimes through HDFG or pump-HDFG-probe.
 
@@
 \begin{split}
-		\chi^{(3)}_{IJKL} &= NF(\omega_4) \langle \gamma_{ijkl} \rangle = -\frac{NF}{4D \hbar \varepsilon_0 \Delta_{gv}} \langle \beta_{ijk} \mu_l \rangle \rho_{gg}\\
+		\chi^{(3)}_{IJKL} &= NF \langle \gamma_{ijkl} \rangle = -\frac{NF}{4D \hbar \varepsilon_0 \Delta_{gv}} \langle \beta_{ijk} \mu_l \rangle \rho_{gg}\\
 \end{split}
@@
 \section{Appendix: Comparison of vSFG and two-beam HDFG output}\label{appendixA}
- To motivate the application of HDFG spectroscopy, we perform a calculation to compare two-color HDFG and vSFG output, where absorption effects are neglected for simplicity.
+ To motivate the application of HDFG spectroscopy, we perform a calculation to compare two-color HDFG and vSFG output, where absorption effects are neglected for simplicity. \cite{Carlson1989}
  The output polarizations under the electric dipole approximation are written as
-
 	 	\begin{subequations}
@@
 		 		\begin{split}
-		 		\abs{P^{(2)}_{\text{vSFG}}} &= \frac{N_\text{surf}}{\ell} F(\omega_1+\omega_2) \abs{\langle \alpha_{ij}\mu_{k} \rangle E(\omega_2)E(\omega_1)} 
+		 		\abs{P^{(2)}_{\text{vSFG}}} &= \frac{N_\text{surf}}{\ell} \abs{F_{\text{SFG}} \langle \alpha_{ij}\mu_{k} \rangle E(\omega_2)E(\omega_1)} 
 		 		\end{split}
@@
 		 		\begin{split}
-			 		\abs{P^{(3)}_{\text{HDFG}}} &= N_\text{bulk}  F(2\omega_2-\omega_1)  \abs{\langle \beta_{ijk} \mu_{l} \rangle E{(\omega_2)}E(\omega_2)E(-\omega_1)}
+			 		\abs{P^{(3)}_{\text{HDFG}}} &= N_\text{bulk} \abs{F_{\text{HDFG}} \langle \beta_{ijk} \mu_{l} \rangle E{(\omega_2)}E(\omega_2)E(-\omega_1)}
 		 		\end{split}
@@
 		 \end{subequations}
-
  where N$_\text{bulk}$ is the bulk number density ($\sim$ 10$^{28}$ m$^{-3}$ for H$_2$O$_{(l)}$ at room temperature), and N$_\text{surf}$ is the surface number density ($\sim$ 10$^{16}$ m$^{-2}$ for H$_2$O adsorbed at quartz).\cite{Du1994}
@@
  We take the film thickness ($\ell$) probed by vSFG to be 1 nm, much less than the vSFG coherence length.\cite{RN133}
- A normal dispersion curve is assumed so that $F(\omega_1+\omega_2) \approx F(2\omega_2-\omega_1)$.
+ A normal dispersion curve is assumed so that $n(\omega_1+\omega_2) \approx n(2\omega_2-\omega_1)$.
  To simplify analysis, orientational averaging is ignored (e.g., $\langle \beta_{ijk} \mu_{l} \rangle \approx \beta \mu$) and the input and output fields are taken to be co-polarized, so that
  \begin{equation}
-	 		P_\text{ratio} \equiv \frac{\abs{P^{(3)}_{\text{HDFG}}}}{\abs{P^{(2)}_{\text{vSFG}}}} \approx \frac{N_\text{bulk}}{N_\text{surf}} \frac{\beta}{\alpha} E(\omega_2) \ell \sim 10^3 \frac{\beta}{\alpha} E(\omega_2)\\
+	 		P_\text{ratio} \equiv \frac{\abs{P^{(3)}_{\text{HDFG}}}}{\abs{P^{(2)}_{\text{vSFG}}}} \approx \frac{N_\text{bulk}}{N_\text{surf}} \abs{\frac{\left(n(\omega_2)\right)^2 + 1}{3}} \frac{\beta}{\alpha} E(\omega_2) \ell \sim 10^3 \frac{\beta}{\alpha} E(\omega_2)\\
 	 \end{equation}

### 2024-07-29 paper.tex
integral fix

@@
 \end{equation}
-where we have used $\mel{v}{Q_v}{g} = \sqrt{\frac{\hbar}{2\omega_{vg}}}$ (in the limit $v-g = 1$) and $\omega_{vg}$ is the characteristic frequency.\cite{RN459}
+where we have used $\mel{v}{Q_v}{g} \equiv \mel{1}{Q_v}{0} = \sqrt{\frac{\hbar}{2\omega_{vg}}}$ and $\omega_{vg}$ is the characteristic $\ket{0} \rightarrow \ket{1}$ frequency.\cite{RN459}
 Since this expression is non-zero in the harmonic oscillator limit, HDFG output is allowed for normal modes in the harmonic limit.

### 2024-07-29 paper.tex
Update paper.tex

@@
 \begin{abstract}
+% DDK: change first sentence, we do not care about vibrational coupling here...
 Nonlinear, four wave mixing vibrational spectroscopies are often used to probe intramolecular vibrational coupling and relaxation dynamics in isotropic media.
 Most of these methods rely on infrared and/or Raman transitions but methods involving hyper-Raman transitions are also possible. 
-Implementing a nonlinear spectroscopy involving hyper-Raman transitions can provide a useful analogue to infrared and Raman based nonlinear spectroscopies to understand the spectroscopy and dynamics of isotropic systems.
-Hyper Difference Frequency Generation (Hyper-DFG, or HDFG) spectroscopy is an underdeveloped four wave mixing vibrational spectroscopy based on the hyper-Raman transition. 
-The method is similar in implementation to that of vibrational sum frequency generation (vSFG) and difference frequency generation (vDFG) spectroscopy.
+Nonlinear spectroscopy involving hyper-Raman transitions provides a useful analogue to infrared and Raman based nonlinear spectroscopies to understand the structure and dynamics of isotropic systems.
+Hyper-Raman Difference Frequency Generation (HDFG) spectroscopy is an underdeveloped four wave mixing vibrational spectroscopy based on the hyper-Raman transition. 
+% The method is similar in implementation to that of vibrational sum frequency generation (vSFG) and difference frequency generation (vDFG) spectroscopy.
 Despite several experimental reports on HDFG, its spectroscopic properties have not been fully explored.  
@@
 		Some spectroscopic methods for investigating (top) electronic-vibrational coupling and (bottom) e-v-x (x: e, v, e-v, e-v-e) coupling through different order nonlinear processes.
-		Note that the coherent $\chi^{(5)}$ e-v-x processes are difficult to isolate due to $\chi^{(3)}$ cascades. 
-		The light-matter interacitons are depicted using Wave Mixing Energy Level (WMEL) diagrams.\cite{RN286}
+		The light-matter interactions are depicted using Wave Mixing Energy Level (WMEL) diagrams.\cite{RN286}
 		Solid and dashed horizontal lines indicate real and virtual states, whereas solid and dotted arrows indicate ket and bra side transitions, respectively. 
@@
 CMDS methods partially mitigate this issue because emission is spatially coherent so that all emission is directional and easily collected.
-In fact, hyper-Raman transitions have been observed in several CMDS studies.\cite{Zilian1994, RN350, RN416, RN351, RN352, RN353, Chen1998, RN362, RN418, Wang2021, Bonn2024, McDonnell2024}
+In fact, hyper-Raman transitions have been observed in several CMDS studies (sometimes under the moniker of SIVE).\cite{Zilian1994, RN350, RN416, RN351, RN352, RN353, Chen1998, RN362, RN418, Wang2021, Bonn2024, McDonnell2024}
 
@@
 \autoref{fig:comparisonwmel} shows both HDFG and HSFG processes and compares them with related spectroscopies that investigate vibrational-electronic coupling.
-The three-wave mixing ($\chi^{(2)}$) techniques are often less applicable as they require non-centrosymmetry.\cite{RN227}
+The three-wave mixing ($\chi^{(2)}$) techniques are often less applicable as they require macroscopic non-centrosymmetry.\cite{RN227}
 Hyper-Raman scattering itself is a six-wave mixing ($\chi^{(5)}$) technique; stimulated hyper-Raman will be weak and susceptible to FWM cascades.\cite{RN515, RN243, Cho2000_Cascade}
@@
 In this section, we investigate the properties of HDFG and make the connections between HDFG and hyper-Raman scattering explicit.
-HSFG will not be discussed, but the application of our treatment to HSFG is straightforward and the informational content is similar.
+HSFG will not be discussed, but the application of our treatment to HSFG is straightforward and the selection rules are similar.
 We note that HDFG emission can be phase-matched in media with normal dispersion, while HSFG cannot.\cite{RN278}
 
-Before presenting selection rules, we note that a potential interferant in HDFG spectroscopy are direct and sequential cascades of second order vDFG and vSFG processes.\cite{RN297, RN302, RN301}
-While unimportant in achiral isotropic systems,\cite{Belkin2000} second order cascades may become important in media where SFG and DFG are allowed, e.g.
-chiral media, interfaces or noncentrosymmetric media.
-Nevertheless, in the discussion that follows for the rest of this manuscript, we will assume negligible second order cascades.
+Before presenting selection rules, we note that a potential interferant in HDFG spectroscopy are direct and sequential cascades of second-order vDFG and vSFG processes.\cite{RN297, RN302, RN301}
+While unimportant in achiral isotropic systems,\cite{Belkin2000} second-order cascades may become important in media where SFG and DFG are allowed, e.g.
+chiral media, interfaces or non-centrosymmetric media.
+Nevertheless, in the discussion that follows for the rest of this manuscript, we will assume negligible second-order cascades.
 
 It is useful to expose relationships between nonlinear output, transition dipoles and hyper-Raman hyperpolarizabilities in the driven limit. \cite{Simpson2004}
-Under the electric dipole approximation, the I$^{th}$ component of the third order nonlinear output polarization, ${P}^{(3)}_I$, of a four wave mixing process, induced by electric fields $E_J$, $E_K$, and $E_L$ at output frequency $\omega_4=-\omega_1 + \omega_2 + \omega_3$ is written as (using Einstein summation) \cite{RN307}
+Under the electric dipole approximation, the $I^\text{th}$ cartesian component of the third order nonlinear output polarization, ${P}^{(3)}_I$, of a four wave mixing process, induced by electric fields $E_J$, $E_K$, and $E_L$ at output frequency $\omega_4=-\omega_1 + \omega_2 + \omega_3$ is written as (using Einstein summation) \cite{RN307}
 \begin{equation} \label{polarization}
@@
 \end{equation}
-where $\chi^{(3)}_{IJKL}$ is the IJKL element of the third order electrical susceptibility, a rank four tensor, generally written as
-\begin{equation}
-	\chi^{(3)}_{IJKL} = NF \langle \gamma_{ijkl} \rangle
+where $\chi^{(3)}_{IJKL}$ is the $IJKL$ element of the third order electrical susceptibility, a rank four tensor, generally written as
+\begin{equation}\label{eq:nfgamma}
+	\chi^{(3)}_{IJKL} = NF \langle \gamma_{ijkl} \rangle.
 \end{equation}
-where $N$ is a number density, $F$ is the Lorentz local field factor, and $\gamma_{ijkl}$ is the third order polarizability (i.e., second hyperpolarizability). 
-For $j$ input and output fields with frequency $\omega_j$, 
-\begin{equation}
-	F = \prod_j \frac{\left(n(\omega_j)\right)^2 + 1}{3}
-\end{equation}
-where $n(\omega_j)$ is the refractive index at frequency $\omega_j$.\cite{Bedeaux1973}
-The brackets indicate an orientational (or rotational) average.\cite{Andrews1977}
+Here $N$ is a number density and $\gamma_{ijkl}$ is the third-order polarizability (i.e., second hyperpolarizability).
+The brackets indicate an orientational average.\cite{Andrews1977}
 Uppercase letters refer to laboratory frame coordinates and lower case letters refer to corresponding molecular frame coordinates.
+$F=\prod_j \frac{n(\omega_j)^2 + 1}{3}$ is the Lorentz local field factor, where $n$ is the (frequency-dependent) refractive index.
 
@@
 \end{equation}
+% DDK: w_j is not the jth frequency--these terms add with each interaction!  consider indexing delta with w_j
 where: $\mu^{ab}_{j}$ is the $j^{th}$ element of $\mel{a}{\vec{\mu}}{b}$, $\Delta_{kl} = \omega_{kl} - \omega_{j} - i\Gamma_{kl}$, $\omega_j$ is the frequency of the j$^{th}$ input field, $\Gamma_{kl}$ is the dephasing of $\rho_{kl}$ and $\rho_{gg}$ is the ground state population.
@@
 
-When there is no electronic resonance, HDFG has also been referred to as singly vibrationally enhanced (SIVE) spectroscopy. \cite{RN352}
+% DDK: moved SIVE mention to intro
 It is useful to investigate the selection rules without vibronic resonance to understand how HDFG can be used as an upconverted infrared spectroscopy.
@@
 
-\subsection{Time Ordering}
+\subsection{Alternative Time Orderings}
+% DDK: this section uses vibronic labels, but we have not used them yet--is it necessary?
 It is useful to briefly discuss the impact of time ordering on HDFG output.
 Dependent upon the time-ordering schemes, it is possible to eliminate output through destructive interference.
-While we have only isolated one specific HDFG process (\autoref{fig:comparisonwmel}), there are at least fourteen different WMELs which can provide HDFG output in the driven limit. \cite{RN352}
+While we have only isolated one specific HDFG process (\autoref{fig:comparisonwmel}), there are several other pathways which can provide HDFG output. \cite{RN352}
 If $\omega_2$ ($\omega_1$) becomes resonant (non-resonant), where $\omega_2 > \omega_1$, then other HDFG pathways appear (\autoref{fig:sivewmel2}).\cite{McDonnell2024} 
-While the methods in \autoref{fig:sivewmel2} possess identical selection rules to \autoref{fig:comparisonwmel}, the WMEL diagrams presented in \autoref{fig:sivewmel2} will interfere, as they share the same phase-matching condition but have oppositely signed amplitudes.
+While the methods in \autoref{fig:sivewmel2} possess identical selection rules to \autoref{fig:comparisonwmel}, the pathways presented in \autoref{fig:sivewmel2} will interfere, as they have oppositely signed amplitudes.
 \begin{figure*}[!htbp]
@@
 In the limit where $\omega_2+\omega_3$ are detuned from an electronic resonance, it becomes simple to interpret the interference schemes. 
-The case where $\omega_1$ is resonant and $\omega_2 + \omega_3$ are nonresonant yields two contributed diagrams, assuming $\omega_1$ interacts with the system first.
-These WMEL diagrams possess identical phase and transition moments, which yields total constructive interference.
+The case where $\omega_1$ interacts first and is resonant, and $\omega_2 + \omega_3$ are nonresonant, yields two contributed pathways (a) and (b).
+These pathways possess identical phase and transition moments, which yields total constructive interference.
 Conversely, diagrams (c,d) and (e,f), when detuned from an electronic resonance, have identical transition moments but opposite phase. 
@@
 The $A$ term contains the static ($\order{Q^0}$) transitions (i.e., Condon approximation), the $B$ term depends upon $\order{Q}$ transitions (Herzberg-Teller contributions), and the $C$ term depends on $\order{Q^2}$ transitions.
-The C term is suppressed in the following discussion as it depends on one and two photon forbidden transitions, making its contribution to $\gamma_{ijkl}$ two orders of magnitude lesser than $A_{ijk}$.
+The $C$ term is suppressed in the following discussion as it depends on one and two photon forbidden transitions, making its contribution to $\gamma_{ijkl}$ roughly two orders of magnitude lesser than $A_{ijk}$.
 \cite{Ziegler1988, Neddersen1989, Bonang1992}
-Note that some reports obtain $A, B$ coefficients through a Herzberg-Teller expansion of the electronic states to expose vibronic couplings via $\partial H / \partial Q$, where H is the electronic Hamiltonian.\cite{HerzbergTeller1933, Petrov1985, Neddersen1989, Baranov1990}
+Note that some reports obtain $A, B$ coefficients through a Herzberg-Teller expansion of the electronic states to expose vibronic couplings via $\partial H / \partial Q$, where $H$ is the electronic Hamiltonian.\cite{HerzbergTeller1933, Petrov1985, Neddersen1989, Baranov1990}
 This approach is not used here as the expansion of $\vec{M}^{ij}$ in normal mode coordinates provides sufficient physical insight into hyper-Raman selection rules.
@@
 		\begin{split}
-			B_{1_{ijk}} &= \frac{1}{\hbar^2} \sum_{m,e,v',z} M^{ge}_{0,i} \langle v | v' \rangle \left(
-			 \frac{\partial M^{em}_{j}}{\partial Q_z} M^{mg}_{0,k} \mel{v'}{Q_z}{0} 
-			+M^{em}_{0,j} \frac{\partial M^{mg}_{k}}{\partial Q_z} \mel{v'}{Q_z}{0} \right) \frac{1}{\Delta_{ev', g0}}\\
+			B_{1_{ijk}} &= \frac{1}{\hbar^2} \sum_{m,e,v',z} M^{ge}_{0,i} \left(
+				\frac{\partial M^{em}_{j}}{\partial Q_z} M^{mg}_{0,k}  
+				+M^{em}_{0,j} \frac{\partial M^{mg}_{k}}{\partial Q_z}
+			\right)
+			\langle v | v' \rangle \mel{v'}{Q_z}{0} \frac{1}{\Delta_{ev', g0}}\\
 		\end{split}
@@
 \end{widetext}
-where terms such as $\langle a | b \rangle$ and $\mel{a}{Q}{b}$ are Franck-Condon factors and Herzberg-Teller-type integrals, respectively. 
+where $\langle a | b \rangle$ and $\mel{a}{Q}{b}$ are Franck-Condon factors and Herzberg-Teller-type integrals, respectively. 
 At this point, the expressions are valid for both electronically resonant and non-resonant cases.
@@
 
-In HDFG, 
+Using \autoref{eq:nfgamma} and \autoref{sivebeta}, we can write
 \begin{equation}\label{chi3}
-\begin{split}
-		\chi^{(3)}_{IJKL} &= NF \langle \gamma_{ijkl} \rangle = -\frac{NF}{4D \hbar \varepsilon_0 \Delta_{gv}} \langle \beta_{ijk} \mu_l \rangle \rho_{gg}\\
-\end{split}
+		\chi^{(3)}_{IJKL} = -\frac{NF}{4D \hbar \varepsilon_0 \Delta_{gv}} \langle \beta_{ijk} \mu_l \rangle \rho_{gg}\\
 \end{equation}
@@
 \cite{Christie1971, Denisov1986, Kozich2007}
-These quantitative aspects of HDFG could prove useful for examining how well computational methods calculate $\beta_{ijk}$ values and the strength of spontaneous hyper-Raman scattering with non-degenerate pulses.
+These quantitative aspects of HDFG could prove useful for examining how well computational methods calculate $\beta_{ijk}$ values.
 

### 2024-07-29 paper.tex
Update paper.tex

@@
 
-Inspired by recent work that demonstrated the presence of HDFG in ultrafast DOVE and terahertz-IR-visible (TIRV) experiments, we investigate the parameters which result in HDFG output.
-\cite{Bonn2024, McDonnell2024}
-This paper is organized as follows.
-In \autoref{steadystate}, we first identify the selection rules that drives HDFG in the absence of electronic resonance. 
+This paper investigates the microscopic parameters that control HDFG output. \cite{Bonn2024, McDonnell2024}
+In \autoref{steadystate}, we first identify the vibrational selection rules. 
 The selection rules of electronically-resonant HDFG are then identified through a Herzberg-Teller dipole expansion.
@@
 A simple harmonic oscillator model system is used to simulate HDFG spectra and illustrate how the excited state potential energy surface affects the hyper-Raman excitation spectrum.
+% DDK: potentially need to change this sentence, depending on how latter sections are reworked.
 After developing selection rules, the site selective properties, useful experimental aspects of HDFG, and a new scheme to extract the hyper-Raman hyperpolarizability ($\beta_{ijk}$) from HDFG spectra are discussed in \autoref{quant}.
@@
 In $B_1$, the Herzberg-Teller coupling is associated with the two-photon absorption process, whereas in $B_2$, the Herzberg-Teller coupling is associated with one-photon emission.
-As such, $B_1$ contributions to a HDFG spectrum will be sensitive to vibronic coupling between the ground state of a mode and vibrational states on the $|e)$ surface. 
-$B_2$ contributions are sensitive to vibronic coupling between the first excited state of a mode $\ket{g,1}$ and vibrational states on $|e)$.
 
@@
 The steps behind orientational averaging of $\gamma_{ijkl}$, a rank four tensor in the molecular frame, are detailed elsewhere.\cite{Andrews1977, McDonnell2024}
-Briefly, a tensor in the molecular frame, A$_{ijkl}$, is transformed into an element of the same tensor in the laboratory frame, A$_{IJKL}$, through A$_{IJKL}$ = $\theta^{ijkl}_{IJKL} A_{ijkl} = \langle A_{ijkl} \rangle$, where summation over repeated indices is implied and $\theta$ is the transformation operator.
+Briefly, a tensor in the molecular frame, A$_{ijkl}$, is transformed into an element of the same tensor in the laboratory frame, $A_{IJKL}$, through $A_{IJKL}$ = $\theta^{ijkl}_{IJKL} A_{ijkl} = \langle A_{ijkl} \rangle$, where summation over repeated indices is implied and $\theta$ is the transformation operator.
 \cite{McDonnell2024}

### 2024-07-30 paper.tex
more edits

@@
 %Title of paper
-\title{Coherent IR-Hyper-Raman Four Wave Mixing Vibrational Spectroscopy}
+\title{Coherent IR-Hyper-Raman Four Wave Mixing Spectroscopy}
 
@@
 \begin{abstract}
-% DDK: change first sentence, we do not care about vibrational coupling here...
-Nonlinear, four wave mixing vibrational spectroscopies are often used to probe intramolecular vibrational coupling and relaxation dynamics in isotropic media.
+Nonlinear, four wave mixing vibrational spectroscopies are commonly used to probe electron-vibration coupling in isotropic media.
 Most of these methods rely on infrared and/or Raman transitions but methods involving hyper-Raman transitions are also possible. 
 Nonlinear spectroscopy involving hyper-Raman transitions provides a useful analogue to infrared and Raman based nonlinear spectroscopies to understand the structure and dynamics of isotropic systems.
-Hyper-Raman Difference Frequency Generation (HDFG) spectroscopy is an underdeveloped four wave mixing vibrational spectroscopy based on the hyper-Raman transition. 
-% The method is similar in implementation to that of vibrational sum frequency generation (vSFG) and difference frequency generation (vDFG) spectroscopy.
+Hyper Difference Frequency Generation (HDFG) spectroscopy is an underdeveloped four wave mixing vibrational spectroscopy based on the hyper-Raman transition. 
+Unlike other coherent four-wave mixing techniques, HDFG only relies on coupling between a vibrational and electronic state.
 Despite several experimental reports on HDFG, its spectroscopic properties have not been fully explored.  
 To this end, we investigate the selection rules and behavior of HDFG spectroscopy as an upconverted infrared spectroscopy and as a probe of vibronic coupling in molecular systems.
-HDFG shows promise as a method to disentangle vibrational spectra and dynamics in isotropic systems.
-
+HDFG is found to possess selection rules based upon infrared absorption spectroscopy and hyper-Raman scattering, making it sensitive to vibronic coupling mechanisms in isotropic systems. 
+Applying the selection rules found for vibronic hyper-Raman scattering, it is found that HDFG output is dependent upon potential well offset.
+It is found that HDFG and vibrational sum frequency generation (vSFG) spectroscopy share similar output, making HDFG feasible for vSFG practitioners. 
 \end{abstract}
@@
 		Solid and dashed horizontal lines indicate real and virtual states, whereas solid and dotted arrows indicate ket and bra side transitions, respectively. 
+		The red box outlines the e-v coupling techniques (HDFG, HSFG) relevant to this manuscript.
 	}
@@
 The hyper-Raman transition is the nonlinear, two photon analogue to the Raman transition.\cite{Terhune1965, Cyvin1965, Andrews1978}
-Two photons of frequency $\omega_a+\omega_b$ inelastically scatter with matter, promoting or demoting a vibrational mode of frequency $\omega_v$ and emitting a single photon of frequency $\omega_a + \omega_b \mp \omega_v$.
+Two photons of frequency $\omega_a$ and $\omega_b$ inelastically scatter with matter, promoting or demoting a vibrational mode of frequency $\omega_v$ and emitting a single photon of frequency $\omega_a + \omega_b \mp \omega_v$.
+While most hyper-Raman experiments are performed using degenerate input pulses ($\omega_a = \omega_b$), it is possible to perform the technique with non-degenerate input pulses ($\omega_a \neq \omega_b$).
+\cite{Denisov1986, Kozich2007}
 The single photon emission is a significantly different frequency from the excitation frequencies, making rejection of excitation scatter much easier.
-Unlike Raman, all infrared active modes are hyper-Raman active, which allows infrared active modes to be probed through an inelastic scattering event. \cite{Andrews1978}
+Unlike Raman, all infrared active modes are hyper-Raman active, which allows infrared active modes to be probed through a two-photon inelastic scattering event. \cite{Andrews1978}
 One drawback is that hyper-Raman transitions are typically weak compared to their Raman counterparts, even when accounting for the high intensities available to ultrafast pulsed lasers.\cite{RN515, Kelley2010}
@@
 
-Hyper-Raman difference frequency generation (HDFG) spectroscopy and hyper-Raman sum frequency generation (HSFG) spectroscopy are four wave mixing CMDS methods based on direct excitation of a vibrational mode through IR absorption and subsequent scattering to or from the vibrational mode through a hyper-Raman transition.
+Hyper difference frequency generation (HDFG) spectroscopy and hyper sum frequency generation (HSFG) spectroscopy are four wave mixing CMDS methods based on direct excitation of a vibrational mode through IR absorption and subsequent scattering to or from the vibrational mode through a hyper-Raman transition.
 In HDFG/HSFG, an infrared pulse is resonant with a vibrational mode, while two other excitations stimulate the hyper-Raman scattering process.
@@
 \autoref{fig:comparisonwmel} shows both HDFG and HSFG processes and compares them with related spectroscopies that investigate vibrational-electronic coupling.
-The three-wave mixing ($\chi^{(2)}$) techniques are often less applicable as they require macroscopic non-centrosymmetry.\cite{RN227}
+The three-wave mixing ($\chi^{(2)}$) techniques are often less applicable as they require macroscopic non-centrosymmetry under the electric dipole approximation.\cite{RN133}
 Hyper-Raman scattering itself is a six-wave mixing ($\chi^{(5)}$) technique; stimulated hyper-Raman will be weak and susceptible to FWM cascades.\cite{RN515, RN243, Cho2000_Cascade}
@@
 %rpm: not sure what you're trying to say by this
-With the other four-wave mixing techniques (\autoref{fig:comparisonwmel}, second row), the output signal depends on more states than just a single vibrational mode and electronic state (``evx'' coupling).
+With the other four-wave and six-wave mixing techniques (\autoref{fig:comparisonwmel}, second row), the output signal depends on more states than just a single vibrational mode and electronic state (``evx'' coupling).\cite{RN445, RN335}
 As a result, the relationship between the output and vibrational-electronic coupling is more detailed, but also more complicated.
 HDFG, HSFG and Raman are more direct probes of electronic-vibrational coupling.
-Notably, HDFG and HSFG can be implemented as 2-color experiments (with $\omega_2=\omega_3$);\cite{Cho2001} vibrational sum frequency generation (vSFG) or difference frequency generation (vDFG) setups can be trivially reconfigured to perform HSFG or HDFG measurements, respectively, to investigate ev coupling in bulk systems.
+Notably, HDFG and HSFG can be implemented as two-color experiments (with $\omega_2=\omega_3$);\cite{Cho2001} vibrational sum frequency generation (vSFG) or difference frequency generation (vDFG) setups can be trivially reconfigured to perform HSFG or HDFG measurements, respectively, to investigate ev coupling in bulk systems.
 
-When the hyper-Raman excitation is resonant or near-resonant with electronic states, the brightness of the vibrational feature depends on the nature of the electronic state.
-The electronic spectrum can inform on processes that control ultrafast electronic relaxation in molecular and biological systems in similar ways to resonance Raman.\cite{Bredenbeck2015, Arsenault2021}
+When the hyper-Raman excitation is resonant or near-resonant with electronic states, the brightness of the vibrational feature depends on the vibronic structure of the electronic state.
+The electronic spectrum probed in HDFG can inform on processes that control ultrafast electronic relaxation in molecular and biological systems in similar ways to resonance Raman.\cite{Bredenbeck2015, Arsenault2021}
 Since the selection rules of hyper-Raman scattering differ from Raman scattering, the hyper-Raman excitation spectra give a unique alternative to Raman scattering to understand vibrational spectra, electronic structure and vibronic coupling in molecular systems.
@@
 A simple harmonic oscillator model system is used to simulate HDFG spectra and illustrate how the excited state potential energy surface affects the hyper-Raman excitation spectrum.
-% DDK: potentially need to change this sentence, depending on how latter sections are reworked.
-After developing selection rules, the site selective properties, useful experimental aspects of HDFG, and a new scheme to extract the hyper-Raman hyperpolarizability ($\beta_{ijk}$) from HDFG spectra are discussed in \autoref{quant}.
+After developing selection rules, some quantitative aspects of HDFG are discussed in \autoref{quant}.
 The main findings are summarized in \autoref{conclusion}.
@@
 HSFG will not be discussed, but the application of our treatment to HSFG is straightforward and the selection rules are similar.
-We note that HDFG emission can be phase-matched in media with normal dispersion, while HSFG cannot.\cite{RN278}
+We note that HDFG emission can be phase-matched in media with normal dispersion, while HSFG cannot,\cite{RN278} although experimental strategies can be implemented to minimize phase-mismatch in HSFG processes.
+\cite{Kaufman2024}
 
-Before presenting selection rules, we note that a potential interferant in HDFG spectroscopy are direct and sequential cascades of second-order vDFG and vSFG processes.\cite{RN297, RN302, RN301}
+It is useful to briefly discuss the impact of time ordering on HDFG output.
+Dependent upon the time-ordering schemes, it is possible to eliminate output through destructive interference.
+While we have only isolated one specific HDFG resonance and time-ordering scheme (\autoref{fig:comparisonwmel}), there are several other pathways which can provide HDFG output. \cite{RN352}
+If $\omega_2$ becomes resonant and $\omega_1$ becomes non-resonant, where $\omega_2 > \omega_1$, then other HDFG pathways appear (\autoref{fig:sivewmel2}).\cite{McDonnell2024} 
+While the methods in \autoref{fig:sivewmel2} possess identical selection rules to \autoref{fig:comparisonwmel}, the pathways presented in \autoref{fig:sivewmel2} will interfere, which can amplify or obscure coherent output.
+\begin{figure*}[!htbp]
+	\centering
+	\includegraphics[width=6.66 in]{figures/timeorderedwmel.png}
+	\caption{WMEL diagrams of HDFG pathways for when (a,b) $\omega_1$ (black arrow) interacts first and (c-f) $\omega_2$ (orange arrow) interacts first. 
+		The states are labeled as $\ket{a,b}$, where $a$ refers to an electronic state and $b$ refers to quanta in a vibration on $a$, described in \autoref{Albrecht}.
+		In all cases, $\omega_2 > \omega_1$.
+	}
+	\label{fig:sivewmel2}
+\end{figure*}
+
+In the limit where $\omega_2+\omega_3$ is detuned from an electronic resonance, it becomes simple to interpret the interference schemes. 
+The case where $\omega_1$ interacts first and is resonant, and $\omega_2 + \omega_3$ is nonresonant, yields two contributed pathways: \autoref{fig:sivewmel2} (a) and (b).
+These pathways possess identical phase and transition moments, which yields total constructive interference, assuming similar non-resonant dispersion from each pathway.
+Conversely, in the case where only $\omega_2$ is vibrationally resonant, diagrams (c,d) and (e,f), when detuned from an electronic resonance, have identical transition moments but opposite phase. 
+As a result, the output from (c,d) and (e,f) completely destructively interfere; no signal can be obtained from these pathways when significantly detuned. \cite{RN287, McDonnell2024}
+
+When $\omega_2 + \omega_3$ becomes electronically resonant, the interference changes for the \autoref{fig:sivewmel2}c-f pathways.
+Note that in this regime, only pathways (c,e,f) possess identical transition moments.
+As a result, pathways (c,d) survive and can provide output when $\omega_2+\omega_3$ is resonant with an electronic state. 
+These results provide a simple rule of thumb for collecting HDFG spectra: use \autoref{fig:sivewmel2}a,b pathways to measure spectra when significantly detuned from an electronic resonance, and any of these vibrationally resonant pathway can measure spectra when electronically resonant.
+However, since electronic states commonly have short dephasing times and significant inhomogeneous broadening,\cite{Dong2015, Lewis2015} it is likely the \autoref{fig:sivewmel2}f pathway will become triply resonant and possibly contribute greater than the other pathways.
+Such instances are system dependent. 
+Discussion will be isolated to the \autoref{fig:sivewmel2}a pathway in the sections that follow.
+
+Another potential interferant in HDFG spectroscopy is direct and sequential cascades of second-order vDFG and vSFG processes.\cite{RN297, RN301}
 While unimportant in achiral isotropic systems,\cite{Belkin2000} second-order cascades may become important in media where SFG and DFG are allowed, e.g.
@@
 Uppercase letters refer to laboratory frame coordinates and lower case letters refer to corresponding molecular frame coordinates.
-$F=\prod_j \frac{n(\omega_j)^2 + 1}{3}$ is the Lorentz local field factor, where $n$ is the (frequency-dependent) refractive index.
+$F=\prod_j  \frac{1}{3} \left({\left(n(\omega_j)\right)^2 + 1} \right)$ is the Lorentz local field factor, where $n$ is the (frequency dependent) refractive index. \cite{Bedeaux1973}
 
-By propagating density matrix elements in the steady state limit under the rotating wave approximation, the HDFG hyperpolarizability is \cite{RN133}
+By propagating density matrix elements in the steady state limit, the HDFG hyperpolarizability is \cite{RN133}
 \begin{equation}\label{sivegamma}
-		\gamma_{ijkl}^{vg} =	- \sum_{e,m} \frac{1}{\varepsilon_0} \frac{1}{4D} \frac{1}{\hbar^3} \frac{\mu^{ve}_{i} \mu^{em}_{j} \mu^{mg}_{k} \mu^{gv}_{l} }{\Delta_{ev} \Delta_{mv}\Delta_{gv}}  \rho_{gg}
+		\gamma_{ijkl}^{vg} =	- \sum_{e,m} \frac{1}{\varepsilon_0} \frac{1}{4D} \frac{1}{\hbar^3} \frac{\mu^{ve}_{i} \mu^{em}_{j} \mu^{mg}_{k} \mu^{gv}_{l} }{\Delta_{ev}^{3+2-1} \Delta_{mv}^{2-1}\Delta_{gv}^{-1}}  \rho_{gg}
 \end{equation}
-% DDK: w_j is not the jth frequency--these terms add with each interaction!  consider indexing delta with w_j
-where: $\mu^{ab}_{j}$ is the $j^{th}$ element of $\mel{a}{\vec{\mu}}{b}$, $\Delta_{kl} = \omega_{kl} - \omega_{j} - i\Gamma_{kl}$, $\omega_j$ is the frequency of the j$^{th}$ input field, $\Gamma_{kl}$ is the dephasing of $\rho_{kl}$ and $\rho_{gg}$ is the ground state population.
+where: $\mu^{ab}_{j}$ is the $j^{th}$ element of $\mel{a}{\vec{\mu}}{b}$, $\Delta_{kl}^{-x+y+z} = \omega_{kl} - (-\omega_{x}+\omega_{y} + \omega_{z}) - i\Gamma_{kl}$, $\omega_j$ is the frequency of the j$^{th}$ input field, $\Gamma_{kl}$ is the dephasing of $\rho_{kl}$ and $\rho_{gg}$ is the ground state population.
+Here, $\ket{e}$ and $\ket{m}$ are virtual states, and thus necessarily summed over in \autoref{sivegamma}.
+The pulse identifiers on the $\Delta_{kl}$ terms will be suppressed henceforth for simplicity.
 $D$, the Maker-Terhune degeneracy factor, accounts for permutation symmetry of the excitation fields.\cite{RN134} 
@@
 
-% DDK: or should this be "Vibrational Selection Rules"?  Does Placzek == nonresonant?
 \subsection{Vibrational Selection Rules}
 
-% DDK: moved SIVE mention to intro
 It is useful to investigate the selection rules without vibronic resonance to understand how HDFG can be used as an upconverted infrared spectroscopy.
@@
 \end{equation}
-where we have used $\mel{v}{Q_v}{g} \equiv \mel{1}{Q_v}{0} = \sqrt{\frac{\hbar}{2\omega_{vg}}}$ and $\omega_{vg}$ is the characteristic $\ket{0} \rightarrow \ket{1}$ frequency.\cite{RN459}
-Since this expression is non-zero in the harmonic oscillator limit, HDFG output is allowed for normal modes in the harmonic limit.
+where we have used $\mel{1}{\mu_{l,0}}{0} = 0 = \mel{1}{\beta_{ijk,0}}{0}$, and $\mel{v}{Q_v}{g} \equiv \mel{1}{Q_v}{0} = \sqrt{\frac{\hbar}{2\omega_{vg}}}$.
+Here, $\omega_{vg}$ is the characteristic $\ket{0} \rightarrow \ket{1}$ frequency.\cite{RN459}
+Since \autoref{SIVEselection} is non-zero in the harmonic oscillator limit, HDFG output is allowed for infrared active normal modes in the harmonic limit.
 
-\subsection{Alternative Time Orderings}
-% DDK: this section uses vibronic labels, but we have not used them yet--is it necessary?
-It is useful to briefly discuss the impact of time ordering on HDFG output.
-Dependent upon the time-ordering schemes, it is possible to eliminate output through destructive interference.
-While we have only isolated one specific HDFG process (\autoref{fig:comparisonwmel}), there are several other pathways which can provide HDFG output. \cite{RN352}
-If $\omega_2$ ($\omega_1$) becomes resonant (non-resonant), where $\omega_2 > \omega_1$, then other HDFG pathways appear (\autoref{fig:sivewmel2}).\cite{McDonnell2024} 
-While the methods in \autoref{fig:sivewmel2} possess identical selection rules to \autoref{fig:comparisonwmel}, the pathways presented in \autoref{fig:sivewmel2} will interfere, as they have oppositely signed amplitudes.
-\begin{figure*}[!htbp]
-	\centering
-	\includegraphics[width=6.66 in]{figures/timeorderedwmel.png}
-	\caption{WMEL diagrams of HDFG pathways for when (a,b) $\omega_1$ (black arrow) interacts first and (c-f) $\omega_2$ (orange arrow) interacts first. 
-		The states are labeled as $\ket{a,b}$, where $a$ refers to an electronic state and $b$ refers to quanta in a vibration on $a$.
-		In all cases, $\omega_2 > \omega_1$.
-	}
-	\label{fig:sivewmel2}
-\end{figure*}
-
-In the limit where $\omega_2+\omega_3$ are detuned from an electronic resonance, it becomes simple to interpret the interference schemes. 
-The case where $\omega_1$ interacts first and is resonant, and $\omega_2 + \omega_3$ are nonresonant, yields two contributed pathways (a) and (b).
-These pathways possess identical phase and transition moments, which yields total constructive interference.
-Conversely, diagrams (c,d) and (e,f), when detuned from an electronic resonance, have identical transition moments but opposite phase. 
-As a result, the output from (c,d) and (e,f) completely destructively interfere; no signal can be obtained from these pathways when significantly detuned. \cite{RN287, McDonnell2024}
-
-When $\omega_2 + \omega_3$ become electronically resonant, the interference changes for the \autoref{fig:sivewmel2}c-f pathways.
-Note that only pathways (c,e,f) possess identical transition moments.
-As a result, pathways (c,d) survive and can provide output when $\omega_2+\omega_3$ is resonant with an electronic state. 
-These results provide a simple rule of thumb for collecting HDFG spectra: use \autoref{fig:sivewmel2}a,b pathways to measure spectra when significantly detuned from an electronic resonance, and any pathway can measure spectra when electronically resonant.
-However, since electronic states commonly have short dephasing times and have significant inhomogeneous broadening,\cite{Dong2015, Lewis2015} it is likely the \autoref{fig:sivewmel2}f pathway will become triply resonant and possibly contribute greater than the other pathways.
-Such instances are system dependent. 
-For consistency, discussion will be isolated to the \autoref{fig:sivewmel2}a pathway in the sections that follow.
-
-\subsection{Electronically resonant and pre-resonant: Vibronic Selection Rules}
-% TODO: note that the IR dipole selection rule persists here--this is all about w2+w3 resonance
-
+\subsection{Electronically resonant and pre-resonant: Vibronic Selection Rules}\label{Albrecht}
 While the Placzek treatment provides the general source of HDFG output, it does not predict the behavior of $\beta_{ijk}$ as $\omega_2 + \omega_3$ is changed.
 We now explicitly consider electronic resonances through the $A,B,C$ decomposition of $\beta$ introduced by Chung and Ziegler, analogous to those found in Albrecht's treatment of Raman spectroscopy.\cite{Albrecht1961, Ziegler1988}
-To employ this formalism, we write the states in a Born-Oppenheimer basis $\ket{a,b}$, where $\ket{a,b} = |a(Q)) \otimes \ket{b}$ for electronic states $\{|a(Q))\}$ and vibrational states $\{\ket{b}\}$ (i.e., adiabatic approximation).
+To employ this formalism, we write the states in a Born-Oppenheimer basis $\ket{a,b}$, where $\ket{a,b} = |a(Q)) \otimes \ket{b}$ for electronic states $\{|a(Q))\}$ and vibrational states $\{\ket{b}\}$ (i.e., adiabatic approximation), where $Q$ is the adiabatic parameter.
 \cite{BornOppenheimer, Tang1970}
@@
 yields $A, B, C$ coefficients similar to those in the Albrecht formalism of Raman scattering, \cite{Albrecht1961, Warshel1977, Ziegler1988} so that
-\begin{equation}
+\begin{equation}\label{gammaabc}
 		\gamma_{ijkl} \sim \left(A_{ijk} + B_{ijk} + C_{ijk}\right) \frac{\mel{v}{\mu_{l}}{0}} {\Delta_{g0,gv}}
@@
 The $A$ term contains the static ($\order{Q^0}$) transitions (i.e., Condon approximation), the $B$ term depends upon $\order{Q}$ transitions (Herzberg-Teller contributions), and the $C$ term depends on $\order{Q^2}$ transitions.
-The $C$ term is suppressed in the following discussion as it depends on one and two photon forbidden transitions, making its contribution to $\gamma_{ijkl}$ roughly two orders of magnitude lesser than $A_{ijk}$.
+The $C$ term is suppressed in the following discussion as it depends on one and two photon forbidden transitions, making its contribution to $\gamma_{ijkl}$ roughly two orders of magnitude less than $A_{ijk}$.
 \cite{Ziegler1988, Neddersen1989, Bonang1992}
@@
 where $\langle a | b \rangle$ and $\mel{a}{Q}{b}$ are Franck-Condon factors and Herzberg-Teller-type integrals, respectively. 
+Duschinsky rotation effects are ignored in this discussion. \cite{Duschinsky1937}
 At this point, the expressions are valid for both electronically resonant and non-resonant cases.
@@
 By working only in terms of a single normal mode and assuming the infrared pulse selectively excites $\ket{g,0} \rightarrow \ket{g,1}$ (i.e., removing the sum over $z$ and taking $v=1$), 
-% $v' = \{0,1,2\}$, 
 the A and B terms are rewritten as 
@@
 			\begin{split}
-				B_{1_{ijk}} &= \frac{1}{\hbar} \sum_{v'} M^{ge}_{0,i} \langle 1 | v' \rangle 
-				\frac{\partial \Lambda^{eg}_{jk}}{\partial Q} \mel{v'}{Q}{0} 
+				B_{1_{ijk}} &= \frac{1}{\hbar} \sum_{v'} M^{ge}_{0,i}
+				\frac{\partial \Lambda^{eg}_{jk}}{\partial Q} \langle 1 | v' \rangle \mel{v'}{Q}{0} 
 				\frac{1}{\Delta_{ev', g0}}\\
@@
 $\Lambda$ contains the summation over $m$ in \autoref{ABterms} (N.B., here we use $\Lambda^{ab}_{ij} = 1/\hbar \sum_m M_i^{am}M_j^{mb} $).
+Here, we restrict $v' = \{0,1,2\}$ for simplicity.
 
-\autoref{ABterms_DR} shows important selection rules for the vibronic transitions.
-The $A$ term is allowed whenever an electronic transition has a one- and two- photon transition moment.
-The brightness is controlled by vibrational overlap (Franck-Condon factors).
-For centrosymmetric molecules, however, an electronic transition cannot be both one- and two- photon allowed, so the $A$ term will vanish.\cite{Milojevich2013}
-This makes HDFG a unique tool for studying the electronic structure of centrosymmetric species in isotropic media, as it is sensitive to non-Condon effects.\cite{Olson2018}
-In the absence of an $A$ term, the $B$ terms will dominate.
-The $B_1$ and $B_2$ terms involve different types of vibronic coupling pathways.
-In $B_1$, the Herzberg-Teller coupling is associated with the two-photon absorption process, whereas in $B_2$, the Herzberg-Teller coupling is associated with one-photon emission.
-
-\begin{figure*}[!htbp]
-	\centering
-	\includegraphics[width=6.66in]{drsive_spectrum.png}
-	\caption{Contributions of $A, B$ (\autoref{ABterms_DR}) to HDFG spectrum for a simple two harmonic well system.
-		(a) Potential energy surfaces for a two-well system, (b) 1D HDFG spectrum for $\xi = 0.5$, $\omega_1 = \omega_{g1, g0}$. 
-		It is assumed that $\omega_2 = \omega_3$.
-		Note that (b) plots magnitudes of the labeled quantities.
-		The vibrational states on the $|g)$ and $|e)$ manifolds are spaced 2200 cm$^{-1}$ apart, with the vibronic states $\ket{e,v'}$ given linewidths of 700 cm$^{-1}$ and $\hbar \omega_{eg}$ = 30000 cm$^{-1}$.
-		Dotted lines in (b) denote the $v'$ = 0, 1, 2 vibronic resonances. 
-		The vibronic one and two photon absorption operators are scaled such that $\abs{B}/\abs{A} \sim$ 0.1, following Chung and Ziegler. \cite{Ziegler1988}}
-	\label{fig:doubres_spec}
-\end{figure*}
-
-The impact of vibronic coupling in the 2D spectrum is made clear by using a simple model. \cite{Kundu2022}
+The impact of vibronic coupling in the HDFG spectrum is made clear by using a simple model. \cite{Kundu2022}
 Using a two-well system described by 
-\begin{subequations}
+\begin{subequations}\label{Hamiltonian}
 	\begin{equation}
@@
 
+\begin{figure*}[!htbp]
+	\centering
+	\includegraphics[width=6.66in]{drsive_spectrum.png}
+	\caption{Contributions of $A, B$ (\autoref{ABterms_DR}) to HDFG spectrum for a simple two harmonic well system.
+		(a) Potential energy surfaces for a two-well system, (b) 1D HDFG spectrum for $\xi = 0.5$, $\omega_1 = \omega_{g1, g0}$. 
+		It is assumed that $\omega_2 = \omega_3$.
+		Note that (b) plots magnitudes of the labeled quantities.
+		The vibrational states on the $|g)$ and $|e)$ manifolds are spaced 2200 cm$^{-1}$ apart, with the vibronic states $\ket{e,v'}$ given linewidths of 700 cm$^{-1}$ and $\hbar \omega_{eg}$ = 30000 cm$^{-1}$.
+		Dotted lines in (b) denote the $v'$ = 0, 1, 2 vibronic resonances. 
+		The vibronic one and two photon absorption operators are scaled such that $\abs{B}/\abs{A} \sim$ 0.1, following Chung and Ziegler. \cite{Ziegler1988}
+		The Franck-Condon and Herzberg-Teller contributions to each of these terms are found in \autoref{T:contributions}.}
+	\label{fig:doubres_spec}
+\end{figure*}
+
+\autoref{ABterms_DR} shows important selection rules for the vibronic transitions.
+We stress that while the $A,B$ selection rules are based upon any hyper-Raman active mode, the $\mel{v}{\mu_l}{0}$ term in \autoref{gammaabc} imposes the constraint that the $A,B$ transitions occur for infrared active normal mode.
+The $A$ term is allowed whenever an electronic transition has a one- and two- photon transition moment.
+The brightness is controlled by vibrational overlap (Franck-Condon factors).
+Note that in the limit of complete potential energy surface overlap ($\xi \rightarrow 0$), $A$ vanishes as $\lim_{\xi \rightarrow 0} \langle 1 | 0 \rangle = 0$ for potential wells with identical curvature.
+This selection rule is imposed by the dipole transition in HDFG. 
+$B$ does not vanish in the same limit, as $\lim_{\xi \rightarrow 0} \mel{0}{Q}{1} = 1/\sqrt{2}$ for wells with identical curvature.
+For centrosymmetric molecules, an electronic transition cannot be both one- and two- photon allowed by parity, so the $A$ term will vanish.
+This makes HDFG a unique tool for studying the electronic structure of centrosymmetric species in isotropic media, as it is sensitive to non-Condon effects.\cite{Olson2018}
+In the absence of an $A$ term, the $B$ terms will dominate.
+The $B_1$ and $B_2$ terms involve different types of vibronic coupling pathways.
+In $B_1$, the Herzberg-Teller coupling is associated with the two-photon absorption process, whereas in $B_2$, the Herzberg-Teller coupling is associated with one-photon emission.
+
 Simulating the HDFG spectrum for the simple two-well system allows dissection of selection rules and spectral signatures without the need for complex couplings.
 The spectrum selectively probes coupling between the vibronic states and $\ket{g,0}$, $\ket{g,1}$.
-There are two relevant regions of interest: the resonant region (2$\omega_2$ $\in$ [29000, 35000] cm$^{-1}$) and the non-resonant region.
-Focusing far away from the resonant region ($2\omega_2 \sim$ 20000 cm$^{-1}$), the nonresonant $A$ term response is roughly equivalent to that of the resonant $B$ term response. 
 Previous reports suggest that $A$ term contributions may become negligible when significantly detuned from a resonance such that $\Delta_{ev', g0} \approx \Delta_{eg}$, i.e., the resonance denominator loses $\ket{v'}$ dependence.
 \cite{Neddersen1989}
-The lack of $\ket{v'}$ dependence in the resonance denominator would cause $A$ to vanish through closure ($A_{ijk} \sim \sum_{v'} \langle 1|v' \rangle \langle v'|0\rangle$ = $\delta_{10} = 0$).
-However, the simulated spectrum (\autoref{fig:doubres_spec}b) shows a non-negligible $A$ contribution to HDFG output well beyond $\sim$ 20000 cm$^{-1}$, the limit for this model system where $\abs{\omega_{ev',g0} - 2\omega_2} \gg 2\Gamma_{ev',g0}$.
+The lack of $\ket{v'}$ dependence in the resonance denominator causes $A$ to vanish through closure.
+However, the simulated spectrum (\autoref{fig:doubres_spec}b) shows a non-negligible $A$ contribution for $\omega_2 < 20000$ cm$^{-1}$, the limit for this model system where $\abs{\omega_{ev',g0} - 2\omega_2} \gg 2\Gamma_{ev',g0}$.
 In other words, it appears difficult to escape the pre-resonance regime of hyper-Raman scattering.
-As such, it is difficult to eliminate $A$ term resonances in HDFG spectra, even when largely detuned ($\gg 2\Gamma_{ev',g0}$) from the electronic state. 
-This is not unexpected, as when $\abs{\omega_{ev',g0} - 2\omega_2} \gg 2\Gamma_{ev',g0}$, $A_{ijk} \sim \left(2\omega_2 - \omega_{ev',g0}\right)^{-1}$, which slowly converges as $\omega_2 \rightarrow 0$.
 Similar ideas have been seen in spontaneous Raman scattering. \cite{Warshel1977, Li1990, Gong2015}
@@
 
-In the resonant region, the $A$ term contains character from all three possible transitions between $\ket{g,0}$, $\ket{e,v'}$ and $\ket{g,1}$. 
-Significant contributions from $\ket{e,0}$ and $\ket{e,1}$ in the spectrum correspond well with expectations given the relative wavefunction overlap in \autoref{fig:doubres_spec}a. 
-The small contribution to $A$ involving transitions with $\ket{e,2}$ is consistent with the large change in quantum number from $\ket{g,0}$ and its considerable displacement from the equilibrium point of $|g)$.
-The dependence of $A$ on these Franck-Condon factors is in agreement with expectations following \autoref{ABterms_DR}.
+In the resonant region, the $A$ and $B$ terms contain character from all three possible transitions between $\ket{g,0}$, $\ket{e,v'}$ and $\ket{g,1}$. 
+This discussion assumes that mode symmetry allows for coupling between all of the vibronic states considered here.
+Significant contributions from $\ket{e,0}$ and $\ket{e,1}$ in the $A$ term spectrum correspond well with expectations given the relative wavefunction overlap in \autoref{fig:doubres_spec}a, tabulated in \autoref{T:contributions}.
+Similarly, the $B_1$ term is dominated by coupling with the $\ket{e,1}$ state and $B_2$ is dominated by coupling with the $\ket{e,0}$ state (\autoref{T:contributions}). 
+Note that contributions involving $\ket{e,2}$ are suppressed relative to the $\ket{e,0}$ and $\ket{e,1}$ contributions in the $A$ and $B$ terms.
+This is expected, considering the large change in quantum number when involving $\ket{e,2}$ and the offset of the potential wells in \autoref{Hamiltonian}.
 
-Unlike $A$ term contributions, the $B_1$ and $B_2$ terms are dependent upon both Franck-Condon and Herzberg-Teller contributions.
-The $B_1$ term, whose vibronic coupling term is involved in the two-photon absorption event from $|g)$ to $|e)$, seemingly has minimal $0-0$ contributions. 
-This is expected, as the Herzberg-Teller integral $\mel{0}{Q}{0}$ is smaller than $\mel{1}{Q}{0}$ and $\mel{2}{Q}{0}$. 
-An explanation for the contribution from the $0-1$ transition in $B_2$ is similar.
-Vibronic contributions to $B_2$ arise from the one photon emission transition; $\mel{1}{Q}{1}$ is smaller than the $\mel{1}{Q}{0}$ and $\mel{1}{Q}{2}$ contributions to the $B_2$ term.
-However, the $0-2$ transition is smaller in amplitude than the $0-1$ transition because it is also dependent upon a $\langle 2 | 0 \rangle$ Franck-Condon factor.
-In a realistic molecular system, where higher order contributions (e.g.
-Duschinsky rotation) affect vibronic coupling signatures, the spectral signatures will change to incorporate anharmonicites.
-\cite{Duschinsky1937, Carlson1990, Kundu2022}
-Investigating coupling between $\ket{g,2}$ and the same $\ket{e,v'}$ vibronic states will likely assist in dissecting the site-selective electronic spectra.
+\begin{table}[!htbp]
+	\caption{\label{T:contributions} Franck-Condon and/or Herzberg-Teller contributions to $A$, $B_1$, $B_2$ terms between $\ket{g,0}$, $\ket{g,1}$ and vibronic states $\ket{e,0}$, $\ket{e,1}$, $\ket{e,2}$ for \autoref{Hamiltonian} with an offset $\xi = 0.5$.
+	Closed-form expressions for the Franck-Condon and Herzberg-Teller integrals used here have been tabulated by Carlson.\cite{Carlson1988thesis}}
+	\begin{ruledtabular}
+		\begin{tabular}{cccc}
+			Resonance Term & $\ket{e,0}$ & $\ket{e,1}$ & $\ket{e,2}$\\
+			\hline  
+			$A$ 
+			& $\langle 1 | 0 \rangle \langle 0 | 0 \rangle = 0.31 $  
+			& $\langle 1 | 1 \rangle \langle 1 | 0 \rangle = 0.27 $ 
+			& $\langle 1 | 2 \rangle \langle 2 | 0 \rangle = -0.04$\\
 
-\section{Comparisons with Other Spectroscopies}\label{quant}
-Unlike resonant hyper-Raman spectroscopy, which allows transitions between different normal modes of varying quanta, the infrared pulse in the HDFG provides a type of site selectivity,\cite{RN103, Carlson1991} so that only the mode pumped by $\omega_1$ can be involved in vibronic coupling.
-While a typical hyper-Raman experiment can probe similar information by tracking the relative intensity of a mode with different excitation color, hyper-Raman output is incoherent and difficult to detect.
-\cite{Kelley2010}
-Since HDFG output depends upon stimulated hyper-Raman scattering, the output is highly directional, increasing the efficency of detecting hyper-Raman based output. 
-As a result, it is easier to assess changes in intensities and quantify coupling strengths in terms of $\chi^{(3)}$ (\textit{vide infra}).
+			$B_1$ 
+			& $\langle 1 | 0 \rangle \mel{0}{Q}{0} = -0.08$ 
+			& $\langle 1 | 1 \rangle \mel{1}{Q}{0} = 0.48$ 
+			&$\langle 1 | 2 \rangle \mel{2}{Q}{0} = 0.14$\\
 
-HDFG methods can supplement other coherent Raman based methods as a method to investigate vibronic coupling mechanisms between a specific vibration on the ground state and vibrational states on an arbitrary excited state.\cite{RN103}
-The combined infrared and hyper-Raman properties of HDFG make it highly sensitive to molecular electronic structure.
-Particularly in the case of a centrosymmetric species, non-Condon effects dominate in the spectrum as the $A$ term vanishes from the presence of an inversion center.
-The site selective properties of HDFG can allow for parsing of non-Condon effects in different vibrational modes, and extend the use of CMDS to understand the electronic and vibronic structure of simple and complex species.
+			$B_2$ 
+			& $\mel{1}{Q}{0} \langle 0 | 0 \rangle = 0.55$  
+			& $\mel{1}{Q}{1} \langle 1 | 0 \rangle = -0.07$ 
+			& $\mel{1}{Q}{2} \langle 2 | 0 \rangle = 0.08$\\
+		\end{tabular}
+	\end{ruledtabular}
+\end{table}
 
-The hybrid infrared / hyper-Raman properties of HDFG make it an intriguing analogue of resonance IR spectroscopy.
-First demonstrated by Boyle et al., resonance IR uses a $2\vec{k}_1 + \vec{k}_3$ pathway, identical to the TSF pathway in \autoref{fig:comparisonwmel}, to amplify weak infrared modes through vibronic coupling, dependent upon the Raman $A,B,C$ coefficients.
-\cite{RN491}
-However, the $2\vec{k}_1 + \vec{k}_3$ resonance IR method implicitly depends upon the coupling of an overtone $\ket{g,2v}$ to vibronics $\ket{e,v'}$.
-% DDK: did we not already discuss this?  Why is this not the introduction? %rpm: I see this as a place to expand on it since discussion in intro is succinct
-Alternatively, HDFG provides another form of resonance IR spectroscopy, but only requires coupling between $\ket{g,v}$ and $\ket{e,v'}$.
-This form of resonance IR spectroscopy would also uniquely depend upon one and two-photon absorption components, as discussed in terms of the hyper-Raman $A,B$ coefficients.
-By combining resonance IR in the HDFG and $2\vec{k}_1 + \vec{k}_3$ geometries, the sensitivity of the Raman and hyper-Raman $A,B$ coefficients to ground state vibrations and electronic structure can be assessed.
-Such experiments can help assess the quality of computationally calculated ground and excited state potential energy surfaces.
-
+\section{Quantitative Aspects of HDFG}\label{quant}
 Despite their increasing use for dissecting intra and intermolecular interactions, four wave mixing techniques are usually not feasible for most laboratories, as they usually demand the use of multiple optical parametric amplifiers and/or complex acousto-optic modulators.
@@
 \cite{RN362, RN418}
-Most quantitative methods in an n$^{th}$ order CMDS experiment are used to measure $\chi^{(n)}$ values to compare the relative strength of nonlinear processes in different media.
+Most quantitative methods in an $n^{th}$ order CMDS experiment are used to measure $\chi^{(n)}$ values to compare the relative strength of nonlinear processes in different media.
 \cite{Zhu87, RN351, RN345}
 The recorded $\chi^{(n)}$ values provide insight into how microscopic quantities ($\vec{\mu}, \alpha_{ij}, \beta_{ijk}$) impact nonlinear output.
-These quantities are usually measured using their incoherent analogues (IR spectroscopy, spontaneous Raman spectroscopy, spontaneous hyper-Raman spectroscopy). \cite{Levenson1974_2, RN412, Shoute2005}
 
@@
 Coherent vibrational, hyper-Raman coherent four wave mixing spectroscopies are identified and discussed.
-Hyper-Raman difference frequency generation (HDFG) processes, a coherent analogue of infrared spectroscopy, are shown to be non-zero for all harmonically allowed infrared transitions.
-We find that HDFG is always allowed for harmonic transitions, making it a potential tool for measuring single quantum coherence lifetimes. 
-Through an examination of the hyper-Raman $A,B,C$ terms, the impact of electronic resonance and vibronic coupling in HDFG spectrum was examined.
-HDFG possesses types of site-selective properties analogous to those of nanosecond coherent Raman experiments. 
-Site-selective properties should allow for a thorough analysis of vibronic coupling schemes in isotropic systems.
-Due to the triviality of performing HDFG as a two-beam experiment, HDFG is shown to be feasible for practioners of vibrational sum-frequency generation (vSFG) spectroscopy. 
-We show that HDFG can extract the hyper-Raman hyperpolarizability without a need for technically difficult, analytically rigorous hyper-Raman scattering experiments. 
-The HDFG method shows promise as a spectroscopic probe of unique electronic structure effects in a variety of molecular systems, but also for understanding the dynamics of single quantum coherences.
+Hyper difference frequency generation (HDFG) possesses infrared absorption and vibronic hyper-Raman scattering selection rules.
+As a result, HDFG output is sensitive to the relative overlap of potential energy surfaces.
+In HDFG, using the Chung-Ziegler approach to vibronic hyper-Raman scattering, output is dependent upon changes in different potential energy surfaces along the coordinate of the vibrational mode selected by the infrared input.
+If the potential energy surface is not significantly modulated along the vibrational coordinate of interest, then output is dominated by $B$ term resonances, i.e. Herzberg-Teller coupling.
+As a result, HDFG possesses types of site-selective properties analogous to those of coherent Raman experiments, which can allow for a thorough analysis of vibronic coupling schemes in isotropic systems.
+We show that HDFG provides alternative methods to extract the hyper-Raman hyperpolarizability of infrared active vibrations. 
+Since HDFG is approachable as a two-beam experiment, analogous to vibrational sum-frequency generation, and phase-matchable in media with normal dispersion, HDFG should be applicable towards understanding vibrational spectroscopy and dynamics, e.g.
+single quantum coherence free induction decay dynamics, in a variety of relevant molecular and materials systems.
 
@@
 This work received support from the National Science Foundation (Grant no. CHE-2203290).
-R.P.M. acknowledges support from the NSF Graduate Research Fellowship Program (Grant no. DGE-2137424).
+R.P.M. acknowledges support from the National Science Foundation Graduate Research Fellowship Program (Grant no. DGE-2137424).
 
@@
  Such an intensity is easily obtained using modern ultrafast sources.
- In this limit, $P_\text{ratio} \sim 1$.
- Since the intensity ratio scales as $\abs{P_\text{ratio}}^2$, we see that the HDFG output is roughly as strong as vSFG, assuming only interfacial contributions in vSFG.
+ In this limit, $P_\text{ratio} \sim 1$, or the HDFG output is roughly as strong as vSFG, assuming only interfacial contributions in vSFG.
  It is important to note that this calculation assumed negligible dipole and Raman polarizability dependence upon the distance from surface normal, ignored orientational averaging effects, and presumed equivalence of local field factors, all of which can significantly reduce output from either process.
  Nevertheless, since HDFG produces a number of photons similar to that of vSFG, HDFG is a viable technique for investigating bulk systems.
- This method provides practitioners of sum frequency generation the ability to probe isotropic dephasing dynamics without many meaningful changes in their optical setup, and thus compare  dephasing in the bulk and at the interface.\cite{RN224}
+ This method provides practitioners of sum frequency generation the ability to measure spectra and dephasing dynamics in isotropic media without many meaningful changes in their optical setup, and thus compare spectroscopy and dephasing in the bulk and at the interface.\cite{RN224}
 

### 2024-07-30 figures/2D_spec.py

@@ -11,7 +11,7 @@ from matplotlib.patches import FancyArrowPatch
 
 wt.artists.apply_rcparams(kind="publication")
 
-save = True
+save = False
 fontsize = 18
 
 #define harmonic wells and coordinates

### 2024-07-30 paper.tex
generalized A vanishes for arbitrary curvature of harmonic well
and cited myers 1982

@@
 	\begin{equation}
-		H_g = \frac{p^2}{2m} + \frac{1}{2} \hbar \omega q^2
+		H_g = \frac{\hbar \omega }{2} \left(p^2 + q^2 \right)
 	\end{equation}
@@
 	\begin{equation}
-		H_e = \frac{p^2}{2m} + \frac{1}{2} \hbar \omega (q-\xi)^2 +\hbar \omega_{eg}
+		H_e = \frac{\hbar \omega }{2} \left(p^2 +  (q-\xi)^2 \right) + \hbar \omega_{eg}
 	\end{equation}
 \end{subequations}
-for the ground ($H_g$) and first excited ($H_e$) states, where $p$ is the momentum of the normal mode, the A and B contributions can be evaluated using Franck-Condon and Herzberg-Teller integrals tabulated in terms of the dimensionless normal mode $q$ and offset parameter $\xi$ (\autoref{fig:doubres_spec}a).
+for the ground ($H_g$) and first excited ($H_e$) states, where $p$ is the dimensionless momentum of the normal mode, the A and B contributions can be evaluated using Franck-Condon and Herzberg-Teller integrals tabulated in terms of the dimensionless normal mode $q$ and offset parameter $\xi$ (\autoref{fig:doubres_spec}a).
 \cite{Carlson1988thesis}
@@
 The brightness is controlled by vibrational overlap (Franck-Condon factors).
-Note that in the limit of complete potential energy surface overlap ($\xi \rightarrow 0$), $A$ vanishes as $\lim_{\xi \rightarrow 0} \langle 1 | 0 \rangle = 0$ for potential wells with identical curvature.
+Note that in the limit of complete potential energy surface overlap ($\xi \rightarrow 0$), $A$ vanishes as $\lim_{\xi \rightarrow 0} \langle 1 | 0 \rangle = 0$ for harmonic potential wells.\cite{Myers1982}
 This selection rule is imposed by the dipole transition in HDFG. 

### 2024-07-30 paper.tex
small stuff
i'll stop editing until later today

@@
 \end{subequations}
-for the ground ($H_g$) and first excited ($H_e$) states, where $p$ is the dimensionless momentum of the normal mode, the A and B contributions can be evaluated using Franck-Condon and Herzberg-Teller integrals tabulated in terms of the dimensionless normal mode $q$ and offset parameter $\xi$ (\autoref{fig:doubres_spec}a).
+for the ground ($H_g$) and first excited ($H_e$) states, where $p$ (momentum) and $q$ (position) are the dimensionless conjugate coordinates of the normal mode, the A and B contributions can be evaluated using Franck-Condon and Herzberg-Teller integrals tabulated in terms of the dimensionless normal mode $q$ and offset parameter $\xi$ (\autoref{fig:doubres_spec}a).
 \cite{Carlson1988thesis}

### 2024-07-30 paper.tex
added todos
small things to edit at minimum

@@
 
-% By contracting over the virtual vibrational states $\ket{n}$, 
-The $A$ and $B$ coefficients, where $B = B_1 + B_2$, are written as:
+The $A$ and $B$ coefficients, where $B = B_1 + B_2$, following closure over $\ket{n}$ are written as:
 \begin{widetext}
@@
 Note that in the limit of complete potential energy surface overlap ($\xi \rightarrow 0$), $A$ vanishes as $\lim_{\xi \rightarrow 0} \langle 1 | 0 \rangle = 0$ for harmonic potential wells.\cite{Myers1982}
-This selection rule is imposed by the dipole transition in HDFG. 
+This selection rule is imposed by the dipole transition in HDFG. %todo: note this is the OPPOSITE of hyper raman
 $B$ does not vanish in the same limit, as $\lim_{\xi \rightarrow 0} \mel{0}{Q}{1} = 1/\sqrt{2}$ for wells with identical curvature.

### 2024-07-30 paper.tex
Update paper.tex

@@
 Nonlinear, four wave mixing vibrational spectroscopies are commonly used to probe electron-vibration coupling in isotropic media.
-Most of these methods rely on infrared and/or Raman transitions but methods involving hyper-Raman transitions are also possible. 
-Nonlinear spectroscopy involving hyper-Raman transitions provides a useful analogue to infrared and Raman based nonlinear spectroscopies to understand the structure and dynamics of isotropic systems.
-Hyper Difference Frequency Generation (HDFG) spectroscopy is an underdeveloped four wave mixing vibrational spectroscopy based on the hyper-Raman transition. 
-Unlike other coherent four-wave mixing techniques, HDFG only relies on coupling between a vibrational and electronic state.
+Most of these methods rely on infrared and/or Raman transitions, but methods involving hyper-Raman transitions are also possible. 
+Hyper Difference Frequency Generation (HDFG) spectroscopy is an underdeveloped four wave mixing vibrational spectroscopy based on the hyper-Raman transition and IR absorption. 
+HDFG is experimentally similar to vibrational sum frequency generation (vSFG) spectroscopy share similar output, making HDFG feasible for vSFG practitioners. 
 Despite several experimental reports on HDFG, its spectroscopic properties have not been fully explored. 
 To this end, we investigate the selection rules and behavior of HDFG spectroscopy as an upconverted infrared spectroscopy and as a probe of vibronic coupling in molecular systems.
-HDFG is found to possess selection rules based upon infrared absorption spectroscopy and hyper-Raman scattering, making it sensitive to vibronic coupling mechanisms in isotropic systems. 
-Applying the selection rules found for vibronic hyper-Raman scattering, it is found that HDFG output is dependent upon potential well offset.
-It is found that HDFG and vibrational sum frequency generation (vSFG) spectroscopy share similar output, making HDFG feasible for vSFG practitioners. 
+HDFG is shown to a sensitive probe of vibronic coupling in bulk systems.
 \end{abstract}
@@
 
-\subsection{Electronically resonant and pre-resonant: Vibronic Selection Rules}\label{Albrecht}
+\subsection{Vibronic Selection Rules}\label{Albrecht}
 While the Placzek treatment provides the general source of HDFG output, it does not predict the behavior of $\beta_{ijk}$ as $\omega_2 + \omega_3$ is changed.
@@
 At this point, the expressions are valid for both electronically resonant and non-resonant cases.
+For the case of electronic resonance, only a few components of this summation will be relevant ($e,v^\prime$ such that $\Delta_{ev^\prime,g0}$ is small).
 
-For the case of electronic resonance, further simplifications can be made.
-We restrict consideration to electronic transitions between $|g)$ and $|e)$.  
-Note that HDFG experiments selectively excite quanta in ground state vibrational modes. 
-By working only in terms of a single normal mode and assuming the infrared pulse selectively excites $\ket{g,0} \rightarrow \ket{g,1}$ (i.e., removing the sum over $z$ and taking $v=1$), 
-the A and B terms are rewritten as 
+To understand the vibronic structure of electronic resonance, we restrict consideration to electronic transitions between $|g)$ and $|e)$.  
+Note that HDFG experiments selectively excite ground state vibrational modes through $\omega_1$; we will assume the IR beam has excited the fundamental of an IR-active mode so that hyper-Raman scattering is between this mode and the ground state.
+By working only in terms of this single normal mode (i.e., removing the sum over $z$ and taking $v=1$), 
+the $A$ and $B$ terms are rewritten as 
 	\begin{subequations}\label{ABterms_DR}
@@
 	\end{subequations}
-where $\Lambda^{eg}_{0,jk}$ is the electronic two photon transition moment between $g$ and $e$.\cite{McClain1977}
-$\Lambda$ contains the summation over $m$ in \autoref{ABterms} (N.B., here we use $\Lambda^{ab}_{ij} = 1/\hbar \sum_m M_i^{am}M_j^{mb} $).
-Here, we restrict $v' = \{0,1,2\}$ for simplicity.
+where $\Lambda^{ab}_{ij} = 1/\hbar \sum_m M_i^{am}M_j^{mb} $ is the electronic two photon transition moment between $a$ and $b$.\cite{McClain1977}
 
-The impact of vibronic coupling in the HDFG spectrum is made clear by using a simple model. \cite{Kundu2022}
+\autoref{ABterms_DR} shows important selection rules for the vibronic transitions.
+The $A$ term is allowed whenever an electronic transition has a one- and two- photon transition moment.
+For centrosymmetric molecules, an electronic transition cannot be both one- and two- photon allowed by parity, so the $A$ term will vanish.
+This makes HDFG a unique tool for studying the electronic structure of centrosymmetric species in isotropic media, as it is sensitive to non-Condon effects.\cite{Olson2018}
+For an allowed electronic transition, the brightness of a vibronic resonance is controlled by overlap of ground and excited state vibrational wavefunctions (Franck-Condon factors).
+The $A$ term relies on excited state perturbations to the vibrational wavefunctions; if the excited electronic state minimally changes potential energy surface, so that ground and excited state vibrational eigenfunctions are identical, $\langle 1 | v^\prime \rangle \langle v^\prime | 0 \rangle = 0$ and $A$ vanishes.
+%todo: note this is the OPPOSITE of hyper raman 
+Some $B$ terms do survive in the same limit, however; for instance, $B_1$ survives for $v^\prime=1$ and $B_2$ survives for $v^\prime=0$.
+In the absence of an $A$ term, the $B$ terms will dominate.
+The $B_1$ and $B_2$ terms involve different types of vibronic coupling pathways.
+In $B_1$, the Herzberg-Teller coupling is associated with the two-photon absorption process, whereas in $B_2$, the Herzberg-Teller coupling is associated with one-photon emission.
+
+The signatures of vibronic coupling in the HDFG spectrum is made clear by using a simple model.
 Using a two-well system described by 
@@
 \end{subequations}
-for the ground ($H_g$) and first excited ($H_e$) states, where $p$ (momentum) and $q$ (position) are the dimensionless conjugate coordinates of the normal mode, the A and B contributions can be evaluated using Franck-Condon and Herzberg-Teller integrals tabulated in terms of the dimensionless normal mode $q$ and offset parameter $\xi$ (\autoref{fig:doubres_spec}a).
-\cite{Carlson1988thesis}
+for the ground ($H_g$) and first excited ($H_e$) states, where $p$ (momentum) and $q$ (position) are the dimensionless conjugate coordinates of the normal mode, the A and B contributions can be evaluated using Franck-Condon and Herzberg-Teller integrals tabulated in terms of the dimensionless normal mode $q$ and offset parameter $\xi=0.5$ (\autoref{fig:doubres_spec}a).\cite{Carlson1988thesis} % DDK: there is probably a better citation than a thesis.
+Carlson wasn't the first to derive these...
+For simplicity, we restrict consideration to $v^\prime \in \{0,1,2\}$.
 Note that $q = \sqrt{\frac{m^2\omega}{\hbar}} Q$.
-The spectrum is simulated for an electronic state which is both one and two photon allowed.
-A simulated spectrum (\autoref{fig:doubres_spec}b) highlighting the contributions of these terms on potential wells with $\xi = 0.5$ dissects the $A$ and $B$ contributions to the HDFG spectrum.
-This stimulated hyper-Raman type spectrum would be the expected result in a HDFG experiment when investigating the vibronic structure of the electronic state coupled to $\ket{g,1}$.
+We assume the electronic state is both one and two photon allowed.
 
@@
 
-\autoref{ABterms_DR} shows important selection rules for the vibronic transitions.
-We stress that while the $A,B$ selection rules are based upon any hyper-Raman active mode, the $\mel{v}{\mu_l}{0}$ term in \autoref{gammaabc} imposes the constraint that the $A,B$ transitions occur for infrared active normal mode.
-The $A$ term is allowed whenever an electronic transition has a one- and two- photon transition moment.
-The brightness is controlled by vibrational overlap (Franck-Condon factors).
-Note that in the limit of complete potential energy surface overlap ($\xi \rightarrow 0$), $A$ vanishes as $\lim_{\xi \rightarrow 0} \langle 1 | 0 \rangle = 0$ for harmonic potential wells.\cite{Myers1982}
-This selection rule is imposed by the dipole transition in HDFG. %todo: note this is the OPPOSITE of hyper raman
-$B$ does not vanish in the same limit, as $\lim_{\xi \rightarrow 0} \mel{0}{Q}{1} = 1/\sqrt{2}$ for wells with identical curvature.
-For centrosymmetric molecules, an electronic transition cannot be both one- and two- photon allowed by parity, so the $A$ term will vanish.
-This makes HDFG a unique tool for studying the electronic structure of centrosymmetric species in isotropic media, as it is sensitive to non-Condon effects.\cite{Olson2018}
-In the absence of an $A$ term, the $B$ terms will dominate.
-The $B_1$ and $B_2$ terms involve different types of vibronic coupling pathways.
-In $B_1$, the Herzberg-Teller coupling is associated with the two-photon absorption process, whereas in $B_2$, the Herzberg-Teller coupling is associated with one-photon emission.
-
-Simulating the HDFG spectrum for the simple two-well system allows dissection of selection rules and spectral signatures without the need for complex couplings.
-The spectrum selectively probes coupling between the vibronic states and $\ket{g,0}$, $\ket{g,1}$.
-Previous reports suggest that $A$ term contributions may become negligible when significantly detuned from a resonance such that $\Delta_{ev', g0} \approx \Delta_{eg}$, i.e., the resonance denominator loses $\ket{v'}$ dependence.
-\cite{Neddersen1989}
-The lack of $\ket{v'}$ dependence in the resonance denominator causes $A$ to vanish through closure.
-However, the simulated spectrum (\autoref{fig:doubres_spec}b) shows a non-negligible $A$ contribution for $\omega_2 < 20000$ cm$^{-1}$, the limit for this model system where $\abs{\omega_{ev',g0} - 2\omega_2} \gg 2\Gamma_{ev',g0}$.
-In other words, it appears difficult to escape the pre-resonance regime of hyper-Raman scattering.
-Similar ideas have been seen in spontaneous Raman scattering. \cite{Warshel1977, Li1990, Gong2015}
-As such, it may prove difficult to examine non-Condon effects ($B$ term contributions) in HDFG spectra of noncentrosymmetric systems.
-
+\autoref{fig:doubres_spec}b shows the simulated $\omega_2+\omega_3$ spectrum for this two-well system.  The spectrum selectively probes vibronic pathways from $\ket{g,0}$ to $\ket{g,1}$.
 In the resonant region, the $A$ and $B$ terms contain character from all three possible transitions between $\ket{g,0}$, $\ket{e,v'}$ and $\ket{g,1}$. 
-This discussion assumes that mode symmetry allows for coupling between all of the vibronic states considered here.
+% This discussion assumes that mode symmetry allows for coupling between all of the vibronic states considered here.  ddk: there is only one mode!
 Significant contributions from $\ket{e,0}$ and $\ket{e,1}$ in the $A$ term spectrum correspond well with expectations given the relative wavefunction overlap in \autoref{fig:doubres_spec}a, tabulated in \autoref{T:contributions}.
@@
 This is expected, considering the large change in quantum number when involving $\ket{e,2}$ and the offset of the potential wells in \autoref{Hamiltonian}.
+
+In the pre-resonance region, both $A$ and $B$ terms die off as $\sim \Delta_{e0,g0}^{-1}$.
+We point this out because a persistent belief in Raman analysis is that $A$ terms disappear and $B$ terms dominate when significantly detuned from electronic resonance.
+% such that $\Delta_{ev', g0} \approx \Delta_{eg}$, i.e., the resonance denominator loses $\ket{v'}$ dependence. 
+The belief arises from a the approximation $\abs{\omega_{ev',g0} - 2\omega_2} \gg 2\Gamma_{ev',g0}$, which then removes $A$ through a closure relationship.\cite{Neddersen1989}
+As has been discussed elsewhere, however, this approximation is in many cases invalid, especially when vibrational energies are large, like those explored here.\cite{Warshel1977, Li1990, Gong2015}
+This means that it is difficult to isolate $B$ terms when $A$ terms are present.
+As such, HDFG will have difficulty examining non-Condon effects ($B$ term contributions) noncentrosymmetric systems.
 
@@
 		\begin{tabular}{cccc}
-			Resonance Term & $\ket{e,0}$ & $\ket{e,1}$ & $\ket{e,2}$\\
+			$2\omega_2$ Electronic Resonance & $\ket{e,0}$ & $\ket{e,1}$ & $\ket{e,2}$\\
 			\hline  
@@
 \section{Quantitative Aspects of HDFG}\label{quant}
-Despite their increasing use for dissecting intra and intermolecular interactions, four wave mixing techniques are usually not feasible for most laboratories, as they usually demand the use of multiple optical parametric amplifiers and/or complex acousto-optic modulators.
+% Despite their increasing use for dissecting intra and intermolecular interactions, CMDS techniques are usually not feasible for most laboratories, as they usually demand the use of multiple optical parametric amplifiers and/or complex acousto-optic modulators.
 \cite{Chen2016}
-Unlike most four wave mixing techniques, HDFG can be performed using only two input beams (i.e., two color HDFG).
-In the case of two color HDFG, only one tunable infrared optical parametric amplifier is needed, as the oscillator which pumps the infrared OPA can be used to perform the two-photon upconversion needed to generate HDFG output.
-Vibrational sum frequency generation (vSFG) is a $\chi^{(2)}$ technique whose output, when only vibrationally resonant, scales as $\chi^{(2)}_{IJK} \sim \langle \alpha_{ij} \mu_k \rangle$, where $\alpha_{ij}$ is the Raman polarizability tensor, whose phase-matching constraint is  $\vec{k}_3 = \vec{k}_1 + \vec{k}_2$.
-HDFG is phase-matchable under $\vec{k}_4 = -\vec{k}_1 + 2\vec{k}_2$ conditions for most, if not all, vibrational resonances.
-Laboratories which use vSFG to investigate interfacial species at buried interfaces thus have the ingredients necessary to perform a HDFG experiment in a transmission geometry. \cite{Piontek2023_1}
-This would allow vSFG practitioners to perform measurements in the bulk, such as measuring steady-state vibrational spectra, free induction decay and vibrational population lifetimes through HDFG or pump-HDFG-probe.
+% Unlike most four wave mixing techniques, HDFG can be performed using only two input beams (i.e., two color HDFG).
+% In the case of two color HDFG, only one tunable infrared optical parametric amplifier is needed, as the oscillator which pumps the infrared OPA can be used to perform the two-photon upconversion needed to generate HDFG output.
+% Vibrational sum frequency generation (vSFG) is a $\chi^{(2)}$ technique whose output, when only vibrationally resonant, scales as $\chi^{(2)}_{IJK} \sim \langle \alpha_{ij} \mu_k \rangle$, where $\alpha_{ij}$ is the Raman polarizability tensor, whose phase-matching constraint is  $\vec{k}_3 = \vec{k}_1 + \vec{k}_2$.
+% HDFG is phase-matchable under $\vec{k}_4 = -\vec{k}_1 + 2\vec{k}_2$ conditions for most, if not all, vibrational resonances.
+% Laboratories which use vSFG to investigate interfacial species at buried interfaces thus have the ingredients necessary to perform a HDFG experiment in a transmission geometry. \cite{Piontek2023_1}
+% This would allow vSFG practitioners to perform measurements in the bulk, such as measuring steady-state vibrational spectra, free induction decay and vibrational population lifetimes through HDFG or pump-HDFG-probe.
 
-To demonstrate the feasibility of HDFG for vSFG practitioners, we compare the relative output of each process. 
-Macroscopically, oddness in spatial inversion of the vSFG polarization eliminates output from centrosymmetric species under the electric dipole approximation.\cite{RN132, RN133}
-As a result, vSFG output is significantly reduced relative to most third order spectroscopies because it depends on surface number density, many orders of magnitude smaller than the bulk surface density, which is weak even for even for non-linear cross-sections.
-However, HDFG depends upon hyper-Raman cross-sections, which are commonly several orders of magnitude weaker than corresponding Raman transitions.\cite{RN515}
-As calculated in \autoref{appendixA}, these effects cancel, and the output polarization of HDFG and vSFG are roughly identical ($\abs{P_\text{vSFG} / P_\text{HDFG}} \sim 1$).
+\subsection{vSFG detection levels are adequate for HDFG}
+
+Can vSFG experimental setups detect HDFG signals?
+SFG is often consider weak compared to third order spectroscopies because it is usually surface selective,\cite{RN132, RN133} so vSFG detection setups are often quite sensitive.
+However, HDFG is a weak $\chi^{(3)}$ process because it depends upon hyper-Raman cross-sections, which are commonly several orders of magnitude weaker than corresponding Raman transitions.\cite{RN515}
+To evaluate the feasibility of HDFG for vSFG practitioners, we have compared the relative output of each process using nominal parameters. 
+As calculated in \autoref{appendixA}, HDFG's weak $\chi^{(3)}$ value and SFG's low emission cancel somewhat, so that the output polarization of HDFG and vSFG are comparable ($\abs{P_\text{vSFG} / P_\text{HDFG}} \sim 1$).
 Transient HDFG, or IR-pump-HDFG-probe, analogous to IR-pump-vSFG-probe, is therefore also feasible under similar experimental conditions, and provides vSFG practitioners a simple method to measure bulk dynamics without significant changes in an experimental setup.
@@
 
-With the selection rules of HDFG understood for vibrational spectroscopy, and with HDFG generating a large enough output polarization, it becomes possible to obtain quantitative information from its spectra.
-Lineshape analysis is essential for extracting quantitative information from CMDS spectra.
-Scanning across resonances create dispersive lineshapes, i.e, self-heterodyning, which inform on $\Re(\chi^{(3)})$ and $\Im(\chi^{(3)})$.\cite{Levenson1974_1, Levenson1974_2}
-In the method introduced by Levenson and Bloembergen (Bloembergen interferometry experiment), an internal standard interferes with the resonant lineshape.
-Self-heterodyning of the internal standard signal measures $\chi^{(3)}$ and does not require measurement of absolute intensities. 
-Resonant lineshapes are also complicated by amplitude level interference between the sample,  substrate and/or sample cell windows, which must be accounted for to obtain quantitatively correct $\chi^{(3)}$ values.
+% With the selection rules of HDFG understood for vibrational spectroscopy, and with HDFG generating a large enough output polarization, it becomes possible to obtain quantitative information from its spectra.
+% Lineshape analysis is essential for extracting quantitative information from CMDS spectra.
+% Scanning across resonances create dispersive lineshapes, i.e, self-heterodyning, which inform on $\Re(\chi^{(3)})$ and $\Im(\chi^{(3)})$.\cite{Levenson1974_1, Levenson1974_2}
+% In the method introduced by Levenson and Bloembergen (Bloembergen interferometry experiment), an internal standard interferes with the resonant lineshape.
+% Self-heterodyning of the internal standard signal measures $\chi^{(3)}$ and does not require measurement of absolute intensities. 
+% Resonant lineshapes are also complicated by amplitude level interference between the sample,  substrate and/or sample cell windows, which must be accounted for to obtain quantitatively correct $\chi^{(3)}$ values.
 \cite{RN362, RN418}
-Most quantitative methods in an $n^{th}$ order CMDS experiment are used to measure $\chi^{(n)}$ values to compare the relative strength of nonlinear processes in different media.
+% Most quantitative methods in an $n^{th}$ order CMDS experiment are used to measure $\chi^{(n)}$ values to compare the relative strength of nonlinear processes in different media.
 \cite{Zhu87, RN351, RN345}
-The recorded $\chi^{(n)}$ values provide insight into how microscopic quantities ($\vec{\mu}, \alpha_{ij}, \beta_{ijk}$) impact nonlinear output.
+% The recorded $\chi^{(n)}$ values provide insight into how microscopic quantities ($\vec{\mu}, \alpha_{ij}, \beta_{ijk}$) impact nonlinear output.
 
-Compared to $\vec{\mu}$ and $\alpha_{ij}$, it is difficult to calculate $\beta_{ijk}$ values from spontaneous hyper-Raman experiments. \cite{Kelley2010}
-Only a few experimental determinations of $\beta_{ijk}$ for vibrational modes have been performed. \cite{Xu1997, Shoute2005, Kelley2010}
-Methods reported in the literature to measure absolute hyper-Raman polarizabilities depend upon external standards such as hyperpolarizabilities of dissolved samples or two-photon absorption cross sections, also difficult to measure.
-\cite{Okuno2020}
+\subsection{Extraction of hyper-Raman cross-sections}
+
+% DDK: make sure statements are correct here
+Compared to $\vec{\mu}$ and $\alpha_{ij}$, it is difficult to calculate $\beta_{ijk}$ values from spontaneous hyper-Raman experiments.\cite{Kelley2010}
+Only a few experimental determinations of $\beta_{ijk}$ for vibrational modes have been performed.\cite{Xu1997, Shoute2005, Kelley2010}
+Methods reported in the literature to measure absolute hyper-Raman polarizabilities depend upon internal standards such as hyperpolarizabilities of dissolved samples or two-photon absorption cross sections, also difficult to measure.
+\cite{Okuno2020}  % DDK:  correct reference?
 Since the Bloembergen interferometry experiment only relies on the third order susceptibility for measured species (e.g., benzene or CaF$_2$),\cite{Levenson1974_2} it is possible to use quantitative four wave mixing spectroscopy to calculate $\beta_{ijk}$ values.
@@
 The steps behind orientational averaging of $\gamma_{ijkl}$, a rank four tensor in the molecular frame, are detailed elsewhere.\cite{Andrews1977, McDonnell2024}
-Briefly, a tensor in the molecular frame, A$_{ijkl}$, is transformed into an element of the same tensor in the laboratory frame, $A_{IJKL}$, through $A_{IJKL}$ = $\theta^{ijkl}_{IJKL} A_{ijkl} = \langle A_{ijkl} \rangle$, where summation over repeated indices is implied and $\theta$ is the transformation operator.
+Briefly, a tensor in the molecular frame, $A_{ijkl}$, is transformed into an element of the same tensor in the laboratory frame, $\langle A \rangle_{IJKL}$, through $\langle A \rangle_{IJKL}$ = $\theta^{ijkl}_{IJKL} A_{ijkl}$, where summation over repeated indices is implied and $\theta$ is the transformation operator.
 \cite{McDonnell2024}
 Orientational averaging shows specific polarization schemes isolate linear combinations of different $\beta_{ijk}$ terms. \cite{Bersohn1966, Willetts1992, Kauranen1996}
-By using the expansions of $\beta_{ijk}$ and $\mu_{l}$ to $\order{Q_v}$ found earlier, and knowing that $\Re(\chi^{(3)})$ vanishes when resonant, we see
+Substituting in \autoref{SIVEselection}, we see
+% DDK: why does it matter that chi is imaginary?
 \begin{equation}\label{betasive}
-	\left\langle \frac{\partial \beta_{ijk}}{\partial Q_v} {\frac{\partial \mu_l}{\partial Q_v}} \right\rangle = -\frac{8D \varepsilon_0}{NF}  {\Gamma_{gv} \omega_{vg}} {\Im(\chi^{(3)}_{IJKL})}
+	\left\langle \frac{\partial \beta}{\partial Q_v} {\frac{\partial \mu}{\partial Q_v}} \right\rangle _{IJKL} = -\frac{8D \varepsilon_0}{NF}  {\Gamma_{gv} \omega_{vg}} \chi^{(3)}_{IJKL}
 \end{equation}
+$\chi^{3}$ itself can be extracted with use of an internal standard.\cite{Levenson1974_1, Levenson1974_2}
 Since $\abs{\partial \mu / \partial Q}$ values can be extracted from FT-IR spectra,\cite{RN459} HDFG can give quantitative information on the magnitude of $\beta_{ijk}$ for infrared active vibrations.

### 2024-07-31 paper.tex
Update paper.tex

@@
 After developing selection rules, some quantitative aspects of HDFG are discussed in \autoref{quant}.
-The main findings are summarized in \autoref{conclusion}.
 
@@
 Can vSFG experimental setups detect HDFG signals?
-SFG is often consider weak compared to third order spectroscopies because it is usually surface selective,\cite{RN132, RN133} so vSFG detection setups are often quite sensitive.
+SFG setups typically leverage the surface selectivity of $\chi^{(2)}$ polarizations,\cite{RN132, RN133} which results in extremely small emission volumes, so SFG setups are typically quite sensitive.
 However, HDFG is a weak $\chi^{(3)}$ process because it depends upon hyper-Raman cross-sections, which are commonly several orders of magnitude weaker than corresponding Raman transitions.\cite{RN515}
@@
 \end{equation}
-$\chi^{3}$ itself can be extracted with use of an internal standard.\cite{Levenson1974_1, Levenson1974_2}
+$\chi^{(3)}$ itself can be extracted with use of an internal standard.\cite{Levenson1974_1, Levenson1974_2}
 Since $\abs{\partial \mu / \partial Q}$ values can be extracted from FT-IR spectra,\cite{RN459} HDFG can give quantitative information on the magnitude of $\beta_{ijk}$ for infrared active vibrations.

### 2024-07-31 figures/2D_spec.py
As submitted, 07-30-2024

@@ -236,7 +236,7 @@ if others:
 
 for i, ax in enumerate(fig.axes):
     # ax.grid(visible=True, color="k", lw=0.5, linestyle=":")
-    wt.artists.corner_text("abcd"[i], ax=ax, corner = 'UL', distance = 0.25, bbox = True, fontsize = fontsize, background_alpha=0.75)
+    wt.artists.corner_text("abcd"[i], ax=ax, corner = 'UL', distance = 0.35, bbox = True, fontsize = fontsize, background_alpha=0.75)
 
 if save:
     wt.artists.savefig("drsive_spectrum.png", transparent = True, bbox_inches='tight')

### 2024-08-29 paper.tex
some words

@@
-\documentclass[aip, jcp, reprint, onecolumn]{revtex4-2}
+\documentclass[aip, jcp, reprint, onecolumn, nofootinbib]{revtex4-2}
 
@@
 \autoref{fig:comparisonwmel} shows both HDFG and HSFG processes and compares them with related spectroscopies that investigate vibrational-electronic coupling.
-The three-wave mixing ($\chi^{(2)}$) techniques are often less applicable as they require macroscopic non-centrosymmetry under the electric dipole approximation.\cite{RN133}
-Hyper-Raman scattering itself is a six-wave mixing ($\chi^{(5)}$) technique; stimulated hyper-Raman will be weak and susceptible to FWM cascades.\cite{RN515, RN243, Cho2000_Cascade}
-A coherent six-wave mixing analogue of hyper-Raman scattering, coherent anti-Stokes hyper-Raman spectroscopy (CAHRS), has been proposed and explored theoretically by several authors; however, it is also highly susceptible to FWM cascades.\cite{Berger1978, Bjarnason1980, Cho1997, Cho1998}
+The three-wave mixing ($\chi^{(2)}$) techniques are often less applicable as they require macroscopic non-centrosymmetry under the electric dipole approximation.\cite{Shen94}
+Hyper-Raman scattering itself is a six-wave mixing ($\chi^{(5)}$) technique; stimulated hyper-Raman will be weak and susceptible to four-wave mixing (FWM) cascades.\cite{RN515, RN243, Cho2000_Cascade}
+A coherent six-wave mixing analogue of hyper-Raman scattering, coherent anti-Stokes hyper-Raman spectroscopy (CAHRS), has been proposed and explored theoretically by several authors; however, it is also weak and highly susceptible to FWM cascades.\cite{Berger1978, Bjarnason1980, Cho1997, Cho1998}
 Of the many four-wave mixing techniques, HDFG and HSFG have strong similarity to Raman, stimulated Raman, and RISRS in that the electronic state must remove or add a $v$ quantum to the ground state (``ev'' coupling).
-%rpm: not sure what you're trying to say by this
 With the other four-wave and six-wave mixing techniques (\autoref{fig:comparisonwmel}, second row), the output signal depends on more states than just a single vibrational mode and electronic state (``evx'' coupling).\cite{RN445, RN335}
@@
 
-When the hyper-Raman excitation is resonant or near-resonant with electronic states, the brightness of the vibrational feature depends on the vibronic structure of the electronic state.
-The electronic spectrum probed in HDFG can inform on processes that control ultrafast electronic relaxation in molecular and biological systems in similar ways to resonance Raman.\cite{Bredenbeck2015, Arsenault2021}
+When the hyper-Raman excitation in HDFG or HSFG is resonant or near-resonant with electronic states, the brightness of the vibrational feature depends on the vibronic structure of the electronic state.
+The electronic spectrum probed in HDFG or HSFG can inform on processes that control ultrafast electronic relaxation in molecular and biological systems in similar ways to resonance Raman.\cite{Cho2001, Bredenbeck2015, Arsenault2021}
 Since the selection rules of hyper-Raman scattering differ from Raman scattering, the hyper-Raman excitation spectra give a unique alternative to Raman scattering to understand vibrational spectra, electronic structure and vibronic coupling in molecular systems.
@@
 
+\section{Density Matrix Propagation}
+In the cases discussed in the introduction, the proposed HDFG spectroscopy method is used to probe vibronic coupling.
+Coherent spectroscopies are often described using the density-matrix formalism, where a density matrix $\rho$ is propagated using the Liouville-von Neumann equation as
+\begin{equation}
+	\dot{\rho} = \frac{1}{i \hbar} [H_0 + H(t), \rho] + \dot{\rho}_R,
+\end{equation}
+where $H_0$ is system Hamiltonian, $H(t)$ is the time-dependent, matter-radiation interaction Hamiltonian and $\rho_R$ is the relaxation density matrix. 
+In most treatments of coherent vibrational spectroscopy, it is sufficient to write $\dot{\rho}_R = \Gamma \rho$, i.e.
+exponential relaxation (Markovian dynamics), where $\Gamma$ is the system's pure dephasing rate.
+\cite{RN455, RN307}
+
 \section{Selection Rules for HDFG Spectroscopy}\label{steadystate}
@@
 HSFG will not be discussed, but the application of our treatment to HSFG is straightforward and the selection rules are similar.
-We note that HDFG emission can be phase-matched in media with normal dispersion, while HSFG cannot,\cite{RN278} although experimental strategies can be implemented to minimize phase-mismatch in HSFG processes.
+We note that HDFG emission can be phase-matched in media with normal dispersion, while HSFG cannot,\cite{RN278} although experimental strategies can be implemented to minimize phase-mismatch in HSFG experiments.
 \cite{Kaufman2024}
@@
 It is useful to briefly discuss the impact of time ordering on HDFG output.
-Dependent upon the time-ordering schemes, it is possible to eliminate output through destructive interference.
+Dependent upon the time-ordering schemes, it is possible to eliminate output through destructive interference.\cite{RN287}
 While we have only isolated one specific HDFG resonance and time-ordering scheme (\autoref{fig:comparisonwmel}), there are several other pathways which can provide HDFG output. \cite{RN352}
@@
 As a result, the output from (c,d) and (e,f) completely destructively interfere; no signal can be obtained from these pathways when significantly detuned. \cite{RN287, McDonnell2024}
+Note that in the case where $\omega_1$ interacts first but $\omega_2$ is resonant, the nonlinear output generated nearly vanishes as the first resonant pulse arrives after a non-resonant pulse.
 
@@
 
-It is useful to expose relationships between nonlinear output, transition dipoles and hyper-Raman hyperpolarizabilities in the driven limit. \cite{Simpson2004}
+It is useful to expose relationships between nonlinear output, transition dipoles and hyper-Raman hyperpolarizabilities in the driven limit. \cite{Simpson2004, Moad2005}
 Under the electric dipole approximation, the $I^\text{th}$ cartesian component of the third order nonlinear output polarization, ${P}^{(3)}_I$, of a four wave mixing process, induced by electric fields $E_J$, $E_K$, and $E_L$ at output frequency $\omega_4=-\omega_1 + \omega_2 + \omega_3$ is written as (using Einstein summation) \cite{RN307}
@@
 We now explicitly consider electronic resonances through the $A,B,C$ decomposition of $\beta$ introduced by Chung and Ziegler, analogous to those found in Albrecht's treatment of Raman spectroscopy.\cite{Albrecht1961, Ziegler1988}
-To employ this formalism, we write the states in a Born-Oppenheimer basis $\ket{a,b}$, where $\ket{a,b} = |a(Q)) \otimes \ket{b}$ for electronic states $\{|a(Q))\}$ and vibrational states $\{\ket{b}\}$ (i.e., adiabatic approximation), where $Q$ is the adiabatic parameter.
+To employ this formalism, we write the states in a Born-Oppenheimer basis $\ket{a,b}$, where $\ket{a,b} = |a(Q)) \otimes \ket{b}$ for electronic states $\{|a(\textbf{Q}))\}$ and vibrational states $\{\ket{b}\}$ (i.e., adiabatic approximation), where \textbf{Q}, the system normal modes, is the adiabatic parameter.
 \cite{BornOppenheimer, Tang1970}
-We will henceforth suppress the dependence of the electronic states on $Q$ for simplicity.
+We will henceforth suppress the dependence of the electronic states on \textbf{Q} for simplicity.
 
@@
 		R_{l}^{g0,gv} 
-	}{\Delta_{g0,gv}
-		\Delta_{ev', mn}
-		\Delta_{mn, g0}
+	}{	\Delta_{ev', gv}
+		\Delta_{mn, gv}
+		\Delta_{g0,gv}
 	}
@@
 where $R_{i}^{ab,cd}$ is the i$^{th}$ element of $\mel{a,b}{\vec{R}}{c,d}$.
-It is common in the hyper-Raman community to write $\Delta_{ev', mn} \Delta_{mn, g0} = \Delta_{ev', g0}$.
+It is common in the hyper-Raman literature to write $\Delta_{ev', gv} \Delta_{mn, gv} = \Delta_{ev', gv}$.
 Using our definition of vibronic states, we can write, for example,
-$R_{i}^{gv,ev'} = \mel{v}{M_i^{ge}}{v'}$, where $\vec{M}_{ab} = (a|\vec{R}|b)$.\cite{Ziegler1974}
+$R_{i}^{gv,ev'} = \mel{v}{M_i^{ge}}{v'}$, where $\vec{M}^{ab} = (a|\vec{R}|b)$.\cite{Ziegler1974}
 Expanding $\vec{M}^{ij}$ to $\order{Q}$ about the equilibrium point of the ground state potential surface as
@@
 \end{equation}
-The $A$ term contains the static ($\order{Q^0}$) transitions (i.e., Condon approximation), the $B$ term depends upon $\order{Q}$ transitions (Herzberg-Teller contributions), and the $C$ term depends on $\order{Q^2}$ transitions.
+The $A$ term contains the static ($\order{Q^0}$) transitions (i.e., Condon approximation), the $B$ term depends upon $\order{Q}$ transitions (Herzberg-Teller contributions), and the $C$ term depends on $\order{Q_i Q_j}$ transitions.
 The $C$ term is suppressed in the following discussion as it depends on one and two photon forbidden transitions, making its contribution to $\gamma_{ijkl}$ roughly two orders of magnitude less than $A_{ijk}$.
@@
 
-The $A$ and $B$ coefficients, where $B = B_1 + B_2$, following closure over $\ket{n}$ are written as:
+The $A$ and $B$ coefficients, where $B = B_1 + B_2$, following closure over $\ket{n}$,\cite{Milojevich2013} are written as:
 \begin{widetext}
@@
 		 \langle v' | 0 \rangle 
-		 \frac{1}{\Delta_{ev', g0}}
+		 \frac{1}{\Delta_{ev', gv}}
 		 \\
@@
 			\right)
-			\langle v | v' \rangle \mel{v'}{Q_z}{0} \frac{1}{\Delta_{ev', g0}}\\
+			\langle v | v' \rangle \mel{v'}{Q_z}{0} \frac{1}{\Delta_{ev', gv}}\\
 		\end{split}
@@
 			\langle v' | 0 \rangle 
-			\frac{1}{\Delta_{ev', g0}}
+			\frac{1}{\Delta_{ev', gv}}
 	\end{split}
@@
 At this point, the expressions are valid for both electronically resonant and non-resonant cases.
-For the case of electronic resonance, only a few components of this summation will be relevant ($e,v^\prime$ such that $\Delta_{ev^\prime,g0}$ is small).
 
@@
 				\langle v' | 0 \rangle 
-				\frac{1}{\Delta_{ev',g0}}
+				\frac{1}{\Delta_{ev',gv}}
 				\\
@@
 				\frac{\partial \Lambda^{eg}_{jk}}{\partial Q} \langle 1 | v' \rangle \mel{v'}{Q}{0} 
-				\frac{1}{\Delta_{ev', g0}}\\
+				\frac{1}{\Delta_{ev', gv}}\\
 			\end{split}
@@
 				\langle v' | 0 \rangle 
-				\frac{1}{\Delta_{ev',g0}}
+				\frac{1}{\Delta_{ev',gv}}
 			\end{split}
@@
 where $\Lambda^{ab}_{ij} = 1/\hbar \sum_m M_i^{am}M_j^{mb} $ is the electronic two photon transition moment between $a$ and $b$.\cite{McClain1977}
-
-\autoref{ABterms_DR} shows important selection rules for the vibronic transitions.
-The $A$ term is allowed whenever an electronic transition has a one- and two- photon transition moment.
-For centrosymmetric molecules, an electronic transition cannot be both one- and two- photon allowed by parity, so the $A$ term will vanish.
-This makes HDFG a unique tool for studying the electronic structure of centrosymmetric species in isotropic media, as it is sensitive to non-Condon effects.\cite{Olson2018}
-For an allowed electronic transition, the brightness of a vibronic resonance is controlled by overlap of ground and excited state vibrational wavefunctions (Franck-Condon factors).
-The $A$ term relies on excited state perturbations to the vibrational wavefunctions; if the excited electronic state minimally changes potential energy surface, so that ground and excited state vibrational eigenfunctions are identical, $\langle 1 | v^\prime \rangle \langle v^\prime | 0 \rangle = 0$ and $A$ vanishes.
-%todo: note this is the OPPOSITE of hyper raman 
-Some $B$ terms do survive in the same limit, however; for instance, $B_1$ survives for $v^\prime=1$ and $B_2$ survives for $v^\prime=0$.
-In the absence of an $A$ term, the $B$ terms will dominate.
-The $B_1$ and $B_2$ terms involve different types of vibronic coupling pathways.
-In $B_1$, the Herzberg-Teller coupling is associated with the two-photon absorption process, whereas in $B_2$, the Herzberg-Teller coupling is associated with one-photon emission.
-
-The signatures of vibronic coupling in the HDFG spectrum is made clear by using a simple model.
-Using a two-well system described by 
-\begin{subequations}\label{Hamiltonian}
-	\begin{equation}
-		H_g = \frac{\hbar \omega }{2} \left(p^2 + q^2 \right)
-	\end{equation}
-	and
-	\begin{equation}
-		H_e = \frac{\hbar \omega }{2} \left(p^2 +  (q-\xi)^2 \right) + \hbar \omega_{eg}
-	\end{equation}
-\end{subequations}
-for the ground ($H_g$) and first excited ($H_e$) states, where $p$ (momentum) and $q$ (position) are the dimensionless conjugate coordinates of the normal mode, the A and B contributions can be evaluated using Franck-Condon and Herzberg-Teller integrals tabulated in terms of the dimensionless normal mode $q$ and offset parameter $\xi=0.5$ (\autoref{fig:doubres_spec}a).\cite{Carlson1988thesis} % DDK: there is probably a better citation than a thesis.
-Carlson wasn't the first to derive these...
-For simplicity, we restrict consideration to $v^\prime \in \{0,1,2\}$.
-Note that $q = \sqrt{\frac{m^2\omega}{\hbar}} Q$.
-We assume the electronic state is both one and two photon allowed.
 
@@
 
+The signatures of vibronic coupling in the HDFG spectrum are made clear by using a simple model.
+Using a two-well system described by 
+\begin{subequations}\label{Hamiltonian}
+	\begin{equation}
+		H_g = \frac{\hbar \omega }{2} \left(p^2 + q^2 \right)
+	\end{equation}
+	and
+	\begin{equation}
+		H_e = \frac{\hbar \omega }{2} \left(p^2 +  (q-\xi)^2 \right) + \hbar \omega_{eg}
+	\end{equation}
+\end{subequations}
+for the ground ($H_g$) and first excited ($H_e$) states, where $p$ (momentum) and $q$ (position) are the dimensionless conjugate coordinates of the normal mode, the A and B contributions can be evaluated using Franck-Condon and Herzberg-Teller integrals tabulated in terms of the dimensionless normal mode $q$ and offset parameter $\xi$ (\autoref{fig:doubres_spec}a).\cite{Carlson1988thesis}
+For simplicity, we restrict consideration to $v^\prime \in \{0,1,2\}$ and take $\xi = 0.5$.
+Note that $q = \sqrt{\frac{m^2\omega}{\hbar}} Q$.
+We assume the electronic state is both one and two photon allowed.
+
+\autoref{ABterms_DR} shows important selection rules for the vibronic transitions.
+The $A$ term is allowed whenever an electronic transition has a one- and two- photon transition moment.
+For centrosymmetric molecules, an electronic transition cannot be both one- and two- photon allowed by parity, so the $A$ term will vanish.
+This makes HDFG a unique tool for studying the electronic structure of centrosymmetric species in isotropic media, as it is sensitive to non-Condon effects.\cite{Olson2018}
+For an allowed electronic transition, the brightness of a vibronic resonance is controlled by overlap of ground and excited state vibrational wavefunctions (Franck-Condon factors).
+The $A$ term relies on excited state perturbations to the vibrational wavefunctions; if the excited electronic state minimally changes potential energy surface, so that ground and excited state vibrational eigenfunctions are identical, $\langle 1 | v^\prime \rangle \langle v^\prime | 0 \rangle = 0$ and $A$ vanishes.
+This follows from $\lim_{\xi \rightarrow 0} \langle v' | 0 \rangle = 0$, $v^\prime \neq 0$, for wells with identical curvature.
+Some $B$ terms do survive in the same limit, however; for instance, $B_1$ survives for $v^\prime=1$ and $B_2$ survives for $v^\prime=0$.
+In the absence of an $A$ term, the $B$ terms will dominate.
+The $B_1$ and $B_2$ terms involve different types of vibronic coupling pathways.
+In $B_1$, the Herzberg-Teller coupling is associated with the two-photon absorption process, whereas in $B_2$, the Herzberg-Teller coupling is associated with one-photon emission.
+
 \autoref{fig:doubres_spec}b shows the simulated $\omega_2+\omega_3$ spectrum for this two-well system.  The spectrum selectively probes vibronic pathways from $\ket{g,0}$ to $\ket{g,1}$.
 In the resonant region, the $A$ and $B$ terms contain character from all three possible transitions between $\ket{g,0}$, $\ket{e,v'}$ and $\ket{g,1}$. 
-% This discussion assumes that mode symmetry allows for coupling between all of the vibronic states considered here.  ddk: there is only one mode!
 Significant contributions from $\ket{e,0}$ and $\ket{e,1}$ in the $A$ term spectrum correspond well with expectations given the relative wavefunction overlap in \autoref{fig:doubres_spec}a, tabulated in \autoref{T:contributions}.
@@
 
-In the pre-resonance region, both $A$ and $B$ terms die off as $\sim \Delta_{e0,g0}^{-1}$.
+In the pre-resonance region, both $A$ and $B$ terms die off as $\sim \Delta_{e0,gv}^{-1}$.
 We point this out because a persistent belief in Raman analysis is that $A$ terms disappear and $B$ terms dominate when significantly detuned from electronic resonance.
 % such that $\Delta_{ev', g0} \approx \Delta_{eg}$, i.e., the resonance denominator loses $\ket{v'}$ dependence. 
-The belief arises from a the approximation $\abs{\omega_{ev',g0} - 2\omega_2} \gg 2\Gamma_{ev',g0}$, which then removes $A$ through a closure relationship.\cite{Neddersen1989}
+The belief arises from the approximation $\abs{\omega_{ev',gv} - 2\omega_2} \gg 2\Gamma_{ev',gv}$, which then removes $A$ through a closure relationship.\cite{Neddersen1989}
 As has been discussed elsewhere, however, this approximation is in many cases invalid, especially when vibrational energies are large, like those explored here.\cite{Warshel1977, Li1990, Gong2015}
@@
 	\caption{\label{T:contributions} Franck-Condon and/or Herzberg-Teller contributions to $A$, $B_1$, $B_2$ terms between $\ket{g,0}$, $\ket{g,1}$ and vibronic states $\ket{e,0}$, $\ket{e,1}$, $\ket{e,2}$ for \autoref{Hamiltonian} with an offset $\xi = 0.5$.
-	Closed-form expressions for the Franck-Condon and Herzberg-Teller integrals used here have been tabulated by Carlson.\cite{Carlson1988thesis}}
+	Closed-form expressions for the Franck-Condon and Herzberg-Teller integrals used here have been tabulated by Carlson.\cite{Carlson1988thesis}}\footnote{The Herzberg-Teller Integrals 
 	\begin{ruledtabular}
@@
 % Unlike most four wave mixing techniques, HDFG can be performed using only two input beams (i.e., two color HDFG).
-% In the case of two color HDFG, only one tunable infrared optical parametric amplifier is needed, as the oscillator which pumps the infrared OPA can be used to perform the two-photon upconversion needed to generate HDFG output.
-% Vibrational sum frequency generation (vSFG) is a $\chi^{(2)}$ technique whose output, when only vibrationally resonant, scales as $\chi^{(2)}_{IJK} \sim \langle \alpha_{ij} \mu_k \rangle$, where $\alpha_{ij}$ is the Raman polarizability tensor, whose phase-matching constraint is  $\vec{k}_3 = \vec{k}_1 + \vec{k}_2$.
-% HDFG is phase-matchable under $\vec{k}_4 = -\vec{k}_1 + 2\vec{k}_2$ conditions for most, if not all, vibrational resonances.
-% Laboratories which use vSFG to investigate interfacial species at buried interfaces thus have the ingredients necessary to perform a HDFG experiment in a transmission geometry. \cite{Piontek2023_1}
-% This would allow vSFG practitioners to perform measurements in the bulk, such as measuring steady-state vibrational spectra, free induction decay and vibrational population lifetimes through HDFG or pump-HDFG-probe.
+%
 
@@
 However, HDFG is a weak $\chi^{(3)}$ process because it depends upon hyper-Raman cross-sections, which are commonly several orders of magnitude weaker than corresponding Raman transitions.\cite{RN515}
+Since HDFG can be performed as a two-beam experiment, it is useful to identify whether vSFG and HDFG responses are similar to quantify hyper-Raman-based FWM response from bulk, isotropic systems.
 To evaluate the feasibility of HDFG for vSFG practitioners, we have compared the relative output of each process using nominal parameters. 
@@
 
-% With the selection rules of HDFG understood for vibrational spectroscopy, and with HDFG generating a large enough output polarization, it becomes possible to obtain quantitative information from its spectra.
-% Lineshape analysis is essential for extracting quantitative information from CMDS spectra.
-% Scanning across resonances create dispersive lineshapes, i.e, self-heterodyning, which inform on $\Re(\chi^{(3)})$ and $\Im(\chi^{(3)})$.\cite{Levenson1974_1, Levenson1974_2}
-% In the method introduced by Levenson and Bloembergen (Bloembergen interferometry experiment), an internal standard interferes with the resonant lineshape.
-% Self-heterodyning of the internal standard signal measures $\chi^{(3)}$ and does not require measurement of absolute intensities. 
-% Resonant lineshapes are also complicated by amplitude level interference between the sample,  substrate and/or sample cell windows, which must be accounted for to obtain quantitatively correct $\chi^{(3)}$ values.
-\cite{RN362, RN418}
-% Most quantitative methods in an $n^{th}$ order CMDS experiment are used to measure $\chi^{(n)}$ values to compare the relative strength of nonlinear processes in different media.
-\cite{Zhu87, RN351, RN345}
-% The recorded $\chi^{(n)}$ values provide insight into how microscopic quantities ($\vec{\mu}, \alpha_{ij}, \beta_{ijk}$) impact nonlinear output.
+\subsection{Extraction of hyper-Raman hyperpolarizability}
 
-\subsection{Extraction of hyper-Raman cross-sections}
-
-% DDK: make sure statements are correct here
-Compared to $\vec{\mu}$ and $\alpha_{ij}$, it is difficult to calculate $\beta_{ijk}$ values from spontaneous hyper-Raman experiments.\cite{Kelley2010}
+Compared to $\vec{\mu}$ and $\alpha_{ij}$, it is difficult to measure $\beta_{ijk}$ values through spontaneous hyper-Raman experiments.\cite{Kelley2010}
 Only a few experimental determinations of $\beta_{ijk}$ for vibrational modes have been performed.\cite{Xu1997, Shoute2005, Kelley2010}
 Methods reported in the literature to measure absolute hyper-Raman polarizabilities depend upon internal standards such as hyperpolarizabilities of dissolved samples or two-photon absorption cross sections, also difficult to measure.
-\cite{Okuno2020}  % DDK:  correct reference?
-Since the Bloembergen interferometry experiment only relies on the third order susceptibility for measured species (e.g., benzene or CaF$_2$),\cite{Levenson1974_2} it is possible to use quantitative four wave mixing spectroscopy to calculate $\beta_{ijk}$ values.
+\cite{Kelley2010}
+In the method introduced by Levenson and Bloembergen (Bloembergen interferometry experiment), an internal standard interferes with the resonant lineshape of a $\chi^{(3)}$ process.
+\cite{Levenson1974_1, Levenson1974_2}
+Self-heterodyning of the internal standard signal measures $\chi^{(3)}$ and does not require measurement of absolute intensities. 
+Since the Bloembergen interferometry experiment only relies on the third order susceptibility for measured species (e.g., benzene or CaF$_2$),\cite{Levenson1974_2} it is possible to use quantitative four wave mixing spectroscopy to calculate $\beta_{ijk}$ values for infrared active vibrations.
 It is thus useful to investigate how a treatment of orientational averaging can extract $\beta_{ijk}$ from the HDFG $\chi^{(3)}_{IJKL}$ expression.
@@
 Briefly, a tensor in the molecular frame, $A_{ijkl}$, is transformed into an element of the same tensor in the laboratory frame, $\langle A \rangle_{IJKL}$, through $\langle A \rangle_{IJKL}$ = $\theta^{ijkl}_{IJKL} A_{ijkl}$, where summation over repeated indices is implied and $\theta$ is the transformation operator.
-\cite{McDonnell2024}
+\cite{McDonnell2024, Andrews1977}
 Orientational averaging shows specific polarization schemes isolate linear combinations of different $\beta_{ijk}$ terms. \cite{Bersohn1966, Willetts1992, Kauranen1996}
 Substituting in \autoref{SIVEselection}, we see
-% DDK: why does it matter that chi is imaginary?
 \begin{equation}\label{betasive}
@@
 To motivate the application of HDFG spectroscopy, we perform a calculation to compare two-color HDFG and vSFG output, where absorption effects are neglected for simplicity. \cite{Carlson1989}
+vSFG is a $\chi^{(2)}$ technique whose output, When only vibrationally resonant, the vSFG $\chi^{(2)}$ scales as $\chi^{(2)}_{IJK} \sim \langle \alpha_{ij} \mu_k \rangle$, where $\alpha_{ij}$ is the Raman polarizability tensor, whose phase-matching constraint is  $\vec{k}_3 = \vec{k}_1 + \vec{k}_2$.
+HDFG is phase-matchable under $\vec{k}_4 = -\vec{k}_1 + 2\vec{k}_2$ conditions for most, if not all, vibrational resonances.
 The output polarizations under the electric dipole approximation are written as
@@
 Nevertheless, since HDFG produces a number of photons similar to that of vSFG, HDFG is a viable technique for investigating bulk systems.
-This method provides practitioners of sum frequency generation the ability to measure spectra and dephasing dynamics in isotropic media without many meaningful changes in their optical setup, and thus compare spectroscopy and dephasing in the bulk and at the interface.\cite{RN224}
+Laboratories which use vSFG to investigate interfacial species at buried interfaces thus have the ingredients necessary to perform a HDFG experiment in a transmission geometry. \cite{Piontek2023_1}
+This method provides vSFG practitioners the ability to measure spectra and dephasing dynamics in isotropic media without many meaningful changes in their optical setup, and thus compare spectroscopy and dephasing in the bulk and at the interface.\cite{RN224}
 

### 2024-08-31 paper.tex
fixed weird crashes

@@
-\documentclass[aip, jcp, reprint, onecolumn, nofootinbib]{revtex4-2}
+\documentclass[aip, jcp, reprint, onecolumn]{revtex4-2}
 
@@
 		The red box outlines the e-v coupling techniques (HDFG, HSFG) relevant to this manuscript.
-	}
+	} %TODO: Fix vsfg
 	\label{fig:comparisonwmel}
@@
 After developing selection rules, some quantitative aspects of HDFG are discussed in \autoref{quant}.
-
-\section{Density Matrix Propagation}
-In the cases discussed in the introduction, the proposed HDFG spectroscopy method is used to probe vibronic coupling.
-Coherent spectroscopies are often described using the density-matrix formalism, where a density matrix $\rho$ is propagated using the Liouville-von Neumann equation as
-\begin{equation}
-	\dot{\rho} = \frac{1}{i \hbar} [H_0 + H(t), \rho] + \dot{\rho}_R,
-\end{equation}
-where $H_0$ is system Hamiltonian, $H(t)$ is the time-dependent, matter-radiation interaction Hamiltonian and $\rho_R$ is the relaxation density matrix. 
-In most treatments of coherent vibrational spectroscopy, it is sufficient to write $\dot{\rho}_R = \Gamma \rho$, i.e.
-exponential relaxation (Markovian dynamics), where $\Gamma$ is the system's pure dephasing rate.
-\cite{RN455, RN307}
 
@@
 
-It is useful to expose relationships between nonlinear output, transition dipoles and hyper-Raman hyperpolarizabilities in the driven limit. \cite{Simpson2004, Moad2005}
+\subsection{Lineshape Models for HDFG Spectroscopy}
+
+It is useful to expose relationships between nonlinear output, transition dipoles and hyper-Raman hyperpolarizabilities in the driven limit. \cite{Simpson2004}
 Under the electric dipole approximation, the $I^\text{th}$ cartesian component of the third order nonlinear output polarization, ${P}^{(3)}_I$, of a four wave mixing process, induced by electric fields $E_J$, $E_K$, and $E_L$ at output frequency $\omega_4=-\omega_1 + \omega_2 + \omega_3$ is written as (using Einstein summation) \cite{RN307}
@@
 The signatures of vibronic coupling in the HDFG spectrum are made clear by using a simple model.
-Using a two-well system described by 
+Using a two-well system described by $H = H_g |g) \left(g| + H_e |e\right) (e|$ where
 \begin{subequations}\label{Hamiltonian}
@@
 	\caption{\label{T:contributions} Franck-Condon and/or Herzberg-Teller contributions to $A$, $B_1$, $B_2$ terms between $\ket{g,0}$, $\ket{g,1}$ and vibronic states $\ket{e,0}$, $\ket{e,1}$, $\ket{e,2}$ for \autoref{Hamiltonian} with an offset $\xi = 0.5$.
-	Closed-form expressions for the Franck-Condon and Herzberg-Teller integrals used here have been tabulated by Carlson.\cite{Carlson1988thesis}}\footnote{The Herzberg-Teller Integrals 
+	Closed-form expressions for the Franck-Condon and Herzberg-Teller integrals used here have been tabulated by Carlson.\cite{Carlson1988thesis}}
 	\begin{ruledtabular}
@@
 \end{table}
+
+\subsection{Line Narrowing in SIVE Spectroscopies}
+An unavoidable consequence in electronic spectroscopy is broadened lineshapes due to the inhomogeneity of electronic transitions (e.g., vibronic sidebands, molecular collisions). 
+Four wave mixing methods can line-narrow transitions and remove some impact of inhomogeneous broadening.\cite{Carlson1990line}
+The line-narrowing properties of DR-SIVE are investigated so that the pathways which line-narrow correlated or anti-correlated modes (\textit{vide infra}) can be identified.
+SR-SIVE cannot linenarrow transitions as it is singly resonant. \cite{RN352}
+In the discussion that follows, we assume that a vibrational mode in the ground state, $\ket{g,v}$, is correlated to the frequency of a vibronic $\ket{e,v'}$.\cite{Carlson1990line, Dong2015}
+If the frequency of $\ket{g,v}$ is written as $\omega_{gv} + \xi$, where $\xi$ is some external strain (e.g.
+molecular collisions), then the frequency of $\ket{e,v}$ is $\omega_{ev} + c\xi$, where c is a shift coefficient.
+Similarly, we take the frequency of $\ket{e,0}$ as $\omega_{e0} \rightarrow \omega_{e0} + \xi$.
+The strains shift resonance denominators, e.g., for $\omega_{ij} \rightarrow \omega_{ij} + c\xi$, as
+\begin{equation}
+	\Delta_{ij}(\xi) = \omega_{ij} + c\xi -\omega_k - i\Gamma_{ij} \equiv \Delta_{ij}(0) + c\xi
+\end{equation}
+Without loss of generality, we assume c = 1 for correlated modes and c = -1 for anti-correlated modes.
+To understand the impact of inhomogeneity on spectral output, we convolute an output density matrix element $\rho_{ab}(\xi)$ with a normalized Lorentzian distribution $P(\xi)$ of half width $\sigma$ as \cite{Penner1976, Desiderio1979, Dick83_1, Carlson1990line}
+\begin{equation}\label{contour}
+	\rho_{ab} = \int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \rho_{ab}(\xi)
+\end{equation} 
+While Gaussian distributions are commonly used to describe inhomogeneous broadening,\cite{RN307} Lorentzian distributions have successfully described inhomogeneous broadening in a variety of spectroscopies and yield easily interpreted closed-form solutions.
+\cite{Dick83_1, Carlson1990line}
+
+By substituting the output density matrix elements for HSFG and non-parametric HDFG into \autoref{contour}, it is clear that HSFG line-narrows anti-correlated modes, whereas non-parametric HDFG line-narrows correlated modes.
+See the supporting information for more information.
+Although \autoref{contour} identifies that only nonparametric HDFG line-narrows correlated modes, these results are only valid in limits where the input pulses only weakly populate excited states.
+When resonant pulses are significantly longer than the dephasing time of some state, then that state can become populated.
+Excited state population effects are particularly important for understanding the spectroscopy of electronic states using input pulses with pulsewidths significantly longer than dephasing times.
+\cite{RN319, Yurs2012}
+Excited state populations can feed other modes, including the ground state and other vibrational/vibronic modes, inducing higher order processes.\cite{Carlson87, RN471}
+These feeding mechanisms can induce line-narrowing properties in spectroscopies that cannot line-narrow in third order perturbation theory.\cite{RN319, Carlson87, RN471, RN410}
 
@@
 To motivate the application of HDFG spectroscopy, we perform a calculation to compare two-color HDFG and vSFG output, where absorption effects are neglected for simplicity. \cite{Carlson1989}
-vSFG is a $\chi^{(2)}$ technique whose output, When only vibrationally resonant, the vSFG $\chi^{(2)}$ scales as $\chi^{(2)}_{IJK} \sim \langle \alpha_{ij} \mu_k \rangle$, where $\alpha_{ij}$ is the Raman polarizability tensor, whose phase-matching constraint is  $\vec{k}_3 = \vec{k}_1 + \vec{k}_2$.
-HDFG is phase-matchable under $\vec{k}_4 = -\vec{k}_1 + 2\vec{k}_2$ conditions for most, if not all, vibrational resonances.
-The output polarizations under the electric dipole approximation are written as
+vSFG is a $\chi^{(2)}$ technique, when only vibrationally resonant, whose output scales as $\chi^{(2)}_{IJK} \sim \langle \alpha_{ij} \mu_k \rangle$, where $\alpha_{ij}$ is the Raman polarizability tensor.
+The output polarizations for vSFG and HDFG, respectively, under the electric dipole approximation are written as
 	 	\begin{subequations}
@@
 \end{equation}
-Ziegler has noted that for a field with intensity 10 GW/cm$^{2}$, $\frac{\beta E}{\alpha} \sim 10^{-3} $ for vibrational modes when $E(\omega_2)$ is largely detuned from electronic resonances.
+Ziegler has noted that for a field with intensity 10 GW/cm$^{2}$, $\frac{\beta E}{\alpha} \sim 10^{-3} $ for vibrational modes when detuned from electronic resonances, i.e.
+singly resonant vSFG and HDFG.
 \cite{RN515}
@@
 It is important to note that this calculation assumed negligible dipole and Raman polarizability dependence upon the distance from surface normal, ignored orientational averaging effects, and presumed equivalence of local field factors, all of which can significantly reduce output from either process.
-Nevertheless, since HDFG produces a number of photons similar to that of vSFG, HDFG is a viable technique for investigating bulk systems.
+Nevertheless, since HDFG produces a similar number of photons as vSFG, HDFG is a viable technique for investigating bulk systems.
 Laboratories which use vSFG to investigate interfacial species at buried interfaces thus have the ingredients necessary to perform a HDFG experiment in a transmission geometry. \cite{Piontek2023_1}
 This method provides vSFG practitioners the ability to measure spectra and dephasing dynamics in isotropic media without many meaningful changes in their optical setup, and thus compare spectroscopy and dephasing in the bulk and at the interface.\cite{RN224}
+
+\section{Appendix: Evaluation of Pathway I-a Linenarrowing Capability}
+The output coherence  for this pathway is $\rho_{ev',gv}(\xi)$.
+Setting $\eta$ equal to the numerator of \autoref{drgamma_alpha_0} along with any constants, we see
+\begin{widetext}
+	\begin{equation}\label{ev'gv}
+		\begin{split}
+			\rho_{ev',gv}(\xi) &= \frac{\eta}{\Delta_{g0,gv}(\xi) \Delta_{ev',gv}(c\xi)}\\
+			&=  \frac{\eta}{(-\omega_{g0,gv} - \xi + \omega_1 - i\Gamma_{g0,gv})(\omega_{ev',gv} + c\xi - (2\omega_3 + \omega_1) - i\Gamma_{ev',gv})}\\ 
+			&= \frac{\eta}{(\Delta_{g0,gv}(0) - \xi)(\Delta_{ev',gv}(0) + c\xi)}\\ 
+		\end{split}
+	\end{equation}
+\end{widetext}
+For notational convenience, we map $\ket{g,0} \rightarrow \ket{g}$, $\ket{g,v} \rightarrow \ket{a}$ and $\ket{e,v'} \rightarrow \ket{b}$.
+Substituting into \autoref{contour}, we see:
+\begin{equation}\label{integraly}
+	\begin{split}
+		\rho_{ba} &= \int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \rho_{ba}(\xi)\\
+		&= \int_{-\infty}^\infty \mathrm{d}\xi \frac{\sigma}{\pi} \frac{1}{\xi^2 + \sigma^2} \eta \frac{1}{\Delta_{ga}(0) - \xi} \frac{1}{\Delta_{ba}(0) + c\xi}\\
+		&= \frac{\eta \sigma}{\pi} \int_{-\infty}^\infty \mathrm{d}\xi\frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga}(0) - \xi} \frac{1}{\Delta_{ba}(0) + c\xi}\\
+	\end{split}
+\end{equation}
+\begin{figure}[!htbp]
+	\centering
+	\includegraphics[width=3.375in]{figures/corr_contour.png}
+	\caption{Poles (black dots) and contour (blue line) used to evaluate \autoref{integraly} for (a) anti-correlated and (b) correlated modes.} 
+	\label{fig:contours}
+\end{figure}
+\subsubsection{Anti-correlated Modes}
+For anti-correlated modes, the poles are situated in the complex plane as shown in \autoref{fig:contours}a.
+Since \autoref{integraly} is evaluated along the real axis, one can choose to evaluate the contour in the upper or lower half of the complex plane.
+Since evaluating the residues in the upper or lower half of the complex plane yields the same result for \autoref{integraly}, we choose the contour which wraps around the least number of poles.
+It is clear for c = -1 that there are four poles: $\pm i \sigma, \Delta_{ga}(0), \Delta_{ba}(0)$. 
+Following \autoref{fig:contours}, the contour that wraps the upper half of the complex plane has only one pole, $i \sigma$; as such, we choose to evaluate \autoref{integraly} in the upper half of the complex plane for the case of anti-correlated modes through the residue theorem as
+\begin{widetext}
+	\begin{equation}
+		\begin{split}
+			\rho_{ba} = \int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \rho_{ba}(\xi) &= 2\pi i \sum_k \lim_{\xi \rightarrow \xi_k} P(\xi) \rho_{ba}(\xi) (\xi - \xi_k)\\
+			&= 2\pi i \frac{\eta \sigma}{\pi} \lim_{\xi \rightarrow i\sigma} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga}(0) - \xi} \frac{1}{\Delta_{ba}(0) - \xi} (\xi - i \sigma)\\
+			&= 2 \eta \sigma i \lim_{\xi \rightarrow i\sigma} \frac{1}{\xi + i\sigma} \frac{1}{\Delta_{ga}(0) - \xi} \frac{1}{\Delta_{ba}(0) - \xi}\\
+			&= 2\eta \sigma i \frac{1}{2i\sigma} \frac{1}{\Delta_{ga}(0) - i\sigma} \frac{1}{\Delta_{ba}(0) - i\sigma}\\
+			&= \frac{\eta}{\Delta_{ga}(i\sigma)\Delta_{ba}(i \sigma)}\\
+		\end{split}
+	\end{equation}
+\end{widetext}
+In words, we see the inhomogeneous envelope width $\sigma$ is added to the linewidth of each resonance (e.g., $\Gamma_{ag} \rightarrow \Gamma_{ag} + \sigma$).
+Therefore, pathway I-a cannot linenarrow anti-correlated modes. 
+\subsubsection{Correlated Modes: c = 1}
+For correlated modes, the poles are situated in the complex plane as shown in \autoref{fig:contours}.
+It is clear that no matter which contour is chosen, there is a contribution to the final integral from either $\Delta_{ba}(0)$ or $\Delta_{ga}(0)$. 
+For the below calculation, we choose to evaluate along the contour in the bottom half of the complex plane, i.e., the poles ($\xi_k$) are $-i\sigma, \Delta_{ga}$.
+We stress that since the integral is evaluated over $\mathbb{R}$ and there are no degenerate poles, the results below can be obtained by evaluating the contour which wraps around the poles $i\sigma, \Delta_{ba}$.
+Since the $\xi_k$ are nondegenerate, \autoref{integraly} can be evaluated using the Residue theorem as 
+\begin{widetext}
+	\begin{equation}
+		\begin{split}
+			\int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \rho_{ba}(\xi) &= 2\pi i \sum_k \lim_{\xi \rightarrow \xi_k} P(\xi) \rho_{ba}(\xi) (\xi - \xi_k)\\
+			&= 2\pi i \frac{\eta \sigma}{\pi} ( \lim_{\xi \rightarrow -i\sigma} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga}(0) - \xi} \frac{1}{\Delta_{ba}(0) - \xi} (\xi + i \sigma) \\ &+
+			\lim_{\xi \rightarrow \Delta_{ga}(0)} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga}(0) - \xi} \frac{1}{\Delta_{ba}(0) - \xi} (\xi - \Delta_{ga}))\\
+			&= 2 \eta i \sigma (\frac{1}{2 i \sigma} \frac{1}{-i \sigma - \Delta_{ga}(0)} \frac{1}{\Delta_{ba}(0) - i\sigma} ) - 2 \eta i \sigma (\frac{1}{\sigma^2 + (\Delta_{ga} (0))^2} \frac{1}{\Delta_{ga}(0) + \Delta_{ba}(0)} )\\
+			&= -\frac{\eta}{\Delta_{ga}(0) + i \sigma} (\frac{1}{\Delta_{ba}(0) - i \sigma} + \frac{2i\sigma}{(\Delta_{ga}(0) - i \sigma)(\Delta_{ga}(0) + \Delta_{ba}(0))})\\
+		\end{split}
+	\end{equation}
+\end{widetext}
+The final line of the above equation shows the presence of a new term, $\frac{2i\sigma}{\Delta_{ga}(0) + \Delta_{ba}(0)}$. 
+This term is amplified by the width of the inhomogeneous envelope ($\sigma$) and has a linewidth $\Gamma_{ba} + \Gamma_{ga}$, which linenarrows the transition. 
+Results for the other pathways follow the same technique.
+Generally, when starting from the ground state, non-parametric spectroscopies line-narrow correlated modes, and parametric spectroscopies line-narrow anti-correlated modes. \cite{Dick83_1, RN425}
 

### 2024-08-31 paper.tex
Update paper.tex

@@
 \subsection{Lineshape Models for HDFG Spectroscopy}
+Coherent spectroscopies are often described using the density-matrix formalism, where a density matrix $\rho$ is propagated using the Liouville-von Neumann equation as
+\begin{equation}
+	\dot{\rho} = \frac{1}{i \hbar} [H_0 + V(t), \rho] + \dot{\rho}_R,
+\end{equation}
+where $H$ is system Hamiltonian, $V(t)$ is the field-matter interaction and $\rho_R$ is the relaxation density matrix. 
+It is often sufficient to write $\dot{\rho}_R = \Gamma \rho$, i.e. exponential relaxation (Markovian dynamics), where $\Gamma$ is the system's pure dephasing rate. \cite{RN455, RN307}
+Before assuming this limit, the system response for an HDFG will be generalized to provide a formalism which supports non-exponential dynamics. %todo: cite Silbey, Mukamel, Kelley etc
 
-It is useful to expose relationships between nonlinear output, transition dipoles and hyper-Raman hyperpolarizabilities in the driven limit. \cite{Simpson2004}
+\subsection{blah}
+
+It is useful to expose relationships between nonlinear output, transition dipoles and hyper-Raman hyperpolarizabilities in the driven limit. \cite{Simpson2004, Moad2005}
 Under the electric dipole approximation, the $I^\text{th}$ cartesian component of the third order nonlinear output polarization, ${P}^{(3)}_I$, of a four wave mixing process, induced by electric fields $E_J$, $E_K$, and $E_L$ at output frequency $\omega_4=-\omega_1 + \omega_2 + \omega_3$ is written as (using Einstein summation) \cite{RN307}
@@
 
-\subsection{Line Narrowing in SIVE Spectroscopies}
+\subsection{Line Narrowing}
 An unavoidable consequence in electronic spectroscopy is broadened lineshapes due to the inhomogeneity of electronic transitions (e.g., vibronic sidebands, molecular collisions). 

### 2024-09-03 paper.tex
edits

@@
 
+Coherent spectroscopies are often described using the density-matrix formalism, where a density matrix $\rho$ is propagated using the Liouville-von Neumann equation $via$
+\begin{equation}
+	\dot{\rho} = \frac{1}{i \hbar} [H + V(t), \rho] + \dot{\rho}_R,
+\end{equation}
+where $H$ is the (static) system Hamiltonian, $V(t)$ is the field-matter interaction and $\rho_R$ is the relaxation density matrix. 
+Under the electric dipole approximation, $V(t) = -\vec{\mu} \cdot \sum_{j} E_j(t)$, where $j$ indexes the input electric fields.
+It is often sufficient to write $\dot{\rho}_R = \Gamma \rho$, i.e. exponential relaxation (Markovian dynamics), where $\Gamma$ is the system's pure dephasing rate. \cite{RN455, RN307, Yurs2012}
+In the exponential relaxation limit, the solution for a density matrix element $\rho_{ab}$, assuming only one input field, is written as
+\begin{equation}
+	\begin{split}
+		\rho_{ab} &= \text{stuff} \int_0^\infty \mathrm{d}t \exp({-it}(\omega_{ab} - \omega - i\Gamma_{ab})) \\
+		&= \frac{\text{stuff}}{\omega_{ab} - \omega - i\Gamma_{ab}}\\
+	\end{split}
+\end{equation}
+This limit is often appropriate for isolated molecules at low temperatures. \cite{RN287}
+However, exponential relaxation is an inappropriate description of most physical systems when system-bath interactions are included. \cite{Sue1986, Yan1988, Li1994, RN287, Myers1997, Sung2001, RN445}
+Such systems are properly described by including Brownian bath oscillators, which changes density matrix propagation as
+\begin{equation}
+	\text{evil stuff}
+\end{equation}
+Nevertheless, in the discussion that follows, we assume the limit of an isolated molecule with no bath interaction and that pulse widths are longer than the electronic dephasing times, which has proven useful in investigating the properties of doubly resonant SFG spectroscopy, 2D-EV spectroscopy and 2D-VE spectroscopy.
+\cite{Raschke2002, Gaynor2017}
+This limit is taken to emphasize the quantum mechanical selection rules of the HDFG technique. 
+We stress that in most systems, e.g., solvated chromophores, system-bath interactions must be explicitly included to properly describe lineshapes of vibronic phenomena. \cite{Li1994}
+Future work will more rigorously investigate the impact of system-bath interactions on HDFG spectral analysis.\cite{McDonnellinprep}
+
 It is useful to briefly discuss the impact of time ordering on HDFG output.
@@
 
-\subsection{Lineshape Models for HDFG Spectroscopy}
-Coherent spectroscopies are often described using the density-matrix formalism, where a density matrix $\rho$ is propagated using the Liouville-von Neumann equation as
-\begin{equation}
-	\dot{\rho} = \frac{1}{i \hbar} [H_0 + V(t), \rho] + \dot{\rho}_R,
-\end{equation}
-where $H$ is system Hamiltonian, $V(t)$ is the field-matter interaction and $\rho_R$ is the relaxation density matrix. 
-It is often sufficient to write $\dot{\rho}_R = \Gamma \rho$, i.e. exponential relaxation (Markovian dynamics), where $\Gamma$ is the system's pure dephasing rate. \cite{RN455, RN307}
-Before assuming this limit, the system response for an HDFG will be generalized to provide a formalism which supports non-exponential dynamics. %todo: cite Silbey, Mukamel, Kelley etc
-
-\subsection{blah}
-
-It is useful to expose relationships between nonlinear output, transition dipoles and hyper-Raman hyperpolarizabilities in the driven limit. \cite{Simpson2004, Moad2005}
+It is useful to expose relationships between nonlinear output, transition dipoles and hyper-Raman hyperpolarizabilities in the driven limit ($\dot{\rho} = 0$). \cite{Simpson2004, Moad2005}
 Under the electric dipole approximation, the $I^\text{th}$ cartesian component of the third order nonlinear output polarization, ${P}^{(3)}_I$, of a four wave mixing process, induced by electric fields $E_J$, $E_K$, and $E_L$ at output frequency $\omega_4=-\omega_1 + \omega_2 + \omega_3$ is written as (using Einstein summation) \cite{RN307}
@@
 for the ground ($H_g$) and first excited ($H_e$) states, where $p$ (momentum) and $q$ (position) are the dimensionless conjugate coordinates of the normal mode, the A and B contributions can be evaluated using Franck-Condon and Herzberg-Teller integrals tabulated in terms of the dimensionless normal mode $q$ and offset parameter $\xi$ (\autoref{fig:doubres_spec}a).\cite{Carlson1988thesis}
+System-bath interactions are neglected for this discussion.
 For simplicity, we restrict consideration to $v^\prime \in \{0,1,2\}$ and take $\xi = 0.5$.
@@
 The $B_1$ and $B_2$ terms involve different types of vibronic coupling pathways.
-In $B_1$, the Herzberg-Teller coupling is associated with the two-photon absorption process, whereas in $B_2$, the Herzberg-Teller coupling is associated with one-photon emission.
+In $B_1$, the Herzberg-Teller coupling is associated with the two-photon absorption process, whereas in $B_2$, the Herzberg-Teller coupling is associated with one-photon emission.\footnote{Franck-Condon factors and Herzberg-Teller integrals are most easily evaluated in the position basis.}
 
@@
 
-\subsection{Line Narrowing}
+\subsection{Linenarrowing Inhomogeneous Lineshapes}
 An unavoidable consequence in electronic spectroscopy is broadened lineshapes due to the inhomogeneity of electronic transitions (e.g., vibronic sidebands, molecular collisions). 
@@
 \end{equation} 
-While Gaussian distributions are commonly used to describe inhomogeneous broadening,\cite{RN307} Lorentzian distributions have successfully described inhomogeneous broadening in a variety of spectroscopies and yield easily interpreted closed-form solutions.
+While Gaussian distributions are commonly used to describe inhomogeneous broadening,\cite{RN307} Lorentzian distributions have successfully described inhomogeneous broadening in a variety of spectroscopies and yield  closed-form solutions.
 \cite{Dick83_1, Carlson1990line}
+Such approaches have been suitable for investigating the inhomogeneity of excitonic resonances in CdSe quantum dots through FWM spectroscopy. \cite{Yurs2011, Yurs2012}
 

### 2024-09-04 paper.tex
editing inhomogeneous broadening

@@
 Under the electric dipole approximation, $V(t) = -\vec{\mu} \cdot \sum_{j} E_j(t)$, where $j$ indexes the input electric fields.
-It is often sufficient to write $\dot{\rho}_R = \Gamma \rho$, i.e. exponential relaxation (Markovian dynamics), where $\Gamma$ is the system's pure dephasing rate. \cite{RN455, RN307, Yurs2012}
-In the exponential relaxation limit, the solution for a density matrix element $\rho_{ab}$, assuming only one input field, is written as
-\begin{equation}
-	\begin{split}
-		\rho_{ab} &= \text{stuff} \int_0^\infty \mathrm{d}t \exp({-it}(\omega_{ab} - \omega - i\Gamma_{ab})) \\
-		&= \frac{\text{stuff}}{\omega_{ab} - \omega - i\Gamma_{ab}}\\
-	\end{split}
-\end{equation}
-This limit is often appropriate for isolated molecules at low temperatures. \cite{RN287}
-However, exponential relaxation is an inappropriate description of most physical systems when system-bath interactions are included. \cite{Sue1986, Yan1988, Li1994, RN287, Myers1997, Sung2001, RN445}
-Such systems are properly described by including Brownian bath oscillators, which changes density matrix propagation as
-\begin{equation}
-	\text{evil stuff}
-\end{equation}
-Nevertheless, in the discussion that follows, we assume the limit of an isolated molecule with no bath interaction and that pulse widths are longer than the electronic dephasing times, which has proven useful in investigating the properties of doubly resonant SFG spectroscopy, 2D-EV spectroscopy and 2D-VE spectroscopy.
-\cite{Raschke2002, Gaynor2017}
+In systems where interactions with surroundings are relevant, $\dot{\rho}_R$ is a complex function which can be modified to include system-bath interactions, solvent-solute coupling, etc.
+\cite{Sung2001}
+In the limit where input field pulsewidths are much longer than electronic dephasing times and the individual molecule limit is approached, it becomes acceptable to write $\dot{\rho}_R = \Gamma \rho$, i.e.
+exponential relaxation (Markovian dynamics), where $\Gamma$ is the system's pure dephasing rate.
+\cite{RN455, RN307, Sung2001}
+While exponential relaxation is usually an inappropriate description of most physical systems involving solvent-solute interactions,\cite{Sue1986, Yan1988, Li1994, Myers1997} our goal is to introduce simple, quantitative models to understand HDFG response.
+Thus, we write $\dot{\rho}_R = \Gamma \rho$.
+This limit which has proven useful in investigating the properties of 2D-EV and 2D-VE spectroscopy. \cite{Gaynor2017} 
+Experimentally, it has been shown to be valid when investigating doubly resonant SFG response using pulses much longer than electronic dephasing times. \cite{Raschke2002}
 This limit is taken to emphasize the quantum mechanical selection rules of the HDFG technique.
-We stress that in most systems, e.g., solvated chromophores, system-bath interactions must be explicitly included to properly describe lineshapes of vibronic phenomena. \cite{Li1994}
-Future work will more rigorously investigate the impact of system-bath interactions on HDFG spectral analysis.\cite{McDonnellinprep}
 
@@
 The $B_1$ and $B_2$ terms involve different types of vibronic coupling pathways.
-In $B_1$, the Herzberg-Teller coupling is associated with the two-photon absorption process, whereas in $B_2$, the Herzberg-Teller coupling is associated with one-photon emission.\footnote{Franck-Condon factors and Herzberg-Teller integrals are most easily evaluated in the position basis.}
+In $B_1$, the Herzberg-Teller coupling is associated with the two-photon absorption process, whereas in $B_2$, the Herzberg-Teller coupling is associated with one-photon emission.\footnote{Franck-Condon factors and Herzberg-Teller integrals are most easily evaluated in the position basis.
+A sample calculation is provided in the supporting information.}
 
@@
 This means that it is difficult to isolate $B$ terms when $A$ terms are present.
-As such, HDFG will have difficulty examining non-Condon effects ($B$ term contributions) noncentrosymmetric systems.
+As such, HDFG will have difficulty examining non-Condon effects ($B$ term contributions) in noncentrosymmetric systems.
 
@@
 
-\subsection{Linenarrowing Inhomogeneous Lineshapes}
-An unavoidable consequence in electronic spectroscopy is broadened lineshapes due to the inhomogeneity of electronic transitions (e.g., vibronic sidebands, molecular collisions). 
-Four wave mixing methods can line-narrow transitions and remove some impact of inhomogeneous broadening.\cite{Carlson1990line}
-The line-narrowing properties of DR-SIVE are investigated so that the pathways which line-narrow correlated or anti-correlated modes (\textit{vide infra}) can be identified.
-SR-SIVE cannot linenarrow transitions as it is singly resonant. \cite{RN352}
+\subsection{Inhomogeneity in HDFG}
+An often unavoidable consequence in electronic spectroscopy is broadened lineshapes due to a high density of vibronic modes. 
 In the discussion that follows, we assume that a vibrational mode in the ground state, $\ket{g,v}$, is correlated to the frequency of a vibronic $\ket{e,v'}$.\cite{Carlson1990line, Dong2015}
@@
 molecular collisions), then the frequency of $\ket{e,v}$ is $\omega_{ev} + c\xi$, where c is a shift coefficient.
-Similarly, we take the frequency of $\ket{e,0}$ as $\omega_{e0} \rightarrow \omega_{e0} + \xi$.
 The strains shift resonance denominators, e.g., for $\omega_{ij} \rightarrow \omega_{ij} + c\xi$, as
@@
 Without loss of generality, we assume c = 1 for correlated modes and c = -1 for anti-correlated modes.
-To understand the impact of inhomogeneity on spectral output, we convolute an output density matrix element $\rho_{ab}(\xi)$ with a normalized Lorentzian distribution $P(\xi)$ of half width $\sigma$ as \cite{Penner1976, Desiderio1979, Dick83_1, Carlson1990line}
+
+To understand the impact of inhomogeneity on spectral output, we consider static inhomogeneity by convolving the HDFG output hyperpolarizability $\gamma_{ijkl}(\xi)$ with a normalized Lorentzian distribution $P(\xi)$ of half width $\sigma$ as \cite{Penner1976, Desiderio1979, Dick83_1, Carlson1990line}
 \begin{equation}\label{contour}
-	\rho_{ab} = \int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \rho_{ab}(\xi)
+	\gamma_{ijkl} = \int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi)
 \end{equation} 
-While Gaussian distributions are commonly used to describe inhomogeneous broadening,\cite{RN307} Lorentzian distributions have successfully described inhomogeneous broadening in a variety of spectroscopies and yield  closed-form solutions.
+While Gaussian distributions are commonly used to describe inhomogeneous broadening,\cite{RN307, RN131} Lorentzian distributions have successfully described inhomogeneous broadening in a variety of spectroscopies and yield  closed-form solutions.
 \cite{Dick83_1, Carlson1990line}
@@
 
-By substituting the output density matrix elements for HSFG and non-parametric HDFG into \autoref{contour}, it is clear that HSFG line-narrows anti-correlated modes, whereas non-parametric HDFG line-narrows correlated modes.
-See the supporting information for more information.
-Although \autoref{contour} identifies that only nonparametric HDFG line-narrows correlated modes, these results are only valid in limits where the input pulses only weakly populate excited states.
+Evaluating \autoref{contour} for the HDFG pathway above shows \footnote{See the supporting information for more details} 
+\begin{subequations}\label{linenarrow}
+	\begin{equation}\label{linenarrowa}
+		\gamma_{ijkl} = \frac{- \gamma_0}{(\Delta_{ga}(- i \sigma)} \left( \frac{1}{\Delta_{ba}(i \sigma)} + \frac{2 i \sigma}{\Delta_{ga}(i \sigma)} \frac{1}{\Delta_{ba}(0) + \Delta_{ga}(0)} \right)
+	\end{equation}
+	\begin{equation}
+		\gamma_{ijkl} = \frac{\gamma_0}{\Delta_{ga}(i\sigma)\Delta_{ba}(i \sigma)}
+	\end{equation}
+\end{subequations}
+for correlated and anti-correlated modes, respectively, where $\gamma_0$ involves factors related to $A,B$ and $\mu$.
+
+The output for correlated modes shows the presence of a new term, $\frac{2i\sigma}{\Delta_{ga}(0) + \Delta_{ba}(0)}$. 
+This term is amplified by the width of the inhomogeneous envelope ($\sigma$) and has a linewidth $\Gamma_{ba} + \Gamma_{ga}$, which linenarrows the transition. 
+For anti-correlated modes, we see the inhomogeneous envelope width $\sigma$ is added to the linewidth of each resonance (e.g., $\Gamma_{ag} \rightarrow \Gamma_{ag} + \sigma$).
+As such, the HDFG pathway considered in this work line-narrows correlated modes. 
+These results are consistent with the idea that non-parametric, non-linear spectroscopies line-narrow correlated modes. \cite{Dick83_1, Carlson1990line}
+
+Although \autoref{linenarrowa} identifies that parametric HDFG line-narrows correlated modes, these results are only valid in limits where the input pulses only weakly populate excited states.
 When resonant pulses are significantly longer than the dephasing time of some state, then that state can become populated.
@@
 
-\section{Appendix: Evaluation of Pathway I-a Linenarrowing Capability}
-The output coherence  for this pathway is $\rho_{ev',gv}(\xi)$.
-Setting $\eta$ equal to the numerator of \autoref{drgamma_alpha_0} along with any constants, we see
-\begin{widetext}
-	\begin{equation}\label{ev'gv}
-		\begin{split}
-			\rho_{ev',gv}(\xi) &= \frac{\eta}{\Delta_{g0,gv}(\xi) \Delta_{ev',gv}(c\xi)}\\
-			&=  \frac{\eta}{(-\omega_{g0,gv} - \xi + \omega_1 - i\Gamma_{g0,gv})(\omega_{ev',gv} + c\xi - (2\omega_3 + \omega_1) - i\Gamma_{ev',gv})}\\ 
-			&= \frac{\eta}{(\Delta_{g0,gv}(0) - \xi)(\Delta_{ev',gv}(0) + c\xi)}\\ 
-		\end{split}
-	\end{equation}
-\end{widetext}
-For notational convenience, we map $\ket{g,0} \rightarrow \ket{g}$, $\ket{g,v} \rightarrow \ket{a}$ and $\ket{e,v'} \rightarrow \ket{b}$.
-Substituting into \autoref{contour}, we see:
-\begin{equation}\label{integraly}
-	\begin{split}
-		\rho_{ba} &= \int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \rho_{ba}(\xi)\\
-		&= \int_{-\infty}^\infty \mathrm{d}\xi \frac{\sigma}{\pi} \frac{1}{\xi^2 + \sigma^2} \eta \frac{1}{\Delta_{ga}(0) - \xi} \frac{1}{\Delta_{ba}(0) + c\xi}\\
-		&= \frac{\eta \sigma}{\pi} \int_{-\infty}^\infty \mathrm{d}\xi\frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga}(0) - \xi} \frac{1}{\Delta_{ba}(0) + c\xi}\\
-	\end{split}
-\end{equation}
-\begin{figure}[!htbp]
-	\centering
-	\includegraphics[width=3.375in]{figures/corr_contour.png}
-	\caption{Poles (black dots) and contour (blue line) used to evaluate \autoref{integraly} for (a) anti-correlated and (b) correlated modes.} 
-	\label{fig:contours}
-\end{figure}
-\subsubsection{Anti-correlated Modes}
-For anti-correlated modes, the poles are situated in the complex plane as shown in \autoref{fig:contours}a.
-Since \autoref{integraly} is evaluated along the real axis, one can choose to evaluate the contour in the upper or lower half of the complex plane.
-Since evaluating the residues in the upper or lower half of the complex plane yields the same result for \autoref{integraly}, we choose the contour which wraps around the least number of poles.
-It is clear for c = -1 that there are four poles: $\pm i \sigma, \Delta_{ga}(0), \Delta_{ba}(0)$. 
-Following \autoref{fig:contours}, the contour that wraps the upper half of the complex plane has only one pole, $i \sigma$; as such, we choose to evaluate \autoref{integraly} in the upper half of the complex plane for the case of anti-correlated modes through the residue theorem as
-\begin{widetext}
-	\begin{equation}
-		\begin{split}
-			\rho_{ba} = \int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \rho_{ba}(\xi) &= 2\pi i \sum_k \lim_{\xi \rightarrow \xi_k} P(\xi) \rho_{ba}(\xi) (\xi - \xi_k)\\
-			&= 2\pi i \frac{\eta \sigma}{\pi} \lim_{\xi \rightarrow i\sigma} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga}(0) - \xi} \frac{1}{\Delta_{ba}(0) - \xi} (\xi - i \sigma)\\
-			&= 2 \eta \sigma i \lim_{\xi \rightarrow i\sigma} \frac{1}{\xi + i\sigma} \frac{1}{\Delta_{ga}(0) - \xi} \frac{1}{\Delta_{ba}(0) - \xi}\\
-			&= 2\eta \sigma i \frac{1}{2i\sigma} \frac{1}{\Delta_{ga}(0) - i\sigma} \frac{1}{\Delta_{ba}(0) - i\sigma}\\
-			&= \frac{\eta}{\Delta_{ga}(i\sigma)\Delta_{ba}(i \sigma)}\\
-		\end{split}
-	\end{equation}
-\end{widetext}
-In words, we see the inhomogeneous envelope width $\sigma$ is added to the linewidth of each resonance (e.g., $\Gamma_{ag} \rightarrow \Gamma_{ag} + \sigma$).
-Therefore, pathway I-a cannot linenarrow anti-correlated modes. 
-\subsubsection{Correlated Modes: c = 1}
-For correlated modes, the poles are situated in the complex plane as shown in \autoref{fig:contours}.
-It is clear that no matter which contour is chosen, there is a contribution to the final integral from either $\Delta_{ba}(0)$ or $\Delta_{ga}(0)$. 
-For the below calculation, we choose to evaluate along the contour in the bottom half of the complex plane, i.e., the poles ($\xi_k$) are $-i\sigma, \Delta_{ga}$.
-We stress that since the integral is evaluated over $\mathbb{R}$ and there are no degenerate poles, the results below can be obtained by evaluating the contour which wraps around the poles $i\sigma, \Delta_{ba}$.
-Since the $\xi_k$ are nondegenerate, \autoref{integraly} can be evaluated using the Residue theorem as 
-\begin{widetext}
-	\begin{equation}
-		\begin{split}
-			\int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \rho_{ba}(\xi) &= 2\pi i \sum_k \lim_{\xi \rightarrow \xi_k} P(\xi) \rho_{ba}(\xi) (\xi - \xi_k)\\
-			&= 2\pi i \frac{\eta \sigma}{\pi} ( \lim_{\xi \rightarrow -i\sigma} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga}(0) - \xi} \frac{1}{\Delta_{ba}(0) - \xi} (\xi + i \sigma) \\ &+
-			\lim_{\xi \rightarrow \Delta_{ga}(0)} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga}(0) - \xi} \frac{1}{\Delta_{ba}(0) - \xi} (\xi - \Delta_{ga}))\\
-			&= 2 \eta i \sigma (\frac{1}{2 i \sigma} \frac{1}{-i \sigma - \Delta_{ga}(0)} \frac{1}{\Delta_{ba}(0) - i\sigma} ) - 2 \eta i \sigma (\frac{1}{\sigma^2 + (\Delta_{ga} (0))^2} \frac{1}{\Delta_{ga}(0) + \Delta_{ba}(0)} )\\
-			&= -\frac{\eta}{\Delta_{ga}(0) + i \sigma} (\frac{1}{\Delta_{ba}(0) - i \sigma} + \frac{2i\sigma}{(\Delta_{ga}(0) - i \sigma)(\Delta_{ga}(0) + \Delta_{ba}(0))})\\
-		\end{split}
-	\end{equation}
-\end{widetext}
-The final line of the above equation shows the presence of a new term, $\frac{2i\sigma}{\Delta_{ga}(0) + \Delta_{ba}(0)}$. 
-This term is amplified by the width of the inhomogeneous envelope ($\sigma$) and has a linewidth $\Gamma_{ba} + \Gamma_{ga}$, which linenarrows the transition. 
-Results for the other pathways follow the same technique.
-Generally, when starting from the ground state, non-parametric spectroscopies line-narrow correlated modes, and parametric spectroscopies line-narrow anti-correlated modes. \cite{Dick83_1, RN425}
-
 \section{References}

### 2024-09-04 figures/2D_spec.py

@@ -11,7 +11,7 @@ from matplotlib.patches import FancyArrowPatch
 
 wt.artists.apply_rcparams(kind="publication")
 
-save = False
+save = True
 fontsize = 18
 
 #define harmonic wells and coordinates

### 2024-09-04 paper.tex
small tihngs

@@
 \begin{equation}
-	\Delta_{ij}(\xi) = \omega_{ij} + c\xi -\omega_k - i\Gamma_{ij} \equiv \Delta_{ij}(0) + c\xi
+	\Delta_{ij}(c\xi) = \omega_{ij} + c\xi -\omega_k - i\Gamma_{ij} \equiv \Delta_{ij}(0) + c\xi
 \end{equation}
@@
 
-To understand the impact of inhomogeneity on spectral output, we consider static inhomogeneity by convolving the HDFG output hyperpolarizability $\gamma_{ijkl}(\xi)$ with a normalized Lorentzian distribution $P(\xi)$ of half width $\sigma$ as \cite{Penner1976, Desiderio1979, Dick83_1, Carlson1990line}
+We investigate the impact of inhomogeneity on spectral output by convolving the HDFG output hyperpolarizability $\gamma_{ijkl}(\xi)$ with a normalized Lorentzian distribution $P(\xi)$ of half width $\sigma$ as \cite{Penner1976, Desiderio1979, Dick83_1, Carlson1990line}
 \begin{equation}\label{contour}
 	\gamma_{ijkl} = \int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi)
+	= \frac{\sigma}{\pi}\int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi)
 \end{equation} 
-While Gaussian distributions are commonly used to describe inhomogeneous broadening,\cite{RN307, RN131} Lorentzian distributions have successfully described inhomogeneous broadening in a variety of spectroscopies and yield  closed-form solutions.
-\cite{Dick83_1, Carlson1990line}
-Such approaches have been suitable for investigating the inhomogeneity of excitonic resonances in CdSe quantum dots through FWM spectroscopy. \cite{Yurs2011, Yurs2012}
+The limit of static inhomogeneity is chosen for simplicity.
+While Gaussian distributions are commonly used to describe inhomogeneous broadening, Lorentzian distributions have successfully described inhomogeneous broadening in a variety of spectroscopies and yield easily interpretable closed-form solutions.
+\cite{Dick83_1, Carlson1990line, Yurs2011, Yurs2012}
 
-Evaluating \autoref{contour} for the HDFG pathway above shows \footnote{See the supporting information for more details} 
+Evaluating \autoref{contour} for the HDFG pathway above shows\footnote{See the supporting information for more details} 
 \begin{subequations}\label{linenarrow}
@@
 for correlated and anti-correlated modes, respectively, where $\gamma_0$ involves factors related to $A,B$ and $\mu$.
-
 The output for correlated modes shows the presence of a new term, $\frac{2i\sigma}{\Delta_{ga}(0) + \Delta_{ba}(0)}$. 

### 2024-09-05 paper.tex
added si part 1

@@
 For simplicity, we restrict consideration to $v^\prime \in \{0,1,2\}$ and take $\xi = 0.5$.
-Note that $q = \sqrt{\frac{m^2\omega}{\hbar}} Q$.
+Note that $q = \sqrt{\frac{\omega}{\hbar}} Q$.
 We assume the electronic state is both one and two photon allowed.
@@
 molecular collisions), then the frequency of $\ket{e,v}$ is $\omega_{ev} + c\xi$, where c is a shift coefficient.
-The strains shift resonance denominators, e.g., for $\omega_{ij} \rightarrow \omega_{ij} + c\xi$, as
+The strains shift resonance denominators, e.g., for $\omega_{ij} \rightarrow \omega_{ij} \pm c\xi$, as
 \begin{equation}
-	\Delta_{ij}(c\xi) = \omega_{ij} + c\xi -\omega_k - i\Gamma_{ij} \equiv \Delta_{ij}(0) + c\xi
+	\Delta_{ij}(c\xi) = \omega_{ij} \pm c\xi -\omega_k - i\Gamma_{ij} \equiv \Delta_{ij}(0) \pm c\xi
 \end{equation}
-Without loss of generality, we assume c = 1 for correlated modes and c = -1 for anti-correlated modes.
+where $+ (-)$ refers to correlated (anti-correlated) modes.
+For simplicity, we assume c = 1.
 
@@
 	\gamma_{ijkl} = \int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi)
-	= \frac{\sigma}{\pi}\int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi)
+	= \frac{\sigma}{\pi}\int_{-\infty}^\infty \mathrm{d}\xi \frac{1}{\sigma^2 + \xi^2} \frac{\gamma_0}{\Delta_{ga}(\xi)\Delta_{ba}(\xi)}
 \end{equation} 
@@
 While Gaussian distributions are commonly used to describe inhomogeneous broadening, Lorentzian distributions have successfully described inhomogeneous broadening in a variety of spectroscopies and yield easily interpretable closed-form solutions.
-\cite{Dick83_1, Carlson1990line, Yurs2011, Yurs2012}
+\cite{Dick83_1, Carlson1990line, RN410, Yurs2011, Yurs2012}
 
@@
 	\begin{equation}\label{linenarrowa}
-		\gamma_{ijkl} = \frac{- \gamma_0}{(\Delta_{ga}(- i \sigma)} \left( \frac{1}{\Delta_{ba}(i \sigma)} + \frac{2 i \sigma}{\Delta_{ga}(i \sigma)} \frac{1}{\Delta_{ba}(0) + \Delta_{ga}(0)} \right)
+		\gamma_{ijkl} = \frac{- \gamma_0}{\Delta_{ga}(- i \sigma)} \left( \frac{1}{\Delta_{ba}(i \sigma)} + \frac{2 i \sigma}{\Delta_{ga}(i \sigma)} \frac{1}{\Delta_{ba}(0) + \Delta_{ga}(0)} \right)
 	\end{equation}
@@
 This term is amplified by the width of the inhomogeneous envelope ($\sigma$) and has a linewidth $\Gamma_{ba} + \Gamma_{ga}$, which linenarrows the transition. 
-For anti-correlated modes, we see the inhomogeneous envelope width $\sigma$ is added to the linewidth of each resonance (e.g., $\Gamma_{ag} \rightarrow \Gamma_{ag} + \sigma$).
+For anti-correlated modes, we see the inhomogeneous envelope width $\sigma$ is added to the linewidth of each resonance (e.g., $\Gamma_{ga} \rightarrow \Gamma_{ga} + \sigma$).
 As such, the HDFG pathway considered in this work line-narrows correlated modes. 
@@
 Excited state populations can feed other modes, including the ground state and other vibrational/vibronic modes, inducing higher order processes.\cite{Carlson87, RN471}
-These feeding mechanisms can induce line-narrowing properties in spectroscopies that cannot line-narrow in third order perturbation theory.\cite{RN319, Carlson87, RN471, RN410}
+These feeding mechanisms can induce line-narrowing properties in spectroscopies that cannot line-narrow in third order perturbation theory.\cite{RN319, Carlson87, RN471}
 

### 2024-09-05 si.tex
added si part 1

\documentclass[aip, jcp, reprint, onecolumn, nofootinbib]{revtex4-2}

\bibliographystyle{apsrev4-2}

\usepackage{physics}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage[colorlinks=true, linkcolor=black, urlcolor=blue, citecolor=black, anchorcolor=black]{hyperref}

%supplementary figs
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thetable}{S\arabic{table}}
\renewcommand\theequation{S\arabic{equation}}
\renewcommand*{\thepage}{S\arabic{page}}

\graphicspath{{"figures/"}}
\begin{document}
%Title of paper
\title{Supporting Information for Coherent IR-Hyper-Raman Four Wave Mixing Spectroscopy}

\author{Ryan P. McDonnell} 
\author{Daniel D. Kohler}
\author{John C. Wright} \email{wright@chem.wisc.edu}

\affiliation{Department of Chemistry, 
        University of Wisconsin - Madison, 
        Madison, Wisconsin 53706, 
        United States of America}

\date{\today}

\maketitle
\tableofcontents
\clearpage

\section{Evaluating Herzberg-Teller Integrals for Harmonic Wells of Identical Curvature}
In this section, we discuss the evaluation of Herzberg-Teller integrals, in the limit of no Duschinsky coupling, when the ground and first excited state are harmonic wells.
We use the Hamiltonian described in the main text, $H = H_g |g) \left(g| + H_e |e\right) (e|$, where
\begin{subequations}\label{Hamiltonian}
	\begin{equation}
		H_g = \frac{\hbar \omega }{2} \left(p^2 + q^2 \right)
	\end{equation}
	and
	\begin{equation}
		H_e = \frac{\hbar \omega }{2} \left(p^2 +  (q-\Delta)^2 \right) + \hbar \omega_{eg}.
	\end{equation}
\end{subequations}
Here, $p,q$ are the dimensionless conjugate normal mode coordinates.
Franck-Condon factors and Herzberg-Teller integrals are often evaluated in position space using known solutions to the Harmonic Oscillator Hamiltonian \cite{RN230}
\begin{equation}
	\psi_m(q) = \langle q | m \rangle = N(m) H_m(q) \exp(-q^2/2)
\end{equation}
where $N(m) = (m! \ 2^m \pi^{\frac{1}{2}})^{-\frac{1}{2}}$ is the normalization factor and $H_m$ is the m$^{th}$ Hermite Polynomial.
We begin by generating an expression for $\mel{n}{q^k}{m}$, as this will resolve into Franck-Condon factors for $n = 0$ and Herzberg-Teller integrals for $n=1$.

By letting $\ket{m}$ belong to the ground state surface $|g)$ and $\ket{n}$ belong to the first excited surface $|e)$, we write\footnote{Note that any instance of $\int \mathrm{d}q f(q) \equiv \int_{-\infty}^{\infty} \mathrm{d}q f(q)$.}
\begin{equation}
\begin{split}
		\mel{n}{q^k}{m} &= \int \mathrm{d}q \psi^*_n(q+\Delta) q^k \psi_m(q)\\
		&= \int \mathrm{d}q N(n) N(m) H_n(q+\Delta) \exp(-\frac{(q + \Delta)^2}{2}) q^k H_m(q) \exp(-\frac{q^2}{2})
\end{split}
\end{equation}
Introducing $\tilde{N} \equiv N(n)N(m)$ and slightly rearranging, we see
\begin{equation}\label{key}
	\mel{n}{q^k}{m} = \tilde{N} \exp(-\frac{\Delta^2}{2}) \int \mathrm{d}q H_n(q+\Delta) q^k H_m(q) \exp(-q^2 - q\Delta)
\end{equation}
This is the key result.
As a side note, \autoref{key} explicitly shows
\begin{subequations}
	\begin{equation}
		\lim_{\Delta \rightarrow 0} \langle n | m \rangle = \delta_{n,m}
	\end{equation}
and
	\begin{equation}
	\lim_{\Delta \rightarrow 0} \mel{n}{q}{m} = \sqrt{\frac{1}{2}} \left(\sqrt{m}\delta_{n,m-1} + \sqrt{m+1} \delta_{n,m+1}\right)
	\end{equation}
\end{subequations}
i.e., as the offset vanishes, the normal harmonic oscillator selection rules are obtained, the expected result, where $\delta$ is the Kronecher delta.

It is well known that the Hermite polynomials $H_v(q)$ are linear combinations of $q^b$, $b \in \mathbf{N}$. 
Thus, evaluating \autoref{key} for arbitrary $m,n,k$ values resolves into evaluating sums of integrals of the form
\begin{equation}\label{integral}
	\int \mathrm{d}q \ q^w \exp(-q^2 - q\Delta)
\end{equation}
When $w=0$, the result is trivial:\footnote{$\int_{-\infty}^{\infty} \mathrm{d}x \exp(-(x-a)^2) = \sqrt{\pi}$}
\begin{equation}
	\begin{split}
		\int \mathrm{d}q \exp(-q^2 - q\Delta) &= \int \mathrm{d}q \exp(-(q^2 + q\Delta +\frac{\Delta^2}{4} - \frac{\Delta^2}{4}))\\
		&= \exp(\frac{\Delta^2}{4}) \int \mathrm{d}q \exp(-(q + \frac{\Delta}{2})^2) \\
		&= \sqrt{\pi} \exp(\frac{\Delta^2}{4})
	\end{split}
\end{equation}

For $w \neq 0$, \autoref{integral} is evaluated through repeated use of a well-known Gaussian identity
\begin{equation}\label{identity}
	\int \mathrm{d}q \ q^w \exp(-q^2 - q\Delta) = -\partial_{\Delta} \int \mathrm{d}q \ q^{w-1} \exp(-q^2 - q\Delta)
\end{equation}

We now have the background needed to calculate $\mel{1}{q}{0}$ for an arbitrary offset $\Delta$.
We note that Myers et al. have developed a general expression to evaluate Franck-Condon factors for two displaced harmonic wells of arbitrary curvature,\cite{Myers1982} so we focus our attention onto Herzberg-Teller integrals, which are not commonly tabulated.

Starting with \autoref{key},
\begin{equation}
\begin{split}
	\mel{1}{q}{0} = \tilde{N} \exp(-\frac{\Delta^2}{2}) \int \mathrm{d}q H_1(q+\Delta) q H_0(q) \exp(-q^2 - q\Delta)
\end{split}
\end{equation}
Using the fact that $H_0(q) = 1$ and $H_1(q) = 2q$, 
\begin{equation}\label{HT10}
	\begin{split}
		\mel{1}{q}{0} &= \tilde{N} \exp(-\frac{\Delta^2}{2}) \int \mathrm{d}q \ 2(q + \Delta) q \exp(-q^2 - q\Delta)\\
		&= 2\tilde{N} \exp(-\frac{\Delta^2}{2}) \int \mathrm{d}q \ (q^2 + q \Delta) \exp(-q^2 - q\Delta)\\
		&=  2\tilde{N} \exp(-\frac{\Delta^2}{2}) \left(\int \mathrm{d}q \ q^2 \exp(-q^2 - q\Delta) + 2\Delta \int \mathrm{d}q \ q \exp(-q^2 - q\Delta) \right)
	\end{split}
\end{equation}
These integrals are now easily evaluated using \autoref{identity}:
\begin{subequations}\label{evalGaussians}
	\begin{equation}
		\begin{split}
					\int \mathrm{d}q \ q \exp(-q^2 - q\Delta) &= -\partial_{\Delta} \left(\sqrt{\pi} \exp(\frac{\Delta^2}{4})\right)\\
					& = -\sqrt{\pi} \left(\frac{\Delta}{2} \exp(\frac{\Delta^2}{4})\right)
		\end{split}
	\end{equation}
giving
\begin{equation}
	\begin{split}
		\int \mathrm{d}q \ q^2 \exp(-q^2 - q\Delta) &= -\partial_{\Delta} \left(-\sqrt{\pi} \left(\frac{\Delta}{2} \exp(\frac{\Delta^2}{4})\right)\right)\\
		& =\sqrt{\pi} \left(\frac{1}{2}\exp(\frac{\Delta^2}{4}) + \frac{\Delta^2}{4} \exp(\frac{\Delta^2}{4})\right)
	\end{split}
\end{equation}
\end{subequations}
With $\tilde{N} = N(1)*N(0) = (1! \ 2^1 \pi^{\frac{1}{2}})^{-\frac{1}{2}} * (0! \ 2^0 \pi^{\frac{1}{2}})^{-\frac{1}{2}} = \sqrt{1/2\pi}$ and substituting the results of \autoref{evalGaussians} into \autoref{HT10}, 
\begin{equation}
	\mel{1}{q}{0} = \sqrt{\frac{1}{2}} (1 - \frac{\Delta^2}{2}) \exp(\frac{-\Delta^2}{4})
\end{equation}
The evaluation of other Herzberg-Teller integrals follows a similar process.
These results have been tabulated by Carlson. \cite{Carlson1988thesis}

\section{Impact of $\Delta$ on $A,B$ Terms in HDFG Spectra}
In the main text, the potential well offset ($\Delta$) was taken as $\Delta = 0.5$.
Here, we vary $\Delta$ to investigate its impact on the structure of the $\abs{A+B}$ spectrum.

\section{Evaluation of Equation 14}
In this section, the integral
\begin{equation}
	\begin{split}
		\gamma_{ijkl} &= \int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi)\\
		&=\frac{\sigma}{\pi}\int_{-\infty}^\infty \mathrm{d}\xi \frac{1}{\sigma^2 + \xi^2} \frac{\gamma_0}{\Delta_{ga}(\xi)\Delta_{ba}(\xi)} \\
		&= \frac{\gamma_0 \sigma}{\pi} \int_{-\infty}^\infty \mathrm{d}\xi\frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga}(0) - \xi} \frac{1}{\Delta_{ba}(0) + c\xi}\\
	\end{split}
\end{equation}
is evaluated using Contour integration.
\begin{figure}[!htbp]
	\centering
	\includegraphics[width=3.375in]{figures/corr_contour.png}
	\caption{Poles (black dots) and contour (blue line) used to evaluate \autoref{integraly} for (a) anti-correlated and (b) correlated modes.} 
	\label{fig:contours}
\end{figure}
\subsection{Anti-correlated Modes}
For anti-correlated modes, the poles are situated in the complex plane as shown in \autoref{fig:contours}a.
Since \autoref{integraly} is evaluated along the real axis, one can choose to evaluate the contour in the upper or lower half of the complex plane.
Since evaluating the residues in the upper or lower half of the complex plane yields the same result for \autoref{integraly}, we choose the contour which wraps around the least number of poles.
It is clear for c = -1 that there are four poles: $\pm i \sigma, \Delta_{ga}(0), \Delta_{ba}(0)$. 
Following \autoref{fig:contours}, the contour that wraps the upper half of the complex plane has only one pole, $i \sigma$; as such, we choose to evaluate \autoref{integraly} in the upper half of the complex plane for the case of anti-correlated modes through the residue theorem as
\begin{widetext}
	\begin{equation}
		\begin{split}
			\int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi) &= 2\pi i \sum_k \lim_{\xi \rightarrow \xi_k} P(\xi) \gamma_{ijkl}(\xi) (\xi - \xi_k)\\
			&= 2\pi i \frac{\gamma_0 \sigma}{\pi} \lim_{\xi \rightarrow i\sigma} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga}(0) - \xi} \frac{1}{\Delta_{ba}(0) - \xi} (\xi - i \sigma)\\
			&= 2 \gamma_0 \sigma i \lim_{\xi \rightarrow i\sigma} \frac{1}{\xi + i\sigma} \frac{1}{\Delta_{ga}(0) - \xi} \frac{1}{\Delta_{ba}(0) - \xi}\\
			&= 2\gamma_0 \sigma i \frac{1}{2i\sigma} \frac{1}{\Delta_{ga}(0) - i\sigma} \frac{1}{\Delta_{ba}(0) - i\sigma}\\
			&= \frac{\gamma_0}{\Delta_{ga}(i\sigma)\Delta_{ba}(i \sigma)}\\
		\end{split}
	\end{equation}
\end{widetext}

\subsection{Correlated Modes}
For correlated modes, the poles are situated in the complex plane as shown in \autoref{fig:contours}.
It is clear that no matter which contour is chosen, there is a contribution to the final integral from either $\Delta_{ba}(0)$ or $\Delta_{ga}(0)$. 
For the below calculation, we choose to evaluate along the contour in the bottom half of the complex plane, i.e., the poles ($\xi_k$) are $-i\sigma, \Delta_{ga}$.
We stress that since the integral is evaluated over $\mathbb{R}$ and there are no degenerate poles, the results below can be obtained by evaluating the contour which wraps around the poles $i\sigma, \Delta_{ba}$. 
Since the $\xi_k$ are nondegenerate,
\begin{widetext}
	\begin{equation}
		\begin{split}
			\int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi) &= 2\pi i \sum_k \lim_{\xi \rightarrow \xi_k} P(\xi) \gamma_{ijkl}(\xi) (\xi - \xi_k)\\
			&= 2\pi i \frac{\gamma_0 \sigma}{\pi}  \lim_{\xi \rightarrow -i\sigma} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga}(0) - \xi} \frac{1}{\Delta_{ba}(0) - \xi} (\xi + i \sigma) \\ 
			&+ 2\pi i \frac{\gamma_0 \sigma}{\pi} \lim_{\xi \rightarrow \Delta_{ga}(0)} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga}(0) - \xi} \frac{1}{\Delta_{ba}(0) - \xi} (\xi - \Delta_{ga})\\
			&= 2 \gamma_0 i \sigma (\frac{1}{2 i \sigma} \frac{1}{-i \sigma - \Delta_{ga}(0)} \frac{1}{\Delta_{ba}(0) - i\sigma} ) - 2 \gamma_0 i \sigma (\frac{1}{\sigma^2 + (\Delta_{ga} (0))^2} \frac{1}{\Delta_{ga}(0) + \Delta_{ba}(0)} )\\
			&= -\frac{\gamma_0}{\Delta_{ga}(0) + i \sigma} (\frac{1}{\Delta_{ba}(0) - i \sigma} + \frac{2i\sigma}{(\Delta_{ga}(0) - i \sigma)(\Delta_{ga}(0) + \Delta_{ba}(0))})\\
		\end{split}
	\end{equation}
\end{widetext}
Generally, when starting from the ground state, non-parametric spectroscopies line-narrow correlated modes, and parametric spectroscopies line-narrow anti-correlated modes. \cite{Dick83_1, RN425}

\section{References}
% Create the reference section using BibTeX:
\bibliography{library.bib}

\end{document}
%

### 2024-09-06 paper.tex
edits

@@
 We point this out because a persistent belief in Raman analysis is that $A$ terms disappear and $B$ terms dominate when significantly detuned from electronic resonance.
-% such that $\Delta_{ev', g0} \approx \Delta_{eg}$, i.e., the resonance denominator loses $\ket{v'}$ dependence. 
 The belief arises from the approximation $\abs{\omega_{ev',gv} - 2\omega_2} \gg 2\Gamma_{ev',gv}$, which then removes $A$ through a closure relationship.\cite{Neddersen1989}
-As has been discussed elsewhere, however, this approximation is in many cases invalid, especially when vibrational energies are large, like those explored here.\cite{Warshel1977, Li1990, Gong2015}
+As has been discussed elsewhere, however, this approximation is in many cases invalid, especially when vibrational energies are large, like those explored here.\cite{Warshel1977, Myers1982, Li1990, Gong2015}
 This means that it is difficult to isolate $B$ terms when $A$ terms are present.

### 2024-09-06 si.tex
edits

@@
 
-It is well known that the Hermite polynomials $H_v(q)$ are linear combinations of $q^b$, $b \in \mathbf{N}$. 
+It is well known that the Hermite polynomials $H_v(q)$ are linear combinations of $q^w$, $w \in \mathbf{N}$. 
 Thus, evaluating \autoref{key} for arbitrary $m,n,k$ values resolves into evaluating sums of integrals of the form
@@
 \end{equation}
-
  For $w \neq 0$, \autoref{integral} is evaluated through repeated use of a well-known Gaussian identity
@@
 have developed a general expression to evaluate Franck-Condon factors for two displaced harmonic wells of arbitrary curvature,\cite{Myers1982} so we focus our attention onto Herzberg-Teller integrals, which are not commonly tabulated.
-
 Starting with \autoref{key},
@@
 \end{equation}
-Using the fact that $H_0(q) = 1$ and $H_1(q) = 2q$, 
+Using $H_0(q) = 1$ and $H_1(q) = 2q$,\cite{RN230} 
 \begin{equation}\label{HT10}
@@
 					\int \mathrm{d}q \ q \exp(-q^2 - q\Delta) &= -\partial_{\Delta} \left(\sqrt{\pi} \exp(\frac{\Delta^2}{4})\right)\\
-					& = -\sqrt{\pi} \left(\frac{\Delta}{2} \exp(\frac{\Delta^2}{4})\right)
+					& = -\sqrt{\pi} \frac{\Delta}{2} \exp(\frac{\Delta^2}{4})
 		\end{split}
@@
 Here, we vary $\Delta$ to investigate its impact on the structure of the $\abs{A+B}$ spectrum.
+First, we investigate how the Franck-Condon factors and Herzberg-Teller integrals are manipulated as a function of $\Delta$.
+%TODO - plot
 

### 2024-09-06 figures/Varying_Delta_SI.py

@@ -1,0 +1,224 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Tue Jan 17 09:28:39 2023
+
+@author: rpm
+"""
+import numpy as np
+import WrightTools as wt
+import matplotlib.pyplot as plt 
+from matplotlib.patches import FancyArrowPatch
+
+wt.artists.apply_rcparams(kind="publication")
+
+save = False
+fontsize = 18
+
+#define harmonic wells and coordinates
+d = [0.1, 0.2, 0.6] #offset for es
+
+#make figure
+cols = [1, 1] 
+aspects = [[[0, 0], 1], [[1, 0], 1]] 
+
+
+
+#todo: make an array so I can just call specific matrix element of the fc and ht factors, then do a for loop over that array, should work out well.
+
+
+#define Franck-Condon factors following page 164 of Roger Carlson's thesis in terms of 'q', the offset
+def f00(q): #<0|0>
+    return np.e**(-q**2/4)
+
+def f01(q): #<0|1>
+    return -q/(np.sqrt(2)) * f00(q)
+
+def f10(q): #<1|0>
+    return -1*f01(q)
+
+def f11(q): #<1|1>
+    return (1 - q**2/2) *f00(q)
+
+def f02(q): #<0|2>
+    return q**2/(2*np.sqrt(2)) * f00(q)
+
+def f20(q): #<2|0>
+    return f02(q)
+
+def f12(q): #<1|2>
+    return -q * (1 - q**2/4) *f00(q)
+    
+
+#define Herzberg Teller overlap integrals following page 165 of Roger Carlson's thesis in terms of q
+def h00(q): #<0|Q|0>
+    return -q/2 * f00(q)
+
+def h01(q): #<0|Q|1>
+    return 1/np.sqrt(2) * (1 + q**2 /2) * f00(q)
+
+def h10(q): #<1|Q|0>
+    return 1/np.sqrt(2) * (1 - q**2 /2) * f00(q)
+
+def h11(q): #<1|Q|1>
+    return -q/2 * (1 - q**2 / 2) * f00(q)
+
+def h12(q): #<1|Q|2>
+    return (1 + q**2/4 - q**4/8) * f00(q)
+
+def h20(q): #<2|Q|0>
[…]

### 2024-09-06 figures/plotting_fcht.py

@@ -1,0 +1,148 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Tue Jan 17 09:28:39 2023
+
+@author: rpm
+"""
+import numpy as np
+import WrightTools as wt
+import matplotlib.pyplot as plt 
+from matplotlib.patches import FancyArrowPatch
+
+wt.artists.apply_rcparams(kind="publication")
+
+save = False
+fontsize = 18
+
+#define harmonic wells and coordinates
+d = np.linspace(0, 5, 5000)
+
+#make figure
+cols = [1, 1] 
+aspects = [[[0, 0], 1], [[1, 0], 1]] 
+
+
+
+#todo: make an array so I can just call specific matrix element of the fc and ht factors, then do a for loop over that array, should work out well.
+
+
+#define Franck-Condon factors following page 164 of Roger Carlson's thesis in terms of 'q', the offset
+def f00(q): #<0|0>
+    return np.e**(-q**2/4)
+
+def f01(q): #<0|1>
+    return -q/(np.sqrt(2)) * f00(q)
+
+def f10(q): #<1|0>
+    return -1*f01(q)
+
+def f11(q): #<1|1>
+    return (1 - q**2/2) *f00(q)
+
+def f02(q): #<0|2>
+    return q**2/(2*np.sqrt(2)) * f00(q)
+
+def f20(q): #<2|0>
+    return f02(q)
+
+def f12(q): #<1|2>
+    return -q * (1 - q**2/4) *f00(q)
+    
+
+#define Herzberg Teller overlap integrals following page 165 of Roger Carlson's thesis in terms of q
+def h00(q): #<0|Q|0>
+    return -q/2 * f00(q)
+
+def h01(q): #<0|Q|1>
+    return 1/np.sqrt(2) * (1 + q**2 /2) * f00(q)
+
+def h10(q): #<1|Q|0>
+    return 1/np.sqrt(2) * (1 - q**2 /2) * f00(q)
+
+def h11(q): #<1|Q|1>
+    return -q/2 * (1 - q**2 / 2) * f00(q)
+
+def h12(q): #<1|Q|2>
+    return (1 + q**2/4 - q**4/8) * f00(q)
+
+def h20(q): #<2|Q|0>
+    return -q/np.sqrt(2) * (1 - q**2 /4) * f00(q)
+
+
+#plot
[…]

### 2024-09-06 paper.tex
in the middle of checking roger's thesis

@@
 \end{subequations}
-for the ground ($H_g$) and first excited ($H_e$) states, where $p$ (momentum) and $q$ (position) are the dimensionless conjugate coordinates of the normal mode, the A and B contributions can be evaluated using Franck-Condon and Herzberg-Teller integrals tabulated in terms of the dimensionless normal mode $q$ and offset parameter $\xi$ (\autoref{fig:doubres_spec}a).\cite{Carlson1988thesis}
+for the ground ($H_g$) and first excited ($H_e$) states, where $p$ (momentum) and $q$ (position) are the dimensionless conjugate coordinates of the normal mode, the A and B contributions can be evaluated using Franck-Condon and Herzberg-Teller integrals tabulated in terms of the dimensionless normal mode $q$ and offset parameter $\xi$ (\autoref{fig:doubres_spec}a).
 System-bath interactions are neglected for this discussion.
@@
 	\caption{\label{T:contributions} Franck-Condon and/or Herzberg-Teller contributions to $A$, $B_1$, $B_2$ terms between $\ket{g,0}$, $\ket{g,1}$ and vibronic states $\ket{e,0}$, $\ket{e,1}$, $\ket{e,2}$ for \autoref{Hamiltonian} with an offset $\xi = 0.5$.
-	Closed-form expressions for the Franck-Condon and Herzberg-Teller integrals used here have been tabulated by Carlson.\cite{Carlson1988thesis}}
+	The bra and ket labels are written according to their order in $A$, $B_1$, $B_2$ as written in \autoref{ABterms_DR}.
+	Closed-form expressions for the Franck-Condon and Herzberg-Teller integrals used here are tabulated in the Supporting Information.}
 	\begin{ruledtabular}

### 2024-09-06 si.tex
in the middle of checking roger's thesis

@@
 
-By letting $\ket{m}$ belong to the ground state surface $|g)$ and $\ket{n}$ belong to the first excited surface $|e)$, we write\footnote{Note that any instance of $\int \mathrm{d}q f(q) \equiv \int_{-\infty}^{\infty} \mathrm{d}q f(q)$.}
+By letting $\ket{m}$ belong to the ground state surface $|g)$ and $\ket{n}$ belong to the first excited surface $|e)$, we write
 \begin{equation}
 \begin{split}
-		\mel{n}{q^k}{m} &= \int \mathrm{d}q \psi^*_n(q+\Delta) q^k \psi_m(q)\\
-		&= \int \mathrm{d}q N(n) N(m) H_n(q+\Delta) \exp(-\frac{(q + \Delta)^2}{2}) q^k H_m(q) \exp(-\frac{q^2}{2})
+		\mel{n}{q^k}{m} &= \int_{-\infty}^\infty \mathrm{d}q \psi^*_n(q-\Delta) q^k \psi_m(q)\\
+		&= \int_{-\infty}^\infty \mathrm{d}q N(n) N(m) H_n(q-\Delta) \exp(-\frac{(q - \Delta)^2}{2}) q^k H_m(q) \exp(-\frac{q^2}{2})
 \end{split}
@@
 \begin{equation}\label{key}
-	\mel{n}{q^k}{m} = \tilde{N} \exp(-\frac{\Delta^2}{2}) \int \mathrm{d}q H_n(q+\Delta) q^k H_m(q) \exp(-q^2 - q\Delta)
+	\mel{n}{q^k}{m} = \tilde{N} \exp(-\frac{\Delta^2}{2}) \int_{-\infty}^\infty \mathrm{d}q H_n(q+\Delta) q^k H_m(q) \exp(-q^2 + q\Delta)
 \end{equation}
@@
 \begin{equation}\label{integral}
-	\int \mathrm{d}q \ q^w \exp(-q^2 - q\Delta)
+	\int_{-\infty}^\infty \mathrm{d}q \ q^w \exp(-q^2 + q\Delta)
 \end{equation}
@@
 	\begin{split}
-		\int \mathrm{d}q \exp(-q^2 - q\Delta) &= \int \mathrm{d}q \exp(-(q^2 + q\Delta +\frac{\Delta^2}{4} - \frac{\Delta^2}{4}))\\
-		&= \exp(\frac{\Delta^2}{4}) \int \mathrm{d}q \exp(-(q + \frac{\Delta}{2})^2) \\
+		\int_{-\infty}^\infty \mathrm{d}q \exp(-q^2 + q\Delta) &= \int_{-\infty}^\infty \mathrm{d}q \exp(-(q^2 + q\Delta +\frac{\Delta^2}{4} - \frac{\Delta^2}{4}))\\
+		&= \exp(\frac{\Delta^2}{4}) \int_{-\infty}^\infty \mathrm{d}q \exp(-(q - \frac{\Delta}{2})^2) \\
 		&= \sqrt{\pi} \exp(\frac{\Delta^2}{4})
@@
 \begin{equation}\label{identity}
-	\int \mathrm{d}q \ q^w \exp(-q^2 - q\Delta) = -\partial_{\Delta} \int \mathrm{d}q \ q^{w-1} \exp(-q^2 - q\Delta)
+	\int_{-\infty}^\infty \mathrm{d}q \ q^w \exp(-q^2 + q\Delta) = \partial_{\Delta} \int_{-\infty}^\infty \mathrm{d}q \ q^{w-1} \exp(-q^2 + q\Delta)
 \end{equation}
@@
 \begin{split}
-	\mel{1}{q}{0} = \tilde{N} \exp(-\frac{\Delta^2}{2}) \int \mathrm{d}q H_1(q+\Delta) q H_0(q) \exp(-q^2 - q\Delta)
+	\mel{1}{q}{0} = \tilde{N} \exp(-\frac{\Delta^2}{2}) \int_{-\infty}^\infty \mathrm{d}q H_1(q+\Delta) q H_0(q) \exp(-q^2 - q\Delta)
 \end{split}
@@
 	\begin{split}
-		\mel{1}{q}{0} &= \tilde{N} \exp(-\frac{\Delta^2}{2}) \int \mathrm{d}q \ 2(q + \Delta) q \exp(-q^2 - q\Delta)\\
-		&= 2\tilde{N} \exp(-\frac{\Delta^2}{2}) \int \mathrm{d}q \ (q^2 + q \Delta) \exp(-q^2 - q\Delta)\\
-		&=  2\tilde{N} \exp(-\frac{\Delta^2}{2}) \left(\int \mathrm{d}q \ q^2 \exp(-q^2 - q\Delta) + 2\Delta \int \mathrm{d}q \ q \exp(-q^2 - q\Delta) \right)
+		\mel{1}{q}{0} &= \tilde{N} \exp(-\frac{\Delta^2}{2}) \int_{-\infty}^\infty \mathrm{d}q \ 2(q + \Delta) q \exp(-q^2 - q\Delta)\\
+		&= 2\tilde{N} \exp(-\frac{\Delta^2}{2}) \int_{-\infty}^\infty \mathrm{d}q \ (q^2 + q \Delta) \exp(-q^2 - q\Delta)\\
+		&=  2\tilde{N} \exp(-\frac{\Delta^2}{2}) \left(\int_{-\infty}^\infty \mathrm{d}q \ q^2 \exp(-q^2 - q\Delta) + 2\Delta \int_{-\infty}^\infty \mathrm{d}q \ q \exp(-q^2 - q\Delta) \right)
 	\end{split}
@@
 		\begin{split}
-					\int \mathrm{d}q \ q \exp(-q^2 - q\Delta) &= -\partial_{\Delta} \left(\sqrt{\pi} \exp(\frac{\Delta^2}{4})\right)\\
+					\int_{-\infty}^\infty \mathrm{d}q \ q \exp(-q^2 - q\Delta) &= -\partial_{\Delta} \left(\sqrt{\pi} \exp(\frac{\Delta^2}{4})\right)\\
 					& = -\sqrt{\pi} \frac{\Delta}{2} \exp(\frac{\Delta^2}{4})
@@
 	\begin{split}
-		\int \mathrm{d}q \ q^2 \exp(-q^2 - q\Delta) &= -\partial_{\Delta} \left(-\sqrt{\pi} \left(\frac{\Delta}{2} \exp(\frac{\Delta^2}{4})\right)\right)\\
+		\int_{-\infty}^\infty \mathrm{d}q \ q^2 \exp(-q^2 - q\Delta) &= -\partial_{\Delta} \left(-\sqrt{\pi} \left(\frac{\Delta}{2} \exp(\frac{\Delta^2}{4})\right)\right)\\
 		& =\sqrt{\pi} \left(\frac{1}{2}\exp(\frac{\Delta^2}{4}) + \frac{\Delta^2}{4} \exp(\frac{\Delta^2}{4})\right)
@@
 \end{equation}
-The evaluation of other Herzberg-Teller integrals follows a similar process.
-These results have been tabulated by Carlson. \cite{Carlson1988thesis}
+The evaluation of other Herzberg-Teller integrals follows a similar process, or by using symbolic manipulation packages. 
+The relevant Franck-Condon factors and Herzberg-Teller integrals, assuming identical curvature and no Duschinsky coupling, are tabulated below.
+
+\begin{table}[!htbp]
+	\caption{\label{T:FC Integral} Franck-Condon Factors.}
+	\begin{ruledtabular}
+		\begin{tabular}{cc}
+			$\mel{n}{0}{m}$ & Expression\\
+			\hline  
+			$A$ & $\langle 1 | 0 \rangle \langle 0 | 0 \rangle = 0.31 $  \\
+
+			$B_1$ & $\langle 1 | 0 \rangle \mel{0}{Q}{0} = -0.08$ \\
+
+			$B_2$ & $\mel{1}{Q}{0} \langle 0 | 0 \rangle = 0.55$\\
+		\end{tabular}
+	\end{ruledtabular}
+\end{table}
+
+\begin{table}[!htbp]
+	\caption{\label{T:HT Integral} Franck-Condon Factors.}
+	\begin{ruledtabular}
+		\begin{tabular}{cc}
+			$\mel{n}{q}{m}$& Expression\\
+			\hline  
+			$\mel{0}{q}{0}$ & $\frac{\Delta}{2} \exp(-\Delta^2/4)$  \\ 
+			$\mel{1}{q}{0}$ & $\frac{1}{\sqrt{2}} \exp(-\Delta^2/4)(1 - \Delta^2/2) $ \\
+			$\mel{2}{q}{0}$ & $\frac{1}{\sqrt{2}} \exp(-\Delta^2/4)(1 - \Delta^2/2) $ \\
+			$\mel{0}{q}{1}$ & $\frac{1}{\sqrt{2}} \exp(-\Delta^2/4)(1 + \Delta^2/2) $ \\
+			$\mel{1}{q}{1}$ & $\frac{\Delta}{{2}} \exp(-\Delta^2/4)(1 - \Delta^2/2) $ \\
+			$\mel{2}{q}{1}$ & $\frac{\Delta}{{2}} \exp(-\Delta^2/4)(1 - \Delta^2/2) $ \\
+			$\mel{1}{q}{1}$ & $\frac{\Delta}{{2}} \exp(-\Delta^2/4)(1 - \Delta^2/2) $ \\
+
+		\end{tabular}
+	\end{ruledtabular}
+\end{table}
 

### 2024-09-07 paper.tex
fixing ht and fc integrals

@@
 \begin{equation}\label{drgamma_notaylor}
-	\gamma_{ijkl} = -\frac{1}{\varepsilon_0} \frac{1}{4D \hbar^3} \sum_{m,n,e,v'} \frac{
-		R_{i}^{gv, ev'} 
-		R_{j}^{ev',mn} 
+	\gamma_{ijkl} = -\frac{1}{\varepsilon_0} \frac{1}{4D \hbar^3} \sum_{m,n,e,\tilde{v}'} \frac{
+		R_{i}^{gv, e\tilde{v}'} 
+		R_{j}^{e\tilde{v}',mn} 
 		R_{k}^{mn,g0} 
 		R_{l}^{g0,gv} 
-	}{	\Delta_{ev', gv}
+	}{	\Delta_{e\tilde{v}', gv}
 		\Delta_{mn, gv}
@@
 where $R_{i}^{ab,cd}$ is the i$^{th}$ element of $\mel{a,b}{\vec{R}}{c,d}$.
-It is common in the hyper-Raman literature to write $\Delta_{ev', gv} \Delta_{mn, gv} = \Delta_{ev', gv}$.
+It is common in the hyper-Raman literature to write $\Delta_{e\tilde{v}', gv} \Delta_{mn, gv} = \Delta_{e\tilde{v}', gv}$.
 Using our definition of vibronic states, we can write, for example,
-$R_{i}^{gv,ev'} = \mel{v}{M_i^{ge}}{v'}$, where $\vec{M}^{ab} = (a|\vec{R}|b)$.\cite{Ziegler1974}
+$R_{i}^{gv,e\tilde{v}'} = \mel{v}{M_i^{ge}}{\tilde{v}'}$, where $\vec{M}^{ab} = (a|\vec{R}|b)$.\cite{Ziegler1974}
 Expanding $\vec{M}^{ij}$ to $\order{Q}$ about the equilibrium point of the ground state potential surface as
@@
 	\begin{split}
-		A_{ijk} = \frac{1}{\hbar^2}\sum_{m,e,v'} M^{ge}_{0,i} 
+		A_{ijk} = \frac{1}{\hbar^2}\sum_{m,e,\tilde{v}'} M^{ge}_{0,i} 
 		M^{em}_{0,j} 
 		M^{mg}_{0,k}
-		 \langle v | v' \rangle
-		 \langle v' | 0 \rangle 
-		 \frac{1}{\Delta_{ev', gv}}
+		 \langle v | \tilde{v}' \rangle
+		 \langle \tilde{v}' | 0 \rangle 
+		 \frac{1}{\Delta_{e\tilde{v}', gv}}
 		 \\
@@
 		\begin{split}
-			B_{1_{ijk}} &= \frac{1}{\hbar^2} \sum_{m,e,v',z} M^{ge}_{0,i} \left(
+			B_{1_{ijk}} &= \frac{1}{\hbar^2} \sum_{m,e,\tilde{v}',z} M^{ge}_{0,i} \left(
 				\frac{\partial M^{em}_{j}}{\partial Q_z} M^{mg}_{0,k}  
@@
 			\right)
-			\langle v | v' \rangle \mel{v'}{Q_z}{0} \frac{1}{\Delta_{ev', gv}}\\
+			\langle v | \tilde{v}' \rangle \mel{\tilde{v}'}{Q_z}{0} \frac{1}{\Delta_{e\tilde{v}', gv}}\\
 		\end{split}
@@
 	\begin{split}
-			B_{2_{ijk}} = \frac{1}{\hbar^2} \sum_{m,e,v',z} \frac{\partial M^{ge}_{i}}{\partial Q_z} M^{em}_{0,j} 
-			M^{mg}_{0,k} \mel{v}{Q_z}{v'} 
-			\langle v' | 0 \rangle 
-			\frac{1}{\Delta_{ev', gv}}
+			B_{2_{ijk}} = \frac{1}{\hbar^2} \sum_{m,e,\tilde{v}',z} \frac{\partial M^{ge}_{i}}{\partial Q_z} M^{em}_{0,j} 
+			M^{mg}_{0,k} \mel{v}{Q_z}{\tilde{v}'} 
+			\langle \tilde{v}' | 0 \rangle 
+			\frac{1}{\Delta_{e\tilde{v}', gv}}
 	\end{split}
@@
 where $\langle a | b \rangle$ and $\mel{a}{Q}{b}$ are Franck-Condon factors and Herzberg-Teller-type integrals, respectively.
+To ease readability, we use $\ket{a}$ to refer to ground state vibrational modes and $\ket{\tilde{b}}$ to refer to excited state vibrational modes. 
 Duschinsky rotation effects are ignored in this discussion. \cite{Duschinsky1937}
@@
 			\begin{split}
-				A_{ijk} = \frac{1}{\hbar}\sum_{v'} M^{ge}_{0,i} 
+				A_{ijk} = \frac{1}{\hbar}\sum_{\tilde{v}'} M^{ge}_{0,i} 
 				\Lambda^{eg}_{0,jk}
-				\langle 1 | v' \rangle
-				\langle v' | 0 \rangle 
-				\frac{1}{\Delta_{ev',gv}}
+				\langle 1 | \tilde{v}' \rangle
+				\langle \tilde{v}' | 0 \rangle 
+				\frac{1}{\Delta_{e\tilde{v}',gv}}
 				\\
@@
 			\begin{split}
-				B_{1_{ijk}} &= \frac{1}{\hbar} \sum_{v'} M^{ge}_{0,i}
-				\frac{\partial \Lambda^{eg}_{jk}}{\partial Q} \langle 1 | v' \rangle \mel{v'}{Q}{0} 
-				\frac{1}{\Delta_{ev', gv}}\\
+				B_{1_{ijk}} &= \frac{1}{\hbar} \sum_{\tilde{v}'} M^{ge}_{0,i}
+				\frac{\partial \Lambda^{eg}_{jk}}{\partial Q} \langle 1 | \tilde{v}' \rangle \mel{\tilde{v}'}{Q}{0} 
+				\frac{1}{\Delta_{e\tilde{v}', gv}}\\
 			\end{split}
@@
 			\begin{split}
-				B_{2_{ijk}} = \frac{1}{\hbar} \sum_{v'} \frac{\partial M^{ge}_{i}}{\partial Q} 
+				B_{2_{ijk}} = \frac{1}{\hbar} \sum_{\tilde{v}'} \frac{\partial M^{ge}_{i}}{\partial Q} 
 				\Lambda^{eg}_{0,jk} 
-				\mel{1}{Q}{v'} 
-				\langle v' | 0 \rangle 
-				\frac{1}{\Delta_{ev',gv}}
+				\mel{1}{Q}{\tilde{v}'} 
+				\langle \tilde{v}' | 0 \rangle 
+				\frac{1}{\Delta_{e\tilde{v}',gv}}
 			\end{split}
@@
 	\caption{Contributions of $A, B$ (\autoref{ABterms_DR}) to HDFG spectrum for a simple two harmonic well system.
-		(a) Potential energy surfaces for a two-well system, (b) 1D HDFG spectrum for $\xi = 0.5$, $\omega_1 = \omega_{g1, g0}$. 
+		(a) Potential energy surfaces for a two-well system, (b) 1D HDFG spectrum for $\Delta = 0.5$, $\omega_1 = \omega_{g1, g0}$. 
 		It is assumed that $\omega_2 = \omega_3$.
 		Note that (b) plots magnitudes of the labeled quantities.
-		The vibrational states on the $|g)$ and $|e)$ manifolds are spaced 2200 cm$^{-1}$ apart, with the vibronic states $\ket{e,v'}$ given linewidths of 700 cm$^{-1}$ and $\hbar \omega_{eg}$ = 30000 cm$^{-1}$.
-		Dotted lines in (b) denote the $v'$ = 0, 1, 2 vibronic resonances. 
+		The vibrational states on the $|g)$ and $|e)$ manifolds are spaced 2200 cm$^{-1}$ apart, with the vibronic states $\ket{e,\tilde{v}'}$ given linewidths of 700 cm$^{-1}$ and $\hbar \omega_{eg}$ = 30000 cm$^{-1}$.
+		Dotted lines in (b) denote the $\tilde{v}'$ = 0, 1, 2 vibronic resonances. 
 		The vibronic one and two photon absorption operators are scaled such that $\abs{B}/\abs{A} \sim$ 0.1, following Chung and Ziegler. \cite{Ziegler1988}
@@
 	\begin{equation}
-		H_e = \frac{\hbar \omega }{2} \left(p^2 +  (q-\xi)^2 \right) + \hbar \omega_{eg}
+		H_e = \frac{\hbar \omega }{2} \left(p^2 +  (q-\Delta)^2 \right) + \hbar \omega_{eg}
 	\end{equation}
 \end{subequations}
-for the ground ($H_g$) and first excited ($H_e$) states, where $p$ (momentum) and $q$ (position) are the dimensionless conjugate coordinates of the normal mode, the A and B contributions can be evaluated using Franck-Condon and Herzberg-Teller integrals tabulated in terms of the dimensionless normal mode $q$ and offset parameter $\xi$ (\autoref{fig:doubres_spec}a).
+for the ground ($H_g$) and first excited ($H_e$) states, where $p$ (momentum) and $q$ (position) are the dimensionless conjugate coordinates of the normal mode, the A and B contributions can be evaluated using Franck-Condon and Herzberg-Teller integrals tabulated in terms of the dimensionless normal mode $q$ and offset parameter $\Delta$ (\autoref{fig:doubres_spec}a).
 System-bath interactions are neglected for this discussion.
-For simplicity, we restrict consideration to $v^\prime \in \{0,1,2\}$ and take $\xi = 0.5$.
+For simplicity, we restrict consideration to $v^\prime \in \{0,1,2\}$ and take $\Delta = 0.5$.
 Note that $q = \sqrt{\frac{\omega}{\hbar}} Q$.
@@
 For an allowed electronic transition, the brightness of a vibronic resonance is controlled by overlap of ground and excited state vibrational wavefunctions (Franck-Condon factors).
-The $A$ term relies on excited state perturbations to the vibrational wavefunctions; if the excited electronic state minimally changes potential energy surface, so that ground and excited state vibrational eigenfunctions are identical, $\langle 1 | v^\prime \rangle \langle v^\prime | 0 \rangle = 0$ and $A$ vanishes.
-This follows from $\lim_{\xi \rightarrow 0} \langle v' | 0 \rangle = 0$, $v^\prime \neq 0$, for wells with identical curvature.
-Some $B$ terms do survive in the same limit, however; for instance, $B_1$ survives for $v^\prime=1$ and $B_2$ survives for $v^\prime=0$.
+The $A$ term relies on excited state perturbations to the vibrational wavefunctions; if the excited electronic state minimally changes potential energy surface, so that ground and excited state vibrational eigenfunctions are identical, $\langle 1 | \tilde{v}' \rangle \langle \tilde{v}' | 0 \rangle = 0$ and $A$ vanishes, as discussed in the supporting information.
+Some $B$ terms do survive in the same limit, however; for instance, $B_1$ survives for $\tilde{v}'=1$ and $B_2$ survives for $\tilde{v}'=0$.
 In the absence of an $A$ term, the $B$ terms will dominate.
@@
 \autoref{fig:doubres_spec}b shows the simulated $\omega_2+\omega_3$ spectrum for this two-well system.  The spectrum selectively probes vibronic pathways from $\ket{g,0}$ to $\ket{g,1}$.
-In the resonant region, the $A$ and $B$ terms contain character from all three possible transitions between $\ket{g,0}$, $\ket{e,v'}$ and $\ket{g,1}$. 
+In the resonant region, the $A$ and $B$ terms contain character from all three possible transitions between $\ket{g,0}$, $\ket{e,\tilde{v}'}$ and $\ket{g,1}$. 
 Significant contributions from $\ket{e,0}$ and $\ket{e,1}$ in the $A$ term spectrum correspond well with expectations given the relative wavefunction overlap in \autoref{fig:doubres_spec}a, tabulated in \autoref{T:contributions}.
@@
 
-In the pre-resonance region, both $A$ and $B$ terms die off as $\sim \Delta_{e0,gv}^{-1}$.
+In the pre-resonance region, both $A$ and $B$ terms die off as $\sim \Delta_{e\tilde{v}',gv}^{-1}$.
 We point this out because a persistent belief in Raman analysis is that $A$ terms disappear and $B$ terms dominate when significantly detuned from electronic resonance.
-The belief arises from the approximation $\abs{\omega_{ev',gv} - 2\omega_2} \gg 2\Gamma_{ev',gv}$, which then removes $A$ through a closure relationship.\cite{Neddersen1989}
+The belief arises from the approximation $\abs{\omega_{e\tilde{v}',gv} - 2\omega_2} \gg 2\Gamma_{e\tilde{v}',gv}$, which then removes $A$ through a closure relationship.\cite{Neddersen1989}
 As has been discussed elsewhere, however, this approximation is in many cases invalid, especially when vibrational energies are large, like those explored here.\cite{Warshel1977, Myers1982, Li1990, Gong2015}
@@
 \begin{table}[!htbp]
-	\caption{\label{T:contributions} Franck-Condon and/or Herzberg-Teller contributions to $A$, $B_1$, $B_2$ terms between $\ket{g,0}$, $\ket{g,1}$ and vibronic states $\ket{e,0}$, $\ket{e,1}$, $\ket{e,2}$ for \autoref{Hamiltonian} with an offset $\xi = 0.5$.
+	\caption{\label{T:contributions} Franck-Condon and/or Herzberg-Teller contributions to $A$, $B_1$, $B_2$ terms between $\ket{g,0}$, $\ket{g,1}$ and vibronic states $\ket{e,\tilde{0}}$, $\ket{e,\tilde{1}}$, $\ket{e,\tilde{2}}$ for \autoref{Hamiltonian} with an offset $\Delta = 0.5$.
 	The bra and ket labels are written according to their order in $A$, $B_1$, $B_2$ as written in \autoref{ABterms_DR}.
@@
 		\begin{tabular}{cccc}
-			$2\omega_2$ Electronic Resonance & $\ket{e,0}$ & $\ket{e,1}$ & $\ket{e,2}$\\
+			$2\omega_2$ Electronic Resonance & $\ket{e,\tilde{0}}$ & $\ket{e,\tilde{1}}$ & $\ket{e,\tilde{2}}$\\
 			\hline  
 			$A$ 
-			& $\langle 1 | 0 \rangle \langle 0 | 0 \rangle = 0.31 $  
-			& $\langle 1 | 1 \rangle \langle 1 | 0 \rangle = 0.27 $ 
-			& $\langle 1 | 2 \rangle \langle 2 | 0 \rangle = -0.04$\\
+			& $\langle 1 | \tilde{0} \rangle \langle \tilde{0} | 0 \rangle = 0.31 $  
+			& $\langle 1 | \tilde{1} \rangle \langle \tilde{1} | 0 \rangle = 0.27 $ 
+			& $\langle 1 | \tilde{2} \rangle \langle \tilde{2} | 0 \rangle = -0.04$\\
 
 			$B_1$ 
-			& $\langle 1 | 0 \rangle \mel{0}{Q}{0} = -0.08$ 
-			& $\langle 1 | 1 \rangle \mel{1}{Q}{0} = 0.48$ 
-			&$\langle 1 | 2 \rangle \mel{2}{Q}{0} = 0.14$\\
+			& $\langle 1 | \tilde{0} \rangle \mel{\tilde{0}}{Q}{0} = -0.08$ 
+			& $\langle 1 | \tilde{1} \rangle \mel{\tilde{1}}{Q}{0} = 0.48$ 
+			&$\langle 1 | \tilde{2} \rangle \mel{\tilde{2}}{Q}{0} = 0.14$\\
 
 			$B_2$ 
-			& $\mel{1}{Q}{0} \langle 0 | 0 \rangle = 0.55$  
-			& $\mel{1}{Q}{1} \langle 1 | 0 \rangle = -0.07$ 
-			& $\mel{1}{Q}{2} \langle 2 | 0 \rangle = 0.08$\\
+			& $\mel{1}{Q}{\tilde{0}} \langle \tilde{0} | 0 \rangle = 0.55$  
+			& $\mel{1}{Q}{\tilde{1}} \langle \tilde{1} | 0 \rangle = -0.07$ 
+			& $\mel{1}{Q}{\tilde{2}} \langle \tilde{2} | 0 \rangle = 0.08$\\
 		\end{tabular}
@@
 An often unavoidable consequence in electronic spectroscopy is broadened lineshapes due to a high density of vibronic modes. 
-In the discussion that follows, we assume that a vibrational mode in the ground state, $\ket{g,v}$, is correlated to the frequency of a vibronic $\ket{e,v'}$.\cite{Carlson1990line, Dong2015}
+In the discussion that follows, we assume that a vibrational mode in the ground state, $\ket{g,v}$, is correlated to the frequency of a vibronic $\ket{e,\tilde{v}'}$.\cite{Carlson1990line, Dong2015}
 If the frequency of $\ket{g,v}$ is written as $\omega_{gv} + \xi$, where $\xi$ is some external strain (e.g.

### 2024-09-07 si.tex
fixing ht and fc integrals

@@
 where $N(m) = (m! \ 2^m \pi^{\frac{1}{2}})^{-\frac{1}{2}}$ is the normalization factor and $H_m$ is the m$^{th}$ Hermite Polynomial.
-We begin by generating an expression for $\mel{n}{q^k}{m}$, as this will resolve into Franck-Condon factors for $n = 0$ and Herzberg-Teller integrals for $n=1$.
+We begin by generating an expression for $\mel{\tilde{n}}{q^k}{m}$, as this will resolve into Franck-Condon factors for $n = 0$ and Herzberg-Teller integrals for $n=1$.
+As in the main text, $\{\ket{\tilde{a}}\}$ are vibrational states on the first excited state $|e)$ and $\{\ket{b}\}$ are vibrational states on the ground state $|g)$.
 
-By letting $\ket{m}$ belong to the ground state surface $|g)$ and $\ket{n}$ belong to the first excited surface $|e)$, we write
+By letting $\ket{m}$ belong to the ground state surface $|g)$ and $\ket{\tilde{n}}$ belong to the first excited surface $|e)$, we write
 \begin{equation}
 \begin{split}
-		\mel{n}{q^k}{m} &= \int_{-\infty}^\infty \mathrm{d}q \psi^*_n(q-\Delta) q^k \psi_m(q)\\
+		\mel{\tilde{n}}{q^k}{m} &= \int_{-\infty}^\infty \mathrm{d}q \psi^*_n(q-\Delta) q^k \psi_m(q)\\
 		&= \int_{-\infty}^\infty \mathrm{d}q N(n) N(m) H_n(q-\Delta) \exp(-\frac{(q - \Delta)^2}{2}) q^k H_m(q) \exp(-\frac{q^2}{2})
@@
 \begin{equation}\label{key}
-	\mel{n}{q^k}{m} = \tilde{N} \exp(-\frac{\Delta^2}{2}) \int_{-\infty}^\infty \mathrm{d}q H_n(q+\Delta) q^k H_m(q) \exp(-q^2 + q\Delta)
+	\mel{\tilde{n}}{q^k}{m} = \tilde{N} \exp(-\frac{\Delta^2}{2}) \int_{-\infty}^\infty \mathrm{d}q H_n(q+\Delta) q^k H_m(q) \exp(-q^2 + q\Delta)
 \end{equation}
@@
 	\begin{equation}
-		\lim_{\Delta \rightarrow 0} \langle n | m \rangle = \delta_{n,m}
+		\lim_{\Delta \rightarrow 0} \langle \tilde{n} | m \rangle = \langle n | m \rangle = \delta_{n,m}
 	\end{equation}
@@
 	\begin{equation}
-	\lim_{\Delta \rightarrow 0} \mel{n}{q}{m} = \sqrt{\frac{1}{2}} \left(\sqrt{m}\delta_{n,m-1} + \sqrt{m+1} \delta_{n,m+1}\right)
+	\lim_{\Delta \rightarrow 0} \mel{\tilde{n}}{q}{m} = \mel{{n}}{q}{m} = \sqrt{\frac{1}{2}} \left(\sqrt{m}\delta_{n,m-1} + \sqrt{m+1} \delta_{n,m+1}\right)
 	\end{equation}
@@
 
-We now have the background needed to calculate $\mel{1}{q}{0}$ for an arbitrary offset $\Delta$.
+We now have the background needed to calculate $\mel{\tilde{1}}{q}{0}$ for an arbitrary offset $\Delta$.
 We note that Myers et al.
@@
 \begin{split}
-	\mel{1}{q}{0} = \tilde{N} \exp(-\frac{\Delta^2}{2}) \int_{-\infty}^\infty \mathrm{d}q H_1(q+\Delta) q H_0(q) \exp(-q^2 - q\Delta)
+	\mel{\tilde{1}}{q}{0} = \tilde{N} \exp(-\frac{\Delta^2}{2}) \int_{-\infty}^\infty \mathrm{d}q H_1(q+\Delta) q H_0(q) \exp(-q^2 - q\Delta)
 \end{split}
@@
 	\begin{split}
-		\mel{1}{q}{0} &= \tilde{N} \exp(-\frac{\Delta^2}{2}) \int_{-\infty}^\infty \mathrm{d}q \ 2(q + \Delta) q \exp(-q^2 - q\Delta)\\
+		\mel{\tilde{1}}{q}{0} &= \tilde{N} \exp(-\frac{\Delta^2}{2}) \int_{-\infty}^\infty \mathrm{d}q \ 2(q + \Delta) q \exp(-q^2 - q\Delta)\\
 		&= 2\tilde{N} \exp(-\frac{\Delta^2}{2}) \int_{-\infty}^\infty \mathrm{d}q \ (q^2 + q \Delta) \exp(-q^2 - q\Delta)\\
@@
 \begin{equation}
-	\mel{1}{q}{0} = \sqrt{\frac{1}{2}} (1 - \frac{\Delta^2}{2}) \exp(\frac{-\Delta^2}{4})
+	\mel{\tilde{1}}{q}{0} = \sqrt{\frac{1}{2}} (1 - \frac{\Delta^2}{2}) \exp(\frac{-\Delta^2}{4})
 \end{equation}
-The evaluation of other Herzberg-Teller integrals follows a similar process, or by using symbolic manipulation packages. 
+The evaluation of other Herzberg-Teller integrals follows a similar process. 
 The relevant Franck-Condon factors and Herzberg-Teller integrals, assuming identical curvature and no Duschinsky coupling, are tabulated below.

### 2024-09-07 figures/plotting_fcht.py

@@ -15,7 +15,7 @@ save = False
 fontsize = 18
 
 #define harmonic wells and coordinates
-d = np.linspace(0, 5, 5000)
+d = np.linspace(-5, 5, 5000)
 
 #make figure
 cols = [1, 1] 
@@ -51,7 +51,7 @@ def f12(q): #<1|2>
 
 #define Herzberg Teller overlap integrals following page 165 of Roger Carlson's thesis in terms of q
 def h00(q): #<0|Q|0>
-    return -q/2 * f00(q)
+    return q/2 * f00(q)
 
 def h01(q): #<0|Q|1>
     return 1/np.sqrt(2) * (1 + q**2 /2) * f00(q)
@@ -60,9 +60,12 @@ def h10(q): #<1|Q|0>
     return 1/np.sqrt(2) * (1 - q**2 /2) * f00(q)
 
 def h11(q): #<1|Q|1>
-    return -q/2 * (1 - q**2 / 2) * f00(q)
+    return -q/2 * (-1 + q**2 / 2) * f00(q)
 
 def h12(q): #<1|Q|2>
+    return (1 + q**2/4 - q**4/8) * f00(q)
+
+def h21(q): #<2|Q|1>
     return (1 + q**2/4 - q**4/8) * f00(q)
 
 def h20(q): #<2|Q|0>
@@ -88,15 +91,15 @@ ax0.set_ylabel(r'$\mathsf{Integral \ Value \ (norm.)}$', fontsize = fontsize)
 
 ax1 = plt.subplot(gs[0,1])
 ax1.plot(d, h00(d), linewidth = '2', label = r'$\mathsf{00}$', color = 'black', zorder = 4)
-ax1.plot(d, h01(d), linewidth = '2', label = r'$\mathsf{01}$', color = 'cyan', zorder = 3)
-ax1.plot(d, h10(d), linewidth = '2', label = r'$\mathsf{10}$', color = 'red', zorder = 3)
-ax1.plot(d, h11(d), label = r'$\mathsf{11}$', color = 'orange', zorder = 2)
-ax1.plot(d, h20(d), linewidth = '2', label = r'$\mathsf{20}$', color = 'green', zorder = 1)
-ax1.plot(d, h12(d), linewidth = '2', label = r'$\mathsf{12}$', color = 'pink', zorder = 1)
+ax1.plot(d, h10(d), linewidth = '2', label = r'$\mathsf{10}$', color = 'cyan', zorder = 3)
[…]

### 2024-09-09 paper.tex
fixing SI and trying to understand plot
weird behavior in the plot after changing FC and HT integrals.

@@
 
+Nonlinear spectroscopic probes of electronic-vibrational coupling are not limited to the Raman and hyper-Raman based techniques diagrammed in \autoref{fig:comparisonwmel}.
+Independently developed by the Fleming and Khalil groups, respectively, 2D Electronic-Vibrational (2D-EV) and 2D Vibrational-Electronic spectroscopy are based upon pump-probe and absorption type pathways which also investigate e-v coupling.\cite{Oliver2014, Courtney2015}
+\textbf{add some more words, compare and contrast just a hair}
+
 When the hyper-Raman excitation in HDFG or HSFG is resonant or near-resonant with electronic states, the brightness of the vibrational feature depends on the vibronic structure of the electronic state.
@@
 
-This paper investigates the microscopic parameters that control HDFG output. \cite{Bonn2024, McDonnell2024}
+This paper investigates the microscopic parameters that control HDFG output. \cite{RN352, Bonn2024, McDonnell2024}
+HSFG will not be discussed, but the application of our treatment to HSFG is straightforward and the results are similar.
+We note that HDFG emission can be phase-matched in media with normal dispersion, while HSFG cannot,\cite{RN278} although experimental strategies can be implemented to minimize phase-mismatch in HSFG experiments.
+\cite{Kaufman2024}
 In \autoref{steadystate}, we first identify the vibrational selection rules. 
@@
 In this section, we investigate the properties of HDFG and make the connections between HDFG and hyper-Raman scattering explicit.
-HSFG will not be discussed, but the application of our treatment to HSFG is straightforward and the selection rules are similar.
-We note that HDFG emission can be phase-matched in media with normal dispersion, while HSFG cannot,\cite{RN278} although experimental strategies can be implemented to minimize phase-mismatch in HSFG experiments.
-\cite{Kaufman2024}
-
-Coherent spectroscopies are often described using the density-matrix formalism, where a density matrix $\rho$ is propagated using the Liouville-von Neumann equation $via$
-\begin{equation}
+Coherent spectroscopies are often described using the density matrix formalism, where a density matrix $\rho$ is propagated using the Liouville-von Neumann equation $via$
+\begin{equation}\label{LVNE}
 	\dot{\rho} = \frac{1}{i \hbar} [H + V(t), \rho] + \dot{\rho}_R,
@@
 In the limit where input field pulsewidths are much longer than electronic dephasing times and the individual molecule limit is approached, it becomes acceptable to write $\dot{\rho}_R = \Gamma \rho$, i.e.
-exponential relaxation (Markovian dynamics), where $\Gamma$ is the system's pure dephasing rate.
+exponential relaxation, where $\Gamma$ is the system's pure dephasing rate.
 \cite{RN455, RN307, Sung2001}
@@
 \begin{equation}\label{eq:nfgamma}
-	\chi^{(3)}_{IJKL} = NF \langle \gamma_{ijkl} \rangle.
+	\chi^{(3)}_{IJKL} = NF \langle \gamma_{ijkl} \rangle_{IJKL}.
 \end{equation}
@@
 
-By propagating density matrix elements in the steady state limit, the HDFG hyperpolarizability is \cite{RN133}
+By propagating \autoref{LVNE} in the steady state limit ($\dot{\rho} = 0$), the HDFG hyperpolarizability is \cite{RN442, RN133}
 \begin{equation}\label{sivegamma}
@@
 While the Placzek treatment provides the general source of HDFG output, it does not predict the behavior of $\beta_{ijk}$ as $\omega_2 + \omega_3$ is changed.
-We now explicitly consider electronic resonances through the $A,B,C$ decomposition of $\beta$ introduced by Chung and Ziegler, analogous to those found in Albrecht's treatment of Raman spectroscopy.\cite{Albrecht1961, Ziegler1988}
+We now explicitly consider electronic resonances through the $A,B,C$ decomposition of $\beta$ introduced by Chung and Ziegler, analogous to those found in Albrecht's treatment of Raman spectroscopy (i.e., sum-over-states formalism).\cite{Albrecht1961, Ziegler1988}
 To employ this formalism, we write the states in a Born-Oppenheimer basis $\ket{a,b}$, where $\ket{a,b} = |a(Q)) \otimes \ket{b}$ for electronic states $\{|a(\textbf{Q}))\}$ and vibrational states $\{\ket{b}\}$ (i.e., adiabatic approximation), where \textbf{Q}, the system normal modes, is the adiabatic parameter.
@@
 \cite{Ziegler1988, Neddersen1989, Bonang1992}
-Note that some reports obtain $A, B$ coefficients through a Herzberg-Teller expansion of the electronic states to expose vibronic couplings via $\partial H / \partial Q$, where $H$ is the electronic Hamiltonian.\cite{HerzbergTeller1933, Petrov1985, Neddersen1989, Baranov1990}
-This approach is not used here as the expansion of $\vec{M}^{ij}$ in normal mode coordinates provides sufficient physical insight into hyper-Raman selection rules.
+Note that some reports obtain $A, B$ coefficients through a Herzberg-Teller expansion of the electronic states to expose vibronic couplings via $\partial H / \partial Q$.\cite{HerzbergTeller1933, Petrov1985, Neddersen1989, Baranov1990}
+This approach is not used here as the expansion of $\vec{M}^{ij}$ in normal mode coordinates provides sufficient physical insight into HDFG selection rules.
 
@@
 		Note that (b) plots magnitudes of the labeled quantities.
-		The vibrational states on the $|g)$ and $|e)$ manifolds are spaced 2200 cm$^{-1}$ apart, with the vibronic states $\ket{e,\tilde{v}'}$ given linewidths of 700 cm$^{-1}$ and $\hbar \omega_{eg}$ = 30000 cm$^{-1}$.
+		The vibrational states on the $|g)$ and $|e)$ manifolds are spaced 1600 cm$^{-1}$ apart, with the vibronic states $\ket{e,\tilde{v}'}$ given linewidths of 800 cm$^{-1}$ and $\hbar \omega_{eg}$ = 30000 cm$^{-1}$.
 		Dotted lines in (b) denote the $\tilde{v}'$ = 0, 1, 2 vibronic resonances. 
@@
 We point this out because a persistent belief in Raman analysis is that $A$ terms disappear and $B$ terms dominate when significantly detuned from electronic resonance.
-The belief arises from the approximation $\abs{\omega_{e\tilde{v}',gv} - 2\omega_2} \gg 2\Gamma_{e\tilde{v}',gv}$, which then removes $A$ through a closure relationship.\cite{Neddersen1989}
+The belief arises from the approximation that when $\abs{\omega_{e\tilde{v}',gv} - 2\omega_2} \gg 2\Gamma_{e\tilde{v}',gv}$, $A$ vanishes through a closure relationship.\cite{Neddersen1989}
 As has been discussed elsewhere, however, this approximation is in many cases invalid, especially when vibrational energies are large, like those explored here.\cite{Warshel1977, Myers1982, Li1990, Gong2015}
@@
 			$A$ 
-			& $\langle 1 | \tilde{0} \rangle \langle \tilde{0} | 0 \rangle = 0.31 $  
+			& $\langle 1 | \tilde{0} \rangle \langle \tilde{0} | 0 \rangle = -0.31 $  
 			& $\langle 1 | \tilde{1} \rangle \langle \tilde{1} | 0 \rangle = 0.27 $ 
-			& $\langle 1 | \tilde{2} \rangle \langle \tilde{2} | 0 \rangle = -0.04$\\
+			& $\langle 1 | \tilde{2} \rangle \langle \tilde{2} | 0 \rangle = 0.04$\\
 
@@
 			& $\langle 1 | \tilde{1} \rangle \mel{\tilde{1}}{Q}{0} = 0.48$ 
-			&$\langle 1 | \tilde{2} \rangle \mel{\tilde{2}}{Q}{0} = 0.14$\\
+			&$\langle 1 | \tilde{2} \rangle \mel{\tilde{2}}{Q}{0} = -0.14$\\
 
 			$B_2$ 
-			& $\mel{1}{Q}{\tilde{0}} \langle \tilde{0} | 0 \rangle = 0.55$  
-			& $\mel{1}{Q}{\tilde{1}} \langle \tilde{1} | 0 \rangle = -0.07$ 
+			& $\mel{1}{Q}{\tilde{0}} \langle \tilde{0} | 0 \rangle = 0.70$  
+			& $\mel{1}{Q}{\tilde{1}} \langle \tilde{1} | 0 \rangle = 0.07$ 
 			& $\mel{1}{Q}{\tilde{2}} \langle \tilde{2} | 0 \rangle = 0.08$\\

### 2024-09-09 si.tex
fixing SI and trying to understand plot
weird behavior in the plot after changing FC and HT integrals.

@@
 \section{Evaluating Herzberg-Teller Integrals for Harmonic Wells of Identical Curvature}
-In this section, we discuss the evaluation of Herzberg-Teller integrals, in the limit of no Duschinsky coupling, when the ground and first excited state are harmonic wells.
+In this section, we discuss the evaluation of Herzberg-Teller integrals,\cite{HerzbergTeller1933} in the limit of no Duschinsky coupling,\cite{Duschinsky1937} when the ground and first excited state are harmonic wells of identical curvature.
 We use the Hamiltonian described in the main text, $H = H_g |g) \left(g| + H_e |e\right) (e|$, where
@@
 This is the key result.
+While integrals of form \autoref{key} can be computed straightforwardly using mathematical packages such as \texttt{Mathematica} or \texttt{sympy}, it is a useful exercise in Gaussian integral manipulation to evaluate Herzberg-Teller or Franck-Condon integrals.
 As a side note, \autoref{key} explicitly shows
@@
 \end{equation}
-When $w=0$, the result is trivial:\footnote{$\int_{-\infty}^{\infty} \mathrm{d}x \exp(-(x-a)^2) = \sqrt{\pi}$}
+When $w=0$, the result follows by completing the square:\footnote{$\int_{-\infty}^{\infty} \mathrm{d}x \exp(-(x-a)^2) = \sqrt{\pi}$}
 \begin{equation}
@@
 The evaluation of other Herzberg-Teller integrals follows a similar process.
-The relevant Franck-Condon factors and Herzberg-Teller integrals, assuming identical curvature and no Duschinsky coupling, are tabulated below.
-
-\begin{table}[!htbp]
-	\caption{\label{T:FC Integral} Franck-Condon Factors.}
-	\begin{ruledtabular}
-		\begin{tabular}{cc}
-			$\mel{n}{0}{m}$ & Expression\\
-			\hline  
-			$A$ & $\langle 1 | 0 \rangle \langle 0 | 0 \rangle = 0.31 $  \\
-
-			$B_1$ & $\langle 1 | 0 \rangle \mel{0}{Q}{0} = -0.08$ \\
-
-			$B_2$ & $\mel{1}{Q}{0} \langle 0 | 0 \rangle = 0.55$\\
-		\end{tabular}
-	\end{ruledtabular}
-\end{table}
-
-\begin{table}[!htbp]
-	\caption{\label{T:HT Integral} Franck-Condon Factors.}
-	\begin{ruledtabular}
-		\begin{tabular}{cc}
-			$\mel{n}{q}{m}$& Expression\\
-			\hline  
-			$\mel{0}{q}{0}$ & $\frac{\Delta}{2} \exp(-\Delta^2/4)$  \\ 
-			$\mel{1}{q}{0}$ & $\frac{1}{\sqrt{2}} \exp(-\Delta^2/4)(1 - \Delta^2/2) $ \\
-			$\mel{2}{q}{0}$ & $\frac{1}{\sqrt{2}} \exp(-\Delta^2/4)(1 - \Delta^2/2) $ \\
-			$\mel{0}{q}{1}$ & $\frac{1}{\sqrt{2}} \exp(-\Delta^2/4)(1 + \Delta^2/2) $ \\
-			$\mel{1}{q}{1}$ & $\frac{\Delta}{{2}} \exp(-\Delta^2/4)(1 - \Delta^2/2) $ \\
-			$\mel{2}{q}{1}$ & $\frac{\Delta}{{2}} \exp(-\Delta^2/4)(1 - \Delta^2/2) $ \\
-			$\mel{1}{q}{1}$ & $\frac{\Delta}{{2}} \exp(-\Delta^2/4)(1 - \Delta^2/2) $ \\
-
-		\end{tabular}
-	\end{ruledtabular}
-\end{table}
 
@@
 Here, we vary $\Delta$ to investigate its impact on the structure of the $\abs{A+B}$ spectrum.
-First, we investigate how the Franck-Condon factors and Herzberg-Teller integrals are manipulated as a function of $\Delta$.
-%TODO - plot
+The relevant Franck-Condon factors and Herzberg-Teller integrals, assuming identical curvature and no Duschinsky coupling, are plotted in \autoref{fig:fcht} as a function of offset, $\Delta$.
+These functions were generated by evaluating \autoref{key} for $k=0, 1$ using \texttt{sympy}.%todo:citesympy
+
+\begin{figure}[!htbp]
+	\centering
+	\includegraphics[width=6.675in]{figures/fcht.png}
+	\caption{Poles (black dots) and contour (blue line) used to evaluate \autoref{integraly} for (a) anti-correlated and (b) correlated modes.} 
+	\label{fig:fcht}
+\end{figure}
 

### 2024-09-09 figures/2D_spec_nonorm.py

@@ -169,17 +169,17 @@ B2 = B20 + B21 + B22
 
 #Real parts
 totRe = A.real + B1.real + B2.real
-ARe = A.real / totRe.max()
-BRe = (B1+B2).real / totRe.max()
-B1Re = B1.real / totRe.max()
-B2Re = B2.real / totRe.max()
+ARe = A.real
+BRe = (B1+B2).real 
+B1Re = B1.real 
+B2Re = B2.real 
 
 #Im parts
 totIm = A.imag + B1.imag + B2.imag
-AIm = A.imag / totIm.max()
-BIm = (B1+B2).imag / totIm.max()
-B1Im = B1.imag / totIm.max()
-B2Im = B2.imag / totIm.max()
+AIm = A.imag 
+BIm = (B1+B2).imag 
+B1Im = B1.imag
+B2Im = B2.imag 
 
 
 # absolute value
@@ -188,32 +188,33 @@ abs_max = tot.max()
 
 #plot the A and B
 ax1 = plt.subplot(gs[0,1])
-ax1.plot(y, tot / tot.max(), linewidth = '2', label = r'$\mathsf{|A + B|}$', color = 'black', zorder = 4)
-ax1.plot(y, np.abs(A) / abs_max, linewidth = '2', label = r'$\mathsf{|A|}$', color = 'cyan', zorder = 3)
-ax1.plot(y, np.abs(B1+B2) / abs_max, linewidth = '2', label = r'$\mathsf{|B|}$', color = 'red', zorder = 3)
-ax1.plot(y, np.abs(B1) / abs_max, linewidth = '2', label = r'$\mathsf{|B_1|}$', color = 'orange', zorder = 2)
-ax1.plot(y, np.abs(B2) / abs_max, linewidth = '2', label = r'$\mathsf{|B_2|}$', color = 'green', zorder = 1)
+ax1.plot(y, tot, linewidth = '2', label = r'$\mathsf{|A + B|}$', color = 'black', zorder = 4)
+ax1.plot(y, np.abs(A), linewidth = '2', label = r'$\mathsf{|A|}$', color = 'cyan', zorder = 3)
+ax1.plot(y, np.abs(B1+B2), linewidth = '2', label = r'$\mathsf{|B|}$', color = 'red', zorder = 3)
+ax1.plot(y, np.abs(B1), linewidth = '2', label = r'$\mathsf{|B_1|}$', color = 'orange', zorder = 2)
[…]

### 2024-09-09 figures/plotting_fcht.py

@@ -12,10 +12,10 @@ from matplotlib.patches import FancyArrowPatch
 wt.artists.apply_rcparams(kind="publication")
 
 save = False
-fontsize = 18
+fontsize =18
 
 #define harmonic wells and coordinates
-d = np.linspace(-5, 5, 5000)
+d = np.linspace(-1, 5, 5000)
 
 #make figure
 cols = [1, 1] 
@@ -44,10 +44,9 @@ def f02(q): #<0|2>
 
 def f20(q): #<2|0>
     return f02(q)
-
-def f12(q): #<1|2>
-    return -q * (1 - q**2/4) *f00(q)
-    
+   
+def f21(q): #<2|1>
+    return q * (1 - q**2/4) *f00(q)
 
 #define Herzberg Teller overlap integrals following page 165 of Roger Carlson's thesis in terms of q
 def h00(q): #<0|Q|0>
@@ -75,14 +74,14 @@ def h20(q): #<2|Q|0>
 #plot
 fig, gs = wt.artists.create_figure(width="dissertation", nrows=2, cols=cols, aspects=aspects, wspace=1) 
 ax0 = plt.subplot(gs[0,0])
-ax0.plot(d, f00(d), linewidth = '2', label = r'$\mathsf{00}$', color = 'black', zorder = 4)
-ax0.plot(d, f01(d), linewidth = '2', label = r'$\mathsf{01}$', color = 'cyan', zorder = 3)
-ax0.plot(d, f10(d), linewidth = '2', label = r'$\mathsf{10}$', color = 'red', zorder = 3)
-ax0.plot(d, f11(d), label = r'$\mathsf{11}$', color = 'orange', zorder = 2)
-ax0.plot(d, f02(d), linewidth = '2', label = r'$\mathsf{02}$', color = 'green', zorder = 1)
-ax0.plot(d, f20(d), linewidth = '2', label = r'$\mathsf{20}$', color = 'pink', zorder = 1)
-ax0.plot(d, f12(d), linewidth = '2', label = r'$\mathsf{12}$', color = 'yellow', zorder = 1)
-ax0.set_ylabel(r'$\mathsf{Integral \ Value \ (norm.)}$', fontsize = fontsize)
+ax0.plot(d, f00(d), linewidth = '2', label = r'$\mathsf{\langle\tilde{0}|0\rangle}$', color = 'black', zorder = 4)
[…]

### 2024-09-09 paper.tex
more edits

@@
 To target vibrational and electronic coupling, methods commonly make use of Raman transitions, e.g., doubly vibrationally enhanced spectroscopy (DOVE), triple sum frequency (TSF), coherent anti-Stokes Raman spectroscopy (CARS), resonant impulse stimulated Raman spectroscopy (RISRS).\cite{RN103, Dhar1994, RN345, Cho2000, RN491}
-Here we explore the less-utilized hyper-Raman transitions in four wave mixing CMDS.
+Here we explore the less-utilized hyper-Raman transition in four wave mixing CMDS.
 
@@
 \autoref{fig:comparisonwmel} shows both HDFG and HSFG processes and compares them with related spectroscopies that investigate vibrational-electronic coupling.
-The three-wave mixing ($\chi^{(2)}$) techniques are often less applicable as they require macroscopic non-centrosymmetry under the electric dipole approximation.\cite{Shen94}
+The three-wave mixing ($\chi^{(2)}$) techniques are often less applicable as they require macroscopic non-centrosymmetry under the electric dipole approximation.\cite{RN480}
 Hyper-Raman scattering itself is a six-wave mixing ($\chi^{(5)}$) technique; stimulated hyper-Raman will be weak and susceptible to four-wave mixing (FWM) cascades.\cite{RN515, RN243, Cho2000_Cascade}
@@
 Nonlinear spectroscopic probes of electronic-vibrational coupling are not limited to the Raman and hyper-Raman based techniques diagrammed in \autoref{fig:comparisonwmel}.
-Independently developed by the Fleming and Khalil groups, respectively, 2D Electronic-Vibrational (2D-EV) and 2D Vibrational-Electronic spectroscopy are based upon pump-probe and absorption type pathways which also investigate e-v coupling.\cite{Oliver2014, Courtney2015}
+Independently developed by the Fleming and Khalil groups, respectively, 2D Electronic-Vibrational (2D-EV) and 2D Vibrational-Electronic (2D-VE) spectroscopy are based upon pump-probe and absorption type pathways which also investigate e-v coupling.\cite{Oliver2014, Courtney2015}
 \textbf{add some more words, compare and contrast just a hair}
@@
 In this section, we investigate the properties of HDFG and make the connections between HDFG and hyper-Raman scattering explicit.
-Coherent spectroscopies are often described using the density matrix formalism, where a density matrix $\rho$ is propagated using the Liouville-von Neumann equation $via$
+Coherent spectroscopies are often described in the perturbative limit using the density matrix formalism, where a density matrix $\rho$ is propagated using the Liouville-von Neumann equation $via$
 \begin{equation}\label{LVNE}
@@
 \end{equation}
-where $H$ is the (static) system Hamiltonian, $V(t)$ is the field-matter interaction and $\rho_R$ is the relaxation density matrix. 
-Under the electric dipole approximation, $V(t) = -\vec{\mu} \cdot \sum_{j} E_j(t)$, where $j$ indexes the input electric fields.
+where $H$ is the (static) system Hamiltonian, $V(t)$ is the field-matter interaction and $\rho_R$ is the relaxation density matrix. \cite{RN455}
+We describe the input electric fields as $\vec{E}(\vec{x},t) = \frac{1}{2} \vec{E}_j\exp(-i(\omega_j t - \vec{k}_j \cdot \vec{x})) + \mathrm{c.c.}$.
 In systems where interactions with surroundings are relevant, $\dot{\rho}_R$ is a complex function which can be modified to include system-bath interactions, solvent-solute coupling, etc.
@@
 In the limit where input field pulsewidths are much longer than electronic dephasing times and the individual molecule limit is approached, it becomes acceptable to write $\dot{\rho}_R = \Gamma \rho$, i.e.
-exponential relaxation, where $\Gamma$ is the system's pure dephasing rate.
+exponential relaxation, where $\Gamma$ is the system's dephasing rate.
 \cite{RN455, RN307, Sung2001}
-While exponential relaxation is usually an inappropriate description of most physical systems involving solvent-solute interactions,\cite{Sue1986, Yan1988, Li1994, Myers1997} our goal is to introduce simple, quantitative models to understand HDFG response.
+While exponential relaxation is usually an inappropriate description of most physical systems involving solvent-solute interactions,\cite{Yan1988, Li1994, Myers1997} our goal is to introduce simple, quantitative models to understand HDFG response.
 Thus, we write $\dot{\rho}_R = \Gamma \rho$.
-This limit which has proven useful in investigating the properties of 2D-EV and 2D-VE spectroscopy. \cite{Gaynor2017} 
-Experimentally, it has been shown to be valid when investigating doubly resonant SFG response using pulses much longer than electronic dephasing times. \cite{Raschke2002}
-This limit is taken to emphasize the quantum mechanical selection rules of the HDFG technique.
+The exponential relaxation limit has proven useful in investigating the properties of 2D-EV and 2D-VE spectroscopy and doubly resonant SFG response using pulses much longer than electronic dephasing times.
+\cite{Raschke2002, Gaynor2017}
 
@@
 It is useful to expose relationships between nonlinear output, transition dipoles and hyper-Raman hyperpolarizabilities in the driven limit ($\dot{\rho} = 0$). \cite{Simpson2004, Moad2005}
-Under the electric dipole approximation, the $I^\text{th}$ cartesian component of the third order nonlinear output polarization, ${P}^{(3)}_I$, of a four wave mixing process, induced by electric fields $E_J$, $E_K$, and $E_L$ at output frequency $\omega_4=-\omega_1 + \omega_2 + \omega_3$ is written as (using Einstein summation) \cite{RN307}
+Under the electric dipole approximation, the $I^\text{th}$ Cartesian component of the third order nonlinear output polarization, ${P}^{(3)}_I$, of a four wave mixing process, induced by electric fields $E_J$, $E_K$, and $E_L$ at output frequency $\omega_4=-\omega_1 + \omega_2 + \omega_3$ is written as (using Einstein summation) \cite{RN307}
 \begin{equation} \label{polarization}
@@
 
-By propagating \autoref{LVNE} in the steady state limit ($\dot{\rho} = 0$), the HDFG hyperpolarizability is \cite{RN442, RN133}
+By propagating \autoref{LVNE} in the steady state limit ($\dot{\rho} = 0$), the HDFG hyperpolarizability is \cite{Prior1984, McDonnell2024}
 \begin{equation}\label{sivegamma}
@@
 When $\omega_2+\omega_3$ is significantly detuned from resonance and the vibronic nature of the virtual states is ignored, the Placzek approximation can be used to study selection rules in terms of the hyper-Raman hyperpolarizability, $\beta$.
-\cite{Placzek1934, Long1970, Altmann1982}
+\cite{Placzek1934, Long1970}
 Summing over the virtual states $\ket{e}$ and $\ket{m}$ forms the hyper-Raman hyperpolarizability so that\cite{Long1970} 
@@
 \end{subequations}
-Substituting into \autoref{sivebeta} gives the HDFG hyperpolarizability to $\order{Q_n}$ as \begin{equation}\label{SIVEselection}
+Taking $\ket{g} = \ket{0}, \ket{v} = \ket{1}$, substituting into \autoref{sivebeta} and using typical Harmonic Oscillator selection rules, gives the HDFG hyperpolarizability to $\order{Q_n}$ as \begin{equation}\label{SIVEselection}
 	\gamma_{ijkl} =	-\frac{1}{\varepsilon_0} \frac{1}{8D \omega_{vg}}  \frac{1}{{\Delta_{gv}}} \ \left(\frac{\partial \beta^{vg}_{ijk}}{\partial Q_v}\right)_0 \left({\frac{\partial \mu^{gv}_{l}}{\partial Q_v}}\right)_0  \rho_{gg}
 \end{equation}
-where we have used $\mel{1}{\mu_{l,0}}{0} = 0 = \mel{1}{\beta_{ijk,0}}{0}$, and $\mel{v}{Q_v}{g} \equiv \mel{1}{Q_v}{0} = \sqrt{\frac{\hbar}{2\omega_{vg}}}$.
+where we have used $\mel{v}{\mu_{l,0}}{g} = 0 = \mel{1}{\beta_{ijk,0}}{0}$, and $\mel{1}{Q_v}{0} = \sqrt{\frac{\hbar}{2\omega_{vg}}}$.
 Here, $\omega_{vg}$ is the characteristic $\ket{0} \rightarrow \ket{1}$ frequency.\cite{RN459}
@@
 
-We investigate the impact of inhomogeneity on spectral output by convolving the HDFG output hyperpolarizability $\gamma_{ijkl}(\xi)$ with a normalized Lorentzian distribution $P(\xi)$ of half width $\sigma$ as \cite{Penner1976, Desiderio1979, Dick83_1, Carlson1990line}
+We investigate the impact of inhomogeneity on spectral output by convolving the HDFG output hyperpolarizability $\gamma_{ijkl}(\xi)$ with a normalized Lorentzian distribution $P(\xi)$ of half width $\sigma$ as \cite{Desiderio1979, Dick83_1, Carlson1990line}
 \begin{equation}\label{contour}
@@
 Excited state population effects are particularly important for understanding the spectroscopy of electronic states using input pulses with pulsewidths significantly longer than dephasing times.
-\cite{RN319, Yurs2012}
-Excited state populations can feed other modes, including the ground state and other vibrational/vibronic modes, inducing higher order processes.\cite{Carlson87, RN471}
-These feeding mechanisms can induce line-narrowing properties in spectroscopies that cannot line-narrow in third order perturbation theory.\cite{RN319, Carlson87, RN471}
+\cite{RN471, Yurs2012}
+Excited state populations can feed other modes, including the ground state and other vibrational/vibronic modes, inducing higher order processes.\cite{RN471}
+These feeding mechanisms can induce line-narrowing properties in spectroscopies that cannot line-narrow in third order perturbation theory.\cite{RN471, RN410}
 
 \section{Quantitative Aspects of HDFG}\label{quant}
-% Despite their increasing use for dissecting intra and intermolecular interactions, CMDS techniques are usually not feasible for most laboratories, as they usually demand the use of multiple optical parametric amplifiers and/or complex acousto-optic modulators.
-\cite{Chen2016}
-% Unlike most four wave mixing techniques, HDFG can be performed using only two input beams (i.e., two color HDFG).
-%
 
 \subsection{vSFG detection levels are adequate for HDFG}
-
 Can vSFG experimental setups detect HDFG signals?
@@
 \section{Conclusions}\label{conclusion}
+\textbf{NEED TO READ THIS SECTION!}
+
 Coherent vibrational, hyper-Raman coherent four wave mixing spectroscopies are identified and discussed.
@@
 \section{Appendix: Comparison of vSFG and two-beam HDFG output}\label{appendixA}
-To motivate the application of HDFG spectroscopy, we perform a calculation to compare two-color HDFG and vSFG output, where absorption effects are neglected for simplicity. \cite{Carlson1989}
+To motivate the application of HDFG spectroscopy, we perform a calculation to compare two-color HDFG and vSFG output, where absorption effects are neglected for simplicity.
 vSFG is a $\chi^{(2)}$ technique, when only vibrationally resonant, whose output scales as $\chi^{(2)}_{IJK} \sim \langle \alpha_{ij} \mu_k \rangle$, where $\alpha_{ij}$ is the Raman polarizability tensor.

### 2024-09-16 paper.tex
si exists
almost there

@@
 Most of these methods rely on infrared and/or Raman transitions, but methods involving hyper-Raman transitions are also possible. 
-Hyper Difference Frequency Generation (HDFG) spectroscopy is an underdeveloped four wave mixing vibrational spectroscopy based on the hyper-Raman transition and IR absorption. 
-HDFG is experimentally similar to vibrational sum frequency generation (vSFG) spectroscopy share similar output, making HDFG feasible for vSFG practitioners. 
+Hyper Difference Frequency Generation (HDFG) spectroscopy is an underdeveloped four wave mixing vibrational spectroscopy based both infrared absorption and hyper-Raman scattering transitions. 
 Despite several experimental reports on HDFG, its spectroscopic properties have not been fully explored. 
 To this end, we investigate the selection rules and behavior of HDFG spectroscopy as an upconverted infrared spectroscopy and as a probe of vibronic coupling in molecular systems.
-HDFG is shown to a sensitive probe of vibronic coupling in bulk systems.
+We discuss the similarities between HDFG, a four wave mixing technique, and vibrational sum frequency generation (vSFG) spectroscopy, a three wave mixing technique. 
+vSFG and HDFG appear to provide similar output intensities, making HDFG feasible for vSFG practitioners.
+HDFG is shown to a sensitive probe of vibronic coupling in bulk systems and provides an alternative method to investigate electronic-nuclear coordinate correlations.
 \end{abstract}
@@
 Independently developed by the Fleming and Khalil groups, respectively, 2D Electronic-Vibrational (2D-EV) and 2D Vibrational-Electronic (2D-VE) spectroscopy are based upon pump-probe and absorption type pathways which also investigate e-v coupling.\cite{Oliver2014, Courtney2015}
-\textbf{add some more words, compare and contrast just a hair}
+They have been used to investigate vibronic coupling in a variety of complex molecular systems, and serve as 2D pump-probe type analogues to the hyper-Raman-based spectroscopies discussed here.
 
 When the hyper-Raman excitation in HDFG or HSFG is resonant or near-resonant with electronic states, the brightness of the vibrational feature depends on the vibronic structure of the electronic state.
-The electronic spectrum probed in HDFG or HSFG can inform on processes that control ultrafast electronic relaxation in molecular and biological systems in similar ways to resonance Raman.\cite{Cho2001, Bredenbeck2015, Arsenault2021}
+The electronic spectrum probed in HDFG or HSFG can inform on processes that control ultrafast electronic relaxation in molecular and biological systems in ways similar to resonance Raman.\cite{Cho2001, Bredenbeck2015, Arsenault2021}
 Since the selection rules of hyper-Raman scattering differ from Raman scattering, the hyper-Raman excitation spectra give a unique alternative to Raman scattering to understand vibrational spectra, electronic structure and vibronic coupling in molecular systems.
@@
 HSFG will not be discussed, but the application of our treatment to HSFG is straightforward and the results are similar.
-We note that HDFG emission can be phase-matched in media with normal dispersion, while HSFG cannot,\cite{RN278} although experimental strategies can be implemented to minimize phase-mismatch in HSFG experiments.
+We note that HDFG emission can be phase-matched in media with normal dispersion while HSFG cannot,\cite{RN279, RN278} although experimental strategies can be implemented to minimize phase-mismatch in HSFG experiments.
 \cite{Kaufman2024}
 In \autoref{steadystate}, we first identify the vibrational selection rules. 
-The selection rules of electronically-resonant HDFG are then identified through a Herzberg-Teller dipole expansion.
+The selection rules of electronically-resonant HDFG are then identified through an expansion of electronic dipole moments following Chung and Ziegler.\cite{Ziegler1988}
 HDFG is found to be allowed in any harmonic system that has infrared active vibrations.
@@
 In this section, we investigate the properties of HDFG and make the connections between HDFG and hyper-Raman scattering explicit.
-Coherent spectroscopies are often described in the perturbative limit using the density matrix formalism, where a density matrix $\rho$ is propagated using the Liouville-von Neumann equation $via$
+Coherent spectroscopies are often described using the density matrix formalism, where a density matrix $\rho$ is propagated using the Liouville-von Neumann equation $via$
 \begin{equation}\label{LVNE}
@@
 where $H$ is the (static) system Hamiltonian, $V(t)$ is the field-matter interaction and $\rho_R$ is the relaxation density matrix. \cite{RN455}
-We describe the input electric fields as $\vec{E}(\vec{x},t) = \frac{1}{2} \vec{E}_j\exp(-i(\omega_j t - \vec{k}_j \cdot \vec{x})) + \mathrm{c.c.}$.
-In systems where interactions with surroundings are relevant, $\dot{\rho}_R$ is a complex function which can be modified to include system-bath interactions, solvent-solute coupling, etc.
+For simplicity, as dynamics is not a major focus of this article, we write electric fields as plane waves, such that $\vec{E}(\vec{x},t) = \frac{1}{2} \vec{E}_0\exp(-i(\vec{k} \cdot \vec{x} - \omega t)) + \mathrm{c.c.}$.
+In systems where interactions with surroundings are relevant, $\dot{\rho}_R$ becomes a complex function that can be modified to include phenomena such as system-bath interactions, solvent-solute coupling, among others.
 \cite{Sung2001}
-In the limit where input field pulsewidths are much longer than electronic dephasing times and the individual molecule limit is approached, it becomes acceptable to write $\dot{\rho}_R = \Gamma \rho$, i.e.
+In the limit where input field pulsewidths are much longer than electronic dephasing times and the individual molecule limit is approached, it becomes acceptable to write $\dot{\rho}_R \approx \Gamma \rho$, i.e.
 exponential relaxation, where $\Gamma$ is the system's dephasing rate.
-\cite{RN455, RN307, Sung2001}
+\cite{RN455, Sung2001}
 While exponential relaxation is usually an inappropriate description of most physical systems involving solvent-solute interactions,\cite{Yan1988, Li1994, Myers1997} our goal is to introduce simple, quantitative models to understand HDFG response.
 Thus, we write $\dot{\rho}_R = \Gamma \rho$.
-The exponential relaxation limit has proven useful in investigating the properties of 2D-EV and 2D-VE spectroscopy and doubly resonant SFG response using pulses much longer than electronic dephasing times.
+The exponential relaxation limit has proven useful in investigating the properties of 2D-EV, 2D-VE, and doubly resonant SFG using pulses much longer than electronic dephasing times.
 \cite{Raschke2002, Gaynor2017}
@@
 		In all cases, $\omega_2 > \omega_1$.
+		The virtual states are arbitrarily placed and fluctuate in energy dependent upon the energy of the input fields.
 	}
@@
 \end{equation}
-Here $N$ is a number density and $\gamma_{ijkl}$ is the third-order polarizability (i.e., second hyperpolarizability).
+Here $N$ is a number density, $F=\prod_j  \frac{1}{3} \left({\left(n(\omega_j)\right)^2 + 1} \right)$ is the Lorentz local field factor, where $n$ is the (frequency dependent) refractive index and $\gamma_{ijkl}$ is the third-order polarizability (i.e., second hyperpolarizability).
+\cite{Bedeaux1973}
 The brackets indicate an orientational average.\cite{Andrews1977}
 Uppercase letters refer to laboratory frame coordinates and lower case letters refer to corresponding molecular frame coordinates.
-$F=\prod_j  \frac{1}{3} \left({\left(n(\omega_j)\right)^2 + 1} \right)$ is the Lorentz local field factor, where $n$ is the (frequency dependent) refractive index. \cite{Bedeaux1973}
+The steps behind orientational averaging of $\gamma_{ijkl}$, a rank four tensor in the molecular frame, are detailed elsewhere.\cite{Andrews1977, McDonnell2024}
+Briefly, a tensor in the molecular frame, $A_{ijkl}$, is transformed into an element of the same tensor in the laboratory frame, $\langle A_{ijkl} \rangle_{IJKL}$, through $\langle A_{ijkl} \rangle_{IJKL}$ = $\theta^{ijkl}_{IJKL} A_{ijkl}$, where summation over repeated indices is implied and $\theta$ is the transformation operator.
+\cite{McDonnell2024, Andrews1977}
 
-By propagating \autoref{LVNE} in the steady state limit ($\dot{\rho} = 0$), the HDFG hyperpolarizability is \cite{Prior1984, McDonnell2024}
+By propagating \autoref{LVNE} in the steady state limit ($\dot{\rho} = 0$), the HDFG hyperpolarizability is \cite{Prior1984}
 \begin{equation}\label{sivegamma}
@@
 Here, $\ket{e}$ and $\ket{m}$ are virtual states, and thus necessarily summed over in \autoref{sivegamma}.
-The pulse identifiers on the $\Delta_{kl}$ terms will be suppressed henceforth for simplicity.
+The pulse identifiers on the $\Delta_{kl}$ terms will be suppressed henceforth for legibility.
 $D$, the Maker-Terhune degeneracy factor, accounts for permutation symmetry of the excitation fields.\cite{RN134} 
@@
 \end{subequations}
-Taking $\ket{g} = \ket{0}, \ket{v} = \ket{1}$, substituting into \autoref{sivebeta} and using typical Harmonic Oscillator selection rules, gives the HDFG hyperpolarizability to $\order{Q_n}$ as \begin{equation}\label{SIVEselection}
+Taking $\ket{g} = \ket{0}, \ket{v} = \ket{1}$, substituting into \autoref{sivebeta} and using typical Harmonic Oscillator selection rules, gives the HDFG hyperpolarizability to $\order{Q_v}$ as \begin{equation}\label{SIVEselection}
 	\gamma_{ijkl} =	-\frac{1}{\varepsilon_0} \frac{1}{8D \omega_{vg}}  \frac{1}{{\Delta_{gv}}} \ \left(\frac{\partial \beta^{vg}_{ijk}}{\partial Q_v}\right)_0 \left({\frac{\partial \mu^{gv}_{l}}{\partial Q_v}}\right)_0  \rho_{gg}
@@
 We now explicitly consider electronic resonances through the $A,B,C$ decomposition of $\beta$ introduced by Chung and Ziegler, analogous to those found in Albrecht's treatment of Raman spectroscopy (i.e., sum-over-states formalism).\cite{Albrecht1961, Ziegler1988}
-To employ this formalism, we write the states in a Born-Oppenheimer basis $\ket{a,b}$, where $\ket{a,b} = |a(Q)) \otimes \ket{b}$ for electronic states $\{|a(\textbf{Q}))\}$ and vibrational states $\{\ket{b}\}$ (i.e., adiabatic approximation), where \textbf{Q}, the system normal modes, is the adiabatic parameter.
+To employ this formalism, we write the states in a Born-Oppenheimer basis $\ket{a,b}$, where $\ket{a,b} = |a(\textbf{Q})) \otimes \ket{b}$ for electronic states $\{|a(\textbf{Q}))\}$ and vibrational states $\{\ket{b}\}$ (i.e., adiabatic approximation), where \textbf{Q}, the system normal modes, is the adiabatic parameter.
 \cite{BornOppenheimer, Tang1970}
 We will henceforth suppress the dependence of the electronic states on \textbf{Q} for simplicity.
+It is worthwhile to note that the time-dependent Raman formalism developed by Heller \textit{et al.} can be applied to hyper-Raman scattering. \cite{Myers1982, Shoute2005}
+However, since our goal is to expose the Quantum Mechanical aspects of HDFG spectroscopy, we choose to employ the typical sum-over-states formalism.
 
@@
 where $R_{i}^{ab,cd}$ is the i$^{th}$ element of $\mel{a,b}{\vec{R}}{c,d}$.
-It is common in the hyper-Raman literature to write $\Delta_{e\tilde{v}', gv} \Delta_{mn, gv} = \Delta_{e\tilde{v}', gv}$.
+To ease readability, we use $\ket{a}$ to refer to ground state vibrational modes and $\ket{\tilde{b}}$ to refer to excited state vibrational modes.
 Using our definition of vibronic states, we can write, for example,
@@
 \end{widetext}
-where $\langle a | b \rangle$ and $\mel{a}{Q}{b}$ are Franck-Condon factors and Herzberg-Teller-type integrals, respectively.
-To ease readability, we use $\ket{a}$ to refer to ground state vibrational modes and $\ket{\tilde{b}}$ to refer to excited state vibrational modes. 
+Note that it is common in the hyper-Raman literature to write $\Delta_{e\tilde{v}', gv} \Delta_{mn, gv} = \Delta_{e\tilde{v}', gv}$.
+Here, $\langle \tilde{a} | b \rangle$ and $\mel{\tilde{a}}{Q}{b}$ are Franck-Condon factors and Herzberg-Teller-type integrals, respectively.
 Duschinsky rotation effects are ignored in this discussion. \cite{Duschinsky1937}
@@
 To understand the vibronic structure of electronic resonance, we restrict consideration to electronic transitions between $|g)$ and $|e)$.  
-Note that HDFG experiments selectively excite ground state vibrational modes through $\omega_1$; we will assume the IR beam has excited the fundamental of an IR-active mode so that hyper-Raman scattering is between this mode and the ground state.
+Note that HDFG experiments selectively excite ground state vibrational modes through $\omega_1$; we will assume the IR beam has excited the fundamental of an IR-active mode, $\ket{g,1}$, so that hyper-Raman scattering is between ground state and $\ket{g,1}$.
 By working only in terms of this single normal mode (i.e., removing the sum over $z$ and taking $v=1$), 
@@
 	\caption{Contributions of $A, B$ (\autoref{ABterms_DR}) to HDFG spectrum for a simple two harmonic well system.
-		(a) Potential energy surfaces for a two-well system, (b) 1D HDFG spectrum for $\Delta = 0.5$, $\omega_1 = \omega_{g1, g0}$. 
+		(a) Potential energy surfaces for a two-well system, (b) 1D HDFG spectrum for $\Delta = 0.5$, $\omega_1 = \omega_{g1, g0}$, (c,d) Real and imaginary parts of terms plotted in (b), respectively.
+		All spectra are referenced to $\max{(A+B)}$. 
 		It is assumed that $\omega_2 = \omega_3$.
@@
 For an allowed electronic transition, the brightness of a vibronic resonance is controlled by overlap of ground and excited state vibrational wavefunctions (Franck-Condon factors).
-The $A$ term relies on excited state perturbations to the vibrational wavefunctions; if the excited electronic state minimally changes potential energy surface, so that ground and excited state vibrational eigenfunctions are identical, $\langle 1 | \tilde{v}' \rangle \langle \tilde{v}' | 0 \rangle = 0$ and $A$ vanishes, as discussed in the supporting information.
+The $A$ term relies on excited state perturbations to the vibrational wavefunctions; if the excited electronic state is minimally offset ($\Delta \rightarrow 0$), $\langle 1 | \tilde{v}' \rangle \langle \tilde{v}' | 0 \rangle = 0$ and $A$ vanishes, as discussed in the supporting information.
 Some $B$ terms do survive in the same limit, however; for instance, $B_1$ survives for $\tilde{v}'=1$ and $B_2$ survives for $\tilde{v}'=0$.
@@
 	\begin{ruledtabular}
-		\begin{tabular}{cccc}
+		\begin{tabular}{cccc}\label{fcht}
 			$2\omega_2$ Electronic Resonance & $\ket{e,\tilde{0}}$ & $\ket{e,\tilde{1}}$ & $\ket{e,\tilde{2}}$\\
@@
 			$A$ 
-			& $\langle 1 | \tilde{0} \rangle \langle \tilde{0} | 0 \rangle = -0.31 $  
-			& $\langle 1 | \tilde{1} \rangle \langle \tilde{1} | 0 \rangle = 0.27 $ 
-			& $\langle 1 | \tilde{2} \rangle \langle \tilde{2} | 0 \rangle = 0.04$\\
+			& $\langle 1 | \tilde{0} \rangle \langle \tilde{0} | 0 \rangle = 0.31 $  
+			& $\langle 1 | \tilde{1} \rangle \langle \tilde{1} | 0 \rangle = -0.27 $ 
+			& $\langle 1 | \tilde{2} \rangle \langle \tilde{2} | 0 \rangle = -0.04$\\
 
 			$B_1$ 
-			& $\langle 1 | \tilde{0} \rangle \mel{\tilde{0}}{Q}{0} = -0.08$ 
+			& $\langle 1 | \tilde{0} \rangle \mel{\tilde{0}}{Q}{0} = 0.08$ 
 			& $\langle 1 | \tilde{1} \rangle \mel{\tilde{1}}{Q}{0} = 0.48$ 
-			&$\langle 1 | \tilde{2} \rangle \mel{\tilde{2}}{Q}{0} = -0.14$\\
+			&$\langle 1 | \tilde{2} \rangle \mel{\tilde{2}}{Q}{0} = 0.14$\\
 
@@
 			& $\mel{1}{Q}{\tilde{0}} \langle \tilde{0} | 0 \rangle = 0.70$  
-			& $\mel{1}{Q}{\tilde{1}} \langle \tilde{1} | 0 \rangle = 0.07$ 
-			& $\mel{1}{Q}{\tilde{2}} \langle \tilde{2} | 0 \rangle = 0.08$\\
+			& $\mel{1}{Q}{\tilde{1}} \langle \tilde{1} | 0 \rangle = -0.07$ 
+			& $\mel{1}{Q}{\tilde{2}} \langle \tilde{2} | 0 \rangle = 0.06$\\
 		\end{tabular}
@@
 
+In the post-resonance region, the amplitude takes on an unexpected lineshape.
+This arises due to interference between the real and imaginary parts of $\gamma$ (\autoref{fig:doubres_spec}c, d).
+The abnormal lineshapes in both terms arises due to the sign of the Franck-Condon and Herzberg-Teller integrals that drive the output of the vibronic transitions for $\Delta = 0.5$ (\autoref{fcht}).
+Such effects have been seen elsewhere in spontaneous, surface enhanced hyper-Raman studies. \cite{Milojevich2011}
+Since $\Delta$ can take on a variety of values given a specific system, in the supporting information we demonstrate the impact of $\Delta$ on the HDFG response using previously reported values for Raman active vibrations in isoprene.
+\cite{Myers1982}
+Clearly, specific $\Delta$ values have a significant impact on the
+
 \subsection{Inhomogeneity in HDFG}
-An often unavoidable consequence in electronic spectroscopy is broadened lineshapes due to a high density of vibronic modes. 
+An often unavoidable consequence in electronic spectroscopy is broadened lineshapes due to a high density of vibronic modes, i.e., inhomogeneous broadening.
+It is worthwhile to investigate the impact of inhomogeneity on HDFG response and the resultant lineshapes. 
 In the discussion that follows, we assume that a vibrational mode in the ground state, $\ket{g,v}$, is correlated to the frequency of a vibronic $\ket{e,\tilde{v}'}$.\cite{Carlson1990line, Dong2015}
@@
 molecular collisions), then the frequency of $\ket{e,v}$ is $\omega_{ev} + c\xi$, where c is a shift coefficient.
-The strains shift resonance denominators, e.g., for $\omega_{ij} \rightarrow \omega_{ij} \pm c\xi$, as
-\begin{equation}
-	\Delta_{ij}(c\xi) = \omega_{ij} \pm c\xi -\omega_k - i\Gamma_{ij} \equiv \Delta_{ij}(0) \pm c\xi
-\end{equation}
-where $+ (-)$ refers to correlated (anti-correlated) modes.
-For simplicity, we assume c = 1.
+When two modes are positively correlated, $c > 0$; similarly, modes are negatively correlated when $c < 0$.
+For simplicity, we assume c = $\pm$1.
 
@@
 	\gamma_{ijkl} = \int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi)
-	= \frac{\sigma}{\pi}\int_{-\infty}^\infty \mathrm{d}\xi \frac{1}{\sigma^2 + \xi^2} \frac{\gamma_0}{\Delta_{ga}(\xi)\Delta_{ba}(\xi)}
+	= \frac{\sigma}{\pi}\int_{-\infty}^\infty \mathrm{d}\xi \frac{1}{\sigma^2 + \xi^2} \frac{\gamma_0}{\left(\Delta_{ga} - \xi\right)\left(\Delta_{ba}+\xi\right)}
 \end{equation} 
@@
 While Gaussian distributions are commonly used to describe inhomogeneous broadening, Lorentzian distributions have successfully described inhomogeneous broadening in a variety of spectroscopies and yield easily interpretable closed-form solutions.
-\cite{Dick83_1, Carlson1990line, RN410, Yurs2011, Yurs2012}
+\cite{Dick83_1, Carlson1990line, RN410}
 
@@
 Can vSFG experimental setups detect HDFG signals?
-SFG setups typically leverage the surface selectivity of $\chi^{(2)}$ polarizations,\cite{RN132, RN133} which results in extremely small emission volumes, so SFG setups are typically quite sensitive.
+SFG setups typically leverage the surface selectivity of $\chi^{(2)}$ polarizations, which results in extremely small emission volumes, so SFG setups are typically quite sensitive.
 However, HDFG is a weak $\chi^{(3)}$ process because it depends upon hyper-Raman cross-sections, which are commonly several orders of magnitude weaker than corresponding Raman transitions.\cite{RN515}
@@
 \begin{equation}\label{chi3}
-		\chi^{(3)}_{IJKL} = -\frac{NF}{4D \hbar \varepsilon_0 \Delta_{gv}} \langle \beta_{ijk} \mu_l \rangle \rho_{gg}\\
+		\chi^{(3)}_{IJKL} = -\frac{NF}{4D \hbar \varepsilon_0 \Delta_{gv}} \langle \beta_{ijk} \mu_l \rangle_{IJKL} \rho_{gg}\\
 \end{equation}
 For simplicity, we take $\rho_{gg} = 1$.
-The steps behind orientational averaging of $\gamma_{ijkl}$, a rank four tensor in the molecular frame, are detailed elsewhere.\cite{Andrews1977, McDonnell2024}
-Briefly, a tensor in the molecular frame, $A_{ijkl}$, is transformed into an element of the same tensor in the laboratory frame, $\langle A \rangle_{IJKL}$, through $\langle A \rangle_{IJKL}$ = $\theta^{ijkl}_{IJKL} A_{ijkl}$, where summation over repeated indices is implied and $\theta$ is the transformation operator.
-\cite{McDonnell2024, Andrews1977}
 Orientational averaging shows specific polarization schemes isolate linear combinations of different $\beta_{ijk}$ terms. \cite{Bersohn1966, Willetts1992, Kauranen1996}
@@
 \begin{equation}\label{betasive}
-	\left\langle \frac{\partial \beta}{\partial Q_v} {\frac{\partial \mu}{\partial Q_v}} \right\rangle _{IJKL} = -\frac{8D \varepsilon_0}{NF}  {\Gamma_{gv} \omega_{vg}} \chi^{(3)}_{IJKL}
+	\left\langle \frac{\partial \beta_{ijk}}{\partial Q_v} {\frac{\partial \mu_l}{\partial Q_v}} \right\rangle_{IJKL} = -\frac{8D \varepsilon_0}{NF}  {\Gamma_{gv} \omega_{vg}} \chi^{(3)}_{IJKL}
 \end{equation}
-$\chi^{(3)}$ itself can be extracted with use of an internal standard.\cite{Levenson1974_1, Levenson1974_2}
-Since $\abs{\partial \mu / \partial Q}$ values can be extracted from FT-IR spectra,\cite{RN459} HDFG can give quantitative information on the magnitude of $\beta_{ijk}$ for infrared active vibrations.
+
+Since $\abs{\partial \mu_l / \partial Q}$ values can be extracted from FT-IR spectra and $\chi^{(3)}$ can be extracted through the Bloembergen interferometry experiment,\cite{Levenson1974_1, Levenson1974_2, RN459} HDFG can give quantitative information on the magnitude of $\beta_{ijk}$ for infrared active vibrations.
 Additionally, by using non-degenerate input frequencies to stimulate the hyper-Raman transition, the asymmetric properties of $\beta_{ijk}$ can be examined and quantified.
-\cite{Christie1971, Denisov1986, Kozich2007}
+\cite{Denisov1986, Kozich2007}
 These quantitative aspects of HDFG could prove useful for examining how well computational methods calculate $\beta_{ijk}$ values.
@@
 R.P.M. acknowledges support from the National Science Foundation Graduate Research Fellowship Program (Grant no. DGE-2137424).
+
+\section{Supplemental Information}
+See the supporting information for details on deriving closed-form solutions to Herzberg-Teller integrals, dependence of the HDFG spectrum on $\Delta$, and integration of \autoref{contour}.
 

### 2024-09-16 si.tex
more edits
almost there

@@
 \section{Evaluating Herzberg-Teller Integrals for Harmonic Wells of Identical Curvature}
-In this section, we discuss the evaluation of Herzberg-Teller integrals,\cite{HerzbergTeller1933} in the limit of no Duschinsky coupling,\cite{Duschinsky1937} when the ground and first excited state are harmonic wells of identical curvature.
-We use the Hamiltonian described in the main text, $H = H_g |g) \left(g| + H_e |e\right) (e|$, where
+In this section, we discuss the evaluation of Herzberg-Teller integrals, in the limit of no Duschinsky coupling, when the ground and first excited state are harmonic wells of identical curvature.\cite{HerzbergTeller1933, Duschinsky1937}
+We investigate the one dimensional case using the Hamiltonian described in the main text, $H = H_g |g) \left(g| + H_e |e\right) (e|$, where
 \begin{subequations}\label{Hamiltonian}
@@
 \end{subequations}
-Here, $p,q$ are the dimensionless conjugate normal mode coordinates.
-Franck-Condon factors and Herzberg-Teller integrals are often evaluated in position space using known solutions to the Harmonic Oscillator Hamiltonian \cite{RN230}
+Here, $p,q$ are the dimensionless conjugate normal mode coordinates, $\hbar\omega_{eg}$ is the energy difference between $H_e$ and $H_g$, and $\Delta$ is the dimensionless offset of the excited state surface relative to the ground state.
+Franck-Condon factors and Herzberg-Teller integrals are often evaluated in position space using known solutions to the Harmonic Oscillator Hamiltonian, 
 \begin{equation}
-	\psi_m(q) = \langle q | m \rangle = N(m) H_m(q) \exp(-q^2/2)
+	\psi_m(q) = \langle q | m \rangle = N(m) H_m(q) \exp(-q^2/2),
 \end{equation}
-where $N(m) = (m! \ 2^m \pi^{\frac{1}{2}})^{-\frac{1}{2}}$ is the normalization factor and $H_m$ is the m$^{th}$ Hermite Polynomial.
-We begin by generating an expression for $\mel{\tilde{n}}{q^k}{m}$, as this will resolve into Franck-Condon factors for $n = 0$ and Herzberg-Teller integrals for $n=1$.
+where $N(m) = (m! \ 2^m \pi^{\frac{1}{2}})^{-\frac{1}{2}}$ is the normalization factor and $H_m$ is the m$^{th}$ Hermite Polynomial.\cite{RN230}
+We begin by generating an expression for $\mel{\tilde{n}}{q^k}{m}$, as this will resolve into Franck-Condon factors for $k = 0$ and Herzberg-Teller integrals for $k=1$.
 As in the main text, $\{\ket{\tilde{a}}\}$ are vibrational states on the first excited state $|e)$ and $\{\ket{b}\}$ are vibrational states on the ground state $|g)$.
@@
 		\mel{\tilde{n}}{q^k}{m} &= \int_{-\infty}^\infty \mathrm{d}q \psi^*_n(q-\Delta) q^k \psi_m(q)\\
-		&= \int_{-\infty}^\infty \mathrm{d}q N(n) N(m) H_n(q-\Delta) \exp(-\frac{(q - \Delta)^2}{2}) q^k H_m(q) \exp(-\frac{q^2}{2})
+		&= \int_{-\infty}^\infty \mathrm{d}q N(n) N(m) H_n(q-\Delta) \exp(-\frac{(q - \Delta)^2}{2}) q^k H_m(q) \exp(-\frac{q^2}{2}),
 \end{split}
 \end{equation}
+where $k=0$ corresponds to a Franck-Condon factor and $k=1$ refers to a Herzberg-Teller integral.
 Introducing $\tilde{N} \equiv N(n)N(m)$ and slightly rearranging, we see
 \begin{equation}\label{key}
-	\mel{\tilde{n}}{q^k}{m} = \tilde{N} \exp(-\frac{\Delta^2}{2}) \int_{-\infty}^\infty \mathrm{d}q H_n(q+\Delta) q^k H_m(q) \exp(-q^2 + q\Delta)
+	\mel{\tilde{n}}{q^k}{m} = \tilde{N} \exp(-\frac{\Delta^2}{2}) \int_{-\infty}^\infty \mathrm{d}q H_n(q-\Delta) q^k H_m(q) \exp(-q^2 + q\Delta)
 \end{equation}
 This is the key result.
-While integrals of form \autoref{key} can be computed straightforwardly using mathematical packages such as \texttt{Mathematica} or \texttt{sympy}, it is a useful exercise in Gaussian integral manipulation to evaluate Herzberg-Teller or Franck-Condon integrals.
+While integrals of form \autoref{key} can be computed straightforwardly using mathematical packages such as \texttt{Mathematica} or \texttt{SymPy}, \cite{Mathematica, sympy} it is a useful exercise in Gaussian integral manipulation to evaluate Herzberg-Teller or Franck-Condon integrals.
 As a side note, \autoref{key} explicitly shows
@@
 	\begin{split}
-		\int_{-\infty}^\infty \mathrm{d}q \exp(-q^2 + q\Delta) &= \int_{-\infty}^\infty \mathrm{d}q \exp(-(q^2 + q\Delta +\frac{\Delta^2}{4} - \frac{\Delta^2}{4}))\\
+		\int_{-\infty}^\infty \mathrm{d}q \exp(-q^2 + q\Delta) &= \int_{-\infty}^\infty \mathrm{d}q \exp(-(q^2 - q\Delta +\frac{\Delta^2}{4} - \frac{\Delta^2}{4}))\\
 		&= \exp(\frac{\Delta^2}{4}) \int_{-\infty}^\infty \mathrm{d}q \exp(-(q - \frac{\Delta}{2})^2) \\
@@
 \begin{split}
-	\mel{\tilde{1}}{q}{0} = \tilde{N} \exp(-\frac{\Delta^2}{2}) \int_{-\infty}^\infty \mathrm{d}q H_1(q+\Delta) q H_0(q) \exp(-q^2 - q\Delta)
+	\mel{\tilde{1}}{q}{0} = \tilde{N} \exp(-\frac{\Delta^2}{2}) \int_{-\infty}^\infty \mathrm{d}q H_1(q-\Delta) q H_0(q) \exp(-q^2 + q\Delta)
 \end{split}
 \end{equation}
-Using $H_0(q) = 1$ and $H_1(q) = 2q$,\cite{RN230} 
+Using $H_0(q) = 1$ and $H_1(q) = 2q$,
 \begin{equation}\label{HT10}
 	\begin{split}
-		\mel{\tilde{1}}{q}{0} &= \tilde{N} \exp(-\frac{\Delta^2}{2}) \int_{-\infty}^\infty \mathrm{d}q \ 2(q + \Delta) q \exp(-q^2 - q\Delta)\\
-		&= 2\tilde{N} \exp(-\frac{\Delta^2}{2}) \int_{-\infty}^\infty \mathrm{d}q \ (q^2 + q \Delta) \exp(-q^2 - q\Delta)\\
-		&=  2\tilde{N} \exp(-\frac{\Delta^2}{2}) \left(\int_{-\infty}^\infty \mathrm{d}q \ q^2 \exp(-q^2 - q\Delta) + 2\Delta \int_{-\infty}^\infty \mathrm{d}q \ q \exp(-q^2 - q\Delta) \right)
+		\mel{\tilde{1}}{q}{0} &= \tilde{N} \exp(-\frac{\Delta^2}{2}) \int_{-\infty}^\infty \mathrm{d}q \ 2(q - \Delta) q \exp(-q^2 + q\Delta)\\
+		&= 2\tilde{N} \exp(-\frac{\Delta^2}{2}) \int_{-\infty}^\infty \mathrm{d}q \ (q^2 - q \Delta) \exp(-q^2 + q\Delta)\\
+		&=  2\tilde{N} \exp(-\frac{\Delta^2}{2}) \left(\int_{-\infty}^\infty \mathrm{d}q \ q^2 \exp(-q^2 + q\Delta) - \Delta \int_{-\infty}^\infty \mathrm{d}q \ q \exp(-q^2 + q\Delta) \right)
 	\end{split}
@@
 		\begin{split}
-					\int_{-\infty}^\infty \mathrm{d}q \ q \exp(-q^2 - q\Delta) &= -\partial_{\Delta} \left(\sqrt{\pi} \exp(\frac{\Delta^2}{4})\right)\\
-					& = -\sqrt{\pi} \frac{\Delta}{2} \exp(\frac{\Delta^2}{4})
+					\int_{-\infty}^\infty \mathrm{d}q \ q \exp(-q^2 + q\Delta) &= \partial_{\Delta} \left(\sqrt{\pi} \exp(\frac{\Delta^2}{4})\right)\\
+					& = \sqrt{\pi} \frac{\Delta}{2} \exp(\frac{\Delta^2}{4})
 		\end{split}
@@
 	\begin{split}
-		\int_{-\infty}^\infty \mathrm{d}q \ q^2 \exp(-q^2 - q\Delta) &= -\partial_{\Delta} \left(-\sqrt{\pi} \left(\frac{\Delta}{2} \exp(\frac{\Delta^2}{4})\right)\right)\\
+		\int_{-\infty}^\infty \mathrm{d}q \ q^2 \exp(-q^2 + q\Delta) &= \partial_{\Delta} \left(\sqrt{\pi} \left(\frac{\Delta}{2} \exp(\frac{\Delta^2}{4})\right)\right)\\
 		& =\sqrt{\pi} \left(\frac{1}{2}\exp(\frac{\Delta^2}{4}) + \frac{\Delta^2}{4} \exp(\frac{\Delta^2}{4})\right)
@@
 The relevant Franck-Condon factors and Herzberg-Teller integrals, assuming identical curvature and no Duschinsky coupling, are plotted in \autoref{fig:fcht} as a function of offset, $\Delta$.
-These functions were generated by evaluating \autoref{key} for $k=0, 1$ using \texttt{sympy}.%todo:citesympy
 
@@
 	\includegraphics[width=6.675in]{figures/fcht.png}
-	\caption{Poles (black dots) and contour (blue line) used to evaluate \autoref{integraly} for (a) anti-correlated and (b) correlated modes.} 
+	\caption{Plots of select (a) Franck-Condon factors and (b) Herzberg-Teller integrals relevant to this manuscript as a function of offset, $\Delta$.} 
 	\label{fig:fcht}
@@
 
+It is clear from \autoref{fig:fcht} that the HDFG spectrum will have a significant dependence upon $\Delta$, even for small deviations from complete overlap. 
+To this end, we first investigate the impact of $\Delta$ on a vibrational mode with a fundamental frequency 1600 cm$^{-1}$ and linewidth of 400 cm$^{-1}$ (\autoref{fig:chgdelta}).
+
+\begin{figure}[!htbp]
+	\centering
+	\includegraphics[width=6.675in]{figures/changedelta.png}
+	\caption{Plots of select (a) Franck-Condon factors and (b) Herzberg-Teller integrals relevant to this manuscript as a function of offset, $\Delta$.} 
+	\label{fig:chgdelta}
+\end{figure}
 \section{Evaluation of Equation 14}

### 2024-09-16 figures/Varying_Delta_SI.py

@@ -28,10 +28,10 @@ aspects = [[[0, 0], 1], [[1, 0], 1]]
 
 #define Franck-Condon factors following page 164 of Roger Carlson's thesis in terms of 'q', the offset
 def f00(q): #<0|0>
-    return np.e**(-q**2/4)
+    return np.exp(-q**2/4)
 
 def f01(q): #<0|1>
-    return -q/(np.sqrt(2)) * f00(q)
+    return q/(np.sqrt(2)) * f00(q)
 
 def f10(q): #<1|0>
     return -1*f01(q)
@@ -44,14 +44,13 @@ def f02(q): #<0|2>
 
 def f20(q): #<2|0>
     return f02(q)
-
-def f12(q): #<1|2>
+   
+def f21(q): #<2|1>
     return -q * (1 - q**2/4) *f00(q)
-    
 
 #define Herzberg Teller overlap integrals following page 165 of Roger Carlson's thesis in terms of q
 def h00(q): #<0|Q|0>
-    return -q/2 * f00(q)
+    return q/2 * f00(q)
 
 def h01(q): #<0|Q|1>
     return 1/np.sqrt(2) * (1 + q**2 /2) * f00(q)
@@ -60,20 +59,22 @@ def h10(q): #<1|Q|0>
     return 1/np.sqrt(2) * (1 - q**2 /2) * f00(q)
 
 def h11(q): #<1|Q|1>
-    return -q/2 * (1 - q**2 / 2) * f00(q)
+    return -q/2 * (-1 + q**2 / 2) * f00(q)
 
 def h12(q): #<1|Q|2>
-    return (1 + q**2/4 - q**4/8) * f00(q)
+    return (-1/8) * (q**4 - 2*q**2 - 8) * f00(q)
+
+def h21(q): #<2|Q|1>
+    return (1/8)*(8 - 6*q**2 + q**4) * f00(q)
 
 def h20(q): #<2|Q|0>
     return -q/np.sqrt(2) * (1 - q**2 /4) * f00(q)
 
-
 #define resonance denominator
 def Deltaevgo(v,x,l):
     weg = 30000
-    G = [1000, 1000, 1000] #linewidths
-    return 1/(weg + 2200*v - x - 1j*G[l]) #assuming the |0> -> |n> transiton is 2200*n  cm^-1
+    G = [400, 400, 400] #linewidths
[…]

### 2024-09-16 figures/inhomo.py

@@ -86,12 +86,12 @@ plt.yticks(ticks = [])
 plt.xticks(ticks = [])
 
 
+#todo: make an array so I can just call specific matrix element of the fc and ht factors, then do a for loop over that array, should work out well.
+
 
 #define Franck-Condon factors following page 164 of Roger Carlson's thesis in terms of 'q', the offset
-#<a|b> == |a> is on the ES and |b> is on the GS.
-
 def f00(q): #<0|0>
-    return np.exp(-q**2/4)
+    return np.e**(-q**2/4)
 
 def f01(q): #<0|1>
     return q/(np.sqrt(2)) * f00(q)
@@ -125,19 +125,19 @@ def h11(q): #<1|Q|1>
     return -q/2 * (-1 + q**2 / 2) * f00(q)
 
 def h12(q): #<1|Q|2>
-    return (-1/8) * (q**4 - 2*q**2 - 8) * f00(q)
+    return (1 + q**2/4 - q**4/8) * f00(q)
 
 def h21(q): #<2|Q|1>
-    return (1/8)*(8 - 6*q**2 + q**4) * f00(q)
+    return (1 + q**2/4 - q**4/8) * f00(q)
 
 def h20(q): #<2|Q|0>
     return -q/np.sqrt(2) * (1 - q**2 /4) * f00(q)
 
 #define resonance denominator
-def Deltaevgo(v,x,l):
+def Deltaba(x):
     weg = 30000
-    G = [400, 400, 400] #linewidths
-    return 1/(weg + 1600*v - x - 1j*G[l]) #assuming the |0> -> |n> transiton is 1600*n  cm^-1
+    G = 400 #linewidths
+    return (weg + 1600 - x - 1j*G) #assuming the |0> -> |n> transiton is 1600*n  cm^-1
 
 
 #define numbers for AB terms
@@ -148,51 +148,68 @@ dMgedQ = 0.007 #dM^eg / dQ
 
 
 #define terms
-y = np.linspace(10000, 50000, 3000000)
+y = np.linspace(10000, 50000, 1000000)
 
-
[…]

### 2024-09-16 figures/plotting_fcht.py

@@ -7,7 +7,6 @@ Created on Tue Jan 17 09:28:39 2023
 import numpy as np
 import WrightTools as wt
 import matplotlib.pyplot as plt 
-from matplotlib.patches import FancyArrowPatch
 
 wt.artists.apply_rcparams(kind="publication")
 
@@ -15,7 +14,7 @@ save = False
 fontsize =18
 
 #define harmonic wells and coordinates
-d = np.linspace(-1, 5, 5000)
+d = np.linspace(-5, 5, 5000)
 
 #make figure
 cols = [1, 1] 
@@ -28,10 +27,10 @@ aspects = [[[0, 0], 1], [[1, 0], 1]]
 
 #define Franck-Condon factors following page 164 of Roger Carlson's thesis in terms of 'q', the offset
 def f00(q): #<0|0>
-    return np.e**(-q**2/4)
+    return np.exp(-q**2/4)
 
 def f01(q): #<0|1>
-    return -q/(np.sqrt(2)) * f00(q)
+    return q/(np.sqrt(2)) * f00(q)
 
 def f10(q): #<1|0>
     return -1*f01(q)
@@ -46,7 +45,7 @@ def f20(q): #<2|0>
     return f02(q)
    
 def f21(q): #<2|1>
-    return q * (1 - q**2/4) *f00(q)
+    return -q * (1 - q**2/4) *f00(q)
 
 #define Herzberg Teller overlap integrals following page 165 of Roger Carlson's thesis in terms of q
 def h00(q): #<0|Q|0>
@@ -62,14 +61,13 @@ def h11(q): #<1|Q|1>
     return -q/2 * (-1 + q**2 / 2) * f00(q)
 
 def h12(q): #<1|Q|2>
-    return (1 + q**2/4 - q**4/8) * f00(q)
+    return (-1/8) * (q**4 - 2*q**2 - 8) * f00(q)
 
 def h21(q): #<2|Q|1>
-    return (1 + q**2/4 - q**4/8) * f00(q)
+    return (1/8)*(8 - 6*q**2 + q**4) * f00(q)
 
 def h20(q): #<2|Q|0>
     return -q/np.sqrt(2) * (1 - q**2 /4) * f00(q)
-
 
 #plot
 fig, gs = wt.artists.create_figure(width="dissertation", nrows=2, cols=cols, aspects=aspects, wspace=1) 
[…]

### 2024-09-17 paper.tex
more

@@
 Nonlinear spectroscopic probes of electronic-vibrational coupling are not limited to the Raman and hyper-Raman based techniques diagrammed in \autoref{fig:comparisonwmel}.
-Independently developed by the Fleming and Khalil groups, respectively, 2D Electronic-Vibrational (2D-EV) and 2D Vibrational-Electronic (2D-VE) spectroscopy are based upon pump-probe and absorption type pathways which also investigate e-v coupling.\cite{Oliver2014, Courtney2015}
-They have been used to investigate vibronic coupling in a variety of complex molecular systems, and serve as 2D pump-probe type analogues to the hyper-Raman-based spectroscopies discussed here.
+Independently developed by the Fleming and Khalil groups, respectively, 2D Electronic-Vibrational (2D-EV) and 2D Vibrational-Electronic (2D-VE) spectroscopy are based upon pump-probe and absorption type pathways which also investigate e-v coupling.\cite{Oliver2014, Courtney2015, Courtney2015_1}
+The Rao group has also developed a $\chi^{(4)}$ analogue of 2D-EV, 2D-EV sum frequency generation (2D-EVSFG), to investigate interfacial e-v coupling. \cite{Deng2021}  
+These methods have been used to investigate vibronic coupling in a variety of molecular systems and serve as 2D pump-probe type analogues to the hyper-Raman-based spectroscopies discussed here.\cite{Courtney2015, Gaynor2018, Arsenault2020, HuangFu2023}
 
@@
 where $H$ is the (static) system Hamiltonian, $V(t)$ is the field-matter interaction and $\rho_R$ is the relaxation density matrix. \cite{RN455}
-For simplicity, as dynamics is not a major focus of this article, we write electric fields as plane waves, such that $\vec{E}(\vec{x},t) = \frac{1}{2} \vec{E}_0\exp(-i(\vec{k} \cdot \vec{x} - \omega t)) + \mathrm{c.c.}$.
 In systems where interactions with surroundings are relevant, $\dot{\rho}_R$ becomes a complex function that can be modified to include phenomena such as system-bath interactions, solvent-solute coupling, among others.
@@
 	\gamma_{ijkl} = \int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi)
-	= \frac{\sigma}{\pi}\int_{-\infty}^\infty \mathrm{d}\xi \frac{1}{\sigma^2 + \xi^2} \frac{\gamma_0}{\left(\Delta_{ga} - \xi\right)\left(\Delta_{ba}+\xi\right)}
+	= \frac{\sigma}{\pi}\int_{-\infty}^\infty \mathrm{d}\xi \frac{1}{\sigma^2 + \xi^2} \frac{\gamma_0}{\left(\Delta_{ga} \mp c\xi\right)\left(\Delta_{ba}\pm c\xi\right)}
 \end{equation} 
+where $\gamma_0$ contains all values in \autoref{drgamma_notaylor} not dependent upon $\xi$.
 The limit of static inhomogeneity is chosen for simplicity.
-While Gaussian distributions are commonly used to describe inhomogeneous broadening, Lorentzian distributions have successfully described inhomogeneous broadening in a variety of spectroscopies and yield easily interpretable closed-form solutions.
-\cite{Dick83_1, Carlson1990line, RN410}
+While Gaussian distributions are commonly used as a phenomenological description of inhomogeneous broadening, Lorentzian distributions have successfully described inhomogeneous broadening in a variety of spectroscopies and yield easily interpretable closed-form solutions.
+\cite{Desiderio1979, Dick83_1, Carlson1990line, RN410}
 
@@
 	\begin{equation}\label{linenarrowa}
-		\gamma_{ijkl} = \frac{- \gamma_0}{\Delta_{ga}(- i \sigma)} \left( \frac{1}{\Delta_{ba}(i \sigma)} + \frac{2 i \sigma}{\Delta_{ga}(i \sigma)} \frac{1}{\Delta_{ba}(0) + \Delta_{ga}(0)} \right)
+		\gamma_{ijkl} = \frac{- \gamma_0}{\Delta_{ga}+ i \sigma} \left( \frac{1}{\Delta_{ba}-i \sigma} + \frac{2 i \sigma}{\Delta_{ga}-i \sigma} \frac{1}{\Delta_{ba}(0) + \Delta_{ga}(0)} \right)
 	\end{equation}
 	\begin{equation}
-		\gamma_{ijkl} = \frac{\gamma_0}{\Delta_{ga}(i\sigma)\Delta_{ba}(i \sigma)}
+		\gamma_{ijkl} = \frac{\gamma_0}{\left(\Delta_{ga}-i\sigma \right) \left(\Delta_{ba}-i \sigma\right)}
 	\end{equation}
 \end{subequations}
-for correlated and anti-correlated modes, respectively, where $\gamma_0$ involves factors related to $A,B$ and $\mu$.
-The output for correlated modes shows the presence of a new term, $\frac{2i\sigma}{\Delta_{ga}(0) + \Delta_{ba}(0)}$. 
+for correlated and anti-correlated modes, respectively.
+The output for correlated modes shows the presence of a new term, $\frac{2i\sigma}{\Delta_{ga} + \Delta_{ba}}$. 
 This term is amplified by the width of the inhomogeneous envelope ($\sigma$) and has a linewidth $\Gamma_{ba} + \Gamma_{ga}$, which linenarrows the transition. 
@@
 As a result, HDFG output is sensitive to the relative overlap of potential energy surfaces.
-In HDFG, using the Chung-Ziegler approach to vibronic hyper-Raman scattering, output is dependent upon changes in different potential energy surfaces along the coordinate of the vibrational mode selected by the infrared input.
-If the potential energy surface is not significantly modulated along the vibrational coordinate of interest, then output is dominated by $B$ term resonances, i.e. Herzberg-Teller coupling.
+Using the Chung-Ziegler approach to vibronic hyper-Raman scattering, HDFG output is found to be dependent upon changes in potential energy surfaces along the coordinate of the vibrational mode selected by the infrared input.
+If the potential energy surface is not significantly modulated along the vibrational coordinate of interest, then output is dominated by $A$ term resonances, i.e. Herzberg-Teller coupling.
+However, $B$ term resonances dominate in centrosymmetric media, as $A$ term resonances vanish through parity constraints.
+For positively correlated vibrational and vibronic resonances, HDFG linenarrows the spectral output, eliminating inhomogeneous broadening. 
 As a result, HDFG possesses types of site-selective properties analogous to those of coherent Raman experiments, which can allow for a thorough analysis of vibronic coupling schemes in isotropic systems.

### 2024-09-17 si.tex
more

@@
 			\int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi) &= 2\pi i \sum_k \lim_{\xi \rightarrow \xi_k} P(\xi) \gamma_{ijkl}(\xi) (\xi - \xi_k)\\
-			&= 2\pi i \frac{\gamma_0 \sigma}{\pi}  \lim_{\xi \rightarrow -i\sigma} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga}(0) - \xi} \frac{1}{\Delta_{ba}(0) - \xi} (\xi + i \sigma) \\ 
-			&+ 2\pi i \frac{\gamma_0 \sigma}{\pi} \lim_{\xi \rightarrow \Delta_{ga}(0)} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga}(0) - \xi} \frac{1}{\Delta_{ba}(0) - \xi} (\xi - \Delta_{ga})\\
-			&= 2 \gamma_0 i \sigma (\frac{1}{2 i \sigma} \frac{1}{-i \sigma - \Delta_{ga}(0)} \frac{1}{\Delta_{ba}(0) - i\sigma} ) - 2 \gamma_0 i \sigma (\frac{1}{\sigma^2 + (\Delta_{ga} (0))^2} \frac{1}{\Delta_{ga}(0) + \Delta_{ba}(0)} )\\
-			&= -\frac{\gamma_0}{\Delta_{ga}(0) + i \sigma} (\frac{1}{\Delta_{ba}(0) - i \sigma} + \frac{2i\sigma}{(\Delta_{ga}(0) - i \sigma)(\Delta_{ga}(0) + \Delta_{ba}(0))})\\
+			&= 2\pi i \frac{\gamma_0 \sigma}{\pi}  \lim_{\xi \rightarrow -i\sigma} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga}(0) + \xi} \frac{1}{\Delta_{ba} - \xi} \left(\xi + i \sigma\right) \\
+			&+ 2\pi i \frac{\gamma_0 \sigma}{\pi} \lim_{\xi \rightarrow \Delta_{ga}(0)} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga}(0) - \xi} \frac{1}{\Delta_{ba}(0) - \xi} \left(\xi - \Delta_{ga}\right)\\
+			&= 2 \gamma_0 i \sigma \left(\frac{1}{2 i \sigma} \frac{1}{-i \sigma - \Delta_{ga}(0)} \frac{1}{\Delta_{ba}(0) - i\sigma} \right) - 2 \gamma_0 i \sigma \left(\frac{1}{\sigma^2 + (\Delta_{ga} (0))^2} \frac{1}{\Delta_{ga}(0) + \Delta_{ba}(0)} \right)\\
+			&= -\frac{\gamma_0}{\Delta_{ga}(0) + i \sigma} \left(\frac{1}{\Delta_{ba}(0) - i \sigma} + \frac{2i\sigma}{(\Delta_{ga}(0) - i \sigma)(\Delta_{ga}(0) + \Delta_{ba}(0))}\right)\\
 		\end{split}

### 2024-09-17 paper.tex
just need to plot the different deltas now

@@
 
-\author{Ryan P. McDonnell} 
+\author{Ryan P. McDonnell} \email{rpmcdonnell@wisc.edu}
 \author{Daniel D. Kohler}
@@
 	\caption{Contributions of $A, B$ (\autoref{ABterms_DR}) to HDFG spectrum for a simple two harmonic well system.
-		(a) Potential energy surfaces for a two-well system, (b) 1D HDFG spectrum for $\Delta = 0.5$, $\omega_1 = \omega_{g1, g0}$, (c,d) Real and imaginary parts of terms plotted in (b), respectively.
+		(a) Potential energy surfaces for a two-well system, (b) 1D HDFG spectrum for $\Delta = 0.5$, $\omega_1 = \omega_{g1, g0}$, (c,d) real and imaginary parts of terms plotted in (b), respectively.
 		All spectra are referenced to $\max{(A+B)}$. 
@@
 		Note that (b) plots magnitudes of the labeled quantities.
-		The vibrational states on the $|g)$ and $|e)$ manifolds are spaced 1600 cm$^{-1}$ apart, with the vibronic states $\ket{e,\tilde{v}'}$ given linewidths of 800 cm$^{-1}$ and $\hbar \omega_{eg}$ = 30000 cm$^{-1}$.
+		The vibrational states on the $|g)$ and $|e)$ manifolds are spaced 1600 cm$^{-1}$ apart, with the vibronic states $\ket{e,\tilde{v}'}$ given linewidths of 400 cm$^{-1}$ and $\hbar \omega_{eg}$ = 30000 cm$^{-1}$.
 		Dotted lines in (b) denote the $\tilde{v}'$ = 0, 1, 2 vibronic resonances. 
@@
 for the ground ($H_g$) and first excited ($H_e$) states, where $p$ (momentum) and $q$ (position) are the dimensionless conjugate coordinates of the normal mode, the A and B contributions can be evaluated using Franck-Condon and Herzberg-Teller integrals tabulated in terms of the dimensionless normal mode $q$ and offset parameter $\Delta$ (\autoref{fig:doubres_spec}a).
-System-bath interactions are neglected for this discussion.
+System-bath interactions are neglected in this discussion.
 For simplicity, we restrict consideration to $v^\prime \in \{0,1,2\}$ and take $\Delta = 0.5$.
@@
 
-\autoref{ABterms_DR} shows important selection rules for the vibronic transitions.
+\autoref{ABterms_DR} shows important selection rules for vibronic transitions in HDFG.
 The $A$ term is allowed whenever an electronic transition has a one- and two- photon transition moment.
 For centrosymmetric molecules, an electronic transition cannot be both one- and two- photon allowed by parity, so the $A$ term will vanish.
-This makes HDFG a unique tool for studying the electronic structure of centrosymmetric species in isotropic media, as it is sensitive to non-Condon effects.\cite{Olson2018}
+This makes HDFG a unique tool for studying the electronic structure of centrosymmetric species in isotropic media, as it is sensitive to non-Condon effects.\cite{Milojevich2011, Olson2018}
 For an allowed electronic transition, the brightness of a vibronic resonance is controlled by overlap of ground and excited state vibrational wavefunctions (Franck-Condon factors).
@@
 As has been discussed elsewhere, however, this approximation is in many cases invalid, especially when vibrational energies are large, like those explored here.\cite{Warshel1977, Myers1982, Li1990, Gong2015}
-This means that it is difficult to isolate $B$ terms when $A$ terms are present.
+This means that it could prove difficult to isolate $B$ terms when $A$ terms are present.
 As such, HDFG will have difficulty examining non-Condon effects ($B$ term contributions) in noncentrosymmetric systems.
@@
 If the frequency of $\ket{g,v}$ is written as $\omega_{gv} + \xi$, where $\xi$ is some external strain (e.g.
-molecular collisions), then the frequency of $\ket{e,v}$ is $\omega_{ev} + c\xi$, where c is a shift coefficient.
+molecular collisions), then the frequency of $\ket{e,\tilde{v}'}$ is $\omega_{e\tilde{v}'} + c\xi$, where c is a shift coefficient.
 When two modes are positively correlated, $c > 0$; similarly, modes are negatively correlated when $c < 0$.
@@
 	\gamma_{ijkl} = \int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi)
-	= \frac{\sigma}{\pi}\int_{-\infty}^\infty \mathrm{d}\xi \frac{1}{\sigma^2 + \xi^2} \frac{\gamma_0}{\left(\Delta_{ga} \mp c\xi\right)\left(\Delta_{ba}\pm c\xi\right)}
+	= \frac{\sigma}{\pi}\int_{-\infty}^\infty \mathrm{d}\xi \frac{1}{\sigma^2 + \xi^2} \frac{\eta_{ijkl}}{\left(\Delta_{ga} - \xi\right)\left(\Delta_{ba}+ c\xi\right)}
 \end{equation} 
-where $\gamma_0$ contains all values in \autoref{drgamma_notaylor} not dependent upon $\xi$.
+where $\eta_{ijkl}$ contains all values in \autoref{drgamma_notaylor} not dependent upon $\xi$.
 The limit of static inhomogeneity is chosen for simplicity.
@@
 	\begin{equation}\label{linenarrowa}
-		\gamma_{ijkl} = \frac{- \gamma_0}{\Delta_{ga}+ i \sigma} \left( \frac{1}{\Delta_{ba}-i \sigma} + \frac{2 i \sigma}{\Delta_{ga}-i \sigma} \frac{1}{\Delta_{ba}(0) + \Delta_{ga}(0)} \right)
+		\gamma_{ijkl} = \frac{- \eta_{ijkl}}{\Delta_{ga}+ i \sigma} \left( \frac{1}{\Delta_{ba}-i \sigma} + \frac{2 i \sigma}{\Delta_{ga}-i \sigma} \frac{1}{\Delta_{ba} + \Delta_{ga}} \right)
 	\end{equation}
 	\begin{equation}
-		\gamma_{ijkl} = \frac{\gamma_0}{\left(\Delta_{ga}-i\sigma \right) \left(\Delta_{ba}-i \sigma\right)}
+		\gamma_{ijkl} = \frac{\eta_{ijkl}}{\left(\Delta_{ga}-i\sigma \right) \left(\Delta_{ba}-i \sigma\right)}
 	\end{equation}
 \end{subequations}
-for correlated and anti-correlated modes, respectively.
+for correlated ($c = 1$) and anti-correlated ($c = -1$) modes, respectively.
 The output for correlated modes shows the presence of a new term, $\frac{2i\sigma}{\Delta_{ga} + \Delta_{ba}}$. 
@@
 As a result, HDFG output is sensitive to the relative overlap of potential energy surfaces.
-Using the Chung-Ziegler approach to vibronic hyper-Raman scattering, HDFG output is found to be dependent upon changes in potential energy surfaces along the coordinate of the vibrational mode selected by the infrared input.
-If the potential energy surface is not significantly modulated along the vibrational coordinate of interest, then output is dominated by $A$ term resonances, i.e. Herzberg-Teller coupling.
-However, $B$ term resonances dominate in centrosymmetric media, as $A$ term resonances vanish through parity constraints.
-For positively correlated vibrational and vibronic resonances, HDFG linenarrows the spectral output, eliminating inhomogeneous broadening. 
-As a result, HDFG possesses types of site-selective properties analogous to those of coherent Raman experiments, which can allow for a thorough analysis of vibronic coupling schemes in isotropic systems.
+If the potential energy surface is not significantly modulated along the vibrational coordinate of interest, then output is dominated by $A$ term resonances, or Franck-Condon contributions.
+However, $B$ term resonances, or Herzberg-Teller contributions, dominate in centrosymmetric media, as $A$ term resonances vanish in centrosymmetric media through parity constraints.
+A treatment of inhomogeneous broadening shows that for positively correlated vibrational and vibronic resonances, HDFG linenarrows the spectral output, eliminating inhomogeneous broadening. 
+As a result, HDFG possesses site-selective properties analogous to those of coherent Raman spectroscopies, which can allow for a thorough analysis of vibronic coupling schemes in isotropic systems.
 We show that HDFG provides alternative methods to extract the hyper-Raman hyperpolarizability of infrared active vibrations. 

### 2024-09-17 si.tex
just need to plot the different deltas now

--- 2024-09-16 si.tex
@@
 \end{figure}
-\section{Evaluation of Equation 14}
+\section{Evaluating impact of inhomogeneity on HDFG output}
 In this section, the integral
-\begin{equation}
+\begin{equation}\label{generalcontour}
 	\begin{split}
 		\gamma_{ijkl} &= \int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi)\\
-		&=\frac{\sigma}{\pi}\int_{-\infty}^\infty \mathrm{d}\xi \frac{1}{\sigma^2 + \xi^2} \frac{\gamma_0}{\Delta_{ga}(\xi)\Delta_{ba}(\xi)} \\
-		&= \frac{\gamma_0 \sigma}{\pi} \int_{-\infty}^\infty \mathrm{d}\xi\frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga}(0) - \xi} \frac{1}{\Delta_{ba}(0) + c\xi}\\
+		&= \frac{\sigma}{\pi}\int_{-\infty}^\infty \mathrm{d}\xi \frac{1}{\sigma^2 + \xi^2} \frac{\eta_{ijkl}}{\left(\Delta_{ga} - \xi\right)\left(\Delta_{ba}+ c\xi\right)} \\
+		&= \frac{\eta_{ijkl} \sigma}{\pi} \int_{-\infty}^\infty \mathrm{d}\xi\frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga} - \xi} \frac{1}{\Delta_{ba} + c\xi}\\
 	\end{split}
@@
 	\centering
-	\includegraphics[width=3.375in]{figures/corr_contour.png}
-	\caption{Poles (black dots) and contour (blue line) used to evaluate \autoref{integraly} for (a) anti-correlated and (b) correlated modes.} 
+	\includegraphics[width=6.675in]{figures/corr_contour.png}
+	\caption{Poles (blue dots) and contours (black line) used to evaluate \autoref{generalcontour} for (a) anti-correlated and (b) correlated modes.} 
 	\label{fig:contours}
@@
 \subsection{Anti-correlated Modes}
-For anti-correlated modes, the poles are situated in the complex plane as shown in \autoref{fig:contours}a.
-Since \autoref{integraly} is evaluated along the real axis, one can choose to evaluate the contour in the upper or lower half of the complex plane.
-Since evaluating the residues in the upper or lower half of the complex plane yields the same result for \autoref{integraly}, we choose the contour which wraps around the least number of poles.
-It is clear for c = -1 that there are four poles: $\pm i \sigma, \Delta_{ga}(0), \Delta_{ba}(0)$. 
-Following \autoref{fig:contours}, the contour that wraps the upper half of the complex plane has only one pole, $i \sigma$; as such, we choose to evaluate \autoref{integraly} in the upper half of the complex plane for the case of anti-correlated modes through the residue theorem as
+For anti-correlated modes ($c = -1$), the poles ($\xi_k$) are situated in the complex plane as shown in \autoref{fig:contours}a.
+Since \autoref{generalcontour} is evaluated along the real axis, one can choose to evaluate the contour in the upper or lower half of the complex plane.
+In other words, we can choose the contour which wraps around the least number of poles.
+For c = -1, there are four poles: $\pm i \sigma, \Delta_{ga}, \Delta_{ba}$. 
+The contour that wraps the upper half of the complex plane has only one pole, $i \sigma$; as such, we choose to evaluate \autoref{generalcontour} in the upper half of the complex plane for the case of anti-correlated modes, as it contains the least number of poles.
+Using the residue theorem, we see
 \begin{widetext}
@@
 			\int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi) &= 2\pi i \sum_k \lim_{\xi \rightarrow \xi_k} P(\xi) \gamma_{ijkl}(\xi) (\xi - \xi_k)\\
-			&= 2\pi i \frac{\gamma_0 \sigma}{\pi} \lim_{\xi \rightarrow i\sigma} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga}(0) - \xi} \frac{1}{\Delta_{ba}(0) - \xi} (\xi - i \sigma)\\
-			&= 2 \gamma_0 \sigma i \lim_{\xi \rightarrow i\sigma} \frac{1}{\xi + i\sigma} \frac{1}{\Delta_{ga}(0) - \xi} \frac{1}{\Delta_{ba}(0) - \xi}\\
-			&= 2\gamma_0 \sigma i \frac{1}{2i\sigma} \frac{1}{\Delta_{ga}(0) - i\sigma} \frac{1}{\Delta_{ba}(0) - i\sigma}\\
-			&= \frac{\gamma_0}{\Delta_{ga}(i\sigma)\Delta_{ba}(i \sigma)}\\
+			&= 2\pi i \frac{\eta_{ijkl} \sigma}{\pi} \lim_{\xi \rightarrow i\sigma} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga} - \xi} \frac{1}{\Delta_{ba} - \xi} (\xi - i \sigma)\\
+			&= 2 \eta_{ijkl} \sigma i \lim_{\xi \rightarrow i\sigma} \frac{1}{\xi + i\sigma} \frac{1}{\Delta_{ga} - \xi} \frac{1}{\Delta_{ba} - \xi}\\
+			&= 2\eta_{ijkl} \sigma i \frac{1}{2i\sigma} \frac{1}{\Delta_{ga} - i\sigma} \frac{1}{\Delta_{ba} - i\sigma}\\
+			&= \frac{\eta_{ijkl}}{\left(\Delta_{ga}-i\sigma\right)\left(\Delta_{ba}-i \sigma\right)}\\
 		\end{split}
@@
 \subsection{Correlated Modes}
-For correlated modes, the poles are situated in the complex plane as shown in \autoref{fig:contours}.
-It is clear that no matter which contour is chosen, there is a contribution to the final integral from either $\Delta_{ba}(0)$ or $\Delta_{ga}(0)$. 
-For the below calculation, we choose to evaluate along the contour in the bottom half of the complex plane, i.e., the poles ($\xi_k$) are $-i\sigma, \Delta_{ga}$.
-We stress that since the integral is evaluated over $\mathbb{R}$ and there are no degenerate poles, the results below can be obtained by evaluating the contour which wraps around the poles $i\sigma, \Delta_{ba}$.
-Since the $\xi_k$ are nondegenerate,
+For correlated modes, the poles are situated in the complex plane as shown in \autoref{fig:contours}b.
+It is clear that no matter which contour is chosen, there is a contribution from either $\Delta_{ba}$ or $\Delta_{ga}$. 
+For the below calculation, we choose to evaluate along the contour in the bottom half of the complex plane, i.e., the poles are $\{-i\sigma, \Delta_{ga}\}$.
+We stress that since the integral is evaluated over $\mathbb{R}$ and there are no degenerate poles, the results below can \textit{also} be obtained by evaluating the contour which wraps around the poles $\{i\sigma, -\Delta_{ba}\}$.
+Nevertheless, we choose the contour as drawn in \autoref{fig:contours}b.
+Since the $\xi_k$ are nondegenerate, we see
 \begin{widetext}
@@
 			\int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi) &= 2\pi i \sum_k \lim_{\xi \rightarrow \xi_k} P(\xi) \gamma_{ijkl}(\xi) (\xi - \xi_k)\\
-			&= 2\pi i \frac{\gamma_0 \sigma}{\pi}  \lim_{\xi \rightarrow -i\sigma} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga}(0) - \xi} \frac{1}{\Delta_{ba}(0) - \xi} (\xi + i \sigma) \\ 
-			&+ 2\pi i \frac{\gamma_0 \sigma}{\pi} \lim_{\xi \rightarrow \Delta_{ga}(0)} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga}(0) - \xi} \frac{1}{\Delta_{ba}(0) - \xi} (\xi - \Delta_{ga})\\
-			&= 2 \gamma_0 i \sigma (\frac{1}{2 i \sigma} \frac{1}{-i \sigma - \Delta_{ga}(0)} \frac{1}{\Delta_{ba}(0) - i\sigma} ) - 2 \gamma_0 i \sigma (\frac{1}{\sigma^2 + (\Delta_{ga} (0))^2} \frac{1}{\Delta_{ga}(0) + \Delta_{ba}(0)} )\\
-			&= -\frac{\gamma_0}{\Delta_{ga}(0) + i \sigma} (\frac{1}{\Delta_{ba}(0) - i \sigma} + \frac{2i\sigma}{(\Delta_{ga}(0) - i \sigma)(\Delta_{ga}(0) + \Delta_{ba}(0))})\\
+			&= 2\pi i \frac{\eta_{ijkl} \sigma}{\pi}  \lim_{\xi \rightarrow -i\sigma} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga} + \xi} \frac{1}{\Delta_{ba} - \xi} \left(\xi + i \sigma\right) \\
+			&+ 2\pi i \frac{\eta_{ijkl} \sigma}{\pi} \lim_{\xi \rightarrow \Delta_{ga}} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga} - \xi} \frac{1}{\Delta_{ba} - \xi} \left(\xi - \Delta_{ga}\right)\\
+			&= 2 \eta_{ijkl} i \sigma \left(\frac{1}{2 i \sigma} \frac{1}{-i \sigma - \Delta_{ga}} \frac{1}{\Delta_{ba} - i\sigma} \right) - 2\eta_{ijkl} i \sigma \left(\frac{1}{\sigma^2 + \Delta_{ga} ^2} \frac{1}{\Delta_{ga} + \Delta_{ba}} \right)\\
+			&= -\frac{\eta_{ijkl}}{\Delta_{ga} + i \sigma} \left(\frac{1}{\Delta_{ba} - i \sigma} + \frac{2i\sigma}{(\Delta_{ga} - i \sigma)(\Delta_{ga} + \Delta_{ba})}\right)\\
 		\end{split}

### 2024-09-17 figures/2D_spec.py

@@ -64,10 +64,11 @@ jgs = [0.6, 1.0, 1.29965]
 jes = [1.3, 1.7, 1.9965]
 
 for i in [0,1,2]:
+    kets = [r'$\mathsf{|0\rangle}$', r'$\mathsf{|1\rangle}$', r'$\mathsf{|2\rangle}$']
     ax0.hlines(y = grs(jgs[i]), xmin = -jgs[i], xmax = jgs[i], color = 'black', linestyle = '-', linewidth = 2) #gs states
     ax0.hlines(y = es(jes[i]), xmin = -jes[i]+2*d, xmax = jes[i], color = 'black', linestyle = '-', linewidth = 2) #es states
-    ax0.text(jgs[i] + 0.25, grs(jgs[i])-0.03, str(i), fontsize = 16) #labeling gs
-    ax0.text(jes[i] + 0.25, es(jes[i])-0.03, str(i), fontsize = 16) #labeling es
+    ax0.text(jgs[i] + 0.25, grs(jgs[i])-0.03, kets[i], fontsize = 16) #labeling gs
+    ax0.text(jes[i] + 0.25, es(jes[i])-0.03, kets[i], fontsize = 16) #labeling es
 # for i in [0,1,2]:
 
     
@@ -194,6 +195,12 @@ ax1.plot(y, np.abs(B1+B2) / abs_max, linewidth = '2', label = r'$\mathsf{|B|}$',
 ax1.plot(y, np.abs(B1) / abs_max, linewidth = '2', label = r'$\mathsf{|B_1|}$', color = 'orange', zorder = 2)
 ax1.plot(y, np.abs(B2) / abs_max, linewidth = '2', label = r'$\mathsf{|B_2|}$', color = 'green', zorder = 1)
 
+# ax1.plot(y, tot / tot.max(), linewidth = '2', label = r'$\mathsf{|A + B|}$', color = 'black', zorder = 4)
+# ax1.plot(y, np.abs(A) / abs_max, linewidth = '2', label = r'$\mathsf{|A|}$', zorder = 3)
+# ax1.plot(y, np.abs(B1+B2) / abs_max, linewidth = '2', label = r'$\mathsf{|B|}$', zorder = 3)
+# ax1.plot(y, np.abs(B1) / abs_max, linewidth = '2', label = r'$\mathsf{|B_1|}$', zorder = 2)
+# ax1.plot(y, np.abs(B2) / abs_max, linewidth = '2', label = r'$\mathsf{|B_2|}$', zorder = 1)
+
[…]

### 2024-09-17 figures/contours.py

@@ -1,0 +1,82 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Tue Jan 17 09:28:39 2023
+
+@author: rpm
+"""
+import numpy as np
+import WrightTools as wt
+import matplotlib.pyplot as plt 
+
+wt.artists.apply_rcparams(kind="publication")
+
+save = False
+fontsize = 18
+
+r = 5 #radius of contour
+
+def bottomcontour(k):
+    return -1*np.sqrt(r**2 - k**2) 
+
+def topcontour(k):
+    return np.sqrt(r**2 - k**2) 
+
+x = np.linspace(-r, r, 50000)
+
+#make figure
+cols = [1, 1] 
+aspects = [[[0, 0], 1], [[1, 0], 1]] 
+
+fig, gs = wt.artists.create_figure(width="dissertation", nrows=1, cols=cols, aspects=aspects, hspace=0.7, wspace=1.2) 
+
+###Anti-correlated modes###
+ax0 = plt.subplot(gs[0,0]) 
+
+#insert the poles
+poles = [2, -2, -2.6, -3.5]
+points = [0, 0, 2, 3]
+
+
+#plot it
+ax0.plot(x, topcontour(x), linewidth = '2', color = 'black')
+for i in [0,1,2,3]:
+    ax0.scatter(points[i], poles[i], color = 'blue')
+    label = [r'$\mathsf{i \sigma}$', r'$\mathsf{-i \sigma}$', r'$\mathsf{\Delta_{ga}}$', r'$\mathsf{\Delta_{ba}}$']
+    ax0.text(points[i]+0.1, poles[i]+0.1, label[i], fontsize = 24)
+
+
+###Correlated modes###
+ax1 = plt.subplot(gs[0,1]) 
+
+#insert the poles
+poles = [2, -2, -2.6, 3.5]
+points = [0, 0, 2, 3]
+
+
+#plot it
+for i in [0,1,2,3]:
+    ax1.scatter(points[i], poles[i], color = 'blue')
+    label = [r'$\mathsf{i \sigma}$', r'$\mathsf{-i \sigma}$', r'$\mathsf{\Delta_{ga}}$', r'$\mathsf{-\Delta_{ba}}$']
+    ax1.text(points[i]+0.1, poles[i]+0.1, label[i], fontsize = 24)
+ax0.set_title('Anti-Correlated (c = -1)')
+
+ax1.plot(x,bottomcontour(x), linewidth = '2', color = 'black')
[…]

### 2024-09-17 si.tex
more edits

@@
 is evaluated using Contour integration.
-\begin{figure}[!htbp]
-	\centering
-	\includegraphics[width=6.675in]{figures/corr_contour.png}
-	\caption{Poles (blue dots) and contours (black line) used to evaluate \autoref{generalcontour} for (a) anti-correlated and (b) correlated modes.} 
-	\label{fig:contours}
-\end{figure}
+
 \subsection{Anti-correlated Modes}
@@
 For the below calculation, we choose to evaluate along the contour in the bottom half of the complex plane, i.e., the poles are $\{-i\sigma, \Delta_{ga}\}$.
-We stress that since the integral is evaluated over $\mathbb{R}$ and there are no degenerate poles, the results below can \textit{also} be obtained by evaluating the contour which wraps around the poles $\{i\sigma, -\Delta_{ba}\}$.
+We stress that since the integral is evaluated over $\mathbb{R}$ and there are no degenerate poles, the results below can \textit{also} be obtained by the contour that wraps around the poles $\{i\sigma, -\Delta_{ba}\}$.
 Nevertheless, we choose the contour as drawn in \autoref{fig:contours}b.
@@
 
+\begin{figure}[!htbp]
+	\centering
+	\includegraphics[width=6.675in]{figures/corr_contour.png}
+	\caption{Poles (blue dots) and contours (black line) used to evaluate \autoref{generalcontour} for (a) anti-correlated and (b) correlated modes.} 
+	\label{fig:contours}
+\end{figure}
+
 \section{References}

### 2024-09-17 figures/contours.py

@@ -76,7 +76,7 @@ for ax in [ax0, ax1]:
     ax.set_yticks(ticks = [])
     ax.set_xticks(ticks = [])
 for i, ax in enumerate(fig.axes):
-    wt.artists.corner_text("abcd"[i], ax=ax, corner = 'UL', distance = 0.35, bbox = True, fontsize = fontsize, background_alpha=0.75)
+    wt.artists.corner_text("abcd"[i], ax=ax, corner = 'UL', distance = 0.2, bbox = True, fontsize = fontsize, background_alpha=0.75)
 
 if save:
     wt.artists.savefig("contour.png", transparent = True, bbox_inches='tight')

### 2024-09-18 paper.tex
edits

@@
 		The red box outlines the e-v coupling techniques (HDFG, HSFG) relevant to this manuscript.
-	} %TODO: Fix vsfg
+	} 
 	\label{fig:comparisonwmel}
@@
 	\caption{Contributions of $A, B$ (\autoref{ABterms_DR}) to HDFG spectrum for a simple two harmonic well system.
-		(a) Potential energy surfaces for a two-well system, (b) 1D HDFG spectrum for $\Delta = 0.5$, $\omega_1 = \omega_{g1, g0}$, (c,d) real and imaginary parts of terms plotted in (b), respectively.
-		All spectra are referenced to $\max{(A+B)}$. 
+		(a) Potential energy surfaces for a two-well system, (b) 1D HDFG spectrum for $\Delta = 0.5$, $\omega_1 = \omega_{g1, g0}$, (c, d) real and imaginary parts of terms plotted in (b), respectively.
+		The spectra are referenced to $\max{(A+B)}$. 
 		It is assumed that $\omega_2 = \omega_3$.
-		Note that (b) plots magnitudes of the labeled quantities.
-		The vibrational states on the $|g)$ and $|e)$ manifolds are spaced 1600 cm$^{-1}$ apart, with the vibronic states $\ket{e,\tilde{v}'}$ given linewidths of 400 cm$^{-1}$ and $\hbar \omega_{eg}$ = 30000 cm$^{-1}$.
+		The vibrational states on the $|g)$ and $|e)$ manifolds are spaced 1600 cm$^{-1}$ apart, with the vibronic states $\ket{e,\tilde{v}'}$ given linewidths of 300 cm$^{-1}$ and $\omega_{eg}$ = 30000 cm$^{-1}$.
 		Dotted lines in (b) denote the $\tilde{v}'$ = 0, 1, 2 vibronic resonances. 
@@
 
+Since $\Delta$ can take on a variety of values given a specific system, in the supporting information we demonstrate the impact of $\Delta$ on the HDFG response using previously reported values for some Raman active vibrations in \textit{trans}-hexatriene and UiO-68 metal organic frameworks (Figure S2).
+\cite{Myers1982, Brennan2024}
+Clearly, specific $\Delta$ and $\omega_{g1, g0}$ values have a significant impact on the HDFG spectral profile.
+Indeed, for some values of $\Delta$, it appears that $B$ term resonances dominate over $A$ term resonances, which can allow for significant non-Condon behavior in pre-resonant HDFG response.
+
 In the post-resonance region, the amplitude takes on an unexpected lineshape.
 This arises due to interference between the real and imaginary parts of $\gamma$ (\autoref{fig:doubres_spec}c, d).
-The abnormal lineshapes in both terms arises due to the sign of the Franck-Condon and Herzberg-Teller integrals that drive the output of the vibronic transitions for $\Delta = 0.5$ (\autoref{fcht}).
+The abnormal lineshapes in both terms arises due to the sign of the Franck-Condon and Herzberg-Teller integrals that drive the output of the vibronic transitions for $\Delta = 0.5$ (\autoref{fcht}), in turn driving significant interference in the overall $\abs{A+B}$ output.
 Such effects have been seen elsewhere in spontaneous, surface enhanced hyper-Raman studies. \cite{Milojevich2011}
-Since $\Delta$ can take on a variety of values given a specific system, in the supporting information we demonstrate the impact of $\Delta$ on the HDFG response using previously reported values for Raman active vibrations in isoprene.
-\cite{Myers1982}
-Clearly, specific $\Delta$ values have a significant impact on the
 
@@
 \section{Conclusions}\label{conclusion}
-\textbf{NEED TO READ THIS SECTION!}
-
 Coherent vibrational, hyper-Raman coherent four wave mixing spectroscopies are identified and discussed.
@@
 \section{Supplemental Information}
-See the supporting information for details on deriving closed-form solutions to Herzberg-Teller integrals, dependence of the HDFG spectrum on $\Delta$, and integration of \autoref{contour}.
+See the supporting information for details on deriving closed-form solutions to Herzberg-Teller integrals, HDFG spectrum dependence on $\Delta$, and evaluation of \autoref{contour}.
 

### 2024-09-18 si.tex
edits

@@
 We begin by generating an expression for $\mel{\tilde{n}}{q^k}{m}$, as this will resolve into Franck-Condon factors for $k = 0$ and Herzberg-Teller integrals for $k=1$.
+The relevant Franck-Condon factors and Herzberg-Teller integrals, assuming identical curvature and no Duschinsky coupling, are plotted in \autoref{fig:fcht} as a function of offset, $\Delta$.
 As in the main text, $\{\ket{\tilde{a}}\}$ are vibrational states on the first excited state $|e)$ and $\{\ket{b}\}$ are vibrational states on the ground state $|g)$.
+
+\begin{figure}[!htbp]
+	\centering
+	\includegraphics[width=6.675in]{figures/fcht.png}
+	\caption{Plots of select (a) Franck-Condon factors and (b) Herzberg-Teller integrals relevant to this manuscript as a function of offset, $\Delta$.} 
+	\label{fig:fcht}
+\end{figure}
 
@@
 
+\begin{figure}[!htbp]
+	\centering
+	\includegraphics[width=6.675in]{figures/changedelta.png}
+	\caption{The impact of offset, vibrational resonance, and linewidth on HDFG spectra.
+Parameters for (a,b) follow from Myers et al., whereas parameters for (c,d) follow from Brennan et al.\cite{Myers1982, Brennan2024}}
+	\label{fig:chgdelta}
+\end{figure}
+
 \section{Impact of $\Delta$ on $A,B$ Terms in HDFG Spectra}
@@
 Here, we vary $\Delta$ to investigate its impact on the structure of the $\abs{A+B}$ spectrum.
-The relevant Franck-Condon factors and Herzberg-Teller integrals, assuming identical curvature and no Duschinsky coupling, are plotted in \autoref{fig:fcht} as a function of offset, $\Delta$.
-
-\begin{figure}[!htbp]
-	\centering
-	\includegraphics[width=6.675in]{figures/fcht.png}
-	\caption{Plots of select (a) Franck-Condon factors and (b) Herzberg-Teller integrals relevant to this manuscript as a function of offset, $\Delta$.} 
-	\label{fig:fcht}
-\end{figure}
 
 It is clear from \autoref{fig:fcht} that the HDFG spectrum will have a significant dependence upon $\Delta$, even for small deviations from complete overlap. 
-To this end, we first investigate the impact of $\Delta$ on a vibrational mode with a fundamental frequency 1600 cm$^{-1}$ and linewidth of 400 cm$^{-1}$ (\autoref{fig:chgdelta}).
+To this end, we plot the impact of resonance frequency and offset on the HDFG spectrum \autoref{fig:chgdelta}, using values reported by Myers et al. and Brennan et al. \cite{Myers1982, Brennan2024}
+In this section, we take $\omega_{eg}$ = $37340$ cm$^{-1}$ and vary the offset ($\Delta$), vibrational frequency ($\omega_{g1,g0}$), and linewidth ($\Gamma$) as noted in the figure.
 
-\begin{figure}[!htbp]
-	\centering
-	\includegraphics[width=6.675in]{figures/changedelta.png}
-	\caption{Plots of select (a) Franck-Condon factors and (b) Herzberg-Teller integrals relevant to this manuscript as a function of offset, $\Delta$.} 
-	\label{fig:chgdelta}
-\end{figure}
 \section{Evaluating impact of inhomogeneity on HDFG output}

### 2024-09-18 figures/2D_spec.py

@@ -205,10 +205,10 @@ ax1.set_ylabel(r'$\mathsf{Amplitude \ (norm.)}$', fontsize = fontsize)
 ax1.set_xlabel(r'$\mathsf{2\omega_2} \ (\mathsf{cm}^{-1})$', fontsize = fontsize)
 
 ax1.set_yscale('log')
-ax1.set_xlim(15000, 45000)
-xticks = np.linspace(15000, 45000, 7)
+ax1.set_xlim(20000, 45000)
+xticks = np.linspace(20000, 45000, 6)
 ax1.set_xticks(xticks)
-ax1.set_ylim(0.0007, 3)
+ax1.set_ylim(0.001, 2)
 ax1.legend(loc = 1)
 
 
@@ -225,11 +225,11 @@ if others:
     ax2.plot(y, BRe, linewidth = '2', label = r'$\mathsf{B}$', color = 'red', zorder = 3)
     ax2.plot(y, B1Re, linewidth = '2', label = r'$\mathsf{B_1}$', color = 'orange', zorder = 2)
     ax2.plot(y, B2Re, linewidth = '2', label = r'$\mathsf{B_2}$', color = 'green', zorder = 1)
-    ax2.set_ylabel(r'$\mathsf{Re(\gamma) \ (norm.)}$', fontsize = fontsize)
+    ax2.set_ylabel(r'$\mathsf{Re(\gamma)}$', fontsize = fontsize)
     ax2.set_xlabel(r'$\mathsf{2\omega_2} \ (\mathsf{cm}^{-1})$', fontsize = fontsize)
     
     #ax2.set_yscale('log')
-    ax2.set_xlim(15000, 45000)
+    ax2.set_xlim(20000, 45000)
     # ax2.set_ylim(0.001, 2.2)
     ax2.legend(loc = 1)
     
@@ -240,24 +240,24 @@ if others:
     ax3.plot(y, BIm, linewidth = '2', label = r'$\mathsf{B}$', color = 'red', zorder = 3)
     ax3.plot(y, B1Im, linewidth = '2', label = r'$\mathsf{B_1}$', color = 'orange', zorder = 2)
     ax3.plot(y, B2Im, linewidth = '2', label = r'$\mathsf{B_2}$', color = 'green', zorder = 1)
-    ax3.set_ylabel(r'$\mathsf{Im(\gamma) \ (norm.)}$', fontsize = fontsize)
+    ax3.set_ylabel(r'$\mathsf{Im(\gamma)}$', fontsize = fontsize)
[…]

### 2024-09-18 figures/2D_spec_nonorm.py

@@ -1,258 +1,0 @@
-# -*- coding: utf-8 -*-
-"""
-Created on Tue Jan 17 09:28:39 2023
-
-@author: rpm
-"""
-import numpy as np
-import WrightTools as wt
-import matplotlib.pyplot as plt 
-from matplotlib.patches import FancyArrowPatch
-
-wt.artists.apply_rcparams(kind="publication")
-
-save = False
-fontsize = 18
-
-#define harmonic wells and coordinates
-d = 0.5 #offset for es
-do = 0 #gs placement
-
-def grs(k):
-    return 0.125*(k-do)**2 #arbitrary curvature
-
-def es(k):
-    return 0.125*(k-d-do)**2 + 0.7 #arbitrary curvature and vertical offset
-
-kg = np.linspace(-2, 2, 500) #ground state coordinates
-ke = np.linspace(-1.75, 2.75, 500) #excited state coordinates
-
-#make figure
-cols = [1, 1] 
-aspects = [[[0, 0], 1], [[1, 0], 1]] 
-
-fig, gs = wt.artists.create_figure(width="dissertation", nrows=2, cols=cols, aspects=aspects, hspace=0.7, wspace=1.2) 
-
-ax0 = plt.subplot(gs[0,0])
-
-#hbar omega_eg arrow insert
-yarrow = [grs(0.6), es(1.3)] #where the arrows start and end
-yarrowstop = [(grs(0.6) + es(1.3))/2 - 0.06, (grs(0.6) + es(1.3))/2 + 0.06] #to put in the hbaromegaeg
-myArrow0 = FancyArrowPatch(posA=(-0.35, yarrow[0]), posB=(-0.35, yarrowstop[0]), arrowstyle='<|-', color='blue',
-                           mutation_scale=25, shrinkA=0, shrinkB=0, linewidth = 4)
-myArrow1 = FancyArrowPatch(posA=(-0.35, yarrowstop[1]), posB=(-0.35, yarrow[1]), arrowstyle='-|>', color='blue', 
-                           mutation_scale=25, shrinkA=0, shrinkB=0, linewidth = 4)
-ax0.add_artist(myArrow0)
-ax0.add_artist(myArrow1)
-
[…]

### 2024-09-18 figures/Varying_Delta_SI.py

@@ -14,9 +14,6 @@ wt.artists.apply_rcparams(kind="publication")
 save = False
 fontsize = 18
 
-#define harmonic wells and coordinates
-d = [0.1, 0.2, 0.6] #offset for es
-
 #make figure
 cols = [1, 1] 
 aspects = [[[0, 0], 1], [[1, 0], 1]] 
@@ -70,11 +67,11 @@ def h21(q): #<2|Q|1>
 def h20(q): #<2|Q|0>
     return -q/np.sqrt(2) * (1 - q**2 /4) * f00(q)
 
+
 #define resonance denominator
-def Deltaevgo(v,x,l):
-    weg = 30000
-    G = [400, 400, 400] #linewidths
-    return 1/(weg + 1600*v - x - 1j*G[l]) #assuming the |0> -> |n> transiton is 2200*n  cm^-1
+def Deltaevgo(n,x,l,G):
+    weg = 37430
+    return 1/(weg + l*n - x - 1j*G) #assuming the |0> -> |n> transiton is l*n  cm^-1
 
 
 #define numbers for AB terms
@@ -85,139 +82,99 @@ dMgedQ = 0.007 #dM^eg / dQ
 
 
 #define terms
-y = np.linspace(10000, 50000, 3000000)
-# y = 31000
-
-# d = np.linspace(0, 1, 1000)
+y = np.linspace(17000, 57000, 3000000)
 
 
 
-def A(d):
-    return Mge * Lge * (f01(d)*f00(d)*Deltaevgo(0,y,0) + f11(d)*f10(d)*Deltaevgo(1,y,1) + f21(d)*f20(d)*Deltaevgo(2,y,2)) #there must be a simpler way to do this but idk
+def A(d, w, G):
+    return Mge * Lge * (f01(d)*f00(d)*Deltaevgo(0,y,w,G) + f11(d)*f10(d)*Deltaevgo(1,y,w,G) + f21(d)*f20(d)*Deltaevgo(2,y,w,G)) #there must be a simpler way to do this but idk
 
 #B1 terms
-def B1(d):
-    # B10 = Mge*f10(d) * (dLeg * h00(d)) * Deltaevgo(0, y, 0) #the v' = 0 term
-    # B11 = Mge*f11(d) * (dLeg* h10(d)) * Deltaevgo(1, y, 1) #the v' = 1 term
[…]

### 2024-09-18 figures/contours.py

@@ -50,7 +50,7 @@ ax1 = plt.subplot(gs[0,1])
 
 #insert the poles
 poles = [2, -2, -2.6, 3.5]
-points = [0, 0, 2, 3]
+points = [0, 0, 2, -3]
 
 
 #plot it

### 2024-09-18 figures/inhomo.py

@@ -1,273 +1,0 @@
-# -*- coding: utf-8 -*-
-"""
-Created on Tue Jan 17 09:28:39 2023
-
-@author: rpm
-"""
-import numpy as np
-import WrightTools as wt
-import matplotlib.pyplot as plt 
-from matplotlib.patches import FancyArrowPatch
-
-wt.artists.apply_rcparams(kind="publication")
-
-save = False
-fontsize = 18
-
-#define harmonic wells and coordinates
-d = 0.5 #offset for es
-do = 0 #gs placement
-
-def grs(k):
-    return 0.125*(k-do)**2 #arbitrary curvature
-
-def es(k):
-    return 0.125*(k-d-do)**2 + 0.7 #arbitrary curvature and vertical offset
-
-kg = np.linspace(-2, 2, 500) #ground state coordinates
-ke = np.linspace(-1.75, 2.75, 500) #excited state coordinates
-
-#make figure
-cols = [1, 1] 
-aspects = [[[0, 0], 1], [[1, 0], 1]] 
-
-fig, gs = wt.artists.create_figure(width="dissertation", nrows=2, cols=cols, aspects=aspects, hspace=0.7, wspace=1.2) 
-
-ax0 = plt.subplot(gs[0,0])
-
-#hbar omega_eg arrow insert
-yarrow = [grs(0.6), es(1.3)] #where the arrows start and end
-yarrowstop = [(grs(0.6) + es(1.3))/2 - 0.06, (grs(0.6) + es(1.3))/2 + 0.06] #to put in the hbaromegaeg
-myArrow0 = FancyArrowPatch(posA=(-0.35, yarrow[0]), posB=(-0.35, yarrowstop[0]), arrowstyle='<|-', color='blue',
-                           mutation_scale=25, shrinkA=0, shrinkB=0, linewidth = 4)
-myArrow1 = FancyArrowPatch(posA=(-0.35, yarrowstop[1]), posB=(-0.35, yarrow[1]), arrowstyle='-|>', color='blue', 
-                           mutation_scale=25, shrinkA=0, shrinkB=0, linewidth = 4)
-ax0.add_artist(myArrow0)
-ax0.add_artist(myArrow1)
-
[…]

### 2024-09-18 figures/plotting_fcht.py

@@ -79,7 +79,6 @@ ax0.plot(d, f11(d), linewidth = '2', label = r'$\mathsf{\langle\tilde{1}|1\rangl
 # ax0.plot(d, f02(d), linewidth = '2', label = r'$\mathsf{02}$', color = 'green', zorder = 1)
 ax0.plot(d, f20(d), linewidth = '2', label = r'$\mathsf{\langle\tilde{2}|0\rangle}$', color = 'orange', zorder = 1)
 ax0.plot(d, f21(d), linewidth = '2', label = r'$\mathsf{\langle\tilde{2}|1\rangle}$', color = 'green', zorder = 1)
-ax0.set_ylabel(r'$\mathsf{Integral \ Value \ (arb.)}$', fontsize = fontsize)
 
 # ax0.text(20000, 2, r'$\mathsf{\Delta = 1/\sqrt{2}}$', fontsize = 16)
 
@@ -97,6 +96,7 @@ ax1.plot(d, h21(d), linewidth = '2', label = r'$\mathsf{\langle\tilde{2}|q|1\ran
 
 for ax in [ax0, ax1]:
     # ax.set_yscale('log')
+    ax.set_ylabel(r'$\mathsf{Integral \ Value \ (arb.)}$', fontsize = fontsize)
     ax.set_xlim(-2,2)
     ax.set_xlabel(r'$\mathsf{\Delta}$', fontsize = fontsize)
     # xticks = np.linspace(15000, 45000, 7)

### 2024-09-18 figures/workup.py

@@ -1,129 +1,0 @@
-# -*- coding: utf-8 -*-
-"""
-Created on Tue Feb 20 14:40:11 2024
-
-@author: rpm
-"""
-
-import WrightTools as wt
-import pathlib
-import matplotlib.pyplot as plt
-import numpy as np
-import pandas as pd
-
-plt.rcParams.update({
-"text.usetex": True,
-"font.family": "mathptmx"
-})
-plt.rcParams['figure.dpi'] = 800
-
-here = pathlib.Path(__file__).resolve().parent
-# here = here.parent
-
-data_dir = here.parent / "data" 
-
-dir0 = data_dir / "2024-04-04 39092 grid_scan_wp cobalamin_thin_transmission_wig c38ec440"
-dir1 = data_dir / "2024-04-04 37050 grid_scan_wp cobalamin_thin_transmission_wig_TSF ef139d32"
-
-data0  = wt.open(dir0/'primary.wt5')
-data1  = wt.open(dir1/'primary.wt5')
-
-for data in [data0, data1]:
-    data.create_channel(name = 'normalized', values = data.daq_w1pr[:]/data.daq_pyro_1[:] /data.daq_pyro_3[:])
-    data.smooth(2, channel = 'normalized')
-    channel = data.normalized
-    data.transform('w1_points', 'D1_points')
-    split = True
-if split:
-        data0 = data0.split('w1_points', [1300,1700], units = 'wn')[1]
-        data1 = data1.split('w1_points', [1300,1700], units = 'wn')[1]
-        for data in [data0, data1]:
-            channel = data.normalized
-            channel.normalize()
-# else: channel.normalize()
-
-##ftir from pandas
-spectrum = pd.read_excel(data_dir / "cobir.xlsx")
-d2 = wt.Data(name = 'ftir')
-d2.create_variable(name = 'energy', units = 'wn', values = spectrum.energy.to_numpy())
-d2.create_channel(name = 'signal', values = spectrum.intensity.to_numpy())
-    
-
-
-
-#plot
-cols = [1, 1, "cbar"] 
-aspects = [[[0, 0], 0.2], [[1, 0], 0.9]] 
-
[…]

### 2024-09-18 figures/toc.py
added toc image

@@ -1,0 +1,29 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Jul  8 10:53:49 2024
+
+@author: rpm
+"""
+
+import matplotlib.pyplot as plt 
+from WrightTools.diagrams import WMEL
+
+fig = WMEL.Artist([2,1], [0, 0.2, 0.6, 1], state_names=("$\mathsf{| g, 0\\rangle}$",
+                                                                   "$\mathsf{|g, v\\rangle}$", 
+                                                                   "$\mathsf{|m, n\\rangle}$",
+                                                                   "$\mathsf{|e, \\tilde{v}'\\rangle}$"), number_of_interactions=5, state_font_size=9, state_text_buffer = 0.6, virtual = [2])
+
+fig.add_arrow([0,0], 0, [0,1], kind='bra', color="k", label = "$\mathsf{1}$", head_length = 0.075)
+fig.add_arrow([0,0], 1, [0,2], kind='ket', color="k", label = "$\mathsf{2}$", head_length = 0.075)
+fig.add_arrow([0,0], 2, [2,3], kind='ket', color="k", label = "$\mathsf{3}$", head_length = 0.075)
+fig.add_arrow([0,0], 3, [3,1], kind='out', color="blue", label = "$\mathsf{4}$", head_length = 0.075)
+
+fig.add_arrow([1,0], 0, [0,1], kind='ket', color="k", label = "$\mathsf{1}$", head_length = 0.075)
+fig.add_arrow([1,0], 1, [1,2], kind='ket', color="k", label = "$\mathsf{2}$", head_length = 0.075)
+fig.add_arrow([1,0], 2, [2,3], kind='ket', color="k", label = "$\mathsf{3}$", head_length = 0.075)
+fig.add_arrow([1,0], 3, [3,0], kind='out', color="blue", label = "$\mathsf{4}$", head_length = 0.075)
+
+fig.label_columns(['$\mathsf{HDFG}$', '$\mathsf{HSFG}$'], font_size = 9)
+
+plt.savefig("toc.png", bbox_inches='tight')
+

### 2024-09-18 figures/wmels.py

@@ -99,7 +99,7 @@ if timeorderedwmel:
 
     fig.label_columns(['$(\mathsf{a})$','$(\mathsf{b})$', '$(\mathsf{c})$', '$(\mathsf{d})$'], font_size = 9)
     
-    plt.savefig("timeorderedwmel.png", bbox_inches='tight')
+    plt.savefig("timeorderedwmel1.png", bbox_inches='tight')
     
 if drwmel:
     fig = WMEL.Artist([2,2], [0, 0.2, 0.5, 0.8, 1], state_names=("$\mathsf{|g, 0\\rangle}$",

### 2024-09-20 si.tex
revise SI

@@
 \section{Evaluating Herzberg-Teller Integrals for Harmonic Wells of Identical Curvature}
-In this section, we discuss the evaluation of Herzberg-Teller integrals, in the limit of no Duschinsky coupling, when the ground and first excited state are harmonic wells of identical curvature.\cite{HerzbergTeller1933, Duschinsky1937}
+In this section, we discuss the evaluation of Herzberg-Teller integrals when the ground and first excited state are harmonic wells of identical curvature.\cite{HerzbergTeller1933}
+% We note that Myers et al. have developed a general expression to evaluate Franck-Condon factors for two displaced harmonic wells of differing curvature,\cite{Myers1982} 
 We investigate the one dimensional case using the Hamiltonian described in the main text, $H = H_g |g) \left(g| + H_e |e\right) (e|$, where
@@
 Here, $p,q$ are the dimensionless conjugate normal mode coordinates, $\hbar\omega_{eg}$ is the energy difference between $H_e$ and $H_g$, and $\Delta$ is the dimensionless offset of the excited state surface relative to the ground state.
-Franck-Condon factors and Herzberg-Teller integrals are often evaluated in position space using known solutions to the Harmonic Oscillator Hamiltonian, 
+The Hamiltonians are the well-known quantum harmonic oscillator, and their solutions are
 \begin{equation}
-	\psi_m(q) = \langle q | m \rangle = N(m) H_m(q) \exp(-q^2/2),
+	\psi_m(q) = \langle q | m \rangle = N_m H_m(q) \exp(-q^2/2),
 \end{equation}
-where $N(m) = (m! \ 2^m \pi^{\frac{1}{2}})^{-\frac{1}{2}}$ is the normalization factor and $H_m$ is the m$^{th}$ Hermite Polynomial.\cite{RN230}
-We begin by generating an expression for $\mel{\tilde{n}}{q^k}{m}$, as this will resolve into Franck-Condon factors for $k = 0$ and Herzberg-Teller integrals for $k=1$.
-The relevant Franck-Condon factors and Herzberg-Teller integrals, assuming identical curvature and no Duschinsky coupling, are plotted in \autoref{fig:fcht} as a function of offset, $\Delta$.
-As in the main text, $\{\ket{\tilde{a}}\}$ are vibrational states on the first excited state $|e)$ and $\{\ket{b}\}$ are vibrational states on the ground state $|g)$.
+where $N_m = (m! \ 2^m \pi^{\frac{1}{2}})^{-\frac{1}{2}}$ is the normalization factor and $H_m$ is the $m^{th}$ Hermite Polynomial.\cite{RN230}
 
-\begin{figure}[!htbp]
-	\centering
-	\includegraphics[width=6.675in]{figures/fcht.png}
-	\caption{Plots of select (a) Franck-Condon factors and (b) Herzberg-Teller integrals relevant to this manuscript as a function of offset, $\Delta$.} 
-	\label{fig:fcht}
-\end{figure}
-
-By letting $\ket{m}$ belong to the ground state surface $|g)$ and $\ket{\tilde{n}}$ belong to the first excited surface $|e)$, we write
+For an $n$-quantum excited state vibration $| \tilde{n} \rangle$, and a $m$-quantum ground state vibration $| \tilde{m} \rangle$, the $k^{th}$-order vibrational coupling term is
 \begin{equation}
 	\begin{split}
-		\mel{\tilde{n}}{q^k}{m} &= \int_{-\infty}^\infty \mathrm{d}q \psi^*_n(q-\Delta) q^k \psi_m(q)\\
-		&= \int_{-\infty}^\infty \mathrm{d}q N(n) N(m) H_n(q-\Delta) \exp(-\frac{(q - \Delta)^2}{2}) q^k H_m(q) \exp(-\frac{q^2}{2}),
-\end{split}
+			\mel{\tilde{n}}{q^k}{m} &= \int_{-\infty}^\infty \mathrm{d}q \ \psi^*_n(q-\Delta) q^k \psi_m(q)\\
+			&= \int_{-\infty}^\infty \mathrm{d}q \ N_n H_n(q-\Delta) \exp(-\frac{(q - \Delta)^2}{2}) q^k N_m H_m(q) \exp(-\frac{q^2}{2}). \\
+			&= N_n N_m \exp(-\frac{\Delta^2}{2}) \int_{-\infty}^\infty \mathrm{d}q \ H_n(q-\Delta) q^k H_m(q) \exp(-q^2 + q\Delta)
+		\end{split}\label{key}
 \end{equation}
-where $k=0$ corresponds to a Franck-Condon factor and $k=1$ refers to a Herzberg-Teller integral.
-Introducing $\tilde{N} \equiv N(n)N(m)$ and slightly rearranging, we see
-\begin{equation}\label{key}
-	\mel{\tilde{n}}{q^k}{m} = \tilde{N} \exp(-\frac{\Delta^2}{2}) \int_{-\infty}^\infty \mathrm{d}q H_n(q-\Delta) q^k H_m(q) \exp(-q^2 + q\Delta)
-\end{equation}
-This is the key result.
-While integrals of form \autoref{key} can be computed straightforwardly using mathematical packages such as \texttt{Mathematica} or \texttt{SymPy}, \cite{Mathematica, sympy} it is a useful exercise in Gaussian integral manipulation to evaluate Herzberg-Teller or Franck-Condon integrals.
-As a side note, \autoref{key} explicitly shows
-\begin{subequations}
-	\begin{equation}
-		\lim_{\Delta \rightarrow 0} \langle \tilde{n} | m \rangle = \langle n | m \rangle = \delta_{n,m}
-	\end{equation}
-and
-	\begin{equation}
-	\lim_{\Delta \rightarrow 0} \mel{\tilde{n}}{q}{m} = \mel{{n}}{q}{m} = \sqrt{\frac{1}{2}} \left(\sqrt{m}\delta_{n,m-1} + \sqrt{m+1} \delta_{n,m+1}\right)
-	\end{equation}
-\end{subequations}
-i.e., as the offset vanishes, the normal harmonic oscillator selection rules are obtained, the expected result, where $\delta$ is the Kronecher delta.
+The integral corresponds to Franck-Condon matrix elements for $k=0$ and Herzberg-Teller matrix elements for $k=1$.
 
-It is well known that the Hermite polynomials $H_v(q)$ are linear combinations of $q^w$, $w \in \mathbf{N}$. 
-Thus, evaluating \autoref{key} for arbitrary $m,n,k$ values resolves into evaluating sums of integrals of the form
+The matrix elements of \autoref{key} can be computed numerically, but analytic forms of the integral also exist. 
+Due to the polynomial nature of $H_v(q)$, evaluation of \autoref{key} reduces into evaluating sums of integrals of the form
 \begin{equation}\label{integral}
@@
 		\int_{-\infty}^\infty \mathrm{d}q \exp(-q^2 + q\Delta) &= \int_{-\infty}^\infty \mathrm{d}q \exp(-(q^2 - q\Delta +\frac{\Delta^2}{4} - \frac{\Delta^2}{4}))\\
-		&= \exp(\frac{\Delta^2}{4}) \int_{-\infty}^\infty \mathrm{d}q \exp(-(q - \frac{\Delta}{2})^2) \\
-		&= \sqrt{\pi} \exp(\frac{\Delta^2}{4})
+		&= \exp(-\frac{\Delta^2}{4}) \int_{-\infty}^\infty \mathrm{d}q \exp(-(q - \frac{\Delta}{2})^2) \\
+		&= \sqrt{\pi} \exp(-\frac{\Delta^2}{4})
 	\end{split}
@@
 We now have the background needed to calculate $\mel{\tilde{1}}{q}{0}$ for an arbitrary offset $\Delta$.
-We note that Myers et al.
-have developed a general expression to evaluate Franck-Condon factors for two displaced harmonic wells of arbitrary curvature,\cite{Myers1982} so we focus our attention onto Herzberg-Teller integrals, which are not commonly tabulated.
-Starting with \autoref{key},
-\begin{equation}
-\begin{split}
-	\mel{\tilde{1}}{q}{0} = \tilde{N} \exp(-\frac{\Delta^2}{2}) \int_{-\infty}^\infty \mathrm{d}q H_1(q-\Delta) q H_0(q) \exp(-q^2 + q\Delta)
-\end{split}
-\end{equation}
 Using $H_0(q) = 1$ and $H_1(q) = 2q$,
@@
 	\begin{split}
-		\mel{\tilde{1}}{q}{0} &= \tilde{N} \exp(-\frac{\Delta^2}{2}) \int_{-\infty}^\infty \mathrm{d}q \ 2(q - \Delta) q \exp(-q^2 + q\Delta)\\
-		&= 2\tilde{N} \exp(-\frac{\Delta^2}{2}) \int_{-\infty}^\infty \mathrm{d}q \ (q^2 - q \Delta) \exp(-q^2 + q\Delta)\\
-		&=  2\tilde{N} \exp(-\frac{\Delta^2}{2}) \left(\int_{-\infty}^\infty \mathrm{d}q \ q^2 \exp(-q^2 + q\Delta) - \Delta \int_{-\infty}^\infty \mathrm{d}q \ q \exp(-q^2 + q\Delta) \right)
+		\mel{\tilde{1}}{q}{0} &= N_1 N_0 \exp(-\frac{\Delta^2}{2}) \int_{-\infty}^\infty \mathrm{d}q \ 2(q - \Delta) q \exp(-q^2 + q\Delta)\\
+		&= 2N_1 N_0 \exp(-\frac{\Delta^2}{2}) \left( \int_{-\infty}^\infty \mathrm{d}q \ q^2 \exp(-q^2 + q\Delta) + \Delta \int_{-\infty}^\infty \mathrm{d}q \ q \exp(-q^2 + q\Delta) \right)
 	\end{split}
 \end{equation}
-These integrals are now easily evaluated using \autoref{identity}:
+Both integrals can be evaluated using \autoref{identity}:
 \begin{subequations}\label{evalGaussians}
@@
 	\end{equation}
-giving
 	\begin{equation}
@@
 \end{subequations}
-With $\tilde{N} = N(1)*N(0) = (1!
-\ 2^1 \pi^{\frac{1}{2}})^{-\frac{1}{2}} * (0!
-\ 2^0 \pi^{\frac{1}{2}})^{-\frac{1}{2}} = \sqrt{1/2\pi}$ and substituting the results of \autoref{evalGaussians} into \autoref{HT10},
+Substituting the results of \autoref{evalGaussians} into \autoref{HT10}, 
 \begin{equation}
@@
 \end{equation}
-The evaluation of other Herzberg-Teller integrals follows a similar process.
+The evaluation of other Herzberg-Teller integrals is analogous.
+
+\pagebreak
+\section{Impact of displacement, resonance frequencies, and vibronic linewidth and on HDFG Spectra}
+\begin{figure}[!htbp]
+	\centering
+	\includegraphics[width=6.675in]{figures/fcht.png}
+	\caption{Plots of select (a) Franck-Condon factors and (b) Herzberg-Teller integrals relevant to this manuscript as a function of offset, $\Delta$.} 
+	\label{fig:fcht}
+\end{figure}
 
@@
 
-\section{Impact of $\Delta$ on $A,B$ Terms in HDFG Spectra}
+\pagebreak
+
 In the main text, the potential well offset ($\Delta$) was taken as $\Delta = 0.5$.
 Here, we vary $\Delta$ to investigate its impact on the structure of the $\abs{A+B}$ spectrum.
+The dependence of relevant Franck-Condon factors and Herzberg-Teller factors on displacement are plotted in \autoref{fig:fcht} as a function of offset, $\Delta$.
+\autoref{fig:fcht} shows how different displacements, vibrational frequencies, and vibronic linewidths will alter the vibronic spectrum.
 
@@
 In this section, we take $\omega_{eg}$ = $37340$ cm$^{-1}$ and vary the offset ($\Delta$), vibrational frequency ($\omega_{g1,g0}$), and linewidth ($\Gamma$) as noted in the figure.
+
+\pagebreak
 
@@
 \end{equation}
-is evaluated using Contour integration.
+is evaluated for $c=-1$ (electronic state and vibrational state energy fluctuations are anti-correlated) $c=1$ (electronic state and vibrational state energy fluctuations are correlated).
 
@@
 For correlated modes, the poles are situated in the complex plane as shown in \autoref{fig:contours}b.
-It is clear that no matter which contour is chosen, there is a contribution from either $\Delta_{ba}$ or $\Delta_{ga}$. 
-For the below calculation, we choose to evaluate along the contour in the bottom half of the complex plane, i.e., the poles are $\{-i\sigma, \Delta_{ga}\}$.
-We stress that since the integral is evaluated over $\mathbb{R}$ and there are no degenerate poles, the results below can \textit{also} be obtained by the contour that wraps around the poles $\{i\sigma, -\Delta_{ba}\}$.
-Nevertheless, we choose the contour as drawn in \autoref{fig:contours}b.
+It is clear that no matter which contour is chosen, the contour will envelop two poles.
+We choose to evaluate along the contour in the bottom half of the complex plane (see \autoref{fig:contours}b), where the poles are $\{-i\sigma, \Delta_{ga}\}$.
 Since the $\xi_k$ are nondegenerate, we see
@@
 \end{widetext}
-Generally, when starting from the ground state, non-parametric spectroscopies line-narrow correlated modes, and parametric spectroscopies line-narrow anti-correlated modes. \cite{Dick83_1, RN425}
 

### 2024-09-20 figures/Varying_Delta_SI.py
fig generation - absolute path save
make sure images save in correct directory

@@ -8,11 +8,13 @@ import numpy as np
 import WrightTools as wt
 import matplotlib.pyplot as plt 
 from matplotlib.patches import FancyArrowPatch
+import pathlib
 
 wt.artists.apply_rcparams(kind="publication")
 
-save = False
+save = True
 fontsize = 18
+here = pathlib.Path(__file__).resolve().parent
 
 #make figure
 cols = [1, 1] 
@@ -162,10 +164,6 @@ ax3.text(25000, 0.8, r'$\mathsf{\Delta = 0.135}$', fontsize = 16)
 ax3.text(25000, 0.4, r'$\mathsf{\omega_{g1,g0} = 1610 \ cm^{-1}}$', fontsize = 16)
 ax3.text(25000, 0.2, r'$\mathsf{\Gamma = 300 \ cm^{-1}}$', fontsize = 16)
 
-
-
-
-
 for ax in [ax0, ax1, ax2, ax3]:
     ax.set_yscale('log')
     ax.set_xlim(20000, 50000)
@@ -181,4 +179,4 @@ for i, ax in enumerate(fig.axes):
     wt.artists.corner_text("abcd"[i], ax=ax, corner = 'UL', distance = 0.35, bbox = True, fontsize = fontsize, background_alpha=0.75)
 
 if save:
-    wt.artists.savefig("changedelta.png", transparent = True, bbox_inches='tight')
+    wt.artists.savefig(here / "changedelta.png", transparent = True, bbox_inches='tight')

### 2024-09-20 paper.tex
added toc image

@@
 \subsection{Inhomogeneity in HDFG}
-An often unavoidable consequence in electronic spectroscopy is broadened lineshapes due to a high density of vibronic modes, i.e., inhomogeneous broadening.
+
+An often unavoidable consequence in electronic spectroscopy is broadened line shapes due to a high density of vibronic modes, i.e., inhomogeneous broadening.
 It is worthwhile to investigate the impact of inhomogeneity on HDFG response and the resultant lineshapes. 
-In the discussion that follows, we assume that a vibrational mode in the ground state, $\ket{g,v}$, is correlated to the frequency of a vibronic $\ket{e,\tilde{v}'}$.\cite{Carlson1990line, Dong2015}
+In the discussion that follows, we assume that a ground state vibrational frequency, $\ket{g,v}$, experiences variations that are correlated to the frequency of a vibronic $\ket{e,\tilde{v}'}$.
 If the frequency of $\ket{g,v}$ is written as $\omega_{gv} + \xi$, where $\xi$ is some external strain (e.g.
 molecular collisions), then the frequency of $\ket{e,\tilde{v}'}$ is $\omega_{e\tilde{v}'} + c\xi$, where c is a shift coefficient.
-When two modes are positively correlated, $c > 0$; similarly, modes are negatively correlated when $c < 0$.
-For simplicity, we assume c = $\pm$1.
+We assume the fluctuations controlling the frequency variations are slow (the static limit), so that homogeneous lineshapes are unaffected by this fluctuation. 
+When both states positively correlated, $c > 0$; similarly, modes are negatively correlated when $c < 0$.
+For simplicity, we consider only c = $\pm$1.
 
@@
 \begin{equation}\label{contour}
-	\gamma_{ijkl} = \int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi)
+	\gamma_{ijkl} = \int_{-\infty}^\infty \mathrm{d}\xi \ P(\xi) \gamma_{ijkl}(\xi)
 	= \frac{\sigma}{\pi}\int_{-\infty}^\infty \mathrm{d}\xi \frac{1}{\sigma^2 + \xi^2} \frac{\eta_{ijkl}}{\left(\Delta_{ga} - \xi\right)\left(\Delta_{ba}+ c\xi\right)}
@@
 where $\eta_{ijkl}$ contains all values in \autoref{drgamma_notaylor} not dependent upon $\xi$.
-The limit of static inhomogeneity is chosen for simplicity.
 While Gaussian distributions are commonly used as a phenomenological description of inhomogeneous broadening, Lorentzian distributions have successfully described inhomogeneous broadening in a variety of spectroscopies and yield easily interpretable closed-form solutions.
@@
 Evaluating \autoref{contour} for the HDFG pathway above shows\footnote{See the supporting information for more details}
-\begin{subequations}\label{linenarrow}
+
 \begin{equation}\label{linenarrowa}
@@
 \end{equation}
+	for correlated ($c = 1$) states and
 \begin{equation}
@@
 \end{equation}
-\end{subequations}
-for correlated ($c = 1$) and anti-correlated ($c = -1$) modes, respectively.
+for anti-correlated ($c = -1$) states.
 The output for correlated modes shows the presence of a new term, $\frac{2i\sigma}{\Delta_{ga} + \Delta_{ba}}$. 
@@
 
+\begin{figure*}[!htbp]
+	\centering
+	\includegraphics[width=6.66in]{toc.png}
+	\caption{
+		TOC Image.
+	} 
+	\label{fig:toc}
+\end{figure*}
+
 \end{document}

### 2024-09-22 si.tex
general solution

@@
 \section{Evaluating Herzberg-Teller Integrals for Harmonic Wells of Identical Curvature}
+
 In this section, we discuss the evaluation of Herzberg-Teller integrals when the ground and first excited state are harmonic wells of identical curvature.\cite{HerzbergTeller1933}
@@
 
+\subsection{General Solution to $\langle \tilde{n} | q^k | m \rangle$}
 The matrix elements of \autoref{key} can be computed numerically, but analytic forms of the integral also exist. 
-Due to the polynomial nature of $H_v(q)$, evaluation of \autoref{key} reduces into evaluating sums of integrals of the form
+Due to the polynomial nature of $H_v(q)$, the product $H_n(q-\Delta) q^k H_m(q)$ will also be a polynomial, so that the integral of equation \autoref{key} will be of the form
+\begin{eqnarray}
+	\int dq \ P_{nmk}(q) \exp(-q^2 + q\Delta), \\
+	P_{nmk}(q) \equiv \sum_\lambda^{n+m+k} a_\lambda q^\lambda
+\end{eqnarray}
+for some set coefficients $a_\lambda$, to be specified later. We can recast the integral into the linear combination of integrals,
+\begin{equation}\label{eq:analytic_form}
+	\mel{\tilde{n}}{q^k}{m} = N_n N_m \exp(-\frac{\Delta^2}{2}) \sum_\lambda a_\lambda F_\lambda(\Delta),
+\end{equation}
+where
 \begin{equation}\label{integral}
-	\int_{-\infty}^\infty \mathrm{d}q \ q^w \exp(-q^2 + q\Delta)
+	F_w(\Delta) \equiv \int_{-\infty}^\infty \mathrm{d}q \ q^w \exp(-q^2 + q\Delta).
 \end{equation}
-When $w=0$, the result follows by completing the square:\footnote{$\int_{-\infty}^{\infty} \mathrm{d}x \exp(-(x-a)^2) = \sqrt{\pi}$}
+\autoref{integral} can be readily evaluated, as we now show.
+When $w=0$, the integral is evaluated by completing the square:\footnote{$\int_{-\infty}^{\infty} \mathrm{d}x \exp(-(x-a)^2) = \sqrt{\pi}$}
 \begin{equation}
 	\begin{split}
-		\int_{-\infty}^\infty \mathrm{d}q \exp(-q^2 + q\Delta) &= \int_{-\infty}^\infty \mathrm{d}q \exp(-(q^2 - q\Delta +\frac{\Delta^2}{4} - \frac{\Delta^2}{4}))\\
-		&= \exp(-\frac{\Delta^2}{4}) \int_{-\infty}^\infty \mathrm{d}q \exp(-(q - \frac{\Delta}{2})^2) \\
-		&= \sqrt{\pi} \exp(-\frac{\Delta^2}{4})
+		F_0(\Delta) &= \int_{-\infty}^\infty \mathrm{d}q \exp(-(q^2 - q\Delta +\frac{\Delta^2}{4} - \frac{\Delta^2}{4}))\\
+		&= \exp(\frac{\Delta^2}{4}) \int_{-\infty}^\infty \mathrm{d}q \exp(-(q - \frac{\Delta}{2})^2) \\
+		&= \sqrt{\pi} \exp(\frac{\Delta^2}{4})
 	\end{split}
 \end{equation}
- For $w \neq 0$, \autoref{integral} is evaluated through repeated use of a well-known Gaussian identity
+For the general solution, \autoref{integral} is evaluated via repeated use of a well-known Gaussian identity
 \begin{equation}\label{identity}
-	\int_{-\infty}^\infty \mathrm{d}q \ q^w \exp(-q^2 + q\Delta) = \partial_{\Delta} \int_{-\infty}^\infty \mathrm{d}q \ q^{w-1} \exp(-q^2 + q\Delta)
+	\begin{split}
+		F_w(\Delta) &= \int_{-\infty}^\infty \mathrm{d}q \ q^w \exp(-q^2 + q\Delta) = \partial_{\Delta} \int_{-\infty}^\infty \mathrm{d}q \ q^{w-1} \exp(-q^2 + q\Delta) \\
+		&= \partial_\Delta F_{w-1}(\Delta)
+	\end{split}
+\end{equation}
+so we can write
+\begin{equation}\label{eq:F_solved}
+	\begin{split}
+		F_w(\Delta) &= \left(\partial_\Delta \right)^w F_0(\Delta) \\
+		&= \sqrt{\pi} \frac{\mathrm{d}^w}{\mathrm{d}\Delta^w} \exp(\frac{\Delta^2}{4}) \\
+		&= \sqrt{\pi} \left( -\frac{i}{2} \right)^w \exp(\frac{\Delta^2}{4}) H_w\left(i\frac{\Delta}{2}\right).
+	\end{split}
+\end{equation}
+In the last line we have used the generator definition of Hermite polynomials:  $H_n(x) \equiv (-1)^n e^{x^2} \frac{\mathrm{d}^n}{\mathrm{d}x^n} e^{-x^2}$.
+
+We now will evaluate the polynomial coefficients $P(q)$.
+The Hermite polynomials of \autoref{key} can be explicitly written as 
+\begin{equation}
+\begin{split}
+	H_m(q) &= \sum_{x=0}^{\left\lfloor{m/2}\right\rfloor} a_m^{(m-2x)} q^{m-2x} \\
+	H_n(q-\Delta) &= \sum_{x=0}^{\left\lfloor{n/2}\right\rfloor}
+	a_n^{(n-2x)} (q-\Delta)^{n-2x} \\
+		&= \sum_{x=0}^{\left\lfloor{n/2}\right\rfloor} a_n^{(n-2x)} \sum_{l=0}^{n-2x} \Delta^{n-2x-l} \binom{n-2x}{l} q^l
+\end{split}
+\end{equation}
+where $\left\lfloor n \right\rfloor$ denotes the \textit{floor} of $n$, $\binom{a}{b} = a! / (b!(a-b)!)$, and the Hermite coefficients are
+\begin{equation}
+	a_n^{(n-2x)} = n! \frac{(-1)^x 2^{n-2x}}{x!(n-2x)!}.
+\end{equation}
+Multiplying these terms together give us explicit polynomial coefficients:
+\begin{equation}\label{eq:poly_solved}
+\begin{split}
+	P_{nmk}(q) %&= \sum_{x=0}^{\left\lfloor{m/2}\right\rfloor} a_m^{(m-2x)} \sum_{y=0}^{\left\lfloor{n/2}\right\rfloor} a_n^{(n-2y)} \sum_{l=0}^{n-2y} \Delta^{n-2y-l} \binom{n-2y}{l} q^{l+m-2x+k} \\
+	&= \sum_{x=0}^{\left\lfloor{m/2}\right\rfloor} \sum_{y=0}^{\left\lfloor{n/2}\right\rfloor} \sum_{l=0}^{n-2y} c_{xyl} \ q^{l+m-2x+k}, \\
+	c_xyl &= a_m^{(m-2x)} a_n^{(n-2y)} \Delta^{n-2y-l} \binom{n-2y}{l}.
+\end{split}
+\end{equation}
+\autoref{eq:poly_solved} is not in standard polynomial form, because our summation is not singular and coefficients in our summation may have the same power. 
+Further simplifications can be made to sum to reduce recounting indices, but we do not find these simplifications essential.
+Regardless, substituting \autoref{eq:F_solved} and \autoref{eq:poly_solved} into \autoref{eq:analytic_form}, we can now evaluate the solution as:
+\begin{equation}\label{eq:general_solution}
+	\mel{\tilde{n}}{q^k}{m} = \sqrt{\pi} N_n N_m \exp(-\frac{\Delta^2}{4}) \sum_{x=0}^{\left\lfloor{m/2}\right\rfloor} \sum_{y=0}^{\left\lfloor{n/2}\right\rfloor} \sum_{l=0}^{n-2y} \left( -\frac{i}{2} \right)^{l+m-2x+k} c_{xyl} H_{l+m-2x+k}\left(i\frac{\Delta}{2}\right).
 \end{equation}
 
-We now have the background needed to calculate $\mel{\tilde{1}}{q}{0}$ for an arbitrary offset $\Delta$.
-Using $H_0(q) = 1$ and $H_1(q) = 2q$,
-\begin{equation}\label{HT10}
+\subsection{Evaluating Herzberg Teller terms for HDFG}
+
+\begin{equation}
 \begin{split}
-		\mel{\tilde{1}}{q}{0} &= N_1 N_0 \exp(-\frac{\Delta^2}{2}) \int_{-\infty}^\infty \mathrm{d}q \ 2(q - \Delta) q \exp(-q^2 + q\Delta)\\
-		&= 2N_1 N_0 \exp(-\frac{\Delta^2}{2}) \left( \int_{-\infty}^\infty \mathrm{d}q \ q^2 \exp(-q^2 + q\Delta) + \Delta \int_{-\infty}^\infty \mathrm{d}q \ q \exp(-q^2 + q\Delta) \right)
+	\langle n |q| 0 \rangle &= \cdots \\
 \end{split}
 \end{equation}
-Both integrals can be evaluated using \autoref{identity}:
-\begin{subequations}\label{evalGaussians}
+
 \begin{equation}
 	\begin{split}
-					\int_{-\infty}^\infty \mathrm{d}q \ q \exp(-q^2 + q\Delta) &= \partial_{\Delta} \left(\sqrt{\pi} \exp(\frac{\Delta^2}{4})\right)\\
-					& = \sqrt{\pi} \frac{\Delta}{2} \exp(\frac{\Delta^2}{4})
+		\langle n |q| 1 \rangle &= \cdots \\
 	\end{split}
 \end{equation}
-	\begin{equation}
-	\begin{split}
-		\int_{-\infty}^\infty \mathrm{d}q \ q^2 \exp(-q^2 + q\Delta) &= \partial_{\Delta} \left(\sqrt{\pi} \left(\frac{\Delta}{2} \exp(\frac{\Delta^2}{4})\right)\right)\\
-		& =\sqrt{\pi} \left(\frac{1}{2}\exp(\frac{\Delta^2}{4}) + \frac{\Delta^2}{4} \exp(\frac{\Delta^2}{4})\right)
-	\end{split}
-\end{equation}
-\end{subequations}
-Substituting the results of \autoref{evalGaussians} into \autoref{HT10}, 
-\begin{equation}
-	\mel{\tilde{1}}{q}{0} = \sqrt{\frac{1}{2}} (1 - \frac{\Delta^2}{2}) \exp(\frac{-\Delta^2}{4})
-\end{equation}
-The evaluation of other Herzberg-Teller integrals is analogous.
 
-\pagebreak
+% We now have the background needed to calculate $\langle \tilde{n} |q| m \rangle$.
+% % $\mel{\tilde{1}}{q}{0}$ for an arbitrary offset $\Delta$.
+% Using $H_0(q) = 1$ and $H_1(q) = 2q$,
+% \begin{equation}\label{HT10}
+% 	\begin{split}
+% 		\mel{\tilde{1}}{q}{0} &= N_1 N_0 \exp(-\frac{\Delta^2}{2}) \int_{-\infty}^\infty \mathrm{d}q \ 2(q - \Delta) q \exp(-q^2 + q\Delta)\\
+% 		&= 2N_1 N_0 \exp(-\frac{\Delta^2}{2}) \left( \int_{-\infty}^\infty \mathrm{d}q \ q^2 \exp(-q^2 + q\Delta) + \Delta \int_{-\infty}^\infty \mathrm{d}q \ q \exp(-q^2 + q\Delta) \right)
+% 	\end{split}
+% \end{equation}
+% Both integrals can be evaluated using \autoref{identity}:
+% \begin{subequations}\label{evalGaussians}
+% 	\begin{equation}
+% 		\begin{split}
+% 					\int_{-\infty}^\infty \mathrm{d}q \ q \exp(-q^2 + q\Delta) &= \partial_{\Delta} \left(\sqrt{\pi} \exp(\frac{\Delta^2}{4})\right)\\
+% 					& = \sqrt{\pi} \frac{\Delta}{2} \exp(\frac{\Delta^2}{4})
+% 		\end{split}
+% 	\end{equation}
+% 	\begin{equation}
+% 	\begin{split}
+% 		\int_{-\infty}^\infty \mathrm{d}q \ q^2 \exp(-q^2 + q\Delta) &= \partial_{\Delta} \left(\sqrt{\pi} \left(\frac{\Delta}{2} \exp(\frac{\Delta^2}{4})\right)\right)\\
+% 		& =\sqrt{\pi} \left(\frac{1}{2}\exp(\frac{\Delta^2}{4}) + \frac{\Delta^2}{4} \exp(\frac{\Delta^2}{4})\right)
+% 	\end{split}
+% \end{equation}
+% \end{subequations}
+% Substituting the results of \autoref{evalGaussians} into \autoref{HT10}, 
+% \begin{equation}
+% 	\mel{\tilde{1}}{q}{0} = \sqrt{\frac{1}{2}} (1 - \frac{\Delta^2}{2}) \exp(\frac{-\Delta^2}{4})
+% \end{equation}
+% The evaluation of other Herzberg-Teller integrals is analogous.
+
+\newpage
 \section{Impact of displacement, resonance frequencies, and vibronic linewidth and on HDFG Spectra}

### 2024-09-24 figures/check_ht_math.py
updated integral formulas
fixed a sign error with Delta; still suspicious of typos

@@ -1,0 +1,70 @@
+""" math checks on derivation
+"""
+
+import matplotlib.pyplot as plt
+import numpy as np
+import sympy
+from sympy import hermite
+
+factorial = sympy.functions.combinatorial.factorials.factorial
+
+x = sympy.symbols("x")
+y = sympy.symbols("y")
+n = sympy.symbols("n")
+l = sympy.symbols("l")
+
+def term_n0(x, n, y, l):
+    """ summand terms for <n|q|0>"""
+    return (-1)**y  / (2**(2*y)*factorial(y)) * (-1j/2)**(l+1) \
+    * (-x)**(n-2*y-l) / (factorial(l)*factorial(n-2*y-l)) \
+    * hermite(l+1, 1j * x / 2)
+
+for n, expression in enumerate([
+    # <0|q|0>
+    sympy.simplify(term_n0(x, 0, 0, 0)),
+    # <1|q|0>
+    sympy.simplify(term_n0(x, 1, 0, 0) + term_n0(x, 1, 0, 1)),
+    # <2|q|0>
+    sympy.simplify(term_n0(x, 2, 0, 0) + term_n0(x, 2, 0, 1) + term_n0(x, 2, 0, 2) + term_n0(x, 2, 1, 0)),]
+):
+    print(f"<{n}|q|0>: {expression}")
+
+
+def term_n1(x, n, y, l):
+    """terms for <n|q|1>"""
+    return (-1)**y  / (2**(2*y)*factorial(y)) * (-1j/2)**(l+2) \
+    * (-x)**(n-2*y-l) / (factorial(l)*factorial(n-2*y-l)) \
+    * hermite(l+2, 1j*x/2)
+
+for n, expression in enumerate([
+    # <0|q|0>
+    sympy.simplify(term_n1(x, 0, 0, 0)),
+    # <1|q|0>
+    sympy.simplify(term_n1(x, 1, 0, 0) + term_n1(x, 1, 0, 1)),
+    # <2|q|0>
+    sympy.simplify(term_n1(x, 2, 0, 0) + term_n1(x, 2, 0, 1) + term_n1(x, 2, 0, 2) + term_n1(x, 2, 1, 0)),]
+):
+    print(f"<{n}|q|1>: {expression}")
+
+
+
+d = np.linspace(-4,4)
+
[…]

### 2024-09-24 figures/check_ht_math.py
Update check_ht_math.py

@@ -21,11 +21,11 @@ def term_n0(x, n, y, l):
 
 for n, expression in enumerate([
     # <0|q|0>
-    sympy.simplify(term_n0(x, 0, 0, 0)),
+    sympy.simplify(term_n0(x, 0, 0, 0), rational=True),
     # <1|q|0>
-    sympy.simplify(term_n0(x, 1, 0, 0) + term_n0(x, 1, 0, 1)),
+    sympy.simplify(term_n0(x, 1, 0, 0) + term_n0(x, 1, 0, 1), rational=True),
     # <2|q|0>
-    sympy.simplify(term_n0(x, 2, 0, 0) + term_n0(x, 2, 0, 1) + term_n0(x, 2, 0, 2) + term_n0(x, 2, 1, 0)),]
+    sympy.simplify(term_n0(x, 2, 0, 0) + term_n0(x, 2, 0, 1) + term_n0(x, 2, 0, 2) + term_n0(x, 2, 1, 0), rational=True),]
 ):
     print(f"<{n}|q|0>: {expression}")
 
@@ -38,11 +38,11 @@ def term_n1(x, n, y, l):
 
 for n, expression in enumerate([
     # <0|q|0>
-    sympy.simplify(term_n1(x, 0, 0, 0)),
+    sympy.simplify(term_n1(x, 0, 0, 0), rational=True),
     # <1|q|0>
-    sympy.simplify(term_n1(x, 1, 0, 0) + term_n1(x, 1, 0, 1)),
+    sympy.simplify(term_n1(x, 1, 0, 0) + term_n1(x, 1, 0, 1), rational=True),
     # <2|q|0>
-    sympy.simplify(term_n1(x, 2, 0, 0) + term_n1(x, 2, 0, 1) + term_n1(x, 2, 0, 2) + term_n1(x, 2, 1, 0)),]
+    sympy.simplify(term_n1(x, 2, 0, 0) + term_n1(x, 2, 0, 1) + term_n1(x, 2, 0, 2) + term_n1(x, 2, 1, 0), rational=True),]
 ):
     print(f"<{n}|q|1>: {expression}")
 

### 2024-09-24 figures/check_ht_math.py
fix <1|q|1> typo

@@ -56,8 +56,8 @@ f_10 = 2**0.5 / 4 * (2-d**2) * f0
 f_20 = 2**0.5 / 16 * (d**3 - 4*d) * f0
 
 f_01 = 2**0.5 * (.25*d**2 + 0.5) * f0
-f_11 = 2 * (0.25*d - 0.125*d**2) * f0
-f_21 = 8**0.5 * (.03125*d**4 - 0.1875*d**2 +0.25) * f0
+f_11 = 2**0.5 / 4 * (2*d - d**3) * f0
+f_21 = 1/8 * (d**4 - 6*d**2 +8) * f0
 
 fig, ax = plt.subplots()
 ax.plot(d, f_00, label="<0|q|0>")

### 2024-09-25 paper.tex
starting edits

@@
 Hyper-Raman scattering itself is a six-wave mixing ($\chi^{(5)}$) technique; stimulated hyper-Raman will be weak and susceptible to four-wave mixing (FWM) cascades.\cite{RN515, RN243, Cho2000_Cascade}
-A coherent six-wave mixing analogue of hyper-Raman scattering, coherent anti-Stokes hyper-Raman spectroscopy (CAHRS), has been proposed and explored theoretically by several authors; however, it is also weak and highly susceptible to FWM cascades.\cite{Berger1978, Bjarnason1980, Cho1997, Cho1998}
+A coherent six-wave mixing analogue of hyper-Raman scattering, coherent anti-Stokes hyper-Raman spectroscopy (CAHRS), has been proposed and explored theoretically by several authors; however, it is also weak and highly susceptible to FWM cascades.\cite{Taran1977, Berger1978, Bjarnason1980, Cho1997, Cho1998}
 Of the many four-wave mixing techniques, HDFG and HSFG have strong similarity to Raman, stimulated Raman, and RISRS in that the electronic state must remove or add a $v$ quantum to the ground state (``ev'' coupling).
@@
 In this section, we investigate the properties of HDFG and make the connections between HDFG and hyper-Raman scattering explicit.
-Coherent spectroscopies are often described using the density matrix formalism, where a density matrix $\rho$ is propagated using the Liouville-von Neumann equation $via$
+Coherent spectroscopies are often described using the density matrix formalism, where an n$^{th}$ order density matrix $\rho^{(n)}$ is propagated using the Liouville-von Neumann equation $via$
 \begin{equation}\label{LVNE}
-	\dot{\rho} = \frac{1}{i \hbar} [H + V(t), \rho] + \dot{\rho}_R,
+	\dot{\rho}^{(n)} = \frac{1}{i \hbar} [H + V(t), \rho^{(n-1)}] + \dot{\rho}^{(n)}_R,
 \end{equation}
@@
 exponential relaxation, where $\Gamma$ is the system's dephasing rate.
-\cite{RN455, Sung2001}
-While exponential relaxation is usually an inappropriate description of most physical systems involving solvent-solute interactions,\cite{Yan1988, Li1994, Myers1997} our goal is to introduce simple, quantitative models to understand HDFG response.
+\cite{RN455, Sue1986, Sung2001}
+While exponential relaxation is usually an inappropriate description of most physical systems involving solvent-solute interactions,\cite{Sue1986, Yan1988, Li1994, Myers1997} our goal is to introduce simple, quantitative models to understand HDFG response.
 Thus, we write $\dot{\rho}_R = \Gamma \rho$.

### 2024-09-25 si.tex
develop ht section
updated integral formulas
fixed a sign error with Delta; still suspicious of typos
fix <1|q|1> typo
starting edits

@@
 Here, $p,q$ are the dimensionless conjugate normal mode coordinates, $\hbar\omega_{eg}$ is the energy difference between $H_e$ and $H_g$, and $\Delta$ is the dimensionless offset of the excited state surface relative to the ground state.
-The Hamiltonians are the well-known quantum harmonic oscillator, and their solutions are
+The Hamiltonians are the well-known quantum harmonic oscillator, and their position space wavefunctions are
 \begin{equation}
@@
 \end{equation}
-where $N_m = (m! \ 2^m \pi^{\frac{1}{2}})^{-\frac{1}{2}}$ is the normalization factor and $H_m$ is the $m^{th}$ Hermite Polynomial.\cite{RN230}
+where $N_m = (m! \ 2^m \pi^{\frac{1}{2}})^{-\frac{1}{2}}$ is the normalization factor and $H_m$ is the $m^{th}$ Hermite Polynomial.\cite{RN230, MorseFeshbach}
 
-For an $n$-quantum excited state vibration $| \tilde{n} \rangle$, and a $m$-quantum ground state vibration $| \tilde{m} \rangle$, the $k^{th}$-order vibrational coupling term is
+For an $n$-quantum excited state vibration $| \tilde{n} \rangle$, and a $m$-quantum ground state vibration $\ket{m}$, the $k^{th}$-order vibrational coupling term is
 \begin{equation}
@@
 \end{equation}
-The integral corresponds to Franck-Condon matrix elements for $k=0$ and Herzberg-Teller matrix elements for $k=1$.
+The integral corresponds to Franck-Condon factors for $k=0$ and Herzberg-Teller matrix elements for $k=1$.
 
@@
 \begin{eqnarray}
-	\int dq \ P_{nmk}(q) \exp(-q^2 + q\Delta), \\
+	\int_{-\infty}^\infty \mathrm{d}q \ P_{nmk}(q) \exp(-q^2 + q\Delta), \\
 	P_{nmk}(q) \equiv \sum_\lambda^{n+m+k} a_\lambda q^\lambda
@@
 \end{equation}
-so we can write
+so we can write\footnote{Setting $-x^2 \ = \ \Delta^2/4$ (so that $x \ = \ i \Delta /2$) and using the chain rule ($\mathrm{d}/\mathrm{d}x = \mathrm{d}/\mathrm{d}\Delta \ \mathrm{d}\Delta / \mathrm{d}x$) provides the final result in \autoref{eq:F_solved}}
 \begin{equation}\label{eq:F_solved}
@@
 \begin{split}
-	H_m(q) &= \sum_{x=0}^{\left\lfloor{m/2}\right\rfloor} a_m^{(m-2x)} q^{m-2x} \\
-	H_n(q-\Delta) &= \sum_{x=0}^{\left\lfloor{n/2}\right\rfloor}
-	a_n^{(n-2x)} (q-\Delta)^{n-2x} \\
-		&= \sum_{x=0}^{\left\lfloor{n/2}\right\rfloor} a_n^{(n-2x)} \sum_{l=0}^{n-2x} \Delta^{n-2x-l} \binom{n-2x}{l} q^l
+	H_m(q) &= \sum_{s=0}^{\left\lfloor{m/2}\right\rfloor} a_m^{(m-2s)} q^{m-2s} \\
+	H_n(q-\Delta) &= \sum_{s=0}^{\left\lfloor{n/2}\right\rfloor}
+	a_n^{(n-2s)} (q-\Delta)^{n-2s} \\
+		&= \sum_{s=0}^{\left\lfloor{n/2}\right\rfloor} a_n^{(n-2s)} \sum_{l=0}^{n-2s} \left(-\Delta\right)^{n-2s-l} \binom{n-2s}{l} q^l
 \end{split}
 \end{equation}
-where $\left\lfloor n \right\rfloor$ denotes the \textit{floor} of $n$, $\binom{a}{b} = a! / (b!(a-b)!)$, and the Hermite coefficients are
+where $\left\lfloor n \right\rfloor$ denotes the \textit{floor} of $n$, $\binom{a}{b} = a! / (b!(a-b)!)$, and the Hermite coefficients are\cite{MorseFeshbach}
 \begin{equation}
-	a_n^{(n-2x)} = n! \frac{(-1)^x 2^{n-2x}}{x!(n-2x)!}.
+	a_n^{(n-2s)} = n! \frac{(-1)^x 2^{n-2s}}{s!(n-2s)!}.
 \end{equation}
@@
 	&= \sum_{x=0}^{\left\lfloor{m/2}\right\rfloor} \sum_{y=0}^{\left\lfloor{n/2}\right\rfloor} \sum_{l=0}^{n-2y} c_{xyl} \ q^{l+m-2x+k}, \\
-	c_xyl &= a_m^{(m-2x)} a_n^{(n-2y)} \Delta^{n-2y-l} \binom{n-2y}{l}.
+	c_{xyl} &= a_m^{(m-2x)} a_n^{(n-2y)} \left(-\Delta\right)^{n-2y-l} \binom{n-2y}{l}.
 \end{split}
@@
 \begin{equation}\label{eq:general_solution}
-	\mel{\tilde{n}}{q^k}{m} = \sqrt{\pi} N_n N_m \exp(-\frac{\Delta^2}{4}) \sum_{x=0}^{\left\lfloor{m/2}\right\rfloor} \sum_{y=0}^{\left\lfloor{n/2}\right\rfloor} \sum_{l=0}^{n-2y} \left( -\frac{i}{2} \right)^{l+m-2x+k} c_{xyl} H_{l+m-2x+k}\left(i\frac{\Delta}{2}\right).
+	\mel{\tilde{n}}{q^k}{m} = \sqrt{\pi} N_n N_m 
+	\exp(-\frac{\Delta^2}{4}) \sum_{x=0}^{\left\lfloor{m/2}\right\rfloor} \sum_{y=0}^{\left\lfloor{n/2}\right\rfloor} \sum_{l=0}^{n-2y} \left( -\frac{i}{2} \right)^{l+m-2x+k} c_{xyl} H_{l+m-2x+k}\left(i\frac{\Delta}{2}\right).
 \end{equation}
@@
 \subsection{Evaluating Herzberg Teller terms for HDFG}
-
+When starting from $\ket{0}$,
 \begin{equation}
 \begin{split}
-	\langle n |q| 0 \rangle &= \cdots \\
+	\langle \tilde{n} |q| 0 \rangle &= 
+	\sqrt{\pi} N_n N_0 \exp(-\frac{\Delta^2}{4}) \sum_{y=0}^{\left\lfloor{n/2}\right\rfloor} \sum_{l=0}^{n-2y} \left( -\frac{i}{2} \right)^{l+1} c_{0yl} H_{l+1}\left(i\frac{\Delta}{2}\right) \\
+	&= \sqrt{n! \ 2^n} \exp(-\frac{\Delta^2}{4})
+	\sum_{y=0}^{\left\lfloor{n/2}\right\rfloor} 
+	\frac{(-1)^y}{2^{2y}y!}
+	\sum_{l=0}^{n-2y} \left( -\frac{i}{2} \right)^{l+1} 
+	\frac{\left(-\Delta\right)^{n-2y-l}}{l!(n-2y-l)!}
+	H_{l+1}\left(i\frac{\Delta}{2}\right)
 \end{split}
+\end{equation}
+giving the first few relevant integrals as
+\begin{equation}
+	\langle \tilde{0} |q| 0 \rangle = \frac{\Delta}{2} \exp(-\frac{\Delta^2}{4})
 \end{equation}
@@
 \begin{equation}
+	\langle \tilde{1} |q| 0 \rangle = 
+	\frac{\sqrt{2}}{4} \left( 2 - \Delta^2 \right)
+	\exp(-\frac{\Delta^2}{4})
+\end{equation}
+
+\begin{equation}
+	\langle \tilde{2} |q| 0 \rangle = 
+	\frac{\sqrt{2}}{8} \left( \Delta^3 - 4 \Delta \right)
+	\exp(-\frac{\Delta^2}{4})
+\end{equation}
+
+Similarly, when starting from $\ket{1}$, 
+\begin{equation}
 	\begin{split}
-		\langle n |q| 1 \rangle &= \cdots \\
+		\langle \tilde{n} |q| 1 \rangle &= \sqrt{\pi} N_n N_1 \exp(-\frac{\Delta^2}{4}) \sum_{y=0}^{\left\lfloor{n/2}\right\rfloor} \sum_{l=0}^{n-2y} \left( -\frac{i}{2} \right)^{l+2} c_{1yl} H_{l+2}\left(i\frac{\Delta}{2}\right) \\
+		&= 
+		\sqrt{n! \ 2^{n+1}} \exp(-\frac{\Delta^2}{4}) 
+		\sum_{y=0}^{\left\lfloor{n/2}\right\rfloor} 
+		\frac{(-1)^y}{2^{2y}y!}
+		\sum_{l=0}^{n-2y} \left( -\frac{i}{2} \right)^{l+2} 
+		\frac{\left(-\Delta\right)^{n-2y-l}}{l!(n-2y-l)!}
+		H_{l+2}\left(i\frac{\Delta}{2}\right)
 	\end{split}
 \end{equation}
-
-% We now have the background needed to calculate $\langle \tilde{n} |q| m \rangle$.
-% % $\mel{\tilde{1}}{q}{0}$ for an arbitrary offset $\Delta$.
-% Using $H_0(q) = 1$ and $H_1(q) = 2q$,
-% \begin{equation}\label{HT10}
-% 	\begin{split}
-% 		\mel{\tilde{1}}{q}{0} &= N_1 N_0 \exp(-\frac{\Delta^2}{2}) \int_{-\infty}^\infty \mathrm{d}q \ 2(q - \Delta) q \exp(-q^2 + q\Delta)\\
-% 		&= 2N_1 N_0 \exp(-\frac{\Delta^2}{2}) \left( \int_{-\infty}^\infty \mathrm{d}q \ q^2 \exp(-q^2 + q\Delta) + \Delta \int_{-\infty}^\infty \mathrm{d}q \ q \exp(-q^2 + q\Delta) \right)
-% 	\end{split}
-% \end{equation}
-% Both integrals can be evaluated using \autoref{identity}:
-% \begin{subequations}\label{evalGaussians}
-% 	\begin{equation}
-% 		\begin{split}
-% 					\int_{-\infty}^\infty \mathrm{d}q \ q \exp(-q^2 + q\Delta) &= \partial_{\Delta} \left(\sqrt{\pi} \exp(\frac{\Delta^2}{4})\right)\\
-% 					& = \sqrt{\pi} \frac{\Delta}{2} \exp(\frac{\Delta^2}{4})
-% 		\end{split}
-% 	\end{equation}
-% 	\begin{equation}
-% 	\begin{split}
-% 		\int_{-\infty}^\infty \mathrm{d}q \ q^2 \exp(-q^2 + q\Delta) &= \partial_{\Delta} \left(\sqrt{\pi} \left(\frac{\Delta}{2} \exp(\frac{\Delta^2}{4})\right)\right)\\
-% 		& =\sqrt{\pi} \left(\frac{1}{2}\exp(\frac{\Delta^2}{4}) + \frac{\Delta^2}{4} \exp(\frac{\Delta^2}{4})\right)
-% 	\end{split}
-% \end{equation}
-% \end{subequations}
-% Substituting the results of \autoref{evalGaussians} into \autoref{HT10}, 
-% \begin{equation}
-% 	\mel{\tilde{1}}{q}{0} = \sqrt{\frac{1}{2}} (1 - \frac{\Delta^2}{2}) \exp(\frac{-\Delta^2}{4})
-% \end{equation}
-% The evaluation of other Herzberg-Teller integrals is analogous.
+giving
+\begin{equation}
+	\langle \tilde{0} |q| 1 \rangle = \frac{\sqrt{2}}{4}\left( \Delta^2 + 2 \right)
+	\exp(-\frac{\Delta^2}{4})
+\end{equation}
+\begin{equation}
+	\langle \tilde{1} |q| 1 \rangle = \frac{\sqrt{2}}{4}\left( -\Delta^3 + 2\Delta \right)
+	\exp(-\frac{\Delta^2}{4})
+\end{equation}
+\begin{equation}
+	\langle \tilde{2} |q| 1 \rangle = \frac{1}{8} \left( \Delta^4 - 6\Delta^2 + 8 \right)
+	\exp(-\frac{\Delta^2}{4})
+\end{equation}
 
 \newpage
-\section{Impact of displacement, resonance frequencies, and vibronic linewidth and on HDFG Spectra}
+\section{Impact of displacement, resonance frequencies, vibronic linewidth and molecular parameters on HDFG Spectra}
 \begin{figure}[!htbp]

### 2024-09-25 figures/2D_spec.py

@@ -12,7 +12,7 @@ import pathlib
 
 wt.artists.apply_rcparams(kind="publication")
 
-save = True
+save = False
 fontsize = 18
 here = pathlib.Path(__file__).resolve().parent
 
@@ -151,7 +151,7 @@ dMgedQ = 0.007 #dM^eg / dQ
 
 
 #define terms
-y = np.linspace(10000, 50000, 3000000)
+y = np.linspace(5000, 60000, 2750000)
 
 
 A = Mge * Lge * (f01(d)*f00(d)*Deltaevgo(0,y,0) + f11(d)*f10(d)*Deltaevgo(1,y,1) + f21(d)*f20(d)*Deltaevgo(2,y,2)) #there must be a simpler way to do this but idk
@@ -191,17 +191,17 @@ abs_max = tot.max()
 
 #plot the A and B
 ax1 = plt.subplot(gs[0,1])
-ax1.plot(y, tot / tot.max(), linewidth = '2', label = r'$\mathsf{|A + B|}$', color = 'black', zorder = 4)
-ax1.plot(y, np.abs(A) / abs_max, linewidth = '2', label = r'$\mathsf{|A|}$', color = 'cyan', zorder = 3)
-ax1.plot(y, np.abs(B1+B2) / abs_max, linewidth = '2', label = r'$\mathsf{|B|}$', color = 'red', zorder = 3)
-ax1.plot(y, np.abs(B1) / abs_max, linewidth = '2', label = r'$\mathsf{|B_1|}$', color = 'orange', zorder = 2)
-ax1.plot(y, np.abs(B2) / abs_max, linewidth = '2', label = r'$\mathsf{|B_2|}$', color = 'green', zorder = 1)
-
 # ax1.plot(y, tot / tot.max(), linewidth = '2', label = r'$\mathsf{|A + B|}$', color = 'black', zorder = 4)
-# ax1.plot(y, np.abs(A) / abs_max, linewidth = '2', label = r'$\mathsf{|A|}$', zorder = 3)
-# ax1.plot(y, np.abs(B1+B2) / abs_max, linewidth = '2', label = r'$\mathsf{|B|}$', zorder = 3)
-# ax1.plot(y, np.abs(B1) / abs_max, linewidth = '2', label = r'$\mathsf{|B_1|}$', zorder = 2)
[…]

### 2024-09-25 figures/plotting_fcht.py

@@ -11,7 +11,7 @@ import pathlib
 
 wt.artists.apply_rcparams(kind="publication")
 
-save = True
+save = False
 fontsize =18
 here = pathlib.Path(__file__).resolve().parent
 
@@ -105,9 +105,9 @@ for ax in [ax0, ax1]:
     # ax.set_xticks(xticks)
     ax.set_ylim(-0.75, 1.6)
     ax.legend(loc = 1, ncol =2)
-    for d in [0]:
+    for j in [0]:
         # ax.vlines(x = 0, ymin = -1, ymax = 2, color = 'gray', linestyle = '--', linewidth = 1)
-        ax.hlines(xmin=-5, xmax =5, y = d, color = 'gray', linestyle = '--', linewidth = 1)
+        ax.hlines(xmin=-5, xmax =5, y = j, color = 'gray', linestyle = '--', linewidth = 1)
 
 
 for i, ax in enumerate(fig.axes):
@@ -116,3 +116,60 @@ for i, ax in enumerate(fig.axes):
 
 if save:
     wt.artists.savefig(here / "fcht.png", transparent = True, bbox_inches='tight')
+    
+    
+"""doing the products now"""
+
+cols1 = [1, 1, 1] 
+aspects1 = [[[0, 0], 1], [[1, 0], 1], [[2, 0], 1]] 
+
+fig1, gs1 = wt.artists.create_figure(width="dissertation", nrows=1, cols=cols1, aspects=aspects1, wspace=1) 
+
+ax01 = plt.subplot(gs1[0,0])
+
+ax01.plot(d, f00(d)*f01(d), linewidth = '2', label = r'$\mathsf{\langle1|\tilde{0}\rangle  \langle\tilde{0}|0\rangle}$', zorder = 4)
+
+ax01.plot(d, f10(d)*f11(d), linewidth = '2', label = r'$\mathsf{\langle 1 | \tilde{1} \rangle \langle\tilde{1}|0\rangle}$', zorder = 3)
+
+ax01.plot(d, f20(d) * f21(d), linewidth = '2', label = r'$\mathsf{\langle 1 | \tilde{2} \rangle \langle \tilde{2} | 0\rangle  }$', zorder = 1)
+
+ax01.set_title(r'$\mathsf{A \ term}$')
+ax01.set_ylim(-0.6, 1.1)
+
+ax11 = plt.subplot(gs1[0,1])
+
[…]

### 2024-09-25 paper.tex
kinda there, but not really
working on how to present interference effects in the spectrum.

@@
 \cite{Sung2001}
-In the limit where input field pulsewidths are much longer than electronic dephasing times and the individual molecule limit is approached, it becomes acceptable to write $\dot{\rho}_R \approx \Gamma \rho$, i.e.
+In the limit where input field pulsewidths are much longer than electronic dephasing times and the individual molecule limit is approached, it becomes acceptable to write $\dot{\rho}^{(n)}_R= \Gamma \rho^{(n)}$, i.e.
 exponential relaxation, where $\Gamma$ is the system's dephasing rate.
@@
 While exponential relaxation is usually an inappropriate description of most physical systems involving solvent-solute interactions,\cite{Sue1986, Yan1988, Li1994, Myers1997} our goal is to introduce simple, quantitative models to understand HDFG response.
-Thus, we write $\dot{\rho}_R = \Gamma \rho$.
+Thus, we write $\dot{\rho}^{(n)}_R= \Gamma \rho^{(n)}$.
 The exponential relaxation limit has proven useful in investigating the properties of 2D-EV, 2D-VE, and doubly resonant SFG using pulses much longer than electronic dephasing times.
@@
 \end{equation}
-The $A$ term contains the static ($\order{Q^0}$) transitions (i.e., Condon approximation), the $B$ term depends upon $\order{Q}$ transitions (Herzberg-Teller contributions), and the $C$ term depends on $\order{Q_i Q_j}$ transitions.
+The $A$ term contains the static ($\order{Q^0}$) transitions (i.e., Condon approximation),\cite{Condon1928} the $B$ term depends upon $\order{Q}$ transitions (Herzberg-Teller contributions),\cite{HerzbergTeller1933} and the $C$ term depends on $\order{Q_i Q_j}$ transitions.
 The $C$ term is suppressed in the following discussion as it depends on one and two photon forbidden transitions, making its contribution to $\gamma_{ijkl}$ roughly two orders of magnitude less than $A_{ijk}$.
@@
 		The spectra are referenced to $\max{(A+B)}$. 
-		It is assumed that $\omega_2 = \omega_3$.
+		It is assumed that $\omega_2 = \omega_3$, and that all molecular parameters used to simulate the spectra are positive.
 		The vibrational states on the $|g)$ and $|e)$ manifolds are spaced 1600 cm$^{-1}$ apart, with the vibronic states $\ket{e,\tilde{v}'}$ given linewidths of 300 cm$^{-1}$ and $\omega_{eg}$ = 30000 cm$^{-1}$.
@@
 	The bra and ket labels are written according to their order in $A$, $B_1$, $B_2$ as written in \autoref{ABterms_DR}.
-	Closed-form expressions for the Franck-Condon and Herzberg-Teller integrals used here are tabulated in the Supporting Information.}
+	The Franck-Condon and Herzberg-Teller integral products tabulated here are plotted in the Supporting Information (Figure S2) as a function of $\Delta$.}
 	\begin{ruledtabular}
@@
 This arises due to interference between the real and imaginary parts of $\gamma$ (\autoref{fig:doubres_spec}c, d).
-The abnormal lineshapes in both terms arises due to the sign of the Franck-Condon and Herzberg-Teller integrals that drive the output of the vibronic transitions for $\Delta = 0.5$ (\autoref{fcht}), in turn driving significant interference in the overall $\abs{A+B}$ output.
+The abnormal lineshape arises due to the sign of the Franck-Condon and Herzberg-Teller integrals, as well as the molecular parameters that drive the output of the vibronic transitions.
 Such effects have been seen elsewhere in spontaneous, surface enhanced hyper-Raman studies. \cite{Milojevich2011}
+
+The Franck-Condon and Herzberg-Teller integrals can manipulate interference in the total output spectrum as a function of offset (Figure S2).
+When the offset is inverted about the origin ($\Delta \rightarrow -\Delta$),
+
+However, the main source of interference in the HDFG spectra arises from the sign of the molecular parameters. 
+In the HDFG spectrum presented in \autoref{fig:doubres_spec}, the signs of all molecular parameters are taken to be positive. 
+Inverting the sign of one parameter eliminates the interference and restores the expected, purely Lorentzian lineshape.
+
+*orientational averaging
+*changing one trivially fixes interference (cf plot above)
+*in SI, put examples
 
@@
 
-Evaluating \autoref{contour} for the HDFG pathway above shows\footnote{See the supporting information for more details}
+Evaluating \autoref{contour} for the HDFG pathway above shows\footnote{See the supporting information for more details.}
 

### 2024-09-25 si.tex
kinda there, but not really
working on how to present interference effects in the spectrum.

@@
 \end{equation}
+An alternative approach has been introduced by Kundu \textit{et al}, which yields effectively identical results. \cite{Kundu2022}
 
@@
 
-\newpage
-\section{Impact of displacement, resonance frequencies, vibronic linewidth and molecular parameters on HDFG Spectra}
+These integrals, along with some relevant Franck-Condon factors, are plotted below as a function of offset.
+
 \begin{figure}[!htbp]
@@
 
+\newpage
+\section{Impact of displacement, resonance frequencies, vibronic linewidth and molecular parameters on HDFG Spectra}
+Inspection of the $A,B$ terms in the main text show that the HDFG output is dependent upon the relative size of products of Franck-Condon and Herzberg-Teller integrals.
+For clarity, we plot the relevant product factors to assist in understanding the impact of offset on the HDFG spectra.
+
+\begin{figure}[!htbp]
+	\centering
+	\includegraphics[width=6.675in]{figures/fcht_product.png}
+	\caption{Products of Franck-Condon and Herzberg-Teller integrals relevant to the $A, B_1, B_2$ terms in this manuscript as a function of offset, $\Delta$.} 
+	\label{fig:fcht_product}
+\end{figure}
+
+These plots highlight the important distinction that $B$ term contributions to HDFG can dominate in the limit of small offset.
+This is expected, as when $\Delta \rightarrow 0$, the overlap integral \autoref{key} resolves into the typical harmonic oscillator selection rules.
+
 \begin{figure}[!htbp]
@@
 	\caption{The impact of offset, vibrational resonance, and linewidth on HDFG spectra.
-Parameters for (a,b) follow from Myers et al., whereas parameters for (c,d) follow from Brennan et al.\cite{Myers1982, Brennan2024}}
+Parameters for (a,b) follow from Myers et al., whereas parameters for (c,d) follow from Brennan et al.\cite{Myers1982, Brennan2024}
+	Note that in these plots, the ratio $\abs{A/B} = 0.1$ is enforced} 
 	\label{fig:chgdelta}
@@
 
-\section{Evaluating impact of inhomogeneity on HDFG output}
+\section{Evaluating impact of static inhomogeneity on HDFG output}
 In this section, the integral
@@
 \end{equation}
-is evaluated for $c=-1$ (electronic state and vibrational state energy fluctuations are anti-correlated) $c=1$ (electronic state and vibrational state energy fluctuations are correlated).
+is evaluated for $c=-1$ (electronic state and vibrational state energy fluctuations are anti-correlated) and $c=1$ (electronic state and vibrational state energy fluctuations are correlated).
 

### 2024-09-25 figures/2D_spec_chgparams.py

@@ -1,0 +1,157 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Tue Jan 17 09:28:39 2023
+
+@author: rpm
+"""
+import numpy as np
+import WrightTools as wt
+import matplotlib.pyplot as plt 
+from matplotlib.patches import FancyArrowPatch
+import pathlib
+
+wt.artists.apply_rcparams(kind="publication")
+
+save = False
+fontsize = 18
+here = pathlib.Path(__file__).resolve().parent
+
+#define harmonic wells and coordinates
+d = 0.5 #offset for es
+do = 0 #gs placement
+
+#make figure
+cols = [1, 1] 
+aspects = [[[0, 0], 1], [[1, 0], 1]] 
+
+fig, gs = wt.artists.create_figure(width="dissertation", nrows=2, cols=cols, aspects=aspects, hspace=0.7, wspace=1.2) 
+
+#define Franck-Condon factors following page 164 of Roger Carlson's thesis in terms of 'q', the offset
+#<a|b> == |a> is on the ES and |b> is on the GS.
+
+def f00(q): #<0|0>
+    return np.exp(-q**2/4)
+
+def f01(q): #<0|1>
+    return q/(np.sqrt(2)) * f00(q)
+
+def f10(q): #<1|0>
+    return -1*f01(q)
+
+def f11(q): #<1|1>
+    return (1 - q**2/2) *f00(q)
+
+def f02(q): #<0|2>
+    return q**2/(2*np.sqrt(2)) * f00(q)
+
+def f20(q): #<2|0>
+    return f02(q)
+   
+def f21(q): #<2|1>
+    return -q * (1 - q**2/4) *f00(q)
+
+#define Herzberg Teller overlap integrals following page 165 of Roger Carlson's thesis in terms of q
+def h00(q): #<0|Q|0>
+    return q/2 * f00(q)
+
+def h01(q): #<0|Q|1>
+    return 1/np.sqrt(2) * (1 + q**2 /2) * f00(q)
+
+def h10(q): #<1|Q|0>
+    return 1/np.sqrt(2) * (1 - q**2 /2) * f00(q)
+
+def h11(q): #<1|Q|1>
[…]

### 2024-09-25 figures/plotting_fcht.py

@@ -112,7 +112,7 @@ for ax in [ax0, ax1]:
 
 for i, ax in enumerate(fig.axes):
     # ax.grid(visible=True, color="k", lw=0.5, linestyle=":")
-    wt.artists.corner_text("abcd"[i], ax=ax, corner = 'UL', distance = 0.25, bbox = True, fontsize = fontsize, background_alpha=0.75)
+    wt.artists.corner_text("abcd"[i], ax=ax, corner = 'UL', distance = 0.35, bbox = True, fontsize = fontsize, background_alpha=0.75)
 
 if save:
     wt.artists.savefig(here / "fcht.png", transparent = True, bbox_inches='tight')
@@ -169,7 +169,7 @@ for ax in [ax01, ax11, ax21]:
 
 
 for i, ax in enumerate(fig1.axes):
-    wt.artists.corner_text("abcd"[i], ax=ax, corner = 'UL', distance = 0.25, bbox = True, fontsize = fontsize, background_alpha=0.75)
+    wt.artists.corner_text("abcd"[i], ax=ax, corner = 'UL', distance = 0.35, bbox = True, fontsize = fontsize, background_alpha=0.75)
 
 if save:
     wt.artists.savefig("fchtproduct.png", transparent = True, bbox_inches='tight')

### 2024-09-27 paper.tex
more edits
still need to discuss (a) Kundu 2022 integrals, (b) impact of \Delta on spectra, and (c) impact of sign of M, dM/dQ etc on spectra.

@@
 Hyper difference frequency generation (HDFG) spectroscopy and hyper sum frequency generation (HSFG) spectroscopy are four wave mixing CMDS methods based on direct excitation of a vibrational mode through IR absorption and subsequent scattering to or from the vibrational mode through a hyper-Raman transition.
-In HDFG/HSFG, an infrared pulse is resonant with a vibrational mode, while two other excitations stimulate the hyper-Raman scattering process.
-The infrared excitation frequency selects the vibrational modes to be stimulated through the hyper-Raman transition.
+In HDFG/HSFG, an infrared pulse is resonant with a vibrational mode, while two other excitations stimulate the hyper-Raman process.
+The infrared excitation frequency selects the vibrational mode stimulated through the hyper-Raman transition.
 The other two excitation frequencies control electronic enhancement for the hyper-Raman scattering event.
@@
 Independently developed by the Fleming and Khalil groups, respectively, 2D Electronic-Vibrational (2D-EV) and 2D Vibrational-Electronic (2D-VE) spectroscopy are based upon pump-probe and absorption type pathways which also investigate e-v coupling.\cite{Oliver2014, Courtney2015, Courtney2015_1}
-The Rao group has also developed a $\chi^{(4)}$ analogue of 2D-EV, 2D-EV sum frequency generation (2D-EVSFG), to investigate interfacial e-v coupling. \cite{Deng2021}  
-These methods have been used to investigate vibronic coupling in a variety of molecular systems and serve as 2D pump-probe type analogues to the hyper-Raman-based spectroscopies discussed here.\cite{Courtney2015, Gaynor2018, Arsenault2020, HuangFu2023}
+The Rao group has also developed a $\chi^{(4)}$ analogue of 2D-EV, 2D-EV sum frequency generation (2D-EVSFG), to probe interfacial e-v coupling. \cite{Deng2021}  
+These methods have been used to understand vibronic coupling in a variety of molecular systems and, albeit different selection rules, serve as 2D pump-probe type analogues to the hyper-Raman-based spectroscopies discussed here.\cite{Courtney2015, Gaynor2018, Arsenault2020, HuangFu2023}
 
@@
 
-It is useful to expose relationships between nonlinear output, transition dipoles and hyper-Raman hyperpolarizabilities in the driven limit ($\dot{\rho} = 0$). \cite{Simpson2004, Moad2005}
+It is useful to expose relationships between nonlinear output, transition dipoles and hyper-Raman hyperpolarizabilities in the driven limit ($\dot{\rho}^{(n)} = 0 \ \forall n$). \cite{Moad2005}
 Under the electric dipole approximation, the $I^\text{th}$ Cartesian component of the third order nonlinear output polarization, ${P}^{(3)}_I$, of a four wave mixing process, induced by electric fields $E_J$, $E_K$, and $E_L$ at output frequency $\omega_4=-\omega_1 + \omega_2 + \omega_3$ is written as (using Einstein summation) \cite{RN307}
@@
 \end{equation}
-Here $N$ is a number density, $F=\prod_j  \frac{1}{3} \left({\left(n(\omega_j)\right)^2 + 1} \right)$ is the Lorentz local field factor, where $n$ is the (frequency dependent) refractive index and $\gamma_{ijkl}$ is the third-order polarizability (i.e., second hyperpolarizability).
+For clarity, we define the input electric fields as
+\begin{equation}
+	\vec{E}\left(\vec{x},t\right) = \frac{1}{2} \vec{E}_0 \exp(i\left(\vec{k}\cdot\vec{x} -\omega t\right)) +\text{c.c.}.
+\end{equation}
+In \autoref{eq:nfgamma}, $N$ is a number density, $F=\prod_j  \frac{1}{3} \left({\left(n(\omega_j)\right)^2 + 1} \right)$ is the Lorentz local field factor, where $n$ is the (frequency dependent) refractive index and $\gamma_{ijkl}$ is the third-order polarizability (i.e., second hyperpolarizability).
 \cite{Bedeaux1973}
@@
 The steps behind orientational averaging of $\gamma_{ijkl}$, a rank four tensor in the molecular frame, are detailed elsewhere.\cite{Andrews1977, McDonnell2024}
-Briefly, a tensor in the molecular frame, $A_{ijkl}$, is transformed into an element of the same tensor in the laboratory frame, $\langle A_{ijkl} \rangle_{IJKL}$, through $\langle A_{ijkl} \rangle_{IJKL}$ = $\theta^{ijkl}_{IJKL} A_{ijkl}$, where summation over repeated indices is implied and $\theta$ is the transformation operator.
-\cite{McDonnell2024, Andrews1977}
 
-By propagating \autoref{LVNE} in the steady state limit ($\dot{\rho} = 0$), the HDFG hyperpolarizability is \cite{Prior1984}
+By propagating \autoref{LVNE} in the steady state limit, the HDFG hyperpolarizability is \cite{Prior1984}
 \begin{equation}\label{sivegamma}
@@
 \end{equation}
-where: $\mu^{ab}_{j}$ is the $j^{th}$ element of $\mel{a}{\vec{\mu}}{b}$, $\Delta_{kl}^{-x+y+z} = \omega_{kl} - (-\omega_{x}+\omega_{y} + \omega_{z}) - i\Gamma_{kl}$, $\omega_j$ is the frequency of the j$^{th}$ input field, $\Gamma_{kl}$ is the dephasing of $\rho_{kl}$ and $\rho_{gg}$ is the ground state population.
+where: $\mu^{ab}_{j}$ is the $j^{th}$ element of $\mel{a}{\vec{\mu}}{b}$, $\Delta_{kl}^{-x+y+z} = \omega_{kl} - (-\omega_{x}+\omega_{y} + \omega_{z}) - i\Gamma_{kl}$, $\omega_j$ is the frequency of the j$^{th}$ input field, $\Gamma_{kl}$ is the $\rho_{kl}$ dephasing, and $\rho_{gg}$ is the ground state population.
 Here, $\ket{e}$ and $\ket{m}$ are virtual states, and thus necessarily summed over in \autoref{sivegamma}.
@@
 We first investigate the HDFG selection rules through a Placzek type formalism.
-When $\omega_2+\omega_3$ is significantly detuned from resonance and the vibronic nature of the virtual states is ignored, the Placzek approximation can be used to study selection rules in terms of the hyper-Raman hyperpolarizability, $\beta$.
+When $\omega_2+\omega_3$ is significantly detuned from resonance and the vibronic nature of the virtual states is ignored, the Placzek approximation can be invoked to study selection rules in terms of the hyper-Raman hyperpolarizability, $\beta$.
 \cite{Placzek1934, Long1970}
@@
 
-The general selection rule can be simplified by considering excitation of an infrared active normal mode.  
-Assume state $v$ is the $v^{\text{th}}$ normal mode.
-We Taylor expand the dipole and first hyperpolarizability operators to first order in the normal mode coordinate $Q_v$ about equilibrium:\cite{Long1970, Shen90}
+The general selection rule can be simplified by considering the excitation of an infrared active normal mode.  
+Assume $\ket{v}$ is the $v^{\text{th}}$ normal mode.
+We Taylor expand the dipole and first hyperpolarizability operators to first order in the normal mode coordinate $Q_v$ about equilibrium:
 \begin{subequations}
@@
 While the Placzek treatment provides the general source of HDFG output, it does not predict the behavior of $\beta_{ijk}$ as $\omega_2 + \omega_3$ is changed.
-We now explicitly consider electronic resonances through the $A,B,C$ decomposition of $\beta$ introduced by Chung and Ziegler, analogous to those found in Albrecht's treatment of Raman spectroscopy (i.e., sum-over-states formalism).\cite{Albrecht1961, Ziegler1988}
+We now explicitly consider electronic resonances through the $A,B,C$ decomposition of $\beta$ introduced by Chung and Ziegler, analogous to Albrecht's treatment of Raman spectroscopy (i.e., sum-over-states formalism).\cite{Albrecht1961, Ziegler1988}
 To employ this formalism, we write the states in a Born-Oppenheimer basis $\ket{a,b}$, where $\ket{a,b} = |a(\textbf{Q})) \otimes \ket{b}$ for electronic states $\{|a(\textbf{Q}))\}$ and vibrational states $\{\ket{b}\}$ (i.e., adiabatic approximation), where \textbf{Q}, the system normal modes, is the adiabatic parameter.
@@
 We will henceforth suppress the dependence of the electronic states on \textbf{Q} for simplicity.
-It is worthwhile to note that the time-dependent Raman formalism developed by Heller \textit{et al.} can be applied to hyper-Raman scattering. \cite{Myers1982, Shoute2005}
+It is worthwhile to note that the time-dependent Raman formalism developed by Heller \textit{et al.} can be applied to hyper-Raman scattering. \cite{Lee1979, Silverstein2012}
 However, since our goal is to expose the Quantum Mechanical aspects of HDFG spectroscopy, we choose to employ the typical sum-over-states formalism.
@@
 	\end{subequations}
-where $\Lambda^{ab}_{ij} = 1/\hbar \sum_m M_i^{am}M_j^{mb} $ is the electronic two photon transition moment between $a$ and $b$.\cite{McClain1977}
+where $\Lambda^{ab}_{ij} = 1/\hbar \sum_m M_i^{am}M_j^{mb} $ is the electronic two photon transition moment between $|a)$ and $|b)$.\cite{McClain1977}
 

### 2024-09-27 si.tex
more edits
still need to discuss (a) Kundu 2022 integrals, (b) impact of \Delta on spectra, and (c) impact of sign of M, dM/dQ etc on spectra.

@@
 The integral corresponds to Franck-Condon factors for $k=0$ and Herzberg-Teller matrix elements for $k=1$.
+The vibrational coupling integrals are written assuming the expansion of the dipole moment is taken about the equilibirum point of the ground state geometry ($q=0$), as is done in the main text.
 
@@
 		F_w(\Delta) &= \int_{-\infty}^\infty \mathrm{d}q \ q^w \exp(-q^2 + q\Delta) = \partial_{\Delta} \int_{-\infty}^\infty \mathrm{d}q \ q^{w-1} \exp(-q^2 + q\Delta) \\
-		&= \partial_\Delta F_{w-1}(\Delta)
+		&= \frac{\mathrm{d}}{\mathrm{d}\Delta} F_{w-1}(\Delta)
 	\end{split}
 \end{equation}
-so we can write\footnote{Setting $-x^2 \ = \ \Delta^2/4$ (so that $x \ = \ i \Delta /2$) and using the chain rule ($\mathrm{d}/\mathrm{d}x = \mathrm{d}/\mathrm{d}\Delta \ \mathrm{d}\Delta / \mathrm{d}x$) provides the final result in \autoref{eq:F_solved}}
+so we can write\footnote{Setting $-x^2 \ = \ \Delta^2/4$ (so that $x \ = \ i \Delta /2$) and using the chain rule ($\frac{\mathrm{d}}{\mathrm{d}x} =  \frac{\mathrm{d}}{\mathrm{d}\Delta}  \frac{\mathrm{d\Delta}}{\mathrm{d}x}$) provides the final result in \autoref{eq:F_solved}.}
 \begin{equation}\label{eq:F_solved}
 	\begin{split}
-		F_w(\Delta) &= \left(\partial_\Delta \right)^w F_0(\Delta) \\
+		F_w(\Delta) &= \frac{\mathrm{d}^w}{\mathrm{d}\Delta^w} F_0(\Delta) \\
 		&= \sqrt{\pi} \frac{\mathrm{d}^w}{\mathrm{d}\Delta^w} \exp(\frac{\Delta^2}{4}) \\
@@
 \end{equation}
-In the last line we have used the generator definition of Hermite polynomials:  $H_n(x) \equiv (-1)^n e^{x^2} \frac{\mathrm{d}^n}{\mathrm{d}x^n} e^{-x^2}$.
+In the last line we have used the generator definition of Hermite polynomials:  $H_n(x) \equiv (-1)^n e^{x^2} \frac{\mathrm{d}^n}{\mathrm{d}x^n} e^{-x^2}$.\cite{MorseFeshbach}
 
@@
 \end{equation}
-\autoref{eq:poly_solved} is not in standard polynomial form, because our summation is not singular and coefficients in our summation may have the same power. 
-Further simplifications can be made to sum to reduce recounting indices, but we do not find these simplifications essential.
+\autoref{eq:poly_solved} is not in standard polynomial form, because the summation is not singular and coefficients in the summation may have the same power. 
+Further simplifications can be made to reduce recounting indices, but we do not find these simplifications essential.
 Regardless, substituting \autoref{eq:F_solved} and \autoref{eq:poly_solved} into \autoref{eq:analytic_form}, we can now evaluate the solution as:
@@
 \end{equation}
-An alternative approach has been introduced by Kundu \textit{et al}, which yields effectively identical results. \cite{Kundu2022}
 
 \subsection{Evaluating Herzberg Teller terms for HDFG}
-When starting from $\ket{0}$,
+When evaluating Herzberg-Teller integrals involving $\ket{0}$,
 \begin{equation}
@@
 
-Similarly, when starting from $\ket{1}$, 
+Similarly, when evaluating Herzberg-Teller integrals involving $\ket{1}$, 
 \begin{equation}
@@
 
-These integrals, along with some relevant Franck-Condon factors, are plotted below as a function of offset.
+These integrals, along with some relevant Franck-Condon factors, are plotted in \autoref{fig:fcht} as a function of offset.
 
@@
 Inspection of the $A,B$ terms in the main text show that the HDFG output is dependent upon the relative size of products of Franck-Condon and Herzberg-Teller integrals.
-For clarity, we plot the relevant product factors to assist in understanding the impact of offset on the HDFG spectra.
+For clarity, we plot the relevant product factors to assist in understanding the impact of offset on the HDFG spectra (\autoref{fig:fcht_product}).
+These plots highlight the important distinction that $B$ term contributions to HDFG can dominate in the limit of small offset.
+This is expected, as when $\Delta \rightarrow 0$, the overlap integral, \autoref{key}, returns typical harmonic oscillator selection rules.
 
@@
 	\centering
-	\includegraphics[width=6.675in]{figures/fcht_product.png}
+	\includegraphics[width=6.675in]{figures/fchtproduct.png}
 	\caption{Products of Franck-Condon and Herzberg-Teller integrals relevant to the $A, B_1, B_2$ terms in this manuscript as a function of offset, $\Delta$.} 
@@
 
-These plots highlight the important distinction that $B$ term contributions to HDFG can dominate in the limit of small offset.
-This is expected, as when $\Delta \rightarrow 0$, the overlap integral \autoref{key} resolves into the typical harmonic oscillator selection rules.
+In the main text, the potential well offset ($\Delta$) was taken as $\Delta = 0.5$.
+Here, we vary $\Delta$ to investigate its impact on the structure of the $\abs{A+B}$ spectrum.
+The dependence of relevant Franck-Condon factors and Herzberg-Teller factors on displacement are plotted in \autoref{fig:fcht} as a function of offset, $\Delta$.
+\autoref{fig:fcht} shows how different displacements, vibrational frequencies, and vibronic linewidths will alter the vibronic spectrum.
+The products of Franck-Condon and Herzberg-Teller integrals relevant to the $A,B$ coefficents discussed in the main text are plotted in \autoref{fig:fcht_product}.
+
+\pagebreak
+
+It is clear from \autoref{fig:fcht_product} that the HDFG spectrum will have a significant dependence upon $\Delta$, even for small deviations from complete overlap. 
+To this end, we plot the impact of resonance frequency and offset on the HDFG spectrum \autoref{fig:chgdelta}, using values reported by Myers et al. and Brennan et al. \cite{Myers1982, Brennan2024}
+In this section, we take $\omega_{eg}$ = $37340$ cm$^{-1}$ and vary the offset ($\Delta$), vibrational frequency ($\omega_{g1,g0}$), and linewidth ($\Gamma$) as noted in the figure.
 
@@
 
-\pagebreak
-
-In the main text, the potential well offset ($\Delta$) was taken as $\Delta = 0.5$.
-Here, we vary $\Delta$ to investigate its impact on the structure of the $\abs{A+B}$ spectrum.
-The dependence of relevant Franck-Condon factors and Herzberg-Teller factors on displacement are plotted in \autoref{fig:fcht} as a function of offset, $\Delta$.
-\autoref{fig:fcht} shows how different displacements, vibrational frequencies, and vibronic linewidths will alter the vibronic spectrum.
-
-It is clear from \autoref{fig:fcht} that the HDFG spectrum will have a significant dependence upon $\Delta$, even for small deviations from complete overlap. 
-To this end, we plot the impact of resonance frequency and offset on the HDFG spectrum \autoref{fig:chgdelta}, using values reported by Myers et al. and Brennan et al. \cite{Myers1982, Brennan2024}
-In this section, we take $\omega_{eg}$ = $37340$ cm$^{-1}$ and vary the offset ($\Delta$), vibrational frequency ($\omega_{g1,g0}$), and linewidth ($\Gamma$) as noted in the figure.
-
-\pagebreak
+%todo: plot impact of different A,B on output.
 

### 2024-09-30 si.tex
edits

@@
 Here, $p,q$ are the dimensionless conjugate normal mode coordinates, $\hbar\omega_{eg}$ is the energy difference between $H_e$ and $H_g$, and $\Delta$ is the dimensionless offset of the excited state surface relative to the ground state.
-The Hamiltonians are the well-known quantum harmonic oscillator, and their position space wavefunctions are
+The Hamiltonians are quantum harmonic oscillators.
+The solutions to the harmonic oscillator Hamiltonian are well known, and their position space wavefunctions are
 \begin{equation}
@@
 The vibrational coupling integrals are written assuming the expansion of the dipole moment is taken about the equilibirum point of the ground state geometry ($q=0$), as is done in the main text.
+Note that in the limit $\Delta \rightarrow 0$, typical harmonic oscillator selection rules are restored, as the two wells have the same vibrational Hamiltonian and thus share an identical subspace of orthonormal eigenstates.
 
@@
 To this end, we plot the impact of resonance frequency and offset on the HDFG spectrum \autoref{fig:chgdelta}, using values reported by Myers et al. and Brennan et al. \cite{Myers1982, Brennan2024}
-In this section, we take $\omega_{eg}$ = $37340$ cm$^{-1}$ and vary the offset ($\Delta$), vibrational frequency ($\omega_{g1,g0}$), and linewidth ($\Gamma$) as noted in the figure.
+In this section, we take $\omega_{eg}$ = $30000$ cm$^{-1}$ and vary the offset ($\Delta$), vibrational frequency ($\omega_{g1,g0}$), and linewidth ($\Gamma$) as noted in the figure.
 
@@
 Parameters for (a,b) follow from Myers et al., whereas parameters for (c,d) follow from Brennan et al.\cite{Myers1982, Brennan2024}
-	Note that in these plots, the ratio $\abs{A/B} = 0.1$ is enforced} 
+	Note that in these plots, the ratio $\abs{A/B} = 0.1$ is enforced.} 
 	\label{fig:chgdelta}
@@
 
-%todo: plot impact of different A,B on output.
+In addition to the linewidth and offset impacting the shape of the HDFG response, the sign of the molecular parameters $M^{ge}_0, \Lambda^{ge}_0, \frac{\partial M^{ge}}{\partial Q} , \frac{\partial \Lambda^{ge}}{\partial Q}$ will significantly impact the HDFG spectrum.
+As discussed in the main text, the atypical lineshape in the post-resonance region of the HDFG region arises due to the sign of all four aforementioned parameters being identical.
+Changing the sign of one (or three) parameters will change the sign of $A, B$ and eliminate interference between the real and imaginary terms.  
+As an example, we demonstrate the resultant HDFG spectrum when $M_0^{ge} < 0$, and all other terms $>0$ (\autoref{fig:chgsign}).
+Compared to Figure 3 of the main text, the contributions from the $A, B_1$ and $B_2$ terms to $\Re(\gamma)$ and $\Im(\gamma)$ significantly change.
+In particular, $\Re(\gamma)$ and $\Im(\gamma)$ are of similar value in the post-resonance region, eliminating the interference seen in Figure 3 of the main text.
+
+\begin{figure}[!htbp]
+	\centering
+	\includegraphics[width=6.675in]{figures/drsive_chgsign.png}
+	\caption{Contributions of $A, B$ to HDFG spectrum for a simple two harmonic well system, identical to the main text, except $M_0^{ge} < 0$.
+		(a) Potential energy surfaces for a two-well system, (b) 1D HDFG spectrum for $\Delta = 0.5$, $\omega_1 = \omega_{g1, g0}$, (c, d) real and imaginary parts of terms plotted in (b), respectively.
+		The spectra are referenced to $\max{(A+B)}$. 
+		The vibronic one and two photon absorption operators are scaled such that $\abs{B}/\abs{A} \sim$ 0.1, following Chung and Ziegler. \cite{Ziegler1988}
+} 
+	\label{fig:chgsign}
+\end{figure}
 
@@
 is evaluated for $c=-1$ (electronic state and vibrational state energy fluctuations are anti-correlated) and $c=1$ (electronic state and vibrational state energy fluctuations are correlated).
+Integrals such as those found in \autoref{generalcontour} can be evaluated by using the Residue theorem. %@dan i had too much white space, needed something to fill in... delete if you want.
+If a complex valued function $f(z)$ is integrated along a positively oriented closed contour,%guessing on this one
+\begin{subequations}\label{eq:generalcontour}
+	\begin{equation}
+		\oint \mathrm{d}z f(z) = 2\pi i \sum_k \Res[f(z_k)]
+	\end{equation}
+where the residue of an n$^{\text{th}}$ order pole at $z = z_k$, $\Res[f(z_k)]$ is evaluated as
+	\begin{equation}
+		\Res[f(z_k)] = \lim_{z \rightarrow z_k} \frac{1}{\left(n-1\right)!} \frac{\mathrm{d}^{n-1}}{\mathrm{d}z^{n-1}} \left[f(z) (z-z_k) \right]
+	\end{equation}
+For first order poles (the cases considered below), $n=1$, so that 
+	\begin{equation}
+		\oint \mathrm{d}z f(z) = 2\pi i \sum_k \lim_{z \rightarrow z_k} f(z) (z-z_k)
+	\end{equation}
+\end{subequations}
+Note that in \autoref{eq:generalcontour}, the integrals are closed along a contour which wraps all the poles.
 
@@
 The contour that wraps the upper half of the complex plane has only one pole, $i \sigma$; as such, we choose to evaluate \autoref{generalcontour} in the upper half of the complex plane for the case of anti-correlated modes, as it contains the least number of poles.
-Using the residue theorem, we see
+Using the residue theorem for a first order pole,\cite{Carlson1990line} we see
 \begin{widetext}
@@
 We choose to evaluate along the contour in the bottom half of the complex plane (see \autoref{fig:contours}b), where the poles are $\{-i\sigma, \Delta_{ga}\}$.
-Since the $\xi_k$ are nondegenerate, we see
+Since the $\xi_k$ are nondegenerate,
 \begin{widetext}
@@
 	\includegraphics[width=6.675in]{figures/corr_contour.png}
-	\caption{Poles (blue dots) and contours (black line) used to evaluate \autoref{generalcontour} for (a) anti-correlated and (b) correlated modes.} 
+	\caption{Poles (blue dots) and contours (black lines) used to evaluate \autoref{generalcontour} for (a) anti-correlated ($c=-1$) and (b) correlated ($c=1$) modes. 
+	} 
 	\label{fig:contours}
 \end{figure}
+\break
 

### 2024-09-30 figures/2D_spec_chgparams.py

@@ -1,13 +1,6 @@
-# -*- coding: utf-8 -*-
-"""
-Created on Tue Jan 17 09:28:39 2023
-
-@author: rpm
-"""
 import numpy as np
 import WrightTools as wt
 import matplotlib.pyplot as plt 
-from matplotlib.patches import FancyArrowPatch
 import pathlib
 
 wt.artists.apply_rcparams(kind="publication")
@@ -63,8 +56,8 @@ def h10(q): #<1|Q|0>
 def h11(q): #<1|Q|1>
     return -q/2 * (-1 + q**2 / 2) * f00(q)
 
-def h12(q): #<1|Q|2>
-    return (-1/8) * (q**4 - 2*q**2 - 8) * f00(q)
+# def h12(q): #<1|Q|2>
+#     return (-1/8) * (q**4 - 2*q**2 - 8) * f00(q)
 
 def h21(q): #<2|Q|1>
     return (1/8)*(8 - 6*q**2 + q**4) * f00(q)
@@ -100,40 +93,21 @@ def B1(Mge, dLeg):
 def B2(Lge, dMgedQ):
     return dMgedQ * Lge *(h01(d) * f00(d)) * Deltaevgo(0, y, 0) + dMgedQ * Lge *(h11(d) * f10(d)) * Deltaevgo(1, y, 1) + dMgedQ * Lge *(h21(d) * f20(d)) * Deltaevgo(2, y, 2) #the v' = 2 term
 
-# #Real parts
-# totRe = A.real + B1.real + B2.real
-# ARe = A.real / totRe.max()
-# BRe = (B1+B2).real / totRe.max()
-# B1Re = B1.real / totRe.max()
-# B2Re = B2.real / totRe.max()
-
-# #Im parts
-# totIm = A.imag + B1.imag + B2.imag
-# AIm = A.imag / totIm.max()
-# BIm = (B1+B2).imag / totIm.max()
-# B1Im = B1.imag / totIm.max()
-# B2Im = B2.imag / totIm.max()
-
 
 # absolute value
 def tot(Mge, Lge, dLeg, dMgedQ):
     return np.abs(A(Mge, Lge) + B1(Mge, dLeg) + B2(dMgedQ, Lge))
-# abs_max = tot.max()
 
 #plot the A and B
 ax0 = plt.subplot(gs[0,0])
[…]

### 2024-09-30 figures/2D_spec_chgsign.py

@@ -1,9 +1,3 @@
-# -*- coding: utf-8 -*-
-"""
-Created on Tue Jan 17 09:28:39 2023
-
-@author: rpm
-"""
 import numpy as np
 import WrightTools as wt
 import matplotlib.pyplot as plt 

### 2024-09-30 figures/plotting_fcht.py

@@ -1,9 +1,3 @@
-# -*- coding: utf-8 -*-
-"""
-Created on Tue Jan 17 09:28:39 2023
-
-@author: rpm
-"""
 import numpy as np
 import WrightTools as wt
 import matplotlib.pyplot as plt
@@ -74,13 +68,13 @@ def h20(q): #<2|Q|0>
 #plot
 fig, gs = wt.artists.create_figure(width="dissertation", nrows=2, cols=cols, aspects=aspects, wspace=1) 
 ax0 = plt.subplot(gs[0,0])
-ax0.plot(d, f00(d), linewidth = '2', label = r'$\mathsf{\langle\tilde{0}|0\rangle}$', color = 'black', zorder = 4)
-ax0.plot(d, f01(d), linewidth = '2', label = r'$\mathsf{\langle\tilde{0}|1\rangle}$', color = 'pink', zorder = 3)
-ax0.plot(d, f10(d), linewidth = '2', label = r'$\mathsf{\langle\tilde{1}|0\rangle}$', color = 'cyan', zorder = 3)
-ax0.plot(d, f11(d), linewidth = '2', label = r'$\mathsf{\langle\tilde{1}|1\rangle}$', color = 'red', zorder = 2)
+ax0.plot(d, f00(d), linewidth = '2', label = r'$\mathsf{\langle\tilde{0}|0\rangle}$', zorder = 4)
+ax0.plot(d, f01(d), linewidth = '2', label = r'$\mathsf{\langle\tilde{0}|1\rangle}$', zorder = 3)
+ax0.plot(d, f10(d), linewidth = '2', label = r'$\mathsf{\langle\tilde{1}|0\rangle}$', zorder = 3)
+ax0.plot(d, f11(d), linewidth = '2', label = r'$\mathsf{\langle\tilde{1}|1\rangle}$', zorder = 2)
 # ax0.plot(d, f02(d), linewidth = '2', label = r'$\mathsf{02}$', color = 'green', zorder = 1)
-ax0.plot(d, f20(d), linewidth = '2', label = r'$\mathsf{\langle\tilde{2}|0\rangle}$', color = 'orange', zorder = 1)
-ax0.plot(d, f21(d), linewidth = '2', label = r'$\mathsf{\langle\tilde{2}|1\rangle}$', color = 'green', zorder = 1)
[…]

### 2024-09-30 paper.tex

@@
 \usepackage{dcolumn}
+\usepackage{bm}
+%\usepackage{times}
+\usepackage{etoolbox}
 \usepackage[colorlinks=true, linkcolor=black, urlcolor=blue, citecolor=black, anchorcolor=black]{hyperref}
+
+\usepackage{lineno}
+\linenumbers
 
@@
 CMDS methods partially mitigate this issue because emission is spatially coherent so that all emission is directional and easily collected.
-In fact, hyper-Raman transitions have been observed in several CMDS studies (sometimes under the moniker of SIVE).\cite{Zilian1994, RN350, RN416, RN351, RN352, RN353, Chen1998, RN362, RN418, Wang2021, Bonn2024, McDonnell2024}
+In fact, hyper-Raman transitions have been observed in several CMDS studies (sometimes under the moniker of SIVE).\cite{Zilian1994, RN350, RN351, RN352, RN353, Chen1998, RN362, RN418, Wang2021, Bonn2024, McDonnell2024}
 
@@
 HDFG, HSFG and Raman are more direct probes of electronic-vibrational coupling.
-Notably, HDFG and HSFG can be implemented as two-color experiments (with $\omega_2=\omega_3$);\cite{Cho2001} vibrational sum frequency generation (vSFG) or difference frequency generation (vDFG) setups can be trivially reconfigured to perform HSFG or HDFG measurements, respectively, to investigate ev coupling in bulk systems.
+Notably, HDFG and HSFG can be implemented as two-color experiments (with $\omega_2=\omega_3$);\cite{Cho2001} vibrational sum frequency generation (vSFG) or difference frequency generation (vDFG) setups can be trivially reconfigured to perform HSFG or HDFG measurements to investigate ev coupling in bulk systems.
 
@@
 The Rao group has also developed a $\chi^{(4)}$ analogue of 2D-EV, 2D-EV sum frequency generation (2D-EVSFG), to probe interfacial e-v coupling. \cite{Deng2021}  
-These methods have been used to understand vibronic coupling in a variety of molecular systems and, albeit different selection rules, serve as 2D pump-probe type analogues to the hyper-Raman-based spectroscopies discussed here.\cite{Courtney2015, Gaynor2018, Arsenault2020, HuangFu2023}
+These methods have been used to understand vibronic coupling in a variety of molecular systems and, albeit different selection rules, serve as 2D pump-probe type analogues to the infrared-hyper-Raman spectroscopies discussed here.
 
@@
 In this section, we investigate the properties of HDFG and make the connections between HDFG and hyper-Raman scattering explicit.
-Coherent spectroscopies are often described using the density matrix formalism, where an n$^{th}$ order density matrix $\rho^{(n)}$ is propagated using the Liouville-von Neumann equation $via$
+Coherent spectroscopies are often described using the density matrix formalism, where an n$^{\text{th}}$ order density matrix $\rho^{(n)}$ is propagated using the Liouville-von Neumann equation $via$
 \begin{equation}\label{LVNE}
@@
 It is useful to briefly discuss the impact of time ordering on HDFG output.
-Dependent upon the time-ordering schemes, it is possible to eliminate output through destructive interference.\cite{RN287}
+Dependent upon the time-ordering schemes, it is possible to eliminate output through destructive interference.\cite{Cho2008}
 While we have only isolated one specific HDFG resonance and time-ordering scheme (\autoref{fig:comparisonwmel}), there are several other pathways which can provide HDFG output. \cite{RN352}
@@
 Conversely, in the case where only $\omega_2$ is vibrationally resonant, diagrams (c,d) and (e,f), when detuned from an electronic resonance, have identical transition moments but opposite phase. 
-As a result, the output from (c,d) and (e,f) completely destructively interfere; no signal can be obtained from these pathways when significantly detuned. \cite{RN287, McDonnell2024}
+As a result, the output from (c,d) and (e,f) completely destructively interfere; no signal can be obtained from these pathways when significantly detuned. \cite{McDonnell2024}
 Note that in the case where $\omega_1$ interacts first but $\omega_2$ is resonant, the nonlinear output generated nearly vanishes as the first resonant pulse arrives after a non-resonant pulse.
@@
 
-Another potential interferant in HDFG spectroscopy is direct and sequential cascades of second-order vDFG and vSFG processes.\cite{RN297, RN301}
+Other potential interferants in HDFG spectroscopy are direct and sequential cascades of second-order vDFG and vSFG processes.\cite{RN297, Cho2000_Cascade, RN301}
 While unimportant in achiral isotropic systems,\cite{Belkin2000} second-order cascades may become important in media where SFG and DFG are allowed, e.g.
@@
 \end{widetext}
+It is assumed that all derivatives above are evaluated at $Q_z = 0$.
 Note that it is common in the hyper-Raman literature to write $\Delta_{e\tilde{v}', gv} \Delta_{mn, gv} = \Delta_{e\tilde{v}', gv}$.
@@
 
-To understand the vibronic structure of electronic resonance, we restrict consideration to electronic transitions between $|g)$ and $|e)$.  
+To understand the vibronic structure of an excited state $|e)$, we restrict consideration to electronic transitions between $|g)$ and $|e)$.  
 Note that HDFG experiments selectively excite ground state vibrational modes through $\omega_1$; we will assume the IR beam has excited the fundamental of an IR-active mode, $\ket{g,1}$, so that hyper-Raman scattering is between ground state and $\ket{g,1}$.
@@
 		\begin{equation}
-			\begin{split}
 				A_{ijk} = \frac{1}{\hbar}\sum_{\tilde{v}'} M^{ge}_{0,i} 
@@
 				\frac{1}{\Delta_{e\tilde{v}',gv}}
-				\\
-			\end{split}
 		\end{equation}
 		\begin{equation}
-			\begin{split}
-				B_{1_{ijk}} &= \frac{1}{\hbar} \sum_{\tilde{v}'} M^{ge}_{0,i}
+				B_{1_{ijk}} = \frac{1}{\hbar} \sum_{\tilde{v}'} M^{ge}_{0,i}
 				\frac{\partial \Lambda^{eg}_{jk}}{\partial Q} \langle 1 | \tilde{v}' \rangle \mel{\tilde{v}'}{Q}{0} 
-				\frac{1}{\Delta_{e\tilde{v}', gv}}\\
-			\end{split}
+				\frac{1}{\Delta_{e\tilde{v}', gv}}
 		\end{equation}
 		\begin{equation}
-			\begin{split}
 				B_{2_{ijk}} = \frac{1}{\hbar} \sum_{\tilde{v}'} \frac{\partial M^{ge}_{i}}{\partial Q} 
@@
 				\frac{1}{\Delta_{e\tilde{v}',gv}}
-			\end{split}
 		\end{equation}
 	\end{subequations}
-where $\Lambda^{ab}_{ij} = 1/\hbar \sum_m M_i^{am}M_j^{mb} $ is the electronic two photon transition moment between $|a)$ and $|b)$.\cite{McClain1977}
+where $\Lambda^{ab}_{ij} = 1/\hbar \sum_m M_i^{am}M_j^{mb} $ is the electronic two photon transition moment between $|a)$ and $|b)$.
 
@@
 \end{figure*}
+
+It is important to realize that these expansions are taken about the equilibrium point of the ground state surface, i.e., $Q = 0$.
+Some recent studies investigating interference between Franck-Condon and Herzberg-Teller terms in absorption and emission spectra have found it useful to Taylor expand about the midpoint of the equilibria points of the ground and excited surface.\cite{Kundu2022}
+If such a definition was used here, $B$ would possess non-negligible Franck-Condon character.
+As such, it is more useful to assign Herzberg-Teller character to the $B$ term due to the presence of $\frac {\partial M^{ge}}{\partial Q}$ and $\frac {\partial \Lambda^{ge}}{\partial Q} $ terms.
+Nevertheless, since the molecular response must be invariant to the center point of the Taylor expansion, expanding about $Q = 0$ or the midpoint should provide similar results; if the dipole surface has a kink or node about $Q = 0$, then the midpoint would be a better choice for understanding Herzberg-Teller contributions to the spectra.
 
@@
 Some $B$ terms do survive in the same limit, however; for instance, $B_1$ survives for $\tilde{v}'=1$ and $B_2$ survives for $\tilde{v}'=0$.
-In the absence of an $A$ term, the $B$ terms will dominate.
+In the absence of an $A$ term, the $B$ terms will significantly dominate.
 The $B_1$ and $B_2$ terms involve different types of vibronic coupling pathways.
@@
 A sample calculation is provided in the supporting information.}
+For small $\Delta$ values, it is clear by comparing the relative Franck-Condon and Herzberg-Teller integral products that $B$ term resonances can dominate the spectrum (Figure S2).
+Similar ideas have been observed in resonance hyper-Raman spectra, which makes HDFG a sensitive probe of non-Condon effects for those modes with small $\Delta$ values.
 
@@
 Significant contributions from $\ket{e,0}$ and $\ket{e,1}$ in the $A$ term spectrum correspond well with expectations given the relative wavefunction overlap in \autoref{fig:doubres_spec}a, tabulated in \autoref{T:contributions}.
+The overlaps are plotted as function of offset in Figure S2.
 Similarly, the $B_1$ term is dominated by coupling with the $\ket{e,1}$ state and $B_2$ is dominated by coupling with the $\ket{e,0}$ state (\autoref{T:contributions}). 
@@
 
-Since $\Delta$ can take on a variety of values given a specific system, in the supporting information we demonstrate the impact of $\Delta$ on the HDFG response using previously reported values for some Raman active vibrations in \textit{trans}-hexatriene and UiO-68 metal organic frameworks (Figure S2).
+Since $\Delta$ can take on a variety of values given a specific system, in the supporting information we demonstrate the impact of $\Delta$ on the HDFG response using previously reported values (Figure S3).
 \cite{Myers1982, Brennan2024}
-Clearly, specific $\Delta$ and $\omega_{g1, g0}$ values have a significant impact on the HDFG spectral profile.
-Indeed, for some values of $\Delta$, it appears that $B$ term resonances dominate over $A$ term resonances, which can allow for significant non-Condon behavior in pre-resonant HDFG response.
+Clearly, $\Delta$, $\omega_{g1, g0}$ and $\Gamma$ have a significant impact on the HDFG spectral profile.
+Indeed, for some values of $\Delta$, it appears that $B$ term resonances dominate over $A$ term resonances (see also Figure S2), which can allow for significant non-Condon behavior in pre-resonant HDFG response.
 
@@
 Such effects have been seen elsewhere in spontaneous, surface enhanced hyper-Raman studies. \cite{Milojevich2011}
-
-The Franck-Condon and Herzberg-Teller integrals can manipulate interference in the total output spectrum as a function of offset (Figure S2).
-When the offset is inverted about the origin ($\Delta \rightarrow -\Delta$),
-
-However, the main source of interference in the HDFG spectra arises from the sign of the molecular parameters. 
+The main source of interference in the HDFG spectra arises from the sign of the molecular parameters. 
 In the HDFG spectrum presented in \autoref{fig:doubres_spec}, the signs of all molecular parameters are taken to be positive. 
-Inverting the sign of one parameter eliminates the interference and restores the expected, purely Lorentzian lineshape.
-
-*orientational averaging
-*changing one trivially fixes interference (cf plot above)
-*in SI, put examples
+Inverting the sign of one parameter eliminates the interference and restores the expected, purely Lorentzian lineshape (Figure S4).
+It is important to note that these spectra simulate a single element of the hyperpolarizability tensor, $\gamma_{ijkl}$.
+The true HDFG response must be averaged over the molecular frame, or, the true, HDFG response is a linear combination of different $\gamma_{ijkl}$ terms.
+Nevertheless, if the resultant linear combination results in destructive interference between the $A$ and $B$ terms, it could be possible to elucidate both the amplitude and sign of $\Delta$ from a HDFG experiment.
 
@@
 
-We investigate the impact of inhomogeneity on spectral output by convolving the HDFG output hyperpolarizability $\gamma_{ijkl}(\xi)$ with a normalized Lorentzian distribution $P(\xi)$ of half width $\sigma$ as \cite{Desiderio1979, Dick83_1, Carlson1990line}
+We investigate the impact of inhomogeneity on spectral output by convolving the HDFG output hyperpolarizability $\gamma_{ijkl}(\xi)$ with a normalized Lorentzian distribution $P(\xi)$ of half width $\sigma$ as \cite{Desiderio1979}
 \begin{equation}\label{contour}
@@
 where $\eta_{ijkl}$ contains all values in \autoref{drgamma_notaylor} not dependent upon $\xi$.
-While Gaussian distributions are commonly used as a phenomenological description of inhomogeneous broadening, Lorentzian distributions have successfully described inhomogeneous broadening in a variety of spectroscopies and yield easily interpretable closed-form solutions.
-\cite{Desiderio1979, Dick83_1, Carlson1990line, RN410}
+While Gaussian distributions are commonly used as a phenomenological description of inhomogeneous broadening, Lorentzian distributions have successfully described inhomogeneous broadening in many coherent spectroscopies and yield easily interpretable closed-form solutions.
+\cite{Dick83_1, Carlson1990line, RN410, Yurs2012}
 
 Evaluating \autoref{contour} for the HDFG pathway above shows\footnote{See the supporting information for more details.} 
-
+\begin{subequations}
 \begin{equation}\label{linenarrowa}
@@
 \end{equation}
+\end{subequations}
 for anti-correlated ($c = -1$) states.
@@
 
-Although \autoref{linenarrowa} identifies that parametric HDFG line-narrows correlated modes, these results are only valid in limits where the input pulses only weakly populate excited states.
+Although \autoref{linenarrowa} identifies that parametric HDFG line-narrows correlated modes, these results are only valid in limits where the input pulses weakly populate excited states.
 When resonant pulses are significantly longer than the dephasing time of some state, then that state can become populated.
@@
 For simplicity, we take $\rho_{gg} = 1$.
-Orientational averaging shows specific polarization schemes isolate linear combinations of different $\beta_{ijk}$ terms. \cite{Bersohn1966, Willetts1992, Kauranen1996}
+Orientational averaging shows specific polarization schemes isolate linear combinations of different $\beta_{ijk}$ terms. \cite{Bersohn1966, Kauranen1996}
 Substituting in \autoref{SIVEselection}, we see
@@
 
-Since $\abs{\partial \mu_l / \partial Q}$ values can be extracted from FT-IR spectra and $\chi^{(3)}$ can be extracted through the Bloembergen interferometry experiment,\cite{Levenson1974_1, Levenson1974_2, RN459} HDFG can give quantitative information on the magnitude of $\beta_{ijk}$ for infrared active vibrations.
+Since $\abs{\partial \mu_l / \partial Q}$ values can be extracted from FT-IR spectra and $\chi^{(3)}$ can be extracted through the Bloembergen interferometry experiment,\cite{Levenson1974_1, Levenson1974_2, RN459} HDFG can give quantitative information on the magnitude of $\frac{\partial \beta_{ijk}}{\partial Q}$ for infrared active vibrations.
 Additionally, by using non-degenerate input frequencies to stimulate the hyper-Raman transition, the asymmetric properties of $\beta_{ijk}$ can be examined and quantified.
@@
 Laboratories which use vSFG to investigate interfacial species at buried interfaces thus have the ingredients necessary to perform a HDFG experiment in a transmission geometry. \cite{Piontek2023_1}
-This method provides vSFG practitioners the ability to measure spectra and dephasing dynamics in isotropic media without many meaningful changes in their optical setup, and thus compare spectroscopy and dephasing in the bulk and at the interface.\cite{RN224}
+This method provides vSFG practitioners the ability to measure spectra and dephasing dynamics in isotropic media without many meaningful changes in their optical setup, and thus compare spectroscopy and dephasing in the bulk and at the interface.
 

### 2024-09-30 paper.tex
subtle changes
Added the paper as submitted July 30 to prep for diff

Added widetext / table* where needed

Tried to make all FC things listed as 'Franck Condon factors' and HT things listed as 'Herzberg-Teller integrals'

@@
 		The vibronic one and two photon absorption operators are scaled such that $\abs{B}/\abs{A} \sim$ 0.1, following Chung and Ziegler. \cite{Ziegler1988}
-		The Franck-Condon and Herzberg-Teller contributions to each of these terms are found in \autoref{T:contributions}.}
+		The Franck-Condon factor and Herzberg-Teller integral contributions to each of these terms are found in \autoref{T:contributions}.}
 	\label{fig:doubres_spec}
@@
 
-\begin{table}[!htbp]
+\begin{table*}[!htbp]
 	\caption{\label{T:contributions} Franck-Condon and/or Herzberg-Teller contributions to $A$, $B_1$, $B_2$ terms between $\ket{g,0}$, $\ket{g,1}$ and vibronic states $\ket{e,\tilde{0}}$, $\ket{e,\tilde{1}}$, $\ket{e,\tilde{2}}$ for \autoref{Hamiltonian} with an offset $\Delta = 0.5$.
 	The bra and ket labels are written according to their order in $A$, $B_1$, $B_2$ as written in \autoref{ABterms_DR}.
-	The Franck-Condon and Herzberg-Teller integral products tabulated here are plotted in the Supporting Information (Figure S2) as a function of $\Delta$.}
+	The Franck-Condon factor and Herzberg-Teller integral products tabulated here are plotted in the Supporting Information (Figure S2) as a function of $\Delta$.}
 	\begin{ruledtabular}
@@
 	\end{ruledtabular}
-\end{table}
+\end{table*}
 
@@
 This arises due to interference between the real and imaginary parts of $\gamma$ (\autoref{fig:doubres_spec}c, d).
-The abnormal lineshape arises due to the sign of the Franck-Condon and Herzberg-Teller integrals, as well as the molecular parameters that drive the output of the vibronic transitions.
+The abnormal lineshape arises due to the sign of the Franck-Condon factor and Herzberg-Teller integrals, as well as the molecular parameters that drive the output of the vibronic transitions.
 Such effects have been seen elsewhere in spontaneous, surface enhanced hyper-Raman studies. \cite{Milojevich2011}
@@
 We investigate the impact of inhomogeneity on spectral output by convolving the HDFG output hyperpolarizability $\gamma_{ijkl}(\xi)$ with a normalized Lorentzian distribution $P(\xi)$ of half width $\sigma$ as \cite{Desiderio1979}
+\begin{widetext}
 \begin{equation}\label{contour}
@@
 \end{equation} 
+\end{widetext}
 where $\eta_{ijkl}$ contains all values in \autoref{drgamma_notaylor} not dependent upon $\xi$.

### 2024-09-30 si.tex
subtle changes
Added the paper as submitted July 30 to prep for diff

Added widetext / table* where needed

Tried to make all FC things listed as 'Franck Condon factors' and HT things listed as 'Herzberg-Teller integrals'

@@
 \end{equation}
-The integral corresponds to Franck-Condon factors for $k=0$ and Herzberg-Teller matrix elements for $k=1$.
+The integral corresponds to Franck-Condon factors for $k=0$ and Herzberg-Teller integrals for $k=1$.
 The vibrational coupling integrals are written assuming the expansion of the dipole moment is taken about the equilibirum point of the ground state geometry ($q=0$), as is done in the main text.
-Note that in the limit $\Delta \rightarrow 0$, typical harmonic oscillator selection rules are restored, as the two wells have the same vibrational Hamiltonian and thus share an identical subspace of orthonormal eigenstates.
+Note that in the limit $\Delta \rightarrow 0$, typical harmonic oscillator selection rules are restored, as the two wells have the same vibrational Hamiltonian and thus share a subspace of orthonormal eigenstates.
 
@@
 \section{Impact of displacement, resonance frequencies, vibronic linewidth and molecular parameters on HDFG Spectra}
-Inspection of the $A,B$ terms in the main text show that the HDFG output is dependent upon the relative size of products of Franck-Condon and Herzberg-Teller integrals.
+Inspection of the $A,B$ terms in the main text show that the HDFG output is dependent upon the relative size of products of Franck-Condon factors and Herzberg-Teller integrals.
 For clarity, we plot the relevant product factors to assist in understanding the impact of offset on the HDFG spectra (\autoref{fig:fcht_product}).
@@
 	\includegraphics[width=6.675in]{figures/fchtproduct.png}
-	\caption{Products of Franck-Condon and Herzberg-Teller integrals relevant to the $A, B_1, B_2$ terms in this manuscript as a function of offset, $\Delta$.} 
+	\caption{Products of Franck-Condon factors and Herzberg-Teller integrals relevant to the $A, B_1, B_2$ terms in this manuscript as a function of offset, $\Delta$.} 
 	\label{fig:fcht_product}
@@
 Here, we vary $\Delta$ to investigate its impact on the structure of the $\abs{A+B}$ spectrum.
-The dependence of relevant Franck-Condon factors and Herzberg-Teller factors on displacement are plotted in \autoref{fig:fcht} as a function of offset, $\Delta$.
+The dependence of relevant Franck-Condon factors and Herzberg-Teller integrals on displacement are plotted in \autoref{fig:fcht} as a function of offset, $\Delta$.
 \autoref{fig:fcht} shows how different displacements, vibrational frequencies, and vibronic linewidths will alter the vibronic spectrum.
-The products of Franck-Condon and Herzberg-Teller integrals relevant to the $A,B$ coefficents discussed in the main text are plotted in \autoref{fig:fcht_product}.
+The products of Franck-Condon factors and Herzberg-Teller integrals relevant to the $A,B$ coefficents discussed in the main text are plotted in \autoref{fig:fcht_product}.
 
@@
 Integrals such as those found in \autoref{generalcontour} can be evaluated by using the Residue theorem. %@dan i had too much white space, needed something to fill in... delete if you want.
-If a complex valued function $f(z)$ is integrated along a positively oriented closed contour,%guessing on this one
+Recall that if a complex valued function $f(z)$ is integrated along a positively oriented closed contour,%guessing on this one
 \begin{subequations}\label{eq:generalcontour}

### 2024-09-30 paper.tex
added a word to abstract

@@
 Most of these methods rely on infrared and/or Raman transitions, but methods involving hyper-Raman transitions are also possible. 
-Hyper Difference Frequency Generation (HDFG) spectroscopy is an underdeveloped four wave mixing vibrational spectroscopy based both infrared absorption and hyper-Raman scattering transitions. 
+Hyper Difference Frequency Generation (HDFG) spectroscopy is an underdeveloped four wave mixing vibrational spectroscopy based upon both infrared absorption and hyper-Raman scattering transitions. 
 Despite several experimental reports on HDFG, its spectroscopic properties have not been fully explored. 

### 2024-09-30 paper.tex
first pass at fixing contour problems
pp 408 of Morse and feshbach

@@
 For simplicity, we consider only c = $\pm$1.
+To simplify discussion below, we map $\Delta_{e\tilde{v}', gv} \rightarrow \Delta_{ba}$ and $\Delta_{g0,gv} \rightarrow \Delta_{ga}$.
 
@@
 \begin{equation}\label{linenarrowa}
-	\gamma_{ijkl} = \frac{- \eta_{ijkl}}{\Delta_{ga}+ i \sigma} \left( \frac{1}{\Delta_{ba}-i \sigma} + \frac{2 i \sigma}{\Delta_{ga}-i \sigma} \frac{1}{\Delta_{ba} + \Delta_{ga}} \right)
+	\gamma_{ijkl} = \frac{\eta_{ijkl}}{\Delta_{ba} + i \sigma} \left(\frac{1}{\Delta_{ga} - i \sigma} + \frac{2i\sigma}{(\Delta_{ba} - i \sigma)(\Delta_{ga} + \Delta_{ba})}\right)
 \end{equation}

### 2024-09-30 si.tex
first pass at fixing contour problems
pp 408 of Morse and feshbach

@@
 \autoref{fig:fcht} shows how different displacements, vibrational frequencies, and vibronic linewidths will alter the vibronic spectrum.
-The products of Franck-Condon factors and Herzberg-Teller integrals relevant to the $A,B$ coefficents discussed in the main text are plotted in \autoref{fig:fcht_product}.
+The products of Franck-Condon factors and Herzberg-Teller integrals relevant to the $A,B$ coefficients discussed in the main text are plotted in \autoref{fig:fcht_product}.
 
@@
 Integrals such as those found in \autoref{generalcontour} can be evaluated by using the Residue theorem. %@dan i had too much white space, needed something to fill in... delete if you want.
-Recall that if a complex valued function $f(z)$ is integrated along a positively oriented closed contour,%guessing on this one
+Recall that if an analytic, complex valued function $f(z)$ is integrated along a positively oriented closed contour,%guessing on this one
 \begin{subequations}\label{eq:generalcontour}
@@
 Note that in \autoref{eq:generalcontour}, the integrals are closed along a contour which wraps all the poles. 
+In the case where the integration is only needed along the real axis, the contour can be drawn as a semicircle in the positive half of the complex plane. \cite{MorseFeshbach}
 
@@
 For anti-correlated modes ($c = -1$), the poles ($\xi_k$) are situated in the complex plane as shown in \autoref{fig:contours}a.
-Since \autoref{generalcontour} is evaluated along the real axis, one can choose to evaluate the contour in the upper or lower half of the complex plane.
-In other words, we can choose the contour which wraps around the least number of poles.
 For c = -1, there are four poles: $\pm i \sigma, \Delta_{ga}, \Delta_{ba}$. 
-The contour that wraps the upper half of the complex plane has only one pole, $i \sigma$; as such, we choose to evaluate \autoref{generalcontour} in the upper half of the complex plane for the case of anti-correlated modes, as it contains the least number of poles.
+The contour that wraps the upper half of the complex plane has only one pole, $i \sigma$
 Using the residue theorem for a first order pole,\cite{Carlson1990line} we see
@@
 For correlated modes, the poles are situated in the complex plane as shown in \autoref{fig:contours}b.
-It is clear that no matter which contour is chosen, the contour will envelop two poles.
-We choose to evaluate along the contour in the bottom half of the complex plane (see \autoref{fig:contours}b), where the poles are $\{-i\sigma, \Delta_{ga}\}$.
+We evaluate along the contour where the poles are $\{i\sigma, -\Delta_{ba}\}$.
 Since the $\xi_k$ are nondegenerate,
@@
 			\int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi) &= 2\pi i \sum_k \lim_{\xi \rightarrow \xi_k} P(\xi) \gamma_{ijkl}(\xi) (\xi - \xi_k)\\
-			&= 2\pi i \frac{\eta_{ijkl} \sigma}{\pi}  \lim_{\xi \rightarrow -i\sigma} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga} + \xi} \frac{1}{\Delta_{ba} - \xi} \left(\xi + i \sigma\right) \\
-			&+ 2\pi i \frac{\eta_{ijkl} \sigma}{\pi} \lim_{\xi \rightarrow \Delta_{ga}} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga} - \xi} \frac{1}{\Delta_{ba} - \xi} \left(\xi - \Delta_{ga}\right)\\
-			&= 2 \eta_{ijkl} i \sigma \left(\frac{1}{2 i \sigma} \frac{1}{-i \sigma - \Delta_{ga}} \frac{1}{\Delta_{ba} - i\sigma} \right) - 2\eta_{ijkl} i \sigma \left(\frac{1}{\sigma^2 + \Delta_{ga} ^2} \frac{1}{\Delta_{ga} + \Delta_{ba}} \right)\\
-			&= -\frac{\eta_{ijkl}}{\Delta_{ga} + i \sigma} \left(\frac{1}{\Delta_{ba} - i \sigma} + \frac{2i\sigma}{(\Delta_{ga} - i \sigma)(\Delta_{ga} + \Delta_{ba})}\right)\\
+			&= 2\pi i \frac{\eta_{ijkl} \sigma}{\pi}  \lim_{\xi \rightarrow i\sigma} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga} - \xi} \frac{1}{\Delta_{ba} + \xi} \left(\xi - i \sigma\right) \\
+			&+ 2\pi i \frac{\eta_{ijkl} \sigma}{\pi} \lim_{\xi \rightarrow -\Delta_{ba}} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga} - \xi} \frac{1}{\Delta_{ba} + \xi} \left(\xi + \Delta_{ba}\right)\\
+			&= 2 \eta_{ijkl} i \sigma \left(\frac{1}{2 i \sigma} \frac{1}{\Delta_{ga} - i\sigma} \frac{1}{\Delta_{ba} + i\sigma} \right) + 2\eta_{ijkl} i \sigma \left(\frac{1}{\sigma^2 + \Delta_{ba} ^2} \frac{1}{\Delta_{ga} + \Delta_{ba}} \right)\\
+			&= \frac{\eta_{ijkl}}{\Delta_{ba} + i \sigma} \left(\frac{1}{\Delta_{ga} - i \sigma} + \frac{2i\sigma}{(\Delta_{ba} - i \sigma)(\Delta_{ga} + \Delta_{ba})}\right)\\
 		\end{split}

### 2024-09-30 figures/2D_spec_chgsign.py

@@ -256,4 +256,4 @@ for i, ax in enumerate(fig.axes):
     wt.artists.corner_text("abcd"[i], ax=ax, corner = 'UL', distance = 0.25, bbox = True, fontsize = fontsize, background_alpha=0.75)
 
 if save:
-    wt.artists.savefig(here / "drsive_spectrum.png", transparent = True, bbox_inches='tight')
+    wt.artists.savefig(here / "drsive_chgsign.png", transparent = True, bbox_inches='tight')

### 2024-09-30 figures/contours.py

@@ -15,10 +15,7 @@ fontsize = 18
 
 r = 5 #radius of contour
 
-def bottomcontour(k):
-    return -1*np.sqrt(r**2 - k**2) 
-
-def topcontour(k):
+def contour(k):
     return np.sqrt(r**2 - k**2) 
 
 x = np.linspace(-r, r, 50000)
@@ -38,7 +35,7 @@ points = [0, 0, 2, 3]
 
 
 #plot it
-ax0.plot(x, topcontour(x), linewidth = '2', color = 'black')
+ax0.plot(x, contour(x), linewidth = '2', color = 'black')
 for i in [0,1,2,3]:
     ax0.scatter(points[i], poles[i], color = 'blue')
     label = [r'$\mathsf{i \sigma}$', r'$\mathsf{-i \sigma}$', r'$\mathsf{\Delta_{ga}}$', r'$\mathsf{\Delta_{ba}}$']
@@ -60,7 +57,7 @@ for i in [0,1,2,3]:
     ax1.text(points[i]+0.1, poles[i]+0.1, label[i], fontsize = 24)
 ax0.set_title('Anti-Correlated (c = -1)')
 
-ax1.plot(x,bottomcontour(x), linewidth = '2', color = 'black')
+ax1.plot(x,contour(x), linewidth = '2', color = 'black')
 ax1.set_title('Correlated (c = 1)')
 
 #beautification

### 2024-10-01 si.tex
Fixed contour integration
Made much clearer when you can use this trick.

@@
 In particular, $\Re(\gamma)$ and $\Im(\gamma)$ are of similar value in the post-resonance region, eliminating the interference seen in Figure 3 of the main text.
-
+\newpage
 \begin{figure}[!htbp]
@@
 \end{figure}
-
+\pagebreak
 \section{Evaluating impact of static inhomogeneity on HDFG output}
@@
 is evaluated for $c=-1$ (electronic state and vibrational state energy fluctuations are anti-correlated) and $c=1$ (electronic state and vibrational state energy fluctuations are correlated).
-Integrals such as those found in \autoref{generalcontour} can be evaluated by using the Residue theorem. %@dan i had too much white space, needed something to fill in... delete if you want.
-Recall that if an analytic, complex valued function $f(z)$ is integrated along a positively oriented closed contour,%guessing on this one
+
+Integrals such as \autoref{generalcontour} can be evaluated by using the Residue theorem.\cite{MorseFeshbach}
+For clarity, we briefly outline the technique.
+%@dan i had too much white space, needed something to fill in... delete if you want.
+Consider the integral
+\begin{equation}
+	\int_{-\infty}^{\infty} \mathrm{d}x f(x)
+\end{equation}
+If $\int_{-\infty}^{\infty} \mathrm{d}x f(x)$ exists %is this strict enough?
+and $f(z)$ is an analytic function, where $z$ is a complex variable, then
 \begin{subequations}\label{eq:generalcontour}
 	\begin{equation}
-		\oint \mathrm{d}z f(z) = 2\pi i \sum_k \Res[f(z_k)]
+		\int_{-\infty}^{\infty}  \mathrm{d}x f(x) = 2\pi i \sum_k \Res[f(z_k)]
 	\end{equation}
-where the residue of an n$^{\text{th}}$ order pole at $z = z_k$, $\Res[f(z_k)]$ is evaluated as
+where $\Res[f(z_k)]$ refers to the residue of $f(z)$ in the upper half of the complex plane at the pole $z_k$ and the sum is taken over all the poles, i.e., non-removable singularities, of $f(z)$.
+Note that the residue of an n$^{\text{th}}$ order pole at $z = z_k$ is evaluated as
 	\begin{equation}
-		\Res[f(z_k)] = \lim_{z \rightarrow z_k} \frac{1}{\left(n-1\right)!} \frac{\mathrm{d}^{n-1}}{\mathrm{d}z^{n-1}} \left[f(z) (z-z_k) \right]
+		\Res[f(z_k)] = \lim_{z \rightarrow z_k} \frac{1}{\left(n-1\right)!} \frac{\mathrm{d}^{n-1}}{\mathrm{d}z^{n-1}} \left[f(z) (z-z_k)^n \right]
 	\end{equation}
@@
 	\begin{equation}
-		\oint \mathrm{d}z f(z) = 2\pi i \sum_k \lim_{z \rightarrow z_k} f(z) (z-z_k)
+		\int_{-\infty}^{\infty} \mathrm{d}x f(x) = 2\pi i \sum_k \lim_{z \rightarrow z_k} f(z) (z-z_k)
 	\end{equation}
 \end{subequations}
-Note that in \autoref{eq:generalcontour}, the integrals are closed along a contour which wraps all the poles. 
-In the case where the integration is only needed along the real axis, the contour can be drawn as a semicircle in the positive half of the complex plane. \cite{MorseFeshbach}
+Note that in \autoref{eq:generalcontour}, the integrals are closed along a contour which wraps all the poles in the positive half of the complex plane.
 
@@
 \end{figure}
-\break
 

### 2024-10-01 figures/2D_spec.py
editing scripts, readme

@@ -12,11 +12,11 @@ import pathlib
 
 wt.artists.apply_rcparams(kind="publication")
 
-save = False
+save = True
 fontsize = 18
 here = pathlib.Path(__file__).resolve().parent
 
-#define harmonic wells and coordinates
+"""define harmonic wells and coordinates"""
 d = 0.5 #offset for es
 do = 0 #gs placement
 
@@ -37,6 +37,7 @@ fig, gs = wt.artists.create_figure(width="dissertation", nrows=2, cols=cols, asp
 
 ax0 = plt.subplot(gs[0,0])
 
+"""Add the arrows and other beautification efforts"""
 #hbar omega_eg arrow insert
 yarrow = [grs(0.6), es(1.3)] #where the arrows start and end
 yarrowstop = [(grs(0.6) + es(1.3))/2 - 0.06, (grs(0.6) + es(1.3))/2 + 0.06] #to put in the hbaromegaeg
@@ -71,8 +72,6 @@ for i in [0,1,2]:
     ax0.hlines(y = es(jes[i]), xmin = -jes[i]+2*d, xmax = jes[i], color = 'black', linestyle = '-', linewidth = 2) #es states
     ax0.text(jgs[i] + 0.25, grs(jgs[i])-0.03, kets[i], fontsize = 16) #labeling gs
     ax0.text(jes[i] + 0.25, es(jes[i])-0.03, kets[i], fontsize = 16) #labeling es
-# for i in [0,1,2]:
-
     
 #harmonic surface labels
 ax0.text(kg.max()+0.12, grs(kg.max())-0.05, r'$\mathsf{|g)}$', fontsize = 24)
@@ -90,7 +89,8 @@ plt.xticks(ticks = [])
 
 
 
-#define Franck-Condon factors following page 164 of Roger Carlson's thesis in terms of 'q', the offset
+"""Defining Franck Condon and Herzberg Teller integrals"""
+'''fc integrals'''
 #<a|b> == |a> is on the ES and |b> is on the GS.
 
 def f00(q): #<0|0>
@@ -114,7 +114,7 @@ def f20(q): #<2|0>
 def f21(q): #<2|1>
     return -q * (1 - q**2/4) *f00(q)
 
[…]

### 2024-10-01 figures/2D_spec_chgparams.py

@@ -1,128 +1,0 @@
-import numpy as np
-import WrightTools as wt
-import matplotlib.pyplot as plt 
-import pathlib
-
-wt.artists.apply_rcparams(kind="publication")
-
-save = False
-fontsize = 18
-here = pathlib.Path(__file__).resolve().parent
-
-#define harmonic wells and coordinates
-d = 0.5 #offset for es
-do = 0 #gs placement
-
-#make figure
-cols = [1, 1] 
-aspects = [[[0, 0], 1], [[1, 0], 1]] 
-
-fig, gs = wt.artists.create_figure(width="dissertation", nrows=2, cols=cols, aspects=aspects, hspace=0.7, wspace=1.2) 
-
-#define Franck-Condon factors following page 164 of Roger Carlson's thesis in terms of 'q', the offset
-#<a|b> == |a> is on the ES and |b> is on the GS.
-
-def f00(q): #<0|0>
-    return np.exp(-q**2/4)
-
-def f01(q): #<0|1>
-    return q/(np.sqrt(2)) * f00(q)
-
-def f10(q): #<1|0>
-    return -1*f01(q)
-
-def f11(q): #<1|1>
-    return (1 - q**2/2) *f00(q)
-
-def f02(q): #<0|2>
-    return q**2/(2*np.sqrt(2)) * f00(q)
-
-def f20(q): #<2|0>
-    return f02(q)
-   
-def f21(q): #<2|1>
-    return -q * (1 - q**2/4) *f00(q)
-
-#define Herzberg Teller overlap integrals following page 165 of Roger Carlson's thesis in terms of q
-def h00(q): #<0|Q|0>
-    return q/2 * f00(q)
-
-def h01(q): #<0|Q|1>
-    return 1/np.sqrt(2) * (1 + q**2 /2) * f00(q)
-
-def h10(q): #<1|Q|0>
-    return 1/np.sqrt(2) * (1 - q**2 /2) * f00(q)
-
-def h11(q): #<1|Q|1>
-    return -q/2 * (-1 + q**2 / 2) * f00(q)
-
-# def h12(q): #<1|Q|2>
-#     return (-1/8) * (q**4 - 2*q**2 - 8) * f00(q)
-
-def h21(q): #<2|Q|1>
[…]

### 2024-10-01 figures/2D_spec_chgsign.py

@@ -1,3 +1,9 @@
+# -*- coding: utf-8 -*-
+"""
+Created on Tue Jan 17 09:28:39 2023
+
+@author: rpm
+"""
 import numpy as np
 import WrightTools as wt
 import matplotlib.pyplot as plt 
@@ -10,7 +16,7 @@ save = False
 fontsize = 18
 here = pathlib.Path(__file__).resolve().parent
 
-#define harmonic wells and coordinates
+"""define harmonic wells and coordinates"""
 d = 0.5 #offset for es
 do = 0 #gs placement
 
@@ -31,6 +37,7 @@ fig, gs = wt.artists.create_figure(width="dissertation", nrows=2, cols=cols, asp
 
 ax0 = plt.subplot(gs[0,0])
 
+"""Add the arrows and other beautification efforts"""
 #hbar omega_eg arrow insert
 yarrow = [grs(0.6), es(1.3)] #where the arrows start and end
 yarrowstop = [(grs(0.6) + es(1.3))/2 - 0.06, (grs(0.6) + es(1.3))/2 + 0.06] #to put in the hbaromegaeg
@@ -65,8 +72,6 @@ for i in [0,1,2]:
     ax0.hlines(y = es(jes[i]), xmin = -jes[i]+2*d, xmax = jes[i], color = 'black', linestyle = '-', linewidth = 2) #es states
     ax0.text(jgs[i] + 0.25, grs(jgs[i])-0.03, kets[i], fontsize = 16) #labeling gs
     ax0.text(jes[i] + 0.25, es(jes[i])-0.03, kets[i], fontsize = 16) #labeling es
-# for i in [0,1,2]:
-
     
 #harmonic surface labels
 ax0.text(kg.max()+0.12, grs(kg.max())-0.05, r'$\mathsf{|g)}$', fontsize = 24)
@@ -84,7 +89,8 @@ plt.xticks(ticks = [])
 
 
 
-#define Franck-Condon factors following page 164 of Roger Carlson's thesis in terms of 'q', the offset
+"""Defining Franck Condon and Herzberg Teller integrals"""
+'''fc integrals'''
 #<a|b> == |a> is on the ES and |b> is on the GS.
 
 def f00(q): #<0|0>
@@ -108,7 +114,7 @@ def f20(q): #<2|0>
[…]

### 2024-10-01 figures/contours.py

@@ -10,7 +10,7 @@ import matplotlib.pyplot as plt
 
 wt.artists.apply_rcparams(kind="publication")
 
-save = False
+save = True
 fontsize = 18
 
 r = 5 #radius of contour
@@ -72,6 +72,13 @@ for ax in [ax0, ax1]:
     ax.vlines(ymin=-10, ymax =10, x = 0, color = 'grey', linestyle = '--', linewidth = 1, zorder = 1)
     ax.set_yticks(ticks = [])
     ax.set_xticks(ticks = [])
+    
+    # j = [0]
+    # for i in j:
+    #     ax.text(i-.1, contour(i)-.17, r'$\mathsf{<}$', fontsize = 24, alpha = 1, color = 'r', weight='bold')    
+    #     ax.text(i-.1, -.17, r'$\mathsf{>}$', fontsize = 24, color = 'r') 
+    
+    
 for i, ax in enumerate(fig.axes):
     wt.artists.corner_text("abcd"[i], ax=ax, corner = 'UL', distance = 0.2, bbox = True, fontsize = fontsize, background_alpha=0.75)
 

### 2024-10-01 figures/plotting_fcht.py

@@ -17,11 +17,8 @@ cols = [1, 1]
 aspects = [[[0, 0], 1], [[1, 0], 1]] 
 
 
-
-#todo: make an array so I can just call specific matrix element of the fc and ht factors, then do a for loop over that array, should work out well.
-
-
-#define Franck-Condon factors following page 164 of Roger Carlson's thesis in terms of 'q', the offset
+"""Defining Franck Condon and Herzberg Teller integrals"""
+'''fc integrals'''
 def f00(q): #<0|0>
     return np.exp(-q**2/4)
 
@@ -43,7 +40,7 @@ def f20(q): #<2|0>
 def f21(q): #<2|1>
     return -q * (1 - q**2/4) *f00(q)
 
-#define Herzberg Teller overlap integrals following page 165 of Roger Carlson's thesis in terms of q
+'''ht integrals'''
 def h00(q): #<0|Q|0>
     return q/2 * f00(q)
 
@@ -65,6 +62,7 @@ def h21(q): #<2|Q|1>
 def h20(q): #<2|Q|0>
     return -q/np.sqrt(2) * (1 - q**2 /4) * f00(q)
 
+"""Plotting the Franck Condon and Herzberg Teller integrals"""
 #plot
 fig, gs = wt.artists.create_figure(width="dissertation", nrows=2, cols=cols, aspects=aspects, wspace=1) 
 ax0 = plt.subplot(gs[0,0])
@@ -112,7 +110,7 @@ if save:
     wt.artists.savefig(here / "fcht.png", transparent = True, bbox_inches='tight')
     
     
-"""doing the products now"""
+"""Plotting the FC and HT integral products present in defintiions of A and B in the main text"""
 
 cols1 = [1, 1, 1] 
 aspects1 = [[[0, 0], 1], [[1, 0], 1], [[2, 0], 1]] 

### 2024-10-01 figures/varying_delta.py

@@ -5,7 +5,7 @@ import pathlib
 
 wt.artists.apply_rcparams(kind="publication")
 
-save = False
+save = True
 fontsize = 18
 here = pathlib.Path(__file__).resolve().parent
 
@@ -15,10 +15,10 @@ aspects = [[[0, 0], 1], [[1, 0], 1]]
 
 
 
-#todo: make an array so I can just call specific matrix element of the fc and ht factors, then do a for loop over that array, should work out well.
+"""Defining Franck Condon and Herzberg Teller integrals"""
+'''fc integrals'''
+#<a|b> == |a> is on the ES and |b> is on the GS.
 
-
-#define Franck-Condon factors following page 164 of Roger Carlson's thesis in terms of 'q', the offset
 def f00(q): #<0|0>
     return np.exp(-q**2/4)
 
@@ -40,7 +40,7 @@ def f20(q): #<2|0>
 def f21(q): #<2|1>
     return -q * (1 - q**2/4) *f00(q)
 
-#define Herzberg Teller overlap integrals following page 165 of Roger Carlson's thesis in terms of q
+'''ht integrals'''
 def h00(q): #<0|Q|0>
     return q/2 * f00(q)
 

### 2024-10-05 figures/2D_spec_chgsign.py
ensure images are saved in figures folder

@@ -12,7 +12,7 @@ import pathlib
 
 wt.artists.apply_rcparams(kind="publication")
 
-save = False
+save = True
 fontsize = 18
 here = pathlib.Path(__file__).resolve().parent
 

### 2024-10-05 figures/plotting_fcht.py

@@ -5,7 +5,7 @@ import pathlib
 
 wt.artists.apply_rcparams(kind="publication")
 
-save = False
+save = True
 fontsize =18
 here = pathlib.Path(__file__).resolve().parent
 
@@ -164,4 +164,4 @@ for i, ax in enumerate(fig1.axes):
     wt.artists.corner_text("abcd"[i], ax=ax, corner = 'UL', distance = 0.35, bbox = True, fontsize = fontsize, background_alpha=0.75)
 
 if save:
-    wt.artists.savefig("fchtproduct.png", transparent = True, bbox_inches='tight')
+    wt.artists.savefig(here / "fchtproduct.png", transparent = True, bbox_inches='tight')

### 2024-10-05 figures/wmels.py

@@ -1,6 +1,9 @@
 import matplotlib.pyplot as plt 
 from WrightTools.diagrams import WMEL
 import WrightTools as wt
+import pathlib
+
+here = pathlib.Path(__file__).resolve().parent
 
 wt.artists.apply_rcparams(kind="publication")
 
@@ -51,7 +54,7 @@ if comparisonwmel:
 
     fig.label_columns(['$\mathsf{DFG}$','$\mathsf{SFG}$','$\mathsf{Raman}$', '$\mathsf{HDFG}$', '$\mathsf{HSFG}$','$\mathsf{Hyper-Raman}$'], font_size = 9)
     
-    plt.savefig("comparisonwmel.png", bbox_inches='tight')
+    plt.savefig(here / "comparisonwmel.png", bbox_inches='tight')
 
 if hdfg:
     fig = WMEL.Artist([1,1], [0, 0.2, 0.6, 1], state_names=("$\mathsf{| g, 0\\rangle}$",
@@ -97,7 +100,7 @@ if timeorderedwmel:
 
     fig.label_columns(['$(\mathsf{c})$','$(\mathsf{d})$', '$(\mathsf{e})$', '$(\mathsf{f})$'], font_size = 9)
     # fig.label_rows(['$\mathsf{II}$'], font_size=15, text_buffer=1.5)
-    plt.savefig("timeorderedwmel.png", bbox_inches='tight')
+    wt.artists.savefig(here / "timeorderedwmel.png")
 
 if timeorderedwmel2:
     fig = WMEL.Artist([2,1], [0, 0.2, 0.6, 1], state_names=("$\mathsf{| g, 0\\rangle}$",
@@ -118,7 +121,7 @@ if timeorderedwmel2:
 
     fig.label_columns(['$(\mathsf{a})$','$(\mathsf{b})$'], font_size = 10)
     # fig.label_rows(['$\mathsf{I}$'], font_size=15, text_buffer=1.5)
-    plt.savefig("testing123.png", bbox_inches='tight')
+    plt.savefig(here / "testing123.png", bbox_inches='tight')
 
     
 if drwmel:
@@ -152,7 +155,7 @@ if drwmel:
 
     fig.label_columns(['$(\mathsf{a})$','$(\mathsf{b})$'], font_size = 10)
     fig.label_rows(['$\mathsf{I}$','$\mathsf{II}$'], font_size=15, text_buffer=1.5)
-    plt.savefig("drwmel.png", bbox_inches='tight')
[…]

### 2024-10-06 paper.tex
Update paper.tex

@@
 This approach is not used here as the expansion of $\vec{M}^{ij}$ in normal mode coordinates provides sufficient physical insight into HDFG selection rules. 
+Duschinsky rotation effects\cite{Duschinsky1937} are ignored.
 
@@
 \end{widetext}
-It is assumed that all derivatives above are evaluated at $Q_z = 0$.
 Note that it is common in the hyper-Raman literature to write $\Delta_{e\tilde{v}', gv} \Delta_{mn, gv} = \Delta_{e\tilde{v}', gv}$.
 Here, $\langle \tilde{a} | b \rangle$ and $\mel{\tilde{a}}{Q}{b}$ are Franck-Condon factors and Herzberg-Teller-type integrals, respectively.
-Duschinsky rotation effects are ignored in this discussion. \cite{Duschinsky1937}
 At this point, the expressions are valid for both electronically resonant and non-resonant cases.
@@
 
-It is important to realize that these expansions are taken about the equilibrium point of the ground state surface, i.e., $Q = 0$.
-Some recent studies investigating interference between Franck-Condon and Herzberg-Teller terms in absorption and emission spectra have found it useful to Taylor expand about the midpoint of the equilibria points of the ground and excited surface.\cite{Kundu2022}
-If such a definition was used here, $B$ would possess non-negligible Franck-Condon character.
-As such, it is more useful to assign Herzberg-Teller character to the $B$ term due to the presence of $\frac {\partial M^{ge}}{\partial Q}$ and $\frac {\partial \Lambda^{ge}}{\partial Q} $ terms.
-Nevertheless, since the molecular response must be invariant to the center point of the Taylor expansion, expanding about $Q = 0$ or the midpoint should provide similar results; if the dipole surface has a kink or node about $Q = 0$, then the midpoint would be a better choice for understanding Herzberg-Teller contributions to the spectra.
+\autoref{ABterms_DR} shows important selection rules for vibronic transitions in HDFG.
+The $A$ term is allowed whenever an electronic transition has a one- and two- photon transition moment.
+For centrosymmetric molecules, an electronic transition cannot be both one- and two- photon allowed by parity, so the $A$ term will vanish.
+This makes HDFG a unique tool for studying the electronic structure of centrosymmetric species in isotropic media, as it is sensitive to non-Condon effects.\cite{Milojevich2011, Olson2018}
+For an allowed electronic transition, the brightness of a vibronic resonance is controlled by overlap of ground and excited state vibrational wavefunctions (Franck-Condon factors).
+The $A$ term relies on excited state perturbations to the vibrational wavefunctions; if the excited electronic state is minimally offset ($\Delta \rightarrow 0$), $\langle 1 | \tilde{v}' \rangle \langle \tilde{v}' | 0 \rangle = 0$ and $A$ vanishes, as discussed in the supporting information.
+Some $B$ terms do survive in the same limit, however; for instance, $B_1$ survives for $\tilde{v}'=1$ and $B_2$ survives for $\tilde{v}'=0$.
+In the absence of an $A$ term, the $B$ terms will dominate.
 
@@
 \end{subequations}
-for the ground ($H_g$) and first excited ($H_e$) states, where $p$ (momentum) and $q$ (position) are the dimensionless conjugate coordinates of the normal mode, the A and B contributions can be evaluated using Franck-Condon and Herzberg-Teller integrals tabulated in terms of the dimensionless normal mode $q$ and offset parameter $\Delta$ (\autoref{fig:doubres_spec}a).
-System-bath interactions are neglected in this discussion.
+for the ground ($H_g$) and first excited ($H_e$) states, where $p$ is the dimensionless momentum and $q = \sqrt{\frac{\omega}{\hbar}} Q$ is the dimensionless position, the A and B contributions can be evaluated using Franck-Condon and Herzberg-Teller integrals (\autoref{fig:doubres_spec}a).
 For simplicity, we restrict consideration to $v^\prime \in \{0,1,2\}$ and take $\Delta = 0.5$.
-Note that $q = \sqrt{\frac{\omega}{\hbar}} Q$.
+
 We assume the electronic state is both one and two photon allowed.
+For this simulation, we declare the dipolar coordinate dependences:
+\begin{eqnarray}
+	M^{ge} = M^{ge}_0 (1 + 0.1 q),  \\
+	\Lambda^{ge} = \Lambda^{ge}_0 (1 + 0.1 q).
+\end{eqnarray}
+Here we expand $\vec{M}^{ij}$ about the equilibrium point of the ground state surface, $q = 0$.
+Other reasonable expansion points choices include $q=\Delta$ and $q=\Delta/2$;\cite{Kundu2022}
+so long as $\vec{M}^{ij}(q)$ is roughly linear, the choice minimally affects the total calculation of $\gamma_{ijkl}$, but it does affect the weightings of $A$ and $B$ terms, primarily through changes in $\vec{M}_0^{ij}$ and the Herzberg-Teller integrals.
+In summary, the expansion point somewhat affects the $A$ and $B$ spectra we show, but the overall spectrum $A+B$ is not affected by this choice.
 
-\autoref{ABterms_DR} shows important selection rules for vibronic transitions in HDFG.
-The $A$ term is allowed whenever an electronic transition has a one- and two- photon transition moment.
-For centrosymmetric molecules, an electronic transition cannot be both one- and two- photon allowed by parity, so the $A$ term will vanish.
-This makes HDFG a unique tool for studying the electronic structure of centrosymmetric species in isotropic media, as it is sensitive to non-Condon effects.\cite{Milojevich2011, Olson2018}
-For an allowed electronic transition, the brightness of a vibronic resonance is controlled by overlap of ground and excited state vibrational wavefunctions (Franck-Condon factors).
-The $A$ term relies on excited state perturbations to the vibrational wavefunctions; if the excited electronic state is minimally offset ($\Delta \rightarrow 0$), $\langle 1 | \tilde{v}' \rangle \langle \tilde{v}' | 0 \rangle = 0$ and $A$ vanishes, as discussed in the supporting information.
-Some $B$ terms do survive in the same limit, however; for instance, $B_1$ survives for $\tilde{v}'=1$ and $B_2$ survives for $\tilde{v}'=0$.
-In the absence of an $A$ term, the $B$ terms will significantly dominate.
-The $B_1$ and $B_2$ terms involve different types of vibronic coupling pathways.
-In $B_1$, the Herzberg-Teller coupling is associated with the two-photon absorption process, whereas in $B_2$, the Herzberg-Teller coupling is associated with one-photon emission.\footnote{Franck-Condon factors and Herzberg-Teller integrals are most easily evaluated in the position basis.
-A sample calculation is provided in the supporting information.}
-For small $\Delta$ values, it is clear by comparing the relative Franck-Condon and Herzberg-Teller integral products that $B$ term resonances can dominate the spectrum (Figure S2).
-Similar ideas have been observed in resonance hyper-Raman spectra, which makes HDFG a sensitive probe of non-Condon effects for those modes with small $\Delta$ values.
-
-\autoref{fig:doubres_spec}b shows the simulated $\omega_2+\omega_3$ spectrum for this two-well system.  The spectrum selectively probes vibronic pathways from $\ket{g,0}$ to $\ket{g,1}$.
+% DDK: careful about w_2+w_3 vs 2*w_2; do we ever state that we will use w3=w2 for this experiment?
+\autoref{fig:doubres_spec}b shows the simulated HDFG spectrum for this two-well system.  The spectrum selectively probes vibronic pathways from $\ket{g,0}$ to $\ket{g,1}$.
 In the resonant region, the $A$ and $B$ terms contain character from all three possible transitions between $\ket{g,0}$, $\ket{e,\tilde{v}'}$ and $\ket{g,1}$. 
@@
 
-Since $\Delta$ can take on a variety of values given a specific system, in the supporting information we demonstrate the impact of $\Delta$ on the HDFG response using previously reported values (Figure S3).
-\cite{Myers1982, Brennan2024}
+The value of $\Delta$ is system specific and drastically affects the HDFG spectrum.
+In the supporting information we demonstrate the impact of $\Delta$ on the HDFG response using previously reported values (Figure S3). \cite{Myers1982, Brennan2024}
 Clearly, $\Delta$, $\omega_{g1, g0}$ and $\Gamma$ have a significant impact on the HDFG spectral profile.
-Indeed, for some values of $\Delta$, it appears that $B$ term resonances dominate over $A$ term resonances (see also Figure S2), which can allow for significant non-Condon behavior in pre-resonant HDFG response.
+% DDK: we don't care whether $B$ term dominates, but if $A$ term is insufficient to describe the spectrum...
+Indeed, for some values of $\Delta$, $B$ term resonances can dominate over $A$ term resonances (see also Figure S2), which can allow for significant non-Condon behavior in pre-resonant HDFG response.
 
-In the post-resonance region, the amplitude takes on an unexpected lineshape.
-This arises due to interference between the real and imaginary parts of $\gamma$ (\autoref{fig:doubres_spec}c, d).
-The abnormal lineshape arises due to the sign of the Franck-Condon factor and Herzberg-Teller integrals, as well as the molecular parameters that drive the output of the vibronic transitions.
-Such effects have been seen elsewhere in spontaneous, surface enhanced hyper-Raman studies. \cite{Milojevich2011}
-The main source of interference in the HDFG spectra arises from the sign of the molecular parameters. 
-In the HDFG spectrum presented in \autoref{fig:doubres_spec}, the signs of all molecular parameters are taken to be positive. 
+In the post-resonance region, the amplitude takes on an unusual lineshape.
+This arises due to interference between the $A$ and $B$ terms; for our parameters, this interference is destructive in the post-resonance region (\autoref{fig:doubres_spec}c, d).
+Examination of \autoref{ABterms_DR} shows that, while $A$ and $B$ terms share the same resonances, the relative phases of the contributions can vary due to Franck Condon integrals, Herzberg Teller integrals, and the dipoles.
+In the supporting information we illustrate how changing some of these parameters affects the interference.
 Inverting the sign of one parameter eliminates the interference and restores the expected, purely Lorentzian lineshape (Figure S4).
-It is important to note that these spectra simulate a single element of the hyperpolarizability tensor, $\gamma_{ijkl}$.
-The true HDFG response must be averaged over the molecular frame, or, the true, HDFG response is a linear combination of different $\gamma_{ijkl}$ terms.
-Nevertheless, if the resultant linear combination results in destructive interference between the $A$ and $B$ terms, it could be possible to elucidate both the amplitude and sign of $\Delta$ from a HDFG experiment.
+In bulk systems the HDFG response must be averaged over molecular frame orientations, which may also play a role in the interference.
 

### 2024-10-06 paper.tex
Update paper.tex

@@
 HSFG will not be discussed, but the application of our treatment to HSFG is straightforward and the results are similar.
-We note that HDFG emission can be phase-matched in media with normal dispersion while HSFG cannot,\cite{RN279, RN278} although experimental strategies can be implemented to minimize phase-mismatch in HSFG experiments.
-\cite{Kaufman2024}
+We note that HDFG emission can be phase-matched in media with normal dispersion while HSFG cannot.\cite{RN279, RN278} 
 In \autoref{steadystate}, we first identify the vibrational selection rules. 
@@
 In this section, we investigate the properties of HDFG and make the connections between HDFG and hyper-Raman scattering explicit.
-Coherent spectroscopies are often described using the density matrix formalism, where an n$^{\text{th}}$ order density matrix $\rho^{(n)}$ is propagated using the Liouville-von Neumann equation $via$
+Coherent spectroscopies are often described using the density matrix formalism, where an n$^{\text{th}}$ order density matrix $\rho^{(n)}$ is propagated using the Liouville-von Neumann equation:
 \begin{equation}\label{LVNE}
@@
 where $H$ is the (static) system Hamiltonian, $V(t)$ is the field-matter interaction and $\rho_R$ is the relaxation density matrix. \cite{RN455}
-In systems where interactions with surroundings are relevant, $\dot{\rho}_R$ becomes a complex function that can be modified to include phenomena such as system-bath interactions, solvent-solute coupling, among others.
+In systems where interactions with surroundings are relevant, expressions for $\dot{\rho}_R$ may be quite complicated due to intricate phenomena such as system-bath interactions and solvent-solute coupling, among others.
 \cite{Sung2001}
-In the limit where input field pulsewidths are much longer than electronic dephasing times and the individual molecule limit is approached, it becomes acceptable to write $\dot{\rho}^{(n)}_R= \Gamma \rho^{(n)}$, i.e.
+In the limit where input field pulsewidths are much longer than electronic dephasing times and the individual molecule limit is approached, it becomes acceptable to write a time-independent relaxation matrix $\dot{\rho}^{(n)}_R= \Gamma \rho^{(n)}$, i.e.
 exponential relaxation, where $\Gamma$ is the system's dephasing rate.
@@
 	\centering
-	\includegraphics[width=6.66 in]{figures/timeorderedwmel.png}
+	\includegraphics[width=\textwidth / 2]{figures/timeorderedwmel.png}
 	\caption{WMEL diagrams of HDFG pathways for when (a,b) $\omega_1$ (black arrow) interacts first and (c-f) $\omega_2$ (orange arrow) interacts first. 

### 2024-10-08 paper.tex
Almost ready.
Need to read it one more time

@@
 
-\author{Ryan P. McDonnell} \email{rpmcdonnell@wisc.edu}
+\author{Ryan P. McDonnell} %\email{rpmcdonnell@wisc.edu}
 \author{Daniel D. Kohler}
@@
 \cite{Cho2008, Gaynor2017, Ziegler2018, Ogilvie2019, Bonn2021, RN325, Chen2024}
-To target vibrational and electronic coupling, methods commonly make use of Raman transitions, e.g., doubly vibrationally enhanced spectroscopy (DOVE), triple sum frequency (TSF), coherent anti-Stokes Raman spectroscopy (CARS), resonant impulse stimulated Raman spectroscopy (RISRS).\cite{RN103, Dhar1994, RN345, Cho2000, RN491}
+To target vibrational and electronic coupling, methods commonly make use of Raman transitions, e.g., doubly vibrationally enhanced spectroscopy (DOVE), triple sum frequency (TSF), coherent anti-Stokes Raman spectroscopy (CARS), and resonant impulse stimulated Raman spectroscopy (RISRS).\cite{RN103, Dhar1994, RN345, Cho2000, RN491}
 Here we explore the less-utilized hyper-Raman transition in four wave mixing CMDS.
@@
 CMDS methods partially mitigate this issue because emission is spatially coherent so that all emission is directional and easily collected.
-In fact, hyper-Raman transitions have been observed in several CMDS studies (sometimes under the moniker of SIVE).\cite{Zilian1994, RN350, RN351, RN352, RN353, Chen1998, RN362, RN418, Wang2021, Bonn2024, McDonnell2024}
+In fact, hyper-Raman transitions have been observed in several CMDS studies (sometimes under the moniker of SIVE).\cite{Zilian1994, RN350, RN351, RN352, RN353, Chen1998, RN362, RN418, Hanninen2018, Wang2021, Bonn2024, McDonnell2024}
 
@@
 Nonlinear spectroscopic probes of electronic-vibrational coupling are not limited to the Raman and hyper-Raman based techniques diagrammed in \autoref{fig:comparisonwmel}.
-Independently developed by the Fleming and Khalil groups, respectively, 2D Electronic-Vibrational (2D-EV) and 2D Vibrational-Electronic (2D-VE) spectroscopy are based upon pump-probe and absorption type pathways which also investigate e-v coupling.\cite{Oliver2014, Courtney2015, Courtney2015_1}
-The Rao group has also developed a $\chi^{(4)}$ analogue of 2D-EV, 2D-EV sum frequency generation (2D-EVSFG), to probe interfacial e-v coupling. \cite{Deng2021}  
-These methods have been used to understand vibronic coupling in a variety of molecular systems and, albeit different selection rules, serve as 2D pump-probe type analogues to the infrared-hyper-Raman spectroscopies discussed here.
+Independently developed by the Fleming and Khalil groups, respectively, 2D Electronic-Vibrational (2D-EV) and 2D Vibrational-Electronic (2D-VE) spectroscopy are $\chi^{(3)}$ methods based upon pump-probe and absorption type pathways which also investigate e-v coupling.\cite{Oliver2014, Courtney2015, Courtney2015_1}
+The Rao group has also developed 2D-EV sum frequency generation (2D-EVSFG), a $\chi^{(4)}$ analogue of 2D-EV, to probe interfacial e-v coupling. \cite{Deng2021}  
+These methods have been used to understand vibronic coupling in a variety of molecular systems and, albeit with different selection rules, serve as 2D pump-probe type analogues to the infrared-hyper-Raman spectroscopies discussed here.
 
 When the hyper-Raman excitation in HDFG or HSFG is resonant or near-resonant with electronic states, the brightness of the vibrational feature depends on the vibronic structure of the electronic state.
-The electronic spectrum probed in HDFG or HSFG can inform on processes that control ultrafast electronic relaxation in molecular and biological systems in ways similar to resonance Raman.\cite{Cho2001, Bredenbeck2015, Arsenault2021}
+The electronic spectrum probed in HDFG or HSFG can inform on processes that control ultrafast electronic relaxation in molecular and biological systems in ways similar to resonance Raman.\cite{Cho2001, Bredenbeck2015, Gaynor2018, Arsenault2021}
 Since the selection rules of hyper-Raman scattering differ from Raman scattering, the hyper-Raman excitation spectra give a unique alternative to Raman scattering to understand vibrational spectra, electronic structure and vibronic coupling in molecular systems.
@@
 In this section, we investigate the properties of HDFG and make the connections between HDFG and hyper-Raman scattering explicit.
-Coherent spectroscopies are often described using the density matrix formalism, where an n$^{\text{th}}$ order density matrix $\rho^{(n)}$ is propagated using the Liouville-von Neumann equation:
+Coherent spectroscopies are often described using the density matrix formalism in the interaction picture, where an n$^{\text{th}}$ order density matrix $\rho^{(n)}$ is propagated using the Liouville-von Neumann equation:
 \begin{equation}\label{LVNE}
@@
 \cite{Sung2001}
-In the limit where input field pulsewidths are much longer than electronic dephasing times and the individual molecule limit is approached, it becomes acceptable to write a time-independent relaxation matrix $\dot{\rho}^{(n)}_R= \Gamma \rho^{(n)}$, i.e.
+In the limit where input field pulse widths are much longer than electronic dephasing times and the individual molecule limit is approached, it becomes acceptable to write a time-independent relaxation matrix $\dot{\rho}^{(n)}_R= \Gamma \rho^{(n)}$, i.e.
 exponential relaxation, where $\Gamma$ is the system's dephasing rate.
@@
 	\centering
-	\includegraphics[width=\textwidth / 2]{figures/timeorderedwmel.png}
+	\includegraphics[width=\textwidth]{figures/timeorderedwmel.png}
 	\caption{WMEL diagrams of HDFG pathways for when (a,b) $\omega_1$ (black arrow) interacts first and (c-f) $\omega_2$ (orange arrow) interacts first. 
@@
 		In all cases, $\omega_2 > \omega_1$.
-		The virtual states are arbitrarily placed and fluctuate in energy dependent upon the energy of the input fields.
+		The virtual states fluctuate in energy dependent upon the energy of the input fields.
 	}
@@
 Conversely, in the case where only $\omega_2$ is vibrationally resonant, diagrams (c,d) and (e,f), when detuned from an electronic resonance, have identical transition moments but opposite phase. 
-As a result, the output from (c,d) and (e,f) completely destructively interfere; no signal can be obtained from these pathways when significantly detuned. \cite{McDonnell2024}
+As a result, the output from (c,d) and (e,f) completely destructively interfere; no signal can be obtained from these pathways when significantly detuned from an electronic state. \cite{McDonnell2024}
 Note that in the case where $\omega_1$ interacts first but $\omega_2$ is resonant, the nonlinear output generated nearly vanishes as the first resonant pulse arrives after a non-resonant pulse.
@@
 chiral media, interfaces or non-centrosymmetric media.
-Nevertheless, in the discussion that follows for the rest of this manuscript, we will assume negligible second-order cascades.
+Nevertheless, in the discussion that follows for the rest of this manuscript, we will assume isotropic media, and therefore negligible second-order cascades.
 
@@
 \begin{equation} \label{polarization}
-{P}^{(3)}_I (\omega_4)  = \chi^{(3)}_{IJKL} E_J(\omega_3) E_K(\omega_2) E_L(\omega_1) 
+{P}^{(3)}_I (\omega_4)  = \varepsilon_0 \chi^{(3)}_{IJKL} E_J(\omega_3) E_K(\omega_2) E_L(- \omega_1) 
 \end{equation}
@@
 \end{equation}
-For clarity, we define the input electric fields as
+For clarity, we define the input electric fields as plane waves, where (suppressing the spatial dependence for simplicity)
 \begin{equation}
-	\vec{E}\left(\vec{x},t\right) = \frac{1}{2} \vec{E}_0 \exp(i\left(\vec{k}\cdot\vec{x} -\omega t\right)) +\text{c.c.}.
+	\vec{E}\left(\omega \right) = \frac{1}{2} \left(\vec{E}_0 \exp\left(i \omega t\right) +\text{c.c.}\right) .
 \end{equation}
@@
 
-By propagating \autoref{LVNE} in the steady state limit, the HDFG hyperpolarizability is \cite{Prior1984}
+By propagating \autoref{LVNE} in the steady state limit,\cite{Prior1984} the HDFG hyperpolarizability is 
 \begin{equation}\label{sivegamma}
-		\gamma_{ijkl}^{vg} =	- \sum_{e,m} \frac{1}{\varepsilon_0} \frac{1}{4D} \frac{1}{\hbar^3} \frac{\mu^{ve}_{i} \mu^{em}_{j} \mu^{mg}_{k} \mu^{gv}_{l} }{\Delta_{ev}^{3+2-1} \Delta_{mv}^{2-1}\Delta_{gv}^{-1}}  \rho_{gg}
+		\gamma_{ijkl}^{vg} =	- \sum_{e,m} \frac{1}{\varepsilon_0} \frac{1}{4D} \frac{1}{\hbar^3} \frac{\mu^{ve}_{i} \mu^{em}_{j} \mu^{mg}_{k} \mu^{gv}_{l} }{\Delta_{ev}^{3+2-1} \Delta_{mv}^{2-1}\Delta_{gv}^{-1}}  \rho^{(0)}_{gg}
 \end{equation}
-where: $\mu^{ab}_{j}$ is the $j^{th}$ element of $\mel{a}{\vec{\mu}}{b}$, $\Delta_{kl}^{-x+y+z} = \omega_{kl} - (-\omega_{x}+\omega_{y} + \omega_{z}) - i\Gamma_{kl}$, $\omega_j$ is the frequency of the j$^{th}$ input field, $\Gamma_{kl}$ is the $\rho_{kl}$ dephasing, and $\rho_{gg}$ is the ground state population.
+where: $\mu^{ab}_{j}$ is the $j^{th}$ element of $\mel{a}{\vec{\mu}}{b}$, $\Delta_{kl}^{-x+y+z} = \omega_{kl} - (-\omega_{x}+\omega_{y} + \omega_{z}) - i\Gamma_{kl}$, $\omega_j$ is the frequency of the j$^{th}$ input field, $\Gamma_{kl}$ is the $\rho_{kl}$ dephasing, and $\rho^{(0)}_{gg}$ is the ground state population.
 Here, $\ket{e}$ and $\ket{m}$ are virtual states, and thus necessarily summed over in \autoref{sivegamma}.
@@
 \begin{equation}\label{sivebeta}
-	\gamma_{ijkl} =	-\frac{1}{\varepsilon_0} \frac{1}{4D \hbar}\frac{\beta^{vg}_{ijk} \mu^{gv}_{l}}{\Delta_{gv}} \rho_{gg}.
+	\gamma_{ijkl} =	-\frac{1}{\varepsilon_0} \frac{1}{4D \hbar}\frac{\beta^{vg}_{ijk} \mu^{gv}_{l}}{\Delta_{gv}} \rho^{(0)}_{gg}.
 \end{equation}
@@
 Taking $\ket{g} = \ket{0}, \ket{v} = \ket{1}$, substituting into \autoref{sivebeta} and using typical Harmonic Oscillator selection rules, gives the HDFG hyperpolarizability to $\order{Q_v}$ as \begin{equation}\label{SIVEselection}
-	\gamma_{ijkl} =	-\frac{1}{\varepsilon_0} \frac{1}{8D \omega_{vg}}  \frac{1}{{\Delta_{gv}}} \ \left(\frac{\partial \beta^{vg}_{ijk}}{\partial Q_v}\right)_0 \left({\frac{\partial \mu^{gv}_{l}}{\partial Q_v}}\right)_0  \rho_{gg}
+	\gamma_{ijkl} =	-\frac{1}{\varepsilon_0} \frac{1}{8D \omega_{vg}}  \frac{1}{{\Delta_{gv}}} \ \left(\frac{\partial \beta^{vg}_{ijk}}{\partial Q_v}\right)_0 \left({\frac{\partial \mu^{gv}_{l}}{\partial Q_v}}\right)_0  \rho^{(0)}_{gg},
 \end{equation}
@@
 We will henceforth suppress the dependence of the electronic states on \textbf{Q} for simplicity.
-It is worthwhile to note that the time-dependent Raman formalism developed by Heller \textit{et al.} can be applied to hyper-Raman scattering. \cite{Lee1979, Silverstein2012}
+It is worthwhile noting that the time-dependent Raman formalism developed by Heller \textit{et al.} can be applied to hyper-Raman scattering. \cite{Lee1979, Silverstein2012}
 However, since our goal is to expose the Quantum Mechanical aspects of HDFG spectroscopy, we choose to employ the typical sum-over-states formalism.
@@
 		\Delta_{g0,gv}
-	}
+	},
 \end{equation}
@@
 $R_{i}^{gv,e\tilde{v}'} = \mel{v}{M_i^{ge}}{\tilde{v}'}$, where $\vec{M}^{ab} = (a|\vec{R}|b)$.\cite{Ziegler1974}
-Expanding $\vec{M}^{ij}$ to $\order{Q}$ about the equilibrium point of the ground state potential surface as
+Expanding $\vec{M}^{ij}$ to $\order{Q}$ about the equilibrium point of the ground state potential surface (taken to be $Q = 0$) as
 $\vec{M}^{ij} = \vec{M}^{ij}_0 + \sum_z \frac{\partial\vec{M}^{ij}}{\partial Q_z} Q_z$
@@
 \begin{equation}\label{gammaabc}
-		\gamma_{ijkl} \sim \left(A_{ijk} + B_{ijk} + C_{ijk}\right) \frac{\mel{v}{\mu_{l}}{0}} {\Delta_{g0,gv}}
+		\gamma_{ijkl} \sim \left(A_{ijk} + B_{ijk} + C_{ijk}\right) \frac{\mel{v}{\mu_{l}}{0}} {\Delta_{g0,gv}}.
 \end{equation}
@@
 			\langle \tilde{v}' | 0 \rangle 
-			\frac{1}{\Delta_{e\tilde{v}', gv}}
+			\frac{1}{\Delta_{e\tilde{v}', gv}}.
 	\end{split}
@@
 To understand the vibronic structure of an excited state $|e)$, we restrict consideration to electronic transitions between $|g)$ and $|e)$.  
-Note that HDFG experiments selectively excite ground state vibrational modes through $\omega_1$; we will assume the IR beam has excited the fundamental of an IR-active mode, $\ket{g,1}$, so that hyper-Raman scattering is between ground state and $\ket{g,1}$.
+Note that HDFG experiments selectively excite ground state vibrational modes through $\omega_1$; we will assume the IR beam has excited the fundamental of an IR-active mode, $\ket{g,1}$, so that hyper-Raman scattering is between the ground state and $\ket{g,1}$.
 By working only in terms of this single normal mode (i.e., removing the sum over $z$ and taking $v=1$), 
@@
 				\langle \tilde{v}' | 0 \rangle 
-				\frac{1}{\Delta_{e\tilde{v}',gv}}
+				\frac{1}{\Delta_{e\tilde{v}',g1}}
 		\end{equation}
@@
 				\frac{\partial \Lambda^{eg}_{jk}}{\partial Q} \langle 1 | \tilde{v}' \rangle \mel{\tilde{v}'}{Q}{0} 
-				\frac{1}{\Delta_{e\tilde{v}', gv}}
+				\frac{1}{\Delta_{e\tilde{v}', g1}}
 		\end{equation}
@@
 		Dotted lines in (b) denote the $\tilde{v}'$ = 0, 1, 2 vibronic resonances. 
-		The vibronic one and two photon absorption operators are scaled such that $\abs{B}/\abs{A} \sim$ 0.1, following Chung and Ziegler. \cite{Ziegler1988}
+		The vibronic one and two photon absorption operators are scaled such that $\max \left(\abs{B}/\abs{A}\right) \sim$ 0.1, following Chung and Ziegler. \cite{Ziegler1988}
 		The Franck-Condon factor and Herzberg-Teller integral contributions to each of these terms are found in \autoref{T:contributions}.}
@@
 \end{subequations}
-for the ground ($H_g$) and first excited ($H_e$) states, where $p$ is the dimensionless momentum and $q = \sqrt{\frac{\omega}{\hbar}} Q$ is the dimensionless position, the A and B contributions can be evaluated using Franck-Condon and Herzberg-Teller integrals (\autoref{fig:doubres_spec}a).
+for the ground ($H_g$) and first excited ($H_e$) states, where $p$ is the dimensionless momentum coordinate and $q = \sqrt{\frac{\omega}{\hbar}} Q$ is the dimensionless position coordinate, the A and B contributions can be evaluated using Franck-Condon factors and Herzberg-Teller integrals (\autoref{fig:doubres_spec}a).
 For simplicity, we restrict consideration to $v^\prime \in \{0,1,2\}$ and take $\Delta = 0.5$.
@@
 We assume the electronic state is both one and two photon allowed.
-For this simulation, we declare the dipolar coordinate dependences:
+For this simulation, to enforce $\max \left(\abs{B}/\abs{A}\right) \sim$ 0.1 at $\Delta = 0.5$, we declare the coordinate dependencies
 \begin{eqnarray}
-	M^{ge} = M^{ge}_0 (1 + 0.1 q),  \\
-	\Lambda^{ge} = \Lambda^{ge}_0 (1 + 0.1 q).
+	M^{ge}(q) = M^{ge}_0 \left(1 + 0.04 q + \order{q^2}\right),  \\
+	\Lambda^{ge}(q) = \Lambda^{ge}_0 \left(1 + 0.04 q + \order{q^2}\right).
 \end{eqnarray}
@@
 
-% DDK: careful about w_2+w_3 vs 2*w_2; do we ever state that we will use w3=w2 for this experiment?
-\autoref{fig:doubres_spec}b shows the simulated HDFG spectrum for this two-well system.  The spectrum selectively probes vibronic pathways from $\ket{g,0}$ to $\ket{g,1}$.
+\autoref{fig:doubres_spec}b shows the simulated HDFG spectrum for this two-well system where the hyper-Raman process is stimulated by two degenerate photons ($\omega_2 = \omega_3$). 
+The spectrum selectively probes vibronic pathways from $\ket{g,0}$ to $\ket{g,1}$.
 In the resonant region, the $A$ and $B$ terms contain character from all three possible transitions between $\ket{g,0}$, $\ket{e,\tilde{v}'}$ and $\ket{g,1}$. 
@@
 This means that it could prove difficult to isolate $B$ terms when $A$ terms are present.
-As such, HDFG will have difficulty examining non-Condon effects ($B$ term contributions) in noncentrosymmetric systems.
 
@@
 
-The value of $\Delta$ is system specific and drastically affects the HDFG spectrum.
-In the supporting information we demonstrate the impact of $\Delta$ on the HDFG response using previously reported values (Figure S3). \cite{Myers1982, Brennan2024}
-Clearly, $\Delta$, $\omega_{g1, g0}$ and $\Gamma$ have a significant impact on the HDFG spectral profile.
-% DDK: we don't care whether $B$ term dominates, but if $A$ term is insufficient to describe the spectrum...
-Indeed, for some values of $\Delta$, $B$ term resonances can dominate over $A$ term resonances (see also Figure S2), which can allow for significant non-Condon behavior in pre-resonant HDFG response.
+The pre-resonance response is also dependent upon the specific molecular parameters that drive HDFG output.
+The values of $\Delta$, $\omega_{g1, g0}$ and $\Gamma$ are system specific and affect the HDFG spectrum.
+In the supporting information we demonstrate the impact of these parameters on the HDFG response using previously reported values (Figure S3). \cite{Myers1982, Brennan2024}
+Based upon the response in Figure S3, $\Delta$, $\omega_{g1, g0}$ and $\Gamma$ have a significant impact on the resonant and pre-resonant HDFG response.
+However, the driving terms in the HDFG response are the Franck-Condon factor and Herzberg-Teller integral products, which are only dependent upon $\Delta$.
+Indeed, for some values of $\Delta$, most notably for $\Delta \rightarrow 0$, $A$ term products vanish, while $B$ term products are large (Figure S2).
+As such, a small displacement of the electronic state from the ground state can allow for significant non-Condon behavior in pre-resonant HDFG response.
 
@@
 This arises due to interference between the $A$ and $B$ terms; for our parameters, this interference is destructive in the post-resonance region (\autoref{fig:doubres_spec}c, d).
-Examination of \autoref{ABterms_DR} shows that, while $A$ and $B$ terms share the same resonances, the relative phases of the contributions can vary due to Franck Condon integrals, Herzberg Teller integrals, and the dipoles.
+Examination of \autoref{ABterms_DR} shows that, while $A$ and $B$ terms share the same resonances, the relative phases of the contributions can vary due to Franck-Condon factors, Herzberg Teller integrals, and the dipoles.
 In the supporting information we illustrate how changing some of these parameters affects the interference.
@@
 
-An often unavoidable consequence in electronic spectroscopy is broadened line shapes due to a high density of vibronic modes, i.e., inhomogeneous broadening.
+An often unavoidable consequence in electronic spectroscopy is broadened line shapes due to a high density of vibronic modes and inhomogeneous broadening.
 It is worthwhile to investigate the impact of inhomogeneity on HDFG response and the resultant lineshapes. 
-In the discussion that follows, we assume that a ground state vibrational frequency, $\ket{g,v}$, experiences variations that are correlated to the frequency of a vibronic $\ket{e,\tilde{v}'}$.
+In the discussion that follows, we assume that a ground state vibrational frequency, $\ket{g,v}$, experiences variations that are correlated to local changes in the environment and the frequencies of a vibronic $\ket{e,\tilde{v}'}$.
 If the frequency of $\ket{g,v}$ is written as $\omega_{gv} + \xi$, where $\xi$ is some external strain (e.g.
@@
 For simplicity, we consider only c = $\pm$1.
-To simplify discussion below, we map $\Delta_{e\tilde{v}', gv} \rightarrow \Delta_{ba}$ and $\Delta_{g0,gv} \rightarrow \Delta_{ga}$.
+To simplify discussion below, we map $\Delta^{3+2-1}_{e\tilde{v}', gv} \rightarrow \Delta^{3+2-1}_{ba}$ and $\Delta^{-1}_{g0,gv} \rightarrow \Delta^{-1}_{ga}$.
+For clarity, we have reinstated the input pulse numbering to the $\Delta_{ij}$ terms for the discussion below (cf. \autoref{sivegamma}).
 
@@
 	\gamma_{ijkl} = \int_{-\infty}^\infty \mathrm{d}\xi \ P(\xi) \gamma_{ijkl}(\xi)
-	= \frac{\sigma}{\pi}\int_{-\infty}^\infty \mathrm{d}\xi \frac{1}{\sigma^2 + \xi^2} \frac{\eta_{ijkl}}{\left(\Delta_{ga} - \xi\right)\left(\Delta_{ba}+ c\xi\right)}
+	= \frac{\sigma}{\pi}\int_{-\infty}^\infty \mathrm{d}\xi \frac{1}{\sigma^2 + \xi^2} \frac{\eta_{ijkl}}{\left(\Delta_{ga}^{-1} - \xi\right)\left(\Delta^{3+2-1}_{ba}+ c\xi\right)}
 \end{equation} 
@@
 where $\eta_{ijkl}$ contains all values in \autoref{drgamma_notaylor} not dependent upon $\xi$.
-While Gaussian distributions are commonly used as a phenomenological description of inhomogeneous broadening, Lorentzian distributions have successfully described inhomogeneous broadening in many coherent spectroscopies and yield easily interpretable closed-form solutions.
+While Gaussian distributions are commonly used as a phenomenological description of inhomogeneous broadening,\cite{RN307} Lorentzian distributions have successfully described inhomogeneous broadening in many multiply resonant coherent spectroscopies, and yield easily interpretable closed-form solutions.
 \cite{Dick83_1, Carlson1990line, RN410, Yurs2012}
+\begin{widetext}
+Evaluating \autoref{contour} for the HDFG pathway used above (\autoref{fig:sivewmel2}a) shows\footnote{See the supporting information for more details.} 
+\begin{subequations}
+	\begin{equation}\label{eq:linenarrowa}
+		\gamma_{ijkl} = \frac{\eta_{ijkl}}{\left(\Delta_{ga}^{-1}-i\sigma \right) \left(\Delta^{3+2-1}_{ba}-i \sigma\right)}
+	\end{equation}
+for anti-correlated ($c = -1$) states, and
+\begin{equation}\label{eq:linenarrowb}
+	\gamma_{ijkl} = \frac{\eta_{ijkl}}{\Delta^{3+2-1}_{ba}+ i \sigma} \left(\frac{1}{\Delta_{ga}^{-1} - i \sigma} + \frac{2i\sigma}{(\Delta^{3+2-1}_{ba} - i \sigma)(\Delta_{ga}^{-1} + \Delta^{3+2-1}_{ba})}\right)
+\end{equation}
+for correlated ($c = 1$) states. 
+\end{subequations}
+\end{widetext}
+For anti-correlated modes (\autoref{eq:linenarrowa}), we see the inhomogeneous envelope width $\sigma$ is added to the linewidth of each resonance (e.g., $\Gamma_{ga} \rightarrow \Gamma_{ga} + \sigma$).
+In other words, HDFG spectra of anti-correlated vibrational and vibronic modes will contain the same inhomogeneity present in a typical 1D spectrum.
 
-Evaluating \autoref{contour} for the HDFG pathway above shows\footnote{See the supporting information for more details.} 
-\begin{subequations}
-\begin{equation}\label{linenarrowa}
-	\gamma_{ijkl} = \frac{\eta_{ijkl}}{\Delta_{ba} + i \sigma} \left(\frac{1}{\Delta_{ga} - i \sigma} + \frac{2i\sigma}{(\Delta_{ba} - i \sigma)(\Delta_{ga} + \Delta_{ba})}\right)
-\end{equation}
-for correlated ($c = 1$) states and
-\begin{equation}
-	\gamma_{ijkl} = \frac{\eta_{ijkl}}{\left(\Delta_{ga}-i\sigma \right) \left(\Delta_{ba}-i \sigma\right)}
-\end{equation}
-\end{subequations}
-for anti-correlated ($c = -1$) states.
-The output for correlated modes shows the presence of a new term, $\frac{2i\sigma}{\Delta_{ga} + \Delta_{ba}}$. 
-This term is amplified by the width of the inhomogeneous envelope ($\sigma$) and has a linewidth $\Gamma_{ba} + \Gamma_{ga}$, which linenarrows the transition. 
-For anti-correlated modes, we see the inhomogeneous envelope width $\sigma$ is added to the linewidth of each resonance (e.g., $\Gamma_{ga} \rightarrow \Gamma_{ga} + \sigma$).
-As such, the HDFG pathway considered in this work line-narrows correlated modes. 
+The output for correlated modes shows the presence of a new term, $\frac{2i\sigma}{\Delta_{ga} + \Delta_{ba}}$, along with other terms where the inhomogeneous width is added to the resonance linewidth.
+However, unlike the other terms, the $\frac{2i\sigma}{\Delta_{ga} + \Delta_{ba}}$ term is amplified by the width of the inhomogeneous envelope ($\sigma$) and has a linewidth $\Gamma_{ba} + \Gamma_{ga}$.
+As a result, this term will dominate over the other terms. 
+Since the linewidth of the dominant term, $\Gamma_{ba} + \Gamma_{ga}$, is a direct report on the linewidth of the coupled modes, this is evidence of line-narrowing in the HDFG spectrum. \cite{RN103}
+Or, the HDFG pathway considered in this work line-narrows correlated modes. 
+For all cases, it is useful to note that in the limit of zero inhomogeneity ($\sigma \rightarrow 0$), the results in \autoref{drgamma_notaylor} are restored.
 These results are consistent with the idea that non-parametric, non-linear spectroscopies line-narrow correlated modes. \cite{Dick83_1, Carlson1990line}
 
-Although \autoref{linenarrowa} identifies that parametric HDFG line-narrows correlated modes, these results are only valid in limits where the input pulses weakly populate excited states.
-When resonant pulses are significantly longer than the dephasing time of some state, then that state can become populated.
-Excited state population effects are particularly important for understanding the spectroscopy of electronic states using input pulses with pulsewidths significantly longer than dephasing times.
-\cite{RN471, Yurs2012}
+Although \autoref{eq:linenarrowb} identifies that non-parametric HDFG line-narrows correlated modes, these results are only valid in limits where the input pulses weakly populate excited states.
+When resonant pulses are significantly longer than the dephasing time of some state, then that state can become significantly populated.
+Excited state population effects are particularly important for understanding the spectroscopy of electronic states using input pulses with pulse widths significantly longer than dephasing times.
+\cite{RN471}
 Excited state populations can feed other modes, including the ground state and other vibrational/vibronic modes, inducing higher order processes.\cite{RN471}
@@
 Can vSFG experimental setups detect HDFG signals?
-SFG setups typically leverage the surface selectivity of $\chi^{(2)}$ polarizations, which results in extremely small emission volumes, so SFG setups are typically quite sensitive.
+SFG experiments typically leverage the surface selectivity of $\chi^{(2)}$ polarizations, which results in extremely small emission volumes, so SFG setups are typically quite sensitive.
 However, HDFG is a weak $\chi^{(3)}$ process because it depends upon hyper-Raman cross-sections, which are commonly several orders of magnitude weaker than corresponding Raman transitions.\cite{RN515}
@@
 To evaluate the feasibility of HDFG for vSFG practitioners, we have compared the relative output of each process using nominal parameters. 
-As calculated in \autoref{appendixA}, HDFG's weak $\chi^{(3)}$ value and SFG's low emission cancel somewhat, so that the output polarization of HDFG and vSFG are comparable ($\abs{P_\text{vSFG} / P_\text{HDFG}} \sim 1$).
+As calculated in \autoref{appendixA}, HDFG's weak $\chi^{(3)}$ value and SFG's low emission cancel somewhat, so that the output polarization of HDFG and vSFG are comparable ($\abs{P_\text{vSFG} / P_\text{HDFG}} \sim 2/3$).
 Transient HDFG, or IR-pump-HDFG-probe, analogous to IR-pump-vSFG-probe, is therefore also feasible under similar experimental conditions, and provides vSFG practitioners a simple method to measure bulk dynamics without significant changes in an experimental setup.
@@
 \begin{equation}\label{chi3}
-		\chi^{(3)}_{IJKL} = -\frac{NF}{4D \hbar \varepsilon_0 \Delta_{gv}} \langle \beta_{ijk} \mu_l \rangle_{IJKL} \rho_{gg}\\
+		\chi^{(3)}_{IJKL} = -\frac{NF}{4D \hbar \varepsilon_0 \Delta_{gv}} \langle \beta_{ijk} \mu_l \rangle_{IJKL} \rho^{(0)}_{gg}\\
 \end{equation}
-For simplicity, we take $\rho_{gg} = 1$.
+For simplicity, we take $\rho^{(0)}_{gg} = 1$.
 Orientational averaging shows specific polarization schemes isolate linear combinations of different $\beta_{ijk}$ terms. \cite{Bersohn1966, Kauranen1996}
@@
 \end{equation}
-
 Since $\abs{\partial \mu_l / \partial Q}$ values can be extracted from FT-IR spectra and $\chi^{(3)}$ can be extracted through the Bloembergen interferometry experiment,\cite{Levenson1974_1, Levenson1974_2, RN459} HDFG can give quantitative information on the magnitude of $\frac{\partial \beta_{ijk}}{\partial Q}$ for infrared active vibrations.
@@
 However, $B$ term resonances, or Herzberg-Teller contributions, dominate in centrosymmetric media, as $A$ term resonances vanish in centrosymmetric media through parity constraints.
-A treatment of inhomogeneous broadening shows that for positively correlated vibrational and vibronic resonances, HDFG linenarrows the spectral output, eliminating inhomogeneous broadening. 
+A treatment of inhomogeneous broadening shows that for positively correlated vibrational and vibronic resonances, HDFG line narrows the spectral output, eliminating inhomogeneous broadening. 
 As a result, HDFG possesses site-selective properties analogous to those of coherent Raman spectroscopies, which can allow for a thorough analysis of vibronic coupling schemes in isotropic systems.
@@
 \section{Appendix: Comparison of vSFG and two-beam HDFG output}\label{appendixA}
-To motivate the application of HDFG spectroscopy, we perform a calculation to compare two-color HDFG and vSFG output, where absorption effects are neglected for simplicity.
+To motivate the application of HDFG spectroscopy, we perform a calculation to compare vibrationally resonant two-color HDFG and vSFG output, where absorption effects are neglected for simplicity.
 vSFG is a $\chi^{(2)}$ technique, when only vibrationally resonant, whose output scales as $\chi^{(2)}_{IJK} \sim \langle \alpha_{ij} \mu_k \rangle$, where $\alpha_{ij}$ is the Raman polarizability tensor.
-The output polarizations for vSFG and HDFG, respectively, under the electric dipole approximation are written as
+The output polarizations for two-beam vSFG and HDFG, respectively, under the electric dipole approximation, and assuming exponential dephasing, when vibrationally resonant are written as:
 	 	\begin{subequations}
@@
 		 		\begin{split}
-		 		\abs{P^{(2)}_{\text{vSFG}}} &= \frac{N_\text{surf}}{\ell} \abs{F_{\text{SFG}} \langle \alpha_{ij}\mu_{k} \rangle E(\omega_2)E(\omega_1)} 
+		 		\abs{P^{(2)}_{\text{vSFG}}} &= \frac{N_\text{surf}}{\ell} \abs{ F_{\text{vSFG}} \langle \alpha_{ij}\mu_{k} \rangle E(\omega_2)E(\omega_1) \frac{1}{2 \varepsilon_0 \hbar i \Gamma}} 
 		 		\end{split}
@@
 		 		\begin{split}
-			 		\abs{P^{(3)}_{\text{HDFG}}} &= N_\text{bulk} \abs{F_{\text{HDFG}} \langle \beta_{ijk} \mu_{l} \rangle E{(\omega_2)}E(\omega_2)E(-\omega_1)}
+			 		\abs{P^{(3)}_{\text{HDFG}}} &= 4 N_\text{bulk} \abs{{ F_{\text{HDFG}} \langle \beta_{ijk} \mu_{l} \rangle E{(\omega_2)}E(\omega_2)E(-\omega_1) \frac{-1}{12 \varepsilon_0 \hbar i \Gamma}}}, 
 		 		\end{split}
@@
 		 \end{subequations}
-where N$_\text{bulk}$ is the bulk number density ($\sim$ 10$^{28}$ m$^{-3}$ for H$_2$O$_{(l)}$ at room temperature), and N$_\text{surf}$ is the surface number density ($\sim$ 10$^{16}$ m$^{-2}$ for H$_2$O adsorbed at quartz).\cite{Du1994}
-For simplicity, we assume that $\chi^{(2)}$ is a spatial constant so that $\int_{0^-}^\ell \mathrm{d}z \langle \alpha_{ij}\mu_{k} \rangle \approx \ell \langle \alpha_{ij}\mu_{k} \rangle$, where $z$ is oriented along the surface normal and $0^{-}$ is the edge of the interface where substrate begins.
+where N$_\text{bulk}$ is the bulk number density ($\sim$ 10$^{28}$ m$^{-3}$ for H$_2$O$_{(l)}$ at room temperature), N$_\text{surf}$ is the surface number density ($\sim$ 10$^{16}$ m$^{-2}$ for H$_2$O adsorbed at quartz), and $\Gamma$ is the vibrational dephasing rate.\cite{Du1994}
+The HDFG output gains a multiplicative factor of 4 because four, identical, singly resonant HDFG processes occur at pulse overlap.
+
+For simplicity, we assume that $\chi^{(2)}$ is a spatial constant. 
 We take the film thickness ($\ell$) probed by vSFG to be 1 nm, much less than the vSFG coherence length.\cite{RN133}
@@
 \begin{equation}
-	P_\text{ratio} \equiv \frac{\abs{P^{(3)}_{\text{HDFG}}}}{\abs{P^{(2)}_{\text{vSFG}}}} \approx \frac{N_\text{bulk}}{N_\text{surf}} \abs{\frac{\left(n(\omega_2)\right)^2 + 1}{3}} \frac{\beta}{\alpha} E(\omega_2) \ell \sim 10^3 \frac{\beta}{\alpha} E(\omega_2)\\
+	P_\text{ratio} \equiv \frac{\abs{P^{(3)}_{\text{HDFG}}}}{\abs{P^{(2)}_{\text{vSFG}}}} \approx \frac{2}{3} \frac{N_\text{bulk}}{N_\text{surf}} \ell \abs{\frac{\left(n(\omega_2)\right)^2 + 1}{3}} \frac{\beta}{\alpha} E(\omega_2) \sim \frac{2}{3} \left(10^3 \frac{\beta}{\alpha} E(\omega_2)\right)\\
 \end{equation}
@@
 Such an intensity is easily obtained using modern ultrafast sources.
-In this limit, $P_\text{ratio} \sim 1$, or the HDFG output is roughly as strong as vSFG, assuming only interfacial contributions in vSFG.
+In this limit, $P_\text{ratio} \sim 2/3$, or the HDFG output is slightly weaker than vSFG, assuming only interfacial contributions in vSFG.
 It is important to note that this calculation assumed negligible dipole and Raman polarizability dependence upon the distance from surface normal, ignored orientational averaging effects, and presumed equivalence of local field factors, all of which can significantly reduce output from either process.

### 2024-10-08 si.tex
Almost ready.
Need to read it one more time

@@
 \end{subequations}
-Here, $p,q$ are the dimensionless conjugate normal mode coordinates, $\hbar\omega_{eg}$ is the energy difference between $H_e$ and $H_g$, and $\Delta$ is the dimensionless offset of the excited state surface relative to the ground state.
+Here, $p,q$ are the dimensionless conjugate normal mode coordinates, $\hbar\omega_{eg}$ is the energy difference between $|e)$ and $|g)$, and $\Delta$ is the dimensionless offset of the excited state surface relative to the ground state.
 The Hamiltonians are quantum harmonic oscillators.
@@
 		\mel{\tilde{n}}{q^k}{m} &= \int_{-\infty}^\infty \mathrm{d}q \ \psi^*_n(q-\Delta) q^k \psi_m(q)\\
-		&= \int_{-\infty}^\infty \mathrm{d}q \ N_n H_n(q-\Delta) \exp(-\frac{(q - \Delta)^2}{2}) q^k N_m H_m(q) \exp(-\frac{q^2}{2}). \\
-		&= N_n N_m \exp(-\frac{\Delta^2}{2}) \int_{-\infty}^\infty \mathrm{d}q \ H_n(q-\Delta) q^k H_m(q) \exp(-q^2 + q\Delta)
+		&= \int_{-\infty}^\infty \mathrm{d}q \ N_n H_n(q-\Delta) \exp(-\frac{(q - \Delta)^2}{2}) q^k N_m H_m(q) \exp(-\frac{q^2}{2}) \\
+		&= N_n N_m \exp(-\frac{\Delta^2}{2}) \int_{-\infty}^\infty \mathrm{d}q \ H_n(q-\Delta) q^k H_m(q) \exp(-q^2 + q\Delta).
 	\end{split}\label{key}
@@
 The matrix elements of \autoref{key} can be computed numerically, but analytic forms of the integral also exist. 
-Due to the polynomial nature of $H_v(q)$, the product $H_n(q-\Delta) q^k H_m(q)$ will also be a polynomial, so that the integral of equation \autoref{key} will be of the form
+Due to the polynomial nature of $H_v(q)$, the product $H_n(q-\Delta) q^k H_m(q)$ will also be a polynomial, so that the integral of \autoref{key} will be of the form
 \begin{eqnarray}
@@
 \end{eqnarray}
-for some set coefficients $a_\lambda$, to be specified later. We can recast the integral into the linear combination of integrals,
+for some set coefficients $a_\lambda$, to be specified later. 
+We can recast the integral into the linear combination of integrals,
 \begin{equation}\label{eq:analytic_form}
@@
 It is clear from \autoref{fig:fcht_product} that the HDFG spectrum will have a significant dependence upon $\Delta$, even for small deviations from complete overlap. 
-To this end, we plot the impact of resonance frequency and offset on the HDFG spectrum \autoref{fig:chgdelta}, using values reported by Myers et al. and Brennan et al. \cite{Myers1982, Brennan2024}
-In this section, we take $\omega_{eg}$ = $30000$ cm$^{-1}$ and vary the offset ($\Delta$), vibrational frequency ($\omega_{g1,g0}$), and linewidth ($\Gamma$) as noted in the figure.
+To this end, we plot the impact of offset ($\Delta$), vibrational frequency ($\omega_{g1,g0}$), and linewidth ($\Gamma$) on the HDFG spectrum \autoref{fig:chgdelta}, using values reported by Myers et al.
+and Brennan et al (\autoref{fig:chgdelta}).
+\cite{Myers1982, Brennan2024}
+We maintain the relationship $\max \left(\abs{B}/\abs{A}\right) \sim$ 0.1 at $\Delta = 0.5$ to facilitate comparison to the results in the main text.
 
@@
 Parameters for (a,b) follow from Myers et al., whereas parameters for (c,d) follow from Brennan et al.\cite{Myers1982, Brennan2024}
-	Note that in these plots, the ratio $\abs{A/B} = 0.1$ is enforced.} 
+} 
 	\label{fig:chgdelta}
@@
 	\includegraphics[width=6.675in]{figures/drsive_chgsign.png}
-	\caption{Contributions of $A, B$ to HDFG spectrum for a simple two harmonic well system, identical to the main text, except $M_0^{ge} < 0$.
+	\caption{Contributions of $A, B$ to HDFG spectrum for a simple two harmonic well system, identical to the main text, except $M^{ge}(q) = M^{ge}_0 \left(-1 + 0.04 q + \order{q^2}\right)$.
 		(a) Potential energy surfaces for a two-well system, (b) 1D HDFG spectrum for $\Delta = 0.5$, $\omega_1 = \omega_{g1, g0}$, (c, d) real and imaginary parts of terms plotted in (b), respectively.
-		The spectra are referenced to $\max{(A+B)}$. 
-		The vibronic one and two photon absorption operators are scaled such that $\abs{B}/\abs{A} \sim$ 0.1, following Chung and Ziegler. \cite{Ziegler1988}
+		The spectra are scaled to $\max{(A+B)}$. 
+		The vibronic one and two photon absorption operators are scaled such that $\max(\abs{B}/\abs{A}) \sim$ 0.1, following Chung and Ziegler. \cite{Ziegler1988}
 } 
@@
 For clarity, we briefly outline the technique.
-%@dan i had too much white space, needed something to fill in... delete if you want.
 Consider the integral
@@
 If $\int_{-\infty}^{\infty} \mathrm{d}x f(x)$ exists %is this strict enough?
-and $f(z)$ is an analytic function, where $z$ is a complex variable, then
+and $f(z)$ is analytic, where $z$ is a complex variable, then
 \begin{subequations}\label{eq:generalcontour}
@@
 \end{subequations}
-Note that in \autoref{eq:generalcontour}, the integrals are closed along a contour which wraps all the poles in the positive half of the complex plane.
+Note that in \autoref{eq:generalcontour}, the integrals are evaluated along a contour which wraps all the poles in the positive half of the complex plane.
 
@@
 For c = -1, there are four poles: $\pm i \sigma, \Delta_{ga}, \Delta_{ba}$. 
-The contour that wraps the upper half of the complex plane has only one pole, $i \sigma$
+The contour that envelops the upper half of the complex plane has only one pole, $i \sigma$.
 Using the residue theorem for a first order pole,\cite{Carlson1990line} we see
@@
 		\begin{split}
-			\int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi) &= 2\pi i \sum_k \lim_{\xi \rightarrow \xi_k} P(\xi) \gamma_{ijkl}(\xi) (\xi - \xi_k)\\
-			&= 2\pi i \frac{\eta_{ijkl} \sigma}{\pi} \lim_{\xi \rightarrow i\sigma} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga} - \xi} \frac{1}{\Delta_{ba} - \xi} (\xi - i \sigma)\\
-			&= 2 \eta_{ijkl} \sigma i \lim_{\xi \rightarrow i\sigma} \frac{1}{\xi + i\sigma} \frac{1}{\Delta_{ga} - \xi} \frac{1}{\Delta_{ba} - \xi}\\
+			\int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi) &= 2\pi i \sum_k \lim_{z \rightarrow z_k} P(z) \gamma_{ijkl}(z) (z - z_k)\\
+			&= 2\pi i \frac{\eta_{ijkl} \sigma}{\pi} \lim_{z \rightarrow i\sigma} \frac{1}{(z + i\sigma)(z- i\sigma)} \frac{1}{\Delta_{ga} - z} \frac{1}{\Delta_{ba} - z} (z - i \sigma)\\
+			&= 2 \eta_{ijkl} \sigma i \lim_{z \rightarrow i\sigma} \frac{1}{z + i\sigma} \frac{1}{\Delta_{ga} - z} \frac{1}{\Delta_{ba} - z}\\
 			&= 2\eta_{ijkl} \sigma i \frac{1}{2i\sigma} \frac{1}{\Delta_{ga} - i\sigma} \frac{1}{\Delta_{ba} - i\sigma}\\
@@
 For correlated modes, the poles are situated in the complex plane as shown in \autoref{fig:contours}b.
-We evaluate along the contour where the poles are $\{i\sigma, -\Delta_{ba}\}$.
-Since the $\xi_k$ are nondegenerate,
+We evaluate along the contour that encloses the poles $\{i\sigma, -\Delta_{ba}\}$.
+Since $i\sigma \neq -\Delta_{ba}$, i.e., the poles are nondegenerate, we have two first order poles, giving
 \begin{widetext}
@@
 		\begin{split}
-			\int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi) &= 2\pi i \sum_k \lim_{\xi \rightarrow \xi_k} P(\xi) \gamma_{ijkl}(\xi) (\xi - \xi_k)\\
-			&= 2\pi i \frac{\eta_{ijkl} \sigma}{\pi}  \lim_{\xi \rightarrow i\sigma} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga} - \xi} \frac{1}{\Delta_{ba} + \xi} \left(\xi - i \sigma\right) \\
-			&+ 2\pi i \frac{\eta_{ijkl} \sigma}{\pi} \lim_{\xi \rightarrow -\Delta_{ba}} \frac{1}{(\xi + i\sigma)(\xi - i\sigma)} \frac{1}{\Delta_{ga} - \xi} \frac{1}{\Delta_{ba} + \xi} \left(\xi + \Delta_{ba}\right)\\
+			\int_{-\infty}^\infty \mathrm{d}\xi P(\xi) \gamma_{ijkl}(\xi) &= 2\pi i \sum_k \lim_{z \rightarrow z_k} P(z) \gamma_{ijkl}(z) (z - z_k)\\
+			&= 2\pi i \frac{\eta_{ijkl} \sigma}{\pi}  \lim_{z \rightarrow i\sigma} \frac{1}{(z + i\sigma)(z - i\sigma)} \frac{1}{\Delta_{ga} - z} \frac{1}{\Delta_{ba} + z} \left(z - i \sigma\right) \\ 
+			&+ 2\pi i \frac{\eta_{ijkl} \sigma}{\pi} \lim_{z \rightarrow -\Delta_{ba}} \frac{1}{(z + i\sigma)(z - i\sigma)} \frac{1}{\Delta_{ga} - z} \frac{1}{\Delta_{ba} + z} \left(z + \Delta_{ba}\right)\\
 			&= 2 \eta_{ijkl} i \sigma \left(\frac{1}{2 i \sigma} \frac{1}{\Delta_{ga} - i\sigma} \frac{1}{\Delta_{ba} + i\sigma} \right) + 2\eta_{ijkl} i \sigma \left(\frac{1}{\sigma^2 + \Delta_{ba} ^2} \frac{1}{\Delta_{ga} + \Delta_{ba}} \right)\\
@@
 	\centering
-	\includegraphics[width=6.675in]{figures/corr_contour.png}
+	\includegraphics[width=6.675in]{figures/contour.png}
 	\caption{Poles (blue dots) and contours (black lines) used to evaluate \autoref{generalcontour} for (a) anti-correlated ($c=-1$) and (b) correlated ($c=1$) modes. 

### 2024-10-08 figures/2D_spec.py

@@ -60,7 +60,7 @@ xiarrow = FancyArrowPatch(posA=(xarrow[0], -0.0257), posB=(xarrow[1], -0.0257), 
 ax0.add_artist(xiarrow)
 
 
-ax0.text((do+d)/2-0.13, -0.103, r'$\mathsf{\Delta}$', fontsize = 24)
+ax0.text((do+d)/2-0.133, -0.103, r'$\mathsf{\Delta}$', fontsize = 24)
 
 #labeling vibrational states
 jgs = [0.6, 1.0, 1.29965]
@@ -144,14 +144,14 @@ def Deltaevgo(v,x,l):
 
 
 #define numbers for AB terms
-Mge = 0.1 #M^eg_0
-Lge = 0.01 #Lambda^eg_0
-dLeg = 0.0007 #dLambda^eg / dQ
-dMgedQ = 0.007 #dM^eg / dQ
+Mge = 1 #M^eg_0
+dMgedQ = 0.04 #dM^eg / dQ
+Lge = 0.1 #Lambda^eg_0
+dLeg = 0.004 #dLambda^eg / dQ
 
 
 """Define the A and B terms"""
-y = np.linspace(5000, 60000, 2750000)
+y = np.linspace(5000, 60000, 2750000) #the frequency
 
 
 A = Mge * Lge * (f01(d)*f00(d)*Deltaevgo(0,y,0) + f11(d)*f10(d)*Deltaevgo(1,y,1) + f21(d)*f20(d)*Deltaevgo(2,y,2)) 
@@ -202,12 +202,12 @@ ax1.set_ylabel(r'$\mathsf{Amplitude \ (norm.)}$', fontsize = fontsize)
 ax1.set_xlabel(r'$\mathsf{2\omega_2} \ (\mathsf{cm}^{-1})$', fontsize = fontsize)
 
 ax1.set_yscale('log')
-ax1.set_ylim(0.001, 2)
+ax1.set_ylim(0.0001, 2)
 
 
 #put lines at the vibronic resonances
 for i in [0,1,2]:
-    ax1.vlines(x = 30000+1600*i, ymin = 0.0005, ymax = 4, color = 'gray', linestyle = '--', linewidth = 1)
+    ax1.vlines(x = 30000+1600*i, ymin = 0.00005, ymax = 4, color = 'gray', linestyle = '--', linewidth = 1)
 
 """The Real and Imaginary Parts of Gamma"""
 

### 2024-10-08 figures/2D_spec_chgsign.py

@@ -60,7 +60,7 @@ xiarrow = FancyArrowPatch(posA=(xarrow[0], -0.0257), posB=(xarrow[1], -0.0257), 
 ax0.add_artist(xiarrow)
 
 
-ax0.text((do+d)/2-0.13, -0.103, r'$\mathsf{\Delta}$', fontsize = 24)
+ax0.text((do+d)/2-0.133, -0.103, r'$\mathsf{\Delta}$', fontsize = 24)
 
 #labeling vibrational states
 jgs = [0.6, 1.0, 1.29965]
@@ -144,10 +144,10 @@ def Deltaevgo(v,x,l):
 
 
 #define numbers for AB terms
-Mge = -0.1 #M^eg_0
-Lge = 0.01 #Lambda^eg_0
-dLeg = 0.0007 #dLambda^eg / dQ
-dMgedQ = 0.007 #dM^eg / dQ
+Mge = -1 #M^eg_0
+dMgedQ = 0.04 #dM^eg / dQ
+Lge = 0.1 #Lambda^eg_0
+dLeg = 0.004 #dLambda^eg / dQ
 
 
 """Define the A and B terms"""
@@ -202,12 +202,12 @@ ax1.set_ylabel(r'$\mathsf{Amplitude \ (norm.)}$', fontsize = fontsize)
 ax1.set_xlabel(r'$\mathsf{2\omega_2} \ (\mathsf{cm}^{-1})$', fontsize = fontsize)
 
 ax1.set_yscale('log')
-ax1.set_ylim(0.001, 2)
+ax1.set_ylim(0.0001, 2)
 
 
 #put lines at the vibronic resonances
 for i in [0,1,2]:
-    ax1.vlines(x = 30000+1600*i, ymin = 0.0005, ymax = 4, color = 'gray', linestyle = '--', linewidth = 1)
+    ax1.vlines(x = 30000+1600*i, ymin = 0.00005, ymax = 4, color = 'gray', linestyle = '--', linewidth = 1)
 
 """The Real and Imaginary Parts of Gamma"""
 

### 2024-10-08 figures/contours.py

@@ -82,7 +82,7 @@ for ax in [ax0, ax1]:
     
     
 for i, ax in enumerate(fig.axes):
-    wt.artists.corner_text("abcd"[i], ax=ax, corner = 'UL', distance = 0.2, bbox = True, fontsize = fontsize, background_alpha=0.75)
+    wt.artists.corner_text("abcd"[i], ax=ax, corner = 'UL', distance = 0.3, bbox = True, fontsize = fontsize, background_alpha=0.75)
 
 if save:
     wt.artists.savefig(here / "contour.png", transparent = True, bbox_inches='tight')

### 2024-10-08 figures/varying_delta.py

@@ -70,10 +70,10 @@ def Deltaevgo(n,x,l,G):
 
 
 #define numbers for AB terms
-Mge = 0.1 #M^eg_0
-Lge = 0.01 #Lambda^eg_0
-dLeg = 0.0007 #dLambda^eg / dQ
-dMgedQ = 0.007 #dM^eg / dQ
+Mge = 1 #M^eg_0
+dMgedQ = 0.04 #dM^eg / dQ
+Lge = 0.1 #Lambda^eg_0
+dLeg = 0.004 #dLambda^eg / dQ
 
 
 #define terms
@@ -106,8 +106,8 @@ width = 175 #linewidth
 abs_max = tot(d1, wvib, width).max()
 ax0 = plt.subplot(gs[0,0])#\Delta = 0.1
 ax0.plot(y, tot(d1, wvib, width)/abs_max, linewidth = '2', label = r'$\mathsf{|A + B|}$', color = 'black', zorder = 4)
-ax0.plot(y, np.abs(A(d1, wvib, width)) / abs_max, linewidth = '2', label = r'$\mathsf{|A|}$', color = 'cyan', zorder = 3)
-ax0.plot(y, np.abs(B1(d1, wvib, width)+B2(d1, wvib, width)) / abs_max, linewidth = '2', label = r'$\mathsf{|B|}$', color = 'red', zorder = 3)
+ax0.plot(y, np.abs(A(d1, wvib, width)) / abs_max, linewidth = '2', label = r'$\mathsf{|A|}$', zorder = 3)
+ax0.plot(y, np.abs(B1(d1, wvib, width)+B2(d1, wvib, width)) / abs_max, linewidth = '2', label = r'$\mathsf{|B|}$', zorder = 3)
 
 ax0.set_ylabel(r'$\mathsf{Amplitude \ (norm.)}$', fontsize = fontsize)
 ax0.set_xlabel(r'$\mathsf{2\omega_2} \ (\mathsf{cm}^{-1})$', fontsize = fontsize)
@@ -118,13 +118,12 @@ ax0.text(textplace, 0.2, r'$\mathsf{\Gamma = 175 \ cm^{-1}}$', fontsize = 16)
 
 ax1 = plt.subplot(gs[0,1])
 d2 = 0.26 #offset
-wvib_2 = 932 #vib frequency
+wvib_1 = 932 #vib frequency
 width1 = 175 #linewidth
-abs_max1 = tot(d2, wvib_2, width1).max()
-
[…]

### 2024-10-08 paper.tex
almost ready to go

@@
 Two photons of frequency $\omega_a$ and $\omega_b$ inelastically scatter with matter, promoting or demoting a vibrational mode of frequency $\omega_v$ and emitting a single photon of frequency $\omega_a + \omega_b \mp \omega_v$.
-While most hyper-Raman experiments are performed using degenerate input pulses ($\omega_a = \omega_b$), it is possible to perform the technique with non-degenerate input pulses ($\omega_a \neq \omega_b$).
+While most hyper-Raman experiments are performed using degenerate input pulses ($\omega_a = \omega_b$),\cite{RN515} it is possible to perform the technique with non-degenerate input pulses ($\omega_a \neq \omega_b$).
 \cite{Denisov1986, Kozich2007}
@@
 CMDS methods partially mitigate this issue because emission is spatially coherent so that all emission is directional and easily collected.
-In fact, hyper-Raman transitions have been observed in several CMDS studies (sometimes under the moniker of SIVE).\cite{Zilian1994, RN350, RN351, RN352, RN353, Chen1998, RN362, RN418, Hanninen2018, Wang2021, Bonn2024, McDonnell2024}
+In fact, hyper-Raman transitions have been observed in several CMDS studies (sometimes under the moniker of SIVE, or singly vibrationall enhanced spectroscopy).\cite{Zilian1994, RN350, RN351, RN352, RN353, Chen1998, RN362, RN418, Hanninen2018, Wang2021, Bonn2024, McDonnell2024}
 
@@
 
-\autoref{fig:comparisonwmel} shows both HDFG and HSFG processes and compares them with related spectroscopies that investigate vibrational-electronic coupling.
+The HDFG and HSFG processes and related spectroscopies that investigate vibrational-electronic coupling are diagrammed in \autoref{fig:comparisonwmel} using Wave Mixing Energy Level (WMEL) diagrams.
+\cite{RN286}
 The three-wave mixing ($\chi^{(2)}$) techniques are often less applicable as they require macroscopic non-centrosymmetry under the electric dipole approximation.\cite{RN480}
 Hyper-Raman scattering itself is a six-wave mixing ($\chi^{(5)}$) technique; stimulated hyper-Raman will be weak and susceptible to four-wave mixing (FWM) cascades.\cite{RN515, RN243, Cho2000_Cascade}
-A coherent six-wave mixing analogue of hyper-Raman scattering, coherent anti-Stokes hyper-Raman spectroscopy (CAHRS), has been proposed and explored theoretically by several authors; however, it is also weak and highly susceptible to FWM cascades.\cite{Taran1977, Berger1978, Bjarnason1980, Cho1997, Cho1998}
+A coherent six-wave mixing analogue of hyper-Raman scattering, coherent anti-Stokes hyper-Raman spectroscopy (CAHRS), has been proposed and explored theoretically by several authors; however, it is also weak and susceptible to FWM cascades.\cite{Taran1977, Berger1978, Bjarnason1980, Cho1997, Cho1998}
 Of the many four-wave mixing techniques, HDFG and HSFG have strong similarity to Raman, stimulated Raman, and RISRS in that the electronic state must remove or add a $v$ quantum to the ground state (``ev'' coupling).
@@
 We note that HDFG emission can be phase-matched in media with normal dispersion while HSFG cannot.\cite{RN279, RN278} 
-In \autoref{steadystate}, we first identify the vibrational selection rules. 
-The selection rules of electronically-resonant HDFG are then identified through an expansion of electronic dipole moments following Chung and Ziegler.\cite{Ziegler1988}
+This paper is organized as follows.
+In \autoref{steadystate}, we first identify the HDFG vibrational selection rules. 
+The electronically-resonant HDFG selection rules are then identified through an expansion of electronic dipole moments following Chung and Ziegler.\cite{Ziegler1988}
 HDFG is found to be allowed in any harmonic system that has infrared active vibrations.
@@
 \cite{Sung2001}
-In the limit where input field pulse widths are much longer than electronic dephasing times and the individual molecule limit is approached, it becomes acceptable to write a time-independent relaxation matrix $\dot{\rho}^{(n)}_R= \Gamma \rho^{(n)}$, i.e.
-exponential relaxation, where $\Gamma$ is the system's dephasing rate.
+In the limit where input field pulse widths are much longer than electronic dephasing times and the individual molecule limit is approached, it becomes acceptable to write a time-independent relaxation matrix $\dot{\rho}^{(n)}_R= \Gamma \rho^{(n)}$, i.e., exponential relaxation, where $\Gamma$ is the system's dephasing rate.
 \cite{RN455, Sue1986, Sung2001}
@@
 While we have only isolated one specific HDFG resonance and time-ordering scheme (\autoref{fig:comparisonwmel}), there are several other pathways which can provide HDFG output. \cite{RN352}
-If $\omega_2$ becomes resonant and $\omega_1$ becomes non-resonant, where $\omega_2 > \omega_1$, then other HDFG pathways appear (\autoref{fig:sivewmel2}).\cite{McDonnell2024} 
-While the methods in \autoref{fig:sivewmel2} possess identical selection rules to \autoref{fig:comparisonwmel}, the pathways presented in \autoref{fig:sivewmel2} will interfere, which can amplify or obscure coherent output.
+If $\omega_2$ becomes resonant and $\omega_1$ becomes non-resonant, where $\omega_2 > \omega_1$, then other HDFG pathways appear (\autoref{fig:sivewmel2}c-f).\cite{McDonnell2024} 
+While the methods in \autoref{fig:sivewmel2} possess identical selection rules to \autoref{fig:comparisonwmel}, the pathways presented in \autoref{fig:sivewmel2} will interfere, which can amplify or decrease coherent output.
 \begin{figure*}[!htbp]
@@
 	\caption{WMEL diagrams of HDFG pathways for when (a,b) $\omega_1$ (black arrow) interacts first and (c-f) $\omega_2$ (orange arrow) interacts first. 
+		In (a,b), $\omega_1$ is resonant with a vibrational mode, but in (c-f), $\omega_2$ is resonant with a vibrational mode.
 		The states are labeled as $\ket{a,b}$, where $a$ refers to an electronic state and $b$ refers to quanta in a vibration on $a$, described in \autoref{Albrecht}.
 		In all cases, $\omega_2 > \omega_1$.
-		The virtual states fluctuate in energy dependent upon the energy of the input fields.
 	}
@@
 These pathways possess identical phase and transition moments, which yields total constructive interference, assuming similar non-resonant dispersion from each pathway.
-Conversely, in the case where only $\omega_2$ is vibrationally resonant, diagrams (c,d) and (e,f), when detuned from an electronic resonance, have identical transition moments but opposite phase. 
+Conversely, in the case where only $\omega_2$ is resonant, diagrams (c,d) and (e,f), when detuned from an electronic resonance, have identical transition moments but opposite phase. 
 As a result, the output from (c,d) and (e,f) completely destructively interfere; no signal can be obtained from these pathways when significantly detuned from an electronic state. \cite{McDonnell2024}
-Note that in the case where $\omega_1$ interacts first but $\omega_2$ is resonant, the nonlinear output generated nearly vanishes as the first resonant pulse arrives after a non-resonant pulse.
+Note that in the case where $\omega_1$ interacts first but only $\omega_2$ is resonant, the nonlinear output generated nearly vanishes as the first resonant pulse arrives after a non-resonant pulse.
 
@@
 As a result, pathways (c,d) survive and can provide output when $\omega_2+\omega_3$ is resonant with an electronic state. 
-These results provide a simple rule of thumb for collecting HDFG spectra: use \autoref{fig:sivewmel2}a,b pathways to measure spectra when significantly detuned from an electronic resonance, and any of these vibrationally resonant pathway can measure spectra when electronically resonant.
+These results provide a simple rule of thumb for collecting HDFG spectra: use \autoref{fig:sivewmel2}a,b pathways to measure spectra when significantly detuned from an electronic resonance, and any of these vibrationally resonant pathways can measure spectra when electronically resonant.
 However, since electronic states commonly have short dephasing times and significant inhomogeneous broadening,\cite{Dong2015, Lewis2015} it is likely the \autoref{fig:sivewmel2}f pathway will become triply resonant and possibly contribute greater than the other pathways.
@@
 \subsection{Vibronic Selection Rules}\label{Albrecht}
-While the Placzek treatment provides the general source of HDFG output, it does not predict the behavior of $\beta_{ijk}$ as $\omega_2 + \omega_3$ is changed.
+While the Placzek treatment provides the source of vibrationally HDFG output, it does not predict the behavior of $\beta_{ijk}$ as $\omega_2 + \omega_3$ is changed.
 We now explicitly consider electronic resonances through the $A,B,C$ decomposition of $\beta$ introduced by Chung and Ziegler, analogous to Albrecht's treatment of Raman spectroscopy (i.e., sum-over-states formalism).\cite{Albrecht1961, Ziegler1988}
@@
 We will henceforth suppress the dependence of the electronic states on \textbf{Q} for simplicity.
-It is worthwhile noting that the time-dependent Raman formalism developed by Heller \textit{et al.} can be applied to hyper-Raman scattering. \cite{Lee1979, Silverstein2012}
+It is worthwhile noting that the time-dependent Raman formalism developed by Heller \textit{et al.} can be applied to hyper-Raman scattering. \cite{Lee1979, Shoute2005, Silverstein2012}
 However, since our goal is to expose the Quantum Mechanical aspects of HDFG spectroscopy, we choose to employ the typical sum-over-states formalism.
@@
 where $R_{i}^{ab,cd}$ is the i$^{th}$ element of $\mel{a,b}{\vec{R}}{c,d}$.
-To ease readability, we use $\ket{a}$ to refer to ground state vibrational modes and $\ket{\tilde{b}}$ to refer to excited state vibrational modes.
+To ease readability, we use $\ket{a}$ to refer to ground state vibrational modes and $|\tilde{b}\rangle$ to refer to excited state vibrational modes.
 Using our definition of vibronic states, we can write, for example,
@@
 		 \langle \tilde{v}' | 0 \rangle 
-		 \frac{1}{\Delta_{e\tilde{v}', gv}}
+		 \frac{1}{\Delta_{e\tilde{v}', gv} \Delta_{m, g}}
 		 \\
@@
 			\right)
-			\langle v | \tilde{v}' \rangle \mel{\tilde{v}'}{Q_z}{0} \frac{1}{\Delta_{e\tilde{v}', gv}}\\
+			\langle v | \tilde{v}' \rangle \mel{\tilde{v}'}{Q_z}{0} \frac{1}{\Delta_{e\tilde{v}', gv} \Delta_{m, g}}\\
 		\end{split}
@@
 			\langle \tilde{v}' | 0 \rangle 
-			\frac{1}{\Delta_{e\tilde{v}', gv}}.
+			\frac{1}{\Delta_{e\tilde{v}', gv} \Delta_{m, g}}.
 	\end{split}
@@
 \end{widetext}
-Note that it is common in the hyper-Raman literature to write $\Delta_{e\tilde{v}', gv} \Delta_{mn, gv} = \Delta_{e\tilde{v}', gv}$.
+Note that to allow closure over $\ket{n}$, we write $\Delta_{mn, gv} \approx \Delta_{m, g}$, which is allowed since the system is assumed to be sufficently detuned from $\ket{n}$.
+\cite{Silverstein2012}
 Here, $\langle \tilde{a} | b \rangle$ and $\mel{\tilde{a}}{Q}{b}$ are Franck-Condon factors and Herzberg-Teller-type integrals, respectively.
@@
 To understand the vibronic structure of an excited state $|e)$, we restrict consideration to electronic transitions between $|g)$ and $|e)$.  
-Note that HDFG experiments selectively excite ground state vibrational modes through $\omega_1$; we will assume the IR beam has excited the fundamental of an IR-active mode, $\ket{g,1}$, so that hyper-Raman scattering is between the ground state and $\ket{g,1}$.
+Note that HDFG experiments selectively excite ground state vibrational modes through $\omega_1$; we will assume the IR beam has excited the fundamental of an IR-active mode, $\ket{g,1}$, so that the hyper-Raman scattering is between the ground state and $\ket{g,1}$.
 By working only in terms of this single normal mode (i.e., removing the sum over $z$ and taking $v=1$), 
@@
 				\langle \tilde{v}' | 0 \rangle 
-				\frac{1}{\Delta_{e\tilde{v}',g1}}
+				\frac{1}{ \Delta_{e\tilde{v}',g1}}
 		\end{equation}
@@
 	\end{subequations}
-where $\Lambda^{ab}_{ij} = 1/\hbar \sum_m M_i^{am}M_j^{mb} $ is the electronic two photon transition moment between $|a)$ and $|b)$.
+where $\Lambda^{ab}_{ij} = 1/\hbar \sum_m M_i^{am}M_j^{mb} \Delta^{-1}_{m, b} $ is the electronic two photon transition moment between $|a)$ and $|b)$.
 
@@
 For an allowed electronic transition, the brightness of a vibronic resonance is controlled by overlap of ground and excited state vibrational wavefunctions (Franck-Condon factors).
-The $A$ term relies on excited state perturbations to the vibrational wavefunctions; if the excited electronic state is minimally offset ($\Delta \rightarrow 0$), $\langle 1 | \tilde{v}' \rangle \langle \tilde{v}' | 0 \rangle = 0$ and $A$ vanishes, as discussed in the supporting information.
-Some $B$ terms do survive in the same limit, however; for instance, $B_1$ survives for $\tilde{v}'=1$ and $B_2$ survives for $\tilde{v}'=0$.
-In the absence of an $A$ term, the $B$ terms will dominate.
+The $A$ term relies on excited state perturbations to the vibrational wavefunctions; if the excited electronic state is minimally offset, $\langle 1 | \tilde{v}' \rangle \langle \tilde{v}' | 0 \rangle \rightarrow 0$ (\textit{vide infra}).
+In the absence of an $A$ term, $B$ terms will dominate the HDFG response.
 
@@
 Other reasonable expansion points choices include $q=\Delta$ and $q=\Delta/2$;\cite{Kundu2022}
-so long as $\vec{M}^{ij}(q)$ is roughly linear, the choice minimally affects the total calculation of $\gamma_{ijkl}$, but it does affect the weightings of $A$ and $B$ terms, primarily through changes in $\vec{M}_0^{ij}$ and the Herzberg-Teller integrals.
+so long as $\vec{M}^{ij}(q)$ and $\Lambda^{ge}(q)$ are roughly linear, the choice minimally affects the total calculation of $\gamma_{ijkl}$, but it does affect the weightings of $A$ and $B$ terms, primarily through changes in $\vec{M}_0^{ij}$ and the Herzberg-Teller integrals.
 In summary, the expansion point somewhat affects the $A$ and $B$ spectra we show, but the overall spectrum $A+B$ is not affected by this choice.
@@
 Based upon the response in Figure S3, $\Delta$, $\omega_{g1, g0}$ and $\Gamma$ have a significant impact on the resonant and pre-resonant HDFG response.
-However, the driving terms in the HDFG response are the Franck-Condon factor and Herzberg-Teller integral products, which are only dependent upon $\Delta$.
+However, the driving terms in the HDFG response are the Franck-Condon factor and Herzberg-Teller integral products, which only depend upon $\Delta$.
 Indeed, for some values of $\Delta$, most notably for $\Delta \rightarrow 0$, $A$ term products vanish, while $B$ term products are large (Figure S2).
@@
 This arises due to interference between the $A$ and $B$ terms; for our parameters, this interference is destructive in the post-resonance region (\autoref{fig:doubres_spec}c, d).
-Examination of \autoref{ABterms_DR} shows that, while $A$ and $B$ terms share the same resonances, the relative phases of the contributions can vary due to Franck-Condon factors, Herzberg Teller integrals, and the dipoles.
-In the supporting information we illustrate how changing some of these parameters affects the interference.
-Inverting the sign of one parameter eliminates the interference and restores the expected, purely Lorentzian lineshape (Figure S4).
-In bulk systems the HDFG response must be averaged over molecular frame orientations, which may also play a role in the interference.
+Examination of \autoref{ABterms_DR} shows that, while $A$ and $B$ terms share the same resonances, the relative phases of the contributions can vary due to the signs of $M^{ge}_0, \Lambda^{ge}_0, \frac{\partial M^{ge}}{\partial Q} , \frac{\partial \Lambda^{ge}}{\partial Q}$, as well as the Franck-Condon factor and Herzberg-Teller integral products, as discussed above.
+As a specific example, changing the sign of $M^{ge}_0$ eliminates the interference and restores the expected, purely Lorentzian lineshape (Figure S4).
+Additionally, in this study, the reported spectra have considered only a single element of the HDFG $\gamma_{ijkl}$ tensor.
+In bulk systems, the HDFG $\gamma_{ijkl}$ tensor must be averaged over molecular frame orientations (\autoref{eq:nfgamma}), which may also play a role in interference observed in an experimental HDFG spectrum.
 
@@
 To evaluate the feasibility of HDFG for vSFG practitioners, we have compared the relative output of each process using nominal parameters. 
-As calculated in \autoref{appendixA}, HDFG's weak $\chi^{(3)}$ value and SFG's low emission cancel somewhat, so that the output polarization of HDFG and vSFG are comparable ($\abs{P_\text{vSFG} / P_\text{HDFG}} \sim 2/3$).
+As calculated in \autoref{appendixA}, HDFG's weak $\chi^{(3)}$ value and SFG's low emission cancel somewhat, so that the output polarization of HDFG and vSFG are comparable ($\abs{P_\text{vSFG} / P_\text{HDFG}} \sim 1$).
 Transient HDFG, or IR-pump-HDFG-probe, analogous to IR-pump-vSFG-probe, is therefore also feasible under similar experimental conditions, and provides vSFG practitioners a simple method to measure bulk dynamics without significant changes in an experimental setup.
@@
 		 		\begin{split}
-		 		\abs{P^{(2)}_{\text{vSFG}}} &= \frac{N_\text{surf}}{\ell} \abs{ F_{\text{vSFG}} \langle \alpha_{ij}\mu_{k} \rangle E(\omega_2)E(\omega_1) \frac{1}{2 \varepsilon_0 \hbar i \Gamma}} 
+		 		\abs{P^{(2)}_{\text{vSFG}}} &= \frac{N_\text{surf}}{\ell} \abs{ \frac{F_{\text{vSFG}} \langle \alpha_{ij}\mu_{k} \rangle }{2D' \varepsilon_0 \hbar i \Gamma} E(\omega_2)E(\omega_1) } 
 		 		\end{split}
@@
 		 		\begin{split}
-			 		\abs{P^{(3)}_{\text{HDFG}}} &= 4 N_\text{bulk} \abs{{ F_{\text{HDFG}} \langle \beta_{ijk} \mu_{l} \rangle E{(\omega_2)}E(\omega_2)E(-\omega_1) \frac{-1}{12 \varepsilon_0 \hbar i \Gamma}}}, 
+			 		\abs{P^{(3)}_{\text{HDFG}}} &= 6 N_\text{bulk} \abs{{ \frac{-F_{\text{HDFG}} \langle \beta_{ijk} \mu_{l} \rangle }{6D \varepsilon_0 \hbar i \Gamma} E{(\omega_2)}E(\omega_2)E(-\omega_1) }}, 
 		 		\end{split}
@@
 		 \end{subequations}
-where N$_\text{bulk}$ is the bulk number density ($\sim$ 10$^{28}$ m$^{-3}$ for H$_2$O$_{(l)}$ at room temperature), N$_\text{surf}$ is the surface number density ($\sim$ 10$^{16}$ m$^{-2}$ for H$_2$O adsorbed at quartz), and $\Gamma$ is the vibrational dephasing rate.\cite{Du1994}
-The HDFG output gains a multiplicative factor of 4 because four, identical, singly resonant HDFG processes occur at pulse overlap.
+where N$_\text{bulk}$ is the bulk number density ($\sim$ 10$^{28}$ m$^{-3}$ for liquid H$_2$O at room temperature), N$_\text{surf}$ is the surface number density ($\sim$ 10$^{16}$ m$^{-2}$ for H$_2$O adsorbed at quartz at room temperature),\cite{Du1994} $D'$ is the SFG degeneracy factor, and $\Gamma$ is the vibrational dephasing rate.
+For a two-beam experiment, $D' = 2$ and $D = 3$.
+The HDFG output gains a multiplicative factor of 6 because six singly resonant HDFG processes contribute at pulse overlap.
 
@@
 \begin{equation}
-	P_\text{ratio} \equiv \frac{\abs{P^{(3)}_{\text{HDFG}}}}{\abs{P^{(2)}_{\text{vSFG}}}} \approx \frac{2}{3} \frac{N_\text{bulk}}{N_\text{surf}} \ell \abs{\frac{\left(n(\omega_2)\right)^2 + 1}{3}} \frac{\beta}{\alpha} E(\omega_2) \sim \frac{2}{3} \left(10^3 \frac{\beta}{\alpha} E(\omega_2)\right)\\
+	P_\text{ratio} \equiv \frac{\abs{P^{(3)}_{\text{HDFG}}}}{\abs{P^{(2)}_{\text{vSFG}}}} \approx 2 \frac{N_\text{bulk}}{N_\text{surf}} \ell \abs{\frac{\left(n(\omega_2)\right)^2 + 1}{3}} \frac{\beta}{\alpha} E(\omega_2) \sim 10^3 \frac{\beta}{\alpha} E(\omega_2)\\
 \end{equation}
-Ziegler has noted that for a field with intensity 10 GW/cm$^{2}$, $\frac{\beta E}{\alpha} \sim 10^{-3} $ for vibrational modes when detuned from electronic resonances, i.e.
-singly resonant vSFG and HDFG.
+Ziegler has noted that for a field with intensity 10 GW/cm$^{2}$, $\frac{\beta E}{\alpha} \sim 10^{-3} $ for vibrational modes when detuned from electronic resonances, i.e., singly resonant response.
 \cite{RN515}
 Such an intensity is easily obtained using modern ultrafast sources.
-In this limit, $P_\text{ratio} \sim 2/3$, or the HDFG output is slightly weaker than vSFG, assuming only interfacial contributions in vSFG.
+Under these conditions, $P_\text{ratio} \sim 1$, or the HDFG output is similar to that of vSFG, assuming only interfacial contributions in vSFG.
 It is important to note that this calculation assumed negligible dipole and Raman polarizability dependence upon the distance from surface normal, ignored orientational averaging effects, and presumed equivalence of local field factors, all of which can significantly reduce output from either process.

### 2024-10-08 si.tex
almost ready to go

@@
 In this section, we discuss the evaluation of Herzberg-Teller integrals when the ground and first excited state are harmonic wells of identical curvature.\cite{HerzbergTeller1933}
-% We note that Myers et al. have developed a general expression to evaluate Franck-Condon factors for two displaced harmonic wells of differing curvature,\cite{Myers1982} 
 We investigate the one dimensional case using the Hamiltonian described in the main text, $H = H_g |g) \left(g| + H_e |e\right) (e|$, where
@@
 The integral corresponds to Franck-Condon factors for $k=0$ and Herzberg-Teller integrals for $k=1$.
-The vibrational coupling integrals are written assuming the expansion of the dipole moment is taken about the equilibirum point of the ground state geometry ($q=0$), as is done in the main text.
+The vibrational coupling integrals are written assuming the dipole moment is Taylor expanded about the equilibrium point of the ground state geometry ($q=0$), as done in the main text.
 Note that in the limit $\Delta \rightarrow 0$, typical harmonic oscillator selection rules are restored, as the two wells have the same vibrational Hamiltonian and thus share a subspace of orthonormal eigenstates.
@@
 
-In the main text, the potential well offset ($\Delta$) was taken as $\Delta = 0.5$.
-Here, we vary $\Delta$ to investigate its impact on the structure of the $\abs{A+B}$ spectrum.
-The dependence of relevant Franck-Condon factors and Herzberg-Teller integrals on displacement are plotted in \autoref{fig:fcht} as a function of offset, $\Delta$.
-\autoref{fig:fcht} shows how different displacements, vibrational frequencies, and vibronic linewidths will alter the vibronic spectrum.
-The products of Franck-Condon factors and Herzberg-Teller integrals relevant to the $A,B$ coefficients discussed in the main text are plotted in \autoref{fig:fcht_product}.
-
-\pagebreak
-
 It is clear from \autoref{fig:fcht_product} that the HDFG spectrum will have a significant dependence upon $\Delta$, even for small deviations from complete overlap. 
@@
 We maintain the relationship $\max \left(\abs{B}/\abs{A}\right) \sim$ 0.1 at $\Delta = 0.5$ to facilitate comparison to the results in the main text.
-
+\pagebreak
 \begin{figure}[!htbp]
@@
 Parameters for (a,b) follow from Myers et al., whereas parameters for (c,d) follow from Brennan et al.\cite{Myers1982, Brennan2024}
+	In (a-d), the relationship $\max \left(\abs{B}/\abs{A}\right) \sim$ 0.1 at $\Delta = 0.5$ is enforced.
 } 
@@
 In addition to the linewidth and offset impacting the shape of the HDFG response, the sign of the molecular parameters $M^{ge}_0, \Lambda^{ge}_0, \frac{\partial M^{ge}}{\partial Q} , \frac{\partial \Lambda^{ge}}{\partial Q}$ will significantly impact the HDFG spectrum.
-As discussed in the main text, the atypical lineshape in the post-resonance region of the HDFG region arises due to the sign of all four aforementioned parameters being identical.
+As discussed in the main text, the atypical lineshape in the post-resonance region of the HDFG spectrum arises due to the sign of all four aforementioned parameters being identical.
 Changing the sign of one (or three) parameters will change the sign of $A, B$ and eliminate interference between the real and imaginary terms.  
-As an example, we demonstrate the resultant HDFG spectrum when $M_0^{ge} < 0$, and all other terms $>0$ (\autoref{fig:chgsign}).
+As an example (\autoref{fig:chgsign}), we demonstrate the resultant HDFG spectrum for \begin{eqnarray}
+	M^{ge}(q) = M^{ge}_0 \left(-1 + 0.04 q + \order{q^2}\right),  \\
+	\Lambda^{ge}(q) = \Lambda^{ge}_0 \left(1 + 0.04 q + \order{q^2}\right),
+\end{eqnarray}
+i.e., $M^{ge}_0 < 0$, $\Lambda^{ge}_0, \frac{\partial M^{ge}}{\partial Q} , \frac{\partial \Lambda^{ge}}{\partial Q} > 0$.
 Compared to Figure 3 of the main text, the contributions from the $A, B_1$ and $B_2$ terms to $\Re(\gamma)$ and $\Im(\gamma)$ significantly change.

### 2024-10-08 figures/2D_spec.py

@@ -68,10 +68,11 @@ jes = [1.3, 1.7, 1.9965]
 
 for i in [0,1,2]:
     kets = [r'$\mathsf{|0\rangle}$', r'$\mathsf{|1\rangle}$', r'$\mathsf{|2\rangle}$']
+    ekets = [r'$\mathsf{|\tilde{0}\rangle}$', r'$\mathsf{|\tilde{1}\rangle}$', r'$\mathsf{|\tilde{2}\rangle}$']
     ax0.hlines(y = grs(jgs[i]), xmin = -jgs[i], xmax = jgs[i], color = 'black', linestyle = '-', linewidth = 2) #gs states
     ax0.hlines(y = es(jes[i]), xmin = -jes[i]+2*d, xmax = jes[i], color = 'black', linestyle = '-', linewidth = 2) #es states
     ax0.text(jgs[i] + 0.25, grs(jgs[i])-0.03, kets[i], fontsize = 16) #labeling gs
-    ax0.text(jes[i] + 0.25, es(jes[i])-0.03, kets[i], fontsize = 16) #labeling es
+    ax0.text(jes[i] + 0.25, es(jes[i])-0.03, ekets[i], fontsize = 16) #labeling es
     
 #harmonic surface labels
 ax0.text(kg.max()+0.12, grs(kg.max())-0.05, r'$\mathsf{|g)}$', fontsize = 24)

### 2024-10-08 paper.tex
fixed quantitative
addresses PR#27

@@
 \cite{RN455, Sue1986, Sung2001}
-While exponential relaxation is usually an inappropriate description of most physical systems involving solvent-solute interactions,\cite{Sue1986, Yan1988, Li1994, Myers1997} our goal is to introduce simple, quantitative models to understand HDFG response.
+While exponential relaxation is usually an inappropriate description of most physical systems involving solvent-solute interactions,\cite{Sue1986, Yan1988, Li1994, Myers1997} our goal is to introduce simple, qualitative models to understand HDFG response.
 Thus, we write $\dot{\rho}^{(n)}_R= \Gamma \rho^{(n)}$.
@@
 \subsection{Vibronic Selection Rules}\label{Albrecht}
-While the Placzek treatment provides the source of vibrationally HDFG output, it does not predict the behavior of $\beta_{ijk}$ as $\omega_2 + \omega_3$ is changed.
+While the Placzek treatment provides selection rules for vibrationally resonant HDFG output, it does not predict HDFG output as $\omega_2 + \omega_3$ is changed.
 We now explicitly consider electronic resonances through the $A,B,C$ decomposition of $\beta$ introduced by Chung and Ziegler, analogous to Albrecht's treatment of Raman spectroscopy (i.e., sum-over-states formalism).\cite{Albrecht1961, Ziegler1988}

### 2024-10-08 paper.tex
more fixes

@@
 \end{widetext}
-Note that to allow closure over $\ket{n}$, we write $\Delta_{mn, gv} \approx \Delta_{m, g}$, which is allowed since the system is assumed to be sufficently detuned from $\ket{n}$.
+Note that to allow closure over $\ket{n}$, we write $\Delta_{mn, gv} \approx \Delta_{m, g}$, which is allowed since the system is taken to be sufficently detuned from $\ket{m,n}$.
 \cite{Silverstein2012}
@@
 \end{subequations}
-for the ground ($H_g$) and first excited ($H_e$) states, where $p$ is the dimensionless momentum coordinate and $q = \sqrt{\frac{\omega}{\hbar}} Q$ is the dimensionless position coordinate, the A and B contributions can be evaluated using Franck-Condon factors and Herzberg-Teller integrals (\autoref{fig:doubres_spec}a).
+for the ground ($H_g$) and first excited ($H_e$) states, where $p$ is the dimensionless momentum coordinate, $q = \sqrt{\frac{\omega}{\hbar}} Q$ is the dimensionless position coordinate, and $\Delta$ is the offset of the excited state surface relative to the ground state, the A and B contributions can be evaluated using Franck-Condon factors and Herzberg-Teller integrals (\autoref{fig:doubres_spec}a).
 For simplicity, we restrict consideration to $v^\prime \in \{0,1,2\}$ and take $\Delta = 0.5$.
@@
 Only a few experimental determinations of $\beta_{ijk}$ for vibrational modes have been performed.\cite{Xu1997, Shoute2005, Kelley2010}
-Methods reported in the literature to measure absolute hyper-Raman polarizabilities depend upon internal standards such as hyperpolarizabilities of dissolved samples or two-photon absorption cross sections, also difficult to measure.
+Methods reported in the literature to measure absolute hyper-Raman polarizabilities depend upon external standards, such as hyperpolarizabilities or two-photon excited fluorescence of known samples, also difficult to measure.
 \cite{Kelley2010}
@@
 For simplicity, we take $\rho^{(0)}_{gg} = 1$.
-Orientational averaging shows specific polarization schemes isolate linear combinations of different $\beta_{ijk}$ terms. \cite{Bersohn1966, Kauranen1996}
+Orientational averaging shows polarization schemes can isolate specific linear combinations of different $\beta_{ijk}$ terms. \cite{Bersohn1966, Kauranen1996}
 Substituting in \autoref{SIVEselection}, we see
@@
 		 		\begin{split}
-			 		\abs{P^{(3)}_{\text{HDFG}}} &= 6 N_\text{bulk} \abs{{ \frac{-F_{\text{HDFG}} \langle \beta_{ijk} \mu_{l} \rangle }{6D \varepsilon_0 \hbar i \Gamma} E{(\omega_2)}E(\omega_2)E(-\omega_1) }}, 
+			 		\abs{P^{(3)}_{\text{HDFG}}} &= 6 N_\text{bulk} \abs{{ \frac{-F_{\text{HDFG}} \langle \beta_{ijk} \mu_{l} \rangle }{4D \varepsilon_0 \hbar i \Gamma} E{(\omega_2)}E(\omega_2)E(-\omega_1) }}, 
 		 		\end{split}

### 2024-10-08 figures/2D_spec.py

@@ -12,7 +12,7 @@ import pathlib
 
 wt.artists.apply_rcparams(kind="publication")
 
-save = True
+save = False
 fontsize = 18
 here = pathlib.Path(__file__).resolve().parent
 

### 2024-10-08 figures/2D_spec_chgsign.py

@@ -243,7 +243,7 @@ for ax in [ax1, ax2, ax3]:
 
 for i, ax in enumerate(fig.axes):
     # ax.grid(visible=True, color="k", lw=0.5, linestyle=":")
-    wt.artists.corner_text("abcd"[i], ax=ax, corner = 'UL', distance = 0.25, bbox = True, fontsize = fontsize, background_alpha=0.75)
+    wt.artists.corner_text("abcd"[i], ax=ax, corner = 'UL', distance = 0.3, bbox = True, fontsize = fontsize, background_alpha=0.75)
 
 if save:
     wt.artists.savefig(here / "drsive_chgsign.png", transparent = True, bbox_inches='tight')

### 2024-10-08 figures/_avg_/wmels.py

@@ -9,7 +9,7 @@ wt.artists.apply_rcparams(kind="publication")
 
 
 comparisonwmel = False
-test = False
+test = True
 hdfg = False
 timeorderedwmel = True
 timeorderedwmel2 = True
@@ -196,7 +196,7 @@ if drwmel:
 if test:
     fig0 = WMEL.Artist([2,1], [0, 0.2, 1], state_names=("$\mathsf{|g\\rangle}$",
                                                                    "$\mathsf{|v\\rangle}$", 
-                                                                   "$\mathsf{|e\\rangle}$"), number_of_interactions=4, state_font_size=9, state_text_buffer = 0.6)
+                                                                   "$\mathsf{|e\\rangle}$"), number_of_interactions=5, state_font_size=9, state_text_buffer = 0.6)
 
     fig0.add_arrow([0,0], 0, [0,1], kind='bra', color="k", label = "$\mathsf{1}$", head_length = 0.075)
     fig0.add_arrow([0,0], 1, [0,2], kind='ket', color="k", label = "$\mathsf{2}$", head_length = 0.075)
@@ -205,7 +205,7 @@ if test:
     fig0.add_arrow([1,0], 0, [0,1], kind='ket', color="k", label = "$\mathsf{1}$", head_length = 0.075)
     fig0.add_arrow([1,0], 1, [1,2], kind='ket', color="k", label = "$\mathsf{2}$", head_length = 0.075)
     fig0.add_arrow([1,0], 2, [2,0], kind='out', color="blue", label = "$\mathsf{3}$", head_length = 0.075)    
-    fig0.label_columns(['$\mathsf{vDFG}$','$\mathsf{vSFG}$'], font_size = 9)
+    fig0.label_columns(['$\mathsf{DFG}$','$\mathsf{SFG}$'], font_size = 9)
     plt.savefig(here / "test.png", bbox_inches='tight')
 
 
@@ -275,8 +275,9 @@ if test:
     fig31.label_columns(['$\mathsf{CARS}$', '$\mathsf{CSRS}$'], font_size = 10)
 
     
-    fig3 = WMEL.Artist([2,1], [0, 0.2, 0.35, 1], state_names=("$\mathsf{| g\\rangle}$",
+    fig3 = WMEL.Artist([2,1], [0, 0.2, 0.35, 0.8, 1], state_names=("$\mathsf{| g\\rangle}$",
                                                                     "$\mathsf{|v\\rangle}$", 
+                                                                    "$\mathsf{|v'\\rangle}$",
[…]

### 2024-10-08 paper073024.tex

\documentclass[aip, jcp, reprint, onecolumn]{revtex4-2}

\bibliographystyle{apsrev4-2}

\usepackage{physics}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage[colorlinks=true, linkcolor=black, urlcolor=blue, citecolor=black, anchorcolor=black]{hyperref}

\graphicspath{{"figures/"}}
\begin{document}
%Title of paper
\title{Coherent IR-Hyper-Raman Four Wave Mixing Spectroscopy}

\author{Ryan P. McDonnell} 
\author{Daniel D. Kohler}
\author{John C. Wright} \email{wright@chem.wisc.edu}

\affiliation{Department of Chemistry, 
        University of Wisconsin - Madison, 
        Madison, Wisconsin 53706, 
        United States of America}

\date{\today}

\begin{abstract}
Nonlinear, four wave mixing vibrational spectroscopies are commonly used to probe electron-vibration coupling in isotropic media.
Most of these methods rely on infrared and/or Raman transitions, but methods involving hyper-Raman transitions are also possible. 
Hyper Difference Frequency Generation (HDFG) spectroscopy is an underdeveloped four wave mixing vibrational spectroscopy based on the hyper-Raman transition and IR absorption. 
HDFG is experimentally similar to vibrational sum frequency generation (vSFG) spectroscopy share similar output, making HDFG feasible for vSFG practitioners. 
Despite several experimental reports on HDFG, its spectroscopic properties have not been fully explored. 
To this end, we investigate the selection rules and behavior of HDFG spectroscopy as an upconverted infrared spectroscopy and as a probe of vibronic coupling in molecular systems.
HDFG is shown to a sensitive probe of vibronic coupling in bulk systems.
\end{abstract}

\maketitle

\section{Introduction}
Coherent multidimensional spectroscopy (CMDS) is a family of nonlinear spectroscopy methods that form the optical analogue of multidimensional nuclear magnetic resonance (NMR) spectroscopy.\cite{Cho2008}
Multiresonant, four wave mixing CMDS experiments, first proposed by Oudar and Shen in 1980,\cite{RN307} directly probe coupling and correlations between different vibrational, electronic, and vibronic states. \cite{RN281, RN103, Cho2008} 
Four wave mixing CMDS has resolved anharmonicities, ultrafast dynamics, and other inter- and intra-molecular couplings in numerous systems. \cite{Cho2008, Gaynor2017, Ziegler2018, Ogilvie2019, Bonn2021, RN325, Chen2024}
To target vibrational and electronic coupling, methods commonly make use of Raman transitions, e.g., doubly vibrationally enhanced spectroscopy (DOVE), triple sum frequency (TSF), coherent anti-Stokes Raman spectroscopy (CARS), resonant impulse stimulated Raman spectroscopy (RISRS).\cite{RN103, Dhar1994, RN345, Cho2000, RN491}
Here we explore the less-utilized hyper-Raman transitions in four wave mixing CMDS.

\begin{figure*}[!htbp]
	\centering
	\includegraphics[width=6.66in]{taxonomy.png}
	\caption{
		Some spectroscopic methods for investigating (top) electronic-vibrational coupling and (bottom) e-v-x (x: e, v, e-v, e-v-e) coupling through different order nonlinear processes.
		The light-matter interactions are depicted using Wave Mixing Energy Level (WMEL) diagrams.\cite{RN286}
		Solid and dashed horizontal lines indicate real and virtual states, whereas solid and dotted arrows indicate ket and bra side transitions, respectively. 
		The red box outlines the e-v coupling techniques (HDFG, HSFG) relevant to this manuscript.
	}
	\label{fig:comparisonwmel}
\end{figure*}

The hyper-Raman transition is the nonlinear, two photon analogue to the Raman transition.\cite{Terhune1965, Cyvin1965, Andrews1978}
Two photons of frequency $\omega_a$ and $\omega_b$ inelastically scatter with matter, promoting or demoting a vibrational mode of frequency $\omega_v$ and emitting a single photon of frequency $\omega_a + \omega_b \mp \omega_v$. 
While most hyper-Raman experiments are performed using degenerate input pulses ($\omega_a = \omega_b$), it is possible to perform the technique with non-degenerate input pulses ($\omega_a \neq \omega_b$). \cite{Denisov1986, Kozich2007}
The single photon emission is a significantly different frequency from the excitation frequencies, making rejection of excitation scatter much easier.
Unlike Raman, all infrared active modes are hyper-Raman active, which allows infrared active modes to be probed through a two-photon inelastic scattering event. \cite{Andrews1978}
One drawback is that hyper-Raman transitions are typically weak compared to their Raman counterparts, even when accounting for the high intensities available to ultrafast pulsed lasers.\cite{RN515, Kelley2010}
CMDS methods partially mitigate this issue because emission is spatially coherent so that all emission is directional and easily collected.
In fact, hyper-Raman transitions have been observed in several CMDS studies (sometimes under the moniker of SIVE).\cite{Zilian1994, RN350, RN416, RN351, RN352, RN353, Chen1998, RN362, RN418, Wang2021, Bonn2024, McDonnell2024}

Hyper difference frequency generation (HDFG) spectroscopy and hyper sum frequency generation (HSFG) spectroscopy are four wave mixing CMDS methods based on direct excitation of a vibrational mode through IR absorption and subsequent scattering to or from the vibrational mode through a hyper-Raman transition.
In HDFG/HSFG, an infrared pulse is resonant with a vibrational mode, while two other excitations stimulate the hyper-Raman scattering process.
The infrared excitation frequency selects the vibrational modes to be stimulated through the hyper-Raman transition.
The other two excitation frequencies control electronic enhancement for the hyper-Raman scattering event.

\autoref{fig:comparisonwmel} shows both HDFG and HSFG processes and compares them with related spectroscopies that investigate vibrational-electronic coupling.
The three-wave mixing ($\chi^{(2)}$) techniques are often less applicable as they require macroscopic non-centrosymmetry under the electric dipole approximation.\cite{Shen94}
Hyper-Raman scattering itself is a six-wave mixing ($\chi^{(5)}$) technique; stimulated hyper-Raman will be weak and susceptible to four-wave mixing (FWM) cascades.\cite{RN515, RN243, Cho2000_Cascade}
A coherent six-wave mixing analogue of hyper-Raman scattering, coherent anti-Stokes hyper-Raman spectroscopy (CAHRS), has been proposed and explored theoretically by several authors; however, it is also weak and highly susceptible to FWM cascades.\cite{Berger1978, Bjarnason1980, Cho1997, Cho1998}
Of the many four-wave mixing techniques, HDFG and HSFG have strong similarity to Raman, stimulated Raman, and RISRS in that the electronic state must remove or add a $v$ quantum to the ground state (``ev'' coupling).
With the other four-wave and six-wave mixing techniques (\autoref{fig:comparisonwmel}, second row), the output signal depends on more states than just a single vibrational mode and electronic state (``evx'' coupling).\cite{RN445, RN335} 
As a result, the relationship between the output and vibrational-electronic coupling is more detailed, but also more complicated.
HDFG, HSFG and Raman are more direct probes of electronic-vibrational coupling.
Notably, HDFG and HSFG can be implemented as two-color experiments (with $\omega_2=\omega_3$);\cite{Cho2001} vibrational sum frequency generation (vSFG) or difference frequency generation (vDFG) setups can be trivially reconfigured to perform HSFG or HDFG measurements, respectively, to investigate ev coupling in bulk systems.

When the hyper-Raman excitation in HDFG or HSFG is resonant or near-resonant with electronic states, the brightness of the vibrational feature depends on the vibronic structure of the electronic state.
The electronic spectrum probed in HDFG or HSFG can inform on processes that control ultrafast electronic relaxation in molecular and biological systems in similar ways to resonance Raman.\cite{Cho2001, Bredenbeck2015, Arsenault2021}
Since the selection rules of hyper-Raman scattering differ from Raman scattering, the hyper-Raman excitation spectra give a unique alternative to Raman scattering to understand vibrational spectra, electronic structure and vibronic coupling in molecular systems. \cite{Olson2018}

This paper investigates the microscopic parameters that control HDFG output. \cite{Bonn2024, McDonnell2024}
In \autoref{steadystate}, we first identify the vibrational selection rules. 
The selection rules of electronically-resonant HDFG are then identified through a Herzberg-Teller dipole expansion.
HDFG is found to be allowed in any harmonic system that has infrared active vibrations.
A simple harmonic oscillator model system is used to simulate HDFG spectra and illustrate how the excited state potential energy surface affects the hyper-Raman excitation spectrum.
After developing selection rules, some quantitative aspects of HDFG are discussed in \autoref{quant}.

\section{Selection Rules for HDFG Spectroscopy}\label{steadystate}

In this section, we investigate the properties of HDFG and make the connections between HDFG and hyper-Raman scattering explicit.
HSFG will not be discussed, but the application of our treatment to HSFG is straightforward and the selection rules are similar.
We note that HDFG emission can be phase-matched in media with normal dispersion, while HSFG cannot,\cite{RN278} although experimental strategies can be implemented to minimize phase-mismatch in HSFG experiments. \cite{Kaufman2024}

It is useful to briefly discuss the impact of time ordering on HDFG output.
Dependent upon the time-ordering schemes, it is possible to eliminate output through destructive interference.\cite{RN287}
While we have only isolated one specific HDFG resonance and time-ordering scheme (\autoref{fig:comparisonwmel}), there are several other pathways which can provide HDFG output. \cite{RN352}
If $\omega_2$ becomes resonant and $\omega_1$ becomes non-resonant, where $\omega_2 > \omega_1$, then other HDFG pathways appear (\autoref{fig:sivewmel2}).\cite{McDonnell2024} 
While the methods in \autoref{fig:sivewmel2} possess identical selection rules to \autoref{fig:comparisonwmel}, the pathways presented in \autoref{fig:sivewmel2} will interfere, which can amplify or obscure coherent output.
\begin{figure*}[!htbp]
	\centering
	\includegraphics[width=6.66 in]{figures/timeorderedwmel.png}
	\caption{WMEL diagrams of HDFG pathways for when (a,b) $\omega_1$ (black arrow) interacts first and (c-f) $\omega_2$ (orange arrow) interacts first. 
		The states are labeled as $\ket{a,b}$, where $a$ refers to an electronic state and $b$ refers to quanta in a vibration on $a$, described in \autoref{Albrecht}.
		In all cases, $\omega_2 > \omega_1$.
	}
	\label{fig:sivewmel2}
\end{figure*}

In the limit where $\omega_2+\omega_3$ is detuned from an electronic resonance, it becomes simple to interpret the interference schemes. 
The case where $\omega_1$ interacts first and is resonant, and $\omega_2 + \omega_3$ is nonresonant, yields two contributed pathways: \autoref{fig:sivewmel2} (a) and (b).
These pathways possess identical phase and transition moments, which yields total constructive interference, assuming similar non-resonant dispersion from each pathway.
Conversely, in the case where only $\omega_2$ is vibrationally resonant, diagrams (c,d) and (e,f), when detuned from an electronic resonance, have identical transition moments but opposite phase. 
As a result, the output from (c,d) and (e,f) completely destructively interfere; no signal can be obtained from these pathways when significantly detuned. \cite{RN287, McDonnell2024}
Note that in the case where $\omega_1$ interacts first but $\omega_2$ is resonant, the nonlinear output generated nearly vanishes as the first resonant pulse arrives after a non-resonant pulse.

When $\omega_2 + \omega_3$ becomes electronically resonant, the interference changes for the \autoref{fig:sivewmel2}c-f pathways.
Note that in this regime, only pathways (c,e,f) possess identical transition moments.
As a result, pathways (c,d) survive and can provide output when $\omega_2+\omega_3$ is resonant with an electronic state. 
These results provide a simple rule of thumb for collecting HDFG spectra: use \autoref{fig:sivewmel2}a,b pathways to measure spectra when significantly detuned from an electronic resonance, and any of these vibrationally resonant pathway can measure spectra when electronically resonant.
However, since electronic states commonly have short dephasing times and significant inhomogeneous broadening,\cite{Dong2015, Lewis2015} it is likely the \autoref{fig:sivewmel2}f pathway will become triply resonant and possibly contribute greater than the other pathways. 
Such instances are system dependent. 
Discussion will be isolated to the \autoref{fig:sivewmel2}a pathway in the sections that follow.

Another potential interferant in HDFG spectroscopy is direct and sequential cascades of second-order vDFG and vSFG processes.\cite{RN297, RN301}
While unimportant in achiral isotropic systems,\cite{Belkin2000} second-order cascades may become important in media where SFG and DFG are allowed, e.g. chiral media, interfaces or non-centrosymmetric media. 
Nevertheless, in the discussion that follows for the rest of this manuscript, we will assume negligible second-order cascades.

It is useful to expose relationships between nonlinear output, transition dipoles and hyper-Raman hyperpolarizabilities in the driven limit. \cite{Simpson2004}
Under the electric dipole approximation, the $I^\text{th}$ cartesian component of the third order nonlinear output polarization, ${P}^{(3)}_I$, of a four wave mixing process, induced by electric fields $E_J$, $E_K$, and $E_L$ at output frequency $\omega_4=-\omega_1 + \omega_2 + \omega_3$ is written as (using Einstein summation) \cite{RN307}
\begin{equation} \label{polarization}
{P}^{(3)}_I (\omega_4)  = \chi^{(3)}_{IJKL} E_J(\omega_3) E_K(\omega_2) E_L(\omega_1) 
\end{equation}
where $\chi^{(3)}_{IJKL}$ is the $IJKL$ element of the third order electrical susceptibility, a rank four tensor, generally written as
\begin{equation}\label{eq:nfgamma}
	\chi^{(3)}_{IJKL} = NF \langle \gamma_{ijkl} \rangle.
\end{equation}
Here $N$ is a number density and $\gamma_{ijkl}$ is the third-order polarizability (i.e., second hyperpolarizability).
The brackets indicate an orientational average.\cite{Andrews1977}
Uppercase letters refer to laboratory frame coordinates and lower case letters refer to corresponding molecular frame coordinates.
$F=\prod_j  \frac{1}{3} \left({\left(n(\omega_j)\right)^2 + 1} \right)$ is the Lorentz local field factor, where $n$ is the (frequency dependent) refractive index. \cite{Bedeaux1973}

By propagating density matrix elements in the steady state limit, the HDFG hyperpolarizability is \cite{RN133}
\begin{equation}\label{sivegamma}
		\gamma_{ijkl}^{vg} =	- \sum_{e,m} \frac{1}{\varepsilon_0} \frac{1}{4D} \frac{1}{\hbar^3} \frac{\mu^{ve}_{i} \mu^{em}_{j} \mu^{mg}_{k} \mu^{gv}_{l} }{\Delta_{ev}^{3+2-1} \Delta_{mv}^{2-1}\Delta_{gv}^{-1}}  \rho_{gg}
\end{equation}
where: $\mu^{ab}_{j}$ is the $j^{th}$ element of $\mel{a}{\vec{\mu}}{b}$, $\Delta_{kl}^{-x+y+z} = \omega_{kl} - (-\omega_{x}+\omega_{y} + \omega_{z}) - i\Gamma_{kl}$, $\omega_j$ is the frequency of the j$^{th}$ input field, $\Gamma_{kl}$ is the dephasing of $\rho_{kl}$ and $\rho_{gg}$ is the ground state population.
Here, $\ket{e}$ and $\ket{m}$ are virtual states, and thus necessarily summed over in \autoref{sivegamma}.
The pulse identifiers on the $\Delta_{kl}$ terms will be suppressed henceforth for simplicity.
$D$, the Maker-Terhune degeneracy factor, accounts for permutation symmetry of the excitation fields.\cite{RN134} 
For a HDFG experiment using two (three) distinct, non-degenerate input fields, $D = 3 (6)$.

\subsection{Vibrational Selection Rules}

It is useful to investigate the selection rules without vibronic resonance to understand how HDFG can be used as an upconverted infrared spectroscopy.
We first investigate the HDFG selection rules through a Placzek type formalism.
When $\omega_2+\omega_3$ is significantly detuned from resonance and the vibronic nature of the virtual states is ignored, the Placzek approximation can be used to study selection rules in terms of the hyper-Raman hyperpolarizability, $\beta$. \cite{Placzek1934, Long1970, Altmann1982}
Summing over the virtual states $\ket{e}$ and $\ket{m}$ forms the hyper-Raman hyperpolarizability so that\cite{Long1970} 
\begin{equation}\label{sivebeta}
	\gamma_{ijkl} =	-\frac{1}{\varepsilon_0} \frac{1}{4D \hbar}\frac{\beta^{vg}_{ijk} \mu^{gv}_{l}}{\Delta_{gv}} \rho_{gg}.
\end{equation}
Since all infrared active transitions are hyper-Raman active, HDFG is allowed for any infrared active transition. \cite{Andrews1978}
This selection rule is generally valid for any HDFG or HSFG process when $\omega_2$ and $\omega_3$ are sufficiently detuned from any resonance.

The general selection rule can be simplified by considering excitation of an infrared active normal mode.  
Assume state $v$ is the $v^{\text{th}}$ normal mode.
We Taylor expand the dipole and first hyperpolarizability operators to first order in the normal mode coordinate $Q_v$ about equilibrium:\cite{Long1970, Shen90}
\begin{subequations}
	\begin{equation}
		\mu_l = \mu_{l,0} + \left(\frac{\partial \mu_l}{\partial Q_v}\right)_0 Q_v 
	\end{equation}
	\begin{equation}
		\beta_{ijk} = \beta_{ijk,0} + \left(\frac{\partial \beta_{ijk}}{\partial Q_v}\right)_0 Q_v
	\end{equation}
\end{subequations}
Substituting into \autoref{sivebeta} gives the HDFG hyperpolarizability to $\order{Q_n}$ as \begin{equation}\label{SIVEselection}
	\gamma_{ijkl} =	-\frac{1}{\varepsilon_0} \frac{1}{8D \omega_{vg}}  \frac{1}{{\Delta_{gv}}} \ \left(\frac{\partial \beta^{vg}_{ijk}}{\partial Q_v}\right)_0 \left({\frac{\partial \mu^{gv}_{l}}{\partial Q_v}}\right)_0  \rho_{gg}
\end{equation}
where we have used $\mel{1}{\mu_{l,0}}{0} = 0 = \mel{1}{\beta_{ijk,0}}{0}$, and $\mel{v}{Q_v}{g} \equiv \mel{1}{Q_v}{0} = \sqrt{\frac{\hbar}{2\omega_{vg}}}$. Here, $\omega_{vg}$ is the characteristic $\ket{0} \rightarrow \ket{1}$ frequency.\cite{RN459}
Since \autoref{SIVEselection} is non-zero in the harmonic oscillator limit, HDFG output is allowed for infrared active normal modes in the harmonic limit.

\subsection{Vibronic Selection Rules}\label{Albrecht}
While the Placzek treatment provides the general source of HDFG output, it does not predict the behavior of $\beta_{ijk}$ as $\omega_2 + \omega_3$ is changed.
We now explicitly consider electronic resonances through the $A,B,C$ decomposition of $\beta$ introduced by Chung and Ziegler, analogous to those found in Albrecht's treatment of Raman spectroscopy.\cite{Albrecht1961, Ziegler1988} 
To employ this formalism, we write the states in a Born-Oppenheimer basis $\ket{a,b}$, where $\ket{a,b} = |a(Q)) \otimes \ket{b}$ for electronic states $\{|a(\textbf{Q}))\}$ and vibrational states $\{\ket{b}\}$ (i.e., adiabatic approximation), where \textbf{Q}, the system normal modes, is the adiabatic parameter. \cite{BornOppenheimer, Tang1970}
We will henceforth suppress the dependence of the electronic states on \textbf{Q} for simplicity.

For consistency with previous reports, we use $\vec{R}$ to denote electric transition dipole moments; $\vec{\mu}$ is reserved for transitions on the ground electronic state. \cite{Tang1970}
Following the approach which gave \autoref{sivegamma} and using the time ordering and state labeling of \autoref{fig:sivewmel2}a, we find
\begin{equation}\label{drgamma_notaylor}
	\gamma_{ijkl} = -\frac{1}{\varepsilon_0} \frac{1}{4D \hbar^3} \sum_{m,n,e,v'} \frac{
		R_{i}^{gv, ev'} 
		R_{j}^{ev',mn} 
		R_{k}^{mn,g0} 
		R_{l}^{g0,gv} 
	}{	\Delta_{ev', gv}
		\Delta_{mn, gv}
		\Delta_{g0,gv}
	}
\end{equation}
where $R_{i}^{ab,cd}$ is the i$^{th}$ element of $\mel{a,b}{\vec{R}}{c,d}$.
It is common in the hyper-Raman literature to write $\Delta_{ev', gv} \Delta_{mn, gv} = \Delta_{ev', gv}$.
Using our definition of vibronic states, we can write, for example,
$R_{i}^{gv,ev'} = \mel{v}{M_i^{ge}}{v'}$, where $\vec{M}^{ab} = (a|\vec{R}|b)$.\cite{Ziegler1974}
Expanding $\vec{M}^{ij}$ to $\order{Q}$ about the equilibrium point of the ground state potential surface as
$\vec{M}^{ij} = \vec{M}^{ij}_0 + \sum_z \frac{\partial\vec{M}^{ij}}{\partial Q_z} Q_z$
yields $A, B, C$ coefficients similar to those in the Albrecht formalism of Raman scattering, \cite{Albrecht1961, Warshel1977, Ziegler1988} so that
\begin{equation}\label{gammaabc}
		\gamma_{ijkl} \sim \left(A_{ijk} + B_{ijk} + C_{ijk}\right) \frac{\mel{v}{\mu_{l}}{0}} {\Delta_{g0,gv}}
\end{equation}
The $A$ term contains the static ($\order{Q^0}$) transitions (i.e., Condon approximation), the $B$ term depends upon $\order{Q}$ transitions (Herzberg-Teller contributions), and the $C$ term depends on $\order{Q_i Q_j}$ transitions. 
The $C$ term is suppressed in the following discussion as it depends on one and two photon forbidden transitions, making its contribution to $\gamma_{ijkl}$ roughly two orders of magnitude less than $A_{ijk}$. \cite{Ziegler1988, Neddersen1989, Bonang1992}
Note that some reports obtain $A, B$ coefficients through a Herzberg-Teller expansion of the electronic states to expose vibronic couplings via $\partial H / \partial Q$, where $H$ is the electronic Hamiltonian.\cite{HerzbergTeller1933, Petrov1985, Neddersen1989, Baranov1990}
This approach is not used here as the expansion of $\vec{M}^{ij}$ in normal mode coordinates provides sufficient physical insight into hyper-Raman selection rules.

The $A$ and $B$ coefficients, where $B = B_1 + B_2$, following closure over $\ket{n}$,\cite{Milojevich2013} are written as:
\begin{widetext}
\begin{subequations}\label{ABterms}
\begin{equation}
	\begin{split}
		A_{ijk} = \frac{1}{\hbar^2}\sum_{m,e,v'} M^{ge}_{0,i} 
		M^{em}_{0,j} 
		M^{mg}_{0,k}
		 \langle v | v' \rangle
		 \langle v' | 0 \rangle 
		 \frac{1}{\Delta_{ev', gv}}
		 \\
	\end{split}
\end{equation}
	\begin{equation}
		\begin{split}
			B_{1_{ijk}} &= \frac{1}{\hbar^2} \sum_{m,e,v',z} M^{ge}_{0,i} \left(
				\frac{\partial M^{em}_{j}}{\partial Q_z} M^{mg}_{0,k}  
				+M^{em}_{0,j} \frac{\partial M^{mg}_{k}}{\partial Q_z}
			\right)
			\langle v | v' \rangle \mel{v'}{Q_z}{0} \frac{1}{\Delta_{ev', gv}}\\
		\end{split}
	\end{equation}
	\begin{equation}
	\begin{split}
			B_{2_{ijk}} = \frac{1}{\hbar^2} \sum_{m,e,v',z} \frac{\partial M^{ge}_{i}}{\partial Q_z} M^{em}_{0,j} 
			M^{mg}_{0,k} \mel{v}{Q_z}{v'} 
			\langle v' | 0 \rangle 
			\frac{1}{\Delta_{ev', gv}}
	\end{split}
	\end{equation}
\end{subequations}
\end{widetext}
where $\langle a | b \rangle$ and $\mel{a}{Q}{b}$ are Franck-Condon factors and Herzberg-Teller-type integrals, respectively. 
Duschinsky rotation effects are ignored in this discussion. \cite{Duschinsky1937}
At this point, the expressions are valid for both electronically resonant and non-resonant cases.

To understand the vibronic structure of electronic resonance, we restrict consideration to electronic transitions between $|g)$ and $|e)$.  
Note that HDFG experiments selectively excite ground state vibrational modes through $\omega_1$; we will assume the IR beam has excited the fundamental of an IR-active mode so that hyper-Raman scattering is between this mode and the ground state. 
By working only in terms of this single normal mode (i.e., removing the sum over $z$ and taking $v=1$), 
the $A$ and $B$ terms are rewritten as 
	\begin{subequations}\label{ABterms_DR}
		\begin{equation}
			\begin{split}
				A_{ijk} = \frac{1}{\hbar}\sum_{v'} M^{ge}_{0,i} 
				\Lambda^{eg}_{0,jk}
				\langle 1 | v' \rangle
				\langle v' | 0 \rangle 
				\frac{1}{\Delta_{ev',gv}}
				\\
			\end{split}
		\end{equation}
		\begin{equation}
			\begin{split}
				B_{1_{ijk}} &= \frac{1}{\hbar} \sum_{v'} M^{ge}_{0,i}
				\frac{\partial \Lambda^{eg}_{jk}}{\partial Q} \langle 1 | v' \rangle \mel{v'}{Q}{0} 
				\frac{1}{\Delta_{ev', gv}}\\
			\end{split}
		\end{equation}
		\begin{equation}
			\begin{split}
				B_{2_{ijk}} = \frac{1}{\hbar} \sum_{v'} \frac{\partial M^{ge}_{i}}{\partial Q} 
				\Lambda^{eg}_{0,jk} 
				\mel{1}{Q}{v'} 
				\langle v' | 0 \rangle 
				\frac{1}{\Delta_{ev',gv}}
			\end{split}
		\end{equation}
	\end{subequations}
where $\Lambda^{ab}_{ij} = 1/\hbar \sum_m M_i^{am}M_j^{mb} $ is the electronic two photon transition moment between $a$ and $b$.\cite{McClain1977}

\begin{figure*}[!htbp]
	\centering
	\includegraphics[width=6.66in]{drsive_spectrum.png}
	\caption{Contributions of $A, B$ (\autoref{ABterms_DR}) to HDFG spectrum for a simple two harmonic well system.
		(a) Potential energy surfaces for a two-well system, (b) 1D HDFG spectrum for $\xi = 0.5$, $\omega_1 = \omega_{g1, g0}$. 
		It is assumed that $\omega_2 = \omega_3$.
		Note that (b) plots magnitudes of the labeled quantities.
		The vibrational states on the $|g)$ and $|e)$ manifolds are spaced 2200 cm$^{-1}$ apart, with the vibronic states $\ket{e,v'}$ given linewidths of 700 cm$^{-1}$ and $\hbar \omega_{eg}$ = 30000 cm$^{-1}$.
		Dotted lines in (b) denote the $v'$ = 0, 1, 2 vibronic resonances. 
		The vibronic one and two photon absorption operators are scaled such that $\abs{B}/\abs{A} \sim$ 0.1, following Chung and Ziegler. \cite{Ziegler1988}
		The Franck-Condon and Herzberg-Teller contributions to each of these terms are found in \autoref{T:contributions}.}
	\label{fig:doubres_spec}
\end{figure*}

The signatures of vibronic coupling in the HDFG spectrum are made clear by using a simple model.
Using a two-well system described by 
\begin{subequations}\label{Hamiltonian}
	\begin{equation}
		H_g = \frac{\hbar \omega }{2} \left(p^2 + q^2 \right)
	\end{equation}
	and
	\begin{equation}
		H_e = \frac{\hbar \omega }{2} \left(p^2 +  (q-\xi)^2 \right) + \hbar \omega_{eg}
	\end{equation}
\end{subequations}
for the ground ($H_g$) and first excited ($H_e$) states, where $p$ (momentum) and $q$ (position) are the dimensionless conjugate coordinates of the normal mode, the A and B contributions can be evaluated using Franck-Condon and Herzberg-Teller integrals tabulated in terms of the dimensionless normal mode $q$ and offset parameter $\xi$ (\autoref{fig:doubres_spec}a).\cite{Carlson1988thesis} 
For simplicity, we restrict consideration to $v^\prime \in \{0,1,2\}$ and take $\xi = 0.5$.
Note that $q = \sqrt{\frac{m^2\omega}{\hbar}} Q$.
We assume the electronic state is both one and two photon allowed.

\autoref{ABterms_DR} shows important selection rules for the vibronic transitions.
The $A$ term is allowed whenever an electronic transition has a one- and two- photon transition moment.
For centrosymmetric molecules, an electronic transition cannot be both one- and two- photon allowed by parity, so the $A$ term will vanish.
This makes HDFG a unique tool for studying the electronic structure of centrosymmetric species in isotropic media, as it is sensitive to non-Condon effects.\cite{Olson2018}
For an allowed electronic transition, the brightness of a vibronic resonance is controlled by overlap of ground and excited state vibrational wavefunctions (Franck-Condon factors).
The $A$ term relies on excited state perturbations to the vibrational wavefunctions; if the excited electronic state minimally changes potential energy surface, so that ground and excited state vibrational eigenfunctions are identical, $\langle 1 | v^\prime \rangle \langle v^\prime | 0 \rangle = 0$ and $A$ vanishes.
This follows from $\lim_{\xi \rightarrow 0} \langle v' | 0 \rangle = 0$, $v^\prime \neq 0$, for wells with identical curvature.
Some $B$ terms do survive in the same limit, however; for instance, $B_1$ survives for $v^\prime=1$ and $B_2$ survives for $v^\prime=0$.
In the absence of an $A$ term, the $B$ terms will dominate.
The $B_1$ and $B_2$ terms involve different types of vibronic coupling pathways.
In $B_1$, the Herzberg-Teller coupling is associated with the two-photon absorption process, whereas in $B_2$, the Herzberg-Teller coupling is associated with one-photon emission.

\autoref{fig:doubres_spec}b shows the simulated $\omega_2+\omega_3$ spectrum for this two-well system.  The spectrum selectively probes vibronic pathways from $\ket{g,0}$ to $\ket{g,1}$.
In the resonant region, the $A$ and $B$ terms contain character from all three possible transitions between $\ket{g,0}$, $\ket{e,v'}$ and $\ket{g,1}$. 
Significant contributions from $\ket{e,0}$ and $\ket{e,1}$ in the $A$ term spectrum correspond well with expectations given the relative wavefunction overlap in \autoref{fig:doubres_spec}a, tabulated in \autoref{T:contributions}. 
Similarly, the $B_1$ term is dominated by coupling with the $\ket{e,1}$ state and $B_2$ is dominated by coupling with the $\ket{e,0}$ state (\autoref{T:contributions}). 
Note that contributions involving $\ket{e,2}$ are suppressed relative to the $\ket{e,0}$ and $\ket{e,1}$ contributions in the $A$ and $B$ terms.
This is expected, considering the large change in quantum number when involving $\ket{e,2}$ and the offset of the potential wells in \autoref{Hamiltonian}.

In the pre-resonance region, both $A$ and $B$ terms die off as $\sim \Delta_{e0,gv}^{-1}$.
We point this out because a persistent belief in Raman analysis is that $A$ terms disappear and $B$ terms dominate when significantly detuned from electronic resonance.
% such that $\Delta_{ev', g0} \approx \Delta_{eg}$, i.e., the resonance denominator loses $\ket{v'}$ dependence. 
The belief arises from the approximation $\abs{\omega_{ev',gv} - 2\omega_2} \gg 2\Gamma_{ev',gv}$, which then removes $A$ through a closure relationship.\cite{Neddersen1989}
As has been discussed elsewhere, however, this approximation is in many cases invalid, especially when vibrational energies are large, like those explored here.\cite{Warshel1977, Li1990, Gong2015}
This means that it is difficult to isolate $B$ terms when $A$ terms are present.
As such, HDFG will have difficulty examining non-Condon effects ($B$ term contributions) noncentrosymmetric systems.

\begin{table}[!htbp]
	\caption{\label{T:contributions} Franck-Condon and/or Herzberg-Teller contributions to $A$, $B_1$, $B_2$ terms between $\ket{g,0}$, $\ket{g,1}$ and vibronic states $\ket{e,0}$, $\ket{e,1}$, $\ket{e,2}$ for \autoref{Hamiltonian} with an offset $\xi = 0.5$.
	Closed-form expressions for the Franck-Condon and Herzberg-Teller integrals used here have been tabulated by Carlson.\cite{Carlson1988thesis}}
	\begin{ruledtabular}
		\begin{tabular}{cccc}
			$2\omega_2$ Electronic Resonance & $\ket{e,0}$ & $\ket{e,1}$ & $\ket{e,2}$\\
			\hline  
			$A$ 
			& $\langle 1 | 0 \rangle \langle 0 | 0 \rangle = 0.31 $  
			& $\langle 1 | 1 \rangle \langle 1 | 0 \rangle = 0.27 $ 
			& $\langle 1 | 2 \rangle \langle 2 | 0 \rangle = -0.04$\\

			$B_1$ 
			& $\langle 1 | 0 \rangle \mel{0}{Q}{0} = -0.08$ 
			& $\langle 1 | 1 \rangle \mel{1}{Q}{0} = 0.48$ 
			&$\langle 1 | 2 \rangle \mel{2}{Q}{0} = 0.14$\\

			$B_2$ 
			& $\mel{1}{Q}{0} \langle 0 | 0 \rangle = 0.55$  
			& $\mel{1}{Q}{1} \langle 1 | 0 \rangle = -0.07$ 
			& $\mel{1}{Q}{2} \langle 2 | 0 \rangle = 0.08$\\
		\end{tabular}
	\end{ruledtabular}
\end{table}

\section{Quantitative Aspects of HDFG}\label{quant}
% Despite their increasing use for dissecting intra and intermolecular interactions, CMDS techniques are usually not feasible for most laboratories, as they usually demand the use of multiple optical parametric amplifiers and/or complex acousto-optic modulators. \cite{Chen2016}
% Unlike most four wave mixing techniques, HDFG can be performed using only two input beams (i.e., two color HDFG).
%

\subsection{vSFG detection levels are adequate for HDFG}

Can vSFG experimental setups detect HDFG signals?
SFG setups typically leverage the surface selectivity of $\chi^{(2)}$ polarizations,\cite{RN132, RN133} which results in extremely small emission volumes, so SFG setups are typically quite sensitive.
However, HDFG is a weak $\chi^{(3)}$ process because it depends upon hyper-Raman cross-sections, which are commonly several orders of magnitude weaker than corresponding Raman transitions.\cite{RN515}
Since HDFG can be performed as a two-beam experiment, it is useful to identify whether vSFG and HDFG responses are similar to quantify hyper-Raman-based FWM response from bulk, isotropic systems.
To evaluate the feasibility of HDFG for vSFG practitioners, we have compared the relative output of each process using nominal parameters. 
As calculated in \autoref{appendixA}, HDFG's weak $\chi^{(3)}$ value and SFG's low emission cancel somewhat, so that the output polarization of HDFG and vSFG are comparable ($\abs{P_\text{vSFG} / P_\text{HDFG}} \sim 1$).
Transient HDFG, or IR-pump-HDFG-probe, analogous to IR-pump-vSFG-probe, is therefore also feasible under similar experimental conditions, and provides vSFG practitioners a simple method to measure bulk dynamics without significant changes in an experimental setup. 
Therefore, HDFG is a feasible spectroscopy for practitioners of vSFG both in terms of experimental setup and detection feasibility.

\subsection{Extraction of hyper-Raman hyperpolarizability}

Compared to $\vec{\mu}$ and $\alpha_{ij}$, it is difficult to measure $\beta_{ijk}$ values through spontaneous hyper-Raman experiments.\cite{Kelley2010}
Only a few experimental determinations of $\beta_{ijk}$ for vibrational modes have been performed.\cite{Xu1997, Shoute2005, Kelley2010}
Methods reported in the literature to measure absolute hyper-Raman polarizabilities depend upon internal standards such as hyperpolarizabilities of dissolved samples or two-photon absorption cross sections, also difficult to measure. \cite{Kelley2010} 
In the method introduced by Levenson and Bloembergen (Bloembergen interferometry experiment), an internal standard interferes with the resonant lineshape of a $\chi^{(3)}$ process. \cite{Levenson1974_1, Levenson1974_2}
Self-heterodyning of the internal standard signal measures $\chi^{(3)}$ and does not require measurement of absolute intensities. 
Since the Bloembergen interferometry experiment only relies on the third order susceptibility for measured species (e.g., benzene or CaF$_2$),\cite{Levenson1974_2} it is possible to use quantitative four wave mixing spectroscopy to calculate $\beta_{ijk}$ values for infrared active vibrations.
It is thus useful to investigate how a treatment of orientational averaging can extract $\beta_{ijk}$ from the HDFG $\chi^{(3)}_{IJKL}$ expression.

Using \autoref{eq:nfgamma} and \autoref{sivebeta}, we can write
\begin{equation}\label{chi3}
		\chi^{(3)}_{IJKL} = -\frac{NF}{4D \hbar \varepsilon_0 \Delta_{gv}} \langle \beta_{ijk} \mu_l \rangle \rho_{gg}\\
\end{equation}
For simplicity, we take $\rho_{gg} = 1$.
The steps behind orientational averaging of $\gamma_{ijkl}$, a rank four tensor in the molecular frame, are detailed elsewhere.\cite{Andrews1977, McDonnell2024}
Briefly, a tensor in the molecular frame, $A_{ijkl}$, is transformed into an element of the same tensor in the laboratory frame, $\langle A \rangle_{IJKL}$, through $\langle A \rangle_{IJKL}$ = $\theta^{ijkl}_{IJKL} A_{ijkl}$, where summation over repeated indices is implied and $\theta$ is the transformation operator. \cite{McDonnell2024, Andrews1977}
Orientational averaging shows specific polarization schemes isolate linear combinations of different $\beta_{ijk}$ terms. \cite{Bersohn1966, Willetts1992, Kauranen1996}
Substituting in \autoref{SIVEselection}, we see
\begin{equation}\label{betasive}
	\left\langle \frac{\partial \beta}{\partial Q_v} {\frac{\partial \mu}{\partial Q_v}} \right\rangle _{IJKL} = -\frac{8D \varepsilon_0}{NF}  {\Gamma_{gv} \omega_{vg}} \chi^{(3)}_{IJKL}
\end{equation}
$\chi^{(3)}$ itself can be extracted with use of an internal standard.\cite{Levenson1974_1, Levenson1974_2}
Since $\abs{\partial \mu / \partial Q}$ values can be extracted from FT-IR spectra,\cite{RN459} HDFG can give quantitative information on the magnitude of $\beta_{ijk}$ for infrared active vibrations.
Additionally, by using non-degenerate input frequencies to stimulate the hyper-Raman transition, the asymmetric properties of $\beta_{ijk}$ can be examined and quantified. \cite{Christie1971, Denisov1986, Kozich2007}
These quantitative aspects of HDFG could prove useful for examining how well computational methods calculate $\beta_{ijk}$ values.

\section{Conclusions}\label{conclusion}
Coherent vibrational, hyper-Raman coherent four wave mixing spectroscopies are identified and discussed.
Hyper difference frequency generation (HDFG) possesses infrared absorption and vibronic hyper-Raman scattering selection rules.
As a result, HDFG output is sensitive to the relative overlap of potential energy surfaces.
In HDFG, using the Chung-Ziegler approach to vibronic hyper-Raman scattering, output is dependent upon changes in different potential energy surfaces along the coordinate of the vibrational mode selected by the infrared input. 
If the potential energy surface is not significantly modulated along the vibrational coordinate of interest, then output is dominated by $B$ term resonances, i.e. Herzberg-Teller coupling.
As a result, HDFG possesses types of site-selective properties analogous to those of coherent Raman experiments, which can allow for a thorough analysis of vibronic coupling schemes in isotropic systems.
We show that HDFG provides alternative methods to extract the hyper-Raman hyperpolarizability of infrared active vibrations. 
Since HDFG is approachable as a two-beam experiment, analogous to vibrational sum-frequency generation, and phase-matchable in media with normal dispersion, HDFG should be applicable towards understanding vibrational spectroscopy and dynamics, e.g. single quantum coherence free induction decay dynamics, in a variety of relevant molecular and materials systems.

\section{Data Availability Statement}
The workup scripts that support this study are permissively licensed and available for reuse at \href{https://osf.io/2amkq/}{https://osf.io/2amkq/}.

\section{Acknowledgments}
This work received support from the National Science Foundation (Grant no. CHE-2203290).
R.P.M. acknowledges support from the National Science Foundation Graduate Research Fellowship Program (Grant no. DGE-2137424).

\section{Appendix: Comparison of vSFG and two-beam HDFG output}\label{appendixA}
To motivate the application of HDFG spectroscopy, we perform a calculation to compare two-color HDFG and vSFG output, where absorption effects are neglected for simplicity. \cite{Carlson1989}
vSFG is a $\chi^{(2)}$ technique whose output, When only vibrationally resonant, the vSFG $\chi^{(2)}$ scales as $\chi^{(2)}_{IJK} \sim \langle \alpha_{ij} \mu_k \rangle$, where $\alpha_{ij}$ is the Raman polarizability tensor, whose phase-matching constraint is  $\vec{k}_3 = \vec{k}_1 + \vec{k}_2$.
HDFG is phase-matchable under $\vec{k}_4 = -\vec{k}_1 + 2\vec{k}_2$ conditions for most, if not all, vibrational resonances.
The output polarizations under the electric dipole approximation are written as
	 	\begin{subequations}
		 	\begin{equation}\label{PSFG}
		 		\begin{split}
		 		\abs{P^{(2)}_{\text{vSFG}}} &= \frac{N_\text{surf}}{\ell} \abs{F_{\text{SFG}} \langle \alpha_{ij}\mu_{k} \rangle E(\omega_2)E(\omega_1)} 
		 		\end{split}
			 \end{equation}
		 	\begin{equation}
		 		\begin{split}
			 		\abs{P^{(3)}_{\text{HDFG}}} &= N_\text{bulk} \abs{F_{\text{HDFG}} \langle \beta_{ijk} \mu_{l} \rangle E{(\omega_2)}E(\omega_2)E(-\omega_1)}
		 		\end{split}
			 \end{equation}
		 \end{subequations}
where N$_\text{bulk}$ is the bulk number density ($\sim$ 10$^{28}$ m$^{-3}$ for H$_2$O$_{(l)}$ at room temperature), and N$_\text{surf}$ is the surface number density ($\sim$ 10$^{16}$ m$^{-2}$ for H$_2$O adsorbed at quartz).\cite{Du1994}	
For simplicity, we assume that $\chi^{(2)}$ is a spatial constant so that $\int_{0^-}^\ell \mathrm{d}z \langle \alpha_{ij}\mu_{k} \rangle \approx \ell \langle \alpha_{ij}\mu_{k} \rangle$, where $z$ is oriented along the surface normal and $0^{-}$ is the edge of the interface where substrate begins. 
We take the film thickness ($\ell$) probed by vSFG to be 1 nm, much less than the vSFG coherence length.\cite{RN133}
A normal dispersion curve is assumed so that $n(\omega_1+\omega_2) \approx n(2\omega_2-\omega_1)$.
To simplify analysis, orientational averaging is ignored (e.g., $\langle \beta_{ijk} \mu_{l} \rangle \approx \beta \mu$) and the input and output fields are taken to be co-polarized, so that
\begin{equation}
	P_\text{ratio} \equiv \frac{\abs{P^{(3)}_{\text{HDFG}}}}{\abs{P^{(2)}_{\text{vSFG}}}} \approx \frac{N_\text{bulk}}{N_\text{surf}} \abs{\frac{\left(n(\omega_2)\right)^2 + 1}{3}} \frac{\beta}{\alpha} E(\omega_2) \ell \sim 10^3 \frac{\beta}{\alpha} E(\omega_2)\\
\end{equation}
Ziegler has noted that for a field with intensity 10 GW/cm$^{2}$, $\frac{\beta E}{\alpha} \sim 10^{-3} $ for vibrational modes when $E(\omega_2)$ is largely detuned from electronic resonances. \cite{RN515}
Such an intensity is easily obtained using modern ultrafast sources.
In this limit, $P_\text{ratio} \sim 1$, or the HDFG output is roughly as strong as vSFG, assuming only interfacial contributions in vSFG.
It is important to note that this calculation assumed negligible dipole and Raman polarizability dependence upon the distance from surface normal, ignored orientational averaging effects, and presumed equivalence of local field factors, all of which can significantly reduce output from either process. 
Nevertheless, since HDFG produces a number of photons similar to that of vSFG, HDFG is a viable technique for investigating bulk systems.
Laboratories which use vSFG to investigate interfacial species at buried interfaces thus have the ingredients necessary to perform a HDFG experiment in a transmission geometry. \cite{Piontek2023_1}
This method provides vSFG practitioners the ability to measure spectra and dephasing dynamics in isotropic media without many meaningful changes in their optical setup, and thus compare spectroscopy and dephasing in the bulk and at the interface.\cite{RN224}

\section{References}
% Create the reference section using BibTeX:
\bibliography{library.bib}

\end{document}
%

### 2024-10-09 paper.tex

@@
 CMDS methods partially mitigate this issue because emission is spatially coherent so that all emission is directional and easily collected.
-In fact, hyper-Raman transitions have been observed in several CMDS studies (sometimes under the moniker of SIVE, or singly vibrationall enhanced spectroscopy).\cite{Zilian1994, RN350, RN351, RN352, RN353, Chen1998, RN362, RN418, Hanninen2018, Wang2021, Bonn2024, McDonnell2024}
+In fact, hyper-Raman transitions have been observed in several CMDS studies (sometimes under the moniker of SIVE, or singly vibrationally enhanced spectroscopy).\cite{Zilian1994, RN350, RN351, RN352, RN353, Chen1998, RN362, RN418, Hanninen2018, Wang2021, Bonn2024, McDonnell2024}
 

### 2024-10-09 paper.tex
As submitted 100924
JCP requested no TOC image in and library built into body of text

--- 2024-10-08 paper.tex
@@
 % Create the reference section using BibTeX:
-\bibliography{library.bib}
-
-\begin{figure*}[!htbp]
-	\centering
-	\includegraphics[width=6.66in]{toc.png}
-	\caption{
-		TOC Image.
-	} 
-	\label{fig:toc}
-\end{figure*}
+%\bibliography{library.bib}
+%apsrev4-2.bst 2019-01-14 (MD) hand-edited version of apsrev4-1.bst
+%Control: key (0)
+%Control: author (72) initials jnrlst
+%Control: editor formatted (1) identically to author
+%Control: production of article title (-1) disabled
+%Control: page (0) single
+%Control: year (1) truncated
+%Control: production of eprint (0) enabled
+\begin{thebibliography}{112}%
+	\makeatletter
+	\providecommand \@ifxundefined [1]{%
+		\@ifx{#1\undefined}
+	}%
+	\providecommand \@ifnum [1]{%
+		\ifnum #1\expandafter \@firstoftwo
+		\else \expandafter \@secondoftwo
+		\fi
+	}%
+	\providecommand \@ifx [1]{%
+		\ifx #1\expandafter \@firstoftwo
+		\else \expandafter \@secondoftwo
+		\fi
+	}%
+	\providecommand \natexlab [1]{#1}%
+	\providecommand \enquote  [1]{``#1''}%
+	\providecommand \bibnamefont  [1]{#1}%
+	\providecommand \bibfnamefont [1]{#1}%
+	\providecommand \citenamefont [1]{#1}%
+	\providecommand \href@noop [0]{\@secondoftwo}%
+	\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
+	\providecommand \@href[1]{\@@startlink{#1}\@@href}%
+	\providecommand \@@href[1]{\endgroup#1\@@endlink}%
+	\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
+		`\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
+	\providecommand \@@startlink[1]{}%
+	\providecommand \@@endlink[0]{}%
+	\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
+	\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
+	\providecommand \urlprefix  [0]{URL }%
+	\providecommand \Eprint [0]{\href }%
+	\providecommand \doibase [0]{https://doi.org/}%
+	\providecommand \selectlanguage [0]{\@gobble}%
+	\providecommand \bibinfo  [0]{\@secondoftwo}%
+	\providecommand \bibfield  [0]{\@secondoftwo}%
+	\providecommand \translation [1]{[#1]}%
+	\providecommand \BibitemOpen [0]{}%
+	\providecommand \bibitemStop [0]{}%
+	\providecommand \bibitemNoStop [0]{.\EOS\space}%
+	\providecommand \EOS [0]{\spacefactor3000\relax}%
+	\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
+	\let\auto@bib@innerbib\@empty
+	%</preamble>
+	\bibitem [{\citenamefont {Cho}(2008)}]{Cho2008}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+			{Cho}},\ }\href {https://doi.org/10.1021/cr078377b} {\bibfield  {journal}
+		{\bibinfo  {journal} {Chemical Reviews}\ }\textbf {\bibinfo {volume} {108}},\
+		\bibinfo {pages} {1331} (\bibinfo {year} {2008})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Oudar}\ and\ \citenamefont {Shen}(1980)}]{RN307}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~L.}\ \bibnamefont
+			{Oudar}}\ and\ \bibinfo {author} {\bibfnamefont {Y.~R.}\ \bibnamefont
+			{Shen}},\ }\href {https://doi.org/10.1103/PhysRevA.22.1141} {\bibfield
+		{journal} {\bibinfo  {journal} {Phys. Rev. A}\ }\textbf {\bibinfo {volume}
+			{22}},\ \bibinfo {pages} {1141} (\bibinfo {year} {1980})}\BibitemShut
+	{NoStop}%
+	\bibitem [{\citenamefont {Nguyen}\ and\ \citenamefont {Wright}(1985)}]{RN281}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~C.}\ \bibnamefont
+			{Nguyen}}\ and\ \bibinfo {author} {\bibfnamefont {J.~C.}\ \bibnamefont
+			{Wright}},\ }\href
+	{https://doi.org/https://doi.org/10.1016/0009-2614(85)80208-6} {\bibfield
+		{journal} {\bibinfo  {journal} {Chemical Physics Letters}\ }\textbf {\bibinfo
+			{volume} {117}},\ \bibinfo {pages} {224} (\bibinfo {year}
+		{1985})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Wright}\ \emph {et~al.}(1991)\citenamefont {Wright},
+		\citenamefont {Carlson}, \citenamefont {Hurst}, \citenamefont {Steehler},
+		\citenamefont {Riebe}, \citenamefont {Price}, \citenamefont {Nguyen},\ and\
+		\citenamefont {Lee}}]{RN103}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~C.}\ \bibnamefont
+			{Wright}}, \bibinfo {author} {\bibfnamefont {R.~J.}\ \bibnamefont {Carlson}},
+		\bibinfo {author} {\bibfnamefont {G.~B.}\ \bibnamefont {Hurst}}, \bibinfo
+		{author} {\bibfnamefont {J.~K.}\ \bibnamefont {Steehler}}, \bibinfo {author}
+		{\bibfnamefont {M.~T.}\ \bibnamefont {Riebe}}, \bibinfo {author}
+		{\bibfnamefont {B.~B.}\ \bibnamefont {Price}}, \bibinfo {author}
+		{\bibfnamefont {D.~C.}\ \bibnamefont {Nguyen}},\ and\ \bibinfo {author}
+		{\bibfnamefont {S.~H.}\ \bibnamefont {Lee}},\ }\href
+	{https://doi.org/10.1080/01442359109353262} {\bibfield  {journal} {\bibinfo
+			{journal} {International Reviews in Physical Chemistry}\ }\textbf {\bibinfo
+			{volume} {10}},\ \bibinfo {pages} {349} (\bibinfo {year} {1991})}\BibitemShut
+	{NoStop}%
+	\bibitem [{\citenamefont {Gaynor}\ and\ \citenamefont
+		{Khalil}(2017)}]{Gaynor2017}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~D.}\ \bibnamefont
+			{Gaynor}}\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+			{Khalil}},\ }\href {https://doi.org/10.1063/1.4991745} {\bibfield  {journal}
+		{\bibinfo  {journal} {Journal of Chemical Physics}\ }\textbf {\bibinfo
+			{volume} {147}},\ \bibinfo {pages} {094202} (\bibinfo {year}
+		{2017})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Mandal}\ \emph {et~al.}(2018)\citenamefont {Mandal},
+		\citenamefont {Ng~Pack}, \citenamefont {Shah}, \citenamefont {Erramilli},\
+		and\ \citenamefont {Ziegler}}]{Ziegler2018}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+			{Mandal}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Ng~Pack}},
+		\bibinfo {author} {\bibfnamefont {P.~P.}\ \bibnamefont {Shah}}, \bibinfo
+		{author} {\bibfnamefont {S.}~\bibnamefont {Erramilli}},\ and\ \bibinfo
+		{author} {\bibfnamefont {L.~D.}\ \bibnamefont {Ziegler}},\ }\href
+	{https://doi.org/10.1103/PhysRevLett.120.103401} {\bibfield  {journal}
+		{\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {120}},\
+		\bibinfo {pages} {103401} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Song}\ \emph {et~al.}(2019)\citenamefont {Song},
+		\citenamefont {Schubert}, \citenamefont {Maret}, \citenamefont {Burdick},
+		\citenamefont {Dunietz}, \citenamefont {Geva},\ and\ \citenamefont
+		{Ogilvie}}]{Ogilvie2019}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
+			{Song}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Schubert}},
+		\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Maret}}, \bibinfo
+		{author} {\bibfnamefont {R.~K.}\ \bibnamefont {Burdick}}, \bibinfo {author}
+		{\bibfnamefont {B.~D.}\ \bibnamefont {Dunietz}}, \bibinfo {author}
+		{\bibfnamefont {E.}~\bibnamefont {Geva}},\ and\ \bibinfo {author}
+		{\bibfnamefont {J.~P.}\ \bibnamefont {Ogilvie}},\ }\href
+	{https://doi.org/10.1039/C9SC02329A} {\bibfield  {journal} {\bibinfo
+			{journal} {Chem. Sci.}\ }\textbf {\bibinfo {volume} {10}},\ \bibinfo {pages}
+		{8143} (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Vietze}\ \emph {et~al.}(2021)\citenamefont {Vietze},
+		\citenamefont {Backus}, \citenamefont {Bonn},\ and\ \citenamefont
+		{Grechko}}]{Bonn2021}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+			{Vietze}}, \bibinfo {author} {\bibfnamefont {E.~H.~G.}\ \bibnamefont
+			{Backus}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Bonn}},\ and\
+		\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Grechko}},\ }\href
+	{https://doi.org/10.1063/5.0047918} {\bibfield  {journal} {\bibinfo
+			{journal} {Journal of Chemical Physics}\ }\textbf {\bibinfo {volume} {154}},\
+		\bibinfo {pages} {174201} (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Daniels}\ \emph {et~al.}(2022)\citenamefont
+		{Daniels}, \citenamefont {Wells},\ and\ \citenamefont {Chen}}]{RN325}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~A.}\ \bibnamefont
+			{Daniels}}, \bibinfo {author} {\bibfnamefont {T.~A.}\ \bibnamefont {Wells}},\
+		and\ \bibinfo {author} {\bibfnamefont {P.~C.}\ \bibnamefont {Chen}},\ }\href
+	{https://doi.org/10.1063/5.0109084} {\bibfield  {journal} {\bibinfo
+			{journal} {Journal of Chemical Physics}\ }\textbf {\bibinfo {volume} {157}},\
+		\bibinfo {pages} {184201} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Chen}\ and\ \citenamefont
+		{Daniels}(2024)}]{Chen2024}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~C.}\ \bibnamefont
+			{Chen}}\ and\ \bibinfo {author} {\bibfnamefont {D.~A.}\ \bibnamefont
+			{Daniels}},\ }\href {https://doi.org/10.1021/acs.jpclett.3c03254} {\bibfield
+		{journal} {\bibinfo  {journal} {Journal of Physical Chemistry Letters}\
+		}\textbf {\bibinfo {volume} {15}},\ \bibinfo {pages} {1234} (\bibinfo {year}
+		{2024})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Dhar}\ \emph {et~al.}(1994)\citenamefont {Dhar},
+		\citenamefont {Rogers},\ and\ \citenamefont {Nelson}}]{Dhar1994}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+			{Dhar}}, \bibinfo {author} {\bibfnamefont {J.~A.}\ \bibnamefont {Rogers}},\
+		and\ \bibinfo {author} {\bibfnamefont {K.~A.}\ \bibnamefont {Nelson}},\
+	}\href {https://doi.org/10.1021/cr00025a006} {\bibfield  {journal} {\bibinfo
+			{journal} {Chemical Reviews}\ }\textbf {\bibinfo {volume} {94}},\ \bibinfo
+		{pages} {157} (\bibinfo {year} {1994})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Zhao}\ and\ \citenamefont {Wright}(1999)}]{RN345}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
+			{Zhao}}\ and\ \bibinfo {author} {\bibfnamefont {J.~C.}\ \bibnamefont
+			{Wright}},\ }\href {https://doi.org/10.1103/PhysRevLett.83.1950} {\bibfield
+		{journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo
+			{volume} {83}},\ \bibinfo {pages} {1950} (\bibinfo {year}
+		{1999})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Cho}(2000)}]{Cho2000}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+			{Cho}},\ }\href {https://doi.org/10.1103/PhysRevA.61.023406} {\bibfield
+		{journal} {\bibinfo  {journal} {Phys. Rev. A}\ }\textbf {\bibinfo {volume}
+			{61}},\ \bibinfo {pages} {023406} (\bibinfo {year} {2000})}\BibitemShut
+	{NoStop}%
+	\bibitem [{\citenamefont {Boyle}\ \emph {et~al.}(2014)\citenamefont {Boyle},
+		\citenamefont {Neff-Mallon}, \citenamefont {Handali},\ and\ \citenamefont
+		{Wright}}]{RN491}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.~S.}\ \bibnamefont
+			{Boyle}}, \bibinfo {author} {\bibfnamefont {N.~A.}\ \bibnamefont
+			{Neff-Mallon}}, \bibinfo {author} {\bibfnamefont {J.~D.}\ \bibnamefont
+			{Handali}},\ and\ \bibinfo {author} {\bibfnamefont {J.~C.}\ \bibnamefont
+			{Wright}},\ }\href {https://doi.org/10.1021/jp5018554} {\bibfield  {journal}
+		{\bibinfo  {journal} {Journal of Physical Chemistry A}\ }\textbf {\bibinfo
+			{volume} {118}},\ \bibinfo {pages} {3112} (\bibinfo {year}
+		{2014})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Lee}\ and\ \citenamefont {Albrecht}(1985)}]{RN286}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+			{Lee}}\ and\ \bibinfo {author} {\bibfnamefont {A.~C.}\ \bibnamefont
+			{Albrecht}},\ }\bibinfo {title} {A {U}nified {V}iew of {R}aman, {R}esonance
+		{R}aman, and {F}luorescence {S}pectroscopy (and their {A}nalogues in
+		{T}wo-{P}hoton {A}bsorption)},\ in\ \href@noop {} {\emph {\bibinfo
+			{booktitle} {Advances in Infrared and Raman Spectroscopies}}},\ \bibinfo
+	{editor} {edited by\ \bibinfo {editor} {\bibfnamefont {R.}~\bibnamefont
+			{Clark}}\ and\ \bibinfo {editor} {\bibfnamefont {R.}~\bibnamefont {Hester}}}\
+	(\bibinfo  {publisher} {Wiley},\ \bibinfo {address} {New York},\ \bibinfo
+	{year} {1985})\ pp.\ \bibinfo {pages} {179--213}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Terhune}\ \emph {et~al.}(1965)\citenamefont
+		{Terhune}, \citenamefont {Maker},\ and\ \citenamefont
+		{Savage}}]{Terhune1965}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~W.}\ \bibnamefont
+			{Terhune}}, \bibinfo {author} {\bibfnamefont {P.~D.}\ \bibnamefont {Maker}},\
+		and\ \bibinfo {author} {\bibfnamefont {C.~M.}\ \bibnamefont {Savage}},\
+	}\href {https://doi.org/10.1103/PhysRevLett.14.681} {\bibfield  {journal}
+		{\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {14}},\
+		\bibinfo {pages} {681} (\bibinfo {year} {1965})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Cyvin}\ \emph {et~al.}(1965)\citenamefont {Cyvin},
+		\citenamefont {Rauch},\ and\ \citenamefont {Decius}}]{Cyvin1965}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~J.}\ \bibnamefont
+			{Cyvin}}, \bibinfo {author} {\bibfnamefont {J.~E.}\ \bibnamefont {Rauch}},\
+		and\ \bibinfo {author} {\bibfnamefont {J.~C.}\ \bibnamefont {Decius}},\
+	}\href {https://doi.org/10.1063/1.1696646} {\bibfield  {journal} {\bibinfo
+			{journal} {Journal of Chemical Physics}\ }\textbf {\bibinfo {volume} {43}},\
+		\bibinfo {pages} {4083} (\bibinfo {year} {1965})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Andrews}\ and\ \citenamefont
+		{Thirunamachandran}(1978)}]{Andrews1978}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~L.}\ \bibnamefont
+			{Andrews}}\ and\ \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+			{Thirunamachandran}},\ }\href {https://doi.org/10.1063/1.436047} {\bibfield
+		{journal} {\bibinfo  {journal} {Journal of Chemical Physics}\ }\textbf
+		{\bibinfo {volume} {68}},\ \bibinfo {pages} {2941} (\bibinfo {year}
+		{1978})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Ziegler}(1990)}]{RN515}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.~D.}\ \bibnamefont
+			{Ziegler}},\ }\href {https://doi.org/10.1002/jrs.1250211203} {\bibfield
+		{journal} {\bibinfo  {journal} {Journal of Raman Spectroscopy}\ }\textbf
+		{\bibinfo {volume} {21}},\ \bibinfo {pages} {769} (\bibinfo {year}
+		{1990})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Denisov}\ \emph {et~al.}(1986)\citenamefont
+		{Denisov}, \citenamefont {Mavrin}, \citenamefont {Podobedov},\ and\
+		\citenamefont {Sterin}}]{Denisov1986}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.}~\bibnamefont
+			{Denisov}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Mavrin}},
+		\bibinfo {author} {\bibfnamefont {V.}~\bibnamefont {Podobedov}},\ and\
+		\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Sterin}},\ }\href
+	{https://doi.org/10.1016/0030-4018(86)90125-2} {\bibfield  {journal}
+		{\bibinfo  {journal} {Optics Communications}\ }\textbf {\bibinfo {volume}
+			{60}},\ \bibinfo {pages} {95} (\bibinfo {year} {1986})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Kozich}\ and\ \citenamefont
+		{Werncke}(2007)}]{Kozich2007}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.}~\bibnamefont
+			{Kozich}}\ and\ \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
+			{Werncke}},\ }\href {https://doi.org/10.1002/jrs.1748} {\bibfield  {journal}
+		{\bibinfo  {journal} {Journal of Raman Spectroscopy}\ }\textbf {\bibinfo
+			{volume} {38}},\ \bibinfo {pages} {1180} (\bibinfo {year}
+		{2007})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Kelley}(2010)}]{Kelley2010}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~M.}\ \bibnamefont
+			{Kelley}},\ }\href {https://doi.org/10.1146/annurev.physchem.012809.103347}
+	{\bibfield  {journal} {\bibinfo  {journal} {Annual Review of Physical
+				Chemistry}\ }\textbf {\bibinfo {volume} {61}},\ \bibinfo {pages} {41}
+		(\bibinfo {year} {2010})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Zilian}\ \emph {et~al.}(1994)\citenamefont {Zilian},
+		\citenamefont {LaBuda}, \citenamefont {Hamilton}, \citenamefont {Chen},\ and\
+		\citenamefont {Wright}}]{Zilian1994}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+			{Zilian}}, \bibinfo {author} {\bibfnamefont {M.~J.}\ \bibnamefont {LaBuda}},
+		\bibinfo {author} {\bibfnamefont {J.~P.}\ \bibnamefont {Hamilton}}, \bibinfo
+		{author} {\bibfnamefont {P.~C.}\ \bibnamefont {Chen}},\ and\ \bibinfo
+		{author} {\bibfnamefont {J.~C.}\ \bibnamefont {Wright}},\ }\href
+	{https://doi.org/10.1016/0022-2313(94)90242-9} {\bibfield  {journal}
+		{\bibinfo  {journal} {Journal of Luminescence}\ }\textbf {\bibinfo {volume}
+			{60-61}},\ \bibinfo {pages} {655} (\bibinfo {year} {1994})}\BibitemShut
+	{NoStop}%
+	\bibitem [{\citenamefont {Hamilton}\ \emph {et~al.}(1997)\citenamefont
+		{Hamilton}, \citenamefont {LaBuda},\ and\ \citenamefont {Wright}}]{RN350}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~P.}\ \bibnamefont
+			{Hamilton}}, \bibinfo {author} {\bibfnamefont {M.~J.}\ \bibnamefont
+			{LaBuda}},\ and\ \bibinfo {author} {\bibfnamefont {J.~C.}\ \bibnamefont
+			{Wright}},\ }\href {https://doi.org/10.1016/s0009-2614(97)00875-0} {\bibfield
+		{journal} {\bibinfo  {journal} {Chemical Physics Letters}\ }\textbf
+		{\bibinfo {volume} {277}},\ \bibinfo {pages} {175} (\bibinfo {year}
+		{1997})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {LaBuda}\ and\ \citenamefont {Wright}(1997)}]{RN351}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~J.}\ \bibnamefont
+			{LaBuda}}\ and\ \bibinfo {author} {\bibfnamefont {J.~C.}\ \bibnamefont
+			{Wright}},\ }\href {https://doi.org/10.1103/PhysRevLett.79.2446} {\bibfield
+		{journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo
+			{volume} {79}},\ \bibinfo {pages} {2446} (\bibinfo {year}
+		{1997})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {LaBuda}\ and\ \citenamefont
+		{Wright}(1998{\natexlab{a}})}]{RN352}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~J.}\ \bibnamefont
+			{LaBuda}}\ and\ \bibinfo {author} {\bibfnamefont {J.~C.}\ \bibnamefont
+			{Wright}},\ }\href {https://doi.org/10.1063/1.475809} {\bibfield  {journal}
+		{\bibinfo  {journal} {Journal of Chemical Physics}\ }\textbf {\bibinfo
+			{volume} {108}},\ \bibinfo {pages} {4112} (\bibinfo {year}
+		{1998}{\natexlab{a}})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {LaBuda}\ and\ \citenamefont
+		{Wright}(1998{\natexlab{b}})}]{RN353}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~J.}\ \bibnamefont
+			{LaBuda}}\ and\ \bibinfo {author} {\bibfnamefont {J.~C.}\ \bibnamefont
+			{Wright}},\ }\href {https://doi.org/10.1016/s0009-2614(98)00478-3} {\bibfield
+		{journal} {\bibinfo  {journal} {Chemical Physics Letters}\ }\textbf
+		{\bibinfo {volume} {290}},\ \bibinfo {pages} {29} (\bibinfo {year}
+		{1998}{\natexlab{b}})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Chen}\ \emph {et~al.}(1998)\citenamefont {Chen},
+		\citenamefont {Hamilton}, \citenamefont {Zillan}, \citenamefont {LaBuda},\
+		and\ \citenamefont {Wright}}]{Chen1998}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~C.}\ \bibnamefont
+			{Chen}}, \bibinfo {author} {\bibfnamefont {J.~P.}\ \bibnamefont {Hamilton}},
+		\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Zillan}}, \bibinfo
+		{author} {\bibfnamefont {M.~J.}\ \bibnamefont {LaBuda}},\ and\ \bibinfo
+		{author} {\bibfnamefont {J.~C.}\ \bibnamefont {Wright}},\ }\href
+	{https://doi.org/10.1366/0003702981943563} {\bibfield  {journal} {\bibinfo
+			{journal} {Applied Spectroscopy}\ }\textbf {\bibinfo {volume} {52}},\
+		\bibinfo {pages} {380} (\bibinfo {year} {1998})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Murdoch}\ \emph {et~al.}(2000)\citenamefont
+		{Murdoch}, \citenamefont {Thompson}, \citenamefont {Meyer},\ and\
+		\citenamefont {Wright}}]{RN362}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.~M.}\ \bibnamefont
+			{Murdoch}}, \bibinfo {author} {\bibfnamefont {D.~E.}\ \bibnamefont
+			{Thompson}}, \bibinfo {author} {\bibfnamefont {K.~A.}\ \bibnamefont
+			{Meyer}},\ and\ \bibinfo {author} {\bibfnamefont {J.~C.}\ \bibnamefont
+			{Wright}},\ }\href {https://doi.org/10.1366/0003702001948411} {\bibfield
+		{journal} {\bibinfo  {journal} {Applied Spectroscopy}\ }\textbf {\bibinfo
+			{volume} {54}},\ \bibinfo {pages} {1495} (\bibinfo {year}
+		{2000})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Thompson}\ and\ \citenamefont
+		{Wright}(2000)}]{RN418}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~E.}\ \bibnamefont
+			{Thompson}}\ and\ \bibinfo {author} {\bibfnamefont {J.~C.}\ \bibnamefont
+			{Wright}},\ }\href {https://doi.org/10.1021/jp002343p} {\bibfield  {journal}
+		{\bibinfo  {journal} {Journal of Physical Chemistry A}\ }\textbf {\bibinfo
+			{volume} {104}},\ \bibinfo {pages} {11282} (\bibinfo {year}
+		{2000})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Hanninen}\ \emph {et~al.}(2018)\citenamefont
+		{Hanninen}, \citenamefont {Prince}, \citenamefont {Ramos}, \citenamefont
+		{Plikus},\ and\ \citenamefont {Potma}}]{Hanninen2018}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~M.}\ \bibnamefont
+			{Hanninen}}, \bibinfo {author} {\bibfnamefont {R.~C.}\ \bibnamefont
+			{Prince}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Ramos}},
+		\bibinfo {author} {\bibfnamefont {M.~V.}\ \bibnamefont {Plikus}},\ and\
+		\bibinfo {author} {\bibfnamefont {E.~O.}\ \bibnamefont {Potma}},\ }\href
+	{https://doi.org/10.1364/BOE.9.004807} {\bibfield  {journal} {\bibinfo
+			{journal} {Biomed. Opt. Express}\ }\textbf {\bibinfo {volume} {9}},\ \bibinfo
+		{pages} {4807} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Wang}\ \emph {et~al.}(2021)\citenamefont {Wang},
+		\citenamefont {Wang}, \citenamefont {Shen}, \citenamefont {Han},
+		\citenamefont {Li}, \citenamefont {He}, \citenamefont {Wang}, \citenamefont
+		{Sokolov},\ and\ \citenamefont {Scully}}]{Wang2021}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+			{Wang}}, \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Wang}}, \bibinfo
+		{author} {\bibfnamefont {Y.}~\bibnamefont {Shen}}, \bibinfo {author}
+		{\bibfnamefont {Z.}~\bibnamefont {Han}}, \bibinfo {author} {\bibfnamefont
+			{F.}~\bibnamefont {Li}}, \bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont
+			{He}}, \bibinfo {author} {\bibfnamefont {D.-w.}\ \bibnamefont {Wang}},
+		\bibinfo {author} {\bibfnamefont {A.~V.}\ \bibnamefont {Sokolov}},\ and\
+		\bibinfo {author} {\bibfnamefont {M.~O.}\ \bibnamefont {Scully}},\ }\href
+	{https://doi.org/10.1021/acsphotonics.0c01940} {\bibfield  {journal}
+		{\bibinfo  {journal} {ACS Photonics}\ }\textbf {\bibinfo {volume} {8}},\
+		\bibinfo {pages} {1137} (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Seliya}\ \emph {et~al.}(2024)\citenamefont {Seliya},
+		\citenamefont {Bonn},\ and\ \citenamefont {Grechko}}]{Bonn2024}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+			{Seliya}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Bonn}},\ and\
+		\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Grechko}},\ }\href
+	{https://doi.org/10.1063/5.0179041} {\bibfield  {journal} {\bibinfo
+			{journal} {Journal of Chemical Physics}\ }\textbf {\bibinfo {volume} {160}},\
+		\bibinfo {pages} {034201} (\bibinfo {year} {2024})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {McDonnell}\ \emph {et~al.}(2024)\citenamefont
+		{McDonnell}, \citenamefont {Oram}, \citenamefont {Boyer}, \citenamefont
+		{Kohler}, \citenamefont {Meyer}, \citenamefont {Sibert~III},\ and\
+		\citenamefont {Wright}}]{McDonnell2024}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~P.}\ \bibnamefont
+			{McDonnell}}, \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Oram}},
+		\bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont {Boyer}}, \bibinfo
+		{author} {\bibfnamefont {D.~D.}\ \bibnamefont {Kohler}}, \bibinfo {author}
+		{\bibfnamefont {K.~A.}\ \bibnamefont {Meyer}}, \bibinfo {author}
+		{\bibfnamefont {E.~L.}\ \bibnamefont {Sibert~III}},\ and\ \bibinfo {author}
+		{\bibfnamefont {J.~C.}\ \bibnamefont {Wright}},\ }\href
+	{https://doi.org/10.1021/acs.jpclett.4c00297} {\bibfield  {journal} {\bibinfo
+			{journal} {Journal of Physical Chemistry Letters}\ }\textbf {\bibinfo
+			{volume} {15}},\ \bibinfo {pages} {3975} (\bibinfo {year}
+		{2024})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Armstrong}\ \emph {et~al.}(1962)\citenamefont
+		{Armstrong}, \citenamefont {Bloembergen}, \citenamefont {Ducuing},\ and\
+		\citenamefont {Pershan}}]{RN480}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~A.}\ \bibnamefont
+			{Armstrong}}, \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
+			{Bloembergen}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+			{Ducuing}},\ and\ \bibinfo {author} {\bibfnamefont {P.~S.}\ \bibnamefont
+			{Pershan}},\ }\href {https://doi.org/10.1103/PhysRev.127.1918} {\bibfield
+		{journal} {\bibinfo  {journal} {Physical Review}\ }\textbf {\bibinfo {volume}
+			{127}},\ \bibinfo {pages} {1918} (\bibinfo {year} {1962})}\BibitemShut
+	{NoStop}%
+	\bibitem [{\citenamefont {Ivanecky~III}\ and\ \citenamefont
+		{Wright}(1993)}]{RN243}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~E.}\ \bibnamefont
+			{Ivanecky~III}}\ and\ \bibinfo {author} {\bibfnamefont {J.~C.}\ \bibnamefont
+			{Wright}},\ }\href {https://doi.org/10.1016/0009-2614(93)80164-k} {\bibfield
+		{journal} {\bibinfo  {journal} {Chemical Physics Letters}\ }\textbf {\bibinfo
+			{volume} {206}},\ \bibinfo {pages} {437} (\bibinfo {year}
+		{1993})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Cho}\ \emph {et~al.}(2000)\citenamefont {Cho},
+		\citenamefont {Blank}, \citenamefont {Sung}, \citenamefont {Park},
+		\citenamefont {Hahn},\ and\ \citenamefont {Fleming}}]{Cho2000_Cascade}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+			{Cho}}, \bibinfo {author} {\bibfnamefont {D.~A.}\ \bibnamefont {Blank}},
+		\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Sung}}, \bibinfo {author}
+		{\bibfnamefont {K.}~\bibnamefont {Park}}, \bibinfo {author} {\bibfnamefont
+			{S.}~\bibnamefont {Hahn}},\ and\ \bibinfo {author} {\bibfnamefont {G.~R.}\
+			\bibnamefont {Fleming}},\ }\href {https://doi.org/10.1063/1.480777}
+	{\bibfield  {journal} {\bibinfo  {journal} {Journal of Chemical Physics}\
+		}\textbf {\bibinfo {volume} {112}},\ \bibinfo {pages} {2082} (\bibinfo {year}
+		{2000})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Taran}(1977)}]{Taran1977}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.-P.}\ \bibnamefont
+			{Taran}},\ }in\ \href@noop {} {\emph {\bibinfo {booktitle} {Laser
+				Spectroscopy III}}},\ \bibinfo {editor} {edited by\ \bibinfo {editor}
+		{\bibfnamefont {J.~L.}\ \bibnamefont {Hall}}\ and\ \bibinfo {editor}
+		{\bibfnamefont {J.~L.}\ \bibnamefont {Carlsten}}}\ (\bibinfo  {publisher}
+	{Springer Berlin Heidelberg},\ \bibinfo {address} {Berlin, Heidelberg},\
+	\bibinfo {year} {1977})\ pp.\ \bibinfo {pages} {315--324}\BibitemShut
+	{NoStop}%
+	\bibitem [{\citenamefont {Berger}(1978)}]{Berger1978}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+			{Berger}},\ }\href {https://doi.org/10.1016/0030-4018(78)90301-2} {\bibfield
+		{journal} {\bibinfo  {journal} {Optics Communications}\ }\textbf {\bibinfo
+			{volume} {25}},\ \bibinfo {pages} {179} (\bibinfo {year} {1978})}\BibitemShut
+	{NoStop}%
+	\bibitem [{\citenamefont {Bjarnason}\ \emph {et~al.}(1980)\citenamefont
+		{Bjarnason}, \citenamefont {Andersen},\ and\ \citenamefont
+		{Hudson}}]{Bjarnason1980}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~{\"O}.}\
+			\bibnamefont {Bjarnason}}, \bibinfo {author} {\bibfnamefont {H.~C.}\
+			\bibnamefont {Andersen}},\ and\ \bibinfo {author} {\bibfnamefont {B.~S.}\
+			\bibnamefont {Hudson}},\ }\href {https://doi.org/10.1063/1.440318} {\bibfield
+		{journal} {\bibinfo  {journal} {Journal of Chemical Physics}\ }\textbf
+		{\bibinfo {volume} {73}},\ \bibinfo {pages} {1827} (\bibinfo {year}
+		{1980})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Cho}(1997)}]{Cho1997}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+			{Cho}},\ }\href {https://doi.org/10.1063/1.473758} {\bibfield  {journal}
+		{\bibinfo  {journal} {Journal of Chemical Physics}\ }\textbf {\bibinfo
+			{volume} {106}},\ \bibinfo {pages} {7550} (\bibinfo {year}
+		{1997})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Yang}\ \emph {et~al.}(1998)\citenamefont {Yang},
+		\citenamefont {Kim}, \citenamefont {Jung},\ and\ \citenamefont
+		{Cho}}]{Cho1998}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+			{Yang}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Kim}}, \bibinfo
+		{author} {\bibfnamefont {Y.}~\bibnamefont {Jung}},\ and\ \bibinfo {author}
+		{\bibfnamefont {M.}~\bibnamefont {Cho}},\ }\href
+	{https://doi.org/10.1063/1.475841} {\bibfield  {journal} {\bibinfo  {journal}
+			{Journal of Chemical Physics}\ }\textbf {\bibinfo {volume} {108}},\ \bibinfo
+		{pages} {4013} (\bibinfo {year} {1998})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Molesky}\ \emph {et~al.}(2014)\citenamefont
+		{Molesky}, \citenamefont {Giokas}, \citenamefont {Guo},\ and\ \citenamefont
+		{Moran}}]{RN445}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.~P.}\ \bibnamefont
+			{Molesky}}, \bibinfo {author} {\bibfnamefont {P.~G.}\ \bibnamefont {Giokas}},
+		\bibinfo {author} {\bibfnamefont {Z.~K.}\ \bibnamefont {Guo}},\ and\ \bibinfo
+		{author} {\bibfnamefont {A.~M.}\ \bibnamefont {Moran}},\ }\href
+	{https://doi.org/10.1063/1.4894846} {\bibfield  {journal} {\bibinfo
+			{journal} {Journal of Chemical Physics}\ }\textbf {\bibinfo {volume} {141}},\
+		\bibinfo {pages} {114202} (\bibinfo {year} {2014})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Wright}(2017)}]{RN335}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~C.}\ \bibnamefont
+			{Wright}},\ }\href {https://doi.org/10.1146/annurev-anchem-061516-045349}
+	{\bibfield  {journal} {\bibinfo  {journal} {Annual Review of Analytical
+				Chemistry, Vol 10}\ }\textbf {\bibinfo {volume} {10}},\ \bibinfo {pages} {45}
+		(\bibinfo {year} {2017})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Cho}(2001)}]{Cho2001}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+			{Cho}},\ }\href {https://doi.org/10.1063/1.1363669} {\bibfield  {journal}
+		{\bibinfo  {journal} {Journal of Chemical Physics}\ }\textbf {\bibinfo
+			{volume} {114}},\ \bibinfo {pages} {8040} (\bibinfo {year}
+		{2001})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Oliver}\ \emph {et~al.}(2014)\citenamefont {Oliver},
+		\citenamefont {Lewis},\ and\ \citenamefont {Fleming}}]{Oliver2014}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.~A.~A.}\
+			\bibnamefont {Oliver}}, \bibinfo {author} {\bibfnamefont {N.~H.~C.}\
+			\bibnamefont {Lewis}},\ and\ \bibinfo {author} {\bibfnamefont {G.~R.}\
+			\bibnamefont {Fleming}},\ }\href {https://doi.org/10.1073/pnas.1409207111}
+	{\bibfield  {journal} {\bibinfo  {journal} {Proceedings of the National
+				Academy of Sciences}\ }\textbf {\bibinfo {volume} {111}},\ \bibinfo {pages}
+		{10061} (\bibinfo {year} {2014})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Courtney}\ \emph
+		{et~al.}(2015{\natexlab{a}})\citenamefont {Courtney}, \citenamefont {Fox},
+		\citenamefont {Estergreen},\ and\ \citenamefont {Khalil}}]{Courtney2015}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.~L.}\ \bibnamefont
+			{Courtney}}, \bibinfo {author} {\bibfnamefont {Z.~W.}\ \bibnamefont {Fox}},
+		\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Estergreen}},\ and\
+		\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Khalil}},\ }\href
+	{https://doi.org/10.1021/acs.jpclett.5b00356} {\bibfield  {journal} {\bibinfo
+			{journal} {Journal of Physical Chemistry Letters}\ }\textbf {\bibinfo
+			{volume} {6}},\ \bibinfo {pages} {1286} (\bibinfo {year}
+		{2015}{\natexlab{a}})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Courtney}\ \emph
+		{et~al.}(2015{\natexlab{b}})\citenamefont {Courtney}, \citenamefont {Fox},
+		\citenamefont {Slenkamp},\ and\ \citenamefont {Khalil}}]{Courtney2015_1}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.~L.}\ \bibnamefont
+			{Courtney}}, \bibinfo {author} {\bibfnamefont {Z.~W.}\ \bibnamefont {Fox}},
+		\bibinfo {author} {\bibfnamefont {K.~M.}\ \bibnamefont {Slenkamp}},\ and\
+		\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Khalil}},\ }\href
+	{https://doi.org/10.1063/1.4932983} {\bibfield  {journal} {\bibinfo
+			{journal} {Journal of Chemical Physics}\ }\textbf {\bibinfo {volume} {143}},\
+		\bibinfo {pages} {154201} (\bibinfo {year} {2015}{\natexlab{b}})}\BibitemShut
+	{NoStop}%
+	\bibitem [{\citenamefont {Deng}\ \emph {et~al.}(2021)\citenamefont {Deng},
+		\citenamefont {Qian}, \citenamefont {Zhang}, \citenamefont {Han},
+		\citenamefont {Chen},\ and\ \citenamefont {Rao}}]{Deng2021}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.-H.}\ \bibnamefont
+			{Deng}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Qian}}, \bibinfo
+		{author} {\bibfnamefont {T.}~\bibnamefont {Zhang}}, \bibinfo {author}
+		{\bibfnamefont {J.}~\bibnamefont {Han}}, \bibinfo {author} {\bibfnamefont
+			{H.}~\bibnamefont {Chen}},\ and\ \bibinfo {author} {\bibfnamefont
+			{Y.}~\bibnamefont {Rao}},\ }\href {https://doi.org/10.1073/pnas.2100608118}
+	{\bibfield  {journal} {\bibinfo  {journal} {Proceedings of the National
+				Academy of Sciences}\ }\textbf {\bibinfo {volume} {118}},\ \bibinfo {pages}
+		{e2100608118} (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {van Wilderen}\ and\ \citenamefont
+		{Bredenbeck}(2015)}]{Bredenbeck2015}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.~J. G.~W.}\
+			\bibnamefont {van Wilderen}}\ and\ \bibinfo {author} {\bibfnamefont
+			{J.}~\bibnamefont {Bredenbeck}},\ }\href
+	{https://doi.org/10.1002/anie.201503155} {\bibfield  {journal} {\bibinfo
+			{journal} {Angewandte Chemie International Edition}\ }\textbf {\bibinfo
+			{volume} {54}},\ \bibinfo {pages} {11624} (\bibinfo {year}
+		{2015})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Gaynor}\ \emph {et~al.}(2018)\citenamefont {Gaynor},
+		\citenamefont {Petrone}, \citenamefont {Li},\ and\ \citenamefont
+		{Khalil}}]{Gaynor2018}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~D.}\ \bibnamefont
+			{Gaynor}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Petrone}},
+		\bibinfo {author} {\bibfnamefont {X.}~\bibnamefont {Li}},\ and\ \bibinfo
+		{author} {\bibfnamefont {M.}~\bibnamefont {Khalil}},\ }\href
+	{https://doi.org/10.1021/acs.jpclett.8b02752} {\bibfield  {journal} {\bibinfo
+			{journal} {Journal of Physical Chemistry Letters}\ }\textbf {\bibinfo
+			{volume} {9}},\ \bibinfo {pages} {6289} (\bibinfo {year} {2018})}\BibitemShut
+	{NoStop}%
+	\bibitem [{\citenamefont {Arsenault}\ \emph {et~al.}(2021)\citenamefont
+		{Arsenault}, \citenamefont {Schile}, \citenamefont {Limmer},\ and\
+		\citenamefont {Fleming}}]{Arsenault2021}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.~A.}\ \bibnamefont
+			{Arsenault}}, \bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont
+			{Schile}}, \bibinfo {author} {\bibfnamefont {D.~T.}\ \bibnamefont {Limmer}},\
+		and\ \bibinfo {author} {\bibfnamefont {G.~R.}\ \bibnamefont {Fleming}},\
+	}\href {https://doi.org/10.1063/5.0056478} {\bibfield  {journal} {\bibinfo
+			{journal} {Journal of Chemical Physics}\ }\textbf {\bibinfo {volume} {155}},\
+		\bibinfo {pages} {096101} (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Olson}\ \emph {et~al.}(2018)\citenamefont {Olson},
+		\citenamefont {Tripp}, \citenamefont {Linder}, \citenamefont {Hu},
+		\citenamefont {Detty}, \citenamefont {Jensen},\ and\ \citenamefont
+		{Camden}}]{Olson2018}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~E.}\ \bibnamefont
+			{Olson}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Tripp}},
+		\bibinfo {author} {\bibfnamefont {M.~K.}\ \bibnamefont {Linder}}, \bibinfo
+		{author} {\bibfnamefont {Z.}~\bibnamefont {Hu}}, \bibinfo {author}
+		{\bibfnamefont {M.~R.}\ \bibnamefont {Detty}}, \bibinfo {author}
+		{\bibfnamefont {L.}~\bibnamefont {Jensen}},\ and\ \bibinfo {author}
+		{\bibfnamefont {J.~P.}\ \bibnamefont {Camden}},\ }\href
+	{https://doi.org/10.1021/acs.jpcc.8b07507} {\bibfield  {journal} {\bibinfo
+			{journal} {Journal of Physical Chemistry C}\ }\textbf {\bibinfo {volume}
+			{122}},\ \bibinfo {pages} {25051} (\bibinfo {year} {2018})}\BibitemShut
+	{NoStop}%
+	\bibitem [{\citenamefont {Morrow}\ \emph {et~al.}(2017)\citenamefont {Morrow},
+		\citenamefont {Kohler},\ and\ \citenamefont {Wright}}]{RN279}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~J.}\ \bibnamefont
+			{Morrow}}, \bibinfo {author} {\bibfnamefont {D.~D.}\ \bibnamefont {Kohler}},\
+		and\ \bibinfo {author} {\bibfnamefont {J.~C.}\ \bibnamefont {Wright}},\
+	}\href {https://doi.org/10.1103/PhysRevA.96.063835} {\bibfield  {journal}
+		{\bibinfo  {journal} {Physical Review A}\ }\textbf {\bibinfo {volume} {96}},\
+		\bibinfo {pages} {063835} (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Handali}\ \emph {et~al.}(2018)\citenamefont
+		{Handali}, \citenamefont {Sunden}, \citenamefont {Kaufman},\ and\
+		\citenamefont {Wright}}]{RN278}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~D.}\ \bibnamefont
+			{Handali}}, \bibinfo {author} {\bibfnamefont {K.~F.}\ \bibnamefont {Sunden}},
+		\bibinfo {author} {\bibfnamefont {E.~M.}\ \bibnamefont {Kaufman}},\ and\
+		\bibinfo {author} {\bibfnamefont {J.~C.}\ \bibnamefont {Wright}},\ }\href
+	{https://doi.org/10.1016/j.chemphys.2018.05.023} {\bibfield  {journal}
+		{\bibinfo  {journal} {Chemical Physics}\ }\textbf {\bibinfo {volume} {512}},\
+		\bibinfo {pages} {13} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Chung}\ and\ \citenamefont
+		{Ziegler}(1988)}]{Ziegler1988}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.~C.}\ \bibnamefont
+			{Chung}}\ and\ \bibinfo {author} {\bibfnamefont {L.~D.}\ \bibnamefont
+			{Ziegler}},\ }\href {https://doi.org/10.1063/1.454339} {\bibfield  {journal}
+		{\bibinfo  {journal} {Journal of Chemical Physics}\ }\textbf {\bibinfo
+			{volume} {88}},\ \bibinfo {pages} {7287} (\bibinfo {year}
+		{1988})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Bloembergen}\ and\ \citenamefont
+		{Shen}(1964)}]{RN455}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
+			{Bloembergen}}\ and\ \bibinfo {author} {\bibfnamefont {Y.~R.}\ \bibnamefont
+			{Shen}},\ }\href {https://doi.org/10.1103/PhysRev.133.A37} {\bibfield
+		{journal} {\bibinfo  {journal} {Physical Review}\ }\textbf {\bibinfo {volume}
+			{133}},\ \bibinfo {pages} {A37} (\bibinfo {year} {1964})}\BibitemShut
+	{NoStop}%
+	\bibitem [{\citenamefont {Sung}\ and\ \citenamefont {Silbey}(2001)}]{Sung2001}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+			{Sung}}\ and\ \bibinfo {author} {\bibfnamefont {R.~J.}\ \bibnamefont
+			{Silbey}},\ }\href {https://doi.org/10.1063/1.1413979} {\bibfield  {journal}
+		{\bibinfo  {journal} {Journal of Chemical Physics}\ }\textbf {\bibinfo
+			{volume} {115}},\ \bibinfo {pages} {9266} (\bibinfo {year}
+		{2001})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Sue}\ \emph {et~al.}(1986)\citenamefont {Sue},
+		\citenamefont {Yan},\ and\ \citenamefont {Mukamel}}]{Sue1986}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+			{Sue}}, \bibinfo {author} {\bibfnamefont {Y.~J.}\ \bibnamefont {Yan}},\ and\
+		\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Mukamel}},\ }\href
+	{https://doi.org/10.1063/1.451625} {\bibfield  {journal} {\bibinfo  {journal}
+			{Journal of Chemical Physics}\ }\textbf {\bibinfo {volume} {85}},\ \bibinfo
+		{pages} {462} (\bibinfo {year} {1986})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Yan}\ \emph {et~al.}(1988)\citenamefont {Yan},
+		\citenamefont {Sparpaglione},\ and\ \citenamefont {Mukamel}}]{Yan1988}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.~J.}\ \bibnamefont
+			{Yan}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Sparpaglione}},\
+		and\ \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Mukamel}},\ }\href
+	{https://doi.org/10.1021/j100328a010} {\bibfield  {journal} {\bibinfo
+			{journal} {Journal of Physical Chemistry}\ }\textbf {\bibinfo {volume}
+			{92}},\ \bibinfo {pages} {4842} (\bibinfo {year} {1988})}\BibitemShut
+	{NoStop}%
+	\bibitem [{\citenamefont {Li}\ \emph {et~al.}(1994)\citenamefont {Li},
+		\citenamefont {Johnson}, \citenamefont {Mukamel},\ and\ \citenamefont
+		{Myers}}]{Li1994}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
+			{Li}}, \bibinfo {author} {\bibfnamefont {A.~E.}\ \bibnamefont {Johnson}},
+		\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Mukamel}},\ and\ \bibinfo
+		{author} {\bibfnamefont {A.~B.}\ \bibnamefont {Myers}},\ }\href
+	{https://doi.org/10.1021/ja00103a020} {\bibfield  {journal} {\bibinfo
+			{journal} {Journal of the American Chemical Society}\ }\textbf {\bibinfo
+			{volume} {116}},\ \bibinfo {pages} {11039} (\bibinfo {year}
+		{1994})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Myers}(1997)}]{Myers1997}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~B.}\ \bibnamefont
+			{Myers}},\ }\href
+	{https://doi.org/10.1002/(SICI)1097-4555(199706)28:6%3C389::AID-JRS128%3E3.0.CO;2-M}
+	{\bibfield  {journal} {\bibinfo  {journal} {Journal of Raman Spectroscopy}\
+		}\textbf {\bibinfo {volume} {28}},\ \bibinfo {pages} {389} (\bibinfo {year}
+		{1997})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Raschke}\ \emph {et~al.}(2002)\citenamefont
+		{Raschke}, \citenamefont {Hayashi}, \citenamefont {Lin},\ and\ \citenamefont
+		{Shen}}]{Raschke2002}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~B.}\ \bibnamefont
+			{Raschke}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Hayashi}},
+		\bibinfo {author} {\bibfnamefont {S.~H.}\ \bibnamefont {Lin}},\ and\ \bibinfo
+		{author} {\bibfnamefont {Y.~R.}\ \bibnamefont {Shen}},\ }\href
+	{https://doi.org/10.1016/S0009-2614(02)00560-2} {\bibfield  {journal}
+		{\bibinfo  {journal} {Chemical Physics Letters}\ }\textbf {\bibinfo {volume}
+			{359}},\ \bibinfo {pages} {367} (\bibinfo {year} {2002})}\BibitemShut
+	{NoStop}%
+	\bibitem [{\citenamefont {Dong}\ \emph {et~al.}(2015)\citenamefont {Dong},
+		\citenamefont {Lewis}, \citenamefont {Oliver},\ and\ \citenamefont
+		{Fleming}}]{Dong2015}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+			{Dong}}, \bibinfo {author} {\bibfnamefont {N.~H.~C.}\ \bibnamefont {Lewis}},
+		\bibinfo {author} {\bibfnamefont {T.~A.~A.}\ \bibnamefont {Oliver}},\ and\
+		\bibinfo {author} {\bibfnamefont {G.~R.}\ \bibnamefont {Fleming}},\ }\href
+	{https://doi.org/10.1063/1.4919684} {\bibfield  {journal} {\bibinfo
+			{journal} {Journal of Chemical Physics}\ }\textbf {\bibinfo {volume} {142}},\
+		\bibinfo {pages} {174201} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Lewis}\ \emph {et~al.}(2015)\citenamefont {Lewis},
+		\citenamefont {Dong}, \citenamefont {Oliver},\ and\ \citenamefont
+		{Fleming}}]{Lewis2015}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~H.~C.}\
+			\bibnamefont {Lewis}}, \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+			{Dong}}, \bibinfo {author} {\bibfnamefont {T.~A.~A.}\ \bibnamefont
+			{Oliver}},\ and\ \bibinfo {author} {\bibfnamefont {G.~R.}\ \bibnamefont
+			{Fleming}},\ }\href {https://doi.org/10.1063/1.4919686} {\bibfield  {journal}
+		{\bibinfo  {journal} {Journal of Chemical Physics}\ }\textbf {\bibinfo
+			{volume} {142}},\ \bibinfo {pages} {174202} (\bibinfo {year}
+		{2015})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Yablonovitch}\ \emph {et~al.}(1972)\citenamefont
+		{Yablonovitch}, \citenamefont {Flytzanis},\ and\ \citenamefont
+		{Bloembergen}}]{RN297}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+			{Yablonovitch}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+			{Flytzanis}},\ and\ \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
+			{Bloembergen}},\ }\href {https://doi.org/10.1103/PhysRevLett.29.865}
+	{\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf
+		{\bibinfo {volume} {29}},\ \bibinfo {pages} {865} (\bibinfo {year}
+		{1972})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Bonn}\ \emph {et~al.}(2001)\citenamefont {Bonn},
+		\citenamefont {Hess}, \citenamefont {Miners}, \citenamefont {Heinz},
+		\citenamefont {Bakker},\ and\ \citenamefont {Cho}}]{RN301}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+			{Bonn}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Hess}}, \bibinfo
+		{author} {\bibfnamefont {J.~H.}\ \bibnamefont {Miners}}, \bibinfo {author}
+		{\bibfnamefont {T.~F.}\ \bibnamefont {Heinz}}, \bibinfo {author}
+		{\bibfnamefont {H.~J.}\ \bibnamefont {Bakker}},\ and\ \bibinfo {author}
+		{\bibfnamefont {M.}~\bibnamefont {Cho}},\ }\href
+	{https://doi.org/10.1103/PhysRevLett.86.1566} {\bibfield  {journal} {\bibinfo
+			{journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {86}},\ \bibinfo
+		{pages} {1566} (\bibinfo {year} {2001})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Belkin}\ \emph {et~al.}(2000)\citenamefont {Belkin},
+		\citenamefont {Kulakov}, \citenamefont {Ernst}, \citenamefont {Yan},\ and\
+		\citenamefont {Shen}}]{Belkin2000}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont
+			{Belkin}}, \bibinfo {author} {\bibfnamefont {T.~A.}\ \bibnamefont {Kulakov}},
+		\bibinfo {author} {\bibfnamefont {K.-H.}\ \bibnamefont {Ernst}}, \bibinfo
+		{author} {\bibfnamefont {L.}~\bibnamefont {Yan}},\ and\ \bibinfo {author}
+		{\bibfnamefont {Y.~R.}\ \bibnamefont {Shen}},\ }\href
+	{https://doi.org/10.1103/PhysRevLett.85.4474} {\bibfield  {journal} {\bibinfo
+			{journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {85}},\ \bibinfo
+		{pages} {4474} (\bibinfo {year} {2000})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Moad}\ and\ \citenamefont
+		{Simpson}(2005)}]{Moad2005}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont
+			{Moad}}\ and\ \bibinfo {author} {\bibfnamefont {G.~J.}\ \bibnamefont
+			{Simpson}},\ }\href {https://doi.org/10.1021/jp045866w} {\bibfield  {journal}
+		{\bibinfo  {journal} {Journal of Physical Chemistry A}\ }\textbf {\bibinfo
+			{volume} {109}},\ \bibinfo {pages} {1316} (\bibinfo {year}
+		{2005})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Bedeaux}\ and\ \citenamefont
+		{Bloembergen}(1973)}]{Bedeaux1973}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+			{Bedeaux}}\ and\ \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
+			{Bloembergen}},\ }\href {https://doi.org/10.1016/0031-8914(73)90200-0}
+	{\bibfield  {journal} {\bibinfo  {journal} {Physica}\ }\textbf {\bibinfo
+			{volume} {69}},\ \bibinfo {pages} {57} (\bibinfo {year} {1973})}\BibitemShut
+	{NoStop}%
+	\bibitem [{\citenamefont {Andrews}\ and\ \citenamefont
+		{Thirunamachandran}(1977)}]{Andrews1977}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~L.}\ \bibnamefont
+			{Andrews}}\ and\ \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+			{Thirunamachandran}},\ }\href {https://doi.org/10.1063/1.434725} {\bibfield
+		{journal} {\bibinfo  {journal} {Journal of Chemical Physics}\ }\textbf
+		{\bibinfo {volume} {67}},\ \bibinfo {pages} {5026} (\bibinfo {year}
+		{1977})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Prior}(1984)}]{Prior1984}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
+			{Prior}},\ }\href {https://doi.org/10.1109/JQE.1984.1072262} {\bibfield
+		{journal} {\bibinfo  {journal} {IEEE Journal of Quantum Electronics}\
+		}\textbf {\bibinfo {volume} {20}},\ \bibinfo {pages} {37} (\bibinfo {year}
+		{1984})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Maker}\ and\ \citenamefont {Terhune}(1965)}]{RN134}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~D.}\ \bibnamefont
+			{Maker}}\ and\ \bibinfo {author} {\bibfnamefont {R.~W.}\ \bibnamefont
+			{Terhune}},\ }\href {https://doi.org/10.1103/PhysRev.137.A801} {\bibfield
+		{journal} {\bibinfo  {journal} {Phys. Rev.}\ }\textbf {\bibinfo {volume}
+			{137}},\ \bibinfo {pages} {A801} (\bibinfo {year} {1965})}\BibitemShut
+	{NoStop}%
+	\bibitem [{\citenamefont {Placzek}(1934)}]{Placzek1934}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+			{Placzek}},\ }\bibinfo {title} {Rayleigh-{S}treuung und {R}aman-{E}ffekt},\
+	in\ \href@noop {} {\emph {\bibinfo {booktitle} {Handbuch der Radiologie}}},\
+	Vol.~\bibinfo {volume} {6},\ \bibinfo {editor} {edited by\ \bibinfo {editor}
+		{\bibfnamefont {E.}~\bibnamefont {Marx}}}\ (\bibinfo  {publisher}
+	{Akademische Verlagsgesellschaft},\ \bibinfo {address} {Leipzig},\ \bibinfo
+	{year} {1934})\ p.\ \bibinfo {pages} {204},\ \bibinfo {note} {part
+		2}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Long}\ and\ \citenamefont
+		{Stanton}(1970)}]{Long1970}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~A.}\ \bibnamefont
+			{Long}}\ and\ \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Stanton}},\
+	}\href {https://doi.org/10.1098/rspa.1970.0153} {\bibfield  {journal}
+		{\bibinfo  {journal} {Proceedings of the Royal Society of London. A.
+				Mathematical and Physical Sciences}\ }\textbf {\bibinfo {volume} {318}},\
+		\bibinfo {pages} {441} (\bibinfo {year} {1970})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Wilson}\ \emph {et~al.}(1980)\citenamefont {Wilson},
+		\citenamefont {Decius},\ and\ \citenamefont {Cross}}]{RN459}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.~B.}\ \bibnamefont
+			{Wilson}}, \bibinfo {author} {\bibfnamefont {J.~C.}\ \bibnamefont {Decius}},\
+		and\ \bibinfo {author} {\bibfnamefont {P.~C.}\ \bibnamefont {Cross}},\
+	}\href@noop {} {\emph {\bibinfo {title} {Molecular Vibrations: The Theory of
+				Infrared and Raman Vibrational Spectra}}}\ (\bibinfo  {publisher} {Dover
+		Publications},\ \bibinfo {year} {1980})\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Albrecht}(1961)}]{Albrecht1961}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~C.}\ \bibnamefont
+			{Albrecht}},\ }\href {https://doi.org/10.1063/1.1701032} {\bibfield
+		{journal} {\bibinfo  {journal} {Journal of Chemical Physics}\ }\textbf
+		{\bibinfo {volume} {34}},\ \bibinfo {pages} {1476} (\bibinfo {year}
+		{1961})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Born}\ and\ \citenamefont
+		{Oppenheimer}(1927)}]{BornOppenheimer}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+			{Born}}\ and\ \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+			{Oppenheimer}},\ }\href {https://doi.org/10.1002/andp.19273892002} {\bibfield
+		{journal} {\bibinfo  {journal} {Annalen der Physik}\ }\textbf {\bibinfo
+			{volume} {389}},\ \bibinfo {pages} {457} (\bibinfo {year}
+		{1927})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Tang}\ and\ \citenamefont
+		{Albrecht}(1970)}]{Tang1970}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+			{Tang}}\ and\ \bibinfo {author} {\bibfnamefont {A.~C.}\ \bibnamefont
+			{Albrecht}},\ }\bibinfo {title} {Developments in the {T}heories of
+		{V}ibrational {R}aman {I}ntensities},\ in\ \href
+	{https://doi.org/10.1007/978-1-4684-3027-1_2} {\emph {\bibinfo {booktitle}
+			{Raman Spectroscopy: Theory and Practice}}},\ \bibinfo {editor} {edited by\
+		\bibinfo {editor} {\bibfnamefont {H.~A.}\ \bibnamefont {Szymanski}}}\
+	(\bibinfo  {publisher} {Springer US},\ \bibinfo {address} {Boston, MA},\
+	\bibinfo {year} {1970})\ pp.\ \bibinfo {pages} {33--68}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Lee}\ and\ \citenamefont {Heller}(1979)}]{Lee1979}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+			{Lee}}\ and\ \bibinfo {author} {\bibfnamefont {E.~J.}\ \bibnamefont
+			{Heller}},\ }\href {https://doi.org/10.1063/1.438316} {\bibfield  {journal}
+		{\bibinfo  {journal} {Journal of Chemical Physics}\ }\textbf {\bibinfo
+			{volume} {71}},\ \bibinfo {pages} {4777} (\bibinfo {year}
+		{1979})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Shoute}\ \emph {et~al.}(2005)\citenamefont {Shoute},
+		\citenamefont {Bartholomew}, \citenamefont {Bazan},\ and\ \citenamefont
+		{Kelley}}]{Shoute2005}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.~C.~T.}\
+			\bibnamefont {Shoute}}, \bibinfo {author} {\bibfnamefont {G.~P.}\
+			\bibnamefont {Bartholomew}}, \bibinfo {author} {\bibfnamefont {G.~C.}\
+			\bibnamefont {Bazan}},\ and\ \bibinfo {author} {\bibfnamefont {A.~M.}\
+			\bibnamefont {Kelley}},\ }\href {https://doi.org/10.1063/1.1891708}
+	{\bibfield  {journal} {\bibinfo  {journal} {Journal of Chemical Physics}\
+		}\textbf {\bibinfo {volume} {122}},\ \bibinfo {pages} {184508} (\bibinfo
+		{year} {2005})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Silverstein}\ and\ \citenamefont
+		{Jensen}(2012)}]{Silverstein2012}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~W.}\ \bibnamefont
+			{Silverstein}}\ and\ \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+			{Jensen}},\ }\href {https://doi.org/10.1063/1.3684236} {\bibfield  {journal}
+		{\bibinfo  {journal} {Journal of Chemical Physics}\ }\textbf {\bibinfo
+			{volume} {136}},\ \bibinfo {pages} {064111} (\bibinfo {year}
+		{2012})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Ziegler}\ and\ \citenamefont
+		{Albrecht}(1974)}]{Ziegler1974}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+			{Ziegler}}\ and\ \bibinfo {author} {\bibfnamefont {A.~C.}\ \bibnamefont
+			{Albrecht}},\ }\href {https://doi.org/10.1063/1.1681573} {\bibfield
+		{journal} {\bibinfo  {journal} {Journal of Chemical Physics}\ }\textbf
+		{\bibinfo {volume} {60}},\ \bibinfo {pages} {3558} (\bibinfo {year}
+		{1974})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Warshel}\ and\ \citenamefont
+		{Dauber}(1977)}]{Warshel1977}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+			{Warshel}}\ and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+			{Dauber}},\ }\href {https://doi.org/10.1063/1.433867} {\bibfield  {journal}
+		{\bibinfo  {journal} {Journal of Chemical Physics}\ }\textbf {\bibinfo
+			{volume} {66}},\ \bibinfo {pages} {5477} (\bibinfo {year}
+		{1977})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Condon}(1928)}]{Condon1928}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.~U.}\ \bibnamefont
+			{Condon}},\ }\href {https://doi.org/10.1103/PhysRev.32.858} {\bibfield
+		{journal} {\bibinfo  {journal} {Phys. Rev.}\ }\textbf {\bibinfo {volume}
+			{32}},\ \bibinfo {pages} {858} (\bibinfo {year} {1928})}\BibitemShut
+	{NoStop}%
+	\bibitem [{\citenamefont {Herzberg}\ and\ \citenamefont
+		{Teller}(1933)}]{HerzbergTeller1933}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+			{Herzberg}}\ and\ \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+			{Teller}},\ }\href {https://doi.org/10.1515/zpch-1933-2136} {\bibfield
+		{journal} {\bibinfo  {journal} {Zeitschrift für Physikalische Chemie}\
+		}\textbf {\bibinfo {volume} {21B}},\ \bibinfo {pages} {410} (\bibinfo {year}
+		{1933})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Neddersen}\ \emph {et~al.}(1989)\citenamefont
+		{Neddersen}, \citenamefont {Mounter}, \citenamefont {Bostick},\ and\
+		\citenamefont {Johnson}}]{Neddersen1989}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~P.}\ \bibnamefont
+			{Neddersen}}, \bibinfo {author} {\bibfnamefont {S.~A.}\ \bibnamefont
+			{Mounter}}, \bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont
+			{Bostick}},\ and\ \bibinfo {author} {\bibfnamefont {C.~K.}\ \bibnamefont
+			{Johnson}},\ }\href {https://doi.org/10.1063/1.456592} {\bibfield  {journal}
+		{\bibinfo  {journal} {Journal of Chemical Physics}\ }\textbf {\bibinfo
+			{volume} {90}},\ \bibinfo {pages} {4719} (\bibinfo {year}
+		{1989})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Bonang}\ and\ \citenamefont
+		{Cameron}(1992)}]{Bonang1992}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~C.}\ \bibnamefont
+			{Bonang}}\ and\ \bibinfo {author} {\bibfnamefont {S.~M.}\ \bibnamefont
+			{Cameron}},\ }\href {https://doi.org/10.1063/1.463797} {\bibfield  {journal}
+		{\bibinfo  {journal} {Journal of Chemical Physics}\ }\textbf {\bibinfo
+			{volume} {97}},\ \bibinfo {pages} {5377} (\bibinfo {year}
+		{1992})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Petrov}(1985)}]{Petrov1985}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.~I.}\ \bibnamefont
+			{Petrov}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Optics
+				and Spectroscopy}\ }\textbf {\bibinfo {volume} {59}},\ \bibinfo {pages} {284}
+		(\bibinfo {year} {1985})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Baranov}\ \emph {et~al.}(1990)\citenamefont
+		{Baranov}, \citenamefont {Bobovich},\ and\ \citenamefont
+		{Petrov}}]{Baranov1990}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~V.}\ \bibnamefont
+			{Baranov}}, \bibinfo {author} {\bibfnamefont {Y.~S.}\ \bibnamefont
+			{Bobovich}},\ and\ \bibinfo {author} {\bibfnamefont {V.~I.}\ \bibnamefont
+			{Petrov}},\ }\href {https://doi.org/10.1070/PU1990v033n10ABEH002635}
+	{\bibfield  {journal} {\bibinfo  {journal} {Soviet Physics Uspekhi}\ }\textbf
+		{\bibinfo {volume} {33}},\ \bibinfo {pages} {812} (\bibinfo {year}
+		{1990})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Duschinsky}(1937)}]{Duschinsky1937}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+			{Duschinsky}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+			{Acta Physicochim. U.R.S.S.}\ }\textbf {\bibinfo {volume} {7}},\ \bibinfo
+		{pages} {551} (\bibinfo {year} {1937})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Milojevich}\ \emph {et~al.}(2013)\citenamefont
+		{Milojevich}, \citenamefont {Silverstein}, \citenamefont {Jensen},\ and\
+		\citenamefont {Camden}}]{Milojevich2013}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~B.}\ \bibnamefont
+			{Milojevich}}, \bibinfo {author} {\bibfnamefont {D.~W.}\ \bibnamefont
+			{Silverstein}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+			{Jensen}},\ and\ \bibinfo {author} {\bibfnamefont {J.~P.}\ \bibnamefont
+			{Camden}},\ }\href {https://doi.org/10.1021/jp3094098} {\bibfield  {journal}
+		{\bibinfo  {journal} {Journal of Physical Chemistry C}\ }\textbf {\bibinfo
+			{volume} {117}},\ \bibinfo {pages} {3046} (\bibinfo {year}
+		{2013})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Milojevich}\ \emph {et~al.}(2011)\citenamefont
+		{Milojevich}, \citenamefont {Silverstein}, \citenamefont {Jensen},\ and\
+		\citenamefont {Camden}}]{Milojevich2011}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~B.}\ \bibnamefont
+			{Milojevich}}, \bibinfo {author} {\bibfnamefont {D.~W.}\ \bibnamefont
+			{Silverstein}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+			{Jensen}},\ and\ \bibinfo {author} {\bibfnamefont {J.~P.}\ \bibnamefont
+			{Camden}},\ }\href {https://doi.org/10.1021/ja2054622} {\bibfield  {journal}
+		{\bibinfo  {journal} {Journal of the American Chemical Society}\ }\textbf
+		{\bibinfo {volume} {133}},\ \bibinfo {pages} {14590} (\bibinfo {year}
+		{2011})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Kundu}\ \emph {et~al.}(2022)\citenamefont {Kundu},
+		\citenamefont {Roy}, \citenamefont {Fleming},\ and\ \citenamefont
+		{Makri}}]{Kundu2022}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+			{Kundu}}, \bibinfo {author} {\bibfnamefont {P.~P.}\ \bibnamefont {Roy}},
+		\bibinfo {author} {\bibfnamefont {G.~R.}\ \bibnamefont {Fleming}},\ and\
+		\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Makri}},\ }\href
+	{https://doi.org/10.1021/acs.jpcb.2c00846} {\bibfield  {journal} {\bibinfo
+			{journal} {Journal of Physical Chemistry B}\ }\textbf {\bibinfo {volume}
+			{126}},\ \bibinfo {pages} {2899} (\bibinfo {year} {2022})}\BibitemShut
+	{NoStop}%
+	\bibitem [{\citenamefont {Myers}\ \emph {et~al.}(1982)\citenamefont {Myers},
+		\citenamefont {Mathies}, \citenamefont {Tannor},\ and\ \citenamefont
+		{Heller}}]{Myers1982}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~B.}\ \bibnamefont
+			{Myers}}, \bibinfo {author} {\bibfnamefont {R.~A.}\ \bibnamefont {Mathies}},
+		\bibinfo {author} {\bibfnamefont {D.~J.}\ \bibnamefont {Tannor}},\ and\
+		\bibinfo {author} {\bibfnamefont {E.~J.}\ \bibnamefont {Heller}},\ }\href
+	{https://doi.org/10.1063/1.444339} {\bibfield  {journal} {\bibinfo  {journal}
+			{Journal of Chemical Physics}\ }\textbf {\bibinfo {volume} {77}},\ \bibinfo
+		{pages} {3857} (\bibinfo {year} {1982})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Li}\ and\ \citenamefont {Myers}(1990)}]{Li1990}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
+			{Li}}\ and\ \bibinfo {author} {\bibfnamefont {A.~B.}\ \bibnamefont {Myers}},\
+	}\href {https://doi.org/10.1021/j100373a031} {\bibfield  {journal} {\bibinfo
+			{journal} {Journal of Physical Chemistry}\ }\textbf {\bibinfo {volume}
+			{94}},\ \bibinfo {pages} {4051} (\bibinfo {year} {1990})}\BibitemShut
+	{NoStop}%
+	\bibitem [{\citenamefont {Gong}\ \emph {et~al.}(2015)\citenamefont {Gong},
+		\citenamefont {Tian}, \citenamefont {Duan},\ and\ \citenamefont
+		{Luo}}]{Gong2015}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {Z.-Y.}\ \bibnamefont
+			{Gong}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Tian}}, \bibinfo
+		{author} {\bibfnamefont {S.}~\bibnamefont {Duan}},\ and\ \bibinfo {author}
+		{\bibfnamefont {Y.}~\bibnamefont {Luo}},\ }\href
+	{https://doi.org/10.1021/acs.jctc.5b00761} {\bibfield  {journal} {\bibinfo
+			{journal} {Journal of Chemical Theory and Computation}\ }\textbf {\bibinfo
+			{volume} {11}},\ \bibinfo {pages} {5385} (\bibinfo {year}
+		{2015})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Brennan}\ \emph {et~al.}(2024)\citenamefont
+		{Brennan}, \citenamefont {Choi}, \citenamefont {Soilis}, \citenamefont
+		{Rosi}, \citenamefont {Johnson},\ and\ \citenamefont
+		{Frontiera}}]{Brennan2024}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+			{Brennan}}, \bibinfo {author} {\bibfnamefont {T.~H.}\ \bibnamefont {Choi}},
+		\bibinfo {author} {\bibfnamefont {Z.~M.}\ \bibnamefont {Soilis}}, \bibinfo
+		{author} {\bibfnamefont {N.~L.}\ \bibnamefont {Rosi}}, \bibinfo {author}
+		{\bibfnamefont {J.~K.}\ \bibnamefont {Johnson}},\ and\ \bibinfo {author}
+		{\bibfnamefont {R.}~\bibnamefont {Frontiera}},\ }\href
+	{https://doi.org/10.1063/5.0204383} {\bibfield  {journal} {\bibinfo
+			{journal} {Journal of Chemical Physics}\ }\textbf {\bibinfo {volume} {161}},\
+		\bibinfo {pages} {034701} (\bibinfo {year} {2024})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Desiderio}\ and\ \citenamefont
+		{Hudson}(1979)}]{Desiderio1979}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~A.}\ \bibnamefont
+			{Desiderio}}\ and\ \bibinfo {author} {\bibfnamefont {B.~S.}\ \bibnamefont
+			{Hudson}},\ }\href {https://doi.org/10.1016/0009-2614(79)87146-8} {\bibfield
+		{journal} {\bibinfo  {journal} {Chemical Physics Letters}\ }\textbf {\bibinfo
+			{volume} {61}},\ \bibinfo {pages} {445} (\bibinfo {year} {1979})}\BibitemShut
+	{NoStop}%
+	\bibitem [{\citenamefont {Dick}\ and\ \citenamefont
+		{Hochstrasser}(1983)}]{Dick83_1}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
+			{Dick}}\ and\ \bibinfo {author} {\bibfnamefont {R.~M.}\ \bibnamefont
+			{Hochstrasser}},\ }\href {https://doi.org/10.1063/1.445086} {\bibfield
+		{journal} {\bibinfo  {journal} {Journal of Chemical Physics}\ }\textbf
+		{\bibinfo {volume} {78}},\ \bibinfo {pages} {3398} (\bibinfo {year}
+		{1983})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Carlson}\ and\ \citenamefont
+		{Wright}(1990)}]{Carlson1990line}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~J.}\ \bibnamefont
+			{Carlson}}\ and\ \bibinfo {author} {\bibfnamefont {J.~C.}\ \bibnamefont
+			{Wright}},\ }\href {https://doi.org/10.1016/0022-2852(90)90256-P} {\bibfield
+		{journal} {\bibinfo  {journal} {Journal of Molecular Spectroscopy}\ }\textbf
+		{\bibinfo {volume} {143}},\ \bibinfo {pages} {1} (\bibinfo {year}
+		{1990})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Carlson}(1992)}]{RN410}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~J.}\ \bibnamefont
+			{Carlson}},\ }\href {https://doi.org/10.1016/0301-0104(92)87017-4} {\bibfield
+		{journal} {\bibinfo  {journal} {Chemical Physics}\ }\textbf {\bibinfo
+			{volume} {166}},\ \bibinfo {pages} {177} (\bibinfo {year}
+		{1992})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Yurs}\ \emph {et~al.}(2012)\citenamefont {Yurs},
+		\citenamefont {Block}, \citenamefont {Pakoulev}, \citenamefont {Selinsky},
+		\citenamefont {Jin},\ and\ \citenamefont {Wright}}]{Yurs2012}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.~A.}\ \bibnamefont
+			{Yurs}}, \bibinfo {author} {\bibfnamefont {S.~B.}\ \bibnamefont {Block}},
+		\bibinfo {author} {\bibfnamefont {A.~V.}\ \bibnamefont {Pakoulev}}, \bibinfo
+		{author} {\bibfnamefont {R.~S.}\ \bibnamefont {Selinsky}}, \bibinfo {author}
+		{\bibfnamefont {S.}~\bibnamefont {Jin}},\ and\ \bibinfo {author}
+		{\bibfnamefont {J.~C.}\ \bibnamefont {Wright}},\ }\href
+	{https://doi.org/10.1021/jp3014139} {\bibfield  {journal} {\bibinfo
+			{journal} {Journal of Physical Chemistry C}\ }\textbf {\bibinfo {volume}
+			{116}},\ \bibinfo {pages} {5546} (\bibinfo {year} {2012})}\BibitemShut
+	{NoStop}%
+	\bibitem [{\citenamefont {Riebe}\ and\ \citenamefont {Wright}(1988)}]{RN471}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~T.}\ \bibnamefont
+			{Riebe}}\ and\ \bibinfo {author} {\bibfnamefont {J.~C.}\ \bibnamefont
+			{Wright}},\ }\href {https://doi.org/10.1063/1.453939} {\bibfield  {journal}
+		{\bibinfo  {journal} {Journal of Chemical Physics}\ }\textbf {\bibinfo
+			{volume} {88}},\ \bibinfo {pages} {2981} (\bibinfo {year}
+		{1988})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Xu}\ \emph {et~al.}(1997)\citenamefont {Xu},
+		\citenamefont {Shear},\ and\ \citenamefont {Webb}}]{Xu1997}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+			{Xu}}, \bibinfo {author} {\bibfnamefont {J.~B.}\ \bibnamefont {Shear}},\ and\
+		\bibinfo {author} {\bibfnamefont {W.~W.}\ \bibnamefont {Webb}},\ }\href
+	{https://doi.org/10.1021/ac961185o} {\bibfield  {journal} {\bibinfo
+			{journal} {Analytical Chemistry}\ }\textbf {\bibinfo {volume} {69}},\
+		\bibinfo {pages} {1285} (\bibinfo {year} {1997})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Levenson}\ and\ \citenamefont
+		{Bloembergen}(1974{\natexlab{a}})}]{Levenson1974_1}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~D.}\ \bibnamefont
+			{Levenson}}\ and\ \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
+			{Bloembergen}},\ }\href {https://doi.org/10.1063/1.1681198} {\bibfield
+		{journal} {\bibinfo  {journal} {Journal of Chemical Physics}\ }\textbf
+		{\bibinfo {volume} {60}},\ \bibinfo {pages} {1323} (\bibinfo {year}
+		{1974}{\natexlab{a}})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Levenson}\ and\ \citenamefont
+		{Bloembergen}(1974{\natexlab{b}})}]{Levenson1974_2}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~D.}\ \bibnamefont
+			{Levenson}}\ and\ \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
+			{Bloembergen}},\ }\href {https://doi.org/10.1103/PhysRevB.10.4447} {\bibfield
+		{journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
+			{10}},\ \bibinfo {pages} {4447} (\bibinfo {year}
+		{1974}{\natexlab{b}})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Bersohn}\ \emph {et~al.}(1966)\citenamefont
+		{Bersohn}, \citenamefont {Pao},\ and\ \citenamefont {Frisch}}]{Bersohn1966}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+			{Bersohn}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Pao}},\ and\
+		\bibinfo {author} {\bibfnamefont {H.~L.}\ \bibnamefont {Frisch}},\ }\href
+	{https://doi.org/10.1063/1.1728092} {\bibfield  {journal} {\bibinfo
+			{journal} {Journal of Chemical Physics}\ }\textbf {\bibinfo {volume} {45}},\
+		\bibinfo {pages} {3184} (\bibinfo {year} {1966})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Kauranen}\ and\ \citenamefont
+		{Persoons}(1996)}]{Kauranen1996}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+			{Kauranen}}\ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+			{Persoons}},\ }\href {https://doi.org/10.1063/1.471051} {\bibfield  {journal}
+		{\bibinfo  {journal} {Journal of Chemical Physics}\ }\textbf {\bibinfo
+			{volume} {104}},\ \bibinfo {pages} {3445} (\bibinfo {year}
+		{1996})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Du}\ \emph {et~al.}(1994)\citenamefont {Du},
+		\citenamefont {Freysz},\ and\ \citenamefont {Shen}}]{Du1994}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {Q.}~\bibnamefont
+			{Du}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Freysz}},\ and\
+		\bibinfo {author} {\bibfnamefont {Y.~R.}\ \bibnamefont {Shen}},\ }\href
+	{https://doi.org/10.1103/PhysRevLett.72.238} {\bibfield  {journal} {\bibinfo
+			{journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {72}},\ \bibinfo
+		{pages} {238} (\bibinfo {year} {1994})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Shen}(2003)}]{RN133}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.~R.}\ \bibnamefont
+			{Shen}},\ }\href@noop {} {\emph {\bibinfo {title} {The Principles of
+				Nonlinear Optics}}}\ (\bibinfo  {publisher} {Wiley},\ \bibinfo {year}
+	{2003})\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Piontek}\ and\ \citenamefont
+		{Borguet}(2023)}]{Piontek2023_1}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~M.}\ \bibnamefont
+			{Piontek}}\ and\ \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+			{Borguet}},\ }\href {https://doi.org/10.1016/j.surfrep.2023.100606}
+	{\bibfield  {journal} {\bibinfo  {journal} {Surface Science Reports}\
+		}\textbf {\bibinfo {volume} {78}},\ \bibinfo {pages} {100606} (\bibinfo
+		{year} {2023})}\BibitemShut {NoStop}%
+\end{thebibliography}%
 

### 2024-10-25 si.tex
first page editing

@@
 The Hamiltonians are quantum harmonic oscillators.
-The solutions to the harmonic oscillator Hamiltonian are well known, and their position space wavefunctions are
+The harmonic oscillator wavefunctions are well known, and their position space forms are
 \begin{equation}
-	\psi_m(q) = \langle q | m \rangle = N_m H_m(q) \exp(-q^2/2),
+	\psi_m(q) = \langle q | m \rangle = N_m H_m(q) \exp(-\frac{q^2}{2}),
 \end{equation}
-where $N_m = (m! \ 2^m \pi^{\frac{1}{2}})^{-\frac{1}{2}}$ is the normalization factor and $H_m$ is the $m^{th}$ Hermite Polynomial.\cite{RN230, MorseFeshbach}
+where $N_m = (m! \ 2^m \pi^{\frac{1}{2}})^{-\frac{1}{2}}$ is the normalization factor and $H_m$ is the $m^\text{th}$ Hermite Polynomial.\cite{RN230, MorseFeshbach}
 
-For an $n$-quantum excited state vibration $| \tilde{n} \rangle$, and a $m$-quantum ground state vibration $\ket{m}$, the $k^{th}$-order vibrational coupling term is
+For an $n$-quantum excited state vibration $| \tilde{n} \rangle$, and a $m$-quantum ground state vibration $\ket{m}$, the $k^\text{th}$ order vibrational coupling term is
 \begin{equation}
@@
 The matrix elements of \autoref{key} can be computed numerically, but analytic forms of the integral also exist. 
-Due to the polynomial nature of $H_v(q)$, the product $H_n(q-\Delta) q^k H_m(q)$ will also be a polynomial, so that the integral of \autoref{key} will be of the form
+Due to the polynomial nature of $H_v(q)$, the product $H_n(q-\Delta) q^k H_m(q)$ will also be a polynomial, so that the integral in \autoref{key} will be of the form
 \begin{eqnarray}
@@
 \end{eqnarray}
-for some set coefficients $a_\lambda$, to be specified later. 
-We can recast the integral into the linear combination of integrals,
+for some set coefficients $a_\lambda$ to be specified later. 
+As a result, we can recast the integral into the linear combination of integrals
 \begin{equation}\label{eq:analytic_form}

### 2024-10-29 si.tex
as adjusted 102824

@@
 %Title of paper
-\title{Supporting Information for Coherent IR-Hyper-Raman Four Wave Mixing Spectroscopy}
+\title{Supplementary Material: Coherent IR-Hyper-Raman Four Wave Mixing Spectroscopy}
 
@@
 
-\date{\today}
+%\date{\today}
 
@@
 Here, $p,q$ are the dimensionless conjugate normal mode coordinates, $\hbar\omega_{eg}$ is the energy difference between $|e)$ and $|g)$, and $\Delta$ is the dimensionless offset of the excited state surface relative to the ground state.
-The Hamiltonians are quantum harmonic oscillators.
+The Hamiltonians $H_g$ and $H_e$ are quantum harmonic oscillators.
 The harmonic oscillator wavefunctions are well known, and their position space forms are
@@
 
-For an $n$-quantum excited state vibration $| \tilde{n} \rangle$, and a $m$-quantum ground state vibration $\ket{m}$, the $k^\text{th}$ order vibrational coupling term is
+For an $n$-quantum excited state vibration $| \tilde{n} \rangle$ and a $m$-quantum ground state vibration $\ket{m}$, the $k^\text{th}$ order vibrational coupling term is
 \begin{equation}
@@
 The vibrational coupling integrals are written assuming the dipole moment is Taylor expanded about the equilibrium point of the ground state geometry ($q=0$), as done in the main text.
-Note that in the limit $\Delta \rightarrow 0$, typical harmonic oscillator selection rules are restored, as the two wells have the same vibrational Hamiltonian and thus share a subspace of orthonormal eigenstates.
+Note that in the limit $\Delta \rightarrow 0$, typical harmonic oscillator selection rules are restored as the two wells have the same vibrational Hamiltonian and thus share a subspace of orthonormal eigenstates.
 
@@
 Due to the polynomial nature of $H_v(q)$, the product $H_n(q-\Delta) q^k H_m(q)$ will also be a polynomial, so that the integral in \autoref{key} will be of the form
-\begin{eqnarray}
+\begin{eqnarray}\label{eq:Pnmkdef}
 	\int_{-\infty}^\infty \mathrm{d}q \ P_{nmk}(q) \exp(-q^2 + q\Delta), \\
@@
 for some set coefficients $a_\lambda$ to be specified later. 
-As a result, we can recast the integral into the linear combination of integrals
+As a result, we can recast \autoref{key} into the linear combination of integrals
 \begin{equation}\label{eq:analytic_form}
@@
 	\begin{split}
-		F_0(\Delta) &= \int_{-\infty}^\infty \mathrm{d}q \exp(-(q^2 - q\Delta +\frac{\Delta^2}{4} - \frac{\Delta^2}{4}))\\
+		F_0(\Delta) & =  \int_{-\infty}^\infty \mathrm{d}q \exp\left(-q^2 + q\Delta\right)\\
+		&= \int_{-\infty}^\infty \mathrm{d}q \exp(-(q^2 - q\Delta +\frac{\Delta^2}{4} - \frac{\Delta^2}{4}))\\
 		&= \exp(\frac{\Delta^2}{4}) \int_{-\infty}^\infty \mathrm{d}q \exp(-(q - \frac{\Delta}{2})^2) \\
-		&= \sqrt{\pi} \exp(\frac{\Delta^2}{4})
+		&= \sqrt{\pi} \exp(\frac{\Delta^2}{4}).
 	\end{split}
@@
 \end{equation}
-so we can write\footnote{Setting $-x^2 \ = \ \Delta^2/4$ (so that $x \ = \ i \Delta /2$) and using the chain rule ($\frac{\mathrm{d}}{\mathrm{d}x} =  \frac{\mathrm{d}}{\mathrm{d}\Delta}  \frac{\mathrm{d\Delta}}{\mathrm{d}x}$) provides the final result in \autoref{eq:F_solved}.}
+so we can write\footnote{
+	Rearranging the Hermite polynomial generator so that $e^{-x^2} = (-1)^n H_n(x) \frac{\mathrm{d}^n}{\mathrm{d}x^n} e^{-x^2}$, setting $x \ = \ i \Delta /2$ and using the chain rule ($\frac{\mathrm{d}}{\mathrm{d}x} =  \frac{\mathrm{d}}{\mathrm{d}\Delta}  \frac{\mathrm{d\Delta}}{\mathrm{d}x}$) provides the final result in \autoref{eq:F_solved}.
+	}
 \begin{equation}\label{eq:F_solved}
@@
 In the last line we have used the generator definition of Hermite polynomials:  $H_n(x) \equiv (-1)^n e^{x^2} \frac{\mathrm{d}^n}{\mathrm{d}x^n} e^{-x^2}$.\cite{MorseFeshbach}
+\vspace{3pt}
 
-We now will evaluate the polynomial coefficients $P(q)$.
-The Hermite polynomials of \autoref{key} can be explicitly written as 
+We now will evaluate the polynomial coefficients $P_{nmk}(q)$.
+The Hermite polynomials of \autoref{key} can be explicitly written as\cite{MorseFeshbach}
 \begin{equation}
 \begin{split}
-	H_m(q) &= \sum_{s=0}^{\left\lfloor{m/2}\right\rfloor} a_m^{(m-2s)} q^{m-2s} \\
+	H_m(q) &= \sum_{s=0}^{\left\lfloor{m/2}\right\rfloor} a_m^{(m-2s)} q^{m-2s}, \\
 	H_n(q-\Delta) &= \sum_{s=0}^{\left\lfloor{n/2}\right\rfloor}
 	a_n^{(n-2s)} (q-\Delta)^{n-2s} \\
-		&= \sum_{s=0}^{\left\lfloor{n/2}\right\rfloor} a_n^{(n-2s)} \sum_{l=0}^{n-2s} \left(-\Delta\right)^{n-2s-l} \binom{n-2s}{l} q^l
+		&= \sum_{s=0}^{\left\lfloor{n/2}\right\rfloor} a_n^{(n-2s)} \sum_{l=0}^{n-2s} \left(-\Delta\right)^{n-2s-l} \binom{n-2s}{l} q^l,
 \end{split}
 \end{equation}
-where $\left\lfloor n \right\rfloor$ denotes the \textit{floor} of $n$, $\binom{a}{b} = a! / (b!(a-b)!)$, and the Hermite coefficients are\cite{MorseFeshbach}
+where $\left\lfloor n \right\rfloor$ denotes the \textit{floor} of $n$, $\binom{a}{b} = a! / (b!(a-b)!)$,\footnote{
+	The binomial expansion, $(x-y)^m = \sum_{a=0}^m \binom{m}{a} x^a (-y)^{m-a}$, was used to rewrite $(q-\Delta)^{n-2s}$.
+} and the Hermite coefficients are
 \begin{equation}
@@
 \end{equation}
-\autoref{eq:poly_solved} is not in standard polynomial form, because the summation is not singular and coefficients in the summation may have the same power. 
+\autoref{eq:poly_solved} is not in standard polynomial form because the summation is not singular and coefficients in the summation may have the same power. 
 Further simplifications can be made to reduce recounting indices, but we do not find these simplifications essential.
-Regardless, substituting \autoref{eq:F_solved} and \autoref{eq:poly_solved} into \autoref{eq:analytic_form}, we can now evaluate the solution as:
+Regardless, substituting \autoref{eq:poly_solved} into \autoref{eq:Pnmkdef} and using the results of \autoref{eq:F_solved}, we can now evaluate \autoref{key} as:
 \begin{equation}\label{eq:general_solution}
@@
 	\frac{\left(-\Delta\right)^{n-2y-l}}{l!(n-2y-l)!}
-	H_{l+1}\left(i\frac{\Delta}{2}\right)
+	H_{l+1}\left(i\frac{\Delta}{2}\right),
 \end{split}
@@
 \begin{equation}
-	\langle \tilde{0} |q| 0 \rangle = \frac{\Delta}{2} \exp(-\frac{\Delta^2}{4})
+	\langle \tilde{0} |q| 0 \rangle = \frac{\Delta}{2} \exp(-\frac{\Delta^2}{4}),
 \end{equation}
@@
 	\frac{\sqrt{2}}{4} \left( 2 - \Delta^2 \right)
-	\exp(-\frac{\Delta^2}{4})
+	\exp(-\frac{\Delta^2}{4}),
 \end{equation}
@@
 	\frac{\sqrt{2}}{8} \left( \Delta^3 - 4 \Delta \right)
-	\exp(-\frac{\Delta^2}{4})
+	\exp(-\frac{\Delta^2}{4}).
 \end{equation}
@@
 		\frac{\left(-\Delta\right)^{n-2y-l}}{l!(n-2y-l)!}
-		H_{l+2}\left(i\frac{\Delta}{2}\right)
+		H_{l+2}\left(i\frac{\Delta}{2}\right),
 	\end{split}
@@
 	\langle \tilde{0} |q| 1 \rangle = \frac{\sqrt{2}}{4}\left( \Delta^2 + 2 \right)
-	\exp(-\frac{\Delta^2}{4})
+	\exp(-\frac{\Delta^2}{4}),
 \end{equation}
@@
 	\langle \tilde{1} |q| 1 \rangle = \frac{\sqrt{2}}{4}\left( -\Delta^3 + 2\Delta \right)
-	\exp(-\frac{\Delta^2}{4})
+	\exp(-\frac{\Delta^2}{4}),
 \end{equation}
@@
 	\langle \tilde{2} |q| 1 \rangle = \frac{1}{8} \left( \Delta^4 - 6\Delta^2 + 8 \right)
-	\exp(-\frac{\Delta^2}{4})
+	\exp(-\frac{\Delta^2}{4}).
 \end{equation}
@@
 \newpage
-\section{Impact of displacement, resonance frequencies, vibronic linewidth and molecular parameters on HDFG Spectra}
-Inspection of the $A,B$ terms in the main text show that the HDFG output is dependent upon the relative size of products of Franck-Condon factors and Herzberg-Teller integrals.
+\section{Impact of Displacement, Resonance Frequencies, Vibronic Linewidth and Molecular Parameters on HDFG Spectra}
+Inspection of the $A,B$ terms in the main text shows that the HDFG output is dependent upon the relative size of products of Franck-Condon factors and Herzberg-Teller integrals.
 For clarity, we plot the relevant product factors to assist in understanding the impact of offset on the HDFG spectra (\autoref{fig:fcht_product}).
@@
 
-It is clear from \autoref{fig:fcht_product} that the HDFG spectrum will have a significant dependence upon $\Delta$, even for small deviations from complete overlap. 
+It is clear from \autoref{fig:fcht_product} that the HDFG spectrum will have a significant dependence upon $\Delta$. 
 To this end, we plot the impact of offset ($\Delta$), vibrational frequency ($\omega_{g1,g0}$), and linewidth ($\Gamma$) on the HDFG spectrum \autoref{fig:chgdelta}, using values reported by Myers et al.
@@
 \cite{Myers1982, Brennan2024}
-We maintain the relationship $\max \left(\abs{B}/\abs{A}\right) \sim$ 0.1 at $\Delta = 0.5$ to facilitate comparison to the results in the main text.
+For all spectra presented below, we maintain the relationship $\max \left(\abs{B}/\abs{A}\right) \sim$ 0.1 at $\Delta = 0.5$ to facilitate comparison to the results in the main text.
 \pagebreak
@@
 	\caption{The impact of offset, vibrational resonance, and linewidth on HDFG spectra.
-Parameters for (a,b) follow from Myers et al., whereas parameters for (c,d) follow from Brennan et al.\cite{Myers1982, Brennan2024}
+Parameters for (a,b) follow from Myers et al.,\cite{Myers1982} whereas parameters for (c,d) follow from Brennan et al.\cite{Brennan2024}
 	In (a-d), the relationship $\max \left(\abs{B}/\abs{A}\right) \sim$ 0.1 at $\Delta = 0.5$ is enforced.
@@
 In addition to the linewidth and offset impacting the shape of the HDFG response, the sign of the molecular parameters $M^{ge}_0, \Lambda^{ge}_0, \frac{\partial M^{ge}}{\partial Q} , \frac{\partial \Lambda^{ge}}{\partial Q}$ will significantly impact the HDFG spectrum.
-As discussed in the main text, the atypical lineshape in the post-resonance region of the HDFG spectrum arises due to the sign of all four aforementioned parameters being identical.
-Changing the sign of one (or three) parameters will change the sign of $A, B$ and eliminate interference between the real and imaginary terms.  
-As an example (\autoref{fig:chgsign}), we demonstrate the resultant HDFG spectrum for \begin{eqnarray}
-	M^{ge}(q) = M^{ge}_0 \left(-1 + 0.04 q + \order{q^2}\right),  \\
-	\Lambda^{ge}(q) = \Lambda^{ge}_0 \left(1 + 0.04 q + \order{q^2}\right),
+Changing the sign of these parameters can change the sign of $A, B$ and alter the interference between the terms.  
+As a specific example (\autoref{fig:chgsign}), we demonstrate the resultant HDFG spectrum for \begin{eqnarray}
+	M^{ge}(q) = -1 + 0.04 q,  \\
+	\Lambda^{ge}(q) = 1 + 0.04 q,
 \end{eqnarray}
-i.e., $M^{ge}_0 < 0$, $\Lambda^{ge}_0, \frac{\partial M^{ge}}{\partial Q} , \frac{\partial \Lambda^{ge}}{\partial Q} > 0$.
+i.e., $M^{ge}_0 < 0$, $\Lambda^{ge}_0, \frac{\partial M^{ge}}{\partial Q} , \frac{\partial \Lambda^{ge}}{\partial Q} > 0$, keeping $\Delta = 0.5$.
 Compared to Figure 3 of the main text, the contributions from the $A, B_1$ and $B_2$ terms to $\Re(\gamma)$ and $\Im(\gamma)$ significantly change.
-In particular, $\Re(\gamma)$ and $\Im(\gamma)$ are of similar value in the post-resonance region, eliminating the interference seen in Figure 3 of the main text.
-\newpage
+In particular, $\Re(\gamma)$ and $\Im(\gamma)$ are of similar value in the post-resonance region, eliminating the destructive interference seen in Figure 3 of the main text.
+
+%\newpage
 \begin{figure}[!htbp]
@@
 	\includegraphics[width=6.675in]{figures/drsive_chgsign.png}
-	\caption{Contributions of $A, B$ to HDFG spectrum for a simple two harmonic well system, identical to the main text, except $M^{ge}(q) = M^{ge}_0 \left(-1 + 0.04 q + \order{q^2}\right)$.
+	\caption{Contributions of $A, B$ to HDFG spectrum for the simple two harmonic well system described by \autoref{Hamiltonian}, except $M^{ge}(q) = -1 + 0.04 q$.
 		(a) Potential energy surfaces for a two-well system, (b) 1D HDFG spectrum for $\Delta = 0.5$, $\omega_1 = \omega_{g1, g0}$, (c, d) real and imaginary parts of terms plotted in (b), respectively.
 		The spectra are scaled to $\max{(A+B)}$. 
-		The vibronic one and two photon absorption operators are scaled such that $\max(\abs{B}/\abs{A}) \sim$ 0.1, following Chung and Ziegler. \cite{Ziegler1988}
 } 
@@
 \end{figure}
-\pagebreak
-\section{Evaluating impact of static inhomogeneity on HDFG output}
+
+These effects have been recently observed in 1D and 2D coherent resonant Raman experiments.\cite{Fumero2020, Batignani2022}
+When the sign of $\Delta$, $M(q)$ and $\Lambda(q)$ match, interference in the output lineshape can be observed.
+Changing the absolute sign of these parameters can manipulate the interference (\autoref{fig:chgsign2}).
+HDFG therefore has the ability to discern the absolute sign of $\Delta$ and assign offsets in potential energy wells for some systems.
+
+\begin{figure}[!htbp]
+	\centering
+	\includegraphics[width=6.675in]{figures/changedeltaM.png}
+	\caption{HDFG spectra for the system described by \autoref{Hamiltonian} with $M^{ge}(q) = M^{ge}_0 + 0.04 q,\ \Lambda^{ge}(q) = 1 + 0.04 q$. 
+	The respective $\Delta, M^{0}_{ge}$ values are listed above the panels.
+	Black trace: $\abs{A+B}$, blue trace: $\abs{A}$, orange trace: $\abs{B}$.
+	The spectra are scaled to $\max{\abs{A+B}}$. 
+	} 
+	\label{fig:chgsign2}
+\end{figure}
+\newpage
+\section{Evaluating the Impact of Static Inhomogeneity on HDFG Spectra}
 In this section, the integral
@@
 Consider the integral
-\begin{equation}
-	\int_{-\infty}^{\infty} \mathrm{d}x f(x)
+\begin{equation}\label{eq:integral}
+	\int_{-\infty}^{\infty} \mathrm{d}x f(x).
 \end{equation}
-If $\int_{-\infty}^{\infty} \mathrm{d}x f(x)$ exists %is this strict enough?
-and $f(z)$ is analytic, where $z$ is a complex variable, then
+Assume \autoref{eq:integral} converges.
+If $f(z)$ is analytic on the upper half of the complex plane (except for poles on the real axis), where $z$ is a complex variable, and $f(z)$ asymptotically approaches zero with the form $\abs{Az}^{-m}$, $m > 1$, as $z \rightarrow \infty$, then
 \begin{subequations}\label{eq:generalcontour}
 	\begin{equation}
-		\int_{-\infty}^{\infty}  \mathrm{d}x f(x) = 2\pi i \sum_k \Res[f(z_k)]
+		\int_{-\infty}^{\infty}  \mathrm{d}x f(x) = 2\pi i \sum_k \Res[f(z_k)],
 	\end{equation}
-where $\Res[f(z_k)]$ refers to the residue of $f(z)$ in the upper half of the complex plane at the pole $z_k$ and the sum is taken over all the poles, i.e., non-removable singularities, of $f(z)$.
+where $\Res[f(z_k)]$ refers to the residue of $f(z)$ in the upper half of the complex plane at the pole $z_k$ and the sum is taken over all the poles, i.e., non-removable singularities, of $f(z)$.\cite{MorseFeshbach}
 Note that the residue of an n$^{\text{th}}$ order pole at $z = z_k$ is evaluated as
 	\begin{equation}
-		\Res[f(z_k)] = \lim_{z \rightarrow z_k} \frac{1}{\left(n-1\right)!} \frac{\mathrm{d}^{n-1}}{\mathrm{d}z^{n-1}} \left[f(z) (z-z_k)^n \right]
+		\Res[f(z_k)] = \lim_{z \rightarrow z_k} \frac{1}{\left(n-1\right)!} \frac{\mathrm{d}^{n-1}}{\mathrm{d}z^{n-1}} \left[f(z) (z-z_k)^n \right].
 	\end{equation}
@@
 	\begin{equation}
-		\int_{-\infty}^{\infty} \mathrm{d}x f(x) = 2\pi i \sum_k \lim_{z \rightarrow z_k} f(z) (z-z_k)
+		\int_{-\infty}^{\infty} \mathrm{d}x f(x) = 2\pi i \sum_k \lim_{z \rightarrow z_k} f(z) (z-z_k).
 	\end{equation}
@@
 \subsection{Anti-correlated Modes}
-For anti-correlated modes ($c = -1$), the poles ($\xi_k$) are situated in the complex plane as shown in \autoref{fig:contours}a.
+For anti-correlated modes ($c = -1$), the poles are situated in the complex plane as shown in \autoref{fig:contours}a.
 For c = -1, there are four poles: $\pm i \sigma, \Delta_{ga}, \Delta_{ba}$. 
@@
 			&= 2\eta_{ijkl} \sigma i \frac{1}{2i\sigma} \frac{1}{\Delta_{ga} - i\sigma} \frac{1}{\Delta_{ba} - i\sigma}\\
-			&= \frac{\eta_{ijkl}}{\left(\Delta_{ga}-i\sigma\right)\left(\Delta_{ba}-i \sigma\right)}\\
+			&= \frac{\eta_{ijkl}}{\left(\Delta_{ga}-i\sigma\right)\left(\Delta_{ba}-i \sigma\right)}.\\
 		\end{split}
@@
 \subsection{Correlated Modes}
-For correlated modes, the poles are situated in the complex plane as shown in \autoref{fig:contours}b.
+For correlated modes ($c = 1$), the poles are situated in the complex plane as shown in \autoref{fig:contours}b.
 We evaluate along the contour that encloses the poles $\{i\sigma, -\Delta_{ba}\}$.
@@
 			&= 2 \eta_{ijkl} i \sigma \left(\frac{1}{2 i \sigma} \frac{1}{\Delta_{ga} - i\sigma} \frac{1}{\Delta_{ba} + i\sigma} \right) + 2\eta_{ijkl} i \sigma \left(\frac{1}{\sigma^2 + \Delta_{ba} ^2} \frac{1}{\Delta_{ga} + \Delta_{ba}} \right)\\
-			&= \frac{\eta_{ijkl}}{\Delta_{ba} + i \sigma} \left(\frac{1}{\Delta_{ga} - i \sigma} + \frac{2i\sigma}{(\Delta_{ba} - i \sigma)(\Delta_{ga} + \Delta_{ba})}\right)\\
+			&= \frac{\eta_{ijkl}}{\Delta_{ba} + i \sigma} \left(\frac{1}{\Delta_{ga} - i \sigma} + \frac{2i\sigma}{(\Delta_{ba} - i \sigma)(\Delta_{ga} + \Delta_{ba})}\right).\\
 		\end{split}

### 2024-10-29 figures/2D_spec_chgsign_2.py

@@ -1,0 +1,195 @@
+import numpy as np
+import WrightTools as wt
+import matplotlib.pyplot as plt 
+import pathlib
+
+wt.artists.apply_rcparams(kind="publication")
+
+save = True
+fontsize = 14
+here = pathlib.Path(__file__).resolve().parent
+
+#make figure
+cols = [1, 1, 1, 1] 
+aspects = [[[0, 0], 1], [[1, 0], 1], [[2, 0], 1], [[3, 0], 1]] 
+
+
+
+"""Defining Franck Condon and Herzberg Teller integrals"""
+'''fc integrals'''
+#<a|b> == |a> is on the ES and |b> is on the GS.
+
+def f00(q): #<0|0>
+    return np.exp(-q**2/4)
+
+def f01(q): #<0|1>
+    return q/(np.sqrt(2)) * f00(q)
+
+def f10(q): #<1|0>
+    return -1*f01(q)
+
+def f11(q): #<1|1>
+    return (1 - q**2/2) *f00(q)
+
+def f02(q): #<0|2>
+    return q**2/(2*np.sqrt(2)) * f00(q)
+
+def f20(q): #<2|0>
+    return f02(q)
+   
+def f21(q): #<2|1>
+    return -q * (1 - q**2/4) *f00(q)
+
+'''ht integrals'''
+def h00(q): #<0|Q|0>
+    return q/2 * f00(q)
+
+def h01(q): #<0|Q|1>
+    return 1/np.sqrt(2) * (1 + q**2 /2) * f00(q)
+
+def h10(q): #<1|Q|0>
+    return 1/np.sqrt(2) * (1 - q**2 /2) * f00(q)
+
+def h11(q): #<1|Q|1>
+    return -q/2 * (-1 + q**2 / 2) * f00(q)
+
+def h12(q): #<1|Q|2>
+    return (-1/8) * (q**4 - 2*q**2 - 8) * f00(q)
+
+def h21(q): #<2|Q|1>
+    return (1/8)*(8 - 6*q**2 + q**4) * f00(q)
+
+def h20(q): #<2|Q|0>
+    return -q/np.sqrt(2) * (1 - q**2 /4) * f00(q)
+
+
+#define resonance denominator
+def Deltaevgo(n,x,l,G):
+    weg = 30000
+    return 1/(weg + l*n - x - 1j*G) #assuming the |0> -> |n> transiton is l*n  cm^-1
+
+
[…]

### 2024-10-29 figures/contours.py

@@ -1,9 +1,4 @@
-# -*- coding: utf-8 -*-
-"""
-Created on Tue Jan 17 09:28:39 2023
 
-@author: rpm
-"""
 import numpy as np
 import WrightTools as wt
 import matplotlib.pyplot as plt 
@@ -32,7 +27,7 @@ fig, gs = wt.artists.create_figure(width="dissertation", nrows=1, cols=cols, asp
 ax0 = plt.subplot(gs[0,0]) 
 
 #insert the poles
-poles = [2, -2, -2.6, -3.5]
+poles = [3.5, -3.5, -1.3, -2.2]
 points = [0, 0, 2, 3]
 
 
@@ -48,7 +43,7 @@ for i in [0,1,2,3]:
 ax1 = plt.subplot(gs[0,1]) 
 
 #insert the poles
-poles = [2, -2, -2.6, 3.5]
+poles = [3.5, -3.5, -1.3, 2.2]
 points = [0, 0, 2, -3]
 
 

### 2024-10-29 build.py
edit build.py

@@ -3,7 +3,7 @@ import subprocess
 import platform
 import click
 
-#osf_project = "2amkq"
+osf_project = "2amkq"
 here = pathlib.Path(__file__).resolve().parent
 
 
@@ -48,6 +48,7 @@ def _build_figures():
     print_then_call(python, str(here / "figures" / "contours.py"))
     print_then_call(python, str(here / "figures" / "plotting_fcht.py"))
     print_then_call(python, str(here / "figures" / "varying_delta.py"))
+    print_then_call(python, str(here / "figures" / "hdfgspec_chg_signs.py"))
 
 @click.group()
 def main():

### 2024-11-12 si.tex
minor modifications to si and contour fig
made dots overlay dotted axes
minor issues with language in si adjusted
added explicit reference to section 4.5 in Morse and Feshbach

@@
 so we can write\footnote{
-	Rearranging the Hermite polynomial generator so that $e^{-x^2} = (-1)^n H_n(x) \frac{\mathrm{d}^n}{\mathrm{d}x^n} e^{-x^2}$, setting $x \ = \ i \Delta /2$ and using the chain rule ($\frac{\mathrm{d}}{\mathrm{d}x} =  \frac{\mathrm{d}}{\mathrm{d}\Delta}  \frac{\mathrm{d\Delta}}{\mathrm{d}x}$) provides the final result in \autoref{eq:F_solved}.
+	Rearranging the Hermite polynomial generator so that $\frac{\mathrm{d}^n}{\mathrm{d}x^n} e^{-x^2} = (-1)^n H_n(x) e^{-x^2}$, setting $x \ = \ i \Delta /2$ and using the chain rule ($\frac{\mathrm{d}}{\mathrm{d}x} =  \frac{\mathrm{d}}{\mathrm{d}\Delta}  \frac{\mathrm{d\Delta}}{\mathrm{d}x}$) provides the final result in \autoref{eq:F_solved}.
 	}
@@
 	M^{ge}(q) = -1 + 0.04 q,  \\
-	\Lambda^{ge}(q) = 1 + 0.04 q,
+	\Lambda^{ge}(q) = 0.1 + 0.004 q,
 \end{eqnarray}
@@
 In particular, $\Re(\gamma)$ and $\Im(\gamma)$ are of similar value in the post-resonance region, eliminating the destructive interference seen in Figure 3 of the main text.
+Similar effects have been recently observed in 1D and 2D coherent resonant Raman experiments.\cite{Fumero2020, Batignani2022}
+When the sign of $\Delta$, $M(q)$ and $\Lambda(q)$ match, interference in the output lineshape can be observed.
+Changing the absolute sign of these parameters can manipulate the interference (\autoref{fig:chgsign2}).
+HDFG therefore has the ability to discern the absolute sign of $\Delta$ and assign offsets in potential energy wells for some systems.
 
@@
 
-These effects have been recently observed in 1D and 2D coherent resonant Raman experiments.\cite{Fumero2020, Batignani2022}
-When the sign of $\Delta$, $M(q)$ and $\Lambda(q)$ match, interference in the output lineshape can be observed.
-Changing the absolute sign of these parameters can manipulate the interference (\autoref{fig:chgsign2}).
-HDFG therefore has the ability to discern the absolute sign of $\Delta$ and assign offsets in potential energy wells for some systems.
-
 \begin{figure}[!htbp]
@@
 	\includegraphics[width=6.675in]{figures/changedeltaM.png}
-	\caption{HDFG spectra for the system described by \autoref{Hamiltonian} with $M^{ge}(q) = M^{ge}_0 + 0.04 q,\ \Lambda^{ge}(q) = 1 + 0.04 q$. 
+	\caption{HDFG spectra for the system described by \autoref{Hamiltonian} with $M^{ge}(q) = M^{ge}_0 + 0.04 q,\ \Lambda^{ge}(q) = 0.01 + 0.004 q$. 
 	The respective $\Delta, M^{0}_{ge}$ values are listed above the panels.
@@
 Integrals such as \autoref{generalcontour} can be evaluated by using the Residue theorem.\cite{MorseFeshbach}
-For clarity, we briefly outline the technique.
+For clarity, we briefly outline the technique.\footnote{See \S 4.5 of Morse and Feshbach \cite{MorseFeshbach} for more details.} 
 Consider the integral
@@
 Assume \autoref{eq:integral} converges.
-If $f(z)$ is analytic on the upper half of the complex plane (except for poles on the real axis), where $z$ is a complex variable, and $f(z)$ asymptotically approaches zero with the form $\abs{Az}^{-m}$, $m > 1$, as $z \rightarrow \infty$, then
+If $f(z)$ is analytic on the upper half of the complex plane (except for poles not on the real axis), where $z$ is a complex variable, and $\abs{f(z)}$ asymptotically approaches zero with the form $\abs{Az}^{-m}$, $m > 1$, as $\abs{z} \rightarrow \infty$, then
 \begin{subequations}\label{eq:generalcontour}
@@
 	\end{equation}
-where $\Res[f(z_k)]$ refers to the residue of $f(z)$ in the upper half of the complex plane at the pole $z_k$ and the sum is taken over all the poles, i.e., non-removable singularities, of $f(z)$.\cite{MorseFeshbach}
+where $\Res[f(z_k)]$ refers to the residue of $f(z)$ at the pole $z_k$ and the sum is taken over all the poles of $f(z)$ in the upper half of the complex plane.\cite{MorseFeshbach}
 Note that the residue of an n$^{\text{th}}$ order pole at $z = z_k$ is evaluated as
@@
 \end{subequations}
-Note that in \autoref{eq:generalcontour}, the integrals are evaluated along a contour which wraps all the poles in the positive half of the complex plane.
+Note that in \autoref{eq:generalcontour}, the integrals are evaluated along a counter-clockwise contour that wraps all the poles in the positive half of the complex plane.
 
@@
 	\caption{Poles (blue dots) and contours (black lines) used to evaluate \autoref{generalcontour} for (a) anti-correlated ($c=-1$) and (b) correlated ($c=1$) modes. 
+	The contours are oriented counter-clockwise.
 	} 

### 2024-11-12 figures/contours.py

@@ -34,7 +34,7 @@ points = [0, 0, 2, 3]
 #plot it
 ax0.plot(x, contour(x), linewidth = '2', color = 'black')
 for i in [0,1,2,3]:
-    ax0.scatter(points[i], poles[i], color = 'blue')
+    ax0.scatter(points[i], poles[i], color = 'blue', zorder = 4)
     label = [r'$\mathsf{i \sigma}$', r'$\mathsf{-i \sigma}$', r'$\mathsf{\Delta_{ga}}$', r'$\mathsf{\Delta_{ba}}$']
     ax0.text(points[i]+0.1, poles[i]+0.1, label[i], fontsize = 24)
 

### 2024-11-21 si.tex
minor change
a small goof in a figure caption.
final edits

@@
 Changing the sign of these parameters can change the sign of $A, B$ and alter the interference between the terms.  
-As a specific example (\autoref{fig:chgsign}), we demonstrate the resultant HDFG spectrum for \begin{eqnarray}
+As a specific example (\autoref{fig:chgsign}), we demonstrate the resultant HDFG spectrum for \begin{eqnarray}\label{eq:newdipoles}
 	M^{ge}(q) = -1 + 0.04 q,  \\
@@
 	\includegraphics[width=6.675in]{figures/drsive_chgsign.png}
-	\caption{Contributions of $A, B$ to HDFG spectrum for the simple two harmonic well system described by \autoref{Hamiltonian}, except $M^{ge}(q) = -1 + 0.04 q$.
+	\caption{Contributions of $A, B$ to HDFG spectrum for the system described in Figure 3 of the main text, but with $M^{ge}(q)$ described by \autoref{eq:newdipoles}.
 		(a) Potential energy surfaces for a two-well system, (b) 1D HDFG spectrum for $\Delta = 0.5$, $\omega_1 = \omega_{g1, g0}$, (c, d) real and imaginary parts of terms plotted in (b), respectively.
@@
 	\includegraphics[width=6.675in]{figures/changedeltaM.png}
-	\caption{HDFG spectra for the system described by \autoref{Hamiltonian} with $M^{ge}(q) = M^{ge}_0 + 0.04 q,\ \Lambda^{ge}(q) = 0.01 + 0.004 q$. 
+	\caption{HDFG spectra for the system described by \autoref{Hamiltonian} with $M^{ge}(q) = M^{ge}_0 + 0.04 q,\ \Lambda^{ge}(q) = 0.1 + 0.004 q$. 
 	The respective $\Delta, M^{0}_{ge}$ values are listed above the panels.

### 2024-11-21 figures/contours.py

@@ -49,7 +49,7 @@ points = [0, 0, 2, -3]
 
 #plot it
 for i in [0,1,2,3]:
-    ax1.scatter(points[i], poles[i], color = 'blue')
+    ax1.scatter(points[i], poles[i], color = 'blue', zorder = 4)
     label = [r'$\mathsf{i \sigma}$', r'$\mathsf{-i \sigma}$', r'$\mathsf{\Delta_{ga}}$', r'$\mathsf{-\Delta_{ba}}$']
     ax1.text(points[i]+0.1, poles[i]+0.1, label[i], fontsize = 24)
 ax0.set_title('Anti-Correlated (c = -1)')
@@ -69,11 +69,6 @@ for ax in [ax0, ax1]:
     ax.vlines(ymin=-10, ymax =10, x = 0, color = 'grey', linestyle = '--', linewidth = 1, zorder = 1)
     ax.set_yticks(ticks = [])
     ax.set_xticks(ticks = [])
-    
-    # j = [0]
-    # for i in j:
-    #     ax.text(i-.1, contour(i)-.17, r'$\mathsf{<}$', fontsize = 24, alpha = 1, color = 'r', weight='bold')    
-    #     ax.text(i-.1, -.17, r'$\mathsf{>}$', fontsize = 24, color = 'r') 
     
     
 for i, ax in enumerate(fig.axes):
